### 2018-07-05 journal/main.tex
Added journal files

\documentclass[a4paper]{article}

%% Language and font encodings
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}

%% Sets page size and margins
\usepackage[a4paper,top=3cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

%% Useful packages
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage[caption=false]{subfig} % subfigures.  false option prevents conflicts in caption styling with other packages
\usepackage{float}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

%% Custom commands
\newcommand{\DatestampYMD}[3]{\mbox{#1-#2-#3}}
\newcommand{\entry}[3]{\newpage\section*{\DatestampYMD{#1}{#2}{#3}} }

\title{Research Journal}
\author{Stephen Phillips}
\date{June 2018 to Present}

\begin{document}

\maketitle

\entry{2018}{06}{27}
This entry is a bit of catch up, giving some of my initial work and experiments.
\subsection*{Brief High Level Idea}
We are trying to use Graph Neural Networks for feature matching, using cycle consistency as a loss. What this comes out to in practice is low rank matrix factorization. However just optimizing typical losses such as the Frobenius norm with a rank loss may not capture real-world noise quite properly. So the hope is with Neural Nets we can add additional losses to the training for it to incorporate into its factorization at training time, then it will know how to properly do that at testing time. For now we stick with the aforementioned Frobenius norm to start training.

\subsection*{Literature Review}
\begin{itemize}
\item ``Geometric Deep Learning: Going beyond Euclidean data'' Bronstein et al. 2017. A survey paper going over many types of non-Euclidean networks. Here we use the non-fixed structure neural networks. In particular Kipf and Welling, described below.
\item ``Semi-Supervised Classification with Graph Convolutional Networks'' Kipf and Welling 2017. This paper takes the graph Laplacian and uses is to multiply a node embedding. Combine this with weights and non-linearities you have a fully functional neural network. There was some criticism of this method from \href{https://www.inference.vc/how-powerful-are-graph-convolutions-review-of-kipf-welling-2016-2/}{this blog post} stating that these reduce to rather simple operations when put on a regular graph. Regardless we will be using this method here.
\item ``The graph neural network model'' Scarselli et al. 2009. This is a more complicated framework, similar to the previous one but instead using polynomials of the Laplacian instead of just the Laplacian itself. This gives it more expressively but also means the local nature of it fails to some degree. This is why I will be using Kipf and Welling as my basis for now. If that fails, I may try this.
\item ``Relational inductive biases, deep learning, and graph networks'' Battaglia et al. 2018. This is a high level introduction to a new notion of Graph Neural Networks, with operations on the edges as well as the nodes. This could be potentially quite helpful but unfortunately there is no implementation of this right now, so using it would be difficult. For potential future work.
\end{itemize}

\subsection*{Code base}
Initially this was implemented in PyTorch but due to the potential future need for sparse matrices I switched to TensorFlow. The modules of the code are:
\begin{itemize}
\item \texttt{options.py} - This handles all configuration options for building the models, the dataset, and the learning parameters - every other file depends on this one
\item \texttt{model.py} - File with all the models in it - specifically for graph neural networks. All models are sub-classes of \texttt{DenseGraphLayerWeights} which gives a lot of convenience functions for graph networks
\item \texttt{sim\_graphs.py} - Handles synthetic data creation.
\item \texttt{data\_util.py} - Handles generic data creating and loading for graph networks. Has a feature if tensorflow is not able to load it can ignore it and only use Numpy.
\item \texttt{train.py} - Main training file, implements data loading and feeding to neural net pipe-line
\item \texttt{myutils.py} - Lots of convenience functions
\item \texttt{tfutils.py} - Lots of convenience functions but for TensorFlow
\item \texttt{experiment.py} - This is where all the plots are generated. 
\end{itemize}

\subsection*{Exact model}
The input to our neural network is an undirected graph with each node having a starting embedding. The target is each node having an embedding. The graph structure is given to us as an $n \times n$ Adjacenty matrix, and the embeddings as an $n \times m$ matrix $E$ (typically $m << n$). Thus using Kipf and Welling as our guide, we have our update rule for layer $i$ as:
\begin{align*}
D = \mathrm{diag}((A + I) \mathbf{1}) \\
L = D^{-1/2}(A + I)D^{-1/2} \\
E_{i+1} = \sigma \left(LE_{i} W^{(i+1)}\right) + E_{i} U^{(i+1)}
\end{align*}
With $W^{(i+1)}$ and $U^{(i+1)}$ being a $m_i \times m_{i+1}$ matrix, and $E_i$ being a $n \times m_i$ matrix (with $E_0 = E$). $\sigma$ here is our non-linearity. The $U$ weights are for skip connections. The final layer $F$ is each row of the final embedding $E_N$ normalized to norm 1 (here our network has $N$ layers).

This model seems reasonable. Consider the special case if $m_i = 1$ for all $i$ and $\sigma(x) = x / \|x\|$. Setting the weights to be 1, we get $E_{i+1} = L E_i / \| L E_i \|$. This is exactly the power method of finding the leading eigenvectors, which is an approximation of cycle consistency.

\subsection*{Experiments}
First this was generated using 3 random $25 \times 25$ permutation matrices stacked together to form a $75 \times 25$  matrix as the ground truth node embedding vectors $E_{gt}$, then using the outer product to make a $75 \times 75$ matrix $S_{gt} = E_{gt} E_{gt}^\top$, which serves as the ground truth graph. We have some noise function $\nu$ and so the given graph is $A = \nu(E_{gt})$. We get our output embedding $F$ So this is essentially testing if we can do matrix factorization via Graph Neural Networks with various noise models. We have a very noisy initial embedding. To compute the error, we compute the factored similarity matrix, which means we normalize each embedding row then do an outer product. For the figures we display the node embedding vectors grouped by the ground truth labels, so the true plots look like a diagonal matrix.

Figure \ref{fig:baseline_plot} shows an example of ground truth node embedding and similarities as well as the node embedding vectors and similarities of the initial embedding we use.

\begin{figure}[H]
    \centering
    % \includegraphics[width=0.7\textwidth]{figures/noiseless_sim.png}
    \subfloat[Sorted ground truth embedding and initial embedding]{
        \includegraphics[width=0.45\textwidth]{figures/baseline_embeddings.png}
        \label{fig:baseline_sub1}
    }
    \subfloat[Ground truth and initial similarity]{
        \includegraphics[width=0.45\textwidth]{figures/baseline_sim.png}
        \label{fig:baseline_sub2}
    }
    \caption{Here we show a baseline for the node embedding vectors and the final similarity matrix}
    \label{fig:baseline_plot}
\end{figure}

\subsubsection*{Noiseless Dataset}
Here we use no noise to distort it. This is equivalent to see if Neural Networks can do matrix factorization on a truly low rank matrix.
\begin{figure}[H]
    \centering
    % \includegraphics[width=0.7\textwidth]{figures/noiseless_sim.png}
    \subfloat[Typical embedding and similarity matrix of Noiseless]{
        \includegraphics[width=0.45\textwidth]{figures/synth_plot.png}
        \label{fig:noiseless_sub1}
    }
    \subfloat[Typical histogram for similarities of noiseless]{
        \includegraphics[width=0.45\textwidth]{figures/synth_hist.png}
        \label{fig:noiseless_sub2}
    }
    \caption{Here we show a baseline for the node embedding vectors and the final similarity matrix}
    \label{fig:noiseless_plot}
\end{figure}
The numerical scores come out to be:
\begin{table}[H]
    \centering
    \begin{tabular}{|c|c|} \hline
        Trained Same Point Similarity      & 1.00e+00 $\pm$ 8.07e-08  \\ \hline
        Trained Distinct Point Similarity  & 2.81e-01 $\pm$ 1.81e-01  \\ \hline
        Baseline Same Point Similarity     & 5.04e-01 $\pm$ 3.89e-01  \\ \hline
        Baseline Distinct Point Similarity & 2.56e-01 $\pm$ 2.06e-01  \\ \hline
    \end{tabular}
    \caption{Average cross similarity between points, for no noise}
    \label{tab:noiseless_table}
\end{table}

\subsubsection*{Pairwise Matrix Multiplication Noise}
Our noise model for this one $\nu$ is described by, for the block in row $i$, column $j$
\begin{equation*}
    \nu(E)_{ij} = E_i N_{ij} E_j^\top, \quad \quad N_{ij} = \theta I + (1-\theta) \sum_{k=1}^K M_{ij}^k , \quad \quad M_{ij}^{k} \sim {\Pi}(m, m)
\end{equation*}
With the constraint that $N_{ij} = N_{ji}^\top$. Here $\Pi(m,m)$ denotes the uniform distribution over the $m \times m$ permutation matrices, and $\theta$, and $K$ are parameters.

\paragraph{Parameter Set 1}
Here, $\theta = 0.9$, $K = 1$.
\begin{figure}[H]
    \centering
    % \includegraphics[width=0.7\textwidth]{figures/noiseless_sim.png}
    \subfloat[Typical embedding and similarity matrix of pairwise noise]{
        \includegraphics[width=0.45\textwidth]{figures/pairwise_plot.png}
        \label{fig:pairwise_sub1}
    }
    \subfloat[Typical histogram for similarities of pairwise noise]{
        \includegraphics[width=0.45\textwidth]{figures/pairwise_hist.png}
        \label{fig:pairwise_sub2}
    }
    \caption{Here we show a baseline for the node embedding vectors and the final similarity matrix}
    \label{fig:pairwise_plot}
\end{figure}
Note the clear separation between diagonal and off diagonal in the histogram. The numerical scores come out to be: 
\begin{table}[H]
    \centering
    \begin{tabular}{|c|c|} \hline
        Trained Same Point Similarity      & 9.97e-01 $\pm$ 4.62e-03  \\ \hline
        Trained Distinct Point Similarity  & 2.86e-01 $\pm$ 1.76e-01  \\ \hline
        Baseline Same Point Similarity     & 5.12e-01 $\pm$ 3.90e-01  \\ \hline
        Baseline Distinct Point Similarity & 2.56e-01 $\pm$ 2.06e-01  \\ \hline
    \end{tabular}
    \caption{Average cross similarity between points, for pairwise noise with $K=1$}
    \label{tab:pairwise_table}
\end{table}

\paragraph{Parameter Set 2}
Here, $\theta = 0.9$, $K = 3$.
\begin{figure}[H]
    \centering
    % \includegraphics[width=0.7\textwidth]{figures/noiseless_sim.png}
    \subfloat[Typical embedding and similarity matrix of pairwise noise]{
        \includegraphics[width=0.45\textwidth]{figures/pairwise3_plot.png}
        \label{fig:pairwise3_sub1}
    }
    \subfloat[Typical histogram for similarities of pairwise noise]{
        \includegraphics[width=0.45\textwidth]{figures/pairwise3_hist.png}
        \label{fig:pairwise3_sub2}
    }
    \caption{Here we show a baseline for the node embedding vectors and the final similarity matrix}
    \label{fig:pairwise3_plot}
\end{figure}
Note that the diagonal and off diagonal entries overlap quite a bit. The numerical scores come out to be:
\begin{table}[H]
    \centering
    \begin{tabular}{|c|c|} \hline
        Trained Same Point Similarity      & 9.96e-01 $\pm$ 6.24e-03  \\ \hline
        Trained Distinct Point Similarity  & 6.35e-01 $\pm$ 1.42e-01  \\ \hline
    \end{tabular}
    \caption{Average cross similarity between points, for pairwise noise with $K=3$}
    \label{tab:pairwise3_table}
\end{table}

\paragraph{Parameter Set 3}
Here, $\theta = 0.9$, $K = 5$.
\begin{figure}[H]
    \centering
    % \includegraphics[width=0.7\textwidth]{figures/noiseless_sim.png}
    \subfloat[Typical embedding and similarity matrix of pairwise noise]{
        \includegraphics[width=0.45\textwidth]{figures/pairwise5_plot.png}
        \label{fig:pairwise5_sub1}
    }
    \subfloat[Typical histogram for similarities of pairwise noise]{
        \includegraphics[width=0.45\textwidth]{figures/pairwise5_hist.png}
        \label{fig:pairwise5_sub2}
    }
    \caption{Here we show a baseline for the node embedding vectors and the final similarity matrix}
    \label{fig:pairwise5_plot}
\end{figure}
Note that the diagonal and off diagonal entries overlap almost completely. There is something that goes wrong, and I need to do more investigation before I can determine why. The numerical scores come out to be:
\begin{table}[H]
    \centering
    \begin{tabular}{|c|c|} \hline
        Trained Same Point Similarity      & 9.90e-01 $\pm$ 2.54e-02  \\ \hline
        Trained Distinct Point Similarity  & 5.82e-01 $\pm$ 3.91e-01  \\ \hline
    \end{tabular}
    \caption{Average cross similarity between points, for pairwise noise with $K=5$}
    \label{tab:pairwise5_table}
\end{table}

\entry{2018}{06}{27}
\subsection*{Larger Dataset Test}
So I was considering that the poor performance might have something to do with overfitting so I decided, since this is synthetic data to generate many more samples in the dataset. I got the following results for the $K=3$, slightly better than before but within noise. To put a nail in this coffin, I have been working on generating samples on the fly for training, giving effectively infinite data. Here are the current results, $\theta = 0.9$, $K = 3$.
\begin{figure}[H]
    \begin{minipage}{.45\linewidth}
        \centering
        \subfloat[Typical embedding and similarity matrix of pairwise noise]{
            \includegraphics[width=0.9\textwidth]{figures/pairwise3_large_plot.png}
            \label{fig:pairwise3_large_sub1}
        }
    \end{minipage}
    \begin{minipage}{.45\linewidth}
        \centering
        \subfloat[Typical histogram for similarities of pairwise noise]{
            \includegraphics[width=0.9\textwidth]{figures/pairwise3_large_hist.png}
            \label{fig:pairwise3_large_sub2}
        }
    \end{minipage}
    \centering
    \subfloat[Numerical results]{
        \begin{tabular}{|c|c|c|c|} \hline
                                       &    Trained Model        &    Previous Model        &    Baseline             \\ \hline
            Same Point Similarity      & 9.97e-01 $\pm$ 4.16e-03 & 9.96e-01 $\pm$ 6.24e-03 & 5.11e-01 $\pm$ 3.91e-01 \\ \hline
            Distinct Point Similarity  & 6.34e-01 $\pm$ 1.29e-01 & 6.35e-01 $\pm$ 1.42e-01 & 2.55e-01 $\pm$ 2.06e-01  \\ \hline
        \end{tabular}
        \label{fig:pairwise3_large_tab1}
    }
    \label{fig:pairwise3_large_plot}
\end{figure}

\entry{2018}{07}{02}
\subsection*{Infinite Dataset Test}
After much debugging to get the data generation during training working, we managed to run some experiments. Testing with infinite data did seem to improve generalization substantially compared to a simply larger dataset. So it seems that data is in fact a problem. We will somehow have to address this. 
\begin{figure}[H]
    \begin{minipage}{.45\linewidth}
        \centering
        \subfloat[Typical embedding and similarity matrix of pairwise noise]{
            \includegraphics[width=0.9\textwidth]{figures/pairwise3inf_plot.png}
            \label{fig:pairwise3inf_sub1}
        }
    \end{minipage}
    \begin{minipage}{.45\linewidth}
        \centering
        \subfloat[Typical histogram for similarities of pairwise noise]{
            \includegraphics[width=0.9\textwidth]{figures/pairwise3inf_hist.png}
            \label{fig:pairwise3inf_sub2}
        }
    \end{minipage}
    \centering
    \subfloat[Numerical results]{
        \begin{tabular}{|c|c|c|c|} \hline
                                       &    Trained Model        &    Previous Model        &    Baseline             \\ \hline
            Same Point Similarity      & 9.96e-01 $\pm$ 5.22e-03 & 9.97e-01 $\pm$ 4.16e-03 & 5.11e-01 $\pm$ 3.91e-01 \\ \hline
            Distinct Point Similarity  & 4.31e-01 $\pm$ 2.15e-01 & 6.34e-01 $\pm$ 1.29e-01 & 2.55e-01 $\pm$ 2.06e-01  \\ \hline
        \end{tabular}
        \label{fig:pairwise3inf_large_tab1}
    }
    \label{fig:pairwise3inf_plot}
\end{figure}
Despite this, the distinction between diagonal and off diagonal entries is not as sharp as I would like. I need to brainstorm ideas of how to handle that. There is some work on doing better selection for which edges in the averaging are relevant (e.g. Graph Attention Networks)

\entry{2018}{07}{03}
\subsection*{Infinite Dataset Test}
After much debugging to get the data generation during training working, we managed to run some experiments. Testing with infinite data did seem to improve generalization substantially compared to a simply larger dataset. So it seems that data is in fact a problem. We will somehow have to address this. 
\begin{figure}[H]
    \begin{minipage}{.45\linewidth}
        \centering
        \subfloat[Typical embedding and similarity matrix of pairwise noise]{
            \includegraphics[width=0.9\textwidth]{figures/pairwise5inf_plot.png}
            \label{fig:pairwise5inf_sub1}
        }
    \end{minipage}
    \begin{minipage}{.45\linewidth}
        \centering
        \subfloat[For comparison, the non-infinite data trained version]{
            \includegraphics[width=0.9\textwidth]{figures/pairwise5inf_plot_compare.png}
            \label{fig:pairwise5inf_sub2}
        }
    \end{minipage}
    \begin{minipage}{.9\linewidth}
        \centering
        \subfloat[Typical histogram for similarities of pairwise noise]{
            \includegraphics[width=0.5\textwidth]{figures/pairwise5inf_hist.png}
            \label{fig:pairwise5inf_sub3}
        }
    \end{minipage}
    \centering
    \subfloat[Numerical results]{
        \begin{tabular}{|c|c|c|c|} \hline
                                       &    Trained Model        &    Previous Model        &    Baseline             \\ \hline
            Same Point Similarity      & 9.97e-01 $\pm$ 3.70e-03 & 9.96e-01 $\pm$ 5.38e-03 & 5.11e-01 $\pm$ 3.91e-01 \\ \hline
            Distinct Point Similarity  & 6.71e-01 $\pm$ 1.55e-01 & 7.13e-01 $\pm$ 1.59e-01 & 2.55e-01 $\pm$ 2.06e-01  \\ \hline
        \end{tabular}
        \label{fig:pairwise5inf_tab1}
    }
    \label{fig:pairwise3inf_large_plot}
\end{figure}
It does OK, but this is still a fairly weak noise model. If the noise got more intense, we would need additional mechanisms to handle it. Hence the next mechanism.
\subsection*{Graph Attention Network Code Review}
I was looking at the aforementioned Graph Attention Network (GAT) \href{https://arxiv.org/pdf/1710.10903.pdf}{paper} and its \href{https://github.com/PetarV-/GAT}{code}.

\entry{2018}{07}{04}
\subsection*{GAT Implementation details}
After careful looking at the paper and the code for the GAT paper. After some confusing reading of the code, I figured out the way they are actually implementing it. It is more naive than I originally thought unfortunately. Let $E_k$ be the node embedding vectors at the current layer, with adjacency matrix $A$, and weight matrices $T_{k,1}, T_{k,2} \in \mathbb{R}^{n_k \times m_k}$, with $l$ being a point-wise non-linear function, and $s$ being the row-wise-softmax function:
\begin{align*}
f_1 =&\; E_k T_{k,1} \\
f_2 =&\; E_k T_{k,2} \\
Q_k =&\; l(f_1 So \mathbf{1}^\top + \mathbf{1} f_2^\top) \\
E_{k+1} =&\; \sigma \left( s(Q_k + A) E_k W_k \right)
\end{align*}
This has a few problems - This method is really dense. They have a sparse method but it computes this densely then makes it sparse. Also if you wanted to enforce the symmetry of the weights on the graph... there isn't really a simple way to do that. Except maybe doing something like using $Q_k' = (Q_k + Q_k^\top)/2$ which doesn't help the whole sparsity problem. There are some simple ways to make this sparse using for loops but I am uncertain how to do this using TensorFlow... or even PyTorch. However, as I don't see another way to learn the weights of the edges, this is what I'll be focusing on.

\subsection*{Leaky ReLU Experiments}
So inspired by the previous paper I thought I would try running experiments with the Leaky ReLU nonlinearity, just to see if it was any different. As it turns out, unsurprisingly, not too much.

\entry{2018}{07}{05}
\subsection*{Binary Cross Entropy}
Talking with others in the lab (Drew, Oleh) I realized instead of the L2 loss perhaps the Binary Cross Entropy Loss would perform better. Unfortunately this would make it less directly comparable to the optimization methods, but still I think it would worth trying. First I need to remove the

\end{document}

### 2018-07-05 journal/main.tex
More formatting

@@
 \begin{itemize}
-\item ``Geometric Deep Learning: Going beyond Euclidean data'' Bronstein et al.
-2017.
+\item ``Geometric Deep Learning: Going beyond Euclidean data'' Bronstein et al. 2017.
 A survey paper going over many types of non-Euclidean networks.
@@
 Regardless we will be using this method here.
-\item ``The graph neural network model'' Scarselli et al.
-2009.
+\item ``The graph neural network model'' Scarselli et al. 2009.
 This is a more complicated framework, similar to the previous one but instead using polynomials of the Laplacian instead of just the Laplacian itself.
@@
 If that fails, I may try this.
-\item ``Relational inductive biases, deep learning, and graph networks'' Battaglia et al.
-2018.
+\item ``Relational inductive biases, deep learning, and graph networks'' Battaglia et al. 2018.
 This is a high level introduction to a new notion of Graph Neural Networks, with operations on the edges as well as the nodes.
@@
 \subsubsection*{Noiseless Dataset}
-Here we use no noise to distort it. This is equivalent to see if Neural Networks can do matrix factorization on a truly low rank matrix.
+Here we use no noise to distort it.
+This is equivalent to see if Neural Networks can do matrix factorization on a truly low rank matrix.
 \begin{figure}[H]
@@
 \end{equation*}
-With the constraint that $N_{ij} = N_{ji}^\top$. Here $\Pi(m,m)$ denotes the uniform distribution over the $m \times m$ permutation matrices, and $\theta$, and $K$ are parameters.
+With the constraint that $N_{ij} = N_{ji}^\top$.
+Here $\Pi(m,m)$ denotes the uniform distribution over the $m \times m$ permutation matrices, and $\theta$, and $K$ are parameters.
 
@@
 \end{figure}
-Note that the diagonal and off diagonal entries overlap quite a bit. The numerical scores come out to be:
+Note that the diagonal and off diagonal entries overlap quite a bit.
+The numerical scores come out to be:
 \begin{table}[H]
@@
 Testing with infinite data did seem to improve generalization substantially compared to a simply larger dataset.
-So it seems that data is in fact a problem.
-We will somehow have to address this.
+So it seems that data is in fact a problem, we will somehow have to address this. 
+This is run on the pairwise dataset with $K=3$.
 \begin{figure}[H]
@@
 I need to brainstorm ideas of how to handle that.
-There is some work on doing better selection for which edges in the averaging are relevant (e.g.
-Graph Attention Networks)
+There is some work on doing better selection for which edges in the averaging are relevant (e.g. Graph Attention Networks)
 
@@
 \subsection*{Infinite Dataset Test}
-After much debugging to get the data generation during training working, we managed to run some experiments.
-Testing with infinite data did seem to improve generalization substantially compared to a simply larger dataset.
-So it seems that data is in fact a problem.
-We will somehow have to address this.
+I ran more experiments with the infinite dataset but with a harder dataset.
+This is run on the pairwise dataset with $K=5$.
 \begin{figure}[H]
@@
 \end{figure}
-It does OK, but this is still a fairly weak noise model. If the noise got more intense, we would need additional mechanisms to handle it. Hence the next mechanism.
+It does OK, but this is still a fairly weak noise model even with the stronger noise.
+If the noise got more intense, we would need additional mechanisms to handle it.
+Hence the next mechanism.
+
 \subsection*{Graph Attention Network Code Review}
@@
 They have a sparse method but it computes this densely then makes it sparse.
-Also if you wanted to enforce the symmetry of the weights on the graph...
-there isn't really a simple way to do that.
+Also if you wanted to enforce the symmetry of the weights on the graph.
+. there isn't really a simple way to do that.
 Except maybe doing something like using $Q_k' = (Q_k + Q_k^\top)/2$ which doesn't help the whole sparsity problem.
-There are some simple ways to make this sparse using for loops but I am uncertain how to do this using TensorFlow...
-or even PyTorch.
+There are some simple ways to make this sparse using for loops but I am uncertain how to do this using TensorFlow... or even PyTorch.
 However, as I don't see another way to learn the weights of the edges, this is what I'll be focusing on.
@@
 \subsection*{Leaky ReLU Experiments}
-So inspired by the previous paper I thought I would try running experiments with the Leaky ReLU nonlinearity, just to see if it was any different. As it turns out, unsurprisingly, not too much.
+So inspired by the previous paper I thought I would try running experiments with the Leaky ReLU nonlinearity, just to see if it was any different.
+As it turns out, unsurprisingly, not too much.
 
@@
 \subsection*{Binary Cross Entropy}
-Talking with others in the lab (Drew, Oleh) I realized instead of the L2 loss perhaps the Binary Cross Entropy Loss would perform better.
+Talking with others in the lab (Drew, Oleh) I realized instead of the L2 loss perhaps the Binary Cross Entropy (BCE) Loss would perform better.
 Unfortunately this would make it less directly comparable to the optimization methods, but still I think it would worth trying.
-First I need to remove the
+First I need to change the datasets to make sure that they don't go over weight 1, which means regeneration of all the datasets.
+Next I have to add an addtional loss option for choosing between L2 loss and BCE loss.
 

### 2018-07-05 options.py
Got cross entropy implemented, need to test

@@ -88,9 +88,10 @@ def get_opts():
                       default=12,
                       type=int,
                       help='Dimensionality of the output')
+  activation_types = ['relu','leakyrelu','tanh', 'elu']
   parser.add_argument('--activation_type',
-                      default=None,
-                      choices=['relu','leakyrelu','tanh', 'elu'],
+                      default=activation_types[0],
+                      choices=activation_types,
                       help='What type of activation to use')
 
   # Machine learning parameters
@@ -115,6 +116,11 @@ def get_opts():
                       default=False,
                       type=str2bool,
                       help='Use true adjacency or noisy one in loss')
+  loss_types = [ 'l2', 'bce' ]
+  parser.add_argument('--loss_type',
+                      default=loss_types[0],
+                      choices=loss_types,
+                      help='')
   parser.add_argument('--embedding_offset',
                       default=10,
                       type=int,
@@ -131,9 +137,10 @@ def get_opts():
                       default=3e-5,
                       type=float,
                       help='L1 weight decay regularization')
+  optimizer_types = ['sgd','adam','adadelta','momentum']
   parser.add_argument('--optimizer_type',
-                      default='sgd',
-                      choices=['adam','adadelta','momentum','sgd'],
+                      default=optimizer_types[0],
+                      choices=optimizer_types,
                       help='Optimizer type for adaptive learning methods')
   parser.add_argument('--learning_rate',
                       default=1e-3,
@@ -143,9 +150,10 @@ def get_opts():
                       default=0.6,
                       type=float,
                       help='Learning rate for gradient descent')
+  lr_decay_types = ['exponential','fixed','polynomial']
   parser.add_argument('--learning_rate_decay_type',
-                      default='exponential',
-                      choices=['fixed','exponential','polynomial'],
+                      default=lr_decay_types[0],
+                      choices=lr_decay_types,
                       help='Learning rate decay policy')
   parser.add_argument('--min_learning_rate',
                       default=1e-5,

### 2018-07-05 train.py

@@ -16,19 +16,23 @@ import tfutils
 import options
 
 
-def get_loss(sample, output):
+def get_loss(opts, sample, output):
   emb = sample['TrueEmbedding']
   output_sim = tfutils.get_sim(output)
   if opts.use_unsupervised_loss:
     v = opts.dataset_params.views[-1]
     p = opts.dataset_params.points[-1]
     b = opts.batch_size 
-    emb_sim = sample['AdjMat'] + tf.eye(v*p, b)
+    emb_true = sample['AdjMat'] + tf.eye(v*p, b)
   else:
-    emb_sim = tfutils.get_sim(emb)
+    emb_true = tfutils.get_sim(emb)
   tf.summary.image('Output Similarity', tf.expand_dims(output_sim, -1))
-  tf.summary.image('Embedding Similarity', tf.expand_dims(emb_sim, -1))
-  tf.losses.mean_squared_error(emb_sim, output_sim)
+  tf.summary.image('Embedding Similarity', tf.expand_dims(emb_true, -1))
+  if opts.loss_type == 'l2':
+    tf.losses.mean_squared_error(emb_true, output_sim)
+  elif opts.loss_type == 'bce':
+    bce = tf.reduce_sum(tf.nn.sigmoid_cross_entropy_with_logits(labels=emb_true, logits=output_sim))
+    tf.losses.add_loss(bce)
   loss = tf.losses.get_total_loss()
   tf.summary.scalar('Loss', loss)
   return loss
@@ -99,7 +103,7 @@ def train_with_generation(opts):
     sample = dataset.get_placeholders()
   network = model.get_network(opts, opts.arch)
   output = network.apply(sample)
-  loss = get_loss(sample, output)
+  loss = get_loss(opts, sample, output)
   train_op = get_train_op(opts, loss)
 
   # Tensorflow and logging operations
@@ -156,7 +160,7 @@ def train(opts):
     sample = dataset.get_placeholders()
   network = model.get_network(opts, opts.arch)
   output = network.apply(sample)
-  loss = get_loss(sample, output)
+  loss = get_loss(opts, sample, output)
   train_op = get_train_op(opts, loss)
   global_step = tf.train.get_or_create_global_step()
 

### 2018-07-05 data_util.py
Added some boundary constraints to data_util

@@ -307,6 +307,7 @@ class GraphSimNoisyDataset(GraphSimDataset):
     TEmb = sample['TrueEmbedding']
     Noise = np.eye(p) + noise*(np.eye(p, k=-1) + np.eye(p, k=-1))
     AdjMat = np.dot(np.dot(TEmb, Noise), TEmb.T)
+    AdjMat = np.minimum(1, AdjMat)
     Degrees = np.diag(np.sum(AdjMat,0))
     sample['AdjMat'] = AdjMat.astype(self.dtype)
     sample['Degrees'] = Degrees.astype(self.dtype)
@@ -337,6 +338,7 @@ class GraphSimGaussDataset(GraphSimDataset):
     TEmb = sample['TrueEmbedding']
     Noise = np.abs(np.random.randn(p*n,p*n)*noise)
     AdjMat = np.dot(TEmb, TEmb.T) + Noise - np.eye(p*n)
+    AdjMat = np.minimum(1, AdjMat)
     Degrees = np.diag(np.sum(AdjMat,0))
     sample['AdjMat'] = AdjMat.astype(self.dtype)
     sample['Degrees'] = Degrees.astype(self.dtype)
@@ -368,6 +370,7 @@ class GraphSimSymGaussDataset(GraphSimDataset):
     Noise = np.abs(np.random.randn(p*n,p*n)*noise)
     Mask = np.kron(np.ones((n,n))-np.eye(3),np.ones((p,p)))
     AdjMat = np.dot(TEmb, TEmb.T) + ((Noise+Noise.T)/2.0)*Mask - np.eye(p*n)
+    AdjMat = np.minimum(1, AdjMat)
     Degrees = np.diag(np.sum(AdjMat,0))
     sample['AdjMat'] = AdjMat.astype(self.dtype)
     sample['Degrees'] = Degrees.astype(self.dtype)
@@ -407,6 +410,7 @@ class GraphSimPairwiseDataset(GraphSimDataset):
         Val_ij = np.dot(TEmb_i, np.dot(Noise, TEmb_j.T))
         AdjMat[p*i:p*i+p, p*j:p*j+p] = Val_ij
         AdjMat[p*j:p*j+p, p*i:p*i+p] = Val_ij.T
+    AdjMat = np.minimum(1, AdjMat)
     Degrees = np.diag(np.sum(AdjMat,0))
     sample['AdjMat'] = AdjMat.astype(self.dtype)
     sample['Degrees'] = Degrees.astype(self.dtype)

### 2018-07-05 journal/main.tex

@@
 
-Figure \ref{fig:baseline_plot} shows an example of ground truth node embedding and similarities as well as the node embedding vectors and similarities of the initial embedding we use.
-
+% Figure \ref{fig:baseline_plot} shows an example of ground truth node embedding and similarities as well as the node embedding vectors and similarities of the initial embedding we use.
+% 
 \begin{figure}[H]
@@
     % \includegraphics[width=0.7\textwidth]{figures/noiseless_sim.png}
-    \subfloat[Sorted ground truth embedding and initial embedding]{
-        \includegraphics[width=0.45\textwidth]{figures/baseline_embeddings.png}
-        \label{fig:baseline_sub1}
-    }
-    \subfloat[Ground truth and initial similarity]{
-        \includegraphics[width=0.45\textwidth]{figures/baseline_sim.png}
-        \label{fig:baseline_sub2}
-    }
+    \begin{minipage}{.45\linewidth}
+        \subfloat[Sorted ground truth embedding and initial embedding]{ \includegraphics[width=0.9\textwidth]{figures/baseline_embeddings.png} \label{fig:baseline_sub1} }
+    \end{minipage}
+    \begin{minipage}{.45\linewidth}
+        \subfloat[Ground truth and initial similarity]{ \includegraphics[width=0.9\textwidth]{figures/baseline_sim.png} \label{fig:baseline_sub2} }
+    \end{minipage}
     \caption{Here we show a baseline for the node embedding vectors and the final similarity matrix}
@@
     % \includegraphics[width=0.7\textwidth]{figures/noiseless_sim.png}
-    \subfloat[Typical embedding and similarity matrix of Noiseless]{
-        \includegraphics[width=0.45\textwidth]{figures/synth_plot.png}
-        \label{fig:noiseless_sub1}
-    }
-    \subfloat[Typical histogram for similarities of noiseless]{
-        \includegraphics[width=0.45\textwidth]{figures/synth_hist.png}
-        \label{fig:noiseless_sub2}
-    }
+    \subfloat[Typical embedding and similarity matrix of Noiseless]{ \includegraphics[width=0.45\textwidth]{figures/synth_plot.png} \label{fig:noiseless_sub1} }
+    \subfloat[Typical histogram for similarities of noiseless]{ \includegraphics[width=0.45\textwidth]{figures/synth_hist.png} \label{fig:noiseless_sub2} }
     \caption{Here we show a baseline for the node embedding vectors and the final similarity matrix}
@@
     % \includegraphics[width=0.7\textwidth]{figures/noiseless_sim.png}
-    \subfloat[Typical embedding and similarity matrix of pairwise noise]{
-        \includegraphics[width=0.45\textwidth]{figures/pairwise_plot.png}
-        \label{fig:pairwise_sub1}
-    }
-    \subfloat[Typical histogram for similarities of pairwise noise]{
-        \includegraphics[width=0.45\textwidth]{figures/pairwise_hist.png}
-        \label{fig:pairwise_sub2}
-    }
+    \subfloat[Typical embedding and similarity matrix of pairwise noise]{ \includegraphics[width=0.45\textwidth]{figures/pairwise_plot.png} \label{fig:pairwise_sub1} }
+    \subfloat[Typical histogram for similarities of pairwise noise]{ \includegraphics[width=0.45\textwidth]{figures/pairwise_hist.png} \label{fig:pairwise_sub2} }
     \caption{Here we show a baseline for the node embedding vectors and the final similarity matrix}
@@
     % \includegraphics[width=0.7\textwidth]{figures/noiseless_sim.png}
-    \subfloat[Typical embedding and similarity matrix of pairwise noise]{
-        \includegraphics[width=0.45\textwidth]{figures/pairwise3_plot.png}
-        \label{fig:pairwise3_sub1}
-    }
-    \subfloat[Typical histogram for similarities of pairwise noise]{
-        \includegraphics[width=0.45\textwidth]{figures/pairwise3_hist.png}
-        \label{fig:pairwise3_sub2}
-    }
+    \subfloat[Typical embedding and similarity matrix of pairwise noise]{ \includegraphics[width=0.45\textwidth]{figures/pairwise3_plot.png} \label{fig:pairwise3_sub1} }
+    \subfloat[Typical histogram for similarities of pairwise noise]{ \includegraphics[width=0.45\textwidth]{figures/pairwise3_hist.png} \label{fig:pairwise3_sub2} }
     \caption{Here we show a baseline for the node embedding vectors and the final similarity matrix}
@@
     % \includegraphics[width=0.7\textwidth]{figures/noiseless_sim.png}
-    \subfloat[Typical embedding and similarity matrix of pairwise noise]{
-        \includegraphics[width=0.45\textwidth]{figures/pairwise5_plot.png}
-        \label{fig:pairwise5_sub1}
-    }
-    \subfloat[Typical histogram for similarities of pairwise noise]{
-        \includegraphics[width=0.45\textwidth]{figures/pairwise5_hist.png}
-        \label{fig:pairwise5_sub2}
-    }
+    \subfloat[Typical embedding and similarity matrix of pairwise noise]{ \includegraphics[width=0.45\textwidth]{figures/pairwise5_plot.png} \label{fig:pairwise5_sub1} }
+    \subfloat[Typical histogram for similarities of pairwise noise]{ \includegraphics[width=0.45\textwidth]{figures/pairwise5_hist.png} \label{fig:pairwise5_sub2} }
     \caption{Here we show a baseline for the node embedding vectors and the final similarity matrix}
@@
         \centering
-        \subfloat[Typical embedding and similarity matrix of pairwise noise]{
-            \includegraphics[width=0.9\textwidth]{figures/pairwise3_large_plot.png}
-            \label{fig:pairwise3_large_sub1}
-        }
+        \subfloat[Typical embedding and similarity matrix of pairwise noise]{ \includegraphics[width=0.9\textwidth]{figures/pairwise3_large_plot.png} \label{fig:pairwise3_large_sub1} }
     \end{minipage}
@@
         \centering
-        \subfloat[Typical histogram for similarities of pairwise noise]{
-            \includegraphics[width=0.9\textwidth]{figures/pairwise3_large_hist.png}
-            \label{fig:pairwise3_large_sub2}
-        }
+        \subfloat[Typical histogram for similarities of pairwise noise]{ \includegraphics[width=0.9\textwidth]{figures/pairwise3_large_hist.png} \label{fig:pairwise3_large_sub2} }
     \end{minipage}
@@
         \centering
-        \subfloat[Typical embedding and similarity matrix of pairwise noise]{
-            \includegraphics[width=0.9\textwidth]{figures/pairwise3inf_plot.png}
-            \label{fig:pairwise3inf_sub1}
-        }
+        \subfloat[Typical embedding and similarity matrix of pairwise noise]{ \includegraphics[width=0.9\textwidth]{figures/pairwise3inf_plot.png} \label{fig:pairwise3inf_sub1} }
     \end{minipage}
@@
         \centering
-        \subfloat[Typical histogram for similarities of pairwise noise]{
-            \includegraphics[width=0.9\textwidth]{figures/pairwise3inf_hist.png}
-            \label{fig:pairwise3inf_sub2}
-        }
+        \subfloat[Typical histogram for similarities of pairwise noise]{ \includegraphics[width=0.9\textwidth]{figures/pairwise3inf_hist.png} \label{fig:pairwise3inf_sub2} }
     \end{minipage}
@@
         \centering
-        \subfloat[Typical embedding and similarity matrix of pairwise noise]{
-            \includegraphics[width=0.9\textwidth]{figures/pairwise5inf_plot.png}
-            \label{fig:pairwise5inf_sub1}
-        }
+        \subfloat[Typical embedding and similarity matrix of pairwise noise]{ \includegraphics[width=0.9\textwidth]{figures/pairwise5inf_plot.png} \label{fig:pairwise5inf_sub1} }
     \end{minipage}
@@
         \centering
-        \subfloat[For comparison, the non-infinite data trained version]{
-            \includegraphics[width=0.9\textwidth]{figures/pairwise5inf_plot_compare.png}
-            \label{fig:pairwise5inf_sub2}
-        }
+        \subfloat[For comparison, the non-infinite data trained version]{ \includegraphics[width=0.9\textwidth]{figures/pairwise5inf_plot_compare.png} \label{fig:pairwise5inf_sub2} }
     \end{minipage}
@@
         \centering
-        \subfloat[Typical histogram for similarities of pairwise noise]{
-            \includegraphics[width=0.5\textwidth]{figures/pairwise5inf_hist.png}
-            \label{fig:pairwise5inf_sub3}
-        }
+        \subfloat[Typical histogram for similarities of pairwise noise]{ \includegraphics[width=0.5\textwidth]{figures/pairwise5inf_hist.png} \label{fig:pairwise5inf_sub3} }
     \end{minipage}

### 2018-07-05 options.py
Small cleanup on options

@@ -65,6 +65,9 @@ def get_opts():
                       default=dataset_choices[0],
                       choices=dataset_choices,
                       help='Choose which dataset to use')
+  parser.add_argument('--datasets_dir',
+                      default='/NAS/data/stephen',
+                      help='Directory where all the datasets are')
   parser.add_argument('--use_descriptors',
                       default=True,
                       type=str2bool,
@@ -239,7 +242,7 @@ def get_opts():
 
   # Determine dataset
   dataset_params = types.SimpleNamespace(
-    data_dir='/NAS/data/stephen/{}'.format(opts.dataset),
+    data_dir='{}/{}'.format(opts.datasets_dir, opts.dataset),
     sizes={ 'train': 40000, 'test': 3000 },
     fixed_size=True,
     views=[3],

### 2018-07-05 options.py
Trying to get dataset params working with python 2...

@@ -238,23 +238,25 @@ def get_opts():
     opts.save_dir = 'save/save-{:03d}'.format(save_idx)
 
   # Determine dataset
-  dataset_params = types.SimpleNamespace(
-    data_dir='/NAS/data/stephen/{}'.format(opts.dataset),
-    sizes={ 'train': 40000, 'test': 3000 },
-    fixed_size=True,
-    views=[3],
-    points=[25],
-    points_scale=1,
-    knn=8,
-    scale=3,
-    sparse=False,
-    soft_edges=False,
-    descriptor_dim=12,
-    descriptor_var=1.0,
-    descriptor_noise_var=0,
-    noise_level=0.1,
-    num_repeats=1,
-    dtype='float32')
+  class DatasetParams(object):
+    def __init__(self, opts):
+      self.data_dir='/NAS/data/stephen/{}'.format(opts.dataset),
+      self.sizes={ 'train': 40000, 'test': 3000 }
+      self.fixed_size=True
+      self.views=[3]
+      self.points=[25]
+      self.points_scale=1
+      self.knn=8
+      self.scale=3
+      self.sparse=False
+      self.soft_edges=False
+      self.descriptor_dim=12
+      self.descriptor_var=1.0
+      self.descriptor_noise_var=0
+      self.noise_level=0.1
+      self.num_repeats=1
+      self.dtype='float32'
+  dataset_params = DatasetParams(opts)
   if opts.dataset == 'synth_3view':
     pass
   elif opts.dataset == 'noise_3view':

### 2018-07-05 journal/main.tex

@@
 
+\subsection*{TensorFlow Implementation Details}
+So my TensorFlow code is OK but it lacks some nice features.
+Talking to Drew, it seems Sonnet is the answer, since he showed me some of the features I was missing.
+I also need to start using \texttt{SingularMonitoredSession} instead of slim since slim is just... annoying.
+So I will need to branch off in git and make a new branch while I get Sonnet working.
+
 \end{document}

### 2018-07-09 options.py
More work on converting things to Sonnet'

@@ -54,7 +54,7 @@ def get_opts():
                       default='/NAS/data/stephen/',
                       help='Directory for saving/loading dataset')
   dataset_choices = [
-    'synth_small', 'synth_3view', 'synth_4view',
+    'synth_3view', 'synth_small', 'synth_4view',
     'noise_3view',
     'noise_gauss', 'noise_symgauss',
     'noise_pairwise', 'noise_pairwise3', 'noise_pairwise5',
@@ -243,7 +243,7 @@ def get_opts():
   # Determine dataset
   class DatasetParams(object):
     def __init__(self, opts):
-      self.data_dir='{}/{}'.format(opts.datasets_dir, opts.dataset),
+      self.data_dir='{}/{}'.format(opts.datasets_dir, opts.dataset)
       self.sizes={ 'train': 40000, 'test': 3000 }
       self.fixed_size=True
       self.views=[3]

### 2018-07-09 sonnet_data_test.py

@@ -1,0 +1,590 @@
+import sys
+import os
+import glob
+import tensorflow as tf
+import collections
+import sonnet as snt
+
+import options 
+import model
+import tfutils
+
+class Int64Feature(object):
+  """Custom class used for decoding serialized tensors."""
+  def __init__(self, key, description):
+    super(Int64Feature, self).__init__()
+    self._key = key
+    self.shape = []
+    self._description = description
+
+  def get_placeholder(self):
+    return tf.placeholder(tf.int64, shape=[None])
+
+  def get_feature_write(self, value):
+    return tf.train.Feature(int64_list=tf.train.Int64List(value=[value]))
+
+  def get_feature_read(self):
+    return tf.FixedLenFeature([], tf.int64)
+
+  def tensors_to_item(self, keys_to_tensors):
+    tensor = keys_to_tensors[self._key]
+    return tf.cast(tensor, dtype=tf.int64)
+
+class TensorFeature(object):
+  """Custom class used for decoding serialized tensors."""
+  def __init__(self, key, shape, dtype, description):
+    super(TensorFeature, self).__init__()
+    self._key = key
+    self.shape = shape
+    self._dtype = dtype
+    self._description = description
+
+  def get_placeholder(self):
+    return tf.placeholder(self._dtype, shape=[None] + self.shape)
+
+  def get_feature_write(self, value):
+    v = value.astype(self._dtype).tobytes()
+    return tf.train.Feature(bytes_list=tf.train.BytesList(value=[v]))
+
+  def get_feature_read(self):
+    return tf.FixedLenFeature([], tf.string)
+
+  def tensors_to_item(self, keys_to_tensors):
+    tensor = keys_to_tensors[self._key]
+    tensor = tf.decode_raw(tensor, out_type=self._dtype)
+    return tf.reshape(tensor, self.shape)
+
+
+class GraphSimDataset(object):
+  """Dataset for Cycle Consistency graphs"""
+  MAX_IDX=7000
+
+  def __init__(self, opts, params):
+    self.opts = opts
+    self.dataset_params = params
+    self.data_dir = params.data_dir
+    self.dtype = params.dtype
+    if params.fixed_size:
+      self.n_views = params.views[-1]
+      self.n_pts = params.points[-1]
+    else:
+      self.n_views = np.random.randint(params.views[0], params.views[1]+1)
+      self.n_pts = np.random.randint(params.points[0], params.points[1]+1)
[…]

### 2018-07-09 tfutils.py

@@ -1,4 +1,5 @@
 import tensorflow as tf
+import math
 
 def matmul(x,y):
   return tf.einsum('bik,kj->bij', x, y)
@@ -19,3 +20,13 @@ def get_tf_activ(activ):
     return tf.nn.tanh
   elif activ == 'elu':
     return tf.nn.elu
+
+def create_linear_initializer(input_size, dtype=tf.float32):
+  """Returns a default initializer for weights of a linear module."""
+  stddev = 1 / math.sqrt(input_size)
+  return tf.truncated_normal_initializer(stddev=stddev, dtype=dtype)
+
+def create_bias_initializer(unused_bias_shape, dtype=tf.float32):
+  """Returns a default initializer for the biases of a linear/AddBias module."""
+  return tf.zeros_initializer(dtype=dtype)
+

### 2018-07-10 data_util.py
Modified data_util to use tf.data instead of slim

@@ -8,7 +8,6 @@ import datetime
 import tqdm
 
 import tensorflow as tf
-import tensorflow.contrib.slim as slim
 
 import options
 import myutils
@@ -22,10 +21,10 @@ def _bytes_feature(value):
 def _int64_feature(value):
   return tf.train.Feature(int64_list=tf.train.Int64List(value=[value]))
 
-class Int64Feature(slim.tfexample_decoder.ItemHandler):
+class Int64Feature(object):
   """Custom class used for decoding serialized tensors."""
   def __init__(self, key, description):
-    super(Int64Feature, self).__init__(key)
+    super(Int64Feature, self).__init__()
     self._key = key
     self.shape = []
     self._description = description
@@ -43,10 +42,10 @@ class Int64Feature(slim.tfexample_decoder.ItemHandler):
     tensor = keys_to_tensors[self._key]
     return tf.cast(tensor, dtype=tf.int64)
 
-class TensorFeature(slim.tfexample_decoder.ItemHandler):
+class TensorFeature(object):
   """Custom class used for decoding serialized tensors."""
   def __init__(self, key, shape, dtype, description):
-    super(TensorFeature, self).__init__(key)
+    super(TensorFeature, self).__init__()
     self._key = key
     self.shape = shape
     self._dtype = dtype
@@ -258,37 +257,24 @@ class GraphSimDataset(object):
     assert mode in params.sizes, "Mode {} not supported".format(mode)
     batch_size = opts.batch_size
     data_source_name = mode + '-[0-9][0-9].tfrecords'
+    print((self.data_dir, mode, data_source_name))
     data_sources = glob.glob(os.path.join(self.data_dir, mode, data_source_name))
     # Build dataset provider
     keys_to_features = { k: v.get_feature_read()
                          for k, v in self.features.items() }
-    decoder = slim.tfexample_decoder.TFExampleDecoder(keys_to_features,
-                                                      self.features)
     items_to_descriptions = { k: v._description
                               for k, v in self.features.items() }
-    dataset = slim.dataset.Dataset(
-                data_sources=data_sources,
-                reader=tf.TFRecordReader,
-                decoder=decoder,
-                num_samples=params.sizes[mode],
-                items_to_descriptions=items_to_descriptions)
-    provider = slim.dataset_data_provider.DatasetDataProvider(
-                dataset,
-                num_readers=opts.num_readers,
[…]

### 2018-07-10 model.py
Modified model to use sonnet

@@ -2,213 +2,393 @@
 import numpy as np 
 import os
 import sys
+import tensorflow as tf
+import sonnet as snt
 
-try:
-  import tensorflow as tf
-  import tfutils
-except:
-  print("ERROR: Tensorflow failed to load")
-  tf = None
-  tfutils = None
-
+import tfutils
 import myutils
 import options
 
-class DenseGraphLayerWeights(object):
-  def __init__(self, opts, arch):
-    super(DenseGraphLayerWeights, self).__init__()
-    self.tf_init = False
-    self.np_init = False
-    self.use_descriptors = opts.use_descriptors
-    self.activ = arch.activ
-    self._activ = None # tfutils.get_tf_activ(arch.activ)
-    self._np_activ = None # myutils.get_np_activ(arch.activ)
+# TODO: Organize this into multiple files
+class EmbeddingRightLinear(snt.AbstractModule):
+  """Linear transformation on an embedding, each independently.
+  
+  This functions almost exactly like snt.Linear except it is for tensors of
+  size batch_size x nodes x input_size. Acts by matrix multiplication on the
+  left side of each nodes x input_size matrix.
+  """
+  def __init__(self,
+               output_size,
+               use_bias=True,
+               initializers=None,
+               partitioners=None,
+               regularizers=None,
+               custom_getter=None,
+               name="lin"):
+    super(EmbeddingRightLinear, self).__init__(custom_getter=custom_getter, name=name)
+    self._output_size = output_size
+    self._output_size = output_size
+    self._use_bias = use_bias
+    self._input_shape = None
+    self._w = None
+    self._b = None
+    self.possible_keys = self.get_possible_initializer_keys(use_bias=use_bias)
+    self._initializers = snt.check_initializers(
+        initializers, self.possible_keys)
+    self._partitioners = snt.check_partitioners(
+        partitioners, self.possible_keys)
+    self._regularizers = snt.check_regularizers(
+        regularizers, self.possible_keys)
+
+  @classmethod
+  def get_possible_initializer_keys(cls, use_bias=True):
+    return {"w", "b"} if use_bias else {"w"}
+
+  def _build(self, laplacian, inputs):
+    input_shape = tuple(inputs.get_shape().as_list())
+    if len(input_shape) != 3:
+      raise base.IncompatibleShapeError(
+          "{}: rank of shape must be 3 not: {}".format(
+              self.scope_name, len(input_shape)))
+
+    if input_shape[2] is None:
[…]

### 2018-07-10 train.py
Fixed train a bit

@@ -102,7 +102,7 @@ def train_with_generation(opts):
   else:
     sample = dataset.get_placeholders()
   network = model.get_network(opts, opts.arch)
-  output = network.apply(sample)
+  output = network(sample)
   loss = get_loss(opts, sample, output)
   train_op = get_train_op(opts, loss)
 
@@ -159,7 +159,7 @@ def train(opts):
   else:
     sample = dataset.get_placeholders()
   network = model.get_network(opts, opts.arch)
-  output = network.apply(sample)
+  output = network(sample)
   loss = get_loss(opts, sample, output)
   train_op = get_train_op(opts, loss)
   global_step = tf.train.get_or_create_global_step()

### 2018-09-18 journal/main.tex
More work on converting things to Sonnet'
Automated figure generation draft 1

@@
 
+\entry{2018}{07}{09}
+\subsection*{TensorFlow Implementation Details}
+Still working on updating the TensorFlow features to use Sonnet.
+
+\entry{2018}{09}{17}
+I have much ground to catch up on. But better late than never.
+\subsection*{TensorFlow Implementation Details Completed}
+I finished this and the code is much cleaner - the code is divided better.
+The \texttt{model.py} function has been replaced with a model module (directory with multiple files), so now custom layers, custom network types, and the architecture selection logic are separated.
+However, the regularization is still a bit crude, and when building a new architecture it tends to give a 'gotcha' - I need to fix that.
+Otherwise it is working much better.
+\subsection*{Binary Cross Entropy afterthoughts}
+I have not tested this extensively but the limited experiments I did try didn't seem to make much of a difference.
+I think it might be better dealing with outliers.
+Right now we use a Frobenious norm loss, which implicitly assumes $A_{ij} \sim \mathcal{N}(e_i^\top e_j, \sigma^2)$.
+This assumes infinte support and is not quite we are assuming if we enforce $e_i$ to be norm 1.
+Thus the rational is since it is between 0 and 1, we can treat each element as a classifcation: $P(A_{ij} = 1) = 1 - P(A_{ij} = 0) = e_i^\top e_j$.
+This is more appropriate and possibly more robust to noise (maybe outliers?).
+However, more tests need to be done to determine its actual effectiveness.
+\subsection*{Experiments}
+Many experiments were done during this time. Here are the tables and figures
+
+\begin{figure}[H]
+  \includegraphics[width=0.9\textwidth]{figures/synth-3view-skip-relu-unsup-false-0}
+  \label{fig:synth-3view-skip-relu-unsup-false-0-sub1}
+  \caption{Typical embedding and similarity matrix of pairwise noise}
+\end{figure}
+\begin{figure}[H]
+  \includegraphics[width=0.9\textwidth]{figures/synth-3view-skip-leakyrelu-unsup-true-0}
+  \label{fig:synth-3view-skip-leakyrelu-unsup-true-0-sub1}
+  \caption{Typical embedding and similarity matrix of pairwise noise}
+\end{figure}
+\begin{figure}[H]
+  \includegraphics[width=0.9\textwidth]{figures/synth-3view-skip-leakyrelu-unsup-false-0}
+  \label{fig:synth-3view-skip-leakyrelu-unsup-false-0-sub1}
+  \caption{Typical embedding and similarity matrix of pairwise noise}
+\end{figure}
+Dataset type $\texttt{synth3view}$ - noiseless 3 view dataset.
+\begin{table}[H]
+    \begin{tabular}{|c|c|c|c|} \hline
+                                      &  Same Point Similarities  &  Different Point Similarities  \\ \hline
+Baseline   & 5.11e-01 $\pm$ 3.90e-01 & 2.56e-01 $\pm$ 2.06e-01 \\ \hline
+Skip Type 0 Arch., Leakyrelu   & 9.97e-01 $\pm$ 7.39e-03 & 9.74e-02 $\pm$ 1.38e-01 \\ \hline
+Skip Type 0 Arch., Leakyrelu, Unsupervised   & 9.94e-01 $\pm$ 1.04e-02 & 1.21e-01 $\pm$ 1.31e-01 \\ \hline
+Skip Type 0 Arch., Relu   & 9.98e-01 $\pm$ 5.89e-03 & 8.48e-02 $\pm$ 1.41e-01 \\ \hline
+Skip Type 0 Arch., Relu, Unsupervised  & 9.96e-01 $\pm$ 7.70e-03 & 1.16e-01 $\pm$ 1.32e-01 \\ \hline
+Skip Type 1 Arch., Leakyrelu   & 9.92e-01 $\pm$ 1.68e-02 & 1.10e-01 $\pm$ 1.32e-01 \\ \hline
+Skip Type 1 Arch., Leakyrelu, Unsupervised   & 9.97e-01 $\pm$ 6.13e-03 & 1.25e-01 $\pm$ 1.31e-01 \\ \hline
+Skip Type 1 Arch., Relu   & 9.98e-01 $\pm$ 4.96e-03 & 9.04e-02 $\pm$ 1.37e-01 \\ \hline
+Skip Type 1 Arch., Relu, Unsupervised   & 9.98e-01 $\pm$ 5.27e-03 & 1.19e-01 $\pm$ 1.30e-01 \\ \hline
+      \end{tabular}
+  \caption{Numerical results}
+\end{table}
+% \label{fig:tabletab1}
+% Baseline   & 5.11e-01 $\pm$ 3.90e-01 & 2.56e-01 $\pm$ 2.06e-01 \\ \hline
+% Skip Type 1 Arch., Leakyrelu   & 9.97e-01 $\pm$ 7.39e-03 & 9.74e-02 $\pm$ 1.38e-01 \\ \hline
+% Skip Type 1 Arch., Leakyrelu, Using unsupervised loss   & 9.94e-01 $\pm$ 1.04e-02 & 1.21e-01 $\pm$ 1.31e-01 \\ \hline
+% Skip Type 1 Arch., Relu   & 9.98e-01 $\pm$ 5.89e-03 & 8.48e-02 $\pm$ 1.41e-01 \\ \hline
+% Skip Type 1 Arch., Relu, Using unsupervised loss   & 9.96e-01 $\pm$ 7.70e-03 & 1.16e-01 $\pm$ 1.32e-01 \\ \hline
+% Skip Type 2 Arch., Leakyrelu   & 9.92e-01 $\pm$ 1.68e-02 & 1.10e-01 $\pm$ 1.32e-01 \\ \hline
+% Skip Type 2 Arch., Leakyrelu, Using unsupervised loss   & 9.97e-01 $\pm$ 6.13e-03 & 1.25e-01 $\pm$ 1.31e-01 \\ \hline
+% Skip Type 2 Arch., Relu   & 9.98e-01 $\pm$ 4.96e-03 & 9.04e-02 $\pm$ 1.37e-01 \\ \hline
+
+Using ReLu activation type with aforementioned pairwise noise. 
+\begin{figure}[H]
+\subfloat[Typical embedding and similarity matrix of pairwise noise]{ \includegraphics[width=0.9\textwidth]{figures/pairwise5-skip0-relu-ld-false-unsup-true-0} \label{fig:pairwise5-skip0-relu-ld-false-unsup-true-0-sub1} }
+\subfloat[Typical embedding and similarity matrix of pairwise noise]{ \includegraphics[width=0.9\textwidth]{figures/pairwise3-attn2-relu-ld-true-unsup-false-0} \label{fig:pairwise3-attn2-relu-ld-true-unsup-false-0-sub1} }
+\subfloat[Typical embedding and similarity matrix of pairwise noise]{ \includegraphics[width=0.9\textwidth]{figures/pairwise3-skip0-relu-ld-true-unsup-false-0} \label{fig:pairwise3-skip0-relu-ld-true-unsup-false-0-sub1} }
+  \subfloat[Numerical results]{
+      \begin{tabular}{|c|c|c|c|} \hline
+                                      &  Same Point Similarities  &  Different Point Similarities  \\ \hline
+Baseline   & 5.11e-01 $\pm$ 3.90e-01 & 2.56e-01 $\pm$ 2.06e-01 \\ \hline
+Data type $\texttt{pairwise3}$ \\ \hline
+GAT Network Type 0 Arch., Data generation   & 5.75e-01 $\pm$ 3.58e-01 & 2.26e-01 $\pm$ 1.77e-01 \\ \hline
+GAT Network Type 0 Arch., Data generation, Using unsupervised loss   & 7.11e-01 $\pm$ 2.65e-01 & 1.74e-01 $\pm$ 1.41e-01 \\ \hline
+GAT Network Type 0 Arch.   & 5.95e-01 $\pm$ 3.45e-01 & 2.05e-01 $\pm$ 1.66e-01 \\ \hline
+GAT Network Type 0 Arch., Using unsupervised loss   & 6.64e-01 $\pm$ 3.15e-01 & 1.82e-01 $\pm$ 1.68e-01 \\ \hline
+GAT Network Type 1 Arch., Data generation   & 5.96e-01 $\pm$ 3.44e-01 & 2.07e-01 $\pm$ 1.65e-01 \\ \hline
+GAT Network Type 1 Arch., Data generation, Using unsupervised loss   & 7.65e-01 $\pm$ 2.36e-01 & 1.87e-01 $\pm$ 1.53e-01 \\ \hline
+GAT Network Type 1 Arch.   & 5.09e-01 $\pm$ 3.93e-01 & 2.21e-01 $\pm$ 1.87e-01 \\ \hline
+GAT Network Type 1 Arch., Using unsupervised loss   & 7.07e-01 $\pm$ 2.76e-01 & 1.64e-01 $\pm$ 1.47e-01 \\ \hline
+GAT Network Type 2 Arch., Data generation   & 8.33e-01 $\pm$ 1.79e-01 & 2.17e-01 $\pm$ 1.67e-01 \\ \hline
+GAT Network Type 2 Arch., Data generation, Using unsupervised loss   & 5.13e-01 $\pm$ 3.89e-01 & 1.98e-01 $\pm$ 1.71e-01 \\ \hline
+GAT Network Type 2 Arch.   & 4.92e-01 $\pm$ 4.00e-01 & 2.30e-01 $\pm$ 1.98e-01 \\ \hline
+GAT Network Type 2 Arch., Using unsupervised loss   & 6.12e-01 $\pm$ 3.33e-01 & 2.04e-01 $\pm$ 1.65e-01 \\ \hline
+Skip Type 0 Arch., Data generation   & 9.90e-01 $\pm$ 2.35e-02 & 7.18e-02 $\pm$ 1.60e-01 \\ \hline
+Skip Type 0 Arch., Data generation, Using unsupervised loss   & 9.59e-01 $\pm$ 6.03e-02 & 1.00e-01 $\pm$ 1.57e-01 \\ \hline
+Skip Type 0 Arch.   & 9.80e-01 $\pm$ 3.75e-02 & 8.56e-02 $\pm$ 1.57e-01 \\ \hline
+Skip Type 0 Arch., Using unsupervised loss   & 9.62e-01 $\pm$ 5.32e-02 & 1.01e-01 $\pm$ 1.61e-01 \\ \hline
+Skip Type 0 Arch., Data generation   & 9.74e-01 $\pm$ 5.64e-02 & 9.52e-02 $\pm$ 1.60e-01 \\ \hline
+Skip Type 0 Arch., Data generation, Using unsupervised loss   & 9.66e-01 $\pm$ 7.82e-02 & 8.26e-02 $\pm$ 1.61e-01 \\ \hline
+Skip Type 0 Arch.   & 9.73e-01 $\pm$ 6.48e-02 & 8.12e-02 $\pm$ 1.60e-01 \\ \hline
+Skip Type 0 Arch., Using unsupervised loss   & 9.66e-01 $\pm$ 7.71e-02 & 8.23e-02 $\pm$ 1.57e-01 \\ \hline
+Data type $\texttt{pairwise5}$ \\ \hline
+GAT Network Type 0 Arch., Data generation   & 5.04e-01 $\pm$ 3.97e-01 & 2.12e-01 $\pm$ 1.90e-01 \\ \hline
+GAT Network Type 0 Arch., Data generation, Using unsupervised loss   & 7.51e-01 $\pm$ 2.39e-01 & 2.06e-01 $\pm$ 1.57e-01 \\ \hline
+GAT Network Type 0 Arch.   & 8.06e-01 $\pm$ 2.14e-01 & 1.88e-01 $\pm$ 1.63e-01 \\ \hline
+GAT Network Type 0 Arch., Using unsupervised loss   & 5.92e-01 $\pm$ 3.56e-01 & 1.76e-01 $\pm$ 1.71e-01 \\ \hline
+GAT Network Type 1 Arch., Data generation   & 6.99e-01 $\pm$ 2.74e-01 & 1.99e-01 $\pm$ 1.53e-01 \\ \hline
+GAT Network Type 1 Arch., Data generation, Using unsupervised loss   & 5.41e-01 $\pm$ 3.74e-01 & 2.16e-01 $\pm$ 1.79e-01 \\ \hline
+GAT Network Type 1 Arch.   & 4.96e-01 $\pm$ 3.99e-01 & 2.27e-01 $\pm$ 1.97e-01 \\ \hline
+GAT Network Type 1 Arch., Using unsupervised loss   & 5.95e-01 $\pm$ 3.44e-01 & 2.06e-01 $\pm$ 1.65e-01 \\ \hline
+GAT Network Type 2 Arch., Data generation   & 6.72e-01 $\pm$ 2.90e-01 & 2.01e-01 $\pm$ 1.55e-01 \\ \hline
+GAT Network Type 2 Arch., Data generation, Using unsupervised loss   & 5.09e-01 $\pm$ 3.93e-01 & 1.94e-01 $\pm$ 1.83e-01 \\ \hline
+GAT Network Type 2 Arch.   & 8.11e-01 $\pm$ 2.06e-01 & 2.02e-01 $\pm$ 1.68e-01 \\ \hline
+GAT Network Type 2 Arch., Using unsupervised loss   & 5.84e-01 $\pm$ 3.49e-01 & 1.96e-01 $\pm$ 1.62e-01 \\ \hline
+Skip Type 0 Arch., Data generation   & 9.68e-01 $\pm$ 5.29e-02 & 9.50e-02 $\pm$ 1.58e-01 \\ \hline
+Skip Type 0 Arch., Data generation, Using unsupervised loss   & 9.40e-01 $\pm$ 7.90e-02 & 1.11e-01 $\pm$ 1.54e-01 \\ \hline
+Skip Type 0 Arch.   & 9.66e-01 $\pm$ 5.37e-02 & 9.77e-02 $\pm$ 1.60e-01 \\ \hline
+Skip Type 0 Arch., Using unsupervised loss   & 9.74e-01 $\pm$ 4.28e-02 & 8.56e-02 $\pm$ 1.51e-01 \\ \hline
+Skip Type 0 Arch., Data generation   & 9.69e-01 $\pm$ 7.55e-02 & 6.14e-02 $\pm$ 1.43e-01 \\ \hline
+Skip Type 0 Arch., Data generation, Using unsupervised loss   & 9.66e-01 $\pm$ 8.32e-02 & 6.17e-02 $\pm$ 1.37e-01 \\ \hline
+Skip Type 0 Arch.   & 9.69e-01 $\pm$ 7.68e-02 & 6.22e-02 $\pm$ 1.44e-01 \\ \hline
+Skip Type 0 Arch., Using unsupervised loss   & 9.65e-01 $\pm$ 8.34e-02 & 6.49e-02 $\pm$ 1.42e-01 \\ \hline
+      \end{tabular}
+      \label{fig:{0}_tab1}
+  }
+\end{figure}[H]
+% Skip Type 2 Arch., Relu, Using unsupervised loss   & 9.98e-01 $\pm$ 5.27e-03 & 1.19e-01 $\pm$ 1.30e-01 \\ \hline
+
+\subsubsection*{Thoughts}
+To my dismay, the GAT architecture seems very unstable to train and doesn't converge very well if at all.
+Comparitavely, the best results come from stacking many layers - on the order of 15 seems to work for these problems pretty well.
+Now the best thing to do would be to go to real data since these seem to be working pretty well.
+To get better results we really do need additional losses though.
+
 \end{document}

### 2018-09-18 journal/main.tex
Added a bunch of experiments to journal entry

--- 2018-07-05 journal/main.tex
@@
 \usepackage[caption=false]{subfig} % subfigures.  false option prevents conflicts in caption styling with other packages
+\usepackage{multirow}
+\usepackage{multirow}
 \usepackage{float}
@@
 
+\entry{2018}{07}{09}
+\subsection*{TensorFlow Implementation Details}
+Still working on updating the TensorFlow features to use Sonnet.
+
+\entry{2018}{09}{17}
+I have much ground to catch up on. But better late than never.
+\subsection*{TensorFlow Implementation Details Completed}
+I finished this and the code is much cleaner - the code is divided better.
+The \texttt{model.py} function has been replaced with a model module (directory with multiple files), so now custom layers, custom network types, and the architecture selection logic are separated.
+However, the regularization is still a bit crude, and when building a new architecture it tends to give a 'gotcha' - I need to fix that.
+Otherwise it is working much better.
+\subsection*{Binary Cross Entropy afterthoughts}
+I have not tested this extensively but the limited experiments I did try didn't seem to make much of a difference.
+I think it might be better dealing with outliers.
+Right now we use a Frobenious norm loss, which implicitly assumes $A_{ij} \sim \mathcal{N}(e_i^\top e_j, \sigma^2)$.
+This assumes infinte support and is not quite we are assuming if we enforce $e_i$ to be norm 1.
+Thus the rational is since it is between 0 and 1, we can treat each element as a classifcation: $P(A_{ij} = 1) = 1 - P(A_{ij} = 0) = e_i^\top e_j$.
+This is more appropriate and possibly more robust to noise (maybe outliers?).
+However, more tests need to be done to determine its actual effectiveness.
+\subsection*{Experiments}
+Many experiments were done during this time. Here are the tables and figures
+
+\subsubsection*{Experiment Run 12}
+Dataset type $\texttt{synth3view}$ - noiseless 3 view dataset.
+
+\begin{figure}[H]
+  \includegraphics[width=0.9\textwidth]{figures/synth-3view-skip-relu-unsup-false-0}
+  \label{fig:synth-3view-skip-relu-unsup-false-0-sub1}
+  \caption{Sample embedding, similarity matrix, histogram, and loss curves for best performing of this set}
+\end{figure}
+\begin{figure}[H]
+  \includegraphics[width=0.9\textwidth]{figures/synth-3view-skip-leakyrelu-unsup-true-0}
+  \label{fig:synth-3view-skip-leakyrelu-unsup-true-0-sub1}
+  \caption{Sample embedding, similarity matrix, histogram, and loss curves for worst performing of this set}
+\end{figure}
+\begin{figure}[H]
+  \includegraphics[width=0.9\textwidth]{figures/synth-3view-skip-relu-unsup-true-0}
+  \label{fig:synth-3view-skip-relu-unsup-true-0-sub1}
+  \caption{Sample embedding, similarity matrix, histogram, and loss curves for random experiment of this set}
+\end{figure}
+\begin{table}[H]
+  \caption{Numerical results}
+      \begin{tabular}{|c|c|c|c|} \hline
+                                      &  Same Point Similarities  &  Different Point Similarities  \\ \hline
+Baseline   & 5.11e-01 $\pm$ 3.90e-01 & 2.56e-01 $\pm$ 2.06e-01 \\ \hline
+Skip Type 0 Arch., LeakyReLU, Supervised   & 9.92e-01 $\pm$ 1.68e-02 & 1.10e-01 $\pm$ 1.32e-01 \\ \hline
+Skip Type 0 Arch., LeakyReLU, Unsupervised   & 9.97e-01 $\pm$ 6.13e-03 & 1.25e-01 $\pm$ 1.31e-01 \\ \hline
+Skip Type 0 Arch., ReLU, Supervised   & 9.98e-01 $\pm$ 4.96e-03 & 9.04e-02 $\pm$ 1.37e-01 \\ \hline
+Skip Type 0 Arch., ReLU, Unsupervised   & 9.98e-01 $\pm$ 5.27e-03 & 1.19e-01 $\pm$ 1.30e-01 \\ \hline
+Skip Type 1 Arch., LeakyReLU, Supervised   & 9.97e-01 $\pm$ 7.39e-03 & 9.74e-02 $\pm$ 1.38e-01 \\ \hline
+Skip Type 1 Arch., LeakyReLU, Unsupervised   & 9.94e-01 $\pm$ 1.04e-02 & 1.21e-01 $\pm$ 1.31e-01 \\ \hline
+Skip Type 1 Arch., ReLU, Supervised   & 9.98e-01 $\pm$ 5.89e-03 & 8.48e-02 $\pm$ 1.41e-01 \\ \hline
+Skip Type 1 Arch., ReLU, Unsupervised   & 9.96e-01 $\pm$ 7.70e-03 & 1.16e-01 $\pm$ 1.32e-01 \\ \hline
+      \end{tabular}
+      \label{fig:12_tab1}
+\end{table}
+
+\subsubsection*{Experiment Run 13}
+Using ReLU activation type with aforementioned pairwise noise. 
+The ``Long Skip'' type architecture is basically the skip type but with additional skip connections from layer 1 to layer $n/2$ and layer $n$.
+This helps training and performance a fair amount since it allows way more layers (doubling or tripling).
+
+\begin{figure}[H]
+  \includegraphics[width=0.9\textwidth]{figures/pairwise5-skip0-relu-ld-false-unsup-true-0}
+  \label{fig:pairwise5-skip0-relu-ld-false-unsup-true-0-sub1}
+  \caption{Sample embedding, similarity matrix, histogram, and loss curves for best performing of this set}
+\end{figure}
+\begin{figure}[H]
+  \includegraphics[width=0.9\textwidth]{figures/pairwise3-attn2-relu-ld-true-unsup-false-0}
+  \label{fig:pairwise3-attn2-relu-ld-true-unsup-false-0-sub1}
+  \caption{Sample embedding, similarity matrix, histogram, and loss curves for worst performing of this set}
+\end{figure}
+\begin{figure}[H]
+  \includegraphics[width=0.9\textwidth]{figures/pairwise3-longskip0-relu-ld-true-unsup-false-0}
+  \label{fig:pairwise3-longskip0-relu-ld-true-unsup-false-0-sub1}
+  \caption{Sample embedding, similarity matrix, histogram, and loss curves for random experiment of this set}
+\end{figure}
+
+\begin{table}[H]
+  \caption{\texttt{pairwise3} results}
+      \begin{tabular}{|l|c|c|c|} \hline
+                                      &  Same Point Similarities  &  Different Point Similarities  \\ \hline
+Baseline   & 5.11e-01 $\pm$ 3.90e-01 & 2.56e-01 $\pm$ 2.06e-01 \\ \hline
+\multicolumn{3}{|c|}{Data type \texttt{pairwise3} with generated data} \\ \hline
+GAT Network Type 0 Arch., Supervised   & 5.75e-01 $\pm$ 3.58e-01 & 2.26e-01 $\pm$ 1.77e-01 \\ \hline
+GAT Network Type 0 Arch., Unsupervised   & 7.11e-01 $\pm$ 2.65e-01 & 1.74e-01 $\pm$ 1.41e-01 \\ \hline
+GAT Network Type 1 Arch., Supervised   & 5.96e-01 $\pm$ 3.44e-01 & 2.07e-01 $\pm$ 1.65e-01 \\ \hline
+GAT Network Type 1 Arch., Unsupervised   & 7.65e-01 $\pm$ 2.36e-01 & 1.87e-01 $\pm$ 1.53e-01 \\ \hline
+GAT Network Type 2 Arch., Supervised   & 8.33e-01 $\pm$ 1.79e-01 & 2.17e-01 $\pm$ 1.67e-01 \\ \hline
+GAT Network Type 2 Arch., Unsupervised   & 5.13e-01 $\pm$ 3.89e-01 & 1.98e-01 $\pm$ 1.71e-01 \\ \hline
+Long Skip Type 0 Arch., Supervised   & 9.90e-01 $\pm$ 2.35e-02 & 7.18e-02 $\pm$ 1.60e-01 \\ \hline
+Long Skip Type 0 Arch., Unsupervised   & 9.59e-01 $\pm$ 6.03e-02 & 1.00e-01 $\pm$ 1.57e-01 \\ \hline
+Skip Connections Type 1 Arch., Supervised   & 9.74e-01 $\pm$ 5.64e-02 & 9.52e-02 $\pm$ 1.60e-01 \\ \hline
+Skip Connections Type 1 Arch., Unsupervised   & 9.66e-01 $\pm$ 7.82e-02 & 8.26e-02 $\pm$ 1.61e-01 \\ \hline
+\multicolumn{3}{|c|}{Data type \texttt{pairwise3} with prestored data} \\ \hline
+GAT Network Type 0 Arch., Supervised   & 5.95e-01 $\pm$ 3.45e-01 & 2.05e-01 $\pm$ 1.66e-01 \\ \hline
+GAT Network Type 0 Arch., Unsupervised   & 6.64e-01 $\pm$ 3.15e-01 & 1.82e-01 $\pm$ 1.68e-01 \\ \hline
+GAT Network Type 1 Arch., Supervised   & 5.09e-01 $\pm$ 3.93e-01 & 2.21e-01 $\pm$ 1.87e-01 \\ \hline
+GAT Network Type 1 Arch., Unsupervised   & 7.07e-01 $\pm$ 2.76e-01 & 1.64e-01 $\pm$ 1.47e-01 \\ \hline
+GAT Network Type 2 Arch., Supervised   & 4.92e-01 $\pm$ 4.00e-01 & 2.30e-01 $\pm$ 1.98e-01 \\ \hline
+GAT Network Type 2 Arch., Unsupervised   & 6.12e-01 $\pm$ 3.33e-01 & 2.04e-01 $\pm$ 1.65e-01 \\ \hline
+Long Skip Type 0 Arch., Supervised   & 9.80e-01 $\pm$ 3.75e-02 & 8.56e-02 $\pm$ 1.57e-01 \\ \hline
+Long Skip Type 0 Arch., Unsupervised   & 9.62e-01 $\pm$ 5.32e-02 & 1.01e-01 $\pm$ 1.61e-01 \\ \hline
+Skip Connections Type 1 Arch., Supervised   & 9.73e-01 $\pm$ 6.48e-02 & 8.12e-02 $\pm$ 1.60e-01 \\ \hline
+Skip Connections Type 1 Arch., Unsupervised   & 9.66e-01 $\pm$ 7.71e-02 & 8.23e-02 $\pm$ 1.57e-01 \\ \hline
+      \end{tabular}
+      \label{fig:13_tab1}
+\end{table}
+
+\begin{table}[H]
+  \caption{\texttt{pairwise5} results}
+      \begin{tabular}{|l|c|c|c|} \hline
+                                      &  Same Point Similarities  &  Different Point Similarities  \\ \hline
+Baseline   & 5.11e-01 $\pm$ 3.90e-01 & 2.56e-01 $\pm$ 2.06e-01 \\ \hline
+\multicolumn{3}{|c|}{Data type \texttt{pairwise5} with generated data} \\ \hline
+GAT Network Type 0 Arch., Supervised   & 5.04e-01 $\pm$ 3.97e-01 & 2.12e-01 $\pm$ 1.90e-01 \\ \hline
+GAT Network Type 0 Arch., Unsupervised   & 7.51e-01 $\pm$ 2.39e-01 & 2.06e-01 $\pm$ 1.57e-01 \\ \hline
+GAT Network Type 1 Arch., Supervised   & 6.99e-01 $\pm$ 2.74e-01 & 1.99e-01 $\pm$ 1.53e-01 \\ \hline
+GAT Network Type 1 Arch., Unsupervised   & 5.41e-01 $\pm$ 3.74e-01 & 2.16e-01 $\pm$ 1.79e-01 \\ \hline
+GAT Network Type 2 Arch., Supervised   & 6.72e-01 $\pm$ 2.90e-01 & 2.01e-01 $\pm$ 1.55e-01 \\ \hline
+GAT Network Type 2 Arch., Unsupervised   & 5.09e-01 $\pm$ 3.93e-01 & 1.94e-01 $\pm$ 1.83e-01 \\ \hline
+Long Skip Type 0 Arch., Supervised   & 9.68e-01 $\pm$ 5.29e-02 & 9.50e-02 $\pm$ 1.58e-01 \\ \hline
+Long Skip Type 0 Arch., Unsupervised   & 9.40e-01 $\pm$ 7.90e-02 & 1.11e-01 $\pm$ 1.54e-01 \\ \hline
+Skip Connections Type 1 Arch., Supervised   & 9.69e-01 $\pm$ 7.55e-02 & 6.14e-02 $\pm$ 1.43e-01 \\ \hline
+Skip Connections Type 1 Arch., Unsupervised   & 9.66e-01 $\pm$ 8.32e-02 & 6.17e-02 $\pm$ 1.37e-01 \\ \hline
+\multicolumn{3}{|c|}{Data type \texttt{pairwise5} with prestored data} \\ \hline
+GAT Network Type 0 Arch., Supervised   & 8.06e-01 $\pm$ 2.14e-01 & 1.88e-01 $\pm$ 1.63e-01 \\ \hline
+GAT Network Type 0 Arch., Unsupervised   & 5.92e-01 $\pm$ 3.56e-01 & 1.76e-01 $\pm$ 1.71e-01 \\ \hline
+GAT Network Type 1 Arch., Supervised   & 4.96e-01 $\pm$ 3.99e-01 & 2.27e-01 $\pm$ 1.97e-01 \\ \hline
+GAT Network Type 1 Arch., Unsupervised   & 5.95e-01 $\pm$ 3.44e-01 & 2.06e-01 $\pm$ 1.65e-01 \\ \hline
+GAT Network Type 2 Arch., Supervised   & 8.11e-01 $\pm$ 2.06e-01 & 2.02e-01 $\pm$ 1.68e-01 \\ \hline
+GAT Network Type 2 Arch., Unsupervised   & 5.84e-01 $\pm$ 3.49e-01 & 1.96e-01 $\pm$ 1.62e-01 \\ \hline
+Long Skip Type 0 Arch., Supervised   & 9.66e-01 $\pm$ 5.37e-02 & 9.77e-02 $\pm$ 1.60e-01 \\ \hline
+Long Skip Type 0 Arch., Unsupervised   & 9.74e-01 $\pm$ 4.28e-02 & 8.56e-02 $\pm$ 1.51e-01 \\ \hline
+Skip Connections Type 1 Arch., Supervised   & 9.69e-01 $\pm$ 7.68e-02 & 6.22e-02 $\pm$ 1.44e-01 \\ \hline
+Skip Connections Type 1 Arch., Unsupervised   & 9.65e-01 $\pm$ 8.34e-02 & 6.49e-02 $\pm$ 1.42e-01 \\ \hline
+      \end{tabular}
+      \label{fig:13_tab2}
+\end{table}
+
+\subsubsection*{Experiment Run 14}
+Comparison between GAT and Sparse GAT architecture
+
+\begin{figure}[H]
+  \includegraphics[width=0.9\textwidth]{figures/pairwise3-spattn0-0-0}
+  \label{fig:pairwise3-spattn0-0-0-sub1}
+  \caption{Sample embedding, similarity matrix, histogram, and loss curves for best performing of this set}
+\end{figure}
+\begin{figure}[H]
+  \includegraphics[width=0.9\textwidth]{figures/pairwise5-attn0-0-0}
+  \label{fig:pairwise5-attn0-0-0-sub1}
+  \caption{Sample embedding, similarity matrix, histogram, and loss curves for worst performing of this set}
+\end{figure}
+\begin{figure}[H]
+  \includegraphics[width=0.9\textwidth]{figures/pairwise3-spattn1-0-1}
+  \label{fig:pairwise3-spattn1-0-1-sub1}
+  \caption{Sample embedding, similarity matrix, histogram, and loss curves for random experiment of this se}
+\end{figure}
+\begin{table}[H]
+  \caption{Numerical results}
+      \begin{tabular}{|c|c|c|c|} \hline
+                                      &  Same Point Similarities  &  Different Point Similarities  \\ \hline
+Baseline   & 5.12e-01 $\pm$ 3.91e-01 & 2.56e-01 $\pm$ 2.06e-01 \\ \hline
+\multicolumn{3}{|c|}{Data type \texttt{pairwise3} with prestored data} \\ \hline
+GAT Network Type 0 Architecture   & 7.38e-01 $\pm$ 2.60e-01 & 1.52e-01 $\pm$ 1.55e-01 \\ \hline
+GAT Network Type 0 Architecture   & 7.38e-01 $\pm$ 2.60e-01 & 1.52e-01 $\pm$ 1.55e-01 \\ \hline
+GAT Network Type 1 Architecture   & 7.19e-01 $\pm$ 2.62e-01 & 1.87e-01 $\pm$ 1.64e-01 \\ \hline
+GAT Network Type 1 Architecture   & 7.19e-01 $\pm$ 2.62e-01 & 1.87e-01 $\pm$ 1.64e-01 \\ \hline
+Sparse GAT Network Type 0 Architecture   & 8.90e-01 $\pm$ 1.36e-01 & 1.68e-01 $\pm$ 1.61e-01 \\ \hline
+Sparse GAT Network Type 0 Architecture   & 8.90e-01 $\pm$ 1.36e-01 & 1.68e-01 $\pm$ 1.61e-01 \\ \hline
+Sparse GAT Network Type 1 Architecture   & 9.80e-01 $\pm$ 5.07e-02 & 8.68e-02 $\pm$ 1.43e-01 \\ \hline
+Sparse GAT Network Type 1 Architecture   & 9.80e-01 $\pm$ 5.07e-02 & 8.68e-02 $\pm$ 1.43e-01 \\ \hline
+\multicolumn{3}{|c|}{Data type \texttt{pairwise5} with prestored data} \\ \hline
+GAT Network Type 0 Architecture   & 6.83e-01 $\pm$ 3.22e-01 & 4.33e-01 $\pm$ 2.63e-01 \\ \hline
+GAT Network Type 0 Architecture   & 6.83e-01 $\pm$ 3.22e-01 & 4.33e-01 $\pm$ 2.63e-01 \\ \hline
+GAT Network Type 1 Architecture   & 6.36e-01 $\pm$ 3.54e-01 & 1.97e-01 $\pm$ 2.00e-01 \\ \hline
+GAT Network Type 1 Architecture   & 6.36e-01 $\pm$ 3.54e-01 & 1.97e-01 $\pm$ 2.00e-01 \\ \hline
+Sparse GAT Network Type 0 Architecture   & 9.50e-01 $\pm$ 8.77e-02 & 1.16e-01 $\pm$ 1.49e-01 \\ \hline
+Sparse GAT Network Type 0 Architecture   & 9.50e-01 $\pm$ 8.77e-02 & 1.16e-01 $\pm$ 1.49e-01 \\ \hline
+Sparse GAT Network Type 1 Architecture   & 6.24e-01 $\pm$ 3.50e-01 & 3.99e-01 $\pm$ 2.62e-01 \\ \hline
+Sparse GAT Network Type 1 Architecture   & 6.24e-01 $\pm$ 3.50e-01 & 3.99e-01 $\pm$ 2.62e-01 \\ \hline
+\multicolumn{3}{|c|}{Data type \texttt{pairwise5} with data generation} \\ \hline
+GAT Network Type 0 Architecture   & 5.26e-01 $\pm$ 3.87e-01 & 2.31e-01 $\pm$ 1.94e-01 \\ \hline
+GAT Network Type 0 Architecture   & 5.26e-01 $\pm$ 3.87e-01 & 2.31e-01 $\pm$ 1.94e-01 \\ \hline
+GAT Network Type 0 Architecture   & 4.87e-01 $\pm$ 4.07e-01 & 2.13e-01 $\pm$ 2.00e-01 \\ \hline
+GAT Network Type 0 Architecture   & 4.87e-01 $\pm$ 4.07e-01 & 2.13e-01 $\pm$ 2.00e-01 \\ \hline
+GAT Network Type 0 Architecture   & 4.88e-01 $\pm$ 4.06e-01 & 2.17e-01 $\pm$ 1.97e-01 \\ \hline
+GAT Network Type 0 Architecture   & 4.88e-01 $\pm$ 4.06e-01 & 2.17e-01 $\pm$ 1.97e-01 \\ \hline
+GAT Network Type 0 Architecture   & 4.87e-01 $\pm$ 4.02e-01 & 2.23e-01 $\pm$ 1.98e-01 \\ \hline
+GAT Network Type 0 Architecture   & 4.87e-01 $\pm$ 4.02e-01 & 2.23e-01 $\pm$ 1.98e-01 \\ \hline
+Sparse GAT Network Type 0 Architecture   & 9.30e-01 $\pm$ 1.36e-01 & 1.42e-01 $\pm$ 1.53e-01 \\ \hline
+Sparse GAT Network Type 0 Architecture   & 9.30e-01 $\pm$ 1.36e-01 & 1.42e-01 $\pm$ 1.53e-01 \\ \hline
+Sparse GAT Network Type 0 Architecture   & 9.31e-01 $\pm$ 1.23e-01 & 1.33e-01 $\pm$ 1.56e-01 \\ \hline
+Sparse GAT Network Type 0 Architecture   & 9.31e-01 $\pm$ 1.23e-01 & 1.33e-01 $\pm$ 1.56e-01 \\ \hline
+Sparse GAT Network Type 0 Architecture   & 8.81e-01 $\pm$ 1.57e-01 & 1.51e-01 $\pm$ 1.48e-01 \\ \hline
+Sparse GAT Network Type 0 Architecture   & 8.81e-01 $\pm$ 1.57e-01 & 1.51e-01 $\pm$ 1.48e-01 \\ \hline
+Sparse GAT Network Type 0 Architecture   & 9.30e-01 $\pm$ 1.17e-01 & 1.38e-01 $\pm$ 1.57e-01 \\ \hline
+Sparse GAT Network Type 0 Architecture   & 9.30e-01 $\pm$ 1.17e-01 & 1.38e-01 $\pm$ 1.57e-01 \\ \hline
+      \end{tabular}
+      \label{fig:{0}_tab1}
+\end{table}
+
+\subsubsection*{Experiment Run 16}
+(Run 16 had some errors)
+Testing on outliers. An outlier is the following noise model:
+\begin{equation*}
+Hi
+\end{equation*}
+All the architectures are of type Long Skip Type 0 Arch. (\texttt{longskip0}).
+
+\begin{figure}[H]
+  \includegraphics[width=0.9\textwidth]{figures/outlier1-longskip0-load-false-1}
+  \label{fig:outlier1-longskip0-load-false-1-sub1}
+  \caption{Sample embedding, similarity matrix, histogram, and loss curves for best performing of this set}
+\end{figure}
+\begin{figure}[H]
+  \includegraphics[width=0.9\textwidth]{figures/outlier8-longskip0-load-false-0}
+  \label{fig:outlier8-longskip0-load-false-0-sub1}
+  \caption{Sample embedding, similarity matrix, histogram, and loss curves for worst performing of this set}
+\end{figure}
+\begin{figure}[H]
+  \includegraphics[width=0.9\textwidth]{figures/outlier2-longskip0-load-false-1}
+  \label{fig:outlier2-longskip0-load-false-1-sub1}
+  \caption{Sample embedding, similarity matrix, histogram, and loss curves for random experiment of this set}
+\end{figure}
+
+\begin{table}[H]
+  \caption{Numerical results}
+      \begin{tabular}{|l|c|c|c|} \hline
+                                      &  Same Point Similarities  &  Different Point Similarities  \\ \hline
+Baseline   & 5.10e-01 $\pm$ 3.90e-01 & 2.56e-01 $\pm$ 2.06e-01 \\ \hline
+Data type \texttt{outlier1} & 9.73e-01 $\pm$ 9.43e-02 & 1.53e-01 $\pm$ 1.39e-01 \\ \hline
+Data type \texttt{outlier1} & 9.75e-01 $\pm$ 7.25e-02 & 1.51e-01 $\pm$ 1.44e-01 \\ \hline
+Data type \texttt{outlier1} & 9.70e-01 $\pm$ 9.98e-02 & 1.53e-01 $\pm$ 1.40e-01 \\ \hline
+Data type \texttt{outlier2} & 9.28e-01 $\pm$ 1.51e-01 & 1.57e-01 $\pm$ 1.39e-01 \\ \hline
+Data type \texttt{outlier2} & 9.38e-01 $\pm$ 1.43e-01 & 1.60e-01 $\pm$ 1.38e-01 \\ \hline
+Data type \texttt{outlier2} & 9.46e-01 $\pm$ 1.32e-01 & 1.50e-01 $\pm$ 1.36e-01 \\ \hline
+Data type \texttt{outlier4} & 9.33e-01 $\pm$ 1.79e-01 & 1.46e-01 $\pm$ 1.50e-01 \\ \hline
+Data type \texttt{outlier4} & 9.17e-01 $\pm$ 1.74e-01 & 1.58e-01 $\pm$ 1.41e-01 \\ \hline
+Data type \texttt{outlier4} & 9.29e-01 $\pm$ 1.79e-01 & 1.41e-01 $\pm$ 1.48e-01 \\ \hline
+Data type \texttt{outlier8} & 8.99e-01 $\pm$ 1.95e-01 & 1.61e-01 $\pm$ 1.40e-01 \\ \hline
+Data type \texttt{outlier8} & 9.27e-01 $\pm$ 1.79e-01 & 1.40e-01 $\pm$ 1.51e-01 \\ \hline
+Data type \texttt{outlier8} & 9.22e-01 $\pm$ 1.97e-01 & 1.35e-01 $\pm$ 1.53e-01 \\ \hline
+      \end{tabular}
+      \label{fig:tab1}
+\end{table}
+
+\subsubsection*{Experiment Run 17}
+This was experimenting to see if we could handle more views. As the Long Skip type architectures seemed to work better.
+
+\begin{figure}[H]
+  \includegraphics[width=0.9\textwidth]{figures/pairwise5view5-longskip0-load-true-1}
+  \label{fig:pairwise5view5-longskip0-load-true-1-sub1}
+  \caption{Sample embedding, similarity matrix, histogram, and loss curves for best performing of this set}
+\end{figure}
+\begin{figure}[H]
+  \includegraphics[width=0.9\textwidth]{figures/6view-longskip0-load-true-0}
+  \label{fig:6view-longskip0-load-true-0-sub1}
+  \caption{Sample embedding, similarity matrix, histogram, and loss curves for worst performing of this set}
+\end{figure}
+\begin{figure}[H]
+  \includegraphics[width=0.9\textwidth]{figures/pairwise3view5-longskip1-load-true-1}
+  \label{fig:pairwise3view5-longskip1-load-true-1-sub1}
+  \caption{Sample embedding, similarity matrix, histogram, and loss curves for random experiment of this set}
+\end{figure}
+
+\begin{table}[H]
+  \caption{Numerical results}
+      \begin{tabular}{|l|c|c|c|} \hline
+                                      &  Same Point Similarities  &  Different Point Similarities  \\ \hline
+Baseline   & 4.14e-01 $\pm$ 3.54e-01 & 2.61e-01 $\pm$ 2.13e-01 \\ \hline
+\multicolumn{3}{|c|}{Data type \texttt{4view} with prestored data} \\ \hline
+Long Skip Type 0 Arch.   & 9.47e-01 $\pm$ 8.19e-02 & 1.61e-01 $\pm$ 1.41e-01 \\ \hline
+Long Skip Type 0 Arch.   & 1.00e+00 $\pm$ 1.14e-03 & 1.53e-01 $\pm$ 1.37e-01 \\ \hline
+Long Skip Type 0 Arch.   & 9.06e-01 $\pm$ 1.32e-01 & 1.59e-01 $\pm$ 1.53e-01 \\ \hline
+Long Skip Type 1 Arch.   & 1.00e+00 $\pm$ 2.75e-04 & 1.24e-01 $\pm$ 1.72e-01 \\ \hline
+Long Skip Type 1 Arch.   & 1.00e+00 $\pm$ 6.56e-04 & 1.17e-01 $\pm$ 1.72e-01 \\ \hline
+Long Skip Type 1 Arch.   & 9.99e-01 $\pm$ 4.87e-03 & 1.51e-01 $\pm$ 1.38e-01 \\ \hline
+\multicolumn{3}{|c|}{Data type \texttt{5view} with prestored data} \\ \hline
+Long Skip Type 0 Arch.   & 8.96e-01 $\pm$ 1.33e-01 & 1.66e-01 $\pm$ 1.62e-01 \\ \hline
+Long Skip Type 0 Arch.   & 9.99e-01 $\pm$ 2.73e-03 & 1.50e-01 $\pm$ 1.37e-01 \\ \hline
+Long Skip Type 0 Arch.   & 1.00e+00 $\pm$ 1.30e-03 & 1.50e-01 $\pm$ 1.35e-01 \\ \hline
+Long Skip Type 1 Arch.   & 1.00e+00 $\pm$ 4.15e-04 & 1.22e-01 $\pm$ 1.67e-01 \\ \hline
+Long Skip Type 1 Arch.   & 9.99e-01 $\pm$ 2.63e-03 & 1.52e-01 $\pm$ 1.44e-01 \\ \hline
+Long Skip Type 1 Arch.   & 9.99e-01 $\pm$ 2.98e-03 & 1.50e-01 $\pm$ 1.43e-01 \\ \hline
+\multicolumn{3}{|c|}{Data type \texttt{6view} with prestored data} \\ \hline
+Long Skip Type 0 Arch.   & 8.48e-01 $\pm$ 1.75e-01 & 1.98e-01 $\pm$ 1.72e-01 \\ \hline
+Long Skip Type 0 Arch.   & 9.98e-01 $\pm$ 5.64e-03 & 1.48e-01 $\pm$ 1.42e-01 \\ \hline
+Long Skip Type 0 Arch.   & 9.99e-01 $\pm$ 3.27e-03 & 1.50e-01 $\pm$ 1.36e-01 \\ \hline
+Long Skip Type 1 Arch.   & 9.99e-01 $\pm$ 1.93e-03 & 1.47e-01 $\pm$ 1.39e-01 \\ \hline
+Long Skip Type 1 Arch.   & 1.00e+00 $\pm$ 6.77e-04 & 1.26e-01 $\pm$ 1.82e-01 \\ \hline
+Long Skip Type 1 Arch.   & 1.00e+00 $\pm$ 1.76e-03 & 1.24e-01 $\pm$ 1.75e-01 \\ \hline
+\multicolumn{3}{|c|}{Data type \texttt{pairwise3view5} with prestored data} \\ \hline
+Long Skip Type 0 Arch.   & 9.86e-01 $\pm$ 2.63e-02 & 9.36e-02 $\pm$ 1.57e-01 \\ \hline
+Long Skip Type 0 Arch.   & 9.79e-01 $\pm$ 3.44e-02 & 1.06e-01 $\pm$ 1.64e-01 \\ \hline
+Long Skip Type 1 Arch.   & 9.80e-01 $\pm$ 2.63e-02 & 1.14e-01 $\pm$ 1.60e-01 \\ \hline
+Long Skip Type 1 Arch.   & 9.89e-01 $\pm$ 2.47e-02 & 7.67e-02 $\pm$ 1.56e-01 \\ \hline
+\multicolumn{3}{|c|}{Data type \texttt{pairwise3view6} with prestored data} \\ \hline
+Long Skip Type 0 Arch.   & 8.98e-01 $\pm$ 9.67e-02 & 1.51e-01 $\pm$ 1.51e-01 \\ \hline
+Long Skip Type 0 Arch.   & 9.84e-01 $\pm$ 3.16e-02 & 7.46e-02 $\pm$ 1.57e-01 \\ \hline
+Long Skip Type 1 Arch.   & 8.37e-01 $\pm$ 1.51e-01 & 1.47e-01 $\pm$ 1.61e-01 \\ \hline
+Long Skip Type 1 Arch.   & 8.39e-01 $\pm$ 1.63e-01 & 1.37e-01 $\pm$ 1.51e-01 \\ \hline
+\multicolumn{3}{|c|}{Data type \texttt{pairwise5view5} with prestored data} \\ \hline
+Long Skip Type 0 Arch.   & 9.65e-01 $\pm$ 5.54e-02 & 1.07e-01 $\pm$ 1.57e-01 \\ \hline
+Long Skip Type 0 Arch.   & 9.86e-01 $\pm$ 4.68e-02 & 5.57e-02 $\pm$ 1.38e-01 \\ \hline
+Long Skip Type 1 Arch.   & 9.68e-01 $\pm$ 4.40e-02 & 1.20e-01 $\pm$ 1.47e-01 \\ \hline
+Long Skip Type 1 Arch.   & 9.90e-01 $\pm$ 2.68e-02 & 5.84e-02 $\pm$ 1.37e-01 \\ \hline
+      \end{tabular}
+      \label{fig:tab1}
+\end{table}
+
+\subsubsection*{Thoughts}
+To my dismay, the GAT architecture seems very unstable to train and doesn't converge very well if at all.
+Comparitavely, the best results come from stacking many layers - on the order of 15 seems to work for these problems pretty well.
+Now the best thing to do would be to go to real data since these seem to be working pretty well.
+To get better results we really do need additional losses though.
+On the flip side, the Long Skip was a great discovery and works really well, much better than any of the previous architectures.
+It needs to get more layers for more views...
+this I am guessing a fundamental limitation.
+I wonder if there is a way to get around this.
+
 \end{document}

### 2018-10-11 journal/main.tex
Added more stuff to journal for experiments

@@
 
+\entry{2018}{10}{08}
+\subsubsection*{Rome16K dataset}
+Formatting this dataset took much longer than expected but I managed to build a parser for it, and now can generate data.
+The dataset is quite large - I had to subsample it, but if I used the whole thing there would be 1 million examples of triplets
+
+\subsubsection*{Rome16K Experiments Round 1}
+These initial experiments were a failure, so I did some experimentation with the learning rate afterward
+
+\begin{figure}[H]
+  \includegraphics[width=0.9\textwidth]{figures/rome16kknn0-longskip0-load-true-0}
+  \label{fig:rome16kknn0-longskip0-load-true-0-sub1}
+  \caption{Sample embedding, similarity matrix, histogram, and loss curves for best performing of this set}
+\end{figure}
+\begin{figure}[H]
+  \includegraphics[width=0.9\textwidth]{figures/rome16kknn0-longskip0-load-true-0}
+  \label{fig:rome16kknn0-longskip0-load-true-0-sub1}
+  \caption{Sample embedding, similarity matrix, histogram, and loss curves for worst performing of this set}
+\end{figure}
+\begin{table}[H]
+  \caption{Numerical results}
+      \begin{tabular}{|l|c|c|c|} \hline
+                                      &  Same Point Similarities  &  Different Point Similarities  \\ \hline
+Baseline   & 9.71e-01 $\pm$ 3.87e-02 & 4.75e-01 $\pm$ 1.42e-01 \\ \hline
+Long Skip Type 0 Architecture   & 1.00e+00 $\pm$ 1.64e-07 & 1.00e+00 $\pm$ 3.28e-07 \\ \hline
+Long Skip Type 1 Architecture   & 1.00e+00 $\pm$ 1.66e-06 & 1.00e+00 $\pm$ 1.37e-06 \\ \hline
+      \end{tabular}
+      \label{fig:tab1}
+\end{table}
+
+\subsubsection*{Rome16K Experiments Round 2}
+This seem to work better - using a learning rate of 1e-4 seemed to work best
+
+\begin{figure}[H]
+  \includegraphics[width=0.9\textwidth]{figures/rome16kknn0-longskip0-lr-1e-4-0}
+  \label{fig:rome16kknn0-longskip0-lr-1e-4-0-sub1}
+  \caption{Sample embedding, similarity matrix, histogram, and loss curves for best performing of this set}
+\end{figure}
+\begin{figure}[H]
+  \includegraphics[width=0.9\textwidth]{figures/rome16kknn0-longskip0-lr-1e-3-0}
+  \label{fig:rome16kknn0-longskip0-lr-1e-3-0-sub1}
+  \caption{Sample embedding, similarity matrix, histogram, and loss curves for worst performing of this set}
+\end{figure}
+\begin{figure}[H]
+  \includegraphics[width=0.9\textwidth]{figures/rome16kknn0-longskip0-lr-1e-5-0}
+  \label{fig:rome16kknn0-longskip0-lr-1e-5-0-sub1}
+  \caption{Sample embedding, similarity matrix, histogram, and loss curves for random experiment of this set}
+\end{figure}
+\begin{table}[H]
+  \caption{Numerical results}
+      \begin{tabular}{|l|c|c|c|} \hline
+                                      &  Same Point Similarities  &  Different Point Similarities  \\ \hline
+Baseline   & 9.70e-01 $\pm$ 3.84e-02 & 4.78e-01 $\pm$ 1.42e-01 \\ \hline
+Long Skip Type 0 Architecture, Learning rate 1e-3   & 1.00e+00 $\pm$ 1.80e-07 & 1.00e+00 $\pm$ 4.03e-07 \\ \hline
+Long Skip Type 0 Architecture, Learning rate 1e-4   & 9.00e-01 $\pm$ 1.55e-01 & 1.09e-01 $\pm$ 1.42e-01 \\ \hline
+Long Skip Type 0 Architecture, Learning rate 1e-5   & 7.59e-01 $\pm$ 2.86e-01 & 7.95e-02 $\pm$ 1.19e-01 \\ \hline
+      \end{tabular}
+      \label{fig:tab1}
+\end{table}
+
+\subsubsection*{Rome16K Experiments Round 3}
+Here I tried to use different decay rate schedules to see which worked best. All these tests used the Long Skip Type 0 Architecture and a learning rate of 1e-4. It seems exponential still works best.
+
+\begin{figure}[H]
+  \includegraphics[width=0.9\textwidth]{figures/rome16kknn0-longskip0-lr-1e-4-type-exponential-steps-3e-1-0}
+  \label{fig:rome16kknn0-longskip0-lr-1e-4-type-exponential-steps-3e-1-0-sub1}
+  \caption{Sample embedding, similarity matrix, histogram, and loss curves for best performing of this set}
+\end{figure}
+\begin{figure}[H]
+  \includegraphics[width=0.9\textwidth]{figures/rome16kknn0-longskip0-lr-1e-4-type-fixed-steps-1e0-0}
+  \label{fig:rome16kknn0-longskip0-lr-1e-4-type-fixed-steps-1e0-0-sub1}
+  \caption{Sample embedding, similarity matrix, histogram, and loss curves for worst performing of this set}
+\end{figure}
+\begin{figure}[H]
+  \includegraphics[width=0.9\textwidth]{figures/rome16kknn0-longskip0-lr-1e-4-type-exponential-steps-1e0-0}
+  \label{fig:rome16kknn0-longskip0-lr-1e-4-type-exponential-steps-1e0-0-sub1}
+  \caption{Sample embedding, similarity matrix, histogram, and loss curves for random experiment of this set}
+\end{figure}
+\begin{table}[H]
+  \caption{Numerical results}
+      \begin{tabular}{|l|c|c|c|} \hline
+                                      &  Same Point Similarities  &  Different Point Similarities  \\ \hline
+Baseline   & 9.70e-01 $\pm$ 3.88e-02 & 4.78e-01 $\pm$ 1.42e-01 \\ \hline
+LR Decay Exponential, LR Decay Steps 1e0 & 6.94e-01 $\pm$ 3.18e-01 & 7.96e-02 $\pm$ 1.08e-01 \\ \hline
+LR Decay Exponential, LR Decay Steps 3e-1& 5.84e-01 $\pm$ 3.42e-01 & 8.29e-02 $\pm$ 8.74e-02 \\ \hline
+LR Decay Exponential, LR Decay Steps 5e-1& 7.66e-01 $\pm$ 2.75e-01 & 7.93e-02 $\pm$ 1.06e-01 \\ \hline
+LR Decay Fixed                  & 6.69e-01 $\pm$ 3.34e-01 & 5.18e-01 $\pm$ 2.99e-01 \\ \hline
+LR Decay Fixed                   & 7.84e-01 $\pm$ 2.72e-01 & 8.12e-02 $\pm$ 1.27e-01 \\ \hline
+LR Decay Fixed                   & 4.64e-01 $\pm$ 4.25e-01 & 7.89e-02 $\pm$ 1.04e-01 \\ \hline
+LR Decay Polynomial, LR Decay Steps 1e0  & 5.89e-01 $\pm$ 3.73e-01 & 8.11e-02 $\pm$ 1.01e-01 \\ \hline
+LR Decay Polynomial, LR Decay Steps 3e-1 & 9.31e-01 $\pm$ 1.13e-01 & 1.92e-01 $\pm$ 2.06e-01 \\ \hline
+LR Decay Polynomial, LR Decay Steps 5e-1 & 6.78e-01 $\pm$ 3.33e-01 & 3.18e-01 $\pm$ 2.44e-01 \\ \hline
+      \end{tabular}
+      \label{fig:tab1}
+\end{table}
+
 \end{document}

### 2018-10-14 data_util/real_dataset.py
Added some fixes to the rome16k data generation

@@ -26,8 +26,6 @@ class Rome16KTripletDataset(parent_dataset.GraphSimDataset):
         sum([x[0] for _, x in parse.bundle_file_info['train'].items()])
     self.dataset_params.sizes['test'] = \
         sum([x[0] for _, x in parse.bundle_file_info['test'].items()])
-    self.np_dataset_size = \
-        sum([x[0] for _, x in parse.bundle_file_info['np_dataset'].items()])
 
   def gen_sample(self):
     print("ERROR: Cannot generate sample - need to load data")
@@ -86,9 +84,9 @@ class Rome16KTripletDataset(parent_dataset.GraphSimDataset):
     outfile = lambda idx: os.path.join(out_dir, fname.format(idx))
     print('Writing dataset to {}'.format(out_dir))
     record_idx = 0
-    pbar = tqdm.tqdm(total=self.np_dataset_size)
+    pbar = tqdm.tqdm(total=self.dataset_params.sizes['test'])
     index = 0
-    for bundle_file in parse.bundle_file_info['np_dataset']:
+    for bundle_file in parse.bundle_file_info['test']:
       scene_name = '{}/{}'.format(self.rome16k_dir, parse.scene_name(bundle_file))
       scene = parse.load_scene(scene_name)
       with open(self.triplet_fname(bundle_file), 'rb') as f:

### 2018-10-14 data_util/rome16k/parse.py

@@ -11,7 +11,7 @@ import yaml
 from data_util.rome16k import scenes
 
 # Format:
-# dict: {'train', 'test', 'np_dataset'}
+# dict: {'train', 'test'}
 #   -> dict: rome16k_name -> (ntriplets, ncams)
 bundle_file_info = {
   'train' : {
@@ -66,8 +66,6 @@ bundle_file_info = {
     '56.0.0.0': (477, 30),
     '5.9.0.0': (481, 88),
     '34.1.0.0': (487, 38),
-  },
-  'np_dataset' : {
     '11.2.0.0': (12, 40),
     '125.0.0.0': (21, 34),
     '41.0.0.0': (22, 54),
@@ -90,8 +88,7 @@ bundle_file_info = {
 
 def check_valid_name(bundle_file):
   return ((bundle_file in bundle_file_info['train']) or \
-          (bundle_file in bundle_file_info['test']) or \
-          (bundle_file in bundle_file_info['np_dataset']))
+          (bundle_file in bundle_file_info['test']))
 
 def scene_name(bundle_file):
   if not check_valid_name(bundle_file):

### 2018-10-14 gen_data.py

@@ -13,15 +13,15 @@ if not os.path.exists(opts.data_dir):
   os.makedirs(opts.data_dir)
 mydataset = dataset.get_dataset(opts)
 
-# types = [
-#   'train',
-#   'test'
-# ]
-# for t in types:
-#   dname = os.path.join(opts.data_dir,t)
-#   if not os.path.exists(dname):
-#     os.makedirs(dname)
-#   mydataset.convert_dataset(dname, t)
+types = [
+  'train',
+  'test'
+]
+for t in types:
+  dname = os.path.join(opts.data_dir,t)
+  if not os.path.exists(dname):
+    os.makedirs(dname)
+  mydataset.convert_dataset(dname, t)
 
 # Generate numpy test
 out_dir = os.path.join(opts.data_dir,'np_test')

### 2018-10-15 launch/download_files.py
Modified download_files to be able to exclude jobs in case there are problem cases

@@ -2,19 +2,49 @@ import os
 import sys
 import subprocess
 import csv
+import argparse
 
 import numpy as np
 import matplotlib.pyplot as plt
 
-def get_logs(yaml_name):
-  # raw = subprocess.check_output(["kubectl", "get", "pods", "--show-all"])
-  check_name = os.path.splitext(yaml_name)[0]
-  if len(check_name) > 56:
-    check_name = check_name[:56]
+def get_opts():
+  pass
+  """Parse arguments from command line and get all options for training."""
+  parser = argparse.ArgumentParser(description='Train motion estimator')
+  # Directory and dataset options
+  parser.add_argument('--experiments',
+                      nargs='+',
+                      help='Experiments to test data to run analysis on')
+  parser.add_argument('--exclude',
+                      nargs='+',
+                      help='Experiments to exclude')
+
+  opts = parser.parse_args()
+  return opts
+
+def in_set(x, S):
+  for s in S:
+    if x in s:
+      return True
+  return False
+
+def get_log_names(opts):
+  experiments = []
+  for name in opts.experiments:
+    yaml_name = os.path.splitext(name)[0]
+    if len(yaml_name) > 56:
+      yaml_name = yaml_name[:56]
+    experiments.append(yaml_name) 
   raw = subprocess.check_output(["kubectl", "get", "pods"])
   decoded = [ z.split() for z in raw.decode("utf-8").split("\n") ]
-  log_names = [ w[0] for w in decoded[:-1] if check_name in w[0] ]
-  logs_bytes = [ subprocess.check_output(["kubectl", "logs", log_name]) for log_name in log_names ]
+  log_names_all = [ w[0] for w in decoded[:-1] ]
+  exclude = [ 'kssh-session', 'NAME' ] + opts.exclude
+  log_names = [ w for w in log_names_all if not in_set(w, exclude) ]
+  return log_names
+
+def get_logs(log_names, yaml_name):
+  sel_names = [ w for w in log_names if yaml_name in w  ]
+  logs_bytes = [ subprocess.check_output(["kubectl", "logs", log_name]) for log_name in sel_names ]
   return [ lb.decode("utf-8").split("\n") for lb in logs_bytes ]
 
 def get_loss_values(log):
@@ -29,12 +59,15 @@ def get_loss_values(log):
         loss.append(float(line[line.index('=')+1]))
   return loss, test_loss
 
-
[…]

### 2018-10-15 cvpr2019/main.tex
Added CVPR draft

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% Include other packages here, before hyperref.
\usepackage[outdir=./]{epstopdf}

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[breaklinks=true,bookmarks=false]{hyperref}

% \cvprfinalcopy % *** Uncomment this line for the final submission

\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

%% Custom control sequences
\newcommand{\bR}{\mathbb{R}}
\newcommand{\mat}[1]{\mathbf{#1}}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}

% Pages are numbered in submission mode, and unnumbered in camera-ready
%\ifcvprfinal\pagestyle{empty}\fi
\setcounter{page}{4321}
\begin{document}

%%%%%%%%% TITLE
\title{Learning Multi-Image Matching using Cycle Consistency}

\author{Stephen Phillips, Kostas Daniilidis \\
GRASP Labratory, University of Pennsylvania\\
{\tt\small \{stephi, kostas\}@seas.upenn.edu}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
% \and
% Second Author\\
% Institution2\\
% First line of institution2 address\\
% {\tt\small secondauthor@i2.org}
}

\maketitle
%\thispagestyle{empty}

% Papers, excluding the references section,
% must be no longer than eight pages in length. The references section

%%%%%%%%% ABSTRACT
\begin{abstract}
   % Put abstract here
   % OK I hate this start but we will work on it.
   In this work we present a learning technique for refining multi-image matches in an unsupervised fashion.
   We formulate the multi-image matching problem as a graph embedding problem then use recent work in Graph Neural Networks to learn the appropriate embedding function.
   Since ground truth correspondence is difficult or expensive to come by in many real world datasets, we use cycle consistency as our loss function.
   Additional losses can be added if more information is available in the training set for better test performance.
   To the best of our knowledge, no other works have used learning for multi-image feature matching.
   Our experiments show that our method is competitive with other optimization based approaches.
\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}

% Insert Introduction here
TODO

\begin{figure}[t]
\begin{center}
  \fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
  % \includegraphics[width=0.8\linewidth]{figures/experiments.eps}
\end{center}
   \caption{Example of caption.  It is set in Roman so that mathematics
   (always set in Roman: $B \sin A = A \sin B$) may be included without an
   ugly clash.}
\label{fig:long}
\label{fig:onecol}
\end{figure}

%-------------------------------------------------------------------------
\section{Related Work}

TODO

% When placing figures in \LaTeX, it's almost always best to use
% \verb+\includegraphics+, and to specify the  figure width as a multiple of
% the line width as in the example below
% {\small\begin{verbatim}
%    \usepackage[dvips]{graphicx} ...
%    \includegraphics[width=0.8\linewidth]
%                    {myfile.eps}
% \end{verbatim}
% }

%------------------------------------------------------------------------
\section{Method}
Our goal is to find correspondences between multiple (more than two) images.
There are many techniques for finding such matchins in a pairwise setting, such as graph matching \cite{suh2015subgraph, hu2016distributable} or even learning techniques \cite{yi2018learning}. However, when only doing pairwise matching, errors can accumulate between the images. Our goal is to take a set of pairwise matches and to correct the accumulated pairwise matches.

\subsection{Multi-Image Matching}
In this section we first describe the multi-image matching problem and cycle consistency.
We are given a set of $n$ images $\mathcal{I} = \left\{ I_1, I_2, \ldots, I_n \right\}$.
Associated with each image $I_i$ is a set of $m_i$ features $\mat{Z}_i = \left\{ z_{i1}, z_{i2}, z_{i3}, \ldots, z_{i m_i} \right\}$.
Each feature corresponding to interesting points in the scene from the vantage point of that image.
We also assume that some pairwise matching algorithm has given us a set of matches between the images, represented as a partial permutation matrix, $\mat{M}_{ij} \in \bR^{m_i \times m_j}$, where $(\mat{M}_{ij})_{kl} = 1$ if the features match, and 0 otherwise.
Naturally, the matches are symmetric so $\mat{M}_{ij} = \mat{M}_{ji}$.
As is typical in the multi-image matching problem, we do not assume anything about how these pairwise matches were computed.

However, as the $\mat{M}_{ij}$ are computed pairwise, no global concistency is guaranteed among them if there are errors. 
Thus we need a way to determine the global consistency of these matches.
This is where cycle consitency comes in.

\subsection{Cycle Consistency}
If the pairwise matches are globally consistent, then we can say that, for all $i, j, k$:
\begin{equation}
\mat{M}_{ij} = \mat{M}_{ik} \mat{M}_{kj}
\label{eq:cycconsist1}
\end{equation}
In other words, the matches between two images stays the same no matter what path is taken to get there. 
This constraint is known as \textit{cycle concistency}, and has been used in a number of recent works to optimze for global consistency \cite{zhou2015multi, wang2017multi, leonardos2016distributed}.
Stated in this form, there are $O(n^3)$ cycle consistency constraints to check.
A more elegant way to represent cycle consistency is to first create a `universe' of features that all images match to.
Then one can match each set of features $X_i$ to the universe, denoted $\mat{X}_i$.
Then the cycle consistency becomes:
\begin{equation}
\mat{M}_{ij} = \mat{X}_{i}\mat{X}_{j}^\top
\label{eq:cycconsist2}
\end{equation}
This can be more concisely described using the match matrices $\mat{M}$ and $\mat{X}$:
\begin{equation}
\mat{M} = \begin{pmatrix}
\mat{M}_{11} & \mat{M}_{12} & \hdots & \mat{M}_{1n} \\
\mat{M}_{21} & \mat{M}_{22} & \hdots & \mat{M}_{2n} \\
   \vdots    &     \vdots   & \ddots &    \vdots    \\
\mat{M}_{n1} & \mat{M}_{n2} & \hdots & \mat{M}_{nn}
\end{pmatrix}, \;
\mat{X} = \begin{pmatrix}
\mat{X}_{1}  \\
\mat{X}_{2}  \\
   \vdots     \\
\mat{X}_{n} 
\end{pmatrix}
\label{eq:matchmat}
\end{equation}
Now we define cycle consistency as:
\begin{equation}
\mat{M} = \mat{X} \mat{X}^\top
\label{eq:cycconsist3}
\end{equation}
In practice of course, $M$ has errors, and in fact the $\mat{M}_{ij}$ are typically not given as permutations but as matrices of similarity scores.
We denote this noisy version of the matches $\widetilde{\mat{M}}$.
Thus we can treat this as a low rank factorization problem on $\widetilde{\mat{M}}$, with permutation (or soft permutation) constraints on $\mat{X}$, as done in \cite{zhou2015multi, leonardos2016distributed, pachauri2013solving}:
\begin{align}
\argmin_{\mat{X}} \mathcal{L}(\mat{X})
=&\; \mathcal{D}\left(\widetilde{\mat{M}}, \mat{X}\mat{X}^\top\right) + \mathcal{R}(\mat{X}) \nonumber \\
\mathrm{s.t.} &\; \mat{X} \in \mathcal{X} \label{eq:genericloss}
\end{align}
Here $\mathcal{D}$ denotes some distance function and $\mathcal{R}$ denotes a regularizer on $\mat{X}$.

In previous work, the optimization is done directly.
Here we use learning to adapt to the statistics of the noise of the matching matrices.
Using Equation \ref{eq:genericloss} We have enough for a loss function to train a learning algorithm.
However, our input doesn't match typical image or sequence format most modern learning algorithms rely on.
Thus we need a different type of architecture to be able to perform learning on this task.

\subsection{Graph Neural Networks}
Now we show how to reformulate the problem in terms of graphs, and show how Graph Neural Networks can be applied to solve it.
To see how this is equivalent to a graph problem, we can simply view the $\widetilde{\mat{M}}$ as the adjacency matrix of a graph.
They cycle consistecy constraint is equivalent to there being $k$ disjoint subgraphs, with $k$ being the size of your `universe' of features. 
Ideally we would want to output a refined graph with the correct disjoint subgraphs corresponding to the ground truth features.
One could optimize for this, however, as we wish to use a learning algorithm, outputting a full graph would be difficult.
Instead we learn an embedding, equivalent to $\mat{X}$ in the previous section.

Graph Neural Networks (Graph NNs) have gotten more attention recently in the Machine Learning community \cite{bronstein2017geometric, bruna2013spectral, defferrard2016convolutional, kipf2016semi, scarselli2009graph, gama2018mimo, gama2018convolutional}.
Graph NNs have a long history and there are many varitions of it. 
However, we need one that can handle a different graphs as input and outputs an embedding on each node.
Here we follow the formulation from \cite{kipf2016semi} due to its simplicity, however there are many alternate architectures or formulations one could use in principle.
For this formulation, it is assumed we have some initial embedding on the graph $\mat{X}_0$ and some function of the adjacency matrix $A$ and degree matrix $D$, $L = (D+I)^{-1/2}(A+I)(D+I)^{-1/2}$.
The use of $L$ is more for convience, what is most important is that it is a function of the adjacency matrix.
Thus our update state is from the graph embedding on layer $l$ to layer $l + 1$:
\begin{equation*}
\mat{X}_{l+1} = \sigma\left( L X_l W_l \right)
\label{eq:gnnupdate}
\end{equation*}
This can be viewed as a linear combination of

%------------------------------------------------------------------------
\section{Experiments}

\begin{figure*}
\begin{center}
  % \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
  \includegraphics[width=0.8\linewidth]{figures/experiments01-eps-converted-to.pdf}
  \end{center}
     \caption{Example of a short caption, which should be centered.}
  \label{fig:short}
\end{figure*}

TODO
% \begin{table}
% \begin{center}
% \begin{tabular}{|l|c|}
% \hline
% Method & Frobnability \\
% \hline\hline
% Theirs & Frumpy \\
% Yours & Frobbly \\
% Ours & Makes one's heart Frob\\
% \hline
% \end{tabular}
% \end{center}
% \caption{Results.   Ours is better.}
% \end{table}

%------------------------------------------------------------------------
\section{Conclusion}

You must include your signed IEEE copyright release form when you submit
your finished paper. We MUST have this form before your paper can be
published in the proceedings.

Please direct any questions to the production editor in charge of these
proceedings at the IEEE Computer Society Press: Phone (714) 821-8380, or
Fax (714) 761-1784.

{\small
\bibliographystyle{ieee}
\bibliography{mybib}
}

\end{document}

### 2018-10-16 launch/download_files.py
Fixed up download_files a bit

@@ -13,9 +13,11 @@ def get_opts():
   parser = argparse.ArgumentParser(description='Train motion estimator')
   # Directory and dataset options
   parser.add_argument('--experiments',
+                      default=[],
                       nargs='+',
                       help='Experiments to test data to run analysis on')
   parser.add_argument('--exclude',
+                      default=[],
                       nargs='+',
                       help='Experiments to exclude')
 
@@ -63,7 +65,6 @@ opts = get_opts()
 print("Getting data...")
 losses = []
 log_names = get_log_names(opts)
-print(log_names)
 for n in range(len(opts.experiments)):
   yaml_name = opts.experiments[n]
   name = os.path.splitext(yaml_name)[0]

### 2018-10-21 train.py
Updated training to include L1 and L2 ground truth output

@@ -36,13 +36,16 @@ def get_loss(opts, sample, output, return_gt=False, name='loss'):
   tf.summary.image('Embedding Similarity', tf.expand_dims(sim, -1))
   loss = loss_fns[opts.loss_type](sim, output_sim)
   tf.summary.scalar(name, loss)
-  gt_loss = None
+  gt_l1_loss = None
+  gt_l2_loss = None
   if return_gt or opts.full_tensorboard:
-    gt_loss = loss_fns[opts.loss_type](sim_true, output_sim, add_loss=False)
+    gt_l1_loss = loss_fns['l1'](sim_true, output_sim, add_loss=False)
+    gt_l2_loss = loss_fns['l2'](sim_true, output_sim, add_loss=False)
   if opts.full_tensorboard and opts.use_unsupervised_loss:
-    tf.summary.scalar('GT L2 loss', gt_loss)
+    tf.summary.scalar('GT L1 loss', gt_l1_loss)
+    tf.summary.scalar('GT L2 loss', gt_l2_loss)
   if return_gt:
-    return loss, gt_loss
+    return loss, gt_l1_loss, gt_l2_loss
   else:
     return loss
 
@@ -141,13 +144,15 @@ def get_test_dict(opts, dataset, network):
   test_data['output'] = network(test_data['sample']['Laplacian'],
                                 test_data['sample']['InitEmbeddings'])
   if opts.use_unsupervised_loss:
-    test_loss, test_gt_loss = get_loss(opts,
+    test_loss, test_gt_l1_loss, test_gt_l2_loss = \
+                        get_loss(opts,
                                  test_data['sample'],
                                  test_data['output'],
                                  return_gt=True,
                                  name='test_loss')
     test_data['loss'] = test_loss
-    test_data['loss_gt'] = test_gt_loss
+    test_data['loss_gt_l1'] = test_gt_l1_loss
+    test_data['loss_gt_l2'] = test_gt_l2_loss
   else:
     test_data['loss'] = get_loss(opts,
                                  test_data['sample'],
@@ -158,32 +163,40 @@ def get_test_dict(opts, dataset, network):
   return test_data
 
 def run_test(opts, sess, test_data, verbose=True):
+  # TODO: Seriously we need to find a more elegant way of doing this...
   npsave = {}
   teststr = " ------------------- "
+  teststr += " Test loss = {:.4e} "
[…]

### 2018-10-21 journal/main.tex

@@
 
+\entry{2018}{10}{08}
+\subsubsection*{Rome16K Unsupervised Experiments}
+
+\begin{figure}[H]
+  \includegraphics[width=0.9\textwidth]{figures/rome16kknn0-loss-l2-unsup-true}
+  \label{fig:rome16kknn0-loss-l2-unsup-true-sub1}
+  \caption{Sample embedding, similarity matrix, histogram, and loss curves for best performing of this set}
+\end{figure}
+\begin{figure}[H]
+  \includegraphics[width=0.9\textwidth]{figures/rome16kknn0-loss-l2-unsup-false}
+  \label{fig:rome16kknn0-loss-l2-unsup-false-sub1}
+  \caption{Sample embedding, similarity matrix, histogram, and loss curves for worst performing of this set}
+\end{figure}
+\begin{figure}[H]
+  \includegraphics[width=0.9\textwidth]{figures/rome16kknn0-loss-l1-unsup-true}
+  \label{fig:rome16kknn0-loss-l1-unsup-true-sub1}
+  \caption{Sample embedding, similarity matrix, histogram, and loss curves for random experiment of this set}
+\end{figure}
+\begin{table}[H]
+  \caption{Numerical results}
+      \begin{tabular}{|l|c|c|c|} \hline
+                                      &  Same Point Similarities  &  Different Point Similarities  \\ \hline
+Baseline   & 8.83e-01 $\pm$ 1.26e-01 & 4.67e-01 $\pm$ 1.32e-01 \\ \hline
+Data type \texttt{rome16kknn0}, Loss L1, Supervised   & 5.62e-01 $\pm$ 4.12e-01 & 4.63e-02 $\pm$ 1.31e-01 \\ \hline
+Data type \texttt{rome16kknn0}, Loss L1, Unsupervised   & 6.89e-01 $\pm$ 3.50e-01 & 5.79e-02 $\pm$ 1.62e-01 \\ \hline
+Data type \texttt{rome16kknn0}, Loss L2, Supervised   & 7.84e-01 $\pm$ 2.54e-01 & 3.16e-01 $\pm$ 2.74e-01 \\ \hline
+Data type \texttt{rome16kknn0}, Loss L2, Unsupervised   & 7.21e-01 $\pm$ 2.88e-01 & 1.09e-01 $\pm$ 1.45e-01 \\ \hline
+      \end{tabular}
+      \label{fig:tab1}
+\end{table}
+
 \end{document}

### 2018-10-22 options.py
Added new loss and cleaned up loss code

@@ -34,7 +34,7 @@ arch_choices = [
 ]
 
 activation_types = ['relu','leakyrelu','tanh', 'elu']
-loss_types = [ 'l2', 'bce', 'l1' ]
+loss_types = [ 'l2', 'bce', 'l1', 'l1l2' ]
 optimizer_types = ['sgd','adam','adadelta','momentum','adamw']
 lr_decay_types = ['exponential','fixed','polynomial']
 

### 2018-10-22 tfutils.py

@@ -33,16 +33,27 @@ def create_bias_initializer(unused_in, unused_out, dtype=tf.float32):
 def bce_loss(labels, logits, add_loss=True):
   bce_elements = tf.nn.sigmoid_cross_entropy_with_logits(labels=labels, logits=logits)
   bce_ = tf.reduce_sum(bce_elements)
-  tf.losses.add_loss(bce_)
+  if add_loss:
+    tf.losses.add_loss(bce_)
   return bce_
 
 def l1_loss(x, y, add_loss=True):
   l1_ = tf.reduce_mean(tf.abs(x - y))
-  tf.losses.add_loss(l1_)
+  if add_loss:
+    tf.losses.add_loss(l1_)
   return l1_
 
 def l2_loss(x, y, add_loss=True):
   l2_ = tf.reduce_mean(tf.square(x - y))
-  tf.losses.add_loss(l2_)
+  if add_loss:
+    tf.losses.add_loss(l2_)
   return l2_
+
+def l1_l2_loss(x, y, add_loss=True):
+  l1_ = tf.reduce_mean(tf.abs(x - y))
+  l2_ = tf.reduce_mean(tf.square(x - y))
+  l1l2_ = l1_ + l2_
+  if add_loss:
+    tf.losses.add_loss(l1l2_)
+  return l1l2_
 

### 2018-10-22 train.py

@@ -19,6 +19,7 @@ loss_fns = {
   'bce': tfutils.bce_loss,
   'l1': tfutils.l1_loss,
   'l2': tfutils.l2_loss,
+  'l1l2': tfutils.l2_loss,
 }
 
 def get_loss(opts, sample, output, return_gt=False, name='loss'):
@@ -36,15 +37,12 @@ def get_loss(opts, sample, output, return_gt=False, name='loss'):
   tf.summary.image('Embedding Similarity', tf.expand_dims(sim, -1))
   loss = loss_fns[opts.loss_type](sim, output_sim)
   tf.summary.scalar(name, loss)
-  gt_l1_loss = None
-  gt_l2_loss = None
-  if return_gt or opts.full_tensorboard:
+  if return_gt:
     gt_l1_loss = loss_fns['l1'](sim_true, output_sim, add_loss=False)
     gt_l2_loss = loss_fns['l2'](sim_true, output_sim, add_loss=False)
-  if opts.full_tensorboard and opts.use_unsupervised_loss:
-    tf.summary.scalar('GT L1 loss', gt_l1_loss)
-    tf.summary.scalar('GT L2 loss', gt_l2_loss)
-  if return_gt:
+    if opts.full_tensorboard and opts.use_unsupervised_loss:
+      tf.summary.scalar('GT L1 loss', gt_l1_loss)
+      tf.summary.scalar('GT L2 loss', gt_l2_loss)
     return loss, gt_l1_loss, gt_l2_loss
   else:
     return loss
@@ -163,56 +161,30 @@ def get_test_dict(opts, dataset, network):
   return test_data
 
 def run_test(opts, sess, test_data, verbose=True):
-  # TODO: Seriously we need to find a more elegant way of doing this...
+  # Setup
   npsave = {}
   teststr = " ------------------- "
   teststr += " Test loss = {:.4e} "
+  npsave_keys = [ 'output', 'input', 'adjmat', 'gt' ]
+  test_data_vals = [ test_data['output'], test_data['sample']['InitEmbeddings'], 
+                     test_data['sample']['AdjMat'], test_data['sample']['TrueEmbedding'] ]
+  test_vals = [ test_data['loss'] ]
   start_time = time.time()
   if opts.use_unsupervised_loss:
     teststr += ", GT L1 Loss = {:4e} , GT L2 Loss  = {:4e} "
-    summed_loss, \
-    summed_loss_gt_l1, \
[…]

### 2018-11-01 options.py
Added end_bias to options

@@ -99,7 +99,11 @@ def get_opts():
   parser.add_argument('--loss_type',
                       default=loss_types[0],
                       choices=loss_types,
-                      help='')
+                      help='Loss function to use for training')
+  parser.add_argument('--use_end_bias',
+                      default=False,
+                      type=myutils.str2bool,
+                      help='NOT IMPLEMENTED YET: Use bias in dot product')
   parser.add_argument('--weight_decay',
                       default=4e-5,
                       type=float,

### 2018-11-01 train.py

@@ -28,9 +28,27 @@ def log(string):
   log_file.write(string)
   log_file.write('\n')
 
+# TODO: Make this not a hack
+# HACK!!
+end_bias_global = None
+def get_end_bias():
+  global end_bias_global
+  if end_bias_global is None:
+    with tf.variable_scope("end_variables", reuse=tf.AUTO_REUSE):
+      end_bias_global = tf.get_variable('end_bias', 
+                                        initializer=tf.zeros((1,),
+                                        dtype=tf.float32))
+    if end_bias_global not in tf.get_collection('biases'):
+      tf.add_to_collection('biases', end_bias_global)
+  return end_bias_global
+# END HACK!!
+
 def get_loss(opts, sample, output, return_gt=False, name='loss'):
   emb = sample['TrueEmbedding']
   output_sim = tfutils.get_sim(output)
+  if opts.use_end_bias:
+    end_bias = get_end_bias()
+    output_sim = output_sim + end_bias
   sim_true = tfutils.get_sim(emb)
   if opts.use_unsupervised_loss:
     v = opts.dataset_params.views[-1]
@@ -44,8 +62,11 @@ def get_loss(opts, sample, output, return_gt=False, name='loss'):
   loss = loss_fns[opts.loss_type](sim, output_sim)
   tf.summary.scalar(name, loss)
   if return_gt:
-    gt_l1_loss = loss_fns['l1'](sim_true, output_sim, add_loss=False)
-    gt_l2_loss = loss_fns['l2'](sim_true, output_sim, add_loss=False)
+    output_sim_gt = output_sim
+    if opts.loss_type == 'bce':
+      output_sim_gt = tf.sigmoid(output_sim)
+    gt_l1_loss = loss_fns['l1'](sim_true, output_sim_gt, add_loss=False)
+    gt_l2_loss = loss_fns['l2'](sim_true, output_sim_gt, add_loss=False)
     if opts.full_tensorboard and opts.use_unsupervised_loss:
       tf.summary.scalar('GT L1 loss', gt_l1_loss)
       tf.summary.scalar('GT L2 loss', gt_l2_loss)
@@ -181,6 +202,10 @@ def run_test(opts, sess, test_data, verbose=True):
   npsave_keys = [ 'output', 'input', 'adjmat', 'gt' ]
   test_data_vals = [ test_data['output'], test_data['sample']['InitEmbeddings'], 
[…]

### 2018-11-01 cvpr2019/main.tex
Added a bit more to the tex file

@@
 \usepackage{amssymb}
-
 % Include other packages here, before hyperref.
@@
 %% Custom control sequences
+\let\oldPr\Pr
 \newcommand{\bR}{\mathbb{R}}
+\renewcommand*{\Pr}[1]{\mathbb{P}\left( #1 \right)}
 \newcommand{\mat}[1]{\mathbf{#1}}
@@
 %%%%%%%%% TITLE
-\title{Learning Multi-Image Matching using Cycle Consistency}
+\title{Learning Multiple View Feature Representations}
 
@@
    % OK I hate this start but we will work on it.
-   In this work we present a learning technique for refining multi-image matches in an unsupervised fashion.
+   (Work in progress) In this work we present a learning technique for refining multi-image matches in an unsupervised fashion.
    We formulate the multi-image matching problem as a graph embedding problem then use recent work in Graph Neural Networks to learn the appropriate embedding function.
@@
 
-% Insert Introduction here
-TODO
+% TODO: Add more citations
+Feature matching is an essential part of many geometric computer vision applications.
+Much work has been done on image matching for the last several decades \cite{fischler1981random}.
+However we still have not fully answered the question: What are the best features of an image to capture multiple views of the same scene?
+Recently deep learning has revolutionized how image features are computed \cite{yi2016lift}, and we would like to leverage this to compute better scene features.
+Typically when applied to this area, deep neural networks (DNNs) are trained with photometric losses.
+Photometric losses make the brightness constancy assumption - can we learn using multi-view constraints directly?
+
+Unfortunately there are obstacles to applying multi-view constraints directly to learning. 
+To train networks, we need a large amount of labelled data.
+In the case of multi-image feature matching, one would need to hand label point correspondences between images, which is difficult and expensive to obtain.
+Mutli-view constraints are formulated in terms of sparse features, thus traditional convolutional deep neural nets (CNNs) are not designed to handle such input.
+
+In this work we propose to solve these problems using a Graph Neural Network (GNN) to operate on the correspondence graph, agnostic to the method used to compute the correspondence graph.
+We use an self-supervised loss, the cycle consistency loss, to train the network.
+We also add in side geometric losses used to help training, where the geometric information is not available at train time.
+Our contributions our:
+\begin{itemize}
+\item A novel architecture for feature multi-image feature matching using GNNs with graph embeddings
+\item Using the self-supervised cycle consistency loss
+\item Test geometric consistency losses toward the training
+\item Perform experiments on the Rome16K dataset to test the effectiveness of our baseline
+\end{itemize}
 
@@
 \section{Method}
-Our goal is to find correspondences between multiple (more than two) images.
-There are many techniques for finding such matchins in a pairwise setting, such as graph matching \cite{suh2015subgraph, hu2016distributable} or even learning techniques \cite{yi2018learning}.
-However, when only doing pairwise matching, errors can accumulate between the images.
-Our goal is to take a set of pairwise matches and to correct the accumulated pairwise matches.
+Our goal is to learn optimal features that capture multiple image views.
+We assume we have an initial set of features matches, represented as a graph, $\mathcal{G} = (\mathcal{V}, \mathcal{E})$.
+Each vertex $v$ of the graph is a feature, with its assocated descriptor $f_v$. 
+The graph is represented by its Weighted Adjacency Matrix $A(\mathcal{G}) \in \bR^{n \times n}$, and its degree matrix $D(\mathcal{G}) \in \bR^{n \times n}$ (positive diagonal).
+Combined the features $f_v$ from each of the vertices we can get an embedding matrix $E_0$.
+We can also add other knowledge we will have at test time.
+Putative correspondences are computed from these, and represented by weighted edges, the weight giving the strength of the match.
+While there are many interesting methods for computing these putative correspondences, we do not explore them in this work.
+The graph structure does not have the properties of a Eulcidean domain (such as an image) we cannot use standard CNNs to learn features for this task.
+Thus we need to use graph convolutions to learn feature representations on this space.
 
-\subsection{Multi-Image Matching}
-In this section we first describe the multi-image matching problem and cycle consistency.
-We are given a set of $n$ images $\mathcal{I} = \left\{ I_1, I_2, \ldots, I_n \right\}$.
-Associated with each image $I_i$ is a set of $m_i$ features $\mat{Z}_i = \left\{ z_{i1}, z_{i2}, z_{i3}, \ldots, z_{i m_i} \right\}$.
-Each feature corresponding to interesting points in the scene from the vantage point of that image.
-We also assume that some pairwise matching algorithm has given us a set of matches between the images, represented as a partial permutation matrix, $\mat{M}_{ij} \in \bR^{m_i \times m_j}$, where $(\mat{M}_{ij})_{kl} = 1$ if the features match, and 0 otherwise.
-Naturally, the matches are symmetric so $\mat{M}_{ij} = \mat{M}_{ji}$.
-As is typical in the multi-image matching problem, we do not assume anything about how these pairwise matches were computed.
-
-However, as the $\mat{M}_{ij}$ are computed pairwise, no global concistency is guaranteed among them if there are errors. 
-Thus we need a way to determine the global consistency of these matches.
-This is where cycle consitency comes in.
+\subsection{Graph Neural Networks}
+Much attention has been given to graph neural networks (GNNs) recently
+\cite{bronstein2017geometric, bruna2013spectral, defferrard2016convolutional, kipf2016semi, scarselli2009graph, gama2018mimo, gama2018convolutional}.
+For our purpose we will need a method that can handle different graph structures as input, thus we cannot resort to spectral graph convolution methods.
+Since our goal is to describe correspondence of each of the nodes, we also cannot use pooling of the nodes.
+\begin{align}
+      L =&\; (D + I)^{-1/2} (A + I) (D + I)^{-1/2} \\
+E_{k+1} =&\; \sigma\left(L E_k W_k \right)
+\end{align}
+Here $\sigma$ is the non-linearity (typically a $relu$), and $W_k$ are the learned weights. 
+The matrix $L$ is analogous to the graph Laplacian, and is used to encode the structure of the graph.
+It is with $L$ that the graph convolution is performed.
+However, this is limited to convolutions over a one-hop neighborhood of a node.
+For simplicity we restrict ourselves to this for now, though in principle we could use higher hop neighborhoods \cite{gama2018convolutional}.
+To train this we use a cycle consistency.
 
@@
 \end{equation}
-This can be more concisely described using the match matrices $\mat{M}$ and $\mat{X}$:
+
+In the case, we try to learn embeddings that map to the $\mat{X}_i$ - learn the universe of features via our embeddings.
+Thus our loss would be 
 \begin{equation}
-\mat{M} = \begin{pmatrix}
-\mat{M}_{11} & \mat{M}_{12} & \hdots & \mat{M}_{1n} \\
-\mat{M}_{21} & \mat{M}_{22} & \hdots & \mat{M}_{2n} \\
-   \vdots    &     \vdots   & \ddots &    \vdots    \\
-\mat{M}_{n1} & \mat{M}_{n2} & \hdots & \mat{M}_{nn}
-\end{pmatrix}, \;
-\mat{X} = \begin{pmatrix}
-\mat{X}_{1}  \\
-\mat{X}_{2}  \\
-   \vdots     \\
-\mat{X}_{n} 
-\end{pmatrix}
-\label{eq:matchmat}
+\mathcal{L}(A, E_n) = \mathcal{D}(A, E_nE_n^\top)
 \end{equation}
-Now we define cycle consistency as:
-\begin{equation}
-\mat{M} = \mat{X} \mat{X}^\top
-\label{eq:cycconsist3}
-\end{equation}
-In practice of course, $M$ has errors, and in fact the $\mat{M}_{ij}$ are typically not given as permutations but as matrices of similarity scores.
-We denote this noisy version of the matches $\widetilde{\mat{M}}$.
-Thus we can treat this as a low rank factorization problem on $\widetilde{\mat{M}}$, with permutation (or soft permutation) constraints on $\mat{X}$, as done in \cite{zhou2015multi, leonardos2016distributed, pachauri2013solving}:
-\begin{align}
-\argmin_{\mat{X}} \mathcal{L}(\mat{X})
-=&\; \mathcal{D}\left(\widetilde{\mat{M}}, \mat{X}\mat{X}^\top\right) + \mathcal{R}(\mat{X}) \nonumber \\
-\mathrm{s.t.} &\; \mat{X} \in \mathcal{X} \label{eq:genericloss}
-\end{align}
-Here $\mathcal{D}$ denotes some distance function and $\mathcal{R}$ denotes a regularizer on $\mat{X}$.
-
-In previous work, the optimization is done directly.
-Here we use learning to adapt to the statistics of the noise of the matching matrices.
-Using Equation \ref{eq:genericloss} We have enough for a loss function to train a learning algorithm.
-However, our input doesn't match typical image or sequence format most modern learning algorithms rely on.
-Thus we need a different type of architecture to be able to perform learning on this task.
-
-\subsection{Graph Neural Networks}
-Now we show how to reformulate the problem in terms of graphs, and show how Graph Neural Networks can be applied to solve it.
-To see how this is equivalent to a graph problem, we can simply view the $\widetilde{\mat{M}}$ as the adjacency matrix of a graph.
-They cycle consistecy constraint is equivalent to there being $k$ disjoint subgraphs, with $k$ being the size of your `universe' of features. 
-Ideally we would want to output a refined graph with the correct disjoint subgraphs corresponding to the ground truth features.
-One could optimize for this, however, as we wish to use a learning algorithm, outputting a full graph would be difficult.
-Instead we learn an embedding, equivalent to $\mat{X}$ in the previous section.
-
-Graph Neural Networks (Graph NNs) have gotten more attention recently in the Machine Learning community \cite{bronstein2017geometric, bruna2013spectral, defferrard2016convolutional, kipf2016semi, scarselli2009graph, gama2018mimo, gama2018convolutional}.
-Graph NNs have a long history and there are many varitions of it. 
-However, we need one that can handle a different graphs as input and outputs an embedding on each node.
-Here we follow the formulation from \cite{kipf2016semi} due to its simplicity, however there are many alternate architectures or formulations one could use in principle.
-For this formulation, it is assumed we have some initial embedding on the graph $\mat{X}_0$ and some function of the adjacency matrix $A$ and degree matrix $D$, $L = (D+I)^{-1/2}(A+I)(D+I)^{-1/2}$.
-The use of $L$ is more for convience, what is most important is that it is a function of the adjacency matrix.
-Thus our update state is from the graph embedding on layer $l$ to layer $l + 1$:
-\begin{equation*}
-\mat{X}_{l+1} = \sigma\left( L X_l W_l \right)
-\label{eq:gnnupdate}
-\end{equation*}
-This can be viewed as a linear combination of
+Here $\mathcal{D}$ could be an $L_2$ loss, $L_1$ loss, or many others. 
+This essential models that features $i$ and $j$ match with probability $(E_n)_i \cdot (E_n)_j$
+which is proporitional to $A_{ij}$ with some noise.
 
@@
 
-TODO
-% \begin{table}
-% \begin{center}
-% \begin{tabular}{|l|c|}
-% \hline
-% Method & Frobnability \\
-% \hline\hline
-% Theirs & Frumpy \\
-% Yours & Frobbly \\
-% Ours & Makes one's heart Frob\\
-% \hline
-% \end{tabular}
-% \end{center}
-% \caption{Results.   Ours is better.}
-% \end{table}
+\subsection{Rome 16K Graph Dataset}
+% Filler for now.
+% TODO: Actually run tests on all these with different loss functions
+We extract image triplets, quadtruplets, and quintuplets with overlap of 80 points or more to test our algorithm on.
+For the normal datasets, we extracted 80 points established as corresponding in the bundle adjument given in the Rome16K dataset.
+For the outlier datasets, we take 79 correspondences and 1 non-corresponding point in each image.
+
+We test with various loss functions, including ablation studies on various geometric loss functions.
+
+% leaderConsensus.m  MatchALSTestErrors.txt  mmatch_CVX_ALS.m  mmatch_QP_PG.m  mmatch_spectral.m  PGDDS.m  PGDDSTestErrors.txt  print_errors.py  run_tests.m  SpectralTestErrors.txt
+\begin{table*}
+\begin{center}
+\begin{tabular}{|l|c|c|c|}
+\hline
+Method & L1 Loss & L2 Loss & BCE Loss \\
+\hline\hline\hline
+Spectral                                  & 1.000e-3 & 1.000e-3 & 1.000e-3 \\ \hline
+MatchALS                                  & 1.000e-3 & 1.000e-3 & 1.000e-3 \\ \hline
+PGDDS                                     & 1.000e-3 & 1.000e-3 & 1.000e-3 \\ \hline
+GNN, 12 Layers, w/o Geometric Side Losses & 1.000e-3 & 1.000e-3 & 1.000e-3 \\ \hline
+GNN, 12 Layers, w/ Geometric Side Losses  & 1.000e-3 & 1.000e-3 & 1.000e-3 \\ \hline
+
+\hline
+\end{tabular}
+\end{center}
+\caption{
+Results on Rome16k Correspondence graphs.
+Losses tested against ground truth correspondence graph adjacency matrices.
+Our method was not trained on ground truth corresopndences but on unsupervised methods.
+}
+\end{table*}
 
@@
 
-You must include your signed IEEE copyright release form when you submit
-your finished paper. We MUST have this form before your paper can be
-published in the proceedings.
-
-Please direct any questions to the production editor in charge of these
-proceedings at the IEEE Computer Society Press: Phone (714) 821-8380, or
-Fax (714) 761-1784.
+We have shown a novel method for training feature matching.
 

### 2018-11-01 latex_report.py
Added option to just view for latex plot generation

@@ -28,6 +28,10 @@ def get_latex_opts():
                       default=False,
                       type=str2bool,
                       help='Print everything or not')
+  parser.add_argument('--just_view',
+                      default=False,
+                      type=str2bool,
+                      help='Just view, do not save')
   parser.add_argument('--index',
                       default=0,
                       type=int,
@@ -298,6 +302,7 @@ class LatexGenerator(object):
     self.index = opts.index
     self.viewer_size = opts.viewer_size
     self.verbose = opts.verbose
+    self.just_view = opts.just_view
     for exp_ in tqdm.tqdm(opts.experiments, disable=not self.verbose):
       self.experiments.append(Experiment(exp_, verbose=opts.verbose))
 
@@ -309,7 +314,11 @@ class LatexGenerator(object):
     latex_string += "\\end{{figure}}\n"
     fname = os.path.join(self.save_dir, exp.get_plot_name())
     fig = exp.generate_plot(self.viewer_size, index)
-    fig.savefig(os.path.join(self.top_dir, fname))
+    if self.just_view:
+      print(exp.get_plot_name())
+      plt.show()
+    else:
+      fig.savefig(os.path.join(self.top_dir, fname))
     # plt.show()
     return latex_string.format(fname[:-4], exp.get_latex_name(), caption)
 

### 2018-11-03 data_util/real_dataset.py
Added geometric entities into real_dataset -- needs checking!

@@ -14,29 +14,30 @@ from data_util import parent_dataset
 from data_util import tf_helpers
 from data_util.rome16k import parse
 
-class Rome16KTripletDataset(parent_dataset.GraphSimDataset):
+class Rome16KTupleDataset(parent_dataset.GraphSimDataset):
   """Abstract base class for Rome16K cycle consistency graphs"""
 
-  def __init__(self, opts, params):
+  def __init__(self, opts, params, tuple_size=3):
     parent_dataset.GraphSimDataset.__init__(self, opts, params)
     self.rome16k_dir = opts.rome16k_dir
+    self.tuple_size = tuple_size
     del self.features['Mask']
     del self.features['MaskOffset']
     self.dataset_params.sizes['train'] = \
-        sum([x[0] for _, x in parse.bundle_file_info['train'].items()])
+        sum([x[tuple_size-1] for _, x in parse.bundle_file_info['train'].items()])
     self.dataset_params.sizes['test'] = \
-        sum([x[0] for _, x in parse.bundle_file_info['test'].items()])
+        sum([x[tuple_size-1] for _, x in parse.bundle_file_info['test'].items()])
 
   def gen_sample(self):
     print("ERROR: Cannot generate sample - need to load data")
     sys.exit(1)
 
-  def gen_sample_from_triplet(self, scene, triplet):
+  def gen_sample_from_tuple(self, scene, tupl):
     print("ERROR: Not implemented in abstract base class")
     sys.exit(1)
 
-  def triplet_fname(self, bundle_file):
-    return os.path.join(self.rome16k_dir, parse.triplets_name(bundle_file))
+  def tuple_fname(self, bundle_file):
+    return os.path.join(self.rome16k_dir, parse.tuples_name(bundle_file))
 
   def convert_dataset(self, out_dir, mode):
     """Writes synthetic flow data in .mat format to a TF record file."""
@@ -56,15 +57,15 @@ class Rome16KTripletDataset(parent_dataset.GraphSimDataset):
     for bundle_file in parse.bundle_file_info[mode]:
       scene_name = '{}/{}'.format(self.rome16k_dir, parse.scene_name(bundle_file))
       scene = parse.load_scene(scene_name)
-      with open(self.triplet_fname(bundle_file), 'rb') as f:
-        triplets = pickle.load(f)
[…]

### 2018-11-03 data_util/rome16k/__main__.py

@@ -40,7 +40,7 @@ def get_build_scene_opts():
   parser.add_argument('--verbose',
                       default=True,
                       type=myutils.str2bool,
-                      help='Maximum tuple size')
+                      help='Print out everything')
 
   opts = parser.parse_args()
   return opts

### 2018-11-03 data_util/rome16k/__main__.py
Added tuple and geometric information

@@ -14,10 +14,18 @@ import myutils
 def get_build_scene_opts():
   """Parse arguments from command line and get all options for training."""
   parser = argparse.ArgumentParser(description='Train motion estimator')
-  parser.add_argument('--build_ktuples',
+  parser.add_argument('--build_tuples',
                       type=myutils.str2bool,
                       default=True,
                       help='Name of pickle file to load - None if no loading')
+  parser.add_argument('--save_imsizes',
+                      type=myutils.str2bool,
+                      default=True,
+                      help='Save files of images, which requires internet connectivity')
+  parser.add_argument('--overwrite_tuples',
+                      type=myutils.str2bool,
+                      default=False,
+                      help='If tuple file exists, overwrite it')
   parser.add_argument('--top_dir',
                       default='/NAS/data/stephen/Rome16K',
                       help='Storage location for pickle files')
@@ -33,14 +41,14 @@ def get_build_scene_opts():
                       default=150,
                       type=int,
                       help='Minimum overlap of points for connection')
-  parser.add_argument('--max_k',
+  parser.add_argument('--max_tuple_size',
                       default=4,
                       type=int,
                       help='Maximum tuple size')
   parser.add_argument('--verbose',
-                      default=True,
-                      type=myutils.str2bool,
-                      help='Maximum tuple size')
+                      default=1,
+                      type=int,
+                      help='How much progress to print out')
 
   opts = parser.parse_args()
   return opts
@@ -58,64 +66,65 @@ def choose(n, k):
 def silent(x):
   pass
 
-def process_scene_bundle(opts, bundle_file, verbose=False):
-  if verbose:
+def process_scene_bundle(opts, bundle_file, scene_fname, tuples_fname):
+  if opts.verbose > 0:
     myprint = lambda x: print(x)
   else:
     myprint = lambda x: silent(x)
   ######### Build and save out scene file ###########
[…]

### 2018-11-03 data_util/rome16k/parse.py

@@ -1,12 +1,14 @@
 import numpy as np 
 import os
 import sys
-import argparse
-import matplotlib.pyplot as plt
-from mpl_toolkits.mplot3d import Axes3D
 import gzip
 import pickle
-import yaml
+import tqdm
+
+import requests
+from PIL import Image
+import html.parser
+import io
 
 from data_util.rome16k import scenes
 
@@ -15,70 +17,99 @@ from data_util.rome16k import scenes
 #   -> dict: rome16k_name -> (ntriplets, ncams)
 bundle_file_info = {
   'train' : {
-    '5.1.0.0': (507, 44),
-    '20.0.0.0': (566, 48),
-    '55.0.0.0': (644, 58),
-    '38.0.0.0': (663, 70),
-    '26.1.0.0': (744, 86),
-    '74.0.0.0': (1050, 33),
-    '49.0.0.0': (1053, 37),
-    '36.0.0.0': (1204, 34),
-    '12.0.0.0': (1511, 63),
-    '60.0.0.0': (2057, 47),
-    '54.0.0.0': (2068, 60),
-    '57.0.0.0': (2094, 40),
-    '167.0.0.0': (2119, 42),
-    '4.11.0.0': (2714, 115),
-    '38.3.0.0': (3248, 39),
-    '135.0.0.0': (3476, 46),
-    '4.8.0.0': (3980, 63),
-    '110.0.0.0': (4075, 86),
-    '4.3.0.0': (4442, 81),
-    '29.0.0.0': (4849, 50),
-    '97.0.0.0': (4967, 87),
-    '4.6.0.0': (5409, 99),
-    '84.0.0.0': (5965, 59),
-    '9.1.0.0': (6536, 58),
-    '33.0.0.0': (6698, 125),
-    '15.0.0.0': (9950, 59),
-    '26.5.0.0': (12913, 54),
-    '122.0.0.0': (15269, 93),
-    '10.0.0.0': (16709, 101),
-    '11.0.0.0': (16871, 262),
-    '0.0.0.0': (22632, 186),
-    '17.0.0.0': (28333, 117),
-    '16.0.0.0': (35180, 93),
-    '4.1.0.0': (36460, 163),
+    '5.1.0.0': (507,),
+    '20.0.0.0': (566,),
+    '55.0.0.0': (644,),
+    '38.0.0.0': (663,),
+    '26.1.0.0': (744,),
[…]

### 2018-11-03 data_util/rome16k/scenes.py

@@ -33,24 +33,30 @@ class Feature(Saver):
 
 class Camera(Saver):
   def __init__(self, id_num, values=None):
-    Saver.__init__(self, ['rot', 'trans', 'focal', 'features' ], id_num, values)
-    if self.rot == None:
+    Saver.__init__(self, ['rot','trans','focal','k1','k2','imsize','features'], id_num, values)
+    if self.rot is None:
       self.rot = np.eye(3)
     else:
       self.rot = np.array(self.rot)
-    if self.trans == None:
+    if self.trans is None:
       self.trans = np.zeros(3)
     else:
       self.trans = np.array(self.trans)
+    if self.k1 is None:
+      self.k1 = 0
+    if self.k2 is None:
+      self.k2 = 0
+    if self.imsize is None:
+      self.imsize = (-1,-1)
 
 class Point(Saver):
   def __init__(self, id_num, values=None):
     Saver.__init__(self, [ 'pos', 'color', 'features' ], id_num, values)
-    if self.pos == None:
+    if self.pos is None:
       self.pos = np.zeros(3)
     else:
       self.pos = np.array(self.pos)
-    if self.color == None:
+    if self.color is None:
       self.color = np.zeros(3, dtype='int32')
     else:
       self.color = np.array(self.color)

### 2018-11-06 baselines/print_errors.py
Added BCE error to the baseline stats

@@ -2,6 +2,7 @@ import os
 import sys
 import numpy as np
 
+import matplotlib.pyplot as plt
 
 for fname in sys.argv[1:]:
   f = open(fname, 'r')
@@ -11,6 +12,7 @@ for fname in sys.argv[1:]:
   recall = []
   l1 = []
   l2 = []
+  bce = []
   for line in f:
     l = line.split(' ')
     ids.append(int(l[0]))
@@ -19,6 +21,7 @@ for fname in sys.argv[1:]:
     recall.append(float(l[7][:-1]))
     l1.append(float(l[9][:-1]))
     l2.append(float(l[12][:-1]))
+    bce.append(float(l[14][:-1]))
 
   f.close()
 
@@ -27,8 +30,14 @@ for fname in sys.argv[1:]:
   recall = np.array(recall)
   l1 = np.array(l1)
   l2 = np.array(l2)
+  bce = np.abs(np.array(bce))
+  plt.scatter(l1, l2)
+  plt.show()
+  plt.scatter(l2, bce)
+  plt.show()
 
   print(fname)
-  print("L1: {:.6e} +/- {:.6e}".format(l1.mean(), l1.std()))
-  print("L2: {:.6e} +/- {:.6e}".format(l2.mean(), l2.std()))
+  print("L1 : {:.6e} +/- {:.6e} (min: {:.6e}, max: {:.6e})".format(l1.mean(), l1.std(), l1.min(), l1.max()))
+  print("L2 : {:.6e} +/- {:.6e} (min: {:.6e}, max: {:.6e})".format(l2.mean(), l2.std(), l2.min(), l2.max()))
+  print("BCE: {:.6e} +/- {:.6e} (min: {:.6e}, max: {:.6e})".format(bce.mean(), bce.std(), bce.min(), bce.max()))
 

### 2018-11-06 baselines/run_tests.m

@@ -13,7 +13,7 @@ test_fns = { ...
 
 disp_string =  [ '%06d Errors: ' ...
                  'Overlap: %.03e, Precision: %.03e, Recall: %.03e, ' ...
-                 'L1: %.03e,  L2: %.03e\n' ];
+                 'L1: %.03e,  L2: %.03e, BCE: %.03e\n' ];
 
 for test_fn_index = 1:size(test_fns,1)
   test_fn = test_fns{test_fn_index,2};
@@ -25,9 +25,9 @@ for test_fn_index = 1:size(test_fns,1)
       W = squeeze(test_mats.AdjMat(index,:,:)) + eye(n);
       Xgt = squeeze(test_mats.TrueEmbedding(index,:,:));
       Agt = Xgt*Xgt';
-      Ah = test_fn(W);
-      [overlap, precision, recall, l1, l2] = testOutput_full(Ah,Agt,p);
-      fprintf(fid, disp_string, index, overlap, precision, recall, l1, l2);
+      Ah = max(0,min(1,test_fn(W)));
+      [overlap, precision, recall, l1, l2, bce] = testOutput_full(Ah,Agt,p);
+      fprintf(fid, disp_string, index, overlap, precision, recall, l1, l2, bce);
     end
   end
   fprintf('\n')
@@ -65,11 +65,12 @@ end
 %% test_mats = load(fname);
 %% 
 
-function [overlap, precision, recall, l1, l2] = testOutput_full(Ah,Agt,p)
+function [overlap, precision, recall, l1, l2, bce] = testOutput_full(Ah,Agt,p)
 
 [overlap, precision, recall] = evalMMatch(triu(Ah,1),triu(Agt,1),false);
-l1 = mean(mean(abs(Ah-Agt)));
-l2 = mean(mean((Ah-Agt).^2));
+l1  = mean2(abs(Ah-Agt));
+l2  = mean2((Ah-Agt).^2);
+bce = mean2(Agt.*log2(eps+Ah) + (1-Agt).*log2(eps+1-Ah));
 
 end
 

### 2018-11-06 cvpr2019/main.tex
Updated tex document

@@
 \DeclareMathOperator*{\argmin}{arg\,min}
+\newcommand{\tr}{\mathbf{tr}}
+\newcommand{\cross}[1]{[#1]_{\times}}
 
@@
 }
+
+% When placing figures in \LaTeX, it's almost always best to use
+% \verb+\includegraphics+, and to specify the  figure width as a multiple of
+% the line width as in the example below
+% {\small\begin{verbatim}
+%    \usepackage[dvips]{graphicx} ...
+%    \includegraphics[width=0.8\linewidth]
+%                    {myfile.eps}
+% \end{verbatim}
+% }
 
@@
 
+\begin{figure}[t]
+\begin{center}
+  % \fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
+  \includegraphics[width=0.8\linewidth]{figures/CycleConsistencyBasic.pdf}
+\end{center}
+  \caption{
+    Example of multi-image matching, with images from Rome16K dataset \cite{li2010location}.
+    Shown is an example of an error in matching leading to an inconsistency cycle.
+    In this work, we show how to learn this multi-view matching problem.
+  }
+\label{fig:cycconsistex}
+\label{fig:onecol}
+\end{figure}
+
 Unfortunately there are obstacles to applying multi-view constraints directly to learning. 
@@
 Mutli-view constraints are formulated in terms of sparse features, thus traditional convolutional deep neural nets (CNNs) are not designed to handle such input.
+In the case of multi-image feature matching, geometric constraints would be helpful in rejecting outlier matches.
 
-In this work we propose to solve these problems using a Graph Neural Network (GNN) to operate on the correspondence graph, agnostic to the method used to compute the correspondence graph.
+In this work we propose to solve these problems using a Graph Neural Network (GNN) to operate on the correspondence graph.
+The method proposed works the correspondence graph, agnostic to how correspondnces were computed.
 We use an self-supervised loss, the cycle consistency loss, to train the network.
@@
 \item Test geometric consistency losses toward the training
-\item Perform experiments on the Rome16K dataset to test the effectiveness of our baseline
+\item Perform experiments on the Rome16K \cite{li2010location} dataset to test the effectiveness of our method compared to the optimization based baselines
 \end{itemize}
-
-\begin{figure}[t]
-\begin{center}
-  \fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-  % \includegraphics[width=0.8\linewidth]{figures/experiments.eps}
-\end{center}
-   \caption{Example of caption.  It is set in Roman so that mathematics
-   (always set in Roman: $B \sin A = A \sin B$) may be included without an
-   ugly clash.}
-\label{fig:long}
-\label{fig:onecol}
-\end{figure}
 
@@
 
-TODO
+Matching has a rich history of research.
+The most well known and widely used method for image matching is that of RANSAC \cite{fischler1981random}.
+RANSAC combined with hand-crafted feature descriptors like SIFT \cite{lowe2004distinctive}, SURF \cite{bay2006surf}, BRIEF \cite{calonder2012brief}, or ORB \cite{mur2015orb} has constituted the bulk of the matching literature for the last 40 years.
+To improve matching of all the features of the image, graph matching \cite{suh2015subgraph, hu2016distributable}.
 
-% When placing figures in \LaTeX, it's almost always best to use
-% \verb+\includegraphics+, and to specify the  figure width as a multiple of
-% the line width as in the example below
-% {\small\begin{verbatim}
-%    \usepackage[dvips]{graphicx} ...
-%    \includegraphics[width=0.8\linewidth]
-%                    {myfile.eps}
-% \end{verbatim}
-% }
+Multi-image matching has traditionally been done using optimization based methods optimizing for cycle consistency (see Secion 3.3) such as \cite{pachauri2013solving,zhou2015multi,arrigoni2017synchronization} and \cite{wang2017multi}.
+\cite{pachauri2013solving} and \cite{arrigoni2017synchronization} use the eigenvectors of the matching matrix to obtain the the low dimensional embedding. 
+Thus they are robust to small Gaussian noise but not to stronger noise.
+\cite{zhou2015multi} and \cite{wang2017multi} use most sophisticated optimization techniques on the matching matrix and thus are quite robust.
+However, they use a centralized scheme and thus are not appropriate in a distributed setting,
+as done in \cite{leonardos2016distributed}.
+There are also density based optimization techniques to compute mutli-image correspondence, such as in \cite{tron2017fast}.
+
+Previous attempts to improve image matching techniques using machine learning have focused on learning the descriptors given ground truth correspondence from curated datasets \cite{zagoruyko2015learning, yi2016lift, brachmann2017dsac}.
+This approach is limited if you do not have the ability to get the ground truth correspondences.
+There are other methods to build correspondnces \cite{choy2016universal}, but it only handles two-view constraints and requires dense correspondeces.
+Most similar to ours, \cite{yi2018learning} attempts to improve correspondences by learning match probabilites for RANSAC to speed up test time running.
+However, they only focus on two view tests and do not exploit the advantages of the correspondence structure.
+
+Graph neural networks have been getting more attention recently 
+\cite{bronstein2017geometric, bruna2013spectral, defferrard2016convolutional, kipf2016semi, scarselli2009graph, gama2018mimo, gama2018convolutional, battaglia2018relational}.
+Classical so-called Spectral methods used the eigenvectors of graph Laplacian to compute convolutions \cite{bronstein2017geometric}, but this requires a fixed graph structure a-priori.  
+Non-spectral methods do not have this requirement \cite{bronstein2017geometric, kipf2016semi, scarselli2009graph, gama2018convolutional}.
+Most of these simply use polynomials of the graph Laplacian to compute neighborhood averages.
+\cite{gama2018mimo} formalizes this notion and generalizes it beyond the use of the graph Laplacian, as well as its follow up \cite{gama2018convolutional}.
+More sophisticated aggregation techniques and global information passing can also be used, as discussed in \cite{battaglia2018relational}.
 
 %------------------------------------------------------------------------
+\begin{figure*}[t]
+\begin{center}
+  % \fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
+  \includegraphics[width=0.8\linewidth]{figures/CycleConsistencyMainFigure.pdf}
+\end{center}
+  \caption{
+    An outline of the pipeline of this work.
+    The graph of matches is put to a Graph Convolutional Neural Network \cite{kipf2016semi} then creates a low rank embedding of the Adjacency Matrix of the graph.
+    The matrix reconstruction loss is used to train the network.
+    In addition we can use geometric information at to assist training the network, even if we do not have that geometric information at testing time.
+  }
+\label{fig:pipeline}
+\label{fig:onecol}
+\end{figure*}
+
 \section{Method}
 Our goal is to learn optimal features that capture multiple image views.
-We assume we have an initial set of features matches, represented as a graph, $\mathcal{G} = (\mathcal{V}, \mathcal{E})$.
+We formulate this problem in terms of the correspondece graph of the features.
+We denote vectors $\mat{x}$ and matrices $\mat{A}$ with boldface.
+We denote the $i^{th}$ row of a matrix $(\mat{A})_i$.
+\subsection{Correspondence Graph}
+We assume we have an initial set of features matches, represented as a graph $\mathcal{G} = (\mathcal{V}, \mathcal{E})$.
 Each vertex $v$ of the graph is a feature, with its assocated descriptor $f_v$. 
-The graph is represented by its Weighted Adjacency Matrix $A(\mathcal{G}) \in \bR^{n \times n}$, and its degree matrix $D(\mathcal{G}) \in \bR^{n \times n}$ (positive diagonal).
-Combined the features $f_v$ from each of the vertices we can get an embedding matrix $E_0$.
-We can also add other knowledge we will have at test time.
+The graph is represented by its Weighted Adjacency Matrix $\mat{A}(\mathcal{G}) \in \bR^{n \times n}$, and its degree matrix $\mat{D}(\mathcal{G}) \in \bR^{n \times n}$ (positive diagonal) (we drop the $\mathcal{G}$ for brevity).
+We can get an embedding matrix $E_0$ by combining the features $f_v$ from each of the vertices, which we use as our initializiation for our learning algorithm.
+We can also add any additional knowledge we have into the embedding (e.g. scale, orientation, etc.).
 Putative correspondences are computed from these, and represented by weighted edges, the weight giving the strength of the match.
-While there are many interesting methods for computing these putative correspondences, we do not explore them in this work.
-The graph structure does not have the properties of a Eulcidean domain (such as an image) we cannot use standard CNNs to learn features for this task.
-Thus we need to use graph convolutions to learn feature representations on this space.
+While there are many interesting methods for computing these putative correspondences \cite{suh2015subgraph, yi2018learning}, we do not explore them in this work.
+
+In the absence of noise or outliers, this graph would have $p$ connected components, where $p$ is the number of co-visible points in the world.
+Each feature would only have edges to other features corresponding to the same point.
+Also no points in the same image have edges between them, as if they corresponded to the same point, they would be the same feature.
+Typically putative correspondences match probabilistically, meaning a feature in one image matches to many features in another.
+This could come from repeated features in the world, the inherant ambiguous low level, local feature matching, or just an error in the matching algorithm.
+Filtering out these noisy matches is our primary learning goal.
+
+However, this graph structure does not have the properties of a Eulcidean domain (such as an image).
+Thus we cannot use standard CNNs to learn features for this task.
+Thus we need to use graph convolutions to learn feature representations on this space, which we explore in this next section.
 
@@
 Much attention has been given to graph neural networks (GNNs) recently
-\cite{bronstein2017geometric, bruna2013spectral, defferrard2016convolutional, kipf2016semi, scarselli2009graph, gama2018mimo, gama2018convolutional}.
+\cite{bronstein2017geometric, bruna2013spectral, defferrard2016convolutional, kipf2016semi, scarselli2009graph, gama2018mimo, gama2018convolutional, battaglia2018relational}.
 For our purpose we will need a method that can handle different graph structures as input, thus we cannot resort to spectral graph convolution methods.
@@
 \begin{align}
-      L =&\; (D + I)^{-1/2} (A + I) (D + I)^{-1/2} \\
-E_{k+1} =&\; \sigma\left(L E_k W_k \right)
+      \mat{L} =&\; (\mat{D} + \mat{I})^{-1/2} (\mat{A} + \mat{I}) (\mat{D} + \mat{I})^{-1/2} \\
+\mat{E}_{k+1} =&\; \sigma\left(\mat{L} \mat{E}_k \mat{W}_k \right)
 \end{align}
-Here $\sigma$ is the non-linearity (typically a $relu$), and $W_k$ are the learned weights. 
+Here $\sigma$ is the non-linearity (typically a $relu$), and $W_k$ are the learned weights of layer $k$. 
 The matrix $L$ is analogous to the graph Laplacian, and is used to encode the structure of the graph.
@@
 However, this is limited to convolutions over a one-hop neighborhood of a node.
-For simplicity we restrict ourselves to this for now, though in principle we could use higher hop neighborhoods \cite{gama2018convolutional}.
-To train this we use a cycle consistency.
+For simplicity we restrict ourselves to this for now, though in principle we could use higher hop neighborhoods \cite{gama2018convolutional}, or more complicated structures \cite{battaglia2018relational}.
+The final output $\mat{E}_n$ gives us a new descriptor for every node.
+In the next sections we will discuss the loss functions to train this network.
 
@@
 \end{equation}
+Another way of viewing this is that features $i$ and $j$ match with probability $(\mat{E}_n)_i \cdot (\mat{E}_n)_j$ which is proporitional to $\mat{A}_{ij}$.
 
-In the case, we try to learn embeddings that map to the $\mat{X}_i$ - learn the universe of features via our embeddings.
+In our case, we try to learn embeddings $\mat{E}$ that map to the $\mat{X}_i$ - learn the universe of features via our embeddings.
 Thus our loss would be 
 \begin{equation}
-\mathcal{L}(A, E_n) = \mathcal{D}(A, E_nE_n^\top)
+\mathcal{L}(\mat{A}, \mat{E}_n) = \mathcal{D}(\mat{A}, \mat{E}_n\mat{E}_n^\top)
 \end{equation}
 Here $\mathcal{D}$ could be an $L_2$ loss, $L_1$ loss, or many others.
-This essential models that features $i$ and $j$ match with probability $(E_n)_i \cdot (E_n)_j$
-which is proporitional to $A_{ij}$ with some noise.
+
+\subsection{Geometric Side Information}
+One of the main advantages of this approach over more traditional optimization based approaches is the ability to add geometric side information into the loss at training time, even if it is not available at test time.
+The simplest way to add this, and the approach we use here, is using the epipolar constraint.
+The epipolar constriant describes how two features corresponding to the same point.
+We use the two pose epipolar constraint \cite{tron2014quotient} on corresponding feature locations $X_i$ and $X_j$ in cameras $i$ and $j$:
+\begin{equation}
+X_{i}^\top R_{i}^\top \cross{T_{j} - T_{i}}R_{j} X_{j} = 0
+\label{eq:essential_constraint}
+\end{equation}
+Where the $(R_k, T_k)$ are the poses of cameras $i$ and $j$ respectively.
+This assumes that the $X_k$ are calibrated i.e. the camera intrinsics are known. 
+Given the matrix of correspondences between camera $i$ and $j$, $\mat{M}_{ij}$, we can formulate this as a loss:
+\begin{equation}
+\mathcal{L}_{ij,geom}(\mat{M}_{ij}) = \sum_{k,l} (\mat{M}_{ij})_{kl} \left|X_{i,k}^\top R_{i}^\top \cross{T_{j} - T_{i}}R_{j} X_{j,l}\right|
+\label{eq:geom_cost}
+\end{equation}
+For our purposes, since we use low rank embeddings of the $\mat{M}_{ij}$, the loss would look like:
+\begin{align}
+\mathcal{L}_{geom}(\mat{E}) =&\; \sum_{i,j} (\mat{E})_{i} \cdot (\mat{E})_{j} (\mat{G})_{ij} \\
+(\mat{G})_{ij} =&\; \left|X_{i}^\top R_{c(i)}^\top \cross{T_{c(j)} - T_{c(i)}}R_{c(j)} X_{j}\right| \nonumber
+\label{eq:geom_cost2}
+\end{align}
+Where $c(i)$ is the appropriate camera for index $i$.
+While this is all we use in this work, in principle you could higher order constraints such as the trifocal tensor as additional loss terms.
 
@@
   \end{center}
-     \caption{Example of a short caption, which should be centered.}
+     \caption{Experimental results from Rome16K}
   \label{fig:short}
 \end{figure*}
+
+\begin{table*}
+\begin{center}
+\begin{tabular}{|l|c|c|}
+\hline
+Method & Same Point Similarities & Different Point Similarities  \\
+\hline\hline\hline
+Ideal                              & 1.00e+0 $\pm$ 0.00e+0 & 0.00e+0 $\pm$ 0.00e+0 \\ \hline
+Initialization Baseline            & 5.11e-1 $\pm$ 1.68e-2 & 2.56e-1 $\pm$ 2.06e-1 \\ \hline
+3 Views, Noiseless                 & 9.96e-1 $\pm$ 7.70e-3 & 1.16e-1 $\pm$ 1.32e-1 \\ \hline
+5 Views, Noiseless                 & 1.00e+0 $\pm$ 4.15e-4 & 1.22e-1 $\pm$ 1.67e-1 \\ \hline
+3 Views, Added Noise               & 9.96e-1 $\pm$ 7.70e-3 & 1.16e-1 $\pm$ 1.32e-1 \\ \hline
+3 Views, Added Noise               & 9.68e-1 $\pm$ 5.29e-2 & 9.50e-2 $\pm$ 1.58e-1 \\ \hline
+5 Views, Added Noise               & 9.89e-1 $\pm$ 2.47e-2 & 7.67e-2 $\pm$ 1.56e-1 \\ \hline
+6 Views, Added Noise               & 9.84e-1 $\pm$ 3.16e-2 & 7.46e-2 $\pm$ 1.57e-1 \\ \hline
+3 Views, 5\% Outliers              & 9.29e-1 $\pm$ 1.79e-1 & 1.41e-1 $\pm$ 1.48e-1 \\ \hline
+3 Views, 10\% Outliers             & 9.27e-1 $\pm$ 1.79e-1 & 1.40e-1 $\pm$ 1.51e-1 \\ \hline
+
+\hline
+\end{tabular}
+\end{center}
+\caption{
+Results on Rome16k Correspondence graphs.
+Losses tested against ground truth correspondence graph adjacency matrices.
+Our method was not trained on ground truth corresopndences but on unsupervised methods.
+}
+\end{table*}
+\subsection{Synthetic Graph Dataset}
+We test our method on synthetically generated data as a simple proof of concept.
+To generate the data, we generate $p$ points, each with its own randomly generated descriptor.
+To create the graph, we generate random permutation matrices, with a noise applied to it after it is generated.
+The initial descriptors we created using true descriptor plus some added noise.
+No geometric losses were added during training.
+Testing with different noise functions and parameters.
+All experiments were run with a 12 layer GCN with the ReLU nonlinearity and skip connections between the first layer and the 6th and 12th layers.
+All were trained with the Adam optimizer and a learning rate $10^{-4}$
 
@@
 % TODO: Actually run tests on all these with different loss functions
+We  use the Rome16K dataset \cite{li2010location} to test our algorithm in real world settings.
 We extract image triplets, quadtruplets, and quintuplets with overlap of 80 points or more to test our algorithm on.
@@
 
-We test with various loss functions, including ablation studies on various geometric loss functions.
+We test with various loss functions, specifcally $L_1$, $L_2$, and the binary cross entropy loss (BCE).
+We evaluate on a test set using the ground truth Adjacency matrix which we compute from the bundle adjustment given by the Rome16K dataset.
+Traditional methods of evaluation use Precision and Recall, after making the labels 0 or 1.
+We forgo as our method was trained to output soft labels - we also in turn make the labels soft for the optimization based methods.
+We also include ablation studies on various geometric loss functions for the geometric side information.
 
 % leaderConsensus.m  MatchALSTestErrors.txt  mmatch_CVX_ALS.m  mmatch_QP_PG.m  mmatch_spectral.m  PGDDS.m  PGDDSTestErrors.txt  print_errors.py  run_tests.m  SpectralTestErrors.txt
+
 \begin{table*}
@@
 \hline\hline\hline
-Spectral                                  & 1.000e-3 & 1.000e-3 & 1.000e-3 \\ \hline
-MatchALS                                  & 1.000e-3 & 1.000e-3 & 1.000e-3 \\ \hline
-PGDDS                                     & 1.000e-3 & 1.000e-3 & 1.000e-3 \\ \hline
+Spectral                                  & 1.96e-1 $\pm$ 9.90e-3 & 4.34e-2 $\pm$ 3.21e-3 & 3.24e-1 $\pm$ 1.72e-2 \\ \hline
+MatchALS                                  & 6.73e-3 $\pm$ 3.02e-3 & 6.71e-3 $\pm$ 3.02e-3 & 2.26e-1 $\pm$ 1.04e-1 \\ \hline
+PGDDS                                     & 1.31e-2 $\pm$ 2.18e-3 & 4.73e-3 $\pm$ 1.89e-3 & 3.87e-2 $\pm$ 3.86e-2 \\ \hline
 GNN, 12 Layers, w/o Geometric Side Losses & 1.000e-3 & 1.000e-3 & 1.000e-3 \\ \hline

### 2018-11-06 data_util/__main__.py
Fixed some bugs with the positions for the features

@@ -3,7 +3,7 @@ import numpy as np
 import os
 
 import options
-from data_util import dataset
+from data_util import datasets
 from data_util import noisy_dataset
 from data_util import real_dataset
 
@@ -11,7 +11,7 @@ opts = options.get_opts()
 print("Generating Pose Graphs")
 if not os.path.exists(opts.data_dir):
   os.makedirs(opts.data_dir)
-mydataset = dataset.get_dataset(opts)
+mydataset = datasets.get_dataset(opts)
 
 types = [
   'train',

### 2018-11-06 data_util/real_dataset.py

@@ -24,9 +24,9 @@ class Rome16KTupleDataset(parent_dataset.GraphSimDataset):
     del self.features['Mask']
     del self.features['MaskOffset']
     self.dataset_params.sizes['train'] = \
-        sum([x[tuple_size-1] for _, x in parse.bundle_file_info['train'].items()])
+        sum([x[tuple_size-2] for _, x in parse.bundle_file_info['train'].items()])
     self.dataset_params.sizes['test'] = \
-        sum([x[tuple_size-1] for _, x in parse.bundle_file_info['test'].items()])
+        sum([x[tuple_size-2] for _, x in parse.bundle_file_info['test'].items()])
 
   def gen_sample(self):
     print("ERROR: Cannot generate sample - need to load data")
@@ -36,8 +36,11 @@ class Rome16KTupleDataset(parent_dataset.GraphSimDataset):
     print("ERROR: Not implemented in abstract base class")
     sys.exit(1)
 
+  def scene_fname(self, bundle_file):
+    return os.path.join(self.rome16k_dir, 'scenes', parse.scene_fname(bundle_file))
+
   def tuple_fname(self, bundle_file):
-    return os.path.join(self.rome16k_dir, parse.tuples_name(bundle_file))
+    return os.path.join(self.rome16k_dir, 'scenes', parse.tuples_fname(bundle_file))
 
   def convert_dataset(self, out_dir, mode):
     """Writes synthetic flow data in .mat format to a TF record file."""
@@ -55,16 +58,18 @@ class Rome16KTupleDataset(parent_dataset.GraphSimDataset):
 
     pbar = tqdm.tqdm(total=params.sizes[mode])
     for bundle_file in parse.bundle_file_info[mode]:
-      scene_name = '{}/{}'.format(self.rome16k_dir, parse.scene_name(bundle_file))
+      scene_name = self.scene_fname(bundle_file)
       scene = parse.load_scene(scene_name)
-      with open(self.tuples_fname(bundle_file), 'rb') as f:
-        tuples = pickle.load(f)[self.tuple_size-1]
-      for tupl in triplets:
+      tuples_fname = self.tuples_fname(bundle_file)
+      with open(tuples_fname, 'rb') as f:
+        tuples = pickle.load(f)[self.tuple_size-2]
+      for tupl in tuples:
         if file_idx > self.MAX_IDX:
           file_idx = 0
           if writer: writer.close()
[…]

### 2018-11-06 cvpr2019/main.tex

@@
 Much work has been done on image matching for the last several decades \cite{fischler1981random}.
-However we still have not fully answered the question: What are the best features of an image to capture multiple views of the same scene?
+However we still have not fully answered the question: What are the best image features to describe multiple views of the same scene?
 Recently deep learning has revolutionized how image features are computed \cite{yi2016lift}, and we would like to leverage this to compute better scene features.
 Typically when applied to this area, deep neural networks (DNNs) are trained with photometric losses.
-Photometric losses make the brightness constancy assumption - can we learn using multi-view constraints directly?
+Photometric losses make the brightness constancy assumption, which is not as robust as feature matching.
+Can we learn using multi-view constraints directly?
 
@@
 In the case of multi-image feature matching, one would need to hand label point correspondences between images, which is difficult and expensive to obtain.
-Mutli-view constraints are formulated in terms of sparse features, thus traditional convolutional deep neural nets (CNNs) are not designed to handle such input.
+Multi-view constraints are formulated in terms of sparse features, thus traditional convolutional deep neural nets (CNNs) are not designed to handle such input.
 In the case of multi-image feature matching, geometric constraints would be helpful in rejecting outlier matches.
@@
 In this work we propose to solve these problems using a Graph Neural Network (GNN) to operate on the correspondence graph.
-The method proposed works the correspondence graph, agnostic to how correspondnces were computed.
+The method proposed works on the correspondence graph, agnostic to how correspondnces were computed.
 We use an self-supervised loss, the cycle consistency loss, to train the network.
-We also add in side geometric losses used to help training, where the geometric information is not available at train time.
-Our contributions our:
+We also add in side geometric losses used to help training, which works even when the geometric information is not available at test time.
+Our contributions are:
 \begin{itemize}
@@
 
-Matching has a rich history of research.
+Matching has a rich history of research in computer vision.
 The most well known and widely used method for image matching is that of RANSAC \cite{fischler1981random}.
 RANSAC combined with hand-crafted feature descriptors like SIFT \cite{lowe2004distinctive}, SURF \cite{bay2006surf}, BRIEF \cite{calonder2012brief}, or ORB \cite{mur2015orb} has constituted the bulk of the matching literature for the last 40 years.
-To improve matching of all the features of the image, graph matching \cite{suh2015subgraph, hu2016distributable}.
+To improve matching of all the features of the image, graph matching \cite{suh2015subgraph, hu2016distributable} can also be used for more robust matching.
 
-Multi-image matching has traditionally been done using optimization based methods optimizing for cycle consistency (see Secion 3.3) such as \cite{pachauri2013solving,zhou2015multi,arrigoni2017synchronization} and \cite{wang2017multi}.
-\cite{pachauri2013solving} and \cite{arrigoni2017synchronization} use the eigenvectors of the matching matrix to obtain the the low dimensional embedding. 
+Multi-image matching has traditionally been done using optimization based methods optimizing for cycle consistency (see Section 3.3) such as \cite{pachauri2013solving,zhou2015multi,arrigoni2017synchronization} and \cite{wang2017multi}.
+\cite{pachauri2013solving} and \cite{arrigoni2017synchronization} use the eigenvectors of the matching matrix to obtain a low dimensional embedding. 
 Thus they are robust to small Gaussian noise but not to stronger noise.
@@
 as done in \cite{leonardos2016distributed}.
-There are also density based optimization techniques to compute mutli-image correspondence, such as in \cite{tron2017fast}.
+There are also density based optimization techniques to compute multi-image correspondence, such as in \cite{tron2017fast}.
 
@@
 \cite{bronstein2017geometric, bruna2013spectral, defferrard2016convolutional, kipf2016semi, scarselli2009graph, gama2018mimo, gama2018convolutional, battaglia2018relational}.
-Classical so-called Spectral methods used the eigenvectors of graph Laplacian to compute convolutions \cite{bronstein2017geometric}, but this requires a fixed graph structure a-priori.  
+Classical so-called Spectral methods used the eigenvectors of graph Laplacian to compute convolutions \cite{bronstein2017geometric}, but this requires a fixed graph structure known a-priori.  
 Non-spectral methods do not have this requirement \cite{bronstein2017geometric, kipf2016semi, scarselli2009graph, gama2018convolutional}.
@@
     An outline of the pipeline of this work.
-    The graph of matches is put to a Graph Convolutional Neural Network \cite{kipf2016semi} then creates a low rank embedding of the Adjacency Matrix of the graph.
-    The matrix reconstruction loss is used to train the network.
+    The graph of matches is put to a Graph Convolutional Neural Network (GCN) \cite{kipf2016semi} then creates a low rank embedding of the Adjacency Matrix of the graph.
+    The GCN operates on an embedding over the nodes the graph.
+    The colors on the nodes of the graph in the GCN represent the values of the embedding.
+    The final embedding is used to construct a pairwise similarity matrix, which ideally should be a low dimensional representation of the graph adjacency matrix i.e.
+should be a cycle consistent version of the graph adjacency matrix.
+    We train the network using a reconstruction loss on the similarity matrix.
     In addition we can use geometric information at to assist training the network, even if we do not have that geometric information at testing time.
+    This can be epipolar constraints on the point locations or higher order geometric constraints.
   }
@@
 We assume we have an initial set of features matches, represented as a graph $\mathcal{G} = (\mathcal{V}, \mathcal{E})$.
-Each vertex $v$ of the graph is a feature, with its assocated descriptor $f_v$. 
+Each vertex $v$ of the graph is a feature, with its associated descriptor $f_v$. 
 The graph is represented by its Weighted Adjacency Matrix $\mat{A}(\mathcal{G}) \in \bR^{n \times n}$, and its degree matrix $\mat{D}(\mathcal{G}) \in \bR^{n \times n}$ (positive diagonal) (we drop the $\mathcal{G}$ for brevity).
@@
 
-In the absence of noise or outliers, this graph would have $p$ connected components, where $p$ is the number of co-visible points in the world.
+In the absence of noise or outliers, this graph would have $p$ disjoint connected components, where $p$ is the number of co-visible points in the world.
 Each feature would only have edges to other features corresponding to the same point.
@@
 Typically putative correspondences match probabilistically, meaning a feature in one image matches to many features in another.
-This could come from repeated features in the world, the inherant ambiguous low level, local feature matching, or just an error in the matching algorithm.
+This could come from repeated features in the world, the inherant ambiguity low level, local feature matching, or just an error in the matching algorithm.
 Filtering out these noisy matches is our primary learning goal.
@@
 However, this is limited to convolutions over a one-hop neighborhood of a node.
+However, as we have many layers, the receptive field of the final embedding is quite large.
 For simplicity we restrict ourselves to this for now, though in principle we could use higher hop neighborhoods \cite{gama2018convolutional}, or more complicated structures \cite{battaglia2018relational}.
@@
 In other words, the matches between two images stays the same no matter what path is taken to get there. 
-This constraint is known as \textit{cycle concistency}, and has been used in a number of recent works to optimze for global consistency \cite{zhou2015multi, wang2017multi, leonardos2016distributed}.
+This constraint is known as \textit{cycle concistency}, and has been used in a number of recent works to optimize for global consistency \cite{zhou2015multi, wang2017multi, leonardos2016distributed}.
 Stated in this form, there are $O(n^3)$ cycle consistency constraints to check.
 A more elegant way to represent cycle consistency is to first create a `universe' of features that all images match to.
-Then one can match each set of features $X_i$ to the universe, denoted $\mat{X}_i$.
+Then one can match the $i^{th}$ set of features to the universe, denoted $\mat{X}_i$.
 Then the cycle consistency becomes:
@@
 The simplest way to add this, and the approach we use here, is using the epipolar constraint.
-The epipolar constriant describes how two features corresponding to the same point.
+The epipolar constraint describes how two features corresponding to the same point.
 We use the two pose epipolar constraint \cite{tron2014quotient} on corresponding feature locations $X_i$ and $X_j$ in cameras $i$ and $j$:
@@
 \end{align}
-Where $c(i)$ is the appropriate camera for index $i$.
-While this is all we use in this work, in principle you could higher order constraints such as the trifocal tensor as additional loss terms.
+Where $c(i)$ is the appropriate camera for point index $i$.
+While this is all we use in this work, in principle you could use higher order constraints such as the trifocal tensor as additional loss terms.
 
@@
 To create the graph, we generate random permutation matrices, with a noise applied to it after it is generated.
-The initial descriptors we created using true descriptor plus some added noise.
-No geometric losses were added during training.
+The initial descriptors we created using the true descriptor plus some added noise.
+No geometric losses were added during training for these experiments.
 Testing with different noise functions and parameters.
@@
 Traditional methods of evaluation use Precision and Recall, after making the labels 0 or 1.
-We forgo as our method was trained to output soft labels - we also in turn make the labels soft for the optimization based methods.
+We forgo this as our method was trained to output soft labels - we also in turn make the labels soft for the optimization based methods.
 We also include ablation studies on various geometric loss functions for the geometric side information.
@@
 We have shown a novel method for training feature matching.
+We have demonstrated its effectiveness using experiments on the Rome16K dataset.
+This method can be employed even when labelled training data is not available, but can still incorporate side geometric information.
+For future work we hope to use more robust losses for outlier rejection, and to incorporate learning image level features into this pipeline.
 

### 2018-11-07 data_util/real_dataset.py
Started implementing geometric losses

@@ -165,7 +165,7 @@ class KNNRome16KDataset(Rome16KTupleDataset):
     descs = np.dot(perm,np.concatenate(descs_))
 
     # Build Graph
-    desc_norms = np.sum(descs**2, 1).reshape(-1, 1)
+    desc_norms = np.sqrt(np.sum(descs**2, 1).reshape(-1, 1))
     ndescs = descs / desc_norms
     Dinit = np.dot(ndescs,ndescs.T)
     # Rescaling
@@ -225,6 +225,11 @@ class GeomKNNRome16KDataset(Rome16KTupleDataset):
                          description='Mask offset for loss'),
     })
 
+  def build_mask(self):
+    p = self.n_pts
+    v = self.n_views
+    return tf.convert_to_tensor(1-np.kron(np.eye(v), np.ones((p,p))))
+
   def gen_sample_from_tuple(self, scene, tupl):
     # Parameters
     k = self.dataset_params.knn
@@ -254,7 +259,7 @@ class GeomKNNRome16KDataset(Rome16KTupleDataset):
     scale = np.dot(perm,np.concatenate(scale_)).reshape(-1,1)
     orien = np.dot(perm,np.concatenate(orien_)).reshape(-1,1)
     # Build Graph
-    desc_norms = np.sum(descs**2, 1).reshape(-1, 1)
+    desc_norms = np.sqrt(np.sum(descs**2, 1).reshape(-1, 1))
     ndescs = descs / desc_norms
     Dinit = np.dot(ndescs,ndescs.T)
     # Rescaling

### 2018-11-07 train.py

@@ -19,7 +19,7 @@ loss_fns = {
   'bce': tfutils.bce_loss,
   'l1': tfutils.l1_loss,
   'l2': tfutils.l2_loss,
-  'l1l2': tfutils.l2_loss,
+  'l1l2': tfutils.l1l2_loss,
 }
 
 log_file = None

### 2018-11-08 data_util/parent_dataset.py
Added some of Alex's hints to make data loading faster

@@ -248,6 +248,8 @@ class GraphSimDataset(object):
       dataset = dataset.shuffle(buffer_size=5*opts.batch_size)
     if opts.batch_size > 1:
       dataset = dataset.batch(opts.batch_size)
+      # TODO: Is this the optimal buffer_size?
+      dataset = dataset.prefetch(buffer_size=opts.batch_size)
 
     iterator = dataset.make_one_shot_iterator()
     sample = iterator.get_next()

### 2018-11-08 train.py

@@ -258,10 +258,11 @@ def train(opts):
   dataset = data_util.datasets.get_dataset(opts)
   network = model.get_network(opts, opts.arch)
   # Training
-  if opts.load_data:
-    sample = dataset.load_batch('train')
-  else:
-    sample = dataset.gen_batch('train')
+  with tf.device('/cpu:0'):
+    if opts.load_data:
+      sample = dataset.load_batch('train')
+    else:
+      sample = dataset.gen_batch('train')
   output = network(sample['Laplacian'], sample['InitEmbeddings'])
   loss = get_loss(opts, sample, output)
   train_op = get_train_op(opts, loss)

### 2018-11-08 launch/download_files.py
Fixed download files to use the new log file instead of the klogs

@@ -23,30 +23,6 @@ def get_opts():
   opts = parser.parse_args()
   return opts
 
-def in_set(x, S):
-  for s in S:
-    if x in s:
-      return True
-  return False
-
-def get_log_names(opts):
-  experiments = []
-  for name in opts.experiments:
-    yaml_name = os.path.splitext(name)[0]
-    if len(yaml_name) > 56:
-      yaml_name = yaml_name[:56]
-    experiments.append(yaml_name) 
-  raw = subprocess.check_output(["kubectl", "get", "pods"])
-  decoded = [ z.split() for z in raw.decode("utf-8").split("\n") ]
-  log_names_all = [ w[0] for w in decoded[:-1] ]
-  exclude = [ 'kssh-session', 'NAME' ] + opts.exclude
-  log_names = [ w for w in log_names_all if not in_set(w, exclude) ]
-  return log_names
-
-def get_logs(log_names, yaml_name):
-  sel_names = [ w for w in log_names if yaml_name in w  ]
-  logs_bytes = [ subprocess.check_output(["kubectl", "logs", log_name]) for log_name in sel_names ]
-  return [ lb.decode("utf-8").split("\n") for lb in logs_bytes ]
 
 def get_loss_values(log):
   loss_vals = {
@@ -57,7 +33,7 @@ def get_loss_values(log):
   }
   for x in log:
     line = x.split()
-    if '=' in line: # Marks where the 
+    if '=' in line: # Marks where the loss value is
       if 'Test' in line:
         loss_vals['test'].append(float(line[line.index('=')+1]))
         if 'L1' in line:
@@ -74,44 +50,37 @@ def get_loss_values(log):
   return loss_vals
 
 opts = get_opts()
+assert(all([ x[-len('.yaml'):] == '.yaml' for x in opts.experiments ]))
 print("Getting data...")
-losses = []
-log_names = get_log_names(opts)
-for n in range(len(opts.experiments)):
-  yaml_name = opts.experiments[n]
-  name = os.path.splitext(yaml_name)[0]
-  logs = get_logs(log_names, name)
-  if len(logs) > 0:
-    for l in range(len(logs)):
-      loss_vals = get_loss_values(logs[l])
-      if len(logs) > 1:
-        loss_name ="{}-{}".format(name,l)
-      else:
-        loss_name = name
-      losses.append((loss_vals, loss_name, name))
[…]

### 2018-11-09 cvpr2019/main.tex
Added a better title
Added figures to git repo and made some modifications to latex

@@
 %%%%%%%%% TITLE
-\title{Learning Multiple View Feature Representations}
+% \title{All Graphs Lead to Rome: \\
+% Cycle Consistent Multi-View Representations Using Graph CNNs}
+\title{All Graphs Lead to Rome: Learning Geometric and Cycle Consistent Representations with Graph CNNs}
 
@@
 
+\begin{figure}[t]
+\begin{center}
+  \includegraphics[width=0.8\linewidth]{figures/GeometricConsistency.pdf}
+\end{center}
+  \caption{
+    Illustration of the Geometric loss.
+    We compute the errors on each feature match to determine their validity.
+    Errors are computed via absolute distance from the epipolar line, as expressed by equation \ref{eq:essential_constraint} via the epipolar constraint.
+  }
+\label{fig:cycconsistex}
+\label{fig:onecol}
+\end{figure}
+
 \subsection{Geometric Side Information}
@@
 The epipolar constraint describes how two features corresponding to the same point.
-We use the two pose epipolar constraint \cite{tron2014quotient} on corresponding feature locations $X_i$ and $X_j$ in cameras $i$ and $j$:
+Given a relative pose $(R_{ij}, T_{ij})$ between two cameras $i$ and $j$  (transforms $j$ to $i$) the epipolar on corresponding feature locations $X_i$ and $X_j$:
+\begin{equation}
+X_{i}^\top \cross{T_{ij}}R_{ij} X_{j} = 0
+\label{eq:essential_constraint_rel}
+\end{equation}
+In this work we use the two pose epipolar constraint \cite{tron2014quotient}:
 \begin{equation}
@@
 \begin{align}
-\mathcal{L}_{geom}(\mat{E}) =&\; \sum_{i,j} (\mat{E})_{i} \cdot (\mat{E})_{j} (\mat{G})_{ij} \\
+\mathcal{L}_{geom}(\mat{E})
+=&\; \mathrm{tr}(\mat{G}^\top \mat{E}\mat{E}^\top) = \sum_{i,j} (\mat{E})_{i} \cdot (\mat{E})_{j} (\mat{G})_{ij} \\
 (\mat{G})_{ij} =&\; \left|X_{i}^\top R_{c(i)}^\top \cross{T_{c(j)} - T_{c(i)}}R_{c(j)} X_{j}\right| \nonumber
@@
 \section{Experiments}
+
+\begin{figure*}
+\begin{center}
+  % \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
+  \includegraphics[width=0.8\linewidth]{figures/TrainingCurves.pdf}
+  \end{center}
+    \caption{
+      Training curves with and without Geometric Training loss.
+      The training loss dramatically improves training time and performance.
+      Shown as horizontal lines are the state of the art optimization based baselines.
+      Even with a simple network we compare well with them.
+      NOTE TO READERS: This figure needs to be cleaned up.
+    }
+  \label{fig:short}
+\end{figure*}
 

### 2018-11-09 latex_report.py
Fixed minor bug in latex_report

@@ -358,8 +358,9 @@ class LatexGenerator(object):
     min_idx = np.argmin(losses)
     max_idx = np.argmax(losses)
     rnd_idx = min_idx
-    while rnd_idx in [ min_idx, max_idx ]:
-      rnd_idx = np.random.randint(len(losses))
+    if len(losses) > 2:
+      while rnd_idx in [ min_idx, max_idx ]:
+        rnd_idx = np.random.randint(len(losses))
 
     ##### Create Latex String
     latex_string = ""

### 2018-11-09 model/networks.py
Added group normalization (and fixed possible skip layer bug)

@@ -48,6 +48,48 @@ class GraphConvLayerNetwork(snt.AbstractModule):
       output = tf.nn.l2_normalize(output, axis=2)
     return output
 
+class GraphSkipLayerNetwork(snt.AbstractModule):
+  def __init__(self,
+               opts,
+               arch,
+               use_bias=True,
+               initializers=None,
+               regularizers=None,
+               custom_getter=None,
+               name="graphnn"):
+    super(GraphSkipLayerNetwork, self).__init__(custom_getter=custom_getter, name=name)
+    self._nlayers = len(arch.layer_lens)
+    final_regularizers = None
+    if regularizers is not None:
+      final_regularizers = { k:v
+                             for k, v in regularizers.items()
+                             if k in ["w", "b"] }
+    self._layers = [
+      layers.GraphSkipLayer(
+        output_size=layer_len,
+        activation=arch.activ,
+        initializers=initializers,
+        regularizers=regularizers,
+        name="{}/graph_skip".format(name))
+      for layer_len in arch.layer_lens
+    ] + [
+      layers.EmbeddingLinearLayer(
+        output_size=opts.final_embedding_dim,
+        initializers=initializers,
+        regularizers=final_regularizers,
+        name="{}/embed_lin".format(name))
+    ]
+    self.normalize_emb = arch.normalize_emb
+
+  def _build(self, laplacian, init_embeddings):
+    """Applying this graph network to sample"""
+    output = init_embeddings
+    for layer in self._layers:
+      output = layer(laplacian, output)
+    if self.normalize_emb:
+      output = tf.nn.l2_normalize(output, axis=2)
+    return output
+
 class GraphLongSkipLayerNetwork(snt.AbstractModule):
   def __init__(self,
                opts,
@@ -107,8 +149,7 @@ class GraphLongSkipLayerNetwork(snt.AbstractModule):
       output = tf.nn.l2_normalize(output, axis=2)
     return output
 
-
-class GraphSkipLayerNetwork(snt.AbstractModule):
+class GraphLongSkipNormedNetwork(snt.AbstractModule):
   def __init__(self,
                opts,
                arch,
@@ -117,13 +158,17 @@ class GraphSkipLayerNetwork(snt.AbstractModule):
                regularizers=None,
                custom_getter=None,
                name="graphnn"):
-    super(GraphSkipLayerNetwork, self).__init__(custom_getter=custom_getter, name=name)
+    super(GraphLongSkipLayerNetwork, self).__init__(custom_getter=custom_getter,
[…]

### 2018-11-09 options.py

@@ -30,6 +30,7 @@ arch_choices = [
   'vanilla', 'vanilla0', 'vanilla1',
   'skip', 'skip0', 'skip1',
   'longskip0', 'longskip1',
+  'normedskip0', 'normedskip1',
   'attn0', 'attn1', 'attn2',
   'spattn0', 'spattn1', 'spattn2',
 ]
@@ -302,6 +303,7 @@ def get_opts():
       self.activ = opts.activation_type
       self.attn_lens = []
       self.skip_layers = []
+      self.start_normed = -1
       self.normalize_emb = True
       self.sparse = False
   arch = ArchParams(opts)
@@ -311,17 +313,19 @@ def get_opts():
     arch.layer_lens=[ 2**min(5+k,9) for k in range(5) ]
   elif opts.architecture in ['vanilla1', 'skip1', 'attn2', 'spattn2']:
     arch.layer_lens=[ 2**min(5+k,9) for k in range(5) ]
-  elif opts.architecture in ['longskip0']:
+  elif opts.architecture in ['longskip0', 'normedskip0']:
     arch.layer_lens=[ 32, 64, 128, 256, 512, 512, 512,
                       512, 512, 512, 1024, 1024 ]
     arch.skip_layers = [ len(arch.layer_lens)//2, len(arch.layer_lens) - 1 ]
-  elif opts.architecture in ['longskip1']:
+  elif opts.architecture in ['longskip1', 'normedskip1']:
     arch.layer_lens=[ 32, 64, 128, 256, 512, 512,
                       512, 512, 512, 1024, 1024,
                       512, 512, 512, 1024, 1024 ]
     arch.skip_layers = [ 5, 10, len(arch.layer_lens) - 1 ]
   if opts.architecture in [ 'spattn0', 'spattn1', 'spattn2' ]:
     arch.sparse = True
+  if opts.architecture in [ 'normedskip0', 'normedskip1' ]:
+    arch.start_normed = 1
   if opts.loss_type == 'bce':
     arch.normalize_emb = False
   if opts.dataset not in [ 'rome16kgeom0' ]:

### 2018-11-11 cvpr2019/main.tex
Updates to tex file

@@
 
-Unfortunately there are obstacles to applying multi-view constraints directly to learning. 
+Unfortunately, there are obstacles to applying multi-view constraints directly to learning. 
 To train networks, we need a large amount of labelled data.
@@
 
-In this work we propose to solve these problems using a Graph Neural Network (GNN) to operate on the correspondence graph.
+In this work, we propose to solve these problems using a Graph Neural Network (GNN) to operate on the correspondence graph.
 The method proposed works on the correspondence graph, agnostic to how correspondnces were computed.
-We use an self-supervised loss, the cycle consistency loss, to train the network.
-We also add in side geometric losses used to help training, which works even when the geometric information is not available at test time.
+
+We use a self-supervised loss, the cycle consistency loss, to train the network.
+We also add in side geometric losses to help training, which works even when the geometric information is not available at test time.
 Our contributions are:
 \begin{itemize}
-\item A novel architecture for feature multi-image feature matching using GNNs with graph embeddings
-\item Using the self-supervised cycle consistency loss
+\item A novel architecture for multi-image feature matching using GNNs with graph embeddings
+\item The use of the self-supervised cycle consistency loss
 \item Test geometric consistency losses toward the training
@@
 
-Multi-image matching has traditionally been done using optimization based methods optimizing for cycle consistency (see Section 3.3) such as \cite{pachauri2013solving,zhou2015multi,arrigoni2017synchronization} and \cite{wang2017multi}.
+Multi-image matching has traditionally been done using optimization based methods minimizing a cycle consistency based loss (see Section 3.3) such as \cite{pachauri2013solving,zhou2015multi,arrigoni2017synchronization} and \cite{wang2017multi}.
 \cite{pachauri2013solving} and \cite{arrigoni2017synchronization} use the eigenvectors of the matching matrix to obtain a low dimensional embedding. 
@@
 This approach is limited if you do not have the ability to get the ground truth correspondences.
-There are other methods to build correspondnces \cite{choy2016universal}, but it only handles two-view constraints and requires dense correspondeces.
+There are other methods to build correspondences \cite{choy2016universal}, but it only handles two-view constraints and requires dense correspondences.
 Most similar to ours, \cite{yi2018learning} attempts to improve correspondences by learning match probabilites for RANSAC to speed up test time running.
@@
 Most of these simply use polynomials of the graph Laplacian to compute neighborhood averages.
-\cite{gama2018mimo} formalizes this notion and generalizes it beyond the use of the graph Laplacian, as well as its follow up \cite{gama2018convolutional}.
-More sophisticated aggregation techniques and global information passing can also be used, as discussed in \cite{battaglia2018relational}.
+\cite{gama2018mimo} and \cite{gama2018convolutional} formalize this notion and generalize it beyond the use of the graph Laplacian.
+More sophisticated aggregation techniques and global information passing can also be used as discussed in \cite{battaglia2018relational}.
 
@@
 Our goal is to learn optimal features that capture multiple image views.
-We formulate this problem in terms of the correspondece graph of the features.
+We formulate this problem in terms of the correspondence graph of the features.
 We denote vectors $\mat{x}$ and matrices $\mat{A}$ with boldface.
@@
 \subsection{Correspondence Graph}
-We assume we have an initial set of features matches, represented as a graph $\mathcal{G} = (\mathcal{V}, \mathcal{E})$.
-Each vertex $v$ of the graph is a feature, with its associated descriptor $f_v$. 
-The graph is represented by its Weighted Adjacency Matrix $\mat{A}(\mathcal{G}) \in \bR^{n \times n}$, and its degree matrix $\mat{D}(\mathcal{G}) \in \bR^{n \times n}$ (positive diagonal) (we drop the $\mathcal{G}$ for brevity).
-We can get an embedding matrix $E_0$ by combining the features $f_v$ from each of the vertices, which we use as our initializiation for our learning algorithm.
+We assume we have an initial set of feature matches represented as a graph $\mathcal{G} = (\mathcal{V}, \mathcal{E})$.
+Each vertex $v$ of the graph is a feature with its associated descriptor $f_v$. 
+The graph is represented by its Weighted Adjacency Matrix $\mat{A}(\mathcal{G}) \in \bR^{n \times n}$ and its positive diagonal degree matrix $\mat{D}(\mathcal{G}) \in \bR^{n \times n}$ (denoted $\mat{A}$ and $\mat{D}$ for brevity).
+We can get an embedding matrix $E_0$ by combining the features $f_v$ from each of the vertices.
+We use $E_0$ as our initializiation for our learning algorithm.
 We can also add any additional knowledge we have into the embedding (e.g. scale, orientation, etc.).
-Putative correspondences are computed from these, and represented by weighted edges, the weight giving the strength of the match.
+Putative correspondences are computed from these features and represented by weighted edges in which the weight gives the strength of the match.
 While there are many interesting methods for computing these putative correspondences \cite{suh2015subgraph, yi2018learning}, we do not explore them in this work.
@@
 Each feature would only have edges to other features corresponding to the same point.
-Also no points in the same image have edges between them, as if they corresponded to the same point, they would be the same feature.
+Since features in this case represent unique location in the scene, no points in the same image would have edges between them.
 Typically putative correspondences match probabilistically, meaning a feature in one image matches to many features in another.
-This could come from repeated features in the world, the inherant ambiguity low level, local feature matching, or just an error in the matching algorithm.
+This could come from repeated structures in the scene, ambiguity from the low-level feature descriptors, or just an error in the matching algorithm.
 Filtering out these noisy matches is our primary learning goal.
 
-However, this graph structure does not have the properties of a Eulcidean domain (such as an image).
+However, this graph structure does not have the properties of a Eulcidean domain.
 Thus we cannot use standard CNNs to learn features for this task.
@@
 \cite{bronstein2017geometric, bruna2013spectral, defferrard2016convolutional, kipf2016semi, scarselli2009graph, gama2018mimo, gama2018convolutional, battaglia2018relational}.
-For our purpose we will need a method that can handle different graph structures as input, thus we cannot resort to spectral graph convolution methods.
-Since our goal is to describe correspondence of each of the nodes, we also cannot use pooling of the nodes.
+Modern GNNs use non-spectral methods, such as the following:
 \begin{align}
-      \mat{L} =&\; (\mat{D} + \mat{I})^{-1/2} (\mat{A} + \mat{I}) (\mat{D} + \mat{I})^{-1/2} \\
-\mat{E}_{k+1} =&\; \sigma\left(\mat{L} \mat{E}_k \mat{W}_k \right)
+      \mat{L} =&\; I - \mat{D}^{-1/2} \mat{A} \mat{D}^{-1/2} \\
+\mat{E}_{i+1} =&\; P\left(\sigma\left( \sum_k \mat{L}^k \mat{E}_i \mat{W}_{i,k} \right)\right)
 \end{align}
-Here $\sigma$ is the non-linearity (typically a $relu$), and $W_k$ are the learned weights of layer $k$. 
-The matrix $L$ is analogous to the graph Laplacian, and is used to encode the structure of the graph.
-It is with $L$ that the graph convolution is performed.
-However, this is limited to convolutions over a one-hop neighborhood of a node.
-However, as we have many layers, the receptive field of the final embedding is quite large.
-For simplicity we restrict ourselves to this for now, though in principle we could use higher hop neighborhoods \cite{gama2018convolutional}, or more complicated structures \cite{battaglia2018relational}.
+The matrix $L$ is the graph Laplacian, use to encode the graph structure, and $\mat{W}_{k,i}$ are the learned weights of layer $i$.
+The degree of the polynomial determines the number of hops away from a node one layer can access.
+Here $\sigma$ is the non-linearity (typically a ReLU) and $P$ is the `pooling' operation, known as graph coarsening \cite{bronstein2017geometric, gama2018mimo}.
+As we need an embedding over the whole graph, we cannot perform graph coarsening, and thus we only perform the non-linearity step.
+
+We instead use a modification of the approach in \cite{kipf2016semi}:
+\begin{align}
+      \widetilde{\mat{L}} =&\; (\mat{D} + \mat{I})^{-1/2} (\mat{A} + \mat{I}) (\mat{D} + \mat{I})^{-1/2} \\
+\mat{E}_{l+1} =&\; \sigma\left(\widetilde{\mat{L}} \mat{E}_i \mat{W}_i \right)  \label{eq:graph_conv}
+\end{align}
+
+The matrix $\widetilde{L}$ is analogous to the graph Laplacian (with better numerical stability properties).
+$\widetilde{L}$ is used to encode the structure of the graph and is used to perform the actual graph convolution.
+We use many layers, and thus the receptive field of the final embedding is quite large, even without the pooling operations.
+For simplicity we restrict ourselves to this for now, though in principle we could use higher hop neighborhoods \cite{gama2018convolutional}, or more complicated aggregation structures \cite{battaglia2018relational}.
 The final output $\mat{E}_n$ gives us a new descriptor for every node.
@@
 \end{equation}
-Another way of viewing this is that features $i$ and $j$ match with probability $(\mat{E}_n)_i \cdot (\mat{E}_n)_j$ which is proporitional to $\mat{A}_{ij}$.
 
-In our case, we try to learn embeddings $\mat{E}$ that map to the $\mat{X}_i$ - learn the universe of features via our embeddings.
+% In our case, we try to learn embeddings $\mat{E}$ that map to the $\mat{X}_i$ - learn the universe of features via our embeddings.
+We try to learn $\mat{E}$ to approximate $\mat{X}$ - in other words the final embedding should be an encoding of the universe of features.
 Thus our loss would be 
@@
 Here $\mathcal{D}$ could be an $L_2$ loss, $L_1$ loss, or many others. 
+Another way of viewing this is that features $i$ and $j$ match with probability $(\mat{E}_n)_i \cdot (\mat{E}_n)_j$ which is proporitional to $\mat{A}_{ij}$.
 
@@
 The simplest way to add this, and the approach we use here, is using the epipolar constraint.
-The epipolar constraint describes how two features corresponding to the same point.
+The epipolar constraint describes how the positions of features in different images corresponding to the same point should be related.
 Given a relative pose $(R_{ij}, T_{ij})$ between two cameras $i$ and $j$  (transforms $j$ to $i$) the epipolar on corresponding feature locations $X_i$ and $X_j$:
@@
 \end{equation}
-Where the $(R_k, T_k)$ are the poses of cameras $i$ and $j$ respectively.
+% Where the $(R_k, T_k)$ are the poses of cameras $i$ and $j$ respectively.
 This assumes that the $X_k$ are calibrated i.e. the camera intrinsics are known. 
@@
 \hline\hline\hline
-Spectral                                  & 1.96e-1 $\pm$ 9.90e-3 & 4.34e-2 $\pm$ 3.21e-3 & 3.24e-1 $\pm$ 1.72e-2 \\ \hline
-MatchALS                                  & 6.73e-3 $\pm$ 3.02e-3 & 6.71e-3 $\pm$ 3.02e-3 & 2.26e-1 $\pm$ 1.04e-1 \\ \hline
-PGDDS                                     & 1.31e-2 $\pm$ 2.18e-3 & 4.73e-3 $\pm$ 1.89e-3 & 3.87e-2 $\pm$ 3.86e-2 \\ \hline
+Spectral                                  & 5.368e-2 $\pm$ 5.274e-3 & 1.754e-2 $\pm$ 3.688e-3 & 1.143e-1 $\pm$ 2.774e-2 \\ \hline
+MatchALS                                  & 6.715e-3 $\pm$ 3.035e-3 & 6.696e-3 $\pm$ 3.035e-3 & 2.254e-1 $\pm$ 1.043e-1 \\ \hline
+PGDDS                                     & 1.311e-2 $\pm$ 2.186e-3 & 4.730e-3 $\pm$ 1.886e-3 & 3.872e-2 $\pm$ 3.869e-2 \\ \hline
 GNN, 12 Layers, w/o Geometric Side Losses & 1.000e-3 & 1.000e-3 & 1.000e-3 \\ \hline
 GNN, 12 Layers, w/ Geometric Side Losses  & 1.000e-3 & 1.000e-3 & 1.000e-3 \\ \hline
-
 \hline

### 2018-11-11 baselines/print_errors.py
Added better spectral function... makes my results not as good :/

@@ -4,6 +4,10 @@ import numpy as np
 
 import matplotlib.pyplot as plt
 
+def myformat(x):
+  y = "{:.03e}".format(x).split('e')
+  return "{}e-{}".format(y[0], y[1][-1])
+
 for fname in sys.argv[1:]:
   f = open(fname, 'r')
   ids = []
@@ -16,12 +20,9 @@ for fname in sys.argv[1:]:
   for line in f:
     l = line.split(' ')
     ids.append(int(l[0]))
-    overlap.append(float(l[3][:-1]))
-    precision.append(float(l[5][:-1]))
-    recall.append(float(l[7][:-1]))
-    l1.append(float(l[9][:-1]))
-    l2.append(float(l[12][:-1]))
-    bce.append(float(l[14][:-1]))
+    l1.append(float(l[3][:-1]))
+    l2.append(float(l[5][:-1]))
+    bce.append(float(l[7]))
 
   f.close()
 
@@ -31,13 +32,19 @@ for fname in sys.argv[1:]:
   l1 = np.array(l1)
   l2 = np.array(l2)
   bce = np.abs(np.array(bce))
-  plt.scatter(l1, l2)
-  plt.show()
-  plt.scatter(l2, bce)
-  plt.show()
+  # plt.scatter(l1, l2)
+  # plt.show()
+  # plt.scatter(l2, bce)
+  # plt.show()
 
-  print(fname)
-  print("L1 : {:.6e} +/- {:.6e} (min: {:.6e}, max: {:.6e})".format(l1.mean(), l1.std(), l1.min(), l1.max()))
-  print("L2 : {:.6e} +/- {:.6e} (min: {:.6e}, max: {:.6e})".format(l2.mean(), l2.std(), l2.min(), l2.max()))
-  print("BCE: {:.6e} +/- {:.6e} (min: {:.6e}, max: {:.6e})".format(bce.mean(), bce.std(), bce.min(), bce.max()))
+#   print("{} ({} points)".format(fname, len(l1)))
+#   print("L1 : {:.6e} +/- {:.6e} (min: {:.6e}, max: {:.6e})".format(l1.mean(), l1.std(), l1.min(), l1.max()))
+#   print("L2 : {:.6e} +/- {:.6e} (min: {:.6e}, max: {:.6e})".format(l2.mean(), l2.std(), l2.min(), l2.max()))
[…]

### 2018-11-11 baselines/run_tests.m

@@ -5,65 +5,52 @@ p = 80;
 n = p*v;
 dimGroups = [ p, p, p ];
 
+%  'MatchALSLimited', @(W)  mmatch_CVX_ALS(W, dimGroups, 'maxrank', p, 'maxiter', 15); ...
 test_fns = { ...
  'MatchALS', @(W)  mmatch_CVX_ALS(W, dimGroups, 'maxrank', p, 'maxiter', 400); ...
- 'Spectral', @(W)  mmatch_spectral(W, dimGroups, p); ...
+ 'Spectral', @(W)  myspectral(W, p); ...
  'PGDDS', @(W) PGDDS(W, dimGroups, p); ...
 };
 
 disp_string =  [ '%06d Errors: ' ...
-                 'Overlap: %.03e, Precision: %.03e, Recall: %.03e, ' ...
-                 'L1: %.03e,  L2: %.03e, BCE: %.03e\n' ];
+                 'L1: %.03e, L2: %.03e, BCE: %.03e\n' ];
 
 for test_fn_index = 1:size(test_fns,1)
   test_fn = test_fns{test_fn_index,2};
-  fid = fopen(sprintf('%sTestErrors.txt', test_fns{test_fn_index,1}), 'w');
+  fid = fopen(sprintf('%sTestErrors.log', test_fns{test_fn_index,1}), 'w');
+  fprintf('%s Method:\n', test_fns{test_fn_index,1})
+  test_index = 0;
   for mat_index = 1:length(mat_files)
     test_mats = load(mat_files{mat_index});
-    for index = 1:size(test_mats.AdjMat, 1)
-      fprintf('Matrix %03d of %03d, file %05d of %05d\r', mat_index, length(mat_files), index, size(test_mats.AdjMat, 1))
+    mat_length = size(test_mats.AdjMat, 1);
+    for index = 1:mat_length
+      fprintf('Matrix %03d of %03d, file %05d of %05d\r', mat_index, length(mat_files), index, mat_length)
       W = squeeze(test_mats.AdjMat(index,:,:)) + eye(n);
       Xgt = squeeze(test_mats.TrueEmbedding(index,:,:));
       Agt = Xgt*Xgt';
       Ah = max(0,min(1,test_fn(W)));
-      [overlap, precision, recall, l1, l2, bce] = testOutput_full(Ah,Agt,p);
[…]

### 2018-11-12 data_util/rome16k/__main__.py
Fixed typo

@@ -40,7 +40,7 @@ def get_build_scene_opts():
   parser.add_argument('--max_points',
                       default=150,
                       type=int,
-                      help='Minimum overlap of points for connection')
+                      help='Maximum overlap of points for connection')
   parser.add_argument('--max_tuple_size',
                       default=4,
                       type=int,

### 2018-11-12 data_util/datasets.py
Added geometric 4 view dataset

@@ -27,6 +27,6 @@ def get_dataset(opts):
     return noisy_dataset.GraphSimOutlierDataset(opts, opts.dataset_params)
   elif opts.dataset in [ 'rome16kknn0' ]:
     return real_dataset.KNNRome16KDataset(opts, opts.dataset_params)
-  elif opts.dataset in [ 'rome16kgeom0' ]:
+  elif opts.dataset in [ 'rome16kgeom0', 'rome16kgeom4view0' ]:
     return real_dataset.GeomKNNRome16KDataset(opts, opts.dataset_params)
 

### 2018-11-12 data_util/real_dataset.py

@@ -24,9 +24,11 @@ class Rome16KTupleDataset(parent_dataset.GraphSimDataset):
     del self.features['Mask']
     del self.features['MaskOffset']
     self.dataset_params.sizes['train'] = \
-        sum([x[tuple_size-2] for _, x in parse.bundle_file_info['train'].items()])
+        sum([ min(int(x[1]*1.5), x[tuple_size-2])
+              for _, x in parse.bundle_file_info['train'].items() ])
     self.dataset_params.sizes['test'] = \
-        sum([x[tuple_size-2] for _, x in parse.bundle_file_info['test'].items()])
+        sum([ min(int(x[1]*1.5), x[tuple_size-2])
+              for _, x in parse.bundle_file_info['test'].items()  ])
 
   def gen_sample(self):
     print("ERROR: Cannot generate sample - need to load data")
@@ -39,7 +41,7 @@ class Rome16KTupleDataset(parent_dataset.GraphSimDataset):
   def scene_fname(self, bundle_file):
     return os.path.join(self.rome16k_dir, 'scenes', parse.scene_fname(bundle_file))
 
-  def tuple_fname(self, bundle_file):
+  def tuples_fname(self, bundle_file):
     return os.path.join(self.rome16k_dir, 'scenes', parse.tuples_fname(bundle_file))
 
   def convert_dataset(self, out_dir, mode):
@@ -59,17 +61,30 @@ class Rome16KTupleDataset(parent_dataset.GraphSimDataset):
     pbar = tqdm.tqdm(total=params.sizes[mode])
     for bundle_file in parse.bundle_file_info[mode]:
       scene_name = self.scene_fname(bundle_file)
+      np.random.seed(hash(scene_name) % 2**32)
       scene = parse.load_scene(scene_name)
       tuples_fname = self.tuples_fname(bundle_file)
       with open(tuples_fname, 'rb') as f:
-        tuples = pickle.load(f)[self.tuple_size-2]
+        tuples_all = pickle.load(f)
+        if self.tuple_size == 3:
+          tuples = tuples_all[1]
+        else:
+          tuples_sel = tuples_all[self.tuple_size-2]
+          n_select = int(1.5*len(tuples_all[1])) # TODO: Make this less hacky??
+          if n_select > len(tuples_sel):
+            tuples = tuples_all[self.tuple_size-2]
+          else:
+            tuples = np.array(tuples_sel)
+            tuples_idx = np.random.choice(np.arange(len(tuples)),
[…]

### 2018-11-12 options.py

@@ -23,7 +23,7 @@ dataset_choices = [
   'synth_pts50', 'synth_pts100',
   'noise_outlier1', 'noise_outlier2', 'noise_outlier4', 'noise_outlier8',
   'rome16kknn0',
-  'rome16kgeom0',
+  'rome16kgeom0', 'rome16kgeom4view0',
 ]
 
 arch_choices = [
@@ -98,6 +98,10 @@ def get_opts():
                       default=False,
                       type=myutils.str2bool,
                       help='Use true adjacency or noisy one in loss')
+  parser.add_argument('--use_abs_value',
+                      default=False,
+                      type=myutils.str2bool,
+                      help='Use absolute value on the output similarities')
   parser.add_argument('--loss_type',
                       default=loss_types[0],
                       choices=loss_types,
@@ -287,6 +291,12 @@ def get_opts():
     # The dataset size is undermined until loading
     dataset_params.sizes={ 'train': -1, 'test': -1 }
   elif opts.dataset == 'rome16kgeom0':
+    dataset_params.points=[80] 
+    dataset_params.descriptor_dim=128
+    # The dataset size is undermined until loading
+    dataset_params.sizes={ 'train': -1, 'test': -1 }
+  elif opts.dataset == 'rome16kgeom4view0':
+    dataset_params.views = [4]
     dataset_params.points=[80] 
     dataset_params.descriptor_dim=128
     # The dataset size is undermined until loading

### 2018-11-12 train.py
Added absolute value option to possibly help with training (later)

@@ -66,6 +66,8 @@ def get_loss(opts, sample, output, return_gt=False, name='loss'):
   if opts.use_end_bias:
     end_bias = get_end_bias()
     output_sim = output_sim + end_bias
+  if opts.use_abs_value:
+    output_sim = tf.abs(output_sim)
   sim_true = tfutils.get_sim(emb)
   if opts.use_unsupervised_loss:
     v = opts.dataset_params.views[-1]

### 2018-11-12 model/__init__.py
Added skip 'hop' networks

@@ -2,5 +2,6 @@
 
 from model.layers import *
 from model.networks import *
+from model.skip_networks import *
 from model.model import *
 

### 2018-11-13 options.py
Added clamping flag for possible future use

@@ -98,6 +98,11 @@ def get_opts():
                       default=False,
                       type=myutils.str2bool,
                       help='Use true adjacency or noisy one in loss')
+  # TODO: Combine next two to add post-processing option
+  parser.add_argument('--use_clamping',
+                      default=False,
+                      type=myutils.str2bool,
+                      help='Use clamping to [0, 1] on the output similarities')
   parser.add_argument('--use_abs_value',
                       default=False,
                       type=myutils.str2bool,

### 2018-11-13 test.py
Added similarities - need to test

@@ -42,16 +42,20 @@ def get_test_losses(opts, sample, output, return_gt=False, name='loss'):
     end_bias = get_end_bias()
     output_sim = output_sim + end_bias
   if opts.loss_type == 'bce':
-    output_sim_sigmoid = tf.sigmoid(output_sim)
-    gt_l1_loss = loss_fns['l1'](sim_true, output_sim_sigmoid, add_loss=False)
-    gt_l2_loss = loss_fns['l2'](sim_true, output_sim_sigmoid, add_loss=False)
-    gt_bce_loss = loss_fns['bce'](sim_true, output_sim, add_loss=False)
+    osim = tf.sigmoid(output_sim)
+    osim_log = output_sim
   else:
-    output_sim_log = tf.log(tf.abs(output_sim) + 1e-9)
-    gt_l1_loss = loss_fns['l1'](sim_true, output_sim, add_loss=False)
-    gt_l2_loss = loss_fns['l2'](sim_true, output_sim, add_loss=False)
-    gt_bce_loss = loss_fns['bce'](sim_true, output_sim_log, add_loss=False)
-  return gt_l1_loss, gt_l2_loss, gt_bce_loss
+    osim = output_sim
+    osim_log = tf.log(tf.abs(output_sim) + 1e-9)
+  gt_l1_loss = loss_fns['l1'](sim_true, osim, add_loss=False)
+  gt_l2_loss = loss_fns['l2'](sim_true, osim, add_loss=False)
+  gt_bce_loss = loss_fns['bce'](sim_true, oslim_log, add_loss=False)
+  num_same = tf.reduce_sum(sim_true)
+  num_diff = tf.reduce_sum(1-sim_true)
+  ssame_m, ssame_var = tf.weighted_moments(osim, None, sim_true)
+  sdiff_m, sdiff_var = tf.weighted_moments(osim, None, 1-sim_true)
+
+  return gt_l1_loss, gt_l2_loss, gt_bce_loss, ssame_m, ssame_var, sdiff_m, sdiff_var
 
 def build_test_session(opts):
   config = tf.ConfigProto()
@@ -72,7 +76,11 @@ def test_values(opts):
 
   # Tensorflow and logging operations
   disp_string =  '{:06d} Errors: ' \
-                 'L1: {:.03e},  L2: {:.03e}, BCE: {:.03e}'
+                 'L1: {:.03e},  L2: {:.03e}, BCE: {:.03e} ' \
[…]

### 2018-11-14 cvpr2019/main.tex
Added more on group normalization to tex file
Added Daphne's suggestions to tex file

@@
 %%%%%%%%% ABSTRACT
+% We present a learning technique for refining multi-image feature matches in an unsupervised fashion.
 \begin{abstract}
-   % Put abstract here
-   % OK I hate this start but we will work on it.
-   (Work in progress) In this work we present a learning technique for refining multi-image matches in an unsupervised fashion.
-   We formulate the multi-image matching problem as a graph embedding problem then use recent work in Graph Neural Networks to learn the appropriate embedding function.
-   Since ground truth correspondence is difficult or expensive to come by in many real world datasets, we use cycle consistency as our loss function.
-   Additional losses can be added if more information is available in the training set for better test performance.
+   In this work we formulate the multi-image matching problem as a graph embedding problem then use a Graph Neural Network to learn an appropriate embedding function for aligning image features.
+   Since ground truth correspondence is difficult or expensive to come by in many real world datasets, we use cycle consistency to train our network in an unsupervised fashion.
+   Additional geometric side losses can be added if the information is available in the training set for better test performance.
    To the best of our knowledge, no other works have used learning for multi-image feature matching.
@@
 
-% TODO: Add more citations
-Feature matching is an essential part of many geometric computer vision applications.
-Much work has been done on image matching for the last several decades \cite{fischler1981random}.
+Feature matching is an essential part of Structure from Motion and many geometric computer vision applications.
+The goal in multi-image feature matching is to take 2D image locations from three or more images and find which ones correspond to the same point in the 3D scene.
+Methods such as SIFT feature matching \cite{lowe2004distinctive} and RANSAC \cite{fischler1981random} have been standard for solving this for decades now.
 However we still have not fully answered the question: What are the best image features to describe multiple views of the same scene?
-Recently deep learning has revolutionized how image features are computed \cite{yi2016lift}, and we would like to leverage this to compute better scene features.
-Typically when applied to this area, deep neural networks (DNNs) are trained with photometric losses.
-Photometric losses make the brightness constancy assumption, which is not as robust as feature matching.
+
+Recently deep learning has revolutionized how image features are computed \cite{yi2016lift}. 
+We would like to leverage this to compute better scene features.
+Typically when applied to this area, deep neural networks (DNNs) are trained with photometric losses, directly using pixel color values.
+Using pixel values directly is not that robust due to the many confounding factors in the environment, such as lighting and view-point changes.
+Extracting features from the image is more robust to these confounding factors.
 Can we learn using multi-view constraints directly?
 
+% Photometric losses make the brightness constancy assumption, which is not as robust as feature matching.
 \begin{figure}[t]
@@
     Example of multi-image matching, with images from Rome16K dataset \cite{li2010location}.
-    Shown is an example of an error in matching leading to an inconsistency cycle.
-    In this work, we show how to learn this multi-view matching problem.
+    In this example, an error in matching leads to an inconsistent cycle. 
+    Ideally these pairwise matches would be consistent 
+    In this work, we show how to learn this multi-view matching problem using cycle consistency.
   }
@@
 In this work, we propose to solve these problems using a Graph Neural Network (GNN) to operate on the correspondence graph.
-The method proposed works on the correspondence graph, agnostic to how correspondnces were computed.
+The proposed method works on the correspondence graph, which is agnostic to how the correspondnces were computed.
 
-We use a self-supervised loss, the cycle consistency loss, to train the network.
+We use a unsupervised loss, the cycle consistency loss, to train the network.
 We also add in side geometric losses to help training, which works even when the geometric information is not available at test time.
@@
 \begin{itemize}
-\item A novel architecture for multi-image feature matching using GNNs with graph embeddings
-\item The use of the self-supervised cycle consistency loss
-\item Test geometric consistency losses toward the training
-\item Perform experiments on the Rome16K \cite{li2010location} dataset to test the effectiveness of our method compared to the optimization based baselines
+\item We use novel architecture to solve multi-image feature matching problem using GNNs with graph embeddings
+\item We use the unsupervised cycle consistency loss to train a network to solve the multi-image matching problem
+\item We show the effectiveness of geometric side losses in training the network
+\item We perform experiments on the Rome16K \cite{li2010location} dataset to test the effectiveness of our method compared to the optimization based baselines
 \end{itemize}
@@
 \cite{zhou2015multi} and \cite{wang2017multi} use most sophisticated optimization techniques on the matching matrix and thus are quite robust.
-However, they use a centralized scheme and thus are not appropriate in a distributed setting,
-as done in \cite{leonardos2016distributed}.
+However, they use a centralized scheme and thus are not appropriate in a distributed setting, as done in \cite{leonardos2016distributed}.
 There are also density based optimization techniques to compute multi-image correspondence, such as in \cite{tron2017fast}.
@@
 
-Graph neural networks have been getting more attention recently 
-\cite{bronstein2017geometric, bruna2013spectral, defferrard2016convolutional, kipf2016semi, scarselli2009graph, gama2018mimo, gama2018convolutional, battaglia2018relational}.
-Classical so-called Spectral methods used the eigenvectors of graph Laplacian to compute convolutions \cite{bronstein2017geometric}, but this requires a fixed graph structure known a-priori.  
-Non-spectral methods do not have this requirement \cite{bronstein2017geometric, kipf2016semi, scarselli2009graph, gama2018convolutional}.
+Graph neural networks have been getting more attention recently \cite{bronstein2017geometric, bruna2013spectral, defferrard2016convolutional, kipf2016semi, scarselli2009graph, gama2018mimo, gama2018convolutional, battaglia2018relational}.
+Classical so-called Spectral methods used the eigenvectors of graph Laplacian to compute convolutions \cite{bronstein2017geometric}, but requires a fixed graph structure known a-priori.  
+Non-spectral methods do not require a-priori knowledge \cite{bronstein2017geometric, kipf2016semi, scarselli2009graph, gama2018convolutional}.
 Most of these simply use polynomials of the graph Laplacian to compute neighborhood averages.
@@
     The colors on the nodes of the graph in the GCN represent the values of the embedding.
-    The final embedding is used to construct a pairwise similarity matrix, which ideally should be a low dimensional representation of the graph adjacency matrix i.e.
-should be a cycle consistent version of the graph adjacency matrix.
+    The final embedding is used to construct a pairwise similarity matrix, which ideally should be a low dimensional cycle consistent representation of the graph adjacency matrix.
     We train the network using a reconstruction loss on the similarity matrix.
-    In addition we can use geometric information at to assist training the network, even if we do not have that geometric information at testing time.
-    This can be epipolar constraints on the point locations or higher order geometric constraints.
+    In addition we can use geometric information at to assist training the network, even if we do not have that geometric information at testing time such as epipolar constraints on the point locations or higher order geometric constraints.
   }
@@
 The graph is represented by its Weighted Adjacency Matrix $\mat{A}(\mathcal{G}) \in \bR^{n \times n}$ and its positive diagonal degree matrix $\mat{D}(\mathcal{G}) \in \bR^{n \times n}$ (denoted $\mat{A}$ and $\mat{D}$ for brevity).
-We can get an embedding matrix $E_0$ by combining the features $f_v$ from each of the vertices.
-We use $E_0$ as our initializiation for our learning algorithm.
+We can get our an embedding matrix $\mat{E}_0$ by concatenating the features $f_v$ from each of the vertices.
+We use $\mat{E}_0$ as our initializiation for our learning algorithm.
 We can also add any additional knowledge we have into the embedding (e.g. scale, orientation, etc.).
@@
 
-In the absence of noise or outliers, this graph would have $p$ disjoint connected components, where $p$ is the number of co-visible points in the world.
-Each feature would only have edges to other features corresponding to the same point.
+In the absense of noise or outliers, this graph would have a connected component for each visible point in the world.
+These components should be mutually disjoint. 
+In other words each feature would only have edges to other features corresponding to the same point.
 Since features in this case represent unique location in the scene, no points in the same image would have edges between them.
-Typically putative correspondences match probabilistically, meaning a feature in one image matches to many features in another.
+In the noisy case we expect this structure to be corrupted and thus we need to refine out the erroneous edges.
+
+To compute this matching graph, we do pairwise feature matching between the images, creating putative correspondences for each of the features.
+Typically these putative correspondences are matched probabilistically, meaning a feature in one image matches to many features in another.
 This could come from repeated structures in the scene, ambiguity from the low-level feature descriptors, or just an error in the matching algorithm.
@@
 \subsection{Graph Neural Networks}
-Much attention has been given to graph neural networks (GNNs) recently
-\cite{bronstein2017geometric, bruna2013spectral, defferrard2016convolutional, kipf2016semi, scarselli2009graph, gama2018mimo, gama2018convolutional, battaglia2018relational}.
-Modern GNNs use non-spectral methods, such as the following:
-\begin{align}
-      \mat{L} =&\; I - \mat{D}^{-1/2} \mat{A} \mat{D}^{-1/2} \\
-\mat{E}_{i+1} =&\; P\left(\sigma\left( \sum_k \mat{L}^k \mat{E}_i \mat{W}_{i,k} \right)\right)
-\end{align}
-The matrix $L$ is the graph Laplacian, use to encode the graph structure, and $\mat{W}_{k,i}$ are the learned weights of layer $i$.
+As input to our method we are given the graph Laplacian $\mat{L} \in \bR^{n \times n}$ to encode the graph structure:
+\begin{equation}
+  \mat{L} =\; \mat{I} - \mat{D}^{-1/2} \mat{A} \mat{D}^{-1/2} \\
+\end{equation}
+and an initial embedding $\mat{E}_0 \in \bR^{n \times m_0}$.
+Many older methods assume $\mat{L}$ is known a-priori \cite{bruna2013spectral}, and thus can encode graph convolutions using the eigenvectors of $L$.
+We do not have this luxery, and thus we use more modern non-spectral methods GNNs:
+\begin{equation}
+\mat{E}_{i+1} =\; P\left(\sigma\left( \sum_k \mat{L}^k \mat{E}_i \mat{W}_{i,k} \right)\right)
+\end{equation}
 The degree of the polynomial determines the number of hops away from a node one layer can access.
-Here $\sigma$ is the non-linearity (typically a ReLU) and $P$ is the `pooling' operation, known as graph coarsening \cite{bronstein2017geometric, gama2018mimo}.
-As we need an embedding over the whole graph, we cannot perform graph coarsening, and thus we only perform the non-linearity step.
-
+Here $\sigma$ is the non-linearity (typically a ReLU), $\mat{W}_{k,i}$ are the learned weights of layer $i$,  and $P$ is the `pooling' operation, known as graph coarsening \cite{bronstein2017geometric, gama2018mimo}.
+In the feature matching problem, we require an embedding for each vertex.
+Therefore we cannot perform graph coarsening, and thus we only perform the non-linearity step.
 We instead use a modification of the approach in \cite{kipf2016semi}:
@@
 
-The matrix $\widetilde{L}$ is analogous to the graph Laplacian (with better numerical stability properties).
-$\widetilde{L}$ is used to encode the structure of the graph and is used to perform the actual graph convolution.
-We use many layers, and thus the receptive field of the final embedding is quite large, even without the pooling operations.
-For simplicity we restrict ourselves to this for now, though in principle we could use higher hop neighborhoods \cite{gama2018convolutional}, or more complicated aggregation structures \cite{battaglia2018relational}.
+The matrix $\widetilde{\mat{L}}$ is analogous to the graph Laplacian (with better numerical stability properties).
+$\widetilde{\mat{L}}$ encodes the structure of the graph and is used to perform the actual graph convolution.
+Our network has many layers, and thus the receptive field of the final embedding is quite large, even without the pooling operations.
+In principle we could use higher hop neighborhoods \cite{gama2018convolutional}, or more complicated aggregation structures \cite{battaglia2018relational}, but in this work we restrict ourselves to simpler architectures, which still shows promising results for this task.
+For faster training, we use group normalization \cite{wu2018group} and skip connections.
 The final output $\mat{E}_n$ gives us a new descriptor for every node.
@@
 We try to learn $\mat{E}$ to approximate $\mat{X}$ - in other words the final embedding should be an encoding of the universe of features.
+However for this equation to be valid, we need the dimension of the embedding to be at least the number of unique points in the scene.
+Picking the correct number is difficult a-priori, and is a problem with all cycle consistency based methods.
+Here we use the ground truth dimension of the embedding to test our method and the baselines.
 Thus our loss would be 
@@
 One of the main advantages of this approach over more traditional optimization based approaches is the ability to add geometric side information into the loss at training time, even if it is not available at test time.
-The simplest way to add this, and the approach we use here, is using the epipolar constraint.
+The simplest way to add geometric side losses, and the approach we use here, is to use the epipolar constraint.
 The epipolar constraint describes how the positions of features in different images corresponding to the same point should be related.
@@
 % Where the $(R_k, T_k)$ are the poses of cameras $i$ and $j$ respectively.
-This assumes that the $X_k$ are calibrated i.e. the camera intrinsics are known. 
+The constraint assumes that the $X_k$ are calibrated i.e. the camera intrinsics are known. 
 Given the matrix of correspondences between camera $i$ and $j$, $\mat{M}_{ij}$, we can formulate this as a loss:
@@
 Where $c(i)$ is the appropriate camera for point index $i$.
-While this is all we use in this work, in principle you could use higher order constraints such as the trifocal tensor as additional loss terms.
+In future work we will invistigate using higher order constraints, such as the trifocal tensor as additional loss terms.
 
@@
   % \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
-  \includegraphics[width=0.8\linewidth]{figures/TrainingCurves.pdf}
+  \includegraphics[width=0.8\linewidth]{figures/TrainingCurvesFull.pdf}
   \end{center}

### 2018-11-14 cvpr2019/main.tex
More tex edits - from Alex

@@
 \begin{abstract}
-   In this work we formulate the multi-image matching problem as a graph embedding problem then use a Graph Neural Network to learn an appropriate embedding function for aligning image features.
-   Since ground truth correspondence is difficult or expensive to come by in many real world datasets, we use cycle consistency to train our network in an unsupervised fashion.
-   Additional geometric side losses can be added if the information is available in the training set for better test performance.
+   In this work, we formulate the multi-image matching problem as a graph embedding problem then use a Graph Neural Network to learn an appropriate embedding function for aligning image features.
+   We use cycle consistency to train our network in an unsupervised fashion since ground truth correspondence is difficult or expensive to come by in many real world datasets, although geometric side losses can be added if the information is available in the training set for better test performance.
    To the best of our knowledge, no other works have used learning for multi-image feature matching.
@@
 The goal in multi-image feature matching is to take 2D image locations from three or more images and find which ones correspond to the same point in the 3D scene.
-Methods such as SIFT feature matching \cite{lowe2004distinctive} and RANSAC \cite{fischler1981random} have been standard for solving this for decades now.
+Methods such as SIFT feature matching \cite{lowe2004distinctive} and RANSAC \cite{fischler1981random} have been standard for solving this for decades.
 However we still have not fully answered the question: What are the best image features to describe multiple views of the same scene?
 
-Recently deep learning has revolutionized how image features are computed \cite{yi2016lift}. 
-We would like to leverage this to compute better scene features.
+Deep learning has revolutionized how image features are computed \cite{yi2016lift}, and so we would like to leverage this to compute better scene features.
 Typically when applied to this area, deep neural networks (DNNs) are trained with photometric losses, directly using pixel color values.
-Using pixel values directly is not that robust due to the many confounding factors in the environment, such as lighting and view-point changes.
-Extracting features from the image is more robust to these confounding factors.
-Can we learn using multi-view constraints directly?
+However, using pixel values directly has trouble dealing with the many confounding factors in the environment, such as lighting and view-point changes.
+% Extracting features from the image is more robust to these confounding factors because in can explicitly compute 
+Using features designed to deal with these condfounding factors improves robustness to them, 
+and using learning could help improve the robustness even further.
 
@@
     Example of multi-image matching, with images from Rome16K dataset \cite{li2010location}.
-    In this example, an error in matching leads to an inconsistent cycle. 
-    Ideally these pairwise matches would be consistent 
+    In this example, an error in matching leads to an inconsistent cycle, ideally these pairwise matches would be consistent.
     In this work, we show how to learn this multi-view matching problem using cycle consistency.
@@
 \item We use the unsupervised cycle consistency loss to train a network to solve the multi-image matching problem
-\item We show the effectiveness of geometric side losses in training the network
+\item We peform experiments to demonstrate the effectiveness of geometric side losses in training the network
 \item We perform experiments on the Rome16K \cite{li2010location} dataset to test the effectiveness of our method compared to the optimization based baselines
@@
 Matching has a rich history of research in computer vision.
-The most well known and widely used method for image matching is that of RANSAC \cite{fischler1981random}.
-RANSAC combined with hand-crafted feature descriptors like SIFT \cite{lowe2004distinctive}, SURF \cite{bay2006surf}, BRIEF \cite{calonder2012brief}, or ORB \cite{mur2015orb} has constituted the bulk of the matching literature for the last 40 years.
+The most well known and widely used method for image matching is RANSAC \cite{fischler1981random}.
+RANSAC, combined with hand-crafted feature descriptors like SIFT \cite{lowe2004distinctive}, SURF \cite{bay2006surf}, BRIEF \cite{calonder2012brief}, or ORB \cite{mur2015orb}, has constituted the bulk of the matching literature for the last 40 years.
 To improve matching of all the features of the image, graph matching \cite{suh2015subgraph, hu2016distributable} can also be used for more robust matching.
 
-Multi-image matching has traditionally been done using optimization based methods minimizing a cycle consistency based loss (see Section 3.3) such as \cite{pachauri2013solving,zhou2015multi,arrigoni2017synchronization} and \cite{wang2017multi}.
-\cite{pachauri2013solving} and \cite{arrigoni2017synchronization} use the eigenvectors of the matching matrix to obtain a low dimensional embedding. 
+Multi-image matching has traditionally been done using optimization based methods minimizing a cycle consistency based loss (see Section 3.3).
+Pachauri et al. \cite{pachauri2013solving} and Arrigoni et al. \cite{arrigoni2017synchronization} use the eigenvectors of the matching matrix to obtain a low dimensional embedding. 
 Thus they are robust to small Gaussian noise but not to stronger noise.
-\cite{zhou2015multi} and \cite{wang2017multi} use most sophisticated optimization techniques on the matching matrix and thus are quite robust.
-However, they use a centralized scheme and thus are not appropriate in a distributed setting, as done in \cite{leonardos2016distributed}.
-There are also density based optimization techniques to compute multi-image correspondence, such as in \cite{tron2017fast}.
+Zhou et al. \cite{zhou2015multi} and Wang et al. \cite{wang2017multi} use most sophisticated optimization techniques on the matching matrix and thus are quite robust.
+However, they use a centralized scheme and thus are not appropriate in a distributed setting, as done in Leonardos et al. \cite{leonardos2016distributed}.
+There are also density based optimization techniques to compute multi-image correspondence, such as in Tron et al. \cite{tron2017fast}.
 
@@
 This approach is limited if you do not have the ability to get the ground truth correspondences.
-There are other methods to build correspondences \cite{choy2016universal}, but it only handles two-view constraints and requires dense correspondences.
-Most similar to ours, \cite{yi2018learning} attempts to improve correspondences by learning match probabilites for RANSAC to speed up test time running.
+There are other methods to build correspondences such as Choy et al. \cite{choy2016universal}, but it only handles two-view constraints and requires dense correspondences.
+Most similar to ours, Yi et al. \cite{yi2018learning} attempts to improve correspondences by learning match probabilites for RANSAC to speed up test time running.
 However, they only focus on two view tests and do not exploit the advantages of the correspondence structure.
@@
 Graph neural networks have been getting more attention recently \cite{bronstein2017geometric, bruna2013spectral, defferrard2016convolutional, kipf2016semi, scarselli2009graph, gama2018mimo, gama2018convolutional, battaglia2018relational}.
-Classical so-called Spectral methods used the eigenvectors of graph Laplacian to compute convolutions \cite{bronstein2017geometric}, but requires a fixed graph structure known a-priori.  
+Classical so-called Spectral methods used the eigenvectors of graph Laplacian to compute convolutions like in Bruna et al.
+\cite{bruna2013spectral}, but requires a fixed graph structure known a-priori.
 Non-spectral methods do not require a-priori knowledge \cite{bronstein2017geometric, kipf2016semi, scarselli2009graph, gama2018convolutional}.
 Most of these simply use polynomials of the graph Laplacian to compute neighborhood averages.
-\cite{gama2018mimo} and \cite{gama2018convolutional} formalize this notion and generalize it beyond the use of the graph Laplacian.
-More sophisticated aggregation techniques and global information passing can also be used as discussed in \cite{battaglia2018relational}.
+Gama et al.
+2018 \cite{gama2018mimo, gama2018convolutional} formalize this notion and generalize it beyond the use of the graph Laplacian.
+More sophisticated aggregation techniques and global information passing can also be used as discussed in Battaglia et al. \cite{battaglia2018relational}.
 
@@
     An outline of the pipeline of this work.
-    The graph of matches is put to a Graph Convolutional Neural Network (GCN) \cite{kipf2016semi} then creates a low rank embedding of the Adjacency Matrix of the graph.
+    The graph of matches is put into a Graph Convolutional Neural Network (GCN) \cite{kipf2016semi} and then outputs a low rank embedding of the Adjacency Matrix of the graph.
     The GCN operates on an embedding over the nodes the graph.
-    The colors on the nodes of the graph in the GCN represent the values of the embedding.
+    In the figure, the colors on the nodes of the graph in the GCN represent the values of the embedding.
     The final embedding is used to construct a pairwise similarity matrix, which ideally should be a low dimensional cycle consistent representation of the graph adjacency matrix.
@@
 \section{Method}
-Our goal is to learn optimal features that capture multiple image views.
+Our goal is to learn optimal features that capture multiple image views by way of filtering out noisy feature matches.
+The input to our algorithm is a set of features and noisy correspondences, and the output is a new set of features where the pairwise similarities of these features correspond to the true matches.
+We do this by learning training the new set of feature embeddings to be cycle consistent.
 We formulate this problem in terms of the correspondence graph of the features.
-We denote vectors $\mat{x}$ and matrices $\mat{A}$ with boldface.
-We denote the $i^{th}$ row of a matrix $(\mat{A})_i$.
+Vectors $\mat{x}$ and matrices $\mat{A}$ are denoted with boldface, and the $i^{th}$ row of a matrix is denoted $(\mat{A})_i$.
 \subsection{Correspondence Graph}
@@
 
-However, this graph structure does not have the properties of a Eulcidean domain.
-Thus we cannot use standard CNNs to learn features for this task.
-Thus we need to use graph convolutions to learn feature representations on this space, which we explore in this next section.
+However, this graph structure does not have a regular grid structure and thus we cannot use standard CNNs to learn features for this task.
+Therefore we need to use graph convolutions to learn feature representations on this space, which we explore in this next section.
 
@@
 Many older methods assume $\mat{L}$ is known a-priori \cite{bruna2013spectral}, and thus can encode graph convolutions using the eigenvectors of $L$.
-We do not have this luxery, and thus we use more modern non-spectral methods GNNs:
+We do not have this luxury, and thus we use more modern non-spectral methods GNNs:
 \begin{equation}
@@
 \end{equation}
-The degree of the polynomial determines the number of hops away from a node one layer can access.
+The maximum degree of $\mat{L}$ determines the number of hops away from a node one layer can access.
 Here $\sigma$ is the non-linearity (typically a ReLU), $\mat{W}_{k,i}$ are the learned weights of layer $i$,  and $P$ is the `pooling' operation, known as graph coarsening \cite{bronstein2017geometric, gama2018mimo}.
@@
 Therefore we cannot perform graph coarsening, and thus we only perform the non-linearity step.
-We instead use a modification of the approach in \cite{kipf2016semi}:
+We instead use a modification of the approach in Kipf and Welling \cite{kipf2016semi}:
 \begin{align}
@@
 \subsection{Cycle Consistency}
+Let $\mat{M}$ be the noiseless set of matches between our features, with $\mat{M}_{ij}$ being the matches between image $i$ and image $j$.
 If the pairwise matches are globally consistent, then we can say that, for all $i, j, k$:
@@
 In other words, the matches between two images stays the same no matter what path is taken to get there. 
-This constraint is known as \textit{cycle concistency}, and has been used in a number of recent works to optimize for global consistency \cite{zhou2015multi, wang2017multi, leonardos2016distributed}.
+This constraint is known as \textit{cycle concistency}, and has been used in a number of works to optimize for global consistency \cite{zhou2015multi, wang2017multi, leonardos2016distributed}.
 Stated in this form, there are $O(n^3)$ cycle consistency constraints to check.
 A more elegant way to represent cycle consistency is to first create a `universe' of features that all images match to.
-Then one can match the $i^{th}$ set of features to the universe, denoted $\mat{X}_i$.
+Then, one can match the $i^{th}$ set of features to the universe using a matrix $\mat{X}_i$.
 Then the cycle consistency becomes:
@@
 
-% In our case, we try to learn embeddings $\mat{E}$ that map to the $\mat{X}_i$ - learn the universe of features via our embeddings.
 We try to learn $\mat{E}$ to approximate $\mat{X}$ - in other words the final embedding should be an encoding of the universe of features.
-However for this equation to be valid, we need the dimension of the embedding to be at least the number of unique points in the scene.
-Picking the correct number is difficult a-priori, and is a problem with all cycle consistency based methods.
-Here we use the ground truth dimension of the embedding to test our method and the baselines.
+As we do not have the ground truth matches $\mat{M}$, we approximate it using the noisy adjacency matrix $\mat{A}$ of our correspondence graph.
 Thus our loss would be
@@
 Here $\mathcal{D}$ could be an $L_2$ loss, $L_1$ loss, or many others.
-Another way of viewing this is that features $i$ and $j$ match with probability $(\mat{E}_n)_i \cdot (\mat{E}_n)_j$ which is proporitional to $\mat{A}_{ij}$.
 
@@
   \caption{
-    Illustration of the Geometric loss.
+    Illustrated here is an example of how the geometric loss on one feature.  
     We compute the errors on each feature match to determine their validity.
-    Errors are computed via absolute distance from the epipolar line, as expressed by equation \ref{eq:essential_constraint} via the epipolar constraint.
+    Errors are computed via absolute distance from the epipolar line, as expressed by (\ref{eq:essential_constraint}) via the epipolar constraint.
   }
@@
 The constraint assumes that the $X_k$ are calibrated i.e. the camera intrinsics are known. 
-Given the matrix of correspondences between camera $i$ and $j$, $\mat{M}_{ij}$, we can formulate this as a loss:
+Given the matrix of ground truth correspondences $\mat{M}_{ij}$ between camera $i$ and $j$, we can formulate this as a loss:
 \begin{equation}
@@
 \end{equation}
-For our purposes, since we use low rank embeddings of the $\mat{M}_{ij}$, the loss would look like:
+For our purposes, since we use low rank embeddings $\mat{E}_{i}$, $\mat{E}_{j}$, the loss would look like:
 \begin{align}
@@
 Where $c(i)$ is the appropriate camera for point index $i$.
-In future work we will invistigate using higher order constraints, such as the trifocal tensor as additional loss terms.
+In future work we will invistigate using higher order constraints, such as the trifocal tensor, as additional loss terms.
 
@@
       Training curves with and without Geometric Training loss.
-      The training loss dramatically improves training time and performance.
+      The geometric training loss improves testing performance.
       Shown as horizontal lines are the state of the art optimization based baselines.
       Even with a simple network we compare well with them.
-      NOTE TO READERS: This figure needs to be cleaned up.
     }
@@
 \caption{
-Results on Rome16k Correspondence graphs.
+Results on Synthetic correspondence graphs.
+The `Same Point Similarities' column is the mean and standard deviation of similarities for true corresponding points, while the `Different Point Similarities' is the same for points that do not correspond.
+For the `Same Point Similarities' column higher is better, and for `Different Point Similarities' lower is better.
 Losses tested against ground truth correspondence graph adjacency matrices.
-Our method was not trained on ground truth corresopndences but on unsupervised methods.
+Our method was not trained on ground truth correspondences but using unsupervised methods.
 }
@@
 \subsection{Synthetic Graph Dataset}
-We test our method on synthetically generated data as a simple proof of concept.
+We first test our method on synthetically generated data as a simple proof of concept.
 To generate the data, we generate $p$ points, each with its own randomly generated descriptor.
-To create the graph, we generate random permutation matrices, with a noise applied to it after it is generated.
-The initial descriptors we created using the true descriptor plus some added noise.
+To create the graph, we generate random permutation matrices, with a noise applied to it after generated.
+The initial descriptors we use as input we created using the true descriptor plus some added Gaussian noise.
 No geometric losses were added during training for these experiments.
-Testing with different noise functions and parameters.
+The method was robust in testing with different noise functions and parameters.
 All experiments were run with a 12 layer GCN with the ReLU nonlinearity and skip connections between the first layer and the 6th and 12th layers.
@@
 \subsection{Rome 16K Graph Dataset}
-% Filler for now.
-% TODO: Actually run tests on all these with different loss functions
 We  use the Rome16K dataset \cite{li2010location} to test our algorithm in real world settings.
-We extract image triplets, quadtruplets, and quintuplets with overlap of 80 points or more to test our algorithm on.
+We extract image triplets and quadtruplets with overlap of 80 points or more to test our algorithm on.
 For the normal datasets, we extracted 80 points established as corresponding in the bundle adjument given in the Rome16K dataset.
-For the outlier datasets, we take 79 correspondences and 1 non-corresponding point in each image.
+For the initial embedding we use the original 128 dimensional SIFT descriptors, normalized to have $L_2$ norm 1.
+We also include the calibrated x-y position and the orientation and log scale of the SIFT feature.
+% For the outlier datasets, we take 79 correspondences and 1 non-corresponding point in each image.
 
@@
 We forgo this as our method was trained to output soft labels - we also in turn make the labels soft for the optimization based methods.
+For this method to work, we need the dimension of the embedding to be at least the number of unique points in the scene.
+Picking the correct number is difficult a-priori, and is a problem with all cycle consistency based methods.
+Here we use the ground truth dimension of the embedding to test both our method and the baselines.
 We also include ablation studies on various geometric loss functions for the geometric side information.
@@
 % leaderConsensus.m  MatchALSTestErrors.txt  mmatch_CVX_ALS.m  mmatch_QP_PG.m  mmatch_spectral.m  PGDDS.m  PGDDSTestErrors.txt  print_errors.py  run_tests.m  SpectralTestErrors.txt
+% Spectral                                  & 5.368e-2 $\pm$ 5.274e-3 & 1.754e-2 $\pm$ 3.688e-3 & 1.143e-1 $\pm$ 2.774e-2 \\ \hline
+% MatchALS                                  & 6.715e-3 $\pm$ 3.035e-3 & 6.696e-3 $\pm$ 3.035e-3 & 2.254e-1 $\pm$ 1.043e-1 \\ \hline
+% PGDDS                                     & 1.311e-2 $\pm$ 2.186e-3 & 4.730e-3 $\pm$ 1.886e-3 & 3.872e-2 $\pm$ 3.869e-2 \\ \hline
 
@@
 \hline\hline\hline
-Spectral                                  & 5.368e-2 $\pm$ 5.274e-3 & 1.754e-2 $\pm$ 3.688e-3 & 1.143e-1 $\pm$ 2.774e-2 \\ \hline
-MatchALS                                  & 6.715e-3 $\pm$ 3.035e-3 & 6.696e-3 $\pm$ 3.035e-3 & 2.254e-1 $\pm$ 1.043e-1 \\ \hline
-PGDDS                                     & 1.311e-2 $\pm$ 2.186e-3 & 4.730e-3 $\pm$ 1.886e-3 & 3.872e-2 $\pm$ 3.869e-2 \\ \hline
+MatchALS 15 Iterations                    & 5.217e-2 $\pm$ 2.588e-3 & 1.018e-2 $\pm$ 1.759e-3 & 1.067e-1 $\pm$ 3.801e-2 \\ \hline
+MatchALS 100 Iterations                   & 2.948e-2 $\pm$ 2.287e-2 & 8.446e-3 $\pm$ 3.030e-3 & 1.633e-1 $\pm$ 9.376e-2 \\ \hline
+MatchALS 400 Iterations                   & 2.189e-2 $\pm$ 2.161e-2 & 7.860e-3 $\pm$ 3.144e-3 & 1.839e-1 $\pm$ 1.017e-1 \\ \hline
+PGDDS 15 Iterations                       & 2.029e-2 $\pm$ 1.894e-2 & 7.485e-3 $\pm$ 2.899e-3 & 1.491e-1 $\pm$ 1.083e-1 \\ \hline
+PGDDS 100 Iterations                      & 1.888e-2 $\pm$ 1.720e-2 & 6.948e-3 $\pm$ 2.928e-3 & 1.271e-1 $\pm$ 1.078e-1 \\ \hline
+PGDDS 200 Iterations                      & 1.791e-2 $\pm$ 1.588e-2 & 6.579e-3 $\pm$ 2.902e-3 & 1.123e-1 $\pm$ 1.050e-1 \\ \hline
+Spectral                                  & 2.302e-2 $\pm$ 1.941e-2 & 8.144e-3 $\pm$ 4.886e-3 & 1.126e-1 $\pm$ 9.777e-2 \\ \hline
 GNN, 12 Layers, w/o Geometric Side Losses & 1.000e-3 & 1.000e-3 & 1.000e-3 \\ \hline

### 2018-11-14 cvpr2019/main.tex
Best viewed in color
Added new figure and a few more cleanups

@@
     In this work, we show how to learn this multi-view matching problem using cycle consistency.
+    Best viewed in color.
   }
@@
     In addition we can use geometric information at to assist training the network, even if we do not have that geometric information at testing time such as epipolar constraints on the point locations or higher order geometric constraints.
+    Best viewed in color.
   }
@@
 Many older methods assume $\mat{L}$ is known a-priori \cite{bruna2013spectral}, and thus can encode graph convolutions using the eigenvectors of $L$.
-We do not have this luxury, and thus we use more modern non-spectral methods GNNs:
+We do not have this luxury, and thus we use non-spectral GNNs:
 \begin{equation}
@@
 \subsection{Cycle Consistency}
+
+\begin{figure}[t]
+\begin{center}
+  \includegraphics[width=0.9\linewidth]{figures/UniverseOfFeatures.pdf}
+\end{center}
+  \caption{
+    Illustration of the universe of features.
+    Each feature in each image corresponds to a 3D point in the scene.
+    Therefore, we can get the points to have a cycle consistent embedding by mapping each feature in each image to the one-hot vector of its corresponding 3D point.
+    While there can be many features, there are much fewer 3D points and thus this corrsponds to a low rank factorization of the corrspondence matrix.
+    Best viewed in color.
+  }
+\label{fig:universefeatures}
+\label{fig:onecol}
+\end{figure}
+
 Let $\mat{M}$ be the noiseless set of matches between our features, with $\mat{M}_{ij}$ being the matches between image $i$ and image $j$.
@@
 Stated in this form, there are $O(n^3)$ cycle consistency constraints to check.
-A more elegant way to represent cycle consistency is to first create a `universe' of features that all images match to.
+A more elegant way to represent cycle consistency is to first create a `universe' of features that all images match to (see figure \ref{fig:universefeatures}).
 Then, one can match the $i^{th}$ set of features to the universe using a matrix $\mat{X}_i$.
@@
 
+\subsection{Geometric Side Information}
+
 \begin{figure}[t]
@@
     Errors are computed via absolute distance from the epipolar line, as expressed by (\ref{eq:essential_constraint}) via the epipolar constraint.
+    Best viewed in color.
   }
@@
 
-\subsection{Geometric Side Information}
 One of the main advantages of this approach over more traditional optimization based approaches is the ability to add geometric side information into the loss at training time, even if it is not available at test time.

### 2018-11-14 data_util/real_dataset.py
Fixed up the number issue and normalization issues with rome16k 4-tuple data generation

@@ -44,6 +44,24 @@ class Rome16KTupleDataset(parent_dataset.GraphSimDataset):
   def tuples_fname(self, bundle_file):
     return os.path.join(self.rome16k_dir, 'scenes', parse.tuples_fname(bundle_file))
 
+  def get_tuples(self, bundle_file):
+    tuples_fname = self.tuples_fname(bundle_file)
+    with open(tuples_fname, 'rb') as f:
+      tuples_all = pickle.load(f)
+    if self.tuple_size == 3:
+      tuples = tuples_all[1]
+    else:
+      tuples_sel = tuples_all[self.tuple_size-2]
+      n_select = int(1.5*len(tuples_all[1])) # TODO: Make this less hacky??
+      if n_select > len(tuples_sel):
+        tuples = tuples_all[self.tuple_size-2]
+      else:
+        tuples = np.array(tuples_sel)
+        tuples_idx = np.random.choice(np.arange(len(tuples)),
+                                      size=n_select, replace=False)
+        tuples = np.sort(tuples[np.sort(tuples_idx)]).tolist()
+    return tuples
+
   def convert_dataset(self, out_dir, mode):
     """Writes synthetic flow data in .mat format to a TF record file."""
     params = self.dataset_params
@@ -63,23 +81,7 @@ class Rome16KTupleDataset(parent_dataset.GraphSimDataset):
       scene_name = self.scene_fname(bundle_file)
       np.random.seed(hash(scene_name) % 2**32)
       scene = parse.load_scene(scene_name)
-      tuples_fname = self.tuples_fname(bundle_file)
-      with open(tuples_fname, 'rb') as f:
-        tuples_all = pickle.load(f)
-        if self.tuple_size == 3:
-          tuples = tuples_all[1]
-        else:
-          tuples_sel = tuples_all[self.tuple_size-2]
-          n_select = int(1.5*len(tuples_all[1])) # TODO: Make this less hacky??
-          if n_select > len(tuples_sel):
-            tuples = tuples_all[self.tuple_size-2]
-          else:
-            tuples = np.array(tuples_sel)
-            tuples_idx = np.random.choice(np.arange(len(tuples)),
-                                          size=n_select, replace=False)
-            tuples = np.sort(tuples[np.sort(tuples_idx)]).tolist()
-
-      for tupl in tuples:
[…]

### 2018-11-15 options.py
Added nicer tensorboard outputs

@@ -114,7 +114,11 @@ def get_opts():
   parser.add_argument('--use_end_bias',
                       default=False,
                       type=myutils.str2bool,
-                      help='NOT IMPLEMENTED YET: Use bias in dot product')
+                      help='Use bias in dot product')
+  parser.add_argument('--reconstruction_loss',
+                      default=1.0,
+                      type=float,
+                      help='Use true adjacency or noisy one in loss')
   parser.add_argument('--geometric_loss',
                       default=-1,
                       type=float,

### 2018-11-16 cvpr2019/main.tex
Updated figures more and added a few more things to tex file

@@
 %\ifcvprfinal\pagestyle{empty}\fi
-\setcounter{page}{4321}
+\setcounter{page}{1}
 \begin{document}
@@
 \begin{abstract}
+    Image feature matching is a fundametal part of many geometric computer vision applications, and using multiple images can improve performance.
     In this work, we formulate the multi-image matching problem as a graph embedding problem then use a Graph Neural Network to learn an appropriate embedding function for aligning image features.
-   We use cycle consistency to train our network in an unsupervised fashion since ground truth correspondence is difficult or expensive to come by in many real world datasets, although geometric side losses can be added if the information is available in the training set for better test performance.
+% How to talk about the universe of features here without going too much into the weeds??
+    We use cycle consistency to train our network in an unsupervised fashion since ground truth correspondence is difficult or expensive to come by in many real world datasets.
+    In addtion, geometric consistency losses can be added at train time, even if the information is not available in the test set, unlike previous optimization based methods.
     To the best of our knowledge, no other works have used learning for multi-image feature matching.
@@
 Methods such as SIFT feature matching \cite{lowe2004distinctive} and RANSAC \cite{fischler1981random} have been standard for solving this for decades.
-However we still have not fully answered the question: What are the best image features to describe multiple views of the same scene?
+However RANSAC-based approaches are limited for matching pairs of images.
+Other works, such as Wang et al. \cite{wang2017multi}, have shown improvement in performance by enforcing consistency between multiple images.
+% However we still have not fully answered the question: What are the best image features to describe multiple views of the same scene?
 
 Deep learning has revolutionized how image features are computed \cite{yi2016lift}, and so we would like to leverage this to compute better scene features.
-Typically when applied to this area, deep neural networks (DNNs) are trained with photometric losses, directly using pixel color values.
-However, using pixel values directly has trouble dealing with the many confounding factors in the environment, such as lighting and view-point changes.
-% Extracting features from the image is more robust to these confounding factors because in can explicitly compute 
+Typically when applied to image or feature matching, deep neural networks (DNNs) are trained with photometric losses, directly using pixel color values.
+However direct, pixel-based losses have are not robust to the many confounding factors in the environment, such as lighting and view-point changes.
 Using features designed to deal with these condfounding factors improves robustness to them, 
-and using learning could help improve the robustness even further.
+and learning may improve robustness even further.
 
-% Photometric losses make the brightness constancy assumption, which is not as robust as feature matching.
 \begin{figure}[t]
@@
     Example of multi-image matching, with images from Rome16K dataset \cite{li2010location}.
-    In this example, an error in matching leads to an inconsistent cycle, ideally these pairwise matches would be consistent.
-    In this work, we show how to learn this multi-view matching problem using cycle consistency.
-    Best viewed in color.
+    In this example, an error in matching leads to an inconsistent cycle (shown in red), ideally these pairwise matches would be consistent.
+    We improve consistency between pairwise matches in the multi-view matching problem by training a neural net with cycle consistency.
   }
@@
 In the case of multi-image feature matching, one would need to hand label point correspondences between images, which is difficult and expensive to obtain.
-Multi-view constraints are formulated in terms of sparse features, thus traditional convolutional deep neural nets (CNNs) are not designed to handle such input.
+Multi-view constraints are formulated in terms of sparse features, which traditional convolutional deep neural nets (CNNs) are not designed to handle such input.
 In the case of multi-image feature matching, geometric constraints would be helpful in rejecting outlier matches.
@@
 In this work, we propose to solve these problems using a Graph Neural Network (GNN) to operate on the correspondence graph.
-The proposed method works on the correspondence graph, which is agnostic to how the correspondnces were computed.
+The proposed method works on the correspondence graph, which is agnostic to how the correspondnces were computed, thus allowing the algorithm to work in a broad class of environments.
 
 We use a unsupervised loss, the cycle consistency loss, to train the network.
-We also add in side geometric losses to help training, which works even when the geometric information is not available at test time.
+We add in geometric consistency losses to help training, which works even when the geometric information is not available at test time.
 Our contributions are:
 \begin{itemize}
-\item We use novel architecture to solve multi-image feature matching problem using GNNs with graph embeddings
-\item We use the unsupervised cycle consistency loss to train a network to solve the multi-image matching problem
-\item We peform experiments to demonstrate the effectiveness of geometric side losses in training the network
-\item We perform experiments on the Rome16K \cite{li2010location} dataset to test the effectiveness of our method compared to the optimization based baselines
+\item We use a novel architecture to address multi-image feature matching problem using GNNs with graph embeddings.
+\item We introduce an unsupervised cycle consistency loss that does not require labelled correspondences to train.
+\item We demonstrate the effectiveness of geometric consistency losses in improving training.
+\item We perform experiments on the Rome16K \cite{li2010location} dataset to test the effectiveness of our method compared to optimization based baselines.
 \end{itemize}
@@
 RANSAC, combined with hand-crafted feature descriptors like SIFT \cite{lowe2004distinctive}, SURF \cite{bay2006surf}, BRIEF \cite{calonder2012brief}, or ORB \cite{mur2015orb}, has constituted the bulk of the matching literature for the last 40 years.
-To improve matching of all the features of the image, graph matching \cite{suh2015subgraph, hu2016distributable} can also be used for more robust matching.
+To improve matching of all the features of the image, graph matching \cite{suh2015subgraph, hu2016distributable} can be used for more robust matches.
 
@@
 Pachauri et al. \cite{pachauri2013solving} and Arrigoni et al. \cite{arrigoni2017synchronization} use the eigenvectors of the matching matrix to obtain a low dimensional embedding. 
-Thus they are robust to small Gaussian noise but not to stronger noise.
+Thus they are robust to small Gaussian noise but not to more realistic noise.
 Zhou et al. \cite{zhou2015multi} and Wang et al. \cite{wang2017multi} use most sophisticated optimization techniques on the matching matrix and thus are quite robust.
-However, they use a centralized scheme and thus are not appropriate in a distributed setting, as done in Leonardos et al. \cite{leonardos2016distributed}.
-There are also density based optimization techniques to compute multi-image correspondence, such as in Tron et al. \cite{tron2017fast}.
+Leonardos et al. \cite{leonardos2016distributed} implement a distributed optimizaiton scheme to solve for cycle consistency.
+As an alternative to optimization based techiniques, Tron et al. \cite{tron2017fast} used density based clustering techniques to compute multi-image correspondence.
 
@@
 2018 \cite{gama2018mimo, gama2018convolutional} formalize this notion and generalize it beyond the use of the graph Laplacian.
-More sophisticated aggregation techniques and global information passing can also be used as discussed in Battaglia et al. \cite{battaglia2018relational}.
+To improve performance, more sophisticated aggregation techniques and global information passing can be used as discussed in Battaglia et al. \cite{battaglia2018relational}.
 
@@
     An outline of the pipeline of this work.
-    The graph of matches is put into a Graph Convolutional Neural Network (GCN) \cite{kipf2016semi} and then outputs a low rank embedding of the Adjacency Matrix of the graph.
-    The GCN operates on an embedding over the nodes the graph.
-    In the figure, the colors on the nodes of the graph in the GCN represent the values of the embedding.
+    The Graph Convolutional Neural Network (GCN) \cite{kipf2016semi} takes as input the graph of matches and then outputs a low rank embedding of the adjacency matrix of the graph.
+    The GCN operates on an embedding over the nodes of the graph.
+    In the figure, the the GCN node embeddings are represented by different colors.
     The final embedding is used to construct a pairwise similarity matrix, which ideally should be a low dimensional cycle consistent representation of the graph adjacency matrix.
     We train the network using a reconstruction loss on the similarity matrix.
-    In addition we can use geometric information at to assist training the network, even if we do not have that geometric information at testing time such as epipolar constraints on the point locations or higher order geometric constraints.
-    Best viewed in color.
+    In addition, we can use geometric information at to assist training the network, even if we do not have that geometric information at testing time such as epipolar constraints on the point locations or higher order geometric constraints.
   }
@@
 Each vertex $v$ of the graph is a feature with its associated descriptor $f_v$. 
-The graph is represented by its Weighted Adjacency Matrix $\mat{A}(\mathcal{G}) \in \bR^{n \times n}$ and its positive diagonal degree matrix $\mat{D}(\mathcal{G}) \in \bR^{n \times n}$ (denoted $\mat{A}$ and $\mat{D}$ for brevity).
+The graph is represented by its Weighted Adjacency Matrix $\mat{A}(\mathcal{G}) \in \bR^{n \times n}$, where $(\mat{A}(\mathcal{G}))_{ij}$ is the strength of the match between nodes $i$ and $j$.
+We also have the positive diagonal degree matrix $\mat{D}(\mathcal{G}) \in \bR^{n \times n}$, with $\mat{D}(\mathcal{G})_{ii} = \sum_j (\mat{A}(\mathcal{G}))_{ij}$.
+For brevity we denote these matrices $\mat{A}$ and $\mat{D}$ respectively.
 We can get our an embedding matrix $\mat{E}_0$ by concatenating the features $f_v$ from each of the vertices.
-We use $\mat{E}_0$ as our initializiation for our learning algorithm.
-We can also add any additional knowledge we have into the embedding (e.g. scale, orientation, etc.).
+We use $\mat{E}_0$ as the initializiation for our learning algorithm.
+We add any additional knowledge we have into the embedding as well (e.g. scale, orientation, etc.).
 Putative correspondences are computed from these features and represented by weighted edges in which the weight gives the strength of the match.
@@
 However, this graph structure does not have a regular grid structure and thus we cannot use standard CNNs to learn features for this task.
-Therefore we need to use graph convolutions to learn feature representations on this space, which we explore in this next section.
+Instead we use graph convolutions to learn feature representations on this space.
+We describe our approach in the next section.
 
@@
 Many older methods assume $\mat{L}$ is known a-priori \cite{bruna2013spectral}, and thus can encode graph convolutions using the eigenvectors of $L$.
-We do not have this luxury, and thus we use non-spectral GNNs:
+We do not have this luxury, as the correspondence structure changes from image to image, and thus we use non-spectral GNNs. The standard form of non-spectral GNNs is:
 \begin{equation}
@@
 \end{equation}
+Here $\sigma$ is the non-linearity (typically a ReLU), $\mat{W}_{k,i}$ are the learned weights of layer $i$,  and $P$ is the `pooling' operation, known as graph coarsening \cite{bronstein2017geometric, gama2018mimo}.
 The maximum degree of $\mat{L}$ determines the number of hops away from a node one layer can access.
-Here $\sigma$ is the non-linearity (typically a ReLU), $\mat{W}_{k,i}$ are the learned weights of layer $i$,  and $P$ is the `pooling' operation, known as graph coarsening \cite{bronstein2017geometric, gama2018mimo}.
 In the feature matching problem, we require an embedding for each vertex.
 Therefore we cannot perform graph coarsening, and thus we only perform the non-linearity step.
-We instead use a modification of the approach in Kipf and Welling \cite{kipf2016semi}:
+We instead use a modification of the approach proposed in Kipf and Welling \cite{kipf2016semi}:
 \begin{align}
@@
 
+This reduces our complexity from $O(n^3)$ to $O(n^2)$.
 We try to learn $\mat{E}$ to approximate $\mat{X}$ - in other words the final embedding should be an encoding of the universe of features.
@@
 \end{equation}
-Here $\mathcal{D}$ could be an $L_2$ loss, $L_1$ loss, or many others.
+Here $\mathcal{D}$ could be an $L_2$ loss, $L_1$ loss, or many others. In this work, we use the $L_1$ loss.
 
-\subsection{Geometric Side Information}
+\subsection{Geometric Consistency Loss}
 
@@
   }
-\label{fig:cycconsistex}
+\label{fig:geoconsist}
 \label{fig:onecol}
@@
 
-One of the main advantages of this approach over more traditional optimization based approaches is the ability to add geometric side information into the loss at training time, even if it is not available at test time.
-The simplest way to add geometric side losses, and the approach we use here, is to use the epipolar constraint.
+One of the main advantages of this approach over more traditional optimization based approaches is the ability to add geometric consistency information into the loss at training time, even if it is not available at test time.
+The simplest way to add geometric consistency losses, and the approach we use here, is to use the epipolar constraint.
 The epipolar constraint describes how the positions of features in different images corresponding to the same point should be related.
@@
 Where $c(i)$ is the appropriate camera for point index $i$.
-In future work we will invistigate using higher order constraints, such as the trifocal tensor, as additional loss terms.
 
@@
 }
+\label{fig:synthtable}
 \end{table*}
@@
 No geometric losses were added during training for these experiments.
-The method was robust in testing with different noise functions and parameters.
-All experiments were run with a 12 layer GCN with the ReLU nonlinearity and skip connections between the first layer and the 6th and 12th layers.
-All were trained with the Adam optimizer and a learning rate $10^{-4}$
+However, the method was robust in testing with different noise functions and parameters.
+The normalized noisy input descriptors are our baseline - they correlate with the true values but do not perserve the structure well.
+However, with the GNN we are able to recover the true structure very well, as shown in \ref{fig:synthtable}.
+All experiments were run with a 12 layer GCN with the ReLU nonlinearity and skip connections.
+All were trained with the Adam optimizer \cite{kingma2014adam} and a learning rate $10^{-4}$
 
@@
 We  use the Rome16K dataset \cite{li2010location} to test our algorithm in real world settings.
-We extract image triplets and quadtruplets with overlap of 80 points or more to test our algorithm on.
-For the normal datasets, we extracted 80 points established as corresponding in the bundle adjument given in the Rome16K dataset.
-For the initial embedding we use the original 128 dimensional SIFT descriptors, normalized to have $L_2$ norm 1.
-We also include the calibrated x-y position and the orientation and log scale of the SIFT feature.
+Rome16K consistes of 16 thousand images of various historical sites in Rome extracted from Flickr, along with the 3D structure of the sites provided by bundle adjustment.
+While not a standard dataset to test cycle consistency, other datasets had insufficient data to train a network on.
+Rome16K is typically used to test bundle adjustment methods.
+Therefore, to use for our method, we extract image triplets and quadtruplets with overlap of 80 points or more to test our algorithm on, with the points established as corresponding in the given bundle adjument output.
+For the initial embedding we use the original 128 dimensional SIFT descriptors, normalized to have $L_2$ norm 1, the calibrated x-y position, the orientation, and log scale of the SIFT feature.
 % For the outlier datasets, we take 79 correspondences and 1 non-corresponding point in each image.
 
-We test with various loss functions, specifcally $L_1$, $L_2$, and the binary cross entropy loss (BCE).
-We evaluate on a test set using the ground truth Adjacency matrix which we compute from the bundle adjustment given by the Rome16K dataset.
+For these experiments we train with the $L1$ norm, and ablate the geometric side losses.
+We evaluate on a test set using the ground truth adjacency matrix which we compute from the bundle adjustment given by the Rome16K dataset.
 Traditional methods of evaluation use Precision and Recall, after making the labels 0 or 1.
-We forgo this as our method was trained to output soft labels - we also in turn make the labels soft for the optimization based methods.
+We forgo this as our method was trained to output soft labels - we in turn make the labels soft for the optimization based methods.
 For this method to work, we need the dimension of the embedding to be at least the number of unique points in the scene.
@@
 Here we use the ground truth dimension of the embedding to test both our method and the baselines.
-We also include ablation studies on various geometric loss functions for the geometric side information.
-
-% leaderConsensus.m  MatchALSTestErrors.txt  mmatch_CVX_ALS.m  mmatch_QP_PG.m  mmatch_spectral.m  PGDDS.m  PGDDSTestErrors.txt  print_errors.py  run_tests.m  SpectralTestErrors.txt
-% Spectral                                  & 5.368e-2 $\pm$ 5.274e-3 & 1.754e-2 $\pm$ 3.688e-3 & 1.143e-1 $\pm$ 2.774e-2 \\ \hline
-% MatchALS                                  & 6.715e-3 $\pm$ 3.035e-3 & 6.696e-3 $\pm$ 3.035e-3 & 2.254e-1 $\pm$ 1.043e-1 \\ \hline
-% PGDDS                                     & 1.311e-2 $\pm$ 2.186e-3 & 4.730e-3 $\pm$ 1.886e-3 & 3.872e-2 $\pm$ 3.869e-2 \\ \hline
 
@@
 \hline\hline\hline
-MatchALS 15 Iterations                    & 5.217e-2 $\pm$ 2.588e-3 & 1.018e-2 $\pm$ 1.759e-3 & 1.067e-1 $\pm$ 3.801e-2 \\ \hline
-MatchALS 100 Iterations                   & 2.948e-2 $\pm$ 2.287e-2 & 8.446e-3 $\pm$ 3.030e-3 & 1.633e-1 $\pm$ 9.376e-2 \\ \hline
-MatchALS 400 Iterations                   & 2.189e-2 $\pm$ 2.161e-2 & 7.860e-3 $\pm$ 3.144e-3 & 1.839e-1 $\pm$ 1.017e-1 \\ \hline
-PGDDS 15 Iterations                       & 2.029e-2 $\pm$ 1.894e-2 & 7.485e-3 $\pm$ 2.899e-3 & 1.491e-1 $\pm$ 1.083e-1 \\ \hline
-PGDDS 100 Iterations                      & 1.888e-2 $\pm$ 1.720e-2 & 6.948e-3 $\pm$ 2.928e-3 & 1.271e-1 $\pm$ 1.078e-1 \\ \hline
-PGDDS 200 Iterations                      & 1.791e-2 $\pm$ 1.588e-2 & 6.579e-3 $\pm$ 2.902e-3 & 1.123e-1 $\pm$ 1.050e-1 \\ \hline
-Spectral                                  & 2.302e-2 $\pm$ 1.941e-2 & 8.144e-3 $\pm$ 4.886e-3 & 1.126e-1 $\pm$ 9.777e-2 \\ \hline
-GNN, 12 Layers, w/o Geometric Side Losses & 1.000e-3 & 1.000e-3 & 1.000e-3 \\ \hline
-GNN, 12 Layers, w/ Geometric Side Losses  & 1.000e-3 & 1.000e-3 & 1.000e-3 \\ \hline
+MatchALS \cite{zhou2015multi} 15 Iterations               & 0.052 $\pm$ 0.003 & 0.010 $\pm$ 0.002 & 0.107 $\pm$ 0.038 \\ \hline
+MatchALS \cite{zhou2015multi} 100 Iterations              & 0.029 $\pm$ 0.023 & 0.008 $\pm$ 0.003 & 0.163 $\pm$ 0.094 \\ \hline 
+MatchALS \cite{zhou2015multi} 400 Iterations              & 0.022 $\pm$ 0.022 & 0.008 $\pm$ 0.003 & 0.184 $\pm$ 0.102 \\ \hline 
+PGDDS \cite{leonardos2016distributed} 15 Iterations       & 0.020 $\pm$ 0.019 & 0.007 $\pm$ 0.003 & 0.149 $\pm$ 0.108 \\ \hline 
+PGDDS \cite{leonardos2016distributed} 100 Iterations      & 0.019 $\pm$ 0.017 & 0.007 $\pm$ 0.003 & 0.127 $\pm$ 0.108 \\ \hline 
+PGDDS \cite{leonardos2016distributed} 200 Iterations      & 0.018 $\pm$ 0.016 & 0.007 $\pm$ 0.003 & 0.112 $\pm$ 0.105 \\ \hline 
+Spectral                                                  & 0.023 $\pm$ 0.019 & 0.008 $\pm$ 0.005 & 0.113 $\pm$ 0.098 \\ \hline \hline
+GNN, 12 Layers                                            & 0.027 $\pm$ 0.003 & 0.017 $\pm$ 0.003 & 0.701 $\pm$ 0.002 \\
 \hline
@@
 \end{center}
+% save-rome16kgeom0-normedskip2-loss-l1-geom-10-0 (028249) -> train : +3.1467e-02, test : +3.8864e-02, gt_l1 : +2.6321e-02, gt_l2 : +2.6321e-02
+
 \caption{
-Results on Rome16k Correspondence graphs.
-Losses tested against ground truth correspondence graph adjacency matrices.
-Our method was not trained on ground truth corresopndences but on unsupervised methods.
+Results on Rome16K Correspondence graphs.
+Our method was not trained on ground truth corresopndences but using unsupervised methods and geometric side losses.
+As our method gives soft labels, we use cannot use precision or recall as is standard in testing cycle consistency \cite{zhou2015multi}.
+Thus we test against ground truth correspondence graph adjacency matrices gotten from the bundle adjustment output.
 }
@@
 This method can be employed even when labelled training data is not available, but can still incorporate side geometric information.
-For future work we hope to use more robust losses for outlier rejection, and to incorporate learning image level features into this pipeline.
+For future work we will investigate using more robust losses for outlier rejection and using higher order geometric constraints, such as the trifocal tensor, as additional loss terms.
+A long term goal is to incorporate learning image level features into this pipeline
+We hope to make this method distributed - with group norm, we cannot distribute in its current form.
 

### 2018-11-16 model/layers.py
1. Fixed bug with geometric loss for 4 views 2. Fixed up test.py to work with new architectures

@@ -99,17 +99,17 @@ class GraphGroupNorm(snt.AbstractModule):
                                   shape=(self._input_shape[2]),
                                   dtype=dtype,
                                   initializer=self._initializers["gamma"])
-    self._gamma = tf.reshape(self._gamma, broadcast_shape)
     if self._gamma not in tf.get_collection('weights'):
       tf.add_to_collection('weights', self._gamma)
+    self._gamma = tf.reshape(self._gamma, broadcast_shape)
 
     self._beta = tf.get_variable("beta",
                                  shape=(self._input_shape[2],),
                                  dtype=dtype,
                                  initializer=self._initializers["beta"])
-    self._beta = tf.reshape(self._beta, broadcast_shape)
     if self._beta not in tf.get_collection('biases'):
       tf.add_to_collection('biases', self._beta)
+    self._beta = tf.reshape(self._beta, broadcast_shape)
 
     ##### Actually perform operations
     # Reshape input

### 2018-11-16 options.py

@@ -13,6 +13,27 @@ import re
 
 import myutils
 
+class DatasetParams(argparse.Namespace):
+  def __init__(self, opts):
+    super(DatasetParams, self).__init__()
+    self.data_dir='{}/{}'.format(opts.datasets_dir, opts.dataset)
+    self.sizes={ 'train': 40000, 'test': 3000 }
+    self.fixed_size=True
+    self.views=[3]
+    self.points=[25]
+    self.points_scale=1
+    self.knn=4
+    self.scale=3
+    self.sparse=False
+    self.soft_edges=False
+    self.descriptor_dim=12
+    self.descriptor_var=1.0
+    self.descriptor_noise_var=0
+    self.noise_level=0.1
+    self.num_repeats=1
+    self.num_outliers=0
+    self.dtype='float32'
+
 dataset_choices = [
   'synth_3view', 'synth_small', 'synth_4view', 'synth_5view', 'synth_6view',
   'noise_3view',
@@ -25,6 +46,18 @@ dataset_choices = [
   'rome16kknn0',
   'rome16kgeom0', 'rome16kgeom4view0',
 ]
+
+class ArchParams(argparse.Namespace):
+  def __init__(self, opts):
+    super(ArchParams, self).__init__()
+    self.layer_lens = [ 32, 64 ]
+    self.activ = opts.activation_type
+    self.attn_lens = []
+    self.skip_layers = []
+    self.start_normed = 1
+    self.group_size = 32
+    self.normalize_emb = True
+    self.sparse = False
 
 arch_choices = [
   'vanilla', 'vanilla0', 'vanilla1',
@@ -229,25 +262,7 @@ def get_opts():
   if not opts.load_data and opts.dataset in [ 'rome16kknn0' ]:
     print("ERROR: Cannot generate samples on the fly for this dataset: {}".format(opts.dataset))
     sys.exit(1)
-  class DatasetParams(object):
-    def __init__(self, opts):
-      self.data_dir='{}/{}'.format(opts.datasets_dir, opts.dataset)
-      self.sizes={ 'train': 40000, 'test': 3000 }
-      self.fixed_size=True
-      self.views=[3]
-      self.points=[25]
-      self.points_scale=1
-      self.knn=4
-      self.scale=3
-      self.sparse=False
-      self.soft_edges=False
-      self.descriptor_dim=12
-      self.descriptor_var=1.0
-      self.descriptor_noise_var=0
[…]

### 2018-11-16 test.py

@@ -49,11 +49,11 @@ def get_test_losses(opts, sample, output, return_gt=False, name='loss'):
     osim_log = tf.log(tf.abs(output_sim) + 1e-9)
   gt_l1_loss = loss_fns['l1'](sim_true, osim, add_loss=False)
   gt_l2_loss = loss_fns['l2'](sim_true, osim, add_loss=False)
-  gt_bce_loss = loss_fns['bce'](sim_true, oslim_log, add_loss=False)
+  gt_bce_loss = loss_fns['bce'](sim_true, osim, add_loss=False)
   num_same = tf.reduce_sum(sim_true)
   num_diff = tf.reduce_sum(1-sim_true)
-  ssame_m, ssame_var = tf.weighted_moments(osim, None, sim_true)
-  sdiff_m, sdiff_var = tf.weighted_moments(osim, None, 1-sim_true)
+  ssame_m, ssame_var = tf.nn.weighted_moments(osim, None, sim_true)
+  sdiff_m, sdiff_var = tf.nn.weighted_moments(osim, None, 1-sim_true)
 
   return gt_l1_loss, gt_l2_loss, gt_bce_loss, ssame_m, ssame_var, sdiff_m, sdiff_var
 
@@ -77,8 +77,8 @@ def test_values(opts):
   # Tensorflow and logging operations
   disp_string =  '{:06d} Errors: ' \
                  'L1: {:.03e},  L2: {:.03e}, BCE: {:.03e} ' \
-                 'Same sim: {.03e} +/- {.03e} ' \
-                 'Diff sim: {.03e} +/- {.03e}' 
+                 'Same sim: {:.03e} +/- {:.03e} ' \
+                 'Diff sim: {:.03e} +/- {:.03e}' 
 
 
   # Build session
@@ -86,6 +86,7 @@ def test_values(opts):
   npz_files = sorted(glob.glob(glob_str))
   vars_restore = [ v for v in tf.get_collection('weights') ] + \
                  [ v for v in tf.get_collection('biases') ]
+  print(vars_restore)
   saver = tf.train.Saver(vars_restore)
   with open(os.path.join(opts.save_dir, 'test_output.log'), 'a') as log_file:
     with build_test_session(opts) as sess:
@@ -100,5 +101,8 @@ def test_values(opts):
 
 if __name__ == "__main__":
   opts = options.get_opts()
+  print("Getting options from run...")
+  opts = options.parse_yaml_opts(opts)
+  print("Done")
   test_values(opts)
 

### 2018-11-16 cvpr2019/main.tex
Fixed baselines - got something here

@@
 \hline
-Method                                                    & L1 Loss           & L2 Loss           & BCE Loss \\
+Method                                                    & $L_1$ Loss        & $L_2$ Loss        & BCE Loss \\
+
 \hline\hline\hline
 MatchALS \cite{zhou2015multi} 15 Iterations               & 0.052 $\pm$ 0.003 & 0.010 $\pm$ 0.002 & 0.107 $\pm$ 0.038 \\ \hline
-MatchALS \cite{zhou2015multi} 100 Iterations              & 0.029 $\pm$ 0.023 & 0.008 $\pm$ 0.003 & 0.163 $\pm$ 0.094 \\ \hline 
-MatchALS \cite{zhou2015multi} 400 Iterations              & 0.022 $\pm$ 0.022 & 0.008 $\pm$ 0.003 & 0.184 $\pm$ 0.102 \\ \hline 
-PGDDS \cite{leonardos2016distributed} 15 Iterations       & 0.020 $\pm$ 0.019 & 0.007 $\pm$ 0.003 & 0.149 $\pm$ 0.108 \\ \hline 
-PGDDS \cite{leonardos2016distributed} 100 Iterations      & 0.019 $\pm$ 0.017 & 0.007 $\pm$ 0.003 & 0.127 $\pm$ 0.108 \\ \hline 
-PGDDS \cite{leonardos2016distributed} 200 Iterations      & 0.018 $\pm$ 0.016 & 0.007 $\pm$ 0.003 & 0.112 $\pm$ 0.105 \\ \hline 
-Spectral                                                  & 0.023 $\pm$ 0.019 & 0.008 $\pm$ 0.005 & 0.113 $\pm$ 0.098 \\ \hline \hline
-GNN, 12 Layers                                            & 0.027 $\pm$ 0.003 & 0.017 $\pm$ 0.003 & 0.701 $\pm$ 0.002 \\
+MatchALS \cite{zhou2015multi} 100 Iterations              & 0.007 $\pm$ 0.003 & 0.007 $\pm$ 0.003 & 0.220 $\pm$ 0.099 \\ \hline
+% MatchALS \cite{zhou2015multi} 400 Iterations              & 0.007 $\pm$ 0.003 & 0.007 $\pm$ 0.003 & 0.225 $\pm$ 0.104 \\ \hline
+PGDDS \cite{leonardos2016distributed} 15 Iterations       & 0.016 $\pm$ 0.002 & 0.006 $\pm$ 0.002 & 0.045 $\pm$ 0.037 \\ \hline
+PGDDS \cite{leonardos2016distributed} 100 Iterations      & 0.013 $\pm$ 0.002 & 0.005 $\pm$ 0.002 & 0.039 $\pm$ 0.038 \\ \hline
+% PGDDS \cite{leonardos2016distributed} 200 Iterations      & 0.013 $\pm$ 0.002 & 0.005 $\pm$ 0.002 & 0.039 $\pm$ 0.039 \\ \hline
+Spectral                                                  & 0.054 $\pm$ 0.005 & 0.018 $\pm$ 0.004 & 0.114 $\pm$ 0.028 \\ \hline \hline
+GNN, 12 Layers (ours)                                     & 0.027 $\pm$ 0.003 & 0.017 $\pm$ 0.003 & 0.701 $\pm$ 0.002 \\
 \hline
@@
 \caption{
-Results on Rome16K Correspondence graphs.
+Results on Rome16K Correspondence graphs, showing the mean and standard deviation of the $L_1$ and $L_2$.
 Our method was not trained on ground truth corresopndences but using unsupervised methods and geometric side losses.

### 2018-11-16 baselines/print_errors.py
Fixed a bug in the error printing, and also added a few more baselines to run

@@ -11,6 +11,12 @@ def stdagg(x):
   return np.sqrt(np.mean(np.array(x)**2))
 
 def myformat(x):
+  return '{:.05e}'.format(x)
+
+def myformat2(x):
+  return '{:.03f}'.format(x)
+
+def myformat_old(x):
   y = "{:.03e}".format(x).split('e')
   return "{}e-{}".format(y[0], y[1][-1])
 
@@ -31,6 +37,12 @@ def agg(vals):
   return aggs
 
 def disp_val(aggs):
+  # fstr = "{:40}, L1: {} +/- {} , L2: {} +/- {} , BCE: {} +/- {}"
+  # print(fstr.format(fname, 
+  #                   myformat(aggs['l1'][0]), myformat(aggs['l1'][1]),
+  #                   myformat(aggs['l2'][0]), myformat(aggs['l2'][1]),
+  #                   myformat(aggs['bce'][0]), myformat(aggs['bce'][1])))
+  # return 
   fstr = "{:40} & {} $\pm$ {} & {} $\pm$ {} & {} $\pm$ {}"
   print(fstr.format(fname, 
                     myformat(aggs['l1'][0]), myformat(aggs['l1'][1]),
@@ -38,9 +50,9 @@ def disp_val(aggs):
                     myformat(aggs['bce'][0]), myformat(aggs['bce'][1])))
 
 
-vals = dict(zip(names, [ [] for nm in names ]))
 
 for fname in sys.argv[1:]:
+  vals = dict(zip(names, [ [] for nm in names ]))
   f = open(fname, 'r')
   for line in f:
     vals_ = parse(line)

### 2018-11-16 baselines/run_tests.m

@@ -5,17 +5,21 @@ p = 80;
 n = p*v;
 dimGroups = [ p, p, p ];
 params015.maxiter = 15;
+params050.maxiter = 50;
 params100.maxiter = 100;
 params200.maxiter = 200;
 
+%  'MatchALS400Iter', @(W)  mmatch_CVX_ALS(W, dimGroups, 'maxrank', p, 'maxiter', 400); ...
+%  'MatchALS100Iter', @(W)  mmatch_CVX_ALS(W, dimGroups, 'maxrank', p, 'maxiter', 100); ...
+%  'MatchALS050Iter', @(W)  mmatch_CVX_ALS(W, dimGroups, 'maxrank', p, 'maxiter', 50); ...
+%  'MatchALS015Iter', @(W)  mmatch_CVX_ALS(W, dimGroups, 'maxrank', p, 'maxiter', 15); ...
+%  'Spectral', @(W)  myspectral(W, p); ...
+%  'PGDDS200Iter', @(W) PGDDS(W, dimGroups, p, params200); ...
+%  'PGDDS100Iter', @(W) PGDDS(W, dimGroups, p, params100); ...
+%  'PGDDS015Iter', @(W) PGDDS(W, dimGroups, p, params015); ...
 test_fns = { ...
- 'MatchALS400Iter', @(W)  mmatch_CVX_ALS(W, dimGroups, 'maxrank', p, 'maxiter', 400); ...
- 'MatchALS100Iter', @(W)  mmatch_CVX_ALS(W, dimGroups, 'maxrank', p, 'maxiter', 100); ...
- 'MatchALS015Iter', @(W)  mmatch_CVX_ALS(W, dimGroups, 'maxrank', p, 'maxiter', 15); ...
- 'Spectral', @(W)  myspectral(W, p); ...
- 'PGDDS200Iter', @(W) PGDDS(W, dimGroups, p, params200); ...
- 'PGDDS100Iter', @(W) PGDDS(W, dimGroups, p, params100); ...
- 'PGDDS015Iter', @(W) PGDDS(W, dimGroups, p, params015); ...
+ 'MatchALS025Iter', @(W)  mmatch_CVX_ALS(W, dimGroups, 'maxrank', p, 'maxiter', 25); ...
+ 'PGDDS050Iter', @(W) PGDDS(W, dimGroups, p, params050); ...
 };
 
 % disp_string =  [ '%06d Errors: ' ...

### 2018-11-16 latex_report.py
Added new view_style option to latex_report.py

@@ -32,6 +32,11 @@ def get_latex_opts():
                       default=False,
                       type=str2bool,
                       help='Just view, do not save')
+  view_style_choices = [ 'default', 'paper' ]
+  parser.add_argument('--view_style',
+                      default=view_style_choices[0],
+                      choices=view_style_choices,
+                      help='Options for the figure style')
   parser.add_argument('--index',
                       default=0,
                       type=int,
@@ -74,6 +79,7 @@ class Experiment(object):
     self.name = os.path.split(folder)[1]
     self.extention = extention
     self.verbose = verbose
+    self.view_style = opts.view_style
 
   def get_losses(self, use_time=False):
     loss = np.load(os.path.join(self.folder, 'loss.npy'))
@@ -86,6 +92,12 @@ class Experiment(object):
       return loss, test_loss
 
   def generate_plot(self, size, index=0):
+    if self.view_style == 'default':
+      self.generate_plot_default(size, index=index)
+    elif self.view_style == 'paper':
+      self.generate_plot_paper(size, index=index)
+
+  def generate_plot_default(self, size, index=0):
     nrows, ncols = 1, 5
     fig = plt.figure(figsize=(ncols*size,1.4*nrows*size))
     gs = GridSpec(4, 14)
@@ -148,6 +160,69 @@ class Experiment(object):
     ### Titles
     ax[0].set_title('Train/test loss')
     ax[1].set_title('Normalized Embeddings')
+    ax[-1].set_title('Pairwise similarities')
+    ax[-1].set_axis_off()
+    
+    # Show everything
+    # plt.show()
+    # break
+    return fig
+
+  def generate_plot_paper(self, size, index=0):
+    nrows, ncols = 1, 4
+    fig = plt.figure(figsize=(ncols*size,1.4*nrows*size))
+    gs = GridSpec(4, 10)
+    ax = [
+      plt.subplot(gs[:,0:2]),
+      plt.subplot(gs[1:,2:4]),
+      plt.subplot(gs[:,4:7]),
+      plt.subplot(gs[:,7:10]),
+      plt.subplot(gs[0,2:4]),
+    ]
+    fig.tight_layout()
+
+    ##### Plot a specific example
+    ### Get specific example
+    ldnames = sorted(glob.glob(os.path.join(self.folder, 'test*npz')))
+    ld = np.load(ldnames[-1])
+    emb_init = ld['input'][index]
+    emb_gt = ld['gt'][index]
+    emb_out = ld['output'][index]
[…]

### 2018-11-16 cvpr2019/main.tex
Added some more text and updated figure

@@
 % Include other packages here, before hyperref.
-\usepackage[outdir=./]{epstopdf}
+% \usepackage[outdir=./]{epstopdf}
 
@@
 
-\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
+\def\cvprPaperID{3510} % *** Enter the CVPR Paper ID here
 \def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
@@
 
+%------------------------------------------------------------------------
+\begin{figure*}[t]
+\begin{center}
+  % \fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
+  \includegraphics[width=0.8\linewidth]{figures/CycleConsistencyMainFigure.pdf}
+\end{center}
+  \caption{
+    An outline of the pipeline of this work.
+    The Graph Convolutional Neural Network (GCN) \cite{kipf2016semi} takes as input the graph of matches and then outputs a low rank embedding of the adjacency matrix of the graph.
+    The GCN operates on an embedding over the nodes of the graph.
+    In the figure, the the GCN node embeddings are represented by different colors.
+    The final embedding is used to construct a pairwise similarity matrix, which ideally should be a low dimensional cycle consistent representation of the graph adjacency matrix.
+    We train the network using a reconstruction loss on the similarity matrix.
+    In addition, we can use geometric information at to assist training the network, even if we do not have that geometric information at testing time such as epipolar constraints on the point locations or higher order geometric constraints.
+  }
+\label{fig:pipeline}
+\label{fig:onecol}
+\end{figure*}
+
 Unfortunately, there are obstacles to applying multi-view constraints directly to learning. 
@@
 
-%------------------------------------------------------------------------
-\begin{figure*}[t]
+\section{Method}
+
+\begin{figure}[t]
 \begin{center}
-  % \fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-  \includegraphics[width=0.8\linewidth]{figures/CycleConsistencyMainFigure.pdf}
+  \includegraphics[width=0.9\linewidth]{figures/UniverseOfFeatures.pdf}
 \end{center}
   \caption{
-    An outline of the pipeline of this work.
-    The Graph Convolutional Neural Network (GCN) \cite{kipf2016semi} takes as input the graph of matches and then outputs a low rank embedding of the adjacency matrix of the graph.
-    The GCN operates on an embedding over the nodes of the graph.
-    In the figure, the the GCN node embeddings are represented by different colors.
-    The final embedding is used to construct a pairwise similarity matrix, which ideally should be a low dimensional cycle consistent representation of the graph adjacency matrix.
-    We train the network using a reconstruction loss on the similarity matrix.
-    In addition, we can use geometric information at to assist training the network, even if we do not have that geometric information at testing time such as epipolar constraints on the point locations or higher order geometric constraints.
+    Illustration of the universe of features.
+    Each feature in each image corresponds to a 3D point in the scene.
+    Therefore, we can get the points to have a cycle consistent embedding by mapping each feature in each image to the one-hot vector of its corresponding 3D point.
+    While there can be many features, there are much fewer 3D points and thus this corrsponds to a low rank factorization of the corrspondence matrix.
+    Best viewed in color.
   }
-\label{fig:pipeline}
+\label{fig:universefeatures}
 \label{fig:onecol}
-\end{figure*}
-
-\section{Method}
+\end{figure}
 Our goal is to learn optimal features that capture multiple image views by way of filtering out noisy feature matches.
@@
 
-\begin{figure}[t]
-\begin{center}
-  \includegraphics[width=0.9\linewidth]{figures/UniverseOfFeatures.pdf}
-\end{center}
-  \caption{
-    Illustration of the universe of features.
-    Each feature in each image corresponds to a 3D point in the scene.
-    Therefore, we can get the points to have a cycle consistent embedding by mapping each feature in each image to the one-hot vector of its corresponding 3D point.
-    While there can be many features, there are much fewer 3D points and thus this corrsponds to a low rank factorization of the corrspondence matrix.
-    Best viewed in color.
-  }
-\label{fig:universefeatures}
-\label{fig:onecol}
-\end{figure}
-
 Let $\mat{M}$ be the noiseless set of matches between our features, with $\mat{M}_{ij}$ being the matches between image $i$ and image $j$.
@@
 
+\begin{table*}
+\begin{center}
+\begin{tabular}{|l|c|c|}
+\hline
+Method & Same Point Similarities & Different Point Similarities  \\
+\hline\hline\hline
+Ideal                              & 1.00e+0 $\pm$ 0.00e+0 & 0.00e+0 $\pm$ 0.00e+0 \\ \hline
+Initialization Baseline            & 5.11e-1 $\pm$ 1.68e-2 & 2.56e-1 $\pm$ 2.06e-1 \\ \hline
+3 Views, Noiseless                 & 9.96e-1 $\pm$ 7.70e-3 & 1.16e-1 $\pm$ 1.32e-1 \\ \hline
+5 Views, Noiseless                 & 1.00e+0 $\pm$ 4.15e-4 & 1.22e-1 $\pm$ 1.67e-1 \\ \hline
+3 Views, Added Noise               & 9.96e-1 $\pm$ 7.70e-3 & 1.16e-1 $\pm$ 1.32e-1 \\ \hline
+3 Views, Added Noise               & 9.68e-1 $\pm$ 5.29e-2 & 9.50e-2 $\pm$ 1.58e-1 \\ \hline
+5 Views, Added Noise               & 9.89e-1 $\pm$ 2.47e-2 & 7.67e-2 $\pm$ 1.56e-1 \\ \hline
+6 Views, Added Noise               & 9.84e-1 $\pm$ 3.16e-2 & 7.46e-2 $\pm$ 1.57e-1 \\ \hline
+3 Views, 5\% Outliers              & 9.29e-1 $\pm$ 1.79e-1 & 1.41e-1 $\pm$ 1.48e-1 \\ \hline
+3 Views, 10\% Outliers             & 9.27e-1 $\pm$ 1.79e-1 & 1.40e-1 $\pm$ 1.51e-1 \\ \hline
+
+\hline
+\end{tabular}
+\end{center}
+\caption{
+Results on Synthetic correspondence graphs.
+The `Same Point Similarities' column is the mean and standard deviation of similarities for true corresponding points, while the `Different Point Similarities' is the same for points that do not correspond.
+For the `Same Point Similarities' column higher is better, and for `Different Point Similarities' lower is better.
+Losses tested against ground truth correspondence graph adjacency matrices.
+Our method was not trained on ground truth correspondences but using unsupervised methods.
+}
+\label{fig:synthtable}
+\end{table*}
+
 One of the main advantages of this approach over more traditional optimization based approaches is the ability to add geometric consistency information into the loss at training time, even if it is not available at test time.
@@
 
+\begin{table*}
+\begin{center}
+\begin{tabular}{|l|c|c|c|}
+\hline
+Method                                                    & $L_1$ Loss        & $L_2$ Loss         \\
+
+\hline\hline\hline
+MatchALS \cite{zhou2015multi} 15 Iterations               & 0.052 $\pm$ 0.003 & 0.010 $\pm$ 0.002 \\ \hline
+MatchALS \cite{zhou2015multi} 25 Iterations               & 0.045 $\pm$ 0.007 & 0.009 $\pm$ 0.003 \\ \hline
+MatchALS \cite{zhou2015multi} 50 Iterations               & 0.016 $\pm$ 0.008 & 0.007 $\pm$ 0.003 \\ \hline
+MatchALS \cite{zhou2015multi} 100 Iterations              & 0.007 $\pm$ 0.003 & 0.007 $\pm$ 0.003 \\ \hline
+% MatchALS \cite{zhou2015multi} 400 Iterations              & 0.007 $\pm$ 0.003 & 0.007 $\pm$ 0.003 \\ \hline
+PGDDS \cite{leonardos2016distributed} 15 Iterations       & 0.016 $\pm$ 0.002 & 0.006 $\pm$ 0.002 \\ \hline
+PGDDS \cite{leonardos2016distributed} 50 Iterations       & 0.013 $\pm$ 0.002 & 0.005 $\pm$ 0.002 \\ \hline
+PGDDS \cite{leonardos2016distributed} 100 Iterations      & 0.013 $\pm$ 0.002 & 0.005 $\pm$ 0.002 \\ \hline
+% PGDDS \cite{leonardos2016distributed} 200 Iterations      & 0.013 $\pm$ 0.002 & 0.005 $\pm$ 0.002 & 0.039 $\pm$ 0.039 \\ \hline
+Spectral                                                  & 0.054 $\pm$ 0.005 & 0.018 $\pm$ 0.004 \\ \hline \hline
+GNN, 12 Layers (ours)                                     & 0.025 $\pm$ 0.003 & 0.016 $\pm$ 0.003 \\
+\hline
+\end{tabular}
+\end{center}
+% save-rome16kgeom0-normedskip2-loss-l1-geom-10-0 (028249) -> train : +3.1467e-02, test : +3.8864e-02, gt_l1 : +2.6321e-02, gt_l2 : +2.6321e-02
+
+\caption{
+Results on Rome16K Correspondence graphs, showing the mean and standard deviation of the $L_1$ and $L_2$.
+Our method was not trained on ground truth corresopndences but using unsupervised methods and geometric side losses.
+As our method gives soft labels, we use cannot use precision or recall as is standard in testing cycle consistency \cite{zhou2015multi}.
+Thus we test against ground truth correspondence graph adjacency matrices computed from the bundle adjustment output.
+Our method performs better than 25 iteration of an optimizaiton based method, but does not perform as well as 50 iterations.
+Our network has only 12 layers, thus we have much greater efficiency per iteration.
+}
+\end{table*}
+
 %------------------------------------------------------------------------
@@
   % \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
-  \includegraphics[width=0.8\linewidth]{figures/TrainingCurvesFull.pdf}
+  \includegraphics[width=0.8\linewidth]{figures/TrainingCurves.pdf}
   \end{center}
@@
   % \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
-  \includegraphics[width=0.8\linewidth]{figures/experiments01-eps-converted-to.pdf}
+  \includegraphics[width=0.8\linewidth]{figures/ExampleOutput.pdf}
   \end{center}
-     \caption{Experimental results from Rome16K}
+     \caption{Example output of our network.
+(a) Similarity Matrix of the of the embeddings (b) Histogram of feature similarities for pairs which correspond to the same 3D point, comparing our output features with the original SIFT features (c) Histogram of feature similarities for pairs which correspond to different 3D points, comparing our output features with the original SIFT features}
   \label{fig:short}
 \end{figure*}
-
-\begin{table*}
-\begin{center}
-\begin{tabular}{|l|c|c|}
-\hline
-Method & Same Point Similarities & Different Point Similarities  \\
-\hline\hline\hline
-Ideal                              & 1.00e+0 $\pm$ 0.00e+0 & 0.00e+0 $\pm$ 0.00e+0 \\ \hline
-Initialization Baseline            & 5.11e-1 $\pm$ 1.68e-2 & 2.56e-1 $\pm$ 2.06e-1 \\ \hline
-3 Views, Noiseless                 & 9.96e-1 $\pm$ 7.70e-3 & 1.16e-1 $\pm$ 1.32e-1 \\ \hline
-5 Views, Noiseless                 & 1.00e+0 $\pm$ 4.15e-4 & 1.22e-1 $\pm$ 1.67e-1 \\ \hline
-3 Views, Added Noise               & 9.96e-1 $\pm$ 7.70e-3 & 1.16e-1 $\pm$ 1.32e-1 \\ \hline
-3 Views, Added Noise               & 9.68e-1 $\pm$ 5.29e-2 & 9.50e-2 $\pm$ 1.58e-1 \\ \hline
-5 Views, Added Noise               & 9.89e-1 $\pm$ 2.47e-2 & 7.67e-2 $\pm$ 1.56e-1 \\ \hline
-6 Views, Added Noise               & 9.84e-1 $\pm$ 3.16e-2 & 7.46e-2 $\pm$ 1.57e-1 \\ \hline
-3 Views, 5\% Outliers              & 9.29e-1 $\pm$ 1.79e-1 & 1.41e-1 $\pm$ 1.48e-1 \\ \hline
-3 Views, 10\% Outliers             & 9.27e-1 $\pm$ 1.79e-1 & 1.40e-1 $\pm$ 1.51e-1 \\ \hline
-
-\hline
-\end{tabular}
-\end{center}
-\caption{
-Results on Synthetic correspondence graphs.
-The `Same Point Similarities' column is the mean and standard deviation of similarities for true corresponding points, while the `Different Point Similarities' is the same for points that do not correspond.
-For the `Same Point Similarities' column higher is better, and for `Different Point Similarities' lower is better.
-Losses tested against ground truth correspondence graph adjacency matrices.
-Our method was not trained on ground truth correspondences but using unsupervised methods.
-}
-\label{fig:synthtable}
-\end{table*}
 \subsection{Synthetic Graph Dataset}
@@
 Therefore, to use for our method, we extract image triplets and quadtruplets with overlap of 80 points or more to test our algorithm on, with the points established as corresponding in the given bundle adjument output.
-For the initial embedding we use the original 128 dimensional SIFT descriptors, normalized to have $L_2$ norm 1, the calibrated x-y position, the orientation, and log scale of the SIFT feature.
+For the initial embedding we use the original 128 dimensional SIFT descriptors, normalized to have unit $L_2$ norm, the calibrated x-y position, the orientation, and log scale of the SIFT feature.
 % For the outlier datasets, we take 79 correspondences and 1 non-corresponding point in each image.
 
-For these experiments we train with the $L1$ norm, and ablate the geometric side losses.
+For these experiments we train with the $L1$ norm and geometric consistency losses.
 We evaluate on a test set using the ground truth adjacency matrix which we compute from the bundle adjustment given by the Rome16K dataset.
@@
 Here we use the ground truth dimension of the embedding to test both our method and the baselines.
+For implementation details, our network has 12 layers, and was trained with the Adam optimizer \cite{kingma2014adam} with a learning rate of $10^{-4}$, with an exponentially decaying learning rate.
+We incorporate skip connections between the input, $6^{th}$, and $12^{th}$ layers, which greatly improved training convergence and testing performance (see supplemental material).
 
-\begin{table*}
-\begin{center}
-\begin{tabular}{|l|c|c|c|}
-\hline
-Method                                                    & $L_1$ Loss        & $L_2$ Loss        & BCE Loss \\
-
-\hline\hline\hline
-MatchALS \cite{zhou2015multi} 15 Iterations               & 0.052 $\pm$ 0.003 & 0.010 $\pm$ 0.002 & 0.107 $\pm$ 0.038 \\ \hline
-MatchALS \cite{zhou2015multi} 100 Iterations              & 0.007 $\pm$ 0.003 & 0.007 $\pm$ 0.003 & 0.220 $\pm$ 0.099 \\ \hline
-% MatchALS \cite{zhou2015multi} 400 Iterations              & 0.007 $\pm$ 0.003 & 0.007 $\pm$ 0.003 & 0.225 $\pm$ 0.104 \\ \hline
-PGDDS \cite{leonardos2016distributed} 15 Iterations       & 0.016 $\pm$ 0.002 & 0.006 $\pm$ 0.002 & 0.045 $\pm$ 0.037 \\ \hline
-PGDDS \cite{leonardos2016distributed} 100 Iterations      & 0.013 $\pm$ 0.002 & 0.005 $\pm$ 0.002 & 0.039 $\pm$ 0.038 \\ \hline
-% PGDDS \cite{leonardos2016distributed} 200 Iterations      & 0.013 $\pm$ 0.002 & 0.005 $\pm$ 0.002 & 0.039 $\pm$ 0.039 \\ \hline
-Spectral                                                  & 0.054 $\pm$ 0.005 & 0.018 $\pm$ 0.004 & 0.114 $\pm$ 0.028 \\ \hline \hline
-GNN, 12 Layers (ours)                                     & 0.027 $\pm$ 0.003 & 0.017 $\pm$ 0.003 & 0.701 $\pm$ 0.002 \\
-\hline
-\end{tabular}
-\end{center}
-% save-rome16kgeom0-normedskip2-loss-l1-geom-10-0 (028249) -> train : +3.1467e-02, test : +3.8864e-02, gt_l1 : +2.6321e-02, gt_l2 : +2.6321e-02
-
-\caption{
-Results on Rome16K Correspondence graphs, showing the mean and standard deviation of the $L_1$ and $L_2$.
-Our method was not trained on ground truth corresopndences but using unsupervised methods and geometric side losses.
-As our method gives soft labels, we use cannot use precision or recall as is standard in testing cycle consistency \cite{zhou2015multi}.
-Thus we test against ground truth correspondence graph adjacency matrices gotten from the bundle adjustment output.
-}
-\end{table*}
+We compare our method to spectral and optimization based baselines with different maximum iteration cutoffs.
+Our method is siginificatnly better than a simple spectral based optimization.
+Furthermore, our network, which only has 12 layers has the accuracy of the optimization based method MatchALS \cite{zhou2015multi} between 25 and 50 iterations.
+This inidicates that our method learns a more efficient update with each layer compared with an iteration in the optimization based methods.
 
@@
 We have shown a novel method for training feature matching.
-We have demonstrated its effectiveness using experiments on the Rome16K dataset.
-This method can be employed even when labelled training data is not available, but can still incorporate side geometric information.
+This method can be employed even when labelled training data is not available, but can still incorporate geometric consistency into its losses.
+We have demonstrated its effectiveness using experiments on the Rome16K dataset compared to the traditional optimization based baselines.
 For future work we will investigate using more robust losses for outlier rejection and using higher order geometric constraints, such as the trifocal tensor, as additional loss terms.
 A long term goal is to incorporate learning image level features into this pipeline
-We hope to make this method distributed - with group norm, we cannot distribute in its current form.
+Moreover we hope to make this method distributed - with group norm, we cannot distribute in its current form.
 

### 2018-11-16 baselines/print_errors.py

@@ -10,10 +10,10 @@ egstr = '000000 Errors: L1: 5.297e-02, L2: 1.678e-02, BCE: 1.008e-01, Same sim: 
 def stdagg(x):
   return np.sqrt(np.mean(np.array(x)**2))
 
-def myformat(x):
+def myformat2(x):
   return '{:.05e}'.format(x)
 
-def myformat2(x):
+def myformat(x):
   return '{:.03f}'.format(x)
 
 def myformat_old(x):

### 2018-11-16 baselines/run_tests.m

@@ -1,25 +1,31 @@
-function run_tests(mat_files)
+function run_tests(mat_files, views)
 
-v = 3;
+if nargin < 2
+  views = 3;
+end
+
+v = views;
 p = 80;
 n = p*v;
-dimGroups = [ p, p, p ];
+dimGroups = ones(v,1)*p;
 params015.maxiter = 15;
+params025.maxiter = 25;
 params050.maxiter = 50;
 params100.maxiter = 100;
 params200.maxiter = 200;
 
 %  'MatchALS400Iter', @(W)  mmatch_CVX_ALS(W, dimGroups, 'maxrank', p, 'maxiter', 400); ...
-%  'MatchALS100Iter', @(W)  mmatch_CVX_ALS(W, dimGroups, 'maxrank', p, 'maxiter', 100); ...
-%  'MatchALS050Iter', @(W)  mmatch_CVX_ALS(W, dimGroups, 'maxrank', p, 'maxiter', 50); ...
-%  'MatchALS015Iter', @(W)  mmatch_CVX_ALS(W, dimGroups, 'maxrank', p, 'maxiter', 15); ...
-%  'Spectral', @(W)  myspectral(W, p); ...
 %  'PGDDS200Iter', @(W) PGDDS(W, dimGroups, p, params200); ...
-%  'PGDDS100Iter', @(W) PGDDS(W, dimGroups, p, params100); ...
-%  'PGDDS015Iter', @(W) PGDDS(W, dimGroups, p, params015); ...
 test_fns = { ...
+ 'Spectral', @(W)  myspectral(W, p); ...
+ 'MatchALS015Iter', @(W)  mmatch_CVX_ALS(W, dimGroups, 'maxrank', p, 'maxiter', 15); ...
  'MatchALS025Iter', @(W)  mmatch_CVX_ALS(W, dimGroups, 'maxrank', p, 'maxiter', 25); ...
+ 'MatchALS050Iter', @(W)  mmatch_CVX_ALS(W, dimGroups, 'maxrank', p, 'maxiter', 50); ...
+ 'MatchALS100Iter', @(W)  mmatch_CVX_ALS(W, dimGroups, 'maxrank', p, 'maxiter', 100); ...
+ 'PGDDS015Iter', @(W) PGDDS(W, dimGroups, p, params015); ...
+ 'PGDDS025Iter', @(W) PGDDS(W, dimGroups, p, params025); ...
[…]

### 2018-11-16 latex_report.py

@@ -2,11 +2,13 @@ import os
 import sys
 import glob
 import numpy as np
+import sklearn.manifold as manifold
 import argparse
 import argcomplete
 import matplotlib.pyplot as plt
 from matplotlib.gridspec import GridSpec
 from matplotlib import cm
+from mpl_toolkits.mplot3d import Axes3D
 import tqdm
 # import yaml
 
@@ -21,6 +23,28 @@ def str2bool(v):
     else:
         raise argparse.ArgumentTypeError('Boolean value expected.')
 
+def hinton(matrix, max_weight=None, ax=None):
+    """Draw Hinton diagram for visualizing a weight matrix."""
+    ax = ax if ax is not None else plt.gca()
+
+    if not max_weight:
+        max_weight = 2 ** np.ceil(np.log(np.abs(matrix).max()) / np.log(2))
+
+    ax.patch.set_facecolor('gray')
+    ax.set_aspect('equal', 'box')
+    ax.xaxis.set_major_locator(plt.NullLocator())
+    ax.yaxis.set_major_locator(plt.NullLocator())
+
+    for (x, y), w in np.ndenumerate(matrix):
+        color = 'white' if w > 0 else 'black'
+        size = np.sqrt(np.abs(w) / max_weight)
+        rect = plt.Rectangle([x - size / 2, y - size / 2], size, size,
+                             facecolor=color, edgecolor=color)
+        ax.add_patch(rect)
+
+    ax.autoscale_view()
+    ax.invert_yaxis()
+
 def get_latex_opts():
   parser = argparse.ArgumentParser(description='Experiment with output')
   argcomplete.autocomplete(parser)
@@ -32,7 +56,7 @@ def get_latex_opts():
                       default=False,
                       type=str2bool,
                       help='Just view, do not save')
-  view_style_choices = [ 'default', 'paper' ]
+  view_style_choices = [ 'default', 'paper', 'embeddings' ]
   parser.add_argument('--view_style',
                       default=view_style_choices[0],
                       choices=view_style_choices,
@@ -96,6 +120,8 @@ class Experiment(object):
       self.generate_plot_default(size, index=index)
     elif self.view_style == 'paper':
[…]

### 2018-11-17 cvpr2019/main.tex
One more draft - suggestions from Daphne, Davie, Kostas, and Xiao

@@
 % Cycle Consistent Multi-View Representations Using Graph CNNs}
-\title{All Graphs Lead to Rome: Learning Geometric and Cycle Consistent Representations with Graph CNNs}
+\title{All Graphs Lead to Rome: Learning Geometric and Cycle-Consistent Representations with Graph Convolutional Networks}
 
 \author{Stephen Phillips, Kostas Daniilidis \\
-GRASP Labratory, University of Pennsylvania\\
+GRASP Laboratory, University of Pennsylvania\\
 {\tt\small \{stephi, kostas\}@seas.upenn.edu}
@@
 \begin{abstract}
-    Image feature matching is a fundametal part of many geometric computer vision applications, and using multiple images can improve performance.
-    In this work, we formulate the multi-image matching problem as a graph embedding problem then use a Graph Neural Network to learn an appropriate embedding function for aligning image features.
-% How to talk about the universe of features here without going too much into the weeds??
-    We use cycle consistency to train our network in an unsupervised fashion since ground truth correspondence is difficult or expensive to come by in many real world datasets.
-    In addtion, geometric consistency losses can be added at train time, even if the information is not available in the test set, unlike previous optimization based methods.
+    Image feature matching is a fundamental part of many geometric computer vision applications, and using multiple images can improve performance.
+    In this work, we formulate multi-image matching as a graph embedding problem then use a Graph Convolutional Network to learn an appropriate embedding function for aligning image features.
+    We use cycle consistency to train our network in an unsupervised fashion, since ground truth correspondence is difficult or expensive to aquire.
+    In addition, geometric consistency losses can be added at train time, even if the information is not available in the test set, unlike previous approaches that optimize cycle consistency directly.
     To the best of our knowledge, no other works have used learning for multi-image feature matching.
@@
 The goal in multi-image feature matching is to take 2D image locations from three or more images and find which ones correspond to the same point in the 3D scene.
-Methods such as SIFT feature matching \cite{lowe2004distinctive} and RANSAC \cite{fischler1981random} have been standard for solving this for decades.
-However RANSAC-based approaches are limited for matching pairs of images.
-Other works, such as Wang et al. \cite{wang2017multi}, have shown improvement in performance by enforcing consistency between multiple images.
-% However we still have not fully answered the question: What are the best image features to describe multiple views of the same scene?
+Methods such as SIFT feature matching \cite{lowe2004distinctive} followed by RANSAC \cite{fischler1981random} have been the standard for decades.
+However RANSAC-based approaches are limited for matching pairs of images, which can lead to global inconsistencies in the matching.
+Other works, such as Wang et al.~\cite{wang2017multi}, have shown improvement in performance by optimizing cycle consistency, i.e.
+enforcing the pairwise feature matches to be globally consistent, illustrated in \ref{fig:cycconsistex}.
 
-Deep learning has revolutionized how image features are computed \cite{yi2016lift}, and so we would like to leverage this to compute better scene features.
-Typically when applied to image or feature matching, deep neural networks (DNNs) are trained with photometric losses, directly using pixel color values.
-However direct, pixel-based losses have are not robust to the many confounding factors in the environment, such as lighting and view-point changes.
-Using features designed to deal with these condfounding factors improves robustness to them, 
-and learning may improve robustness even further.
+However, these multi-view consistency algorithms struggle in distributed and robust settings.
+Deep learning has revolutionized how image features are computed \cite{yi2016lift}.
+In this paper, we want to leverage the power of deep representations in order to compute feature descriptors that are robust across multiple views.
+% Typically when applied to image or feature matching, deep neural networks (DNNs) are trained with photometric losses, directly using pixel color values.
+% However direct, pixel-based losses have are not robust to the many confounding factors in the environment, such as lighting and view-point changes.
+% Using features designed to deal with these confounding factors improves robustness to them, and learning may improve robustness even further.
 
@@
   \caption{
-    Example of multi-image matching, with images from Rome16K dataset \cite{li2010location}.
+    Example of multi-image matching and cycle consistency, with images from Rome16K dataset \cite{li2010location}.
+    Pairwise matches between image can lead to global inconsistencies in the matching.
     In this example, an error in matching leads to an inconsistent cycle (shown in red), ideally these pairwise matches would be consistent.
-    We improve consistency between pairwise matches in the multi-view matching problem by training a neural net with cycle consistency.
+    We improve the quality of pairwise matches in the multi-view matching problem by training a neural net with cycle consistency.
   }
@@
   \caption{
-    An outline of the pipeline of this work.
+    An illustration of the approach of this work.
     The Graph Convolutional Neural Network (GCN) \cite{kipf2016semi} takes as input the graph of matches and then outputs a low rank embedding of the adjacency matrix of the graph.
     The GCN operates on an embedding over the nodes of the graph.
-    In the figure, the the GCN node embeddings are represented by different colors.
-    The final embedding is used to construct a pairwise similarity matrix, which ideally should be a low dimensional cycle consistent representation of the graph adjacency matrix.
-    We train the network using a reconstruction loss on the similarity matrix.
-    In addition, we can use geometric information at to assist training the network, even if we do not have that geometric information at testing time such as epipolar constraints on the point locations or higher order geometric constraints.
+    In the figure, the GCN node embeddings are represented by different colors.
+    The final embedding is used to construct a pairwise similarity matrix, which we train to be a low dimensional cycle-consistent representation of the graph adjacency matrix, thus pruning the erroneous matches.
+    We train the network using a reconstruction loss on the similarity matrix with the noisy adjacency matrix, and thus do not need ground truth matches.
+    In addition, we can use geometric consistency information, such as epipolar constraints, to assist training the network.
   }
@@
 
-Unfortunately, there are obstacles to applying multi-view constraints directly to learning. 
-To train networks, we need a large amount of labelled data.
+Unfortunately, there are obstacles to applying multi-view constraints directly to deep learning. 
+To train networks, we need a large amount of labeled data.
 In the case of multi-image feature matching, one would need to hand label point correspondences between images, which is difficult and expensive to obtain.
-Multi-view constraints are formulated in terms of sparse features, which traditional convolutional deep neural nets (CNNs) are not designed to handle such input.
+Multi-view constraints are formulated in terms of sparse features, which traditional convolutional neural nets are not designed to handle.
 In the case of multi-image feature matching, geometric constraints would be helpful in rejecting outlier matches.
 
-In this work, we propose to solve these problems using a Graph Neural Network (GNN) to operate on the correspondence graph.
-The proposed method works on the correspondence graph, which is agnostic to how the correspondnces were computed, thus allowing the algorithm to work in a broad class of environments.
-
-We use a unsupervised loss, the cycle consistency loss, to train the network.
-We add in geometric consistency losses to help training, which works even when the geometric information is not available at test time.
+In this work, we propose to solve these problems using a Graph Convolutional Network (GCN) to operate on the correspondence graph.
+The proposed method works directly on the correspondence graph, which is agnostic to how the correspondences were computed, thus allowing the algorithm to work in a broad class of environments.
+To the best of our knowledge this work is the first to apply deep learning to the multi-view feature matching problem.
+We use an unsupervised loss - the cycle consistency loss - to train the network, and thus avoiding the difficulty of expensive hand labeling.
+% We incorporate geometric consistency losses to guide training, which helps training even when the geometric information is not available at test time.
+Geometric consistency losses can aid training, even if such information is not available at test time.
+Although our network is simple, it shows promising results compared to baselines which optimize for cycle-consistency without learned embeddings.
+Furthermore, since inference requires only a single forward pass over the neural network, our approach is faster (to achieve comparable accuracy) than method which must solve an optimization problem every time.
 Our contributions are:
 \begin{itemize}
-\item We use a novel architecture to address multi-image feature matching problem using GNNs with graph embeddings.
-\item We introduce an unsupervised cycle consistency loss that does not require labelled correspondences to train.
+\item We use a novel architecture to address the multi-image feature matching problem using GCNs with graph embeddings.
+\item We introduce an unsupervised cycle consistency loss that does not require labeled correspondences to train.
 \item We demonstrate the effectiveness of geometric consistency losses in improving training.
-\item We perform experiments on the Rome16K \cite{li2010location} dataset to test the effectiveness of our method compared to optimization based baselines.
+\item We perform experiments on the Rome16K \cite{li2010location} dataset to test the effectiveness of our method compared to optimization based methods.
 \end{itemize}
@@
 
+\subsection{Feature Matching}
 Matching has a rich history of research in computer vision.
 The most well known and widely used method for image matching is RANSAC \cite{fischler1981random}.
-RANSAC, combined with hand-crafted feature descriptors like SIFT \cite{lowe2004distinctive}, SURF \cite{bay2006surf}, BRIEF \cite{calonder2012brief}, or ORB \cite{mur2015orb}, has constituted the bulk of the matching literature for the last 40 years.
-To improve matching of all the features of the image, graph matching \cite{suh2015subgraph, hu2016distributable} can be used for more robust matches.
+RANSAC, combined with hand-crafted feature descriptors such as SIFT \cite{lowe2004distinctive}, SURF \cite{bay2006surf}, BRIEF \cite{calonder2012brief}, or ORB \cite{mur2015orb}, has constituted the bulk of the matching literature for the last 40 years.
+Finally, graph matching \cite{suh2015subgraph, hu2016distributable} can be used as a final step for more robust matches.
 
+\subsection{Multi-image Matching}
 Multi-image matching has traditionally been done using optimization based methods minimizing a cycle consistency based loss (see Section 3.3).
-Pachauri et al. \cite{pachauri2013solving} and Arrigoni et al. \cite{arrigoni2017synchronization} use the eigenvectors of the matching matrix to obtain a low dimensional embedding. 
-Thus they are robust to small Gaussian noise but not to more realistic noise.
-Zhou et al. \cite{zhou2015multi} and Wang et al. \cite{wang2017multi} use most sophisticated optimization techniques on the matching matrix and thus are quite robust.
-Leonardos et al. \cite{leonardos2016distributed} implement a distributed optimizaiton scheme to solve for cycle consistency.
-As an alternative to optimization based techiniques, Tron et al. \cite{tron2017fast} used density based clustering techniques to compute multi-image correspondence.
+Pachauri et al.~\cite{pachauri2013solving} and Arrigoni et al.~\cite{arrigoni2017synchronization} use the eigenvectors of the matching matrix to obtain a low dimensional embedding. 
+However, the low Gaussian noise assumption is not realistic.
+Zhou et al.~\cite{zhou2015multi} and Wang et al.~\cite{wang2017multi} use most sophisticated optimization techniques on the matching matrix and thus produce more robust solutions.
+Leonardos et al.~\cite{leonardos2016distributed} implement a distributed optimization scheme to solve for cycle consistency.
+As an alternative to optimization based techniques, Tron et al.~\cite{tron2017fast} used density based clustering techniques to compute multi-image correspondence.
+To the best of our knowledge, we are the first to use neural networks for multi-image matching.
 
+\subsection{Deep Learning for Matching}
 Previous attempts to improve image matching techniques using machine learning have focused on learning the descriptors given ground truth correspondence from curated datasets \cite{zagoruyko2015learning, yi2016lift, brachmann2017dsac}.
-This approach is limited if you do not have the ability to get the ground truth correspondences.
-There are other methods to build correspondences such as Choy et al. \cite{choy2016universal}, but it only handles two-view constraints and requires dense correspondences.
-Most similar to ours, Yi et al. \cite{yi2018learning} attempts to improve correspondences by learning match probabilites for RANSAC to speed up test time running.
-However, they only focus on two view tests and do not exploit the advantages of the correspondence structure.
+This approach is limited if one do not have the ability to get the ground truth correspondences.
+There are other methods to build correspondences such as Choy et al.~\cite{choy2016universal}, but they only handle two-view constraints and require dense correspondences.
+Most similar to our work, Yi et al.~\cite{yi2018learning} attempts to improve correspondences by learning match probabilities for RANSAC for greater robustness and speed.
+However, they only focus on two view matching and do not exploit the advantages of the correspondence structure.
+Note that while Zhu et al.~\cite{zhu2017unpaired} use cycle consistency in their loss, their method is restricted to pairwise cycle consistency, while we use multi-image cycle consistency.
 
-Graph neural networks have been getting more attention recently \cite{bronstein2017geometric, bruna2013spectral, defferrard2016convolutional, kipf2016semi, scarselli2009graph, gama2018mimo, gama2018convolutional, battaglia2018relational}.
-Classical so-called Spectral methods used the eigenvectors of graph Laplacian to compute convolutions like in Bruna et al.
-\cite{bruna2013spectral}, but requires a fixed graph structure known a-priori.
+\subsection{Graph Neural Networks}
+Graph neural networks have recieved more attention recently \cite{bronstein2017geometric, bruna2013spectral, defferrard2016convolutional, kipf2016semi, scarselli2009graph, gama2018mimo, gama2018convolutional, battaglia2018relational}.
+Classical so-called Spectral methods used the eigenvectors of the graph Laplacian to compute convolutions as in Bruna et al.~\cite{bruna2013spectral}, but requires an a-prior known graph structure. 
 Non-spectral methods do not require a-priori knowledge \cite{bronstein2017geometric, kipf2016semi, scarselli2009graph, gama2018convolutional}.
-Most of these simply use polynomials of the graph Laplacian to compute neighborhood averages.
-Gama et al.
-2018 \cite{gama2018mimo, gama2018convolutional} formalize this notion and generalize it beyond the use of the graph Laplacian.
-To improve performance, more sophisticated aggregation techniques and global information passing can be used as discussed in Battaglia et al. \cite{battaglia2018relational}.
+Most of these methods use polynomials of the graph Laplacian to compute neighborhood averages.
+Gama et al.~2018 \cite{gama2018mimo, gama2018convolutional} formalize this notion and generalize it beyond the use of the graph Laplacian.
+To improve performance, more sophisticated aggregation techniques and global information passing can be used as discussed in Battaglia et al.~\cite{battaglia2018relational}.
 
@@
     Each feature in each image corresponds to a 3D point in the scene.
-    Therefore, we can get the points to have a cycle consistent embedding by mapping each feature in each image to the one-hot vector of its corresponding 3D point.
-    While there can be many features, there are much fewer 3D points and thus this corrsponds to a low rank factorization of the corrspondence matrix.
+    We can construct a cycle consistent embeddings of the features by mapping each one to the one-hot vector of its corresponding 3D point.
+    While there can be many features, there are fewer 3D points and thus this corresponds to a low rank factorization of the correspondence matrix.
     Best viewed in color.
@@
 \end{figure}
-Our goal is to learn optimal features that capture multiple image views by way of filtering out noisy feature matches.
+Our goal is to learn optimal features that capture multiple image views by filtering out noisy feature matches.
 The input to our algorithm is a set of features and noisy correspondences, and the output is a new set of features where the pairwise similarities of these features correspond to the true matches.
-We do this by learning training the new set of feature embeddings to be cycle consistent.
+We do this by training the new set of feature embeddings to be cycle consistent.
 We formulate this problem in terms of the correspondence graph of the features.
@@
 \subsection{Correspondence Graph}
-We assume we have an initial set of feature matches represented as a graph $\mathcal{G} = (\mathcal{V}, \mathcal{E})$.
+We assume there is an initial set of feature matches represented as a graph $\mathcal{G} = (\mathcal{V}, \mathcal{E})$.
 Each vertex $v$ of the graph is a feature with its associated descriptor $f_v$. 
 The graph is represented by its Weighted Adjacency Matrix $\mat{A}(\mathcal{G}) \in \bR^{n \times n}$, where $(\mat{A}(\mathcal{G}))_{ij}$ is the strength of the match between nodes $i$ and $j$.
-We also have the positive diagonal degree matrix $\mat{D}(\mathcal{G}) \in \bR^{n \times n}$, with $\mat{D}(\mathcal{G})_{ii} = \sum_j (\mat{A}(\mathcal{G}))_{ij}$.
+We introduce the positive diagonal degree matrix $\mat{D}(\mathcal{G}) \in \bR^{n \times n}$, with $\mat{D}(\mathcal{G})_{ii} = \sum_j (\mat{A}(\mathcal{G}))_{ij}$.
 For brevity we denote these matrices $\mat{A}$ and $\mat{D}$ respectively.
-We can get our an embedding matrix $\mat{E}_0$ by concatenating the features $f_v$ from each of the vertices.
-We use $\mat{E}_0$ as the initializiation for our learning algorithm.
+We introduce the notion of an embedding matrix $\mat{E}_0$ by concatenating the features $f_v$ from each of the vertices.
+We use $\mat{E}_0$ as the initialization for our learning algorithm.
 We add any additional knowledge we have into the embedding as well (e.g. scale, orientation, etc.).
@@
 
-In the absense of noise or outliers, this graph would have a connected component for each visible point in the world.
+In the absence of noise or outliers, this graph would have a connected component for each visible point in the world.
 These components should be mutually disjoint. 
 In other words each feature would only have edges to other features corresponding to the same point.
-Since features in this case represent unique location in the scene, no points in the same image would have edges between them.
-In the noisy case we expect this structure to be corrupted and thus we need to refine out the erroneous edges.
+Since features in this case represent unique locations in the scene, no points in the same image would have edges between them.
+In the noisy case we expect this structure to be corrupted and thus we need to prune the erroneous edges.
 
@@
 Typically these putative correspondences are matched probabilistically, meaning a feature in one image matches to many features in another.
-This could come from repeated structures in the scene, ambiguity from the low-level feature descriptors, or just an error in the matching algorithm.
+The ambiguity in the matches could come from repeated structures in the scene, insufficiently informative low-level feature descriptors, or just an error in the matching algorithm.
 Filtering out these noisy matches is our primary learning goal.
 
-However, this graph structure does not have a regular grid structure and thus we cannot use standard CNNs to learn features for this task.
+However, this graph structure does not have a regular grid structure and thus we cannot use standard convolutional nets to learn features for this task.
 Instead we use graph convolutions to learn feature representations on this space.
@@
 and an initial embedding $\mat{E}_0 \in \bR^{n \times m_0}$.
-Many older methods assume $\mat{L}$ is known a-priori \cite{bruna2013spectral}, and thus can encode graph convolutions using the eigenvectors of $L$.
-We do not have this luxury, as the correspondence structure changes from image to image, and thus we use non-spectral GNNs. The standard form of non-spectral GNNs is:
+Many older methods assume $\mat{L}$ is known a-priori \cite{bruna2013spectral}, and can encode graph convolutions using the eigenvectors of $L$.
+We do not have this luxury, as the correspondence structure changes from image to image, and thus we use non-spectral Graph Neural Networks.
+The standard form of non-spectral Graph Neural Networks is:
 \begin{equation}
@@
 In the feature matching problem, we require an embedding for each vertex.
-Therefore we cannot perform graph coarsening, and thus we only perform the non-linearity step.
-We instead use a modification of the approach proposed in Kipf and Welling \cite{kipf2016semi}:
+Therefore we cannot perform graph coarsening, and thus only perform the non-linearity step.
+This work uses Graph Convolutional Networks, proposed in Kipf and Welling \cite{kipf2016semi}:
 \begin{align}
@@
 Our network has many layers, and thus the receptive field of the final embedding is quite large, even without the pooling operations.
-In principle we could use higher hop neighborhoods \cite{gama2018convolutional}, or more complicated aggregation structures \cite{battaglia2018relational}, but in this work we restrict ourselves to simpler architectures, which still shows promising results for this task.
+In principle we could use higher hop neighborhoods \cite{gama2018convolutional}, or more complicated aggregation structures \cite{battaglia2018relational}, but in this work we restrict ourselves to simpler architectures, and still obtain promising results for this task.
 For faster training, we use group normalization \cite{wu2018group} and skip connections.
@@
 In the next sections we will discuss the loss functions to train this network.
+
+\begin{figure}[t]
+\begin{center}
+  \includegraphics[width=0.8\linewidth]{figures/GeometricConsistency.pdf}
+\end{center}
+  \caption{
+    Illustrated here is an example of how the geometric loss is computed for one feature.  
+    Errors are computed via absolute distance from the epipolar line, as expressed by (\ref{eq:essential_constraint}) via the epipolar constraint.
+    The epipolar line is the line of projection of the feature on the first image, projected onto to the second.
+    The distance to this line on the second image indicates how likely that point is to correspond geometrically to the original feature.
+    There can be false positives along the projected line, as shown by the square feature in the figure, but other points will be eliminated, such as the hexagonal feature.
+    Best viewed in color.
+  }
+\label{fig:geoconsist}
+\label{fig:onecol}
+\end{figure}
 
@@
 \end{equation}
-In other words, the matches between two images stays the same no matter what path is taken to get there. 
-This constraint is known as \textit{cycle concistency}, and has been used in a number of works to optimize for global consistency \cite{zhou2015multi, wang2017multi, leonardos2016distributed}.
+In other words, the matches between two images stay the same no matter what path is taken to get there. 
+This constraint is known as \textit{cycle consistency}, and has been used in a number of works to optimize for global consistency \cite{zhou2015multi, wang2017multi, leonardos2016distributed}.
 Stated in this form, there are $O(n^3)$ cycle consistency constraints to check.
@@
 \end{equation}
-
-This reduces our complexity from $O(n^3)$ to $O(n^2)$.
-We try to learn $\mat{E}$ to approximate $\mat{X}$ - in other words the final embedding should be an encoding of the universe of features.
-As we do not have the ground truth matches $\mat{M}$, we approximate it using the noisy adjacency matrix $\mat{A}$ of our correspondence graph.
-Thus our loss would be
-\begin{equation}
-\mathcal{L}(\mat{A}, \mat{E}_n) = \mathcal{D}(\mat{A}, \mat{E}_n\mat{E}_n^\top)
-\end{equation}
-Here $\mathcal{D}$ could be an $L_2$ loss, $L_1$ loss, or many others. In this work, we use the $L_1$ loss.
-
-\subsection{Geometric Consistency Loss}
-
-\begin{figure}[t]
-\begin{center}
-  \includegraphics[width=0.8\linewidth]{figures/GeometricConsistency.pdf}
-\end{center}
-  \caption{
-    Illustrated here is an example of how the geometric loss on one feature.  
-    We compute the errors on each feature match to determine their validity.
-    Errors are computed via absolute distance from the epipolar line, as expressed by (\ref{eq:essential_constraint}) via the epipolar constraint.
-    Best viewed in color.
-  }
-\label{fig:geoconsist}
-\label{fig:onecol}
-\end{figure}
 
@@
 
+This reduces our complexity from $O(n^3)$ to $O(n^2)$.
+We try to learn $\mat{E}$ to approximate $\mat{X}$ - in other words the final embedding should be an encoding of the universe of features.
+As we do not have the ground truth matches $\mat{M}$, we approximate it using the noisy adjacency matrix $\mat{A}$ of our correspondence graph.
+Thus our loss would be
+\begin{equation}
+\mathcal{L}(\mat{A}, \mat{E}_n) = \mathcal{D}(\mat{A}, \mat{E}_n\mat{E}_n^\top)
+\end{equation}
+Here $\mathcal{D}$ could be an $L_2$ loss, $L_1$ loss, or many others. In this work, we use the $L_1$ loss. 
+Note that because of this formulation, we can determine our embeddings only up to a rotation, as
+\begin{equation}
+\mat{E}R(\mat{E}R)^\top
+= \mat{E}RR^\top\mat{E}^\top
+= \mat{E}\mat{E}^\top
+\label{eq:rotinvar}
+\end{equation}
+Thus when visualizing embeddings, we rotate them to make them more interpretable (see figure CITE FIGURE).
+
+\subsection{Geometric Consistency Loss}
+
 One of the main advantages of this approach over more traditional optimization based approaches is the ability to add geometric consistency information into the loss at training time, even if it is not available at test time.
@@
 \end{equation}
-For our purposes, since we use low rank embeddings $\mat{E}_{i}$, $\mat{E}_{j}$, the loss would look like:
+For our purposes, since we use low rank embeddings $\mat{E}_{i}$, $\mat{E}_{j}$, the loss would read:
 \begin{align}
@@
 \hline
-Method                                                    & $L_1$ Loss        & $L_2$ Loss         \\
-
-\hline\hline\hline
-MatchALS \cite{zhou2015multi} 15 Iterations               & 0.052 $\pm$ 0.003 & 0.010 $\pm$ 0.002 \\ \hline
-MatchALS \cite{zhou2015multi} 25 Iterations               & 0.045 $\pm$ 0.007 & 0.009 $\pm$ 0.003 \\ \hline
-MatchALS \cite{zhou2015multi} 50 Iterations               & 0.016 $\pm$ 0.008 & 0.007 $\pm$ 0.003 \\ \hline
-MatchALS \cite{zhou2015multi} 100 Iterations              & 0.007 $\pm$ 0.003 & 0.007 $\pm$ 0.003 \\ \hline
-% MatchALS \cite{zhou2015multi} 400 Iterations              & 0.007 $\pm$ 0.003 & 0.007 $\pm$ 0.003 \\ \hline
-PGDDS \cite{leonardos2016distributed} 15 Iterations       & 0.016 $\pm$ 0.002 & 0.006 $\pm$ 0.002 \\ \hline
-PGDDS \cite{leonardos2016distributed} 50 Iterations       & 0.013 $\pm$ 0.002 & 0.005 $\pm$ 0.002 \\ \hline
-PGDDS \cite{leonardos2016distributed} 100 Iterations      & 0.013 $\pm$ 0.002 & 0.005 $\pm$ 0.002 \\ \hline
-% PGDDS \cite{leonardos2016distributed} 200 Iterations      & 0.013 $\pm$ 0.002 & 0.005 $\pm$ 0.002 & 0.039 $\pm$ 0.039 \\ \hline
-Spectral                                                  & 0.054 $\pm$ 0.005 & 0.018 $\pm$ 0.004 \\ \hline \hline
-GNN, 12 Layers (ours)                                     & 0.025 $\pm$ 0.003 & 0.016 $\pm$ 0.003 \\
-\hline
+Method (3 Views)                                          & $L_1$ Loss                          & $L_2$ Loss                          & Run Time (sec)                      \\
+\hline\hline
+MatchALS \cite{zhou2015multi} 15 Iterations               & 0.052 $\pm$ 0.003                   & 0.010 $\pm$ 0.002                   & 0.021 $\pm$ 0.003                   \\ \hline
+MatchALS \cite{zhou2015multi} 25 Iterations               & 0.045 $\pm$ 0.007                   & 0.009 $\pm$ 0.003                   & 0.034 $\pm$ 0.003                   \\ \hline
+MatchALS \cite{zhou2015multi} 50 Iterations               & 0.016 $\pm$ 0.008                   & 0.007 $\pm$ 0.003                   & 0.065 $\pm$ 0.006                   \\ \hline
+PGDDS \cite{leonardos2016distributed} 15 Iterations       & 0.016 $\pm$ 0.002                   & 0.006 $\pm$ 0.002                   & 0.287 $\pm$ 0.043                   \\ \hline
+PGDDS \cite{leonardos2016distributed} 25 Iterations       & 0.014 $\pm$ 0.002                   & 0.005 $\pm$ 0.002                   & 0.613 $\pm$ 0.089                   \\ \hline
+PGDDS \cite{leonardos2016distributed} 50 Iterations       & 0.013 $\pm$ 0.002                   & 0.005 $\pm$ 0.002                   & 1.430 $\pm$ 0.234                   \\ \hline
+Spectral                                                  & 0.054 $\pm$ 0.005                   & 0.018 $\pm$ 0.004                   & 0.018 $\pm$ 0.004                   \\ \hline 
+\textbf{GCN, 12 Layers (ours)}                            & \textbf{0.025} $\pm$ \textbf{0.003} & \textbf{0.016} $\pm$ \textbf{0.003} & \textbf{0.039} $\pm$ \textbf{0.009} \\
+\hline \hline\hline
+Method (4 Views)                                                         & $L_1$ Loss                          & $L_2$ Loss                          & Run Time (sec)                     \\
+\hline\hline
+MatchALS \cite{zhou2015multi} 15 Iterations                              & 0.064 $\pm$ 0.005                   & 0.012 $\pm$ 0.002                   & 0.030 $\pm$ 0.004                   \\  \hline
+MatchALS \cite{zhou2015multi} 25 Iterations                              & 0.041 $\pm$ 0.010                   & 0.008 $\pm$ 0.004                   & 0.048 $\pm$ 0.005                   \\  \hline
+MatchALS \cite{zhou2015multi} 50 Iterations                              & 0.011 $\pm$ 0.008                   & 0.005 $\pm$ 0.003                   & 0.094 $\pm$ 0.008                   \\  \hline
+PGDDS \cite{leonardos2016distributed} 15 Iterations                      & 0.015 $\pm$ 0.002                   & 0.006 $\pm$ 0.001                   & 0.436 $\pm$ 0.090                   \\  \hline
+PGDDS \cite{leonardos2016distributed} 25 Iterations                      & 0.014 $\pm$ 0.002                   & 0.005 $\pm$ 0.001                   & 0.961 $\pm$ 0.181                   \\  \hline
+PGDDS \cite{leonardos2016distributed} 50 Iterations                      & 0.013 $\pm$ 0.002                   & 0.005 $\pm$ 0.002                   & 2.056 $\pm$ 0.424                   \\  \hline
+Spectral Method                                                          & 0.055 $\pm$ 0.004                   & 0.017 $\pm$ 0.003                   & 0.028 $\pm$ 0.003                   \\  \hline
+\textbf{GCN, 12 Layers (ours)}                                           & \textbf{0.023} $\pm$ \textbf{0.003} & \textbf{0.015} $\pm$ \textbf{0.002} & \textbf{0.056} $\pm$ \textbf{0.017} \\ \hline
 \end{tabular}
@@
 Thus we test against ground truth correspondence graph adjacency matrices computed from the bundle adjustment output.
-Our method performs better than 25 iteration of an optimizaiton based method, but does not perform as well as 50 iterations.
+Our method performs better than 25 iteration of the MatchALS \cite{zhou2015multi} method, but does not perform as well as 50 iterations.
 Our network has only 12 layers, thus we have much greater efficiency per iteration.
+We do not perform as well as the Projected Gradient Descent Doubly Stochastic (PGDDS) \cite{leonardos2016distributed} but we perform significantly faster than them.
+Note that we perform much better in $L_1$ performance rather than $L_2$, as we optimized the network weights using an $L_1$ loss.
 }
@@
 To create the graph, we generate random permutation matrices, with a noise applied to it after generated.
-The initial descriptors we use as input we created using the true descriptor plus some added Gaussian noise.
+% The initial descriptors we use as input we created using the true descriptor plus some added Gaussian noise.
+We initialize the input descriptors using the true descriptor, plus some added Gaussian noise.
 No geometric losses were added during training for these experiments.
 However, the method was robust in testing with different noise functions and parameters.
-The normalized noisy input descriptors are our baseline - they correlate with the true values but do not perserve the structure well.
-However, with the GNN we are able to recover the true structure very well, as shown in \ref{fig:synthtable}.
+The normalized noisy input descriptors are our baseline - they correlate with the true values but do not preserve the structure well.
+However, the GCN recovered the true structure very well, as shown in \ref{fig:synthtable}.
 All experiments were run with a 12 layer GCN with the ReLU nonlinearity and skip connections.
@@
 We  use the Rome16K dataset \cite{li2010location} to test our algorithm in real world settings.
-Rome16K consistes of 16 thousand images of various historical sites in Rome extracted from Flickr, along with the 3D structure of the sites provided by bundle adjustment.
+Rome16K consists of 16 thousand images of various historical sites in Rome extracted from Flickr, along with the 3D structure of the sites provided by bundle adjustment.
 While not a standard dataset to test cycle consistency, other datasets had insufficient data to train a network on.
 Rome16K is typically used to test bundle adjustment methods.
-Therefore, to use for our method, we extract image triplets and quadtruplets with overlap of 80 points or more to test our algorithm on, with the points established as corresponding in the given bundle adjument output.
+Therefore, to use our method, we extract image triplets and quadruplets with overlap of 80 points or more to test our algorithm, with the points established as corresponding in the given bundle adjustment output.
 For the initial embedding we use the original 128 dimensional SIFT descriptors, normalized to have unit $L_2$ norm, the calibrated x-y position, the orientation, and log scale of the SIFT feature.
@@
 
-For these experiments we train with the $L1$ norm and geometric consistency losses.
-We evaluate on a test set using the ground truth adjacency matrix which we compute from the bundle adjustment given by the Rome16K dataset.
+For these experiments we train with the $L_1$ norm and geometric consistency losses.
+We evaluate on a test set using the ground truth adjacency matrix, which we compute from the bundle adjustment given by the Rome16K dataset.
 Traditional methods of evaluation use Precision and Recall, after making the labels 0 or 1.
@@
 We compare our method to spectral and optimization based baselines with different maximum iteration cutoffs.
-Our method is siginificatnly better than a simple spectral based optimization.
-Furthermore, our network, which only has 12 layers has the accuracy of the optimization based method MatchALS \cite{zhou2015multi} between 25 and 50 iterations.
-This inidicates that our method learns a more efficient update with each layer compared with an iteration in the optimization based methods.
+Our method is signification better than a simple spectral based optimization.
+% Furthermore, our network, which only has 12 layers has the accuracy of the optimization based method MatchALS \cite{zhou2015multi} inbetween 25 and 50 iterations.
+Our network, though only 12 layers, has comparable accuracy to MatchALS \cite{zhou2015multi} run between 25 and 50 iterations.
+% This indicates that our method learns a more efficient update with each layer compared with an iteration in the optimization based methods.
+Although our method does not outperform the Projected Gradient Descent - Doubly Stochastic (PGDDS) \cite{leonardos2016distributed} method, we have significantly better run time.
+Additional comparisons to different iterations numbers of iterations can be found in the supplementary material.
 
+\begin{figure}[t]
+\begin{center}
+  % \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
+  \includegraphics[width=0.8\linewidth]{figures/EmbeddingsViz.pdf}
+  \end{center}
+     \caption{
+         Visualization of the learned embeddings using Hinton diagrams \cite{bremner1994hinton}.
+         On the left we have the raw outputs, which are difficult to interpret.
+         On the right, we rotated the features to best match the ground truth for a more interpretable visualization.
+     }
+  \label{fig:onecol}
+  \label{fig:embeddingsviz}
+\end{figure}
 %------------------------------------------------------------------------
@@
 
-We have shown a novel method for training feature matching.
-This method can be employed even when labelled training data is not available, but can still incorporate geometric consistency into its losses.
-We have demonstrated its effectiveness using experiments on the Rome16K dataset compared to the traditional optimization based baselines.
-For future work we will investigate using more robust losses for outlier rejection and using higher order geometric constraints, such as the trifocal tensor, as additional loss terms.
-A long term goal is to incorporate learning image level features into this pipeline
-Moreover we hope to make this method distributed - with group norm, we cannot distribute in its current form.
+We have shown a novel method for training feature matching using GCNs, using an unsupervised cycle consistency loss and geometric consistency losses.
+We have demonstrated its effectiveness on the Rome16K dataset compared to the traditional optimization based baselines on a simple GCN.
+For future work, we will investigate robust losses for better outlier rejection, and using higher order geometric constraints, such as the tri-focal tensor, as additional loss terms.
+A long term goal is to incorporate learning image level features into this pipeline.
+Moreover we hope to adapt this method to a distributed setting, which would be simple given current approach.
+% , but with group norm, we cannot distribute in its current form.
 

### 2018-11-19 cvpr2019/main.tex
Added figures and finished up tex document

@@
     We use cycle consistency to train our network in an unsupervised fashion, since ground truth correspondence is difficult or expensive to aquire.
-    In addition, geometric consistency losses can be added at train time, even if the information is not available in the test set, unlike previous approaches that optimize cycle consistency directly.
+    In addition, geometric consistency losses can be added at training time, even if the information is not available in the test set, unlike previous approaches that optimize cycle consistency directly.
     To the best of our knowledge, no other works have used learning for multi-image feature matching.
@@
 Methods such as SIFT feature matching \cite{lowe2004distinctive} followed by RANSAC \cite{fischler1981random} have been the standard for decades.
-However RANSAC-based approaches are limited for matching pairs of images, which can lead to global inconsistencies in the matching.
+However RANSAC-based approaches are limited to matching pairs of images, which can lead to global inconsistencies in the matching.
 Other works, such as Wang et al.~\cite{wang2017multi}, have shown improvement in performance by optimizing cycle consistency, i.e.
-enforcing the pairwise feature matches to be globally consistent, illustrated in \ref{fig:cycconsistex}.
+enforcing the pairwise feature matches to be globally consistent, illustrated in figure \ref{fig:cycconsistex}.
 
@@
 To train networks, we need a large amount of labeled data.
-In the case of multi-image feature matching, one would need to hand label point correspondences between images, which is difficult and expensive to obtain.
+In the case of multi-image feature matching, one would need hand labeled point correspondences between images, which are difficult and expensive to obtain.
 Multi-view constraints are formulated in terms of sparse features, which traditional convolutional neural nets are not designed to handle.
-In the case of multi-image feature matching, geometric constraints would be helpful in rejecting outlier matches.
+Additionally, in the case of multi-image feature matching, geometric constraints would be helpful in rejecting outlier matches.
 
@@
 Although our network is simple, it shows promising results compared to baselines which optimize for cycle-consistency without learned embeddings.
-Furthermore, since inference requires only a single forward pass over the neural network, our approach is faster (to achieve comparable accuracy) than method which must solve an optimization problem every time.
+Furthermore, since inference requires only a single forward pass over the neural network, our approach is faster (to achieve comparable accuracy) than methods which must solve an optimization problem every time.
 Our contributions are:
@@
 Graph neural networks have recieved more attention recently \cite{bronstein2017geometric, bruna2013spectral, defferrard2016convolutional, kipf2016semi, scarselli2009graph, gama2018mimo, gama2018convolutional, battaglia2018relational}.
-Classical so-called Spectral methods used the eigenvectors of the graph Laplacian to compute convolutions as in Bruna et al.~\cite{bruna2013spectral}, but requires an a-prior known graph structure. 
+Classical so-called Spectral methods used the eigenvectors of the graph Laplacian to compute convolutions as in Bruna et al.~\cite{bruna2013spectral}, but requires an a-priori known graph structure. 
 Non-spectral methods do not require a-priori knowledge \cite{bronstein2017geometric, kipf2016semi, scarselli2009graph, gama2018convolutional}.
@@
     Each feature in each image corresponds to a 3D point in the scene.
-    We can construct a cycle consistent embeddings of the features by mapping each one to the one-hot vector of its corresponding 3D point.
+    We can construct cycle consistent embeddings of the features by mapping each one to the one-hot vector of its corresponding 3D point.
     While there can be many features, there are fewer 3D points and thus this corresponds to a low rank factorization of the correspondence matrix.
@@
 Initialization Baseline            & 5.11e-1 $\pm$ 1.68e-2 & 2.56e-1 $\pm$ 2.06e-1 \\ \hline
-3 Views, Noiseless                 & 9.96e-1 $\pm$ 7.70e-3 & 1.16e-1 $\pm$ 1.32e-1 \\ \hline
+3 Views, Noiseless                 & 9.96e-1 $\pm$ 7.70e-3 & 1.16e-1 $\pm$ 1.32e-1 \\ 
 5 Views, Noiseless                 & 1.00e+0 $\pm$ 4.15e-4 & 1.22e-1 $\pm$ 1.67e-1 \\ \hline
-3 Views, Added Noise               & 9.96e-1 $\pm$ 7.70e-3 & 1.16e-1 $\pm$ 1.32e-1 \\ \hline
-3 Views, Added Noise               & 9.68e-1 $\pm$ 5.29e-2 & 9.50e-2 $\pm$ 1.58e-1 \\ \hline
-5 Views, Added Noise               & 9.89e-1 $\pm$ 2.47e-2 & 7.67e-2 $\pm$ 1.56e-1 \\ \hline
+3 Views, Added Noise               & 9.96e-1 $\pm$ 7.70e-3 & 1.16e-1 $\pm$ 1.32e-1 \\ 
+5 Views, Added Noise               & 9.89e-1 $\pm$ 2.47e-2 & 7.67e-2 $\pm$ 1.56e-1 \\ 
 6 Views, Added Noise               & 9.84e-1 $\pm$ 3.16e-2 & 7.46e-2 $\pm$ 1.57e-1 \\ \hline
-3 Views, 5\% Outliers              & 9.29e-1 $\pm$ 1.79e-1 & 1.41e-1 $\pm$ 1.48e-1 \\ \hline
+3 Views, 5\% Outliers              & 9.29e-1 $\pm$ 1.79e-1 & 1.41e-1 $\pm$ 1.48e-1 \\ 
 3 Views, 10\% Outliers             & 9.27e-1 $\pm$ 1.79e-1 & 1.40e-1 $\pm$ 1.51e-1 \\ \hline
@@
 \end{equation}
-Thus when visualizing embeddings, we rotate them to make them more interpretable (see figure CITE FIGURE).
+Thus when visualizing embeddings, we rotate them to make them more interpretable (see figure \ref{fig:embeddingsviz}).
 
@@
 \hline\hline
-MatchALS \cite{zhou2015multi} 15 Iterations               & 0.052 $\pm$ 0.003                   & 0.010 $\pm$ 0.002                   & 0.021 $\pm$ 0.003                   \\ \hline
-MatchALS \cite{zhou2015multi} 25 Iterations               & 0.045 $\pm$ 0.007                   & 0.009 $\pm$ 0.003                   & 0.034 $\pm$ 0.003                   \\ \hline
+MatchALS \cite{zhou2015multi} 15 Iterations               & 0.052 $\pm$ 0.003                   & 0.010 $\pm$ 0.002                   & 0.021 $\pm$ 0.003                   \\
+MatchALS \cite{zhou2015multi} 25 Iterations               & 0.045 $\pm$ 0.007                   & 0.009 $\pm$ 0.003                   & 0.034 $\pm$ 0.003                   \\
 MatchALS \cite{zhou2015multi} 50 Iterations               & 0.016 $\pm$ 0.008                   & 0.007 $\pm$ 0.003                   & 0.065 $\pm$ 0.006                   \\ \hline
-PGDDS \cite{leonardos2016distributed} 15 Iterations       & 0.016 $\pm$ 0.002                   & 0.006 $\pm$ 0.002                   & 0.287 $\pm$ 0.043                   \\ \hline
-PGDDS \cite{leonardos2016distributed} 25 Iterations       & 0.014 $\pm$ 0.002                   & 0.005 $\pm$ 0.002                   & 0.613 $\pm$ 0.089                   \\ \hline
+PGDDS \cite{leonardos2016distributed} 15 Iterations       & 0.016 $\pm$ 0.002                   & 0.006 $\pm$ 0.002                   & 0.287 $\pm$ 0.043                   \\
+PGDDS \cite{leonardos2016distributed} 25 Iterations       & 0.014 $\pm$ 0.002                   & 0.005 $\pm$ 0.002                   & 0.613 $\pm$ 0.089                   \\
 PGDDS \cite{leonardos2016distributed} 50 Iterations       & 0.013 $\pm$ 0.002                   & 0.005 $\pm$ 0.002                   & 1.430 $\pm$ 0.234                   \\ \hline
@@
 \textbf{GCN, 12 Layers (ours)}                            & \textbf{0.025} $\pm$ \textbf{0.003} & \textbf{0.016} $\pm$ \textbf{0.003} & \textbf{0.039} $\pm$ \textbf{0.009} \\
-\hline \hline\hline
+\hline\hline
 Method (4 Views)                                                         & $L_1$ Loss                          & $L_2$ Loss                          & Run Time (sec)                     \\
 \hline\hline
-MatchALS \cite{zhou2015multi} 15 Iterations                              & 0.064 $\pm$ 0.005                   & 0.012 $\pm$ 0.002                   & 0.030 $\pm$ 0.004                   \\  \hline
-MatchALS \cite{zhou2015multi} 25 Iterations                              & 0.041 $\pm$ 0.010                   & 0.008 $\pm$ 0.004                   & 0.048 $\pm$ 0.005                   \\  \hline
+MatchALS \cite{zhou2015multi} 15 Iterations                              & 0.064 $\pm$ 0.005                   & 0.012 $\pm$ 0.002                   & 0.030 $\pm$ 0.004                   \\
+MatchALS \cite{zhou2015multi} 25 Iterations                              & 0.041 $\pm$ 0.010                   & 0.008 $\pm$ 0.004                   & 0.048 $\pm$ 0.005                   \\
 MatchALS \cite{zhou2015multi} 50 Iterations                              & 0.011 $\pm$ 0.008                   & 0.005 $\pm$ 0.003                   & 0.094 $\pm$ 0.008                   \\ \hline
-PGDDS \cite{leonardos2016distributed} 15 Iterations                      & 0.015 $\pm$ 0.002                   & 0.006 $\pm$ 0.001                   & 0.436 $\pm$ 0.090                   \\  \hline
-PGDDS \cite{leonardos2016distributed} 25 Iterations                      & 0.014 $\pm$ 0.002                   & 0.005 $\pm$ 0.001                   & 0.961 $\pm$ 0.181                   \\  \hline
+PGDDS \cite{leonardos2016distributed} 15 Iterations                      & 0.015 $\pm$ 0.002                   & 0.006 $\pm$ 0.001                   & 0.436 $\pm$ 0.090                   \\
+PGDDS \cite{leonardos2016distributed} 25 Iterations                      & 0.014 $\pm$ 0.002                   & 0.005 $\pm$ 0.001                   & 0.961 $\pm$ 0.181                   \\
 PGDDS \cite{leonardos2016distributed} 50 Iterations                      & 0.013 $\pm$ 0.002                   & 0.005 $\pm$ 0.002                   & 2.056 $\pm$ 0.424                   \\ \hline
@@
 Results on Rome16K Correspondence graphs, showing the mean and standard deviation of the $L_1$ and $L_2$.
-Our method was not trained on ground truth corresopndences but using unsupervised methods and geometric side losses.
+Our method was not trained on ground truth correspondences but using unsupervised methods and geometric side losses.
 As our method gives soft labels, we use cannot use precision or recall as is standard in testing cycle consistency \cite{zhou2015multi}.
@@
 Our method performs better than 25 iteration of the MatchALS \cite{zhou2015multi} method, but does not perform as well as 50 iterations.
-Our network has only 12 layers, thus we have much greater efficiency per iteration.
+% Our network has only 12 layers, thus we have much greater efficiency per iteration.
 We do not perform as well as the Projected Gradient Descent Doubly Stochastic (PGDDS) \cite{leonardos2016distributed} but we perform significantly faster than them.
@@
 To generate the data, we generate $p$ points, each with its own randomly generated descriptor.
-To create the graph, we generate random permutation matrices, with a noise applied to it after generated.
+To create the graph, we generate random permutation matrices, with a noise applied to it after it is generated.
 % The initial descriptors we use as input we created using the true descriptor plus some added Gaussian noise.
@@
 The normalized noisy input descriptors are our baseline - they correlate with the true values but do not preserve the structure well.
-However, the GCN recovered the true structure very well, as shown in \ref{fig:synthtable}.
+However, the GCN recovered the true structure very well, as shown in Table \ref{fig:synthtable}.
 All experiments were run with a 12 layer GCN with the ReLU nonlinearity and skip connections.
@@
   % \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
-  \includegraphics[width=0.8\linewidth]{figures/EmbeddingsViz.pdf}
+  \includegraphics[width=0.8\linewidth]{figures/EmbeddingsViz.png}
   \end{center}
@@
 A long term goal is to incorporate learning image level features into this pipeline.
-Moreover we hope to adapt this method to a distributed setting, which would be simple given current approach.
+Moreover we hope to adapt this method to a distributed setting, which would be a simple extention given current approach.
 % , but with group norm, we cannot distribute in its current form.

### 2018-11-19 baselines/print_errors.py
Added time to baselines

@@ -5,7 +5,7 @@ import re
 
 import matplotlib.pyplot as plt
 
-egstr = '000000 Errors: L1: 5.297e-02, L2: 1.678e-02, BCE: 1.008e-01, Same sim: 8.776e-01 +/- 9.812e-02, Diff sim: 5.209e-02 +/- 1.182e-01, '
+egstr = '000000 Errors: L1: 5.297e-02, L2: 1.678e-02, BCE: 1.008e-01, Same sim: 8.776e-01 +/- 9.812e-02, Diff sim: 5.209e-02 +/- 1.182e-01, Time: 2.800e-02, '
 
 def stdagg(x):
   return np.sqrt(np.mean(np.array(x)**2))
@@ -22,15 +22,14 @@ def myformat_old(x):
 
 efmt = '[-+]?\d+\.\d*e[-+]\d+'
 disp_match = re.compile(efmt)
-names = ['l1', 'l2', 'bce', 'ssame_m', 'ssame_s', 'sdiff_m', 'sdiff_s']
-aggregators = [ np.mean, np.mean, np.mean, np.mean, stdagg, np.mean, stdagg ]
+names = ['l1', 'l2', 'bce', 'ssame_m', 'ssame_s', 'sdiff_m', 'sdiff_s', 'time']
 def parse(line):
   return dict(zip(names, [ float(x) for x in disp_match.findall(line) ]))
 
 agg_names = [ 'l1', 'l2', 'bce', 'ssame', 'sdiff' ]
 def agg(vals):
   aggs = dict(zip(agg_names, [ None for nm in agg_names ]))
-  for k in [ 'l1', 'l2', 'bce' ]:
+  for k in [ 'l1', 'l2', 'bce', 'time' ]:
     aggs[k] = (np.mean(vals[k]), np.std(vals[k]))
   for k in [ 'ssame', 'sdiff' ]:
     aggs[k] = ( np.mean(vals[k + '_m']), stdagg(vals[k + '_s']) )
@@ -43,11 +42,11 @@ def disp_val(aggs):
   #                   myformat(aggs['l2'][0]), myformat(aggs['l2'][1]),
   #                   myformat(aggs['bce'][0]), myformat(aggs['bce'][1])))
   # return 
-  fstr = "{:40} & {} $\pm$ {} & {} $\pm$ {} & {} $\pm$ {}"
+  fstr = "{:40} & {} $\pm$ {} & {} $\pm$ {} & {} $\pm$ {} \\\\ \\hline"
   print(fstr.format(fname, 
[…]

### 2018-11-19 baselines/run_tests.m

@@ -16,6 +16,7 @@ params200.maxiter = 200;
 
 %  'MatchALS400Iter', @(W)  mmatch_CVX_ALS(W, dimGroups, 'maxrank', p, 'maxiter', 400); ...
 %  'PGDDS200Iter', @(W) PGDDS(W, dimGroups, p, params200); ...
+%  'PGDDS100Iter', @(W) PGDDS(W, dimGroups, p, params100); ...
 test_fns = { ...
  'Spectral', @(W)  myspectral(W, p); ...
  'MatchALS015Iter', @(W)  mmatch_CVX_ALS(W, dimGroups, 'maxrank', p, 'maxiter', 15); ...
@@ -25,7 +26,6 @@ test_fns = { ...
  'PGDDS015Iter', @(W) PGDDS(W, dimGroups, p, params015); ...
  'PGDDS025Iter', @(W) PGDDS(W, dimGroups, p, params025); ...
  'PGDDS050Iter', @(W) PGDDS(W, dimGroups, p, params050); ...
- 'PGDDS100Iter', @(W) PGDDS(W, dimGroups, p, params100); ...
 };
 
 % disp_string =  [ '%06d Errors: ' ...
@@ -34,6 +34,7 @@ disp_string =  [ '%06d Errors: ' ...
                  'L1: %.03e, L2: %.03e, BCE: %.03e, ' ...
                  'Same sim: %.03e +/- %.03e, ' ...
                  'Diff sim: %.03e +/- %.03e, ' ...
+                 'Time: %.03e, ' ...
                  '\n' ];
 
 for test_fn_index = 1:size(test_fns,1)
@@ -44,6 +45,7 @@ for test_fn_index = 1:size(test_fns,1)
   ssame_s = [];
   sdiff_m = [];
   sdiff_s = [];
+  run_times = [];
   test_fn = test_fns{test_fn_index,2};
   fid = fopen(sprintf('%sTestErrors.log', test_fns{test_fn_index,1}), 'w');
   fprintf('%s Method:\n', test_fns{test_fn_index,1})
@@ -58,12 +60,16 @@ for test_fn_index = 1:size(test_fns,1)
     ssame_s_ = zeros(mat_length,1);
     sdiff_m_ = zeros(mat_length,1);
     sdiff_s_ = zeros(mat_length,1);
+    run_times_ = zeros(mat_length,1);
     for index = 1:mat_length
[…]

### 2018-11-19 test.py
Added time measurements to test.py

@@ -3,6 +3,7 @@ import os
 import sys
 import glob
 import numpy as np
+import time
 
 import tensorflow as tf
 
@@ -58,8 +59,8 @@ def get_test_losses(opts, sample, output, return_gt=False, name='loss'):
   return gt_l1_loss, gt_l2_loss, gt_bce_loss, ssame_m, ssame_var, sdiff_m, sdiff_var
 
 def build_test_session(opts):
-  config = tf.ConfigProto()
-  config.gpu_options.allow_growth = True
+  config = tf.ConfigProto(device_count = {'GPU': 0})
+  # config.gpu_options.allow_growth = True
   return tf.Session(config=config)
 
 
@@ -76,9 +77,10 @@ def test_values(opts):
 
   # Tensorflow and logging operations
   disp_string =  '{:06d} Errors: ' \
-                 'L1: {:.03e},  L2: {:.03e}, BCE: {:.03e} ' \
-                 'Same sim: {:.03e} +/- {:.03e} ' \
-                 'Diff sim: {:.03e} +/- {:.03e}' 
+                 'L1: {:.03e},  L2: {:.03e}, BCE: {:.03e}, ' \
+                 'Same sim: {:.03e} +/- {:.03e}, ' \
+                 'Diff sim: {:.03e} +/- {:.03e}, ' \
+                 'Time: {:.03e}, '
 
 
   # Build session
@@ -93,8 +95,10 @@ def test_values(opts):
       saver.restore(sess, tf.train.latest_checkpoint(opts.save_dir))
       for i, npz_file in enumerate(npz_files):
         sample_ = { k : np.expand_dims(v,0) for k, v in np.load(npz_file).items() }
+        start_time = time.time()
         vals = sess.run(losses, { sample[k] : sample_[k] for k in sample.keys() })
-        dstr = disp_string.format(i, *vals)
+        end_time = time.time()
+        dstr = disp_string.format(i, *vals, end_time - start_time)
         print(dstr)
         log_file.write(dstr)
         log_file.write('\n')

### 2018-11-19 cvpr2019/main.tex

--- 2018-11-16 cvpr2019/main.tex
@@
 % Cycle Consistent Multi-View Representations Using Graph CNNs}
-\title{All Graphs Lead to Rome: Learning Geometric and Cycle Consistent Representations with Graph CNNs}
+\title{All Graphs Lead to Rome: Learning Geometric and Cycle Consistent Representations with Graph Convolutional Networks}
 
@@
     Image feature matching is a fundametal part of many geometric computer vision applications, and using multiple images can improve performance.
-    In this work, we formulate the multi-image matching problem as a graph embedding problem then use a Graph Neural Network to learn an appropriate embedding function for aligning image features.
+    In this work, we formulate the multi-image matching problem as a graph embedding problem then use a Graph Convolutional Network to learn an appropriate embedding function for aligning image features.
 % How to talk about the universe of features here without going too much into the weeds??
@@
 Other works, such as Wang et al. \cite{wang2017multi}, have shown improvement in performance by enforcing consistency between multiple images.
-% However we still have not fully answered the question: What are the best image features to describe multiple views of the same scene?
 
-Deep learning has revolutionized how image features are computed \cite{yi2016lift}, and so we would like to leverage this to compute better scene features.
-Typically when applied to image or feature matching, deep neural networks (DNNs) are trained with photometric losses, directly using pixel color values.
-However direct, pixel-based losses have are not robust to the many confounding factors in the environment, such as lighting and view-point changes.
-Using features designed to deal with these condfounding factors improves robustness to them, 
-and learning may improve robustness even further.
+However, these multi-view consistency algorithms struggle in distributed and robust settings.
+Deep learning has revolutionized how image features are computed \cite{yi2016lift}, and so we would like to leverage this to compute better and more robust multi-view scene features.
+Graph Convolutional Networks \cite{kipf2016semi} also show promise using learning in a distributed setting.
+Thus deep learning seems a promising tool to help solve this problem.
+% Typically when applied to image or feature matching, deep neural networks (DNNs) are trained with photometric losses, directly using pixel color values.
+% However direct, pixel-based losses have are not robust to the many confounding factors in the environment, such as lighting and view-point changes.
+% Using features designed to deal with these condfounding factors improves robustness to them, and learning may improve robustness even further.
 
@@
     In this example, an error in matching leads to an inconsistent cycle (shown in red), ideally these pairwise matches would be consistent.
-    We improve consistency between pairwise matches in the multi-view matching problem by training a neural net with cycle consistency.
+    We improve the quality of pairwise matches in the multi-view matching problem by training a neural net with cycle consistency.
   }
@@
   \caption{
-    An outline of the pipeline of this work.
+    An illustration of the approach of this work.
     The Graph Convolutional Neural Network (GCN) \cite{kipf2016semi} takes as input the graph of matches and then outputs a low rank embedding of the adjacency matrix of the graph.
@@
     In the figure, the the GCN node embeddings are represented by different colors.
-    The final embedding is used to construct a pairwise similarity matrix, which ideally should be a low dimensional cycle consistent representation of the graph adjacency matrix.
-    We train the network using a reconstruction loss on the similarity matrix.
+    The final embedding is used to construct a pairwise similarity matrix, which we train to be a low dimensional cycle consistent representation of the graph adjacency matrix, thus pruning the erroneous matches.
+    We train the network using a reconstruction loss on the similarity matrix with the noisy adjacency matrix, and thus do not need ground truth matches.
     In addition, we can use geometric information at to assist training the network, even if we do not have that geometric information at testing time such as epipolar constraints on the point locations or higher order geometric constraints.
@@
 
-Unfortunately, there are obstacles to applying multi-view constraints directly to learning. 
+Unfortunately, there are obstacles to applying multi-view constraints directly to deep learning. 
 To train networks, we need a large amount of labelled data.
@@
 
-In this work, we propose to solve these problems using a Graph Neural Network (GNN) to operate on the correspondence graph.
-The proposed method works on the correspondence graph, which is agnostic to how the correspondnces were computed, thus allowing the algorithm to work in a broad class of environments.
-
-We use a unsupervised loss, the cycle consistency loss, to train the network.
+In this work, we propose to solve these problems using a Graph Convolutional Network (GCN) to operate on the correspondence graph.
+The proposed method works directly on the correspondence graph, which is agnostic to how the correspondnces were computed, thus allowing the algorithm to work in a broad class of environments.
+To the best of our knowledge this work is the first to apply deep learning to the multi-view feature matching problem.
+We use a unsupervised loss, the cycle consistency loss, to train the network, and thus we avoid the difficulty of expensive hand labelling.
 We add in geometric consistency losses to help training, which works even when the geometric information is not available at test time.
+Our simple network already has promising results compared to previous optimization based baselines.
 Our contributions are:
@@
 
+\subsection{Feature Matching}
 Matching has a rich history of research in computer vision.
@@
 
+\subsection{Multi-image Matching}
 Multi-image matching has traditionally been done using optimization based methods minimizing a cycle consistency based loss (see Section 3.3).
@@
 Thus they are robust to small Gaussian noise but not to more realistic noise.
-Zhou et al. \cite{zhou2015multi} and Wang et al. \cite{wang2017multi} use most sophisticated optimization techniques on the matching matrix and thus are quite robust.
-Leonardos et al. \cite{leonardos2016distributed} implement a distributed optimizaiton scheme to solve for cycle consistency.
+Zhou et al. \cite{zhou2015multi} and Wang et al. \cite{wang2017multi} use most sophisticated optimization techniques on the matching matrix and thus produce more robust solutions.
+Leonardos et al. \cite{leonardos2016distributed} implement a distributed optimization scheme to solve for cycle consistency.
 As an alternative to optimization based techiniques, Tron et al. \cite{tron2017fast} used density based clustering techniques to compute multi-image correspondence.
+To the best of our knowledge, we are the first work to use neural networks for multi-image matching.
 
+\subsection{Deep Learning for Matching}
 Previous attempts to improve image matching techniques using machine learning have focused on learning the descriptors given ground truth correspondence from curated datasets \cite{zagoruyko2015learning, yi2016lift, brachmann2017dsac}.
@@
 
+\subsection{Graph Neural Networks}
 Graph neural networks have been getting more attention recently \cite{bronstein2017geometric, bruna2013spectral, defferrard2016convolutional, kipf2016semi, scarselli2009graph, gama2018mimo, gama2018convolutional, battaglia2018relational}.
@@
     Each feature in each image corresponds to a 3D point in the scene.
-    Therefore, we can get the points to have a cycle consistent embedding by mapping each feature in each image to the one-hot vector of its corresponding 3D point.
-    While there can be many features, there are much fewer 3D points and thus this corrsponds to a low rank factorization of the corrspondence matrix.
+    We can get the points to have a cycle consistent embedding by mapping each feature in each image to the one-hot vector of its corresponding 3D point.
+    While there can be many features, there are many fewer 3D points and thus this corrsponds to a low rank factorization of the corrspondence matrix.
     Best viewed in color.
@@
 Here $\mathcal{D}$ could be an $L_2$ loss, $L_1$ loss, or many others. In this work, we use the $L_1$ loss. 
+Note that because of this formulation, we can determine our embeddings only up to a rotation on the right, as
+\begin{equation}
+\mat{E}R(\mat{E}R)^\top
+= \mat{E}RR^\top\mat{E}^\top
+= \mat{E}\mat{E}^\top
+\label{eq:rotinvar}
+\end{equation}
+and
 
@@
 
+% MatchALS \cite{zhou2015multi} 400 Iterations              & 0.007 $\pm$ 0.003 & 0.007 $\pm$ 0.003 & 0.007 $\pm$ 0.003 \\ \hline
+% PGDDS \cite{leonardos2016distributed} 200 Iterations      & 0.013 $\pm$ 0.002 & 0.005 $\pm$ 0.002 & 0.005 $\pm$ 0.002 & 0.039 $\pm$ 0.039 \\ \hline
 \begin{table*}
@@
 \hline
-Method                                                    & $L_1$ Loss        & $L_2$ Loss         \\
-
-\hline\hline\hline
-MatchALS \cite{zhou2015multi} 15 Iterations               & 0.052 $\pm$ 0.003 & 0.010 $\pm$ 0.002 \\ \hline
-MatchALS \cite{zhou2015multi} 25 Iterations               & 0.045 $\pm$ 0.007 & 0.009 $\pm$ 0.003 \\ \hline
-MatchALS \cite{zhou2015multi} 50 Iterations               & 0.016 $\pm$ 0.008 & 0.007 $\pm$ 0.003 \\ \hline
-MatchALS \cite{zhou2015multi} 100 Iterations              & 0.007 $\pm$ 0.003 & 0.007 $\pm$ 0.003 \\ \hline
-% MatchALS \cite{zhou2015multi} 400 Iterations              & 0.007 $\pm$ 0.003 & 0.007 $\pm$ 0.003 \\ \hline
-PGDDS \cite{leonardos2016distributed} 15 Iterations       & 0.016 $\pm$ 0.002 & 0.006 $\pm$ 0.002 \\ \hline
-PGDDS \cite{leonardos2016distributed} 50 Iterations       & 0.013 $\pm$ 0.002 & 0.005 $\pm$ 0.002 \\ \hline
-PGDDS \cite{leonardos2016distributed} 100 Iterations      & 0.013 $\pm$ 0.002 & 0.005 $\pm$ 0.002 \\ \hline
-% PGDDS \cite{leonardos2016distributed} 200 Iterations      & 0.013 $\pm$ 0.002 & 0.005 $\pm$ 0.002 & 0.039 $\pm$ 0.039 \\ \hline
-Spectral                                                  & 0.054 $\pm$ 0.005 & 0.018 $\pm$ 0.004 \\ \hline \hline
-GNN, 12 Layers (ours)                                     & 0.025 $\pm$ 0.003 & 0.016 $\pm$ 0.003 \\
-\hline
+Method (3 Views)                                          & $L_1$ Loss                          & $L_2$ Loss                          & Run Time (sec) (TODO: Fill out)    \\
+\hline\hline
+MatchALS \cite{zhou2015multi} 15 Iterations               & 0.052 $\pm$ 0.003                   & 0.010 $\pm$ 0.002                   & 0.010 $\pm$ 0.002 \\ \hline
+MatchALS \cite{zhou2015multi} 25 Iterations               & 0.045 $\pm$ 0.007                   & 0.009 $\pm$ 0.003                   & 0.009 $\pm$ 0.003 \\ \hline
+MatchALS \cite{zhou2015multi} 50 Iterations               & 0.016 $\pm$ 0.008                   & 0.007 $\pm$ 0.003                   & 0.007 $\pm$ 0.003 \\ \hline
+MatchALS \cite{zhou2015multi} 100 Iterations              & 0.007 $\pm$ 0.003                   & 0.007 $\pm$ 0.003                   & 0.007 $\pm$ 0.003 \\ \hline
+PGDDS \cite{leonardos2016distributed} 15 Iterations       & 0.016 $\pm$ 0.002                   & 0.006 $\pm$ 0.002                   & 0.006 $\pm$ 0.002 \\ \hline
+PGDDS \cite{leonardos2016distributed} 50 Iterations       & 0.013 $\pm$ 0.002                   & 0.005 $\pm$ 0.002                   & 0.005 $\pm$ 0.002 \\ \hline
+PGDDS \cite{leonardos2016distributed} 100 Iterations      & 0.013 $\pm$ 0.002                   & 0.005 $\pm$ 0.002                   & 0.005 $\pm$ 0.002 \\ \hline
+Spectral                                                  & 0.054 $\pm$ 0.005                   & 0.018 $\pm$ 0.004                   & 0.018 $\pm$ 0.004 \\ \hline 
+\textbf{GNN, 12 Layers (ours)}                            & \textbf{0.025} $\pm$ \textbf{0.003} & \textbf{0.016} $\pm$ \textbf{0.003} & \textbf{0.016} $\pm$ \textbf{0.003} \\
+\hline \hline\hline
+Method (4 Views)                                          & $L_1$ Loss                          & $L_2$ Loss                          & Run Time (sec) (TODO: Fill out)   \\
+\hline\hline
+MatchALS \cite{zhou2015multi} 15 Iterations               & 0.052 $\pm$ 0.003                   & 0.010 $\pm$ 0.002                   & 0.010 $\pm$ 0.002 \\ \hline
+MatchALS \cite{zhou2015multi} 25 Iterations               & 0.045 $\pm$ 0.007                   & 0.009 $\pm$ 0.003                   & 0.009 $\pm$ 0.003 \\ \hline
+MatchALS \cite{zhou2015multi} 50 Iterations               & 0.016 $\pm$ 0.008                   & 0.007 $\pm$ 0.003                   & 0.007 $\pm$ 0.003 \\ \hline
+MatchALS \cite{zhou2015multi} 100 Iterations              & 0.007 $\pm$ 0.003                   & 0.007 $\pm$ 0.003                   & 0.007 $\pm$ 0.003 \\ \hline
+PGDDS \cite{leonardos2016distributed} 15 Iterations       & 0.016 $\pm$ 0.002                   & 0.006 $\pm$ 0.002                   & 0.006 $\pm$ 0.002 \\ \hline
+PGDDS \cite{leonardos2016distributed} 50 Iterations       & 0.013 $\pm$ 0.002                   & 0.005 $\pm$ 0.002                   & 0.005 $\pm$ 0.002 \\ \hline
+PGDDS \cite{leonardos2016distributed} 100 Iterations      & 0.013 $\pm$ 0.002                   & 0.005 $\pm$ 0.002                   & 0.005 $\pm$ 0.002 \\ \hline
+Spectral                                                  & 0.054 $\pm$ 0.005                   & 0.018 $\pm$ 0.004                   & 0.018 $\pm$ 0.004 \\ \hline 
+\textbf{GNN, 12 Layers (ours)}                            & \textbf{0.025} $\pm$ \textbf{0.003} & \textbf{0.016} $\pm$ \textbf{0.003} & \textbf{0.016} $\pm$ \textbf{0.003} \\
 \end{tabular}
@@
 
-We have shown a novel method for training feature matching.
+We have shown a novel method for training feature matching using GCNs and an unsupervised cycle consistency loss.
 This method can be employed even when labelled training data is not available, but can still incorporate geometric consistency into its losses.
-We have demonstrated its effectiveness using experiments on the Rome16K dataset compared to the traditional optimization based baselines.
+We have demonstrated its effectiveness on the Rome16K dataset compared to the traditional optimization based baselines on a simple GCN.
 For future work we will investigate using more robust losses for outlier rejection and using higher order geometric constraints, such as the trifocal tensor, as additional loss terms.
-A long term goal is to incorporate learning image level features into this pipeline
-Moreover we hope to make this method distributed - with group norm, we cannot distribute in its current form.
+A long term goal is to incorporate learning image level features into this pipeline.
+Moreover we plan to focus on making this method work in a distributed setting, which we could do with very small changes to the current approach.
+% , but with group norm, we cannot distribute in its current form.
 

### 2018-12-04 model/skip_networks.py
Additional models for supplemental

@@ -112,6 +112,57 @@ class GraphLongSkipLayerNetwork(snt.AbstractModule):
       output = tf.nn.l2_normalize(output, axis=2)
     return output
 
+class GraphSkipHopLayerNetwork(GraphLongSkipLayerNetwork):
+  def __init__(self,
+               opts,
+               arch,
+               use_bias=True,
+               initializers=None,
+               regularizers=None,
+               custom_getter=None,
+               name="graphnn"):
+    super(GraphSkipHopLayerNetwork, self).__init__(opts,
+                                                   arch,
+                                                   use_bias=use_bias,
+                                                   initializers=initializers,
+                                                   regularizers=regularizers,
+                                                   custom_getter=custom_getter,
+                                                   name=name)
+    lin_regularizers = None
+    if regularizers is not None:
+      lin_regularizers = { k:v
+                           for k, v in regularizers.items()
+                           if k in ["w", "b"] }
+    self._hop_layers = [
+      layers.EmbeddingLinearLayer(
+        output_size=arch.layer_lens[skip_idx],
+        initializers=initializers,
+        regularizers=lin_regularizers,
+        name="{}/hop".format(name))
+      for skip_idx in self._skip_layer_idx[1:]
+    ]
+
+  def _build(self, laplacian, init_embeddings):
+    """Applying this graph network to sample"""
+    output = init_embeddings
+    sk = 0
+    last_skip = None
+    for i, layer in enumerate(self._layers):
+      if i in self._skip_layer_idx:
+        output = layer(laplacian, output)
+        skip_add = self._skip_layers[sk](laplacian, init_embeddings)
+        output = output + skip_add
+        if last_skip is not None:
+          hop_add = self._hop_layers[sk-1](laplacian, last_skip)
+          output = output + hop_add
+        last_skip = output
+        sk += 1
+      else:
+        output = layer(laplacian, output)
+    if self.normalize_emb:
+      output = tf.nn.l2_normalize(output, axis=2)
+    return output
+
 class GraphLongSkipNormedNetwork(GraphLongSkipLayerNetwork):
   def __init__(self,
                opts,

### 2018-12-04 options.py

@@ -62,7 +62,7 @@ class ArchParams(argparse.Namespace):
 arch_choices = [
   'vanilla', 'vanilla0', 'vanilla1',
   'skip', 'skip0', 'skip1',
-  'longskip0', 'longskip1',
+  'longskip0', 'longskip1', 'longskip2', 'longskip3',
   'normedskip0', 'normedskip1', 'normedskip2', 'normedskip3',
   'attn0', 'attn1', 'attn2',
   'spattn0', 'spattn1', 'spattn2',
@@ -338,11 +338,11 @@ def get_opts():
     arch.layer_lens=[ 2**min(5+k,9) for k in range(5) ]
   elif opts.architecture in ['vanilla1', 'skip1', 'attn2', 'spattn2']:
     arch.layer_lens=[ 2**min(5+k,9) for k in range(5) ]
-  elif opts.architecture in ['longskip0', 'normedskip0', 'normedskip2']:
+  elif opts.architecture in ['longskip0', 'longskip2', 'normedskip0', 'normedskip2']:
     arch.layer_lens=[ 32, 64, 128, 256, 512, 512, 512,
                       512, 512, 512, 1024, 1024 ]
     arch.skip_layers = [ len(arch.layer_lens)//2, len(arch.layer_lens) - 1 ]
-  elif opts.architecture in ['longskip1', 'normedskip1', 'normedskip3']:
+  elif opts.architecture in ['longskip1', 'longskip3', 'normedskip1', 'normedskip3']:
     arch.layer_lens=[ 32, 64, 128, 256, 512, 512,
                       512, 512, 512, 1024, 1024,
                       512, 512, 512, 1024, 1024 ]

### 2018-12-04 cvpr2019/supplemental.tex

--- 2018-11-19 cvpr2019/main.tex
@@
 %\ifcvprfinal\pagestyle{empty}\fi
-\setcounter{page}{1}
+\setcounter{page}{9}
 \begin{document}
@@
 % Cycle Consistent Multi-View Representations Using Graph CNNs}
-\title{All Graphs Lead to Rome: Learning Geometric and Cycle Consistent Representations with Graph Convolutional Networks}
+\title{All Graphs Lead to Rome: Learning Geometric and Cycle-Consistent Representations with Graph Convolutional Networks \\
+Supplemental Material}
 
 \author{Stephen Phillips, Kostas Daniilidis \\
-GRASP Labratory, University of Pennsylvania\\
+GRASP Laboratory, University of Pennsylvania\\
 {\tt\small \{stephi, kostas\}@seas.upenn.edu}
@@
 % must be no longer than eight pages in length. The references section
+%%%%%%%%% BODY TEXT
+\section*{A. Relative Efficiency Against Optimization Based Methods}
 
-%%%%%%%%% ABSTRACT
-% We present a learning technique for refining multi-image feature matches in an unsupervised fashion.
-\begin{abstract}
-    Image feature matching is a fundametal part of many geometric computer vision applications, and using multiple images can improve performance.
-    In this work, we formulate the multi-image matching problem as a graph embedding problem then use a Graph Convolutional Network to learn an appropriate embedding function for aligning image features.
-% How to talk about the universe of features here without going too much into the weeds??
-    We use cycle consistency to train our network in an unsupervised fashion since ground truth correspondence is difficult or expensive to come by in many real world datasets.
-    In addtion, geometric consistency losses can be added at train time, even if the information is not available in the test set, unlike previous optimization based methods.
-    To the best of our knowledge, no other works have used learning for multi-image feature matching.
-    Our experiments show that our method is competitive with other optimization based approaches.
-\end{abstract}
+In figure \ref{fig:iterplot} we show a more fine grained comparison of our algorithm to optimization based methods at different numbers of iterations.
+We show the mean and standard devation of the errors of all methods, testing the optimization based methods at different iterations.
 
-%%%%%%%%% BODY TEXT
-\section{Introduction}
-
-Feature matching is an essential part of Structure from Motion and many geometric computer vision applications.
-The goal in multi-image feature matching is to take 2D image locations from three or more images and find which ones correspond to the same point in the 3D scene.
-Methods such as SIFT feature matching \cite{lowe2004distinctive} and RANSAC \cite{fischler1981random} have been standard for solving this for decades.
-However RANSAC-based approaches are limited for matching pairs of images.
-Other works, such as Wang et al. \cite{wang2017multi}, have shown improvement in performance by enforcing consistency between multiple images.
-
-However, these multi-view consistency algorithms struggle in distributed and robust settings.
-Deep learning has revolutionized how image features are computed \cite{yi2016lift}, and so we would like to leverage this to compute better and more robust multi-view scene features.
-Graph Convolutional Networks \cite{kipf2016semi} also show promise using learning in a distributed setting.
-Thus deep learning seems a promising tool to help solve this problem.
-% Typically when applied to image or feature matching, deep neural networks (DNNs) are trained with photometric losses, directly using pixel color values.
-% However direct, pixel-based losses have are not robust to the many confounding factors in the environment, such as lighting and view-point changes.
-% Using features designed to deal with these condfounding factors improves robustness to them, and learning may improve robustness even further.
-
-\begin{figure}[t]
+%------------------------------------------------------------------------
+\begin{figure*}[ht]
 \begin{center}
-  % \fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-  \includegraphics[width=0.8\linewidth]{figures/CycleConsistencyBasic.pdf}
+  \includegraphics[width=0.9\linewidth]{figures/IterationsPlot.pdf}
 \end{center}
   \caption{
-    Example of multi-image matching, with images from Rome16K dataset \cite{li2010location}.
-    In this example, an error in matching leads to an inconsistent cycle (shown in red), ideally these pairwise matches would be consistent.
-    We improve the quality of pairwise matches in the multi-view matching problem by training a neural net with cycle consistency.
+    This figure plots the average accuracy of the optimization methods by iteration compared to 12 iterations of our GCN based method.
+    The bold center line shows the mean, the colored in region shows 1 standard devation of the errors.
+    As we optimize for $L_1$ error, our method's $L_1$ loss is substantially better than its $L_2$ losses.
+    The right most plot shows time, plotted on a log scale for clarity.
   }
-\label{fig:cycconsistex}
-\label{fig:onecol}
-\end{figure}
-
-%------------------------------------------------------------------------
-\begin{figure*}[t]
-\begin{center}
-  % \fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-  \includegraphics[width=0.8\linewidth]{figures/CycleConsistencyMainFigure.pdf}
-\end{center}
-  \caption{
-    An illustration of the approach of this work.
-    The Graph Convolutional Neural Network (GCN) \cite{kipf2016semi} takes as input the graph of matches and then outputs a low rank embedding of the adjacency matrix of the graph.
-    The GCN operates on an embedding over the nodes of the graph.
-    In the figure, the the GCN node embeddings are represented by different colors.
-    The final embedding is used to construct a pairwise similarity matrix, which we train to be a low dimensional cycle consistent representation of the graph adjacency matrix, thus pruning the erroneous matches.
-    We train the network using a reconstruction loss on the similarity matrix with the noisy adjacency matrix, and thus do not need ground truth matches.
-    In addition, we can use geometric information at to assist training the network, even if we do not have that geometric information at testing time such as epipolar constraints on the point locations or higher order geometric constraints.
-  }
-\label{fig:pipeline}
+\label{fig:iterplot}
 \label{fig:onecol}
@@
 
-Unfortunately, there are obstacles to applying multi-view constraints directly to deep learning. 
-To train networks, we need a large amount of labelled data.
-In the case of multi-image feature matching, one would need to hand label point correspondences between images, which is difficult and expensive to obtain.
-Multi-view constraints are formulated in terms of sparse features, which traditional convolutional deep neural nets (CNNs) are not designed to handle such input.
-In the case of multi-image feature matching, geometric constraints would be helpful in rejecting outlier matches.
+\section*{B. Effect of Group Normalization}
+We observe that training with group normalization helps with training and generalization error, as shown in figure \ref{fig:groupnorm}.
+As the Group Normalization operation is not easily parallelized across nodes in the graph, the use of Group Normalization is the main barrier to parallelization.
+Thus we will need to find alternative more parallelizable methods to improve generalization error for future work.
 
-In this work, we propose to solve these problems using a Graph Convolutional Network (GCN) to operate on the correspondence graph.
-The proposed method works directly on the correspondence graph, which is agnostic to how the correspondnces were computed, thus allowing the algorithm to work in a broad class of environments.
-To the best of our knowledge this work is the first to apply deep learning to the multi-view feature matching problem.
-We use a unsupervised loss, the cycle consistency loss, to train the network, and thus we avoid the difficulty of expensive hand labelling.
-We add in geometric consistency losses to help training, which works even when the geometric information is not available at test time.
-Our simple network already has promising results compared to previous optimization based baselines.
-Our contributions are:
-\begin{itemize}
-\item We use a novel architecture to address multi-image feature matching problem using GNNs with graph embeddings.
-\item We introduce an unsupervised cycle consistency loss that does not require labelled correspondences to train.
-\item We demonstrate the effectiveness of geometric consistency losses in improving training.
-\item We perform experiments on the Rome16K \cite{li2010location} dataset to test the effectiveness of our method compared to optimization based baselines.
-\end{itemize}
-
-%-------------------------------------------------------------------------
-\section{Related Work}
-
-\subsection{Feature Matching}
-Matching has a rich history of research in computer vision.
-The most well known and widely used method for image matching is RANSAC \cite{fischler1981random}.
-RANSAC, combined with hand-crafted feature descriptors like SIFT \cite{lowe2004distinctive}, SURF \cite{bay2006surf}, BRIEF \cite{calonder2012brief}, or ORB \cite{mur2015orb}, has constituted the bulk of the matching literature for the last 40 years.
-To improve matching of all the features of the image, graph matching \cite{suh2015subgraph, hu2016distributable} can be used for more robust matches.
-
-\subsection{Multi-image Matching}
-Multi-image matching has traditionally been done using optimization based methods minimizing a cycle consistency based loss (see Section 3.3).
-Pachauri et al. \cite{pachauri2013solving} and Arrigoni et al. \cite{arrigoni2017synchronization} use the eigenvectors of the matching matrix to obtain a low dimensional embedding. 
-Thus they are robust to small Gaussian noise but not to more realistic noise.
-Zhou et al. \cite{zhou2015multi} and Wang et al. \cite{wang2017multi} use most sophisticated optimization techniques on the matching matrix and thus produce more robust solutions.
-Leonardos et al. \cite{leonardos2016distributed} implement a distributed optimization scheme to solve for cycle consistency.
-As an alternative to optimization based techiniques, Tron et al. \cite{tron2017fast} used density based clustering techniques to compute multi-image correspondence.
-To the best of our knowledge, we are the first work to use neural networks for multi-image matching.
-
-\subsection{Deep Learning for Matching}
-Previous attempts to improve image matching techniques using machine learning have focused on learning the descriptors given ground truth correspondence from curated datasets \cite{zagoruyko2015learning, yi2016lift, brachmann2017dsac}.
-This approach is limited if you do not have the ability to get the ground truth correspondences.
-There are other methods to build correspondences such as Choy et al. \cite{choy2016universal}, but it only handles two-view constraints and requires dense correspondences.
-Most similar to ours, Yi et al. \cite{yi2018learning} attempts to improve correspondences by learning match probabilites for RANSAC to speed up test time running.
-However, they only focus on two view tests and do not exploit the advantages of the correspondence structure.
-
-\subsection{Graph Neural Networks}
-Graph neural networks have been getting more attention recently \cite{bronstein2017geometric, bruna2013spectral, defferrard2016convolutional, kipf2016semi, scarselli2009graph, gama2018mimo, gama2018convolutional, battaglia2018relational}.
-Classical so-called Spectral methods used the eigenvectors of graph Laplacian to compute convolutions like in Bruna et al.
-\cite{bruna2013spectral}, but requires a fixed graph structure known a-priori.
-Non-spectral methods do not require a-priori knowledge \cite{bronstein2017geometric, kipf2016semi, scarselli2009graph, gama2018convolutional}.
-Most of these simply use polynomials of the graph Laplacian to compute neighborhood averages.
-Gama et al.
-2018 \cite{gama2018mimo, gama2018convolutional} formalize this notion and generalize it beyond the use of the graph Laplacian.
-To improve performance, more sophisticated aggregation techniques and global information passing can be used as discussed in Battaglia et al. \cite{battaglia2018relational}.
-
-\section{Method}
-
-\begin{figure}[t]
+%------------------------------------------------------------------------
+\begin{figure*}[ht]
 \begin{center}
-  \includegraphics[width=0.9\linewidth]{figures/UniverseOfFeatures.pdf}
+  \includegraphics[width=0.9\linewidth]{figures/GroupNormTest.pdf}
 \end{center}
   \caption{
-    Illustration of the universe of features.
-    Each feature in each image corresponds to a 3D point in the scene.
-    We can get the points to have a cycle consistent embedding by mapping each feature in each image to the one-hot vector of its corresponding 3D point.
-    While there can be many features, there are many fewer 3D points and thus this corrsponds to a low rank factorization of the corrspondence matrix.
-    Best viewed in color.
+    This figure plots the training curves of the network with and without Group Normalization.
+    Note that while the train/test curves are fairly similar with or without Group Normalization, distance to the ground truth is improved greatly with Group Normalization.
   }
-\label{fig:universefeatures}
+\label{fig:groupnorm}
 \label{fig:onecol}
-\end{figure}
-Our goal is to learn optimal features that capture multiple image views by way of filtering out noisy feature matches.
-The input to our algorithm is a set of features and noisy correspondences, and the output is a new set of features where the pairwise similarities of these features correspond to the true matches.
-We do this by learning training the new set of feature embeddings to be cycle consistent.
-We formulate this problem in terms of the correspondence graph of the features.
-Vectors $\mat{x}$ and matrices $\mat{A}$ are denoted with boldface, and the $i^{th}$ row of a matrix is denoted $(\mat{A})_i$.
-\subsection{Correspondence Graph}
-We assume we have an initial set of feature matches represented as a graph $\mathcal{G} = (\mathcal{V}, \mathcal{E})$.
-Each vertex $v$ of the graph is a feature with its associated descriptor $f_v$. 
-The graph is represented by its Weighted Adjacency Matrix $\mat{A}(\mathcal{G}) \in \bR^{n \times n}$, where $(\mat{A}(\mathcal{G}))_{ij}$ is the strength of the match between nodes $i$ and $j$.
-We also have the positive diagonal degree matrix $\mat{D}(\mathcal{G}) \in \bR^{n \times n}$, with $\mat{D}(\mathcal{G})_{ii} = \sum_j (\mat{A}(\mathcal{G}))_{ij}$.
-For brevity we denote these matrices $\mat{A}$ and $\mat{D}$ respectively.
-We can get our an embedding matrix $\mat{E}_0$ by concatenating the features $f_v$ from each of the vertices.
-We use $\mat{E}_0$ as the initializiation for our learning algorithm.
-We add any additional knowledge we have into the embedding as well (e.g. scale, orientation, etc.).
-Putative correspondences are computed from these features and represented by weighted edges in which the weight gives the strength of the match.
-While there are many interesting methods for computing these putative correspondences \cite{suh2015subgraph, yi2018learning}, we do not explore them in this work.
-
-In the absense of noise or outliers, this graph would have a connected component for each visible point in the world.
-These components should be mutually disjoint. 
-In other words each feature would only have edges to other features corresponding to the same point.
-Since features in this case represent unique location in the scene, no points in the same image would have edges between them.
-In the noisy case we expect this structure to be corrupted and thus we need to refine out the erroneous edges.
-
-To compute this matching graph, we do pairwise feature matching between the images, creating putative correspondences for each of the features.
-Typically these putative correspondences are matched probabilistically, meaning a feature in one image matches to many features in another.
-This could come from repeated structures in the scene, ambiguity from the low-level feature descriptors, or just an error in the matching algorithm.
-Filtering out these noisy matches is our primary learning goal.
-
-However, this graph structure does not have a regular grid structure and thus we cannot use standard CNNs to learn features for this task.
-Instead we use graph convolutions to learn feature representations on this space.
-We describe our approach in the next section.
-
-\subsection{Graph Neural Networks}
-As input to our method we are given the graph Laplacian $\mat{L} \in \bR^{n \times n}$ to encode the graph structure:
-\begin{equation}
-  \mat{L} =\; \mat{I} - \mat{D}^{-1/2} \mat{A} \mat{D}^{-1/2} \\
-\end{equation}
-and an initial embedding $\mat{E}_0 \in \bR^{n \times m_0}$.
-Many older methods assume $\mat{L}$ is known a-priori \cite{bruna2013spectral}, and thus can encode graph convolutions using the eigenvectors of $L$.
-We do not have this luxury, as the correspondence structure changes from image to image, and thus we use non-spectral GNNs. The standard form of non-spectral GNNs is:
-\begin{equation}
-\mat{E}_{i+1} =\; P\left(\sigma\left( \sum_k \mat{L}^k \mat{E}_i \mat{W}_{i,k} \right)\right)
-\end{equation}
-Here $\sigma$ is the non-linearity (typically a ReLU), $\mat{W}_{k,i}$ are the learned weights of layer $i$,  and $P$ is the `pooling' operation, known as graph coarsening \cite{bronstein2017geometric, gama2018mimo}.
-The maximum degree of $\mat{L}$ determines the number of hops away from a node one layer can access.
-In the feature matching problem, we require an embedding for each vertex.
-Therefore we cannot perform graph coarsening, and thus we only perform the non-linearity step.
-We instead use a modification of the approach proposed in Kipf and Welling \cite{kipf2016semi}:
-\begin{align}
-      \widetilde{\mat{L}} =&\; (\mat{D} + \mat{I})^{-1/2} (\mat{A} + \mat{I}) (\mat{D} + \mat{I})^{-1/2} \\
-\mat{E}_{l+1} =&\; \sigma\left(\widetilde{\mat{L}} \mat{E}_i \mat{W}_i \right)  \label{eq:graph_conv}
-\end{align}
-
-The matrix $\widetilde{\mat{L}}$ is analogous to the graph Laplacian (with better numerical stability properties).
-$\widetilde{\mat{L}}$ encodes the structure of the graph and is used to perform the actual graph convolution.
-Our network has many layers, and thus the receptive field of the final embedding is quite large, even without the pooling operations.
-In principle we could use higher hop neighborhoods \cite{gama2018convolutional}, or more complicated aggregation structures \cite{battaglia2018relational}, but in this work we restrict ourselves to simpler architectures, which still shows promising results for this task.
-For faster training, we use group normalization \cite{wu2018group} and skip connections.
-The final output $\mat{E}_n$ gives us a new descriptor for every node.
-In the next sections we will discuss the loss functions to train this network.
-
-\subsection{Cycle Consistency}
-
-Let $\mat{M}$ be the noiseless set of matches between our features, with $\mat{M}_{ij}$ being the matches between image $i$ and image $j$.
-If the pairwise matches are globally consistent, then we can say that, for all $i, j, k$:
-\begin{equation}
-\mat{M}_{ij} = \mat{M}_{ik} \mat{M}_{kj}
-\label{eq:cycconsist1}
-\end{equation}
-In other words, the matches between two images stays the same no matter what path is taken to get there. 
-This constraint is known as \textit{cycle concistency}, and has been used in a number of works to optimize for global consistency \cite{zhou2015multi, wang2017multi, leonardos2016distributed}.
-Stated in this form, there are $O(n^3)$ cycle consistency constraints to check.
-A more elegant way to represent cycle consistency is to first create a `universe' of features that all images match to (see figure \ref{fig:universefeatures}).
-Then, one can match the $i^{th}$ set of features to the universe using a matrix $\mat{X}_i$.
-Then the cycle consistency becomes:
-\begin{equation}
-\mat{M}_{ij} = \mat{X}_{i}\mat{X}_{j}^\top
-\label{eq:cycconsist2}
-\end{equation}
-
-This reduces our complexity from $O(n^3)$ to $O(n^2)$.
-We try to learn $\mat{E}$ to approximate $\mat{X}$ - in other words the final embedding should be an encoding of the universe of features.
-As we do not have the ground truth matches $\mat{M}$, we approximate it using the noisy adjacency matrix $\mat{A}$ of our correspondence graph.
-Thus our loss would be
-\begin{equation}
-\mathcal{L}(\mat{A}, \mat{E}_n) = \mathcal{D}(\mat{A}, \mat{E}_n\mat{E}_n^\top)
-\end{equation}
-Here $\mathcal{D}$ could be an $L_2$ loss, $L_1$ loss, or many others. In this work, we use the $L_1$ loss. 
-Note that because of this formulation, we can determine our embeddings only up to a rotation on the right, as
-\begin{equation}
-\mat{E}R(\mat{E}R)^\top
-= \mat{E}RR^\top\mat{E}^\top
-= \mat{E}\mat{E}^\top
-\label{eq:rotinvar}
-\end{equation}
-and
-
-\subsection{Geometric Consistency Loss}
-
-\begin{figure}[t]
-\begin{center}
-  \includegraphics[width=0.8\linewidth]{figures/GeometricConsistency.pdf}
-\end{center}
-  \caption{
-    Illustrated here is an example of how the geometric loss on one feature.  
-    We compute the errors on each feature match to determine their validity.
-    Errors are computed via absolute distance from the epipolar line, as expressed by (\ref{eq:essential_constraint}) via the epipolar constraint.
-    Best viewed in color.
-  }
-\label{fig:geoconsist}
-\label{fig:onecol}
-\end{figure}
-
-\begin{table*}
-\begin{center}
-\begin{tabular}{|l|c|c|}
-\hline
-Method & Same Point Similarities & Different Point Similarities  \\
-\hline\hline\hline
-Ideal                              & 1.00e+0 $\pm$ 0.00e+0 & 0.00e+0 $\pm$ 0.00e+0 \\ \hline
-Initialization Baseline            & 5.11e-1 $\pm$ 1.68e-2 & 2.56e-1 $\pm$ 2.06e-1 \\ \hline
-3 Views, Noiseless                 & 9.96e-1 $\pm$ 7.70e-3 & 1.16e-1 $\pm$ 1.32e-1 \\ \hline
-5 Views, Noiseless                 & 1.00e+0 $\pm$ 4.15e-4 & 1.22e-1 $\pm$ 1.67e-1 \\ \hline
-3 Views, Added Noise               & 9.96e-1 $\pm$ 7.70e-3 & 1.16e-1 $\pm$ 1.32e-1 \\ \hline
-3 Views, Added Noise               & 9.68e-1 $\pm$ 5.29e-2 & 9.50e-2 $\pm$ 1.58e-1 \\ \hline
-5 Views, Added Noise               & 9.89e-1 $\pm$ 2.47e-2 & 7.67e-2 $\pm$ 1.56e-1 \\ \hline
-6 Views, Added Noise               & 9.84e-1 $\pm$ 3.16e-2 & 7.46e-2 $\pm$ 1.57e-1 \\ \hline
-3 Views, 5\% Outliers              & 9.29e-1 $\pm$ 1.79e-1 & 1.41e-1 $\pm$ 1.48e-1 \\ \hline
-3 Views, 10\% Outliers             & 9.27e-1 $\pm$ 1.79e-1 & 1.40e-1 $\pm$ 1.51e-1 \\ \hline
-
-\hline
-\end{tabular}
-\end{center}
-\caption{
-Results on Synthetic correspondence graphs.
-The `Same Point Similarities' column is the mean and standard deviation of similarities for true corresponding points, while the `Different Point Similarities' is the same for points that do not correspond.
-For the `Same Point Similarities' column higher is better, and for `Different Point Similarities' lower is better.
-Losses tested against ground truth correspondence graph adjacency matrices.
-Our method was not trained on ground truth correspondences but using unsupervised methods.
-}
-\label{fig:synthtable}
-\end{table*}
-
-One of the main advantages of this approach over more traditional optimization based approaches is the ability to add geometric consistency information into the loss at training time, even if it is not available at test time.
-The simplest way to add geometric consistency losses, and the approach we use here, is to use the epipolar constraint.
-The epipolar constraint describes how the positions of features in different images corresponding to the same point should be related.
-Given a relative pose $(R_{ij}, T_{ij})$ between two cameras $i$ and $j$  (transforms $j$ to $i$) the epipolar on corresponding feature locations $X_i$ and $X_j$:
-\begin{equation}
-X_{i}^\top \cross{T_{ij}}R_{ij} X_{j} = 0
-\label{eq:essential_constraint_rel}
-\end{equation}
-In this work we use the two pose epipolar constraint \cite{tron2014quotient}:
-\begin{equation}
-X_{i}^\top R_{i}^\top \cross{T_{j} - T_{i}}R_{j} X_{j} = 0
-\label{eq:essential_constraint}
-\end{equation}
-% Where the $(R_k, T_k)$ are the poses of cameras $i$ and $j$ respectively.
-The constraint assumes that the $X_k$ are calibrated i.e. the camera intrinsics are known. 
-Given the matrix of ground truth correspondences $\mat{M}_{ij}$ between camera $i$ and $j$, we can formulate this as a loss:
-\begin{equation}
-\mathcal{L}_{ij,geom}(\mat{M}_{ij}) = \sum_{k,l} (\mat{M}_{ij})_{kl} \left|X_{i,k}^\top R_{i}^\top \cross{T_{j} - T_{i}}R_{j} X_{j,l}\right|
-\label{eq:geom_cost}
-\end{equation}
-For our purposes, since we use low rank embeddings $\mat{E}_{i}$, $\mat{E}_{j}$, the loss would look like:
-\begin{align}
-\mathcal{L}_{geom}(\mat{E})
-=&\; \mathrm{tr}(\mat{G}^\top \mat{E}\mat{E}^\top) = \sum_{i,j} (\mat{E})_{i} \cdot (\mat{E})_{j} (\mat{G})_{ij} \\
-(\mat{G})_{ij} =&\; \left|X_{i}^\top R_{c(i)}^\top \cross{T_{c(j)} - T_{c(i)}}R_{c(j)} X_{j}\right| \nonumber
-\label{eq:geom_cost2}
-\end{align}
-Where $c(i)$ is the appropriate camera for point index $i$.
-
-% MatchALS \cite{zhou2015multi} 400 Iterations              & 0.007 $\pm$ 0.003 & 0.007 $\pm$ 0.003 & 0.007 $\pm$ 0.003 \\ \hline
-% PGDDS \cite{leonardos2016distributed} 200 Iterations      & 0.013 $\pm$ 0.002 & 0.005 $\pm$ 0.002 & 0.005 $\pm$ 0.002 & 0.039 $\pm$ 0.039 \\ \hline
-\begin{table*}
-\begin{center}
-\begin{tabular}{|l|c|c|c|}
-\hline
-Method (3 Views)                                          & $L_1$ Loss                          & $L_2$ Loss                          & Run Time (sec) (TODO: Fill out)    \\
-\hline\hline
-MatchALS \cite{zhou2015multi} 15 Iterations               & 0.052 $\pm$ 0.003                   & 0.010 $\pm$ 0.002                   & 0.010 $\pm$ 0.002 \\ \hline
-MatchALS \cite{zhou2015multi} 25 Iterations               & 0.045 $\pm$ 0.007                   & 0.009 $\pm$ 0.003                   & 0.009 $\pm$ 0.003 \\ \hline
-MatchALS \cite{zhou2015multi} 50 Iterations               & 0.016 $\pm$ 0.008                   & 0.007 $\pm$ 0.003                   & 0.007 $\pm$ 0.003 \\ \hline
-MatchALS \cite{zhou2015multi} 100 Iterations              & 0.007 $\pm$ 0.003                   & 0.007 $\pm$ 0.003                   & 0.007 $\pm$ 0.003 \\ \hline
-PGDDS \cite{leonardos2016distributed} 15 Iterations       & 0.016 $\pm$ 0.002                   & 0.006 $\pm$ 0.002                   & 0.006 $\pm$ 0.002 \\ \hline
-PGDDS \cite{leonardos2016distributed} 50 Iterations       & 0.013 $\pm$ 0.002                   & 0.005 $\pm$ 0.002                   & 0.005 $\pm$ 0.002 \\ \hline
-PGDDS \cite{leonardos2016distributed} 100 Iterations      & 0.013 $\pm$ 0.002                   & 0.005 $\pm$ 0.002                   & 0.005 $\pm$ 0.002 \\ \hline
-Spectral                                                  & 0.054 $\pm$ 0.005                   & 0.018 $\pm$ 0.004                   & 0.018 $\pm$ 0.004 \\ \hline 
-\textbf{GNN, 12 Layers (ours)}                            & \textbf{0.025} $\pm$ \textbf{0.003} & \textbf{0.016} $\pm$ \textbf{0.003} & \textbf{0.016} $\pm$ \textbf{0.003} \\
-\hline \hline\hline
-Method (4 Views)                                          & $L_1$ Loss                          & $L_2$ Loss                          & Run Time (sec) (TODO: Fill out)   \\
-\hline\hline
-MatchALS \cite{zhou2015multi} 15 Iterations               & 0.052 $\pm$ 0.003                   & 0.010 $\pm$ 0.002                   & 0.010 $\pm$ 0.002 \\ \hline
-MatchALS \cite{zhou2015multi} 25 Iterations               & 0.045 $\pm$ 0.007                   & 0.009 $\pm$ 0.003                   & 0.009 $\pm$ 0.003 \\ \hline
-MatchALS \cite{zhou2015multi} 50 Iterations               & 0.016 $\pm$ 0.008                   & 0.007 $\pm$ 0.003                   & 0.007 $\pm$ 0.003 \\ \hline
-MatchALS \cite{zhou2015multi} 100 Iterations              & 0.007 $\pm$ 0.003                   & 0.007 $\pm$ 0.003                   & 0.007 $\pm$ 0.003 \\ \hline
-PGDDS \cite{leonardos2016distributed} 15 Iterations       & 0.016 $\pm$ 0.002                   & 0.006 $\pm$ 0.002                   & 0.006 $\pm$ 0.002 \\ \hline
-PGDDS \cite{leonardos2016distributed} 50 Iterations       & 0.013 $\pm$ 0.002                   & 0.005 $\pm$ 0.002                   & 0.005 $\pm$ 0.002 \\ \hline
-PGDDS \cite{leonardos2016distributed} 100 Iterations      & 0.013 $\pm$ 0.002                   & 0.005 $\pm$ 0.002                   & 0.005 $\pm$ 0.002 \\ \hline
-Spectral                                                  & 0.054 $\pm$ 0.005                   & 0.018 $\pm$ 0.004                   & 0.018 $\pm$ 0.004 \\ \hline 
-\textbf{GNN, 12 Layers (ours)}                            & \textbf{0.025} $\pm$ \textbf{0.003} & \textbf{0.016} $\pm$ \textbf{0.003} & \textbf{0.016} $\pm$ \textbf{0.003} \\
-\end{tabular}
-\end{center}
-% save-rome16kgeom0-normedskip2-loss-l1-geom-10-0 (028249) -> train : +3.1467e-02, test : +3.8864e-02, gt_l1 : +2.6321e-02, gt_l2 : +2.6321e-02
-
-\caption{
-Results on Rome16K Correspondence graphs, showing the mean and standard deviation of the $L_1$ and $L_2$.
-Our method was not trained on ground truth corresopndences but using unsupervised methods and geometric side losses.
-As our method gives soft labels, we use cannot use precision or recall as is standard in testing cycle consistency \cite{zhou2015multi}.
-Thus we test against ground truth correspondence graph adjacency matrices computed from the bundle adjustment output.
-Our method performs better than 25 iteration of an optimizaiton based method, but does not perform as well as 50 iterations.
-Our network has only 12 layers, thus we have much greater efficiency per iteration.
-}
-\end{table*}
-
-%------------------------------------------------------------------------
-\section{Experiments}
-
-\begin{figure*}
-\begin{center}
-  % \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
-  \includegraphics[width=0.8\linewidth]{figures/TrainingCurves.pdf}
-  \end{center}
-    \caption{
-      Training curves with and without Geometric Training loss.
-      The geometric training loss improves testing performance.
-      Shown as horizontal lines are the state of the art optimization based baselines.
-      Even with a simple network we compare well with them.
-    }
-  \label{fig:short}
 \end{figure*}
 
-\begin{figure*}
-\begin{center}
-  % \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
-  \includegraphics[width=0.8\linewidth]{figures/ExampleOutput.pdf}
-  \end{center}
-     \caption{Example output of our network.
-(a) Similarity Matrix of the of the embeddings (b) Histogram of feature similarities for pairs which correspond to the same 3D point, comparing our output features with the original SIFT features (c) Histogram of feature similarities for pairs which correspond to different 3D points, comparing our output features with the original SIFT features}
-  \label{fig:short}
-\end{figure*}
-\subsection{Synthetic Graph Dataset}
-We first test our method on synthetically generated data as a simple proof of concept.
-To generate the data, we generate $p$ points, each with its own randomly generated descriptor.
-To create the graph, we generate random permutation matrices, with a noise applied to it after generated.
-The initial descriptors we use as input we created using the true descriptor plus some added Gaussian noise.
-No geometric losses were added during training for these experiments.
-However, the method was robust in testing with different noise functions and parameters.
-The normalized noisy input descriptors are our baseline - they correlate with the true values but do not perserve the structure well.
-However, with the GNN we are able to recover the true structure very well, as shown in \ref{fig:synthtable}.
-All experiments were run with a 12 layer GCN with the ReLU nonlinearity and skip connections.
-All were trained with the Adam optimizer \cite{kingma2014adam} and a learning rate $10^{-4}$
-
-\subsection{Rome 16K Graph Dataset}
-We  use the Rome16K dataset \cite{li2010location} to test our algorithm in real world settings.
-Rome16K consistes of 16 thousand images of various historical sites in Rome extracted from Flickr, along with the 3D structure of the sites provided by bundle adjustment.
-While not a standard dataset to test cycle consistency, other datasets had insufficient data to train a network on.
-Rome16K is typically used to test bundle adjustment methods.
-Therefore, to use for our method, we extract image triplets and quadtruplets with overlap of 80 points or more to test our algorithm on, with the points established as corresponding in the given bundle adjument output.
-For the initial embedding we use the original 128 dimensional SIFT descriptors, normalized to have unit $L_2$ norm, the calibrated x-y position, the orientation, and log scale of the SIFT feature.
-% For the outlier datasets, we take 79 correspondences and 1 non-corresponding point in each image.
-
-For these experiments we train with the $L1$ norm and geometric consistency losses.
-We evaluate on a test set using the ground truth adjacency matrix which we compute from the bundle adjustment given by the Rome16K dataset.
-Traditional methods of evaluation use Precision and Recall, after making the labels 0 or 1.
-We forgo this as our method was trained to output soft labels - we in turn make the labels soft for the optimization based methods.
-For this method to work, we need the dimension of the embedding to be at least the number of unique points in the scene.
-Picking the correct number is difficult a-priori, and is a problem with all cycle consistency based methods.
-Here we use the ground truth dimension of the embedding to test both our method and the baselines.
-For implementation details, our network has 12 layers, and was trained with the Adam optimizer \cite{kingma2014adam} with a learning rate of $10^{-4}$, with an exponentially decaying learning rate.
-We incorporate skip connections between the input, $6^{th}$, and $12^{th}$ layers, which greatly improved training convergence and testing performance (see supplemental material).
-
-We compare our method to spectral and optimization based baselines with different maximum iteration cutoffs.
-Our method is siginificatnly better than a simple spectral based optimization.
-Furthermore, our network, which only has 12 layers has the accuracy of the optimization based method MatchALS \cite{zhou2015multi} between 25 and 50 iterations.
-This inidicates that our method learns a more efficient update with each layer compared with an iteration in the optimization based methods.
-
-%------------------------------------------------------------------------
-\section{Conclusion}
-
-We have shown a novel method for training feature matching using GCNs and an unsupervised cycle consistency loss.
-This method can be employed even when labelled training data is not available, but can still incorporate geometric consistency into its losses.
-We have demonstrated its effectiveness on the Rome16K dataset compared to the traditional optimization based baselines on a simple GCN.
-For future work we will investigate using more robust losses for outlier rejection and using higher order geometric constraints, such as the trifocal tensor, as additional loss terms.
-A long term goal is to incorporate learning image level features into this pipeline.
-Moreover we plan to focus on making this method work in a distributed setting, which we could do with very small changes to the current approach.
-% , but with group norm, we cannot distribute in its current form.
-
-{\small
-\bibliographystyle{ieee}
-\bibliography{mybib}
-}
-
 \end{document}

### 2019-02-05 cvpr2019/rebuttal/egrebuttal.tex
Added rebuttal LaTeX to file

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

%%%%%%%%% PAPER ID  - PLEASE UPDATE
\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

\begin{document}

%%%%%%%%% TITLE - PLEASE UPDATE
\title{All Graphs Lead to Rome: Rebuttal}  % **** Enter the paper title here

\maketitle
\thispagestyle{empty}

%%%%%%%%% BODY TEXT - ENTER YOUR RESPONSE BELOW
% TODO: Don't worry about space
% TODO: Do more bullet point style
% TODO: Thank all the reviewers at the start, skip sentences later
\section{Reviewer \#1}
Thank you for your comments and feedback. You
mention the benefits of using Graph Neural Networks are not clear. One
of the primary benefits is the ability to integrate the matching in an
end-to-end learning pipeline, which could for instance train on semantic
features. Adding in additional side-losses can assist in training,
even if such information is not available at testing time. While not
explored in this work, GNNs have great potential in fast parallel
computation which has been difficult to do for optimization based
methods. Your comment on how use of a CNN to solve the matching
problem appears contrived but we use GNNs - unless there is some
confusion here.
% TODO: We could use sets but that would throw away the structure of our data
% TODO: Most structured

% TODO: Less apologetic
% TODO: Their comments in quotes
To address your other comments, we did not focus on the mechanics of
GNNs to focus on cycle consistency and the matching graph, however we
can add more to the text to make it clearer. We should reference the
figures more in the text - they are there for illustrative purposes but
we should indeed explicitly cite them. Relatedly, can reference the
figures on the experiments in the text more.
You are right in that we neglected to cite the spectral method
\cite{pachauri2013solving} except briefly in the methods section. This
is simply taking the top $k$ eigenvectors as the embedding. It is the
simplest method to solve mutli-image matching and works perfectly when
there is no noise, but breaks down more quickly when there is more noise.

We admit the lack of larger view-sets for our experiments is an
oversight. However RANSAC based methods start becoming computationally
infeasible at 3 and 4 images (too many points to select) so it appeared
the simplest test to see how our method could function in ways simple
RANSAC based methods wouldn't.

\section{Reviewer \#3}
Thank you for you comments and we agree that this method is interesting
and has many interesting applications.
To address the weaknesses you point out, you are right that an
precision-recall or ROC curve would be a good measure (W1). We have
added in this rebuttal a figure showing the ROC curves of our method
compared to other methods, and we still compare favorably. You are
right in that more outlier experiments could have been done (W2b).

You say that Rome16K is an inappropriate dataset for testing Cycle
Consistency (W2a). We couldn't find a more appropriate large scale
dataset where we could find ground truth matches. We could collect our
own but we wanted to test against a well-known dataset (even if it is
typically used in other contexts) for a more fair comparison. You are 
right we did not specify how we split training and testing - there was
no overlap of sequences in training and testing sets. It was trained on
one set of buildings and tested on another, so it has not overfit to
particular buildings.

You are right to point out we did not include the implementation
details of our architecture. Our layer splits were: 
32, 64, 128, 256, 512, 512, 512, 512, 512, 512, 1024, 1024.
For your other comments, the first comment was addressed in the last
paragraph of Reviewer \#1, and the others are valid comments that we
will attempt to fix.

\section{Reviewer \#5}
Thank you as well for your comments and feedback.
We agree with you that this topic is an important research area and feel
that our method has much to contribute to that.

You as well as Reviewer \#1 felt the discussion on GNNs was insufficient
and we will add more detail should this paper be accepted. To address
your comments on the scale of the mutil-image experiments, see Reviewer
\#1. We appreciate the comment about the axes of figure and we will
fix that, as well as your other comments on typos and figure fixes.
You mentioned~\cite{hajder2006weak}, which did not come up in our
literature search, but it does address mutli-view robust image matching
and we will add it to our citations.

\begin{figure}[t]
\begin{center}
\fbox{\rule{0pt}{1.8in} \rule{0.9\linewidth}{0pt}}
   %\includegraphics[width=0.8\linewidth]{egfigure.eps}
\end{center}
   \caption{Example of caption.  It is set in Roman so that mathematics
   (always set in Roman: $B \sin A = A \sin B$) may be included without an
   ugly clash.}
\label{fig:long}
\label{fig:onecol}
\end{figure}

{\small
\bibliographystyle{ieee}
\bibliography{egbib}
}

\end{document}

### 2019-02-05 roc_test.py
ROC and precision-recall tests

@@ -1,0 +1,81 @@
+# -*- coding: utf-8 -*-
+import os
+import sys
+import glob
+import numpy as np
+import matplotlib.pyplot as plt 
+import time
+
+def calc_classifications(o, a):
+  TP = np.sum(o*a)
+  TN = np.sum((1-o)*(1-a))
+  FP = np.sum(o*(1-a))
+  FN = np.sum((1-o)*a)
+  return TP, TN, FP, FN
+
+fname = '/home/stephen/Documents/Research/cycleconsistencynet/test_output.npz'
+ld = dict(np.load(fname))
+temb = ld['trueemb']
+outemb = ld['out']
+N_cutoffs = 100
+adjmat = np.dot(temb, temb.T)
+# plt.imshow(adjmat)
+# plt.colorbar()
+# plt.show()
+
+output = np.abs(np.dot(outemb, outemb.T))
+# plt.imshow(output)
+# plt.colorbar()
+# plt.show()
+
+def compute_thresh_errs(output, adjmat, N_cutoffs=2048):
+  a = adjmat.astype(np.int32)
+  M_T = np.sum(a)
+  M_F = a.size - M_T
+
+  vals = np.zeros((N_cutoffs, 4)).astype(np.int32)
+  for idx, i in enumerate(range(N_cutoffs-1,-1,-1)):
+    thresh = (1.0*i) / (N_cutoffs-1)
+    o = (output > thresh).astype(np.int32)
+    TP, TN, FP, FN = calc_classifications(o,a)
+    vals[idx,:] = (TP, TN, FP, FN)
+
+  return (vals[:,0], vals[:,1], vals[:,2], vals[:,3])
+
+def roc_lines(TP, TN, FP, FN):
+  roc = np.stack((FP / np.maximum(1e-8, FP + TN),
+                  TP / np.maximum(1e-8, TP + FN)), axis=-1)
+  return roc
+
+def compute_roc(TP, TN, FP, FN):
+  FPR = FP / np.maximum(1e-8, FP + TN)
+  TPR = TP / np.maximum(1e-8, TP + FN)
+  return np.abs(np.trapz(TPR, x=FPR))
+
+def precision_recall_lines(TP, TN, FP, FN):
+  p_r = np.stack((TP / np.maximum(1e-8, TP + FP),
+                  TP / np.maximum(1e-8, TP + FN)), axis=-1)
+  return p_r
+
[…]

### 2019-02-07 baselines/print_errors.py
ROC and P-R analysis

@@ -5,7 +5,10 @@ import re
 
 import matplotlib.pyplot as plt
 
-egstr = '000000 Errors: L1: 5.297e-02, L2: 1.678e-02, BCE: 1.008e-01, Same sim: 8.776e-01 +/- 9.812e-02, Diff sim: 5.209e-02 +/- 1.182e-01, Time: 2.800e-02, '
+egstr = '000008 Errors: L1: 1.430e-02, L2: 5.834e-03, BCE: 5.971e-02, ' \
+        'Same sim: 4.281e-01 +/- 1.905e-01, Diff sim: 7.239e-03 +/- 3.317e-02, ' \
+        'Area under ROC: 9.161e-01, Area under P-R: 7.879e-01, ' \
+        'Time: 2.072e+00'
 
 def stdagg(x):
   return np.sqrt(np.mean(np.array(x)**2))
@@ -22,14 +25,18 @@ def myformat_old(x):
 
 efmt = '[-+]?\d+\.\d*e[-+]\d+'
 disp_match = re.compile(efmt)
-names = ['l1', 'l2', 'bce', 'ssame_m', 'ssame_s', 'sdiff_m', 'sdiff_s', 'time']
+names = [
+  'l1', 'l2', 'bce', \
+  'ssame_m', 'ssame_s', 'sdiff_m', 'sdiff_s', \
+  'roc', 'pr', \
+  'time']
 def parse(line):
   return dict(zip(names, [ float(x) for x in disp_match.findall(line) ]))
 
 agg_names = [ 'l1', 'l2', 'bce', 'ssame', 'sdiff' ]
 def agg(vals):
   aggs = dict(zip(agg_names, [ None for nm in agg_names ]))
-  for k in [ 'l1', 'l2', 'bce', 'time' ]:
+  for k in [ 'l1', 'l2', 'bce', 'roc', 'pr', 'time' ]:
     aggs[k] = (np.mean(vals[k]), np.std(vals[k]))
   for k in [ 'ssame', 'sdiff' ]:
     aggs[k] = ( np.mean(vals[k + '_m']), stdagg(vals[k + '_s']) )
@@ -42,14 +49,23 @@ def disp_val(aggs):
   #                   myformat(aggs['l2'][0]), myformat(aggs['l2'][1]),
   #                   myformat(aggs['bce'][0]), myformat(aggs['bce'][1])))
   # return 
-  fstr = "{:40} & {} $\pm$ {} & {} $\pm$ {} & {} $\pm$ {} \\\\ \\hline"
[…]

### 2019-02-07 baselines/roc_curves.py

@@ -1,0 +1,156 @@
+# -*- coding: utf-8 -*-
+import os
+import sys
+import glob
+import numpy as np
+import matplotlib.pyplot as plt 
+import time
+
+def calc_classifications(o, a):
+  TP = np.sum(o*a)
+  TN = np.sum((1-o)*(1-a))
+  FP = np.sum(o*(1-a))
+  FN = np.sum((1-o)*a)
+  return TP, TN, FP, FN
+
+
+def compute_thresh_errs(output, adjmat, N_cutoffs=2048):
+  a = adjmat.astype(np.int32)
+  M_T = np.sum(a)
+  M_F = a.size - M_T
+
+  TP_, TN_, FP_, FN_ = (np.zeros(N_cutoffs).astype(np.int32) for i in range(4))
+  TP_[ 0], TN_[ 0], FP_[ 0], FN_[ 0] =   0, M_F,   0, M_T
+  TP_[-1], TN_[-1], FP_[-1], FN_[-1] = M_T,   0, M_F,   0
+  for idx in range(1,N_cutoffs-1):
+    i = (N_cutoffs - 1) - idx
+    thresh = (1.0*i) / (N_cutoffs-1)
+    o = (output > thresh).astype(np.int32)
+    TP, TN, FP, FN = calc_classifications(o,a)
+    TP_[idx], TN_[idx], FP_[idx], FN_[idx] = TP, TN, FP, FN
+
+  return (TP_, TN_, FP_, FN_)
+
+def roc_lines(TP, TN, FP, FN):
+  FPR = np.maximum(1e-8, FP) / np.maximum(1e-8, FP + TN)
+  TPR = np.maximum(1e-8, TP) / np.maximum(1e-8, TP + FN)
+  roc = np.stack((FPR, TPR), axis=-1)
+  return roc
+
+def compute_roc(TP, TN, FP, FN):
+  FPR = np.maximum(1e-8, FP) / np.maximum(1e-8, FP + TN)
+  TPR = np.maximum(1e-8, TP) / np.maximum(1e-8, TP + FN)
+  # sidx = np.argsort(FPR)
+  # FPR = FPR[sidx]
+  # TPR = TPR[sidx]
+  return np.abs(np.trapz(TPR, x=FPR))
+
+def precision_recall_lines(TP, TN, FP, FN):
+  precision = np.maximum(1e-8, TP) / np.maximum(1e-8, TP + FP)
[…]

### 2019-02-07 baselines/run_tests.m

@@ -1,8 +1,19 @@
-function run_tests(mat_files, views)
+function run_tests(npz_files, views, save_out)
 
 if nargin < 2
   views = 3;
 end
+if nargin < 3
+  save_out = false;
+end
+
+npymatlab_path = 'npy-matlab/npy-matlab';
+pathCell = regexp(path, pathsep, 'split');
+onPath = any(strcmp(npymatlab_path, pathCell));
+if ~onPath
+  addpath(npymatlab_path);
+end
+[~,~,~] = mkdir('/tmp/unzip');
 
 v = views;
 p = 80;
@@ -14,6 +25,21 @@ params050.maxiter = 50;
 params100.maxiter = 100;
 params200.maxiter = 200;
 
+metric_info = { ...
+      { 'l1',      'L1: %.03e, ',              @mean                 }, ...
+      { 'l2',      'L2: %.03e, ',              @mean                 }, ...
+      { 'bce',     'BCE: %.03e, ' ,            @mean                 }, ...
+      { 'ssame_m', 'Same sim: %.03e ' ,        @mean                 }, ...
+      { 'ssame_s', '+/- %.03e, ' ,             @(x) sqrt(mean(x.^2)) }, ...
+      { 'sdiff_m', 'Diff sim: %.03e ' ,        @mean                 }, ...
+      { 'sdiff_s', '+/- %.03e, ' ,             @(x) sqrt(mean(x.^2)) }, ...
+      { 'roc',     'Area under ROC: %.03e, ' , @mean                 }, ...
+      { 'pr',      'Area under P-R: %.03e, ' , @mean                 }, ...
+};
+metrics = cell(length(metric_info),1);
+for i = 1:length(metric_info)
+  metrics{i} = zeros(length(npz_files),1);
+end
 %  'MatchALS400Iter', @(W)  mmatch_CVX_ALS(W, dimGroups, 'maxrank', p, 'maxiter', 400); ...
 %  'PGDDS200Iter', @(W) PGDDS(W, dimGroups, p, params200); ...
 %  'PGDDS100Iter', @(W) PGDDS(W, dimGroups, p, params100); ...
@@ -28,90 +54,71 @@ test_fns = { ...
  'PGDDS050Iter', @(W) PGDDS(W, dimGroups, p, params050); ...
 };
[…]

### 2019-02-07 cvpr2019/rebuttal/egrebuttal.tex
Updated tex file

@@
 % TODO: Thank all the reviewers at the start, skip sentences later
+Thank you to all the reviewers for all of your constructive comments and feedback.
+We hope to address some of your concerns here.
+
 \section{Reviewer \#1}
-Thank you for your comments and feedback. You
-mention the benefits of using Graph Neural Networks are not clear. One
-of the primary benefits is the ability to integrate the matching in an
-end-to-end learning pipeline, which could for instance train on semantic
-features. Adding in additional side-losses can assist in training,
-even if such information is not available at testing time. While not
-explored in this work, GNNs have great potential in fast parallel
-computation which has been difficult to do for optimization based
-methods. Your comment on how use of a CNN to solve the matching
-problem appears contrived but we use GNNs - unless there is some
-confusion here.
+\textbf{The benefits of applying a GCN instead of classical optimization methods are not clear and the use of a Convolutional Neural Network to solve the multi-view matching problem appears contrived.}:
+One of the primary benefits is the ability to integrate the matching in an end-to-end learning pipeline, which could for instance train on semantic features.
+Adding in additional side-losses can assist in training, even if such information is not available at testing time.
+We could have tried learning on sets of features but that would throw out the structure between the features, so graphs were the best way to represent that.
+
+\textbf{GCNs (Section 3.2) should be deeply described}: 
+We did not focus on the mechanics of GNNs to focus on cycle consistency and the matching graph, however we can add more to the text to make it clearer.
+
+\textbf{most of the figures are not cited in the tex}: 
+We will cite the figures in the appropriate places better.
+
+\textbf{images showing the experimental results (figure 5, 6, 7) should be better clarified and discussed}: 
+Relatedly, can reference the figures on the experiments in the text more, and label the axes better.
+
+\textbf{The reference to the “spectral method” used in the experiments is missing.}: 
+You are right in that we neglected to cite the spectral method \cite{pachauri2013solving} except briefly in the methods section.
+This is simply taking the top $k$ eigenvectors as the embedding.
+It is the simplest method to solve mutli-image matching and works perfectly when there is no noise, but breaks down more quickly when there is more noise.
+
+\textbf{The performances of the proposed method should be evaluated also on sequences of tens of images. Multiview matching with 4 images is not very meaningful}: 
+We admit the lack of larger view-sets for our experiments is an oversight.
+However RANSAC based methods start becoming computationally infeasible at 3 and 4 images (12-point RANSAC for the trifocal tensor is too demanding) so it was the simplest test to see how our method could function in ways simple RANSAC based methods wouldn't.
+% While not explored in this work, GNNs have great potential in fast parallel
+% computation which has been difficult to do for optimization based
+% methods. Your comment on how use of a CNN to solve the matching
+% problem appears contrived but we use GNNs - unless there is some
+% confusion here.
 % TODO: We could use sets but that would throw away the structure of our data
@@
 % TODO: Their comments in quotes
-To address your other comments, we did not focus on the mechanics of
-GNNs to focus on cycle consistency and the matching graph, however we
-can add more to the text to make it clearer. We should reference the
-figures more in the text - they are there for illustrative purposes but
-we should indeed explicitly cite them. Relatedly, can reference the
-figures on the experiments in the text more.
-You are right in that we neglected to cite the spectral method
-\cite{pachauri2013solving} except briefly in the methods section. This
-is simply taking the top $k$ eigenvectors as the embedding. It is the
-simplest method to solve mutli-image matching and works perfectly when
-there is no noise, but breaks down more quickly when there is more noise.
-
-We admit the lack of larger view-sets for our experiments is an
-oversight. However RANSAC based methods start becoming computationally
-infeasible at 3 and 4 images (too many points to select) so it appeared
-the simplest test to see how our method could function in ways simple
-RANSAC based methods wouldn't.
 
 \section{Reviewer \#3}
-Thank you for you comments and we agree that this method is interesting
-and has many interesting applications.
-To address the weaknesses you point out, you are right that an
-precision-recall or ROC curve would be a good measure (W1). We have
-added in this rebuttal a figure showing the ROC curves of our method
-compared to other methods, and we still compare favorably. You are
-right in that more outlier experiments could have been done (W2b).
+\textbf{ In my opinion, measuring the precision and recall in terms of identifying correct matches would be a better evaluation score (and also closer to the problem setting) (W1).}:
+You are right that an precision-recall or ROC curve would be a good measure.
+We have added in this rebuttal a figure showing the ROC curves of our method compared to other methods, and we still compare favorably.
 
-You say that Rome16K is an inappropriate dataset for testing Cycle
-Consistency (W2a). We couldn't find a more appropriate large scale
-dataset where we could find ground truth matches. We could collect our
-own but we wanted to test against a well-known dataset (even if it is
-typically used in other contexts) for a more fair comparison. You are 
-right we did not specify how we split training and testing - there was
-no overlap of sequences in training and testing sets. It was trained on
-one set of buildings and tested on another, so it has not overfit to
-particular buildings.
+\textbf{I am worried that the Rome16k dataset is not really suited to demonstrate the benefits of multi-image matching under cycle consistency (W2a)}:
+We couldn't find a more appropriate large scale dataset where we could find ground truth matches.
+We could collect our own but we wanted to test against a well-known dataset (even if it is typically used in other contexts) for a more fair comparison.
 
-You are right to point out we did not include the implementation
-details of our architecture. Our layer splits were: 
-32, 64, 128, 256, 512, 512, 512, 512, 512, 512, 1024, 1024.
-For your other comments, the first comment was addressed in the last
-paragraph of Reviewer \#1, and the others are valid comments that we
-will attempt to fix.
+\textbf{there are not really experiments analyzing the robustness of the proposed approach to outliers (W2b)}:
+You are right in that more outlier experiments could have been done.
+
+\textbf{Details on the network architecture (beyond it having 12 layers) are missing (W3a)}:
+Our layer splits were: 32, 64, 128, 256, 512, 512, 512, 512, 512, 512, 1024, 1024.
+We had skip connections between the input and layers 7 and 12, with small one layer skip connections between each layer.
+
+\textbf{It is unclear how the Rome16k dataset is split into a test and training set (W3b)}:
+There was no overlap of sequences in training and testing sets. It was trained on one set of buildings and tested on another, so it has not overfit to particular buildings.
 
 \section{Reviewer \#5}
-Thank you as well for your comments and feedback.
-We agree with you that this topic is an important research area and feel
-that our method has much to contribute to that.
 
-You as well as Reviewer \#1 felt the discussion on GNNs was insufficient
-and we will add more detail should this paper be accepted. To address
-your comments on the scale of the mutil-image experiments, see Reviewer
-\#1. We appreciate the comment about the axes of figure and we will
-fix that, as well as your other comments on typos and figure fixes.
-You mentioned~\cite{hajder2006weak}, which did not come up in our
-literature search, but it does address mutli-view robust image matching
-and we will add it to our citations.
+\textbf{I think the method cannot be re-implemented based on the submitted manuscript. Especially Section 3.1-3.3 are very confusing}:
+You as well as Reviewer \#1 felt the discussion on GNNs was insufficient and we will add more detail should this paper be accepted, especially about Graph Neural Networks.
 
-\begin{figure}[t]
+\textbf{The evaluation of the testing part is not satisfactory. Although it is a general multi-image method, only three- and four-view tests are included}:
+See Reviewer \#1 - we were testing on the minimum number of images before RANSAC based methods on multi-view constraints became impractical.
+
+\textbf{Axes in the charts are usually missing. There are typos and grammatical errors in the text}:
+Indeed we did not label them - we will add labels and greater descriptions for each of the figures.
+
+\textbf{ do not agree that RANSAC can only be applied for stereo matching. E.g. a multi-view robust RANSAC-based factorization is proposed in the work of Hajder\&Chetverikov }:
+We indeed did not know of \cite{hajder2006weak}. We will cite it and hope to use some of its techniques in future work.
+
+\begin{table}[t]
 \begin{center}
-\fbox{\rule{0pt}{1.8in} \rule{0.9\linewidth}{0pt}}
-   %\includegraphics[width=0.8\linewidth]{egfigure.eps}
+\begin{tabular}{ |c|c|c|c|c|c| }
+\hline
+Method                                         & ROC    & mAP \\ \hline
+GCN 12 Layers                                  & 0.953  & 0.655  \\ \hline
+MatchALS \cite{zhou2015multi}  15 Iter.        & 0.624  & 0.653  \\ \hline
+MatchALS \cite{zhou2015multi}  25 Iter.        & 0.573  & 0.569  \\ \hline
+MatchALS \cite{zhou2015multi}  50 Iter.        & 0.437  & 0.423  \\ \hline
+MatchALS \cite{zhou2015multi} 100 Iter.        & 0.404  & 0.302  \\ \hline
+PGDDS \cite{leonardos2016distributed} 15 Iter. & 0.918  & 0.724  \\ \hline
+PGDDS \cite{leonardos2016distributed} 25 Iter. & 0.920  & 0.768  \\ \hline
+PGDDS \cite{leonardos2016distributed} 50 Iter. & 0.920  & 0.795  \\ \hline
+Spectral \cite{pachauri2013solving}            & 0.917  & 0.689  \\ \hline
+\end{tabular}
 \end{center}
-   \caption{Example of caption.  It is set in Roman so that mathematics
-   (always set in Roman: $B \sin A = A \sin B$) may be included without an
-   ugly clash.}
-\label{fig:long}
-\label{fig:onecol}
-\end{figure}
+\caption{}
+
+\end{table}
+% GCN 12 Layers                                  & 0.953 $\pm$ 0.071 & 0.655 $\pm$ 0.113 \\ \hline
+% MatchALS \cite{zhou2015multi}  15 Iter.        & 0.624 $\pm$ 0.078 & 0.653 $\pm$ 0.184 \\ \hline
+% MatchALS \cite{zhou2015multi}  25 Iter.        & 0.573 $\pm$ 0.060 & 0.569 $\pm$ 0.167 \\ \hline
+% MatchALS \cite{zhou2015multi}  50 Iter.        & 0.437 $\pm$ 0.042 & 0.423 $\pm$ 0.151 \\ \hline
+% MatchALS \cite{zhou2015multi} 100 Iter.        & 0.404 $\pm$ 0.066 & 0.302 $\pm$ 0.116 \\ \hline
+% PGDDS \cite{leonardos2016distributed} 15 Iter. & 0.918 $\pm$ 0.101 & 0.724 $\pm$ 0.224 \\ \hline
+% PGDDS \cite{leonardos2016distributed} 25 Iter. & 0.920 $\pm$ 0.101 & 0.768 $\pm$ 0.230 \\ \hline
+% PGDDS \cite{leonardos2016distributed} 50 Iter. & 0.920 $\pm$ 0.101 & 0.795 $\pm$ 0.224 \\ \hline
+% Spectral \cite{pachauri2013solving}            & 0.917 $\pm$ 0.103 & 0.689 $\pm$ 0.197 \\ \hline
+
+% \begin{figure}[t]
+% \begin{center}
+% \fbox{\rule{0pt}{1.8in} \rule{0.9\linewidth}{0pt}}
+%    %\includegraphics[width=0.8\linewidth]{egfigure.eps}
+% \end{center}
+%    \caption{Example of caption.  It is set in Roman so that mathematics
+%    (always set in Roman: $B \sin A = A \sin B$) may be included without an
+%    ugly clash.}
+% \label{fig:long}
+% \label{fig:onecol}
+% \end{figure}
 

### 2019-02-08 cvpr2019/rebuttal/egrebuttal.tex
Most recent updates

@@
 One of the primary benefits is the ability to integrate the matching in an end-to-end learning pipeline, which could for instance train on semantic features.
-Adding in additional side-losses can assist in training, even if such information is not available at testing time.
 We could have tried learning on sets of features but that would throw out the structure between the features, so graphs were the best way to represent that.
+Adding in additional side-losses can assist in training, an option not available in optimization based methods.
 
-\textbf{GCNs (Section 3.2) should be deeply described}: 
-We did not focus on the mechanics of GNNs to focus on cycle consistency and the matching graph, however we can add more to the text to make it clearer.
-
-\textbf{most of the figures are not cited in the tex}: 
-We will cite the figures in the appropriate places better.
+\textbf{GCNs (Section 3.2) should be deeply described} and \textbf{most of the figures are not cited in the tex}: 
+We will cite the figures in the appropriate places better, with better descriptions.
 
@@
 \textbf{The reference to the “spectral method” used in the experiments is missing.}: 
-You are right in that we neglected to cite the spectral method \cite{pachauri2013solving} except briefly in the methods section.
-This is simply taking the top $k$ eigenvectors as the embedding.
-It is the simplest method to solve mutli-image matching and works perfectly when there is no noise, but breaks down more quickly when there is more noise.
+We neglected to cite it \cite{pachauri2013solving} in the table only briefly in the methods section. This is simply taking the top $k$ eigenvectors as the embedding.
 
@@
 We admit the lack of larger view-sets for our experiments is an oversight.
-However RANSAC based methods start becoming computationally infeasible at 3 and 4 images (12-point RANSAC for the trifocal tensor is too demanding) so it was the simplest test to see how our method could function in ways simple RANSAC based methods wouldn't.
+However RANSAC based methods start becoming computationally infeasible at 3 and 4 images (12-point RANSAC for the trifocal tensor is too demanding) so it was the simplest test to see how our method would fair.
 % While not explored in this work, GNNs have great potential in fast parallel
@@
 \textbf{ In my opinion, measuring the precision and recall in terms of identifying correct matches would be a better evaluation score (and also closer to the problem setting) (W1).}:
-You are right that an precision-recall or ROC curve would be a good measure.
-We have added in this rebuttal a figure showing the ROC curves of our method compared to other methods, and we still compare favorably.
+You are right that an precision-recall or ROC curve would be a good measure. We have added in this rebuttal a figure showing the ROC curves of our method compared to other methods.
 
 \textbf{I am worried that the Rome16k dataset is not really suited to demonstrate the benefits of multi-image matching under cycle consistency (W2a)}:
-We couldn't find a more appropriate large scale dataset where we could find ground truth matches.
+% We couldn't find a more appropriate large scale dataset where we could find ground truth matches.
 We could collect our own but we wanted to test against a well-known dataset (even if it is typically used in other contexts) for a more fair comparison.
+We needed a large-scale dataset with multi-view matching and having ground truth to evaluate against.
+Rome16K seemed the most appropriate dataset, as other datasets with ground truth were far too small.
+If the review knows of any other datasets that satisfy our constraints, we would appreciate the suggestion.
 

### 2019-02-08 cvpr2019/rebuttal/egrebuttal.tex
Next version

@@
 
-%%%%%%%%% BODY TEXT - ENTER YOUR RESPONSE BELOW
-% TODO: Don't worry about space
-% TODO: Do more bullet point style
-% TODO: Thank all the reviewers at the start, skip sentences later
 Thank you to all the reviewers for all of your constructive comments and feedback.
-We hope to address some of your concerns here.
+We fully understand your concerns and we elaborate on them here.
+We kindly ask you to trust us that the presentation will be clear in
+the camera-ready and to reward the novelty of the idea in your ratings.
 
-\section{Reviewer \#1}
-\textbf{The benefits of applying a GCN instead of classical optimization methods are not clear and the use of a Convolutional Neural Network to solve the multi-view matching problem appears contrived.}:
-One of the primary benefits is the ability to integrate the matching in an end-to-end learning pipeline, which could for instance train on semantic features.
-We could have tried learning on sets of features but that would throw out the structure between the features, so graphs were the best way to represent that.
-Adding in additional side-losses can assist in training, an option not available in optimization based methods.
+\textbf{(R1)} ``\textit{GCNs (Section 3.2) should be deeply described}'' and (R5) ``\textit{Especially Section 3.1-3.3 are very confusing}'':
+We agree that we could have done a better job and we will have a comprehensive introduction into GCNs in the camera ready.
 
-\textbf{GCNs (Section 3.2) should be deeply described} and \textbf{most of the figures are not cited in the tex}: 
-We will cite the figures in the appropriate places better, with better descriptions.
+\textbf{(R1)} ``\textit{images showing the experimental results (figure 5, 6, 7) should be better clarified and discussed}'' and 
+\textbf{(R1)} ``\textit{most of the figures are not cited in the tex}'' and
+\textbf{(R5)} ``\textit{Axes in the charts are usually missing. There are typos and grammatical errors in the text}'':
+We agree and we will make the captions comprehensible and self-contained, reference the figures in the text more, and label the axes better.
 
-\textbf{images showing the experimental results (figure 5, 6, 7) should be better clarified and discussed}: 
-Relatedly, can reference the figures on the experiments in the text more, and label the axes better.
+\textbf{(R1)} ``\textit{The performances of the proposed method should be evaluated also on sequences of tens of images. Multiview matching with 4 images is not very meaningful}'' and 
+\textbf{(R5)} ``\textit{The evaluation of the testing part is not satisfactory. Although it is a general multi-image method, only three- and four-view tests are included}'':
+We fully agree that sets of tens of images would be even better.
+But even with 3-4 views we are doing better than RANSAC computationally: RANSAC using trifocal tensor needs sampling of 7 triples for already established weak correspondences
 
-\textbf{The reference to the “spectral method” used in the experiments is missing.}: 
-We neglected to cite it \cite{pachauri2013solving} in the table only briefly in the methods section. This is simply taking the top $k$ eigenvectors as the embedding.
+\textbf{(R3)} ``\textit{Details on the network architecture (beyond it having 12 layers) are missing}'' and 
+\textbf{(R5)} ``\textit{I think the method cannot be re-implemented based on the submitted manuscript}'':
+Our layer splits were: 32, 64, 128, 256, 512, 512, 512, 512, 512, 512, 1024, 1024.
+We had skip connections between the input and layers 7 and 12, with small one layer skip connections between each layer.
+We will also be releasing code if accepted, which will clarify all points.
 
-\textbf{The performances of the proposed method should be evaluated also on sequences of tens of images. Multiview matching with 4 images is not very meaningful}: 
-We admit the lack of larger view-sets for our experiments is an oversight.
-However RANSAC based methods start becoming computationally infeasible at 3 and 4 images (12-point RANSAC for the trifocal tensor is too demanding) so it was the simplest test to see how our method would fair.
-% While not explored in this work, GNNs have great potential in fast parallel
-% computation which has been difficult to do for optimization based
-% methods. Your comment on how use of a CNN to solve the matching
-% problem appears contrived but we use GNNs - unless there is some
-% confusion here.
-% TODO: We could use sets but that would throw away the structure of our data
-% TODO: Most structured
+\textbf{(R1)} ``\textit{The benefits of applying a GCN instead of classical optimization methods are not clear and the use of a Convolutional Neural Network to solve the multi-view matching problem appears contrived.}'':
+The main benefit is the learning of new feature representations whose distance better supports multi-view matching.
+Learning novel feature representations through CNN (like LIFT descriptor, for example) is a widely admitted interesting line of research although it will not necessarily beat yet benchmarks on SLAM problems.
+Second benefit of the GCN formulation is that we can add to the same end-to-end pipeline geometric or other losses, in addition to cycle consistency.
+If the criticism is regarding the graphs and not the CNN part of GCN, then we claim that graphs is the natural representation for matching problems but we agree that using pointsets would be an interesting future direction, too.
 
-% TODO: Less apologetic
-% TODO: Their comments in quotes
+\textbf{(R1)} ``\textit{The reference to the “spectral method” used in the experiments is missing.}'': 
+We will add \cite{pachauri2013solving} to the table.
 
-\section{Reviewer \#3}
-\textbf{ In my opinion, measuring the precision and recall in terms of identifying correct matches would be a better evaluation score (and also closer to the problem setting) (W1).}:
-You are right that an precision-recall or ROC curve would be a good measure. We have added in this rebuttal a figure showing the ROC curves of our method compared to other methods.
+\textbf{(R3)} ``\textit{In my opinion, measuring the precision and recall in terms of identifying correct matches would be a better evaluation score (and also closer to the problem setting).}'':
+You are right that an precision-recall or ROC curve would be a good measure. We have added in this rebuttal a figure showing the ROC and mAP of our method compared to other methods.
 
-\textbf{I am worried that the Rome16k dataset is not really suited to demonstrate the benefits of multi-image matching under cycle consistency (W2a)}:
+\textbf{(R3)} ``\textit{I am worried that the Rome16k dataset is not really suited to demonstrate the benefits of multi-image matching under cycle consistency}'':
 % We couldn't find a more appropriate large scale dataset where we could find ground truth matches.
 We could collect our own but we wanted to test against a well-known dataset (even if it is typically used in other contexts) for a more fair comparison.
-We needed a large-scale dataset with multi-view matching and having ground truth to evaluate against.
+We needed a large-scale dataset with multi-view matching and ground truth to evaluate against.
 Rome16K seemed the most appropriate dataset, as other datasets with ground truth were far too small.
@@
 
-\textbf{there are not really experiments analyzing the robustness of the proposed approach to outliers (W2b)}:
+\textbf{(R3)} ``\textit{there are not really experiments analyzing the robustness of the proposed approach to outliers}'':
 You are right in that more outlier experiments could have been done.
 
-\textbf{Details on the network architecture (beyond it having 12 layers) are missing (W3a)}:
-Our layer splits were: 32, 64, 128, 256, 512, 512, 512, 512, 512, 512, 1024, 1024.
-We had skip connections between the input and layers 7 and 12, with small one layer skip connections between each layer.
-
-\textbf{It is unclear how the Rome16k dataset is split into a test and training set (W3b)}:
+\textbf{(R3)} ``\textit{It is unclear how the Rome16k dataset is split into a test and training set}'':
 There was no overlap of sequences in training and testing sets. It was trained on one set of buildings and tested on another, so it has not overfit to particular buildings.
 
-\section{Reviewer \#5}
-
-\textbf{I think the method cannot be re-implemented based on the submitted manuscript. Especially Section 3.1-3.3 are very confusing}:
-You as well as Reviewer \#1 felt the discussion on GNNs was insufficient and we will add more detail should this paper be accepted, especially about Graph Neural Networks.
-
-\textbf{The evaluation of the testing part is not satisfactory. Although it is a general multi-image method, only three- and four-view tests are included}:
-See Reviewer \#1 - we were testing on the minimum number of images before RANSAC based methods on multi-view constraints became impractical.
-
-\textbf{Axes in the charts are usually missing. There are typos and grammatical errors in the text}:
-Indeed we did not label them - we will add labels and greater descriptions for each of the figures.
-
-\textbf{ do not agree that RANSAC can only be applied for stereo matching. E.g. a multi-view robust RANSAC-based factorization is proposed in the work of Hajder\&Chetverikov }:
+\textbf{(R5)} ``\textit{do not agree that RANSAC can only be applied for stereo matching. E.g. ... Hajder\&Chetverikov }'':
 We indeed did not know of \cite{hajder2006weak}. We will cite it and hope to use some of its techniques in future work.
@@
 \begin{center}
-\begin{tabular}{ |c|c|c|c|c|c| }
+\begin{tabular}{ |c|c|c| }
 \hline
 Method           & ROC       & mAP       \\ \hline
-GCN 12 Layers                                  & 0.953  & 0.655  \\ \hline
-MatchALS \cite{zhou2015multi}  15 Iter.        & 0.624  & 0.653  \\ \hline
-MatchALS \cite{zhou2015multi}  25 Iter.        & 0.573  & 0.569  \\ \hline
-MatchALS \cite{zhou2015multi}  50 Iter.        & 0.437  & 0.423  \\ \hline
-MatchALS \cite{zhou2015multi} 100 Iter.        & 0.404  & 0.302  \\ \hline
-PGDDS \cite{leonardos2016distributed} 15 Iter. & 0.918  & 0.724  \\ \hline
-PGDDS \cite{leonardos2016distributed} 25 Iter. & 0.920  & 0.768  \\ \hline
-PGDDS \cite{leonardos2016distributed} 50 Iter. & 0.920  & 0.795  \\ \hline
-Spectral \cite{pachauri2013solving}            & 0.917  & 0.689  \\ \hline
+GCN 12 Layers                                     & 9.088e-01 & 6.073e-01 \\ \hline
+Spectral          & 9.175e-01 & 7.735e-01 \\ \hline
+MatchALS 15 Iter. & 9.138e-01 & 7.384e-01 \\ \hline
+MatchALS 50 Iter. & 9.163e-01 & 6.691e-01 \\ \hline
+PGDDS    15 Iter. & 9.170e-01 & 7.357e-01 \\ \hline
+PGDDS    50 Iter. & 8.829e-01 & 6.691e-01 \\ \hline
 \end{tabular}
 \end{center}
-\caption{}
+\caption{ROC area and mean average precision (mAP). Some methods and citations skipped due to space constraints.}
+\vspace{-15pt}
+\end{table}
 
-\end{table}
+% \begin{table}[t]
+% \begin{center}
+% \begin{tabular}{ |c|c|c| }
+% \hline
+% Method           & ROC       & mAP       \\ \hline
+% GCN 12 Layers                                  & 9.088e-01 & 6.073e-01 \\ \hline
+% Spectral \cite{pachauri2013solving}            & 9.175e-01 & 7.735e-01 \\ \hline
+% MatchALS \cite{zhou2015multi}  15 Iter.        & 9.138e-01 & 7.384e-01 \\ \hline
+% MatchALS \cite{zhou2015multi}  50 Iter.        & 9.163e-01 & 6.691e-01 \\ \hline
+% PGDDS \cite{leonardos2016distributed} 15 Iter. & 9.170e-01 & 7.357e-01 \\ \hline
+% PGDDS \cite{leonardos2016distributed} 50 Iter. & 8.829e-01 & 6.691e-01 \\ \hline
+% \end{tabular}
+% \end{center}
+% \caption{ROC area and mean average precision (mAP).}
+% \vspace{-15pt}
+% \end{table}
+
+% \begin{table}[t]
+% \begin{center}
+% \begin{tabular}{ |c|c|c|c|c|c| }
+% \hline
+% Method                                         & ROC    & mAP \\ \hline
+% GCN 12 Layers                                  & 0.953  & 0.655  \\ \hline
+% MatchALS \cite{zhou2015multi}  15 Iter.        & 0.624  & 0.653  \\ \hline
+% MatchALS \cite{zhou2015multi}  25 Iter.        & 0.573  & 0.569  \\ \hline
+% MatchALS \cite{zhou2015multi}  50 Iter.        & 0.437  & 0.423  \\ \hline
+% MatchALS \cite{zhou2015multi} 100 Iter.        & 0.404  & 0.302  \\ \hline
+% PGDDS \cite{leonardos2016distributed} 15 Iter. & 0.918  & 0.724  \\ \hline
+% PGDDS \cite{leonardos2016distributed} 25 Iter. & 0.920  & 0.768  \\ \hline
+% PGDDS \cite{leonardos2016distributed} 50 Iter. & 0.920  & 0.795  \\ \hline
+% Spectral \cite{pachauri2013solving}            & 0.917  & 0.689  \\ \hline
+% \end{tabular}
+% \end{center}
+% \caption{}
+% 
+% \end{table}
 % GCN 12 Layers                                  & 0.953 $\pm$ 0.071 & 0.655 $\pm$ 0.113 \\ \hline
@@
 
-{\small
+{\footnotesize
 \bibliographystyle{ieee}

### 2019-02-12 cvpr2019/rebuttal/egrebuttal.tex
Last update of rebuttal

@@
 
-\textbf{(R1)} ``\textit{GCNs (Section 3.2) should be deeply described}'' and (R5) ``\textit{Especially Section 3.1-3.3 are very confusing}'':
-We agree that we could have done a better job and we will have a comprehensive introduction into GCNs in the camera ready.
-
-\textbf{(R1)} ``\textit{images showing the experimental results (figure 5, 6, 7) should be better clarified and discussed}'' and 
-\textbf{(R1)} ``\textit{most of the figures are not cited in the tex}'' and
-\textbf{(R5)} ``\textit{Axes in the charts are usually missing. There are typos and grammatical errors in the text}'':
-We agree and we will make the captions comprehensible and self-contained, reference the figures in the text more, and label the axes better.
-
-\textbf{(R1)} ``\textit{The performances of the proposed method should be evaluated also on sequences of tens of images. Multiview matching with 4 images is not very meaningful}'' and 
-\textbf{(R5)} ``\textit{The evaluation of the testing part is not satisfactory. Although it is a general multi-image method, only three- and four-view tests are included}'':
-We fully agree that sets of tens of images would be even better.
-But even with 3-4 views we are doing better than RANSAC computationally: RANSAC using trifocal tensor needs sampling of 7 triples for already established weak correspondences
-
-\textbf{(R3)} ``\textit{Details on the network architecture (beyond it having 12 layers) are missing}'' and 
-\textbf{(R5)} ``\textit{I think the method cannot be re-implemented based on the submitted manuscript}'':
-Our layer splits were: 32, 64, 128, 256, 512, 512, 512, 512, 512, 512, 1024, 1024.
-We had skip connections between the input and layers 7 and 12, with small one layer skip connections between each layer.
-We will also be releasing code if accepted, which will clarify all points.
-
 \textbf{(R1)} ``\textit{The benefits of applying a GCN instead of classical optimization methods are not clear and the use of a Convolutional Neural Network to solve the multi-view matching problem appears contrived.}'':
@@
 If the criticism is regarding the graphs and not the CNN part of GCN, then we claim that graphs is the natural representation for matching problems but we agree that using pointsets would be an interesting future direction, too.
-
-\textbf{(R1)} ``\textit{The reference to the “spectral method” used in the experiments is missing.}'': 
-We will add \cite{pachauri2013solving} to the table.
 
@@
 
+\textbf{(R1)} ``\textit{The performances of the proposed method should be evaluated also on sequences of tens of images. Multiview matching with 4 images is not very meaningful}'' and 
+\textbf{(R5)} ``\textit{The evaluation of the testing part is not satisfactory. Although it is a general multi-image method, only three- and four-view tests are included}'':
+Even with 3-4 views we are doing better than RANSAC computationally: RANSAC using trifocal tensor needs sampling of 7 triples for already established weak correspondences.
+But we fully agree that sets of tens of images would be even better.
+
+\textbf{(R1)} ``\textit{GCNs (Section 3.2) should be deeply described}'' and
+\textbf{(R5)} ``\textit{Especially Section 3.1-3.3 are very confusing}'':
+We agree that we could have done a better job and we will have a comprehensive introduction into GCNs in the camera ready.
+
+\textbf{(R1)} ``\textit{images showing the experimental results (figure 5, 6, 7) should be better clarified and discussed}'' and 
+\textbf{(R1)} ``\textit{most of the figures are not cited in the tex}'' and
+\textbf{(R5)} ``\textit{Axes in the charts are usually missing. There are typos and grammatical errors in the text}'':
+We agree and we will make the captions comprehensible and self-contained, reference the figures in the text more, and label the axes better.
+
+\textbf{(R3)} ``\textit{Details on the network architecture (beyond it having 12 layers) are missing}'' and 
+\textbf{(R5)} ``\textit{I think the method cannot be re-implemented based on the submitted manuscript}'':
+Our layer splits were: 32, 64, 128, 256, 512, 512, 512, 512, 512, 512, 1024, 1024.
+We had skip connections between the input and layers 7 and 12, with small one layer skip connections between each layer.
+We will also be releasing code if accepted, which will clarify all points.
+
+\textbf{(R1)} ``\textit{The reference to the “spectral method” used in the experiments is missing.}'': 
+We will add \cite{pachauri2013solving} to the table.
+
 \textbf{(R3)} ``\textit{there are not really experiments analyzing the robustness of the proposed approach to outliers}'':
-You are right in that more outlier experiments could have been done.
+% You are right in that more outlier experiments could have been done. 
+We will add more outlier experiments for the camera-ready.
 
@@
 Method            & ROC       & mAP       \\ \hline
-GCN 12 Layers                                     & 9.088e-01 & 6.073e-01 \\ \hline
-Spectral          & 9.175e-01 & 7.735e-01 \\ \hline
-MatchALS 15 Iter. & 9.138e-01 & 7.384e-01 \\ \hline
-MatchALS 50 Iter. & 9.163e-01 & 6.691e-01 \\ \hline
-PGDDS    15 Iter. & 9.170e-01 & 7.357e-01 \\ \hline
-PGDDS    50 Iter. & 8.829e-01 & 6.691e-01 \\ \hline
+GCN 12 Layers     & 9.531e-01 & 6.772e-01 \\ \hline
+Spectral          & 9.629e-01 & 8.089e-01 \\ \hline
+MatchALS  15 Iter.& 9.540e-01 & 8.149e-01 \\ \hline
+MatchALS  50 Iter.& 9.173e-01 & 7.471e-01 \\ \hline
+PGDDS     15 Iter.& 9.621e-01 & 8.360e-01 \\ \hline
+PGDDS     50 Iter.& 9.635e-01 & 9.033e-01 \\ \hline
 \end{tabular}
@@
 
-% \begin{table}[t]
-% \begin{center}
-% \begin{tabular}{ |c|c|c| }
-% \hline
-% Method           & ROC       & mAP       \\ \hline
-% GCN 12 Layers                                  & 9.088e-01 & 6.073e-01 \\ \hline
-% Spectral \cite{pachauri2013solving}            & 9.175e-01 & 7.735e-01 \\ \hline
-% MatchALS \cite{zhou2015multi}  15 Iter.        & 9.138e-01 & 7.384e-01 \\ \hline
-% MatchALS \cite{zhou2015multi}  50 Iter.        & 9.163e-01 & 6.691e-01 \\ \hline
-% PGDDS \cite{leonardos2016distributed} 15 Iter. & 9.170e-01 & 7.357e-01 \\ \hline
-% PGDDS \cite{leonardos2016distributed} 50 Iter. & 8.829e-01 & 6.691e-01 \\ \hline
-% \end{tabular}
-% \end{center}
-% \caption{ROC area and mean average precision (mAP).}
-% \vspace{-15pt}
-% \end{table}
+% GCN 12 Layers     & 9.531e-01 & 6.772e-01
+% Spectral          & 9.629e-01 & 8.089e-01
+% MatchALS  15 Iter.& 9.540e-01 & 8.149e-01
+% MatchALS  50 Iter.& 9.173e-01 & 7.471e-01
+% PGDDS     15 Iter.& 9.621e-01 & 8.360e-01
+% PGDDS     50 Iter.& 9.635e-01 & 9.033e-01
 
-% \begin{table}[t]
-% \begin{center}
-% \begin{tabular}{ |c|c|c|c|c|c| }
-% \hline
-% Method                                         & ROC    & mAP \\ \hline
-% GCN 12 Layers                                  & 0.953  & 0.655  \\ \hline
-% MatchALS \cite{zhou2015multi}  15 Iter.        & 0.624  & 0.653  \\ \hline
-% MatchALS \cite{zhou2015multi}  25 Iter.        & 0.573  & 0.569  \\ \hline
-% MatchALS \cite{zhou2015multi}  50 Iter.        & 0.437  & 0.423  \\ \hline
-% MatchALS \cite{zhou2015multi} 100 Iter.        & 0.404  & 0.302  \\ \hline
-% PGDDS \cite{leonardos2016distributed} 15 Iter. & 0.918  & 0.724  \\ \hline
-% PGDDS \cite{leonardos2016distributed} 25 Iter. & 0.920  & 0.768  \\ \hline
-% PGDDS \cite{leonardos2016distributed} 50 Iter. & 0.920  & 0.795  \\ \hline
-% Spectral \cite{pachauri2013solving}            & 0.917  & 0.689  \\ \hline
-% \end{tabular}
-% \end{center}
-% \caption{}
-% 
-% \end{table}
-% GCN 12 Layers                                  & 0.953 $\pm$ 0.071 & 0.655 $\pm$ 0.113 \\ \hline
-% MatchALS \cite{zhou2015multi}  15 Iter.        & 0.624 $\pm$ 0.078 & 0.653 $\pm$ 0.184 \\ \hline
-% MatchALS \cite{zhou2015multi}  25 Iter.        & 0.573 $\pm$ 0.060 & 0.569 $\pm$ 0.167 \\ \hline
-% MatchALS \cite{zhou2015multi}  50 Iter.        & 0.437 $\pm$ 0.042 & 0.423 $\pm$ 0.151 \\ \hline
-% MatchALS \cite{zhou2015multi} 100 Iter.        & 0.404 $\pm$ 0.066 & 0.302 $\pm$ 0.116 \\ \hline
-% PGDDS \cite{leonardos2016distributed} 15 Iter. & 0.918 $\pm$ 0.101 & 0.724 $\pm$ 0.224 \\ \hline
-% PGDDS \cite{leonardos2016distributed} 25 Iter. & 0.920 $\pm$ 0.101 & 0.768 $\pm$ 0.230 \\ \hline
-% PGDDS \cite{leonardos2016distributed} 50 Iter. & 0.920 $\pm$ 0.101 & 0.795 $\pm$ 0.224 \\ \hline
-% Spectral \cite{pachauri2013solving}            & 0.917 $\pm$ 0.103 & 0.689 $\pm$ 0.197 \\ \hline
-
-% \begin{figure}[t]
-% \begin{center}
-% \fbox{\rule{0pt}{1.8in} \rule{0.9\linewidth}{0pt}}
-%    %\includegraphics[width=0.8\linewidth]{egfigure.eps}
-% \end{center}
-%    \caption{Example of caption.  It is set in Roman so that mathematics
-%    (always set in Roman: $B \sin A = A \sin B$) may be included without an
-%    ugly clash.}
-% \label{fig:long}
-% \label{fig:onecol}
-% \end{figure}
+% GCN 12 Layers     : ROC: 9.531e-01 +/- 7.094e-02 ; P-R: 6.772e-01 +/- 1.114e-01
+% MatchALS  15 Iter.: ROC: 9.540e-01 +/- 6.538e-02 ; P-R: 8.149e-01 +/- 1.420e-01
+% MatchALS  25 Iter.: ROC: 9.471e-01 +/- 6.208e-02 ; P-R: 8.306e-01 +/- 1.482e-01
+% MatchALS  50 Iter.: ROC: 9.173e-01 +/- 6.018e-02 ; P-R: 7.471e-01 +/- 1.566e-01
+% MatchALS 100 Iter.: ROC: 9.071e-01 +/- 6.694e-02 ; P-R: 7.166e-01 +/- 1.716e-01
+% PGDDS     15 Iter.: ROC: 9.621e-01 +/- 7.694e-02 ; P-R: 8.360e-01 +/- 1.646e-01
+% PGDDS     25 Iter.: ROC: 9.630e-01 +/- 7.676e-02 ; P-R: 8.811e-01 +/- 1.646e-01
+% PGDDS     50 Iter.: ROC: 9.635e-01 +/- 7.650e-02 ; P-R: 9.033e-01 +/- 1.621e-01
+% Spectral          : ROC: 9.629e-01 +/- 7.413e-02 ; P-R: 8.089e-01 +/- 1.577e-01
+% AlmostPerfect     : ROC: 1.000e+00 +/- 0.000e+00 ; P-R: 1.000e+00 +/- 0.000e+00
+% Random            : ROC: 5.001e-01 +/- 8.223e-03 ; P-R: 1.256e-02 +/- 3.765e-04
 

### 2019-02-12 baselines/roc_curves.py

@@ -5,134 +5,105 @@ import glob
 import numpy as np
 import matplotlib.pyplot as plt 
 import time
+import sklearn.metrics as metrics
+import tqdm
+import itertools
 
-def calc_classifications(o, a):
-  TP = np.sum(o*a)
-  TN = np.sum((1-o)*(1-a))
-  FP = np.sum(o*(1-a))
-  FN = np.sum((1-o)*a)
-  return TP, TN, FP, FN
+def scatterplot_matrix(data, names, **kwargs):
+  """Plots a scatterplot matrix of subplots.  Each row of "data" is plotted
+  against other rows, resulting in a nrows by nrows grid of subplots with the
+  diagonal subplots labeled with "names".  Additional keyword arguments are
+  passed on to matplotlib's "plot" command. Returns the matplotlib figure
+  object containg the subplot grid."""
+  numvars, numdata = data.shape
+  fig, axes = plt.subplots(nrows=numvars, ncols=numvars, figsize=(8,8))
+  fig.subplots_adjust(hspace=0.05, wspace=0.05)
 
+  for ax in axes.flat:
+    # Hide all ticks and labels
+    ax.xaxis.set_visible(False)
+    ax.yaxis.set_visible(False)
 
-def compute_thresh_errs(output, adjmat, N_cutoffs=2048):
-  a = adjmat.astype(np.int32)
-  M_T = np.sum(a)
-  M_F = a.size - M_T
+    # Set up ticks only on one side for the "edge" subplots...
+    if ax.is_first_col():
+      ax.yaxis.set_ticks_position('left')
+    if ax.is_last_col():
+      ax.yaxis.set_ticks_position('right')
+    if ax.is_first_row():
+      ax.xaxis.set_ticks_position('top')
+    if ax.is_last_row():
+      ax.xaxis.set_ticks_position('bottom')
 
-  TP_, TN_, FP_, FN_ = (np.zeros(N_cutoffs).astype(np.int32) for i in range(4))
-  TP_[ 0], TN_[ 0], FP_[ 0], FN_[ 0] =   0, M_F,   0, M_T
-  TP_[-1], TN_[-1], FP_[-1], FN_[-1] = M_T,   0, M_F,   0
-  for idx in range(1,N_cutoffs-1):
-    i = (N_cutoffs - 1) - idx
-    thresh = (1.0*i) / (N_cutoffs-1)
[…]

### 2019-02-12 baselines/run_tests.m

@@ -14,6 +14,9 @@ if ~onPath
   addpath(npymatlab_path);
 end
 [~,~,~] = mkdir('/tmp/unzip');
+if save_out
+  [~,~,~] = mkdir('Adjmats');
+end
 
 v = views;
 p = 80;
@@ -54,12 +57,14 @@ test_fns = { ...
  'PGDDS050Iter', @(W) PGDDS(W, dimGroups, p, params050); ...
 };
 
-outputs = zeros(length(npz_files), n, n);
-adjmats = zeros(length(npz_files), n, n);
+saveout_str = '%sOutputs/%04d.npy';
 for test_fn_index = 1:size(test_fns,1)
   test_fn_tic = tic;
   test_fn = test_fns{test_fn_index,2};
   fid = fopen(sprintf('%sTestErrors.log', test_fns{test_fn_index,1}), 'w');
+  if save_out
+    [~,~,~] = mkdir(sprintf('%sOutputs', test_fns{test_fn_index,1}))
+  end
   fprintf('%s Method:\n', test_fns{test_fn_index,1})
   test_index = 0;
   for npz_index = 1:length(npz_files)
@@ -76,8 +81,12 @@ for test_fn_index = 1:size(test_fns,1)
     disp_values(metric_info, fid, npz_index, values, run_time);
     test_index = test_index + 1;
     if save_out
-      outputs(npz_index,:,:) = Ah;
-      adjmats(npz_index,:,:) = Agt;
+      output_name = sprintf(saveout_str, test_fns{test_fn_index,1}, npz_index);
+      writeNPY(single(Ah), output_name);
+      adjmat_name = sprintf('Adjmats/%04d.npy', npz_index);
+      if ~exist(adjmat_name)
+        writeNPY(Agt, adjmat_name)
+      end
     end
   end
   fprintf('\n')
@@ -88,11 +97,6 @@ for test_fn_index = 1:size(test_fns,1)
   end
   disp_values(metric_info, 1, test_fn_index, means, run_time);
   fprintf(1, 'Total time: %.03f seconds\n', toc(test_fn_tic));
-  if save_out
-    fprintf(1, 'Saving out %s', test_fns{test_fn_index,1})
-    writeNPY(outputs, sprintf('%s-Outputs.npy', test_fns{test_fn_index,1}));
[…]

### 2019-03-03 data_util/datasets.py
Added true embeddings to dataset

@@ -29,6 +29,6 @@ def get_dataset(opts):
     return real_dataset.KNNRome16KDataset(opts, opts.dataset_params)
   elif opts.dataset in [ 'rome16kgeom0', 'rome16kgeom4view0' ]:
     return real_dataset.GeomKNNRome16KDataset(opts, opts.dataset_params)
-  elif opts.dataset in [ 'spsynth0' ]:
+  elif opts.dataset in [ 'spsynth0', 'spsynth_test' ]:
     return spgraph_dataset.SpSynthGraphDataset(opts, opts.dataset_params)
 

### 2019-03-03 data_util/spgraph_dataset.py

@@ -17,15 +17,17 @@ from data_util import mydataset
 from data_util import synth_graphs
 from data_util import tf_helpers
 
-def denseNDArrayToSparseTensor(arr):
-  idx  = np.where(arr != 0.0)
-  return tf.SparseTensor(np.vstack(idx).T, arr[idx], arr.shape)
+def np_dense_to_sparse(arr):
+  idx = np.where(arr != 0.0)
+  return idx, arr[idx]
 
 class SpSynthGraphDataset(mydataset.MyDataset):
   MAX_IDX=700
   def __init__(self, opts, params):
     super().__init__(opts, params)
-    d = self.n_pts*self.n_views
+    p = self.n_pts
+    v = self.n_views
+    d = p*v
     e = params.descriptor_dim
     """
     GraphsTuple(nodes=nodes,
@@ -68,17 +70,22 @@ class SpSynthGraphDataset(mydataset.MyDataset):
                          key='senders',
                          dtype='int32',
                          description='Sending nodes for edges'),
-      'adjmat':
+      'adj_mat':
            tf_helpers.SparseTensorFeature(
-                         key='adjmat',
+                         key='adj_mat',
                          shape=[d, d],
                          description='Sparse adjacency matrix of graph'),
+      'true_emb':
+           tf_helpers.SparseTensorFeature(
+                         key='true_emb',
+                         shape=[d, p],
+                         description='Sparse ground truth embedding of graph'),
     }
     self.graph_keys = [
       'n_node', 'nodes', 'n_edge', 'edges', 'receivers', 'senders'
     ]
-    self.other_keys = [ 'adjmat' ]
     # self.other_keys = [ ]
+    self.other_keys = list(set(self.features.keys()) - set(self.graph_keys))
     self.item_keys = self.graph_keys + self.other_keys
 
   def get_placeholders(self):
@@ -87,7 +94,7 @@ class SpSynthGraphDataset(mydataset.MyDataset):
   def gen_init_emb_noise(self, init_emb):
     return init_emb
 
-  def gen_adjmat_noise(self, true_emb):
+  def gen_adj_mat_noise(self, true_emb):
     adj_mat = np.dot(true_emb,true_emb.T) - np.eye(true_emb.shape[0])
     # if np.random.randn() > 0:
     #   d = self.n_pts*self.n_views
[…]

### 2019-03-03 options.py

@@ -328,6 +328,7 @@ def get_opts():
     dataset_params.sizes={ 'train': -1, 'test': -1 }
   elif opts.dataset == 'spsynth0':
     dataset_params.sizes={ 'train': 400, 'test': 300 }
+    # dataset_params.views = [4]
   else:
     pass
   opts.data_dir = dataset_params.data_dir

### 2019-03-03 test_graphnets2.py

@@ -21,6 +21,7 @@ from graph_nets import modules
 
 import options
 import data_util
+import tfutils
 
 import pprint
 pp = pprint.PrettyPrinter(indent=2)
@@ -34,7 +35,8 @@ def mygraphprint(x):
 sys.argv.extend(['--dataset', 'spsynth0',
                  '--datasets_dir', '/data',
                  '--rome16k_dir', '/mount/data/Rome16K',
-                 '--batch_size', '2'])
+                 '--batch_size', '2',
+                 '--save_dir', 'save/testing'])
 opts = options.get_opts()
 dtype = opts.dataset_params.dtype
 LD_FILE_SIZE = 128
@@ -62,16 +64,22 @@ class MLPInteractiveNetwork(snt.AbstractModule):
     return self._network(inputs)
 
 print("network")
-# network = MLPInteractiveNetwork()
-# print(network)
+network = MLPInteractiveNetwork()
+print(network)
 
 print("data")
 dataset = data_util.datasets.get_dataset(opts)
 sample = dataset.load_batch('train')
 
-# print("output")
-# output = network(sample['graph'])
-# print(output)
+print("output")
+output = network(sample['graph'])
+print(output.nodes)
+output_batch = tf.reshape(output.nodes, [ opts.batch_size, -1, 25 ])
+print(output_batch)
+output_sim = tfutils.get_sim(output_batch)
+print(output_sim)
+diff = tf.sparse_add(-output_sim, sample['adj_mat'])
+loss = tf.reduce_mean(tf.abs(diff))
 
 config = tf.ConfigProto()
 config.gpu_options.allow_growth = True
@@ -82,11 +90,10 @@ with tf.Session(config=config) as sess:
   # for i in range(opts.dataset_params.sizes['train'] // opts.batch_size):
   for i in range(10):
     # import pdb; pdb.set_trace()
-    o = sess.run(sample)
-    print("o")
-    mygraphprint(o['graph'])
-    print(o['adjmat'])
-    print("I FINALLY GOT THE OUTPUT :D")
+    [ s, osim, l ] = sess.run([ sample, output_sim, loss ])
+    nodes = s['graph'].nodes
+    print("loss: {}, output_sim: {}, nodes: {}".format(l, osim.shape, nodes.shape))
+  print("I FINALLY GOT THE OUTPUT :D")
 
 
 

### 2019-03-04 latex/arxiv/main.tex
Moved latex related files to folder latex

--- 2018-11-19 cvpr2019/main.tex
@@
 \usepackage{amssymb}
+\usepackage{float}
 % Include other packages here, before hyperref.
@@
 
-% \cvprfinalcopy % *** Uncomment this line for the final submission
+\cvprfinalcopy % *** Uncomment this line for the final submission
 
@@
   % \fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-  \includegraphics[width=0.8\linewidth]{figures/CycleConsistencyBasic.pdf}
+  \includegraphics[width=0.8\linewidth]{figures-CycleConsistencyBasic-v2.pdf}
 \end{center}
@@
   % \fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-  \includegraphics[width=0.8\linewidth]{figures/CycleConsistencyMainFigure.pdf}
+  \includegraphics[width=0.8\linewidth]{figures-CycleConsistencyMainFigure-v2.pdf}
 \end{center}
@@
 \begin{center}
-  \includegraphics[width=0.9\linewidth]{figures/UniverseOfFeatures.pdf}
+  \includegraphics[width=0.9\linewidth]{figures-UniverseOfFeatures-v2.pdf}
 \end{center}
@@
 \begin{center}
-  \includegraphics[width=0.8\linewidth]{figures/GeometricConsistency.pdf}
+  \includegraphics[width=0.8\linewidth]{figures-GeometricConsistency-v2.pdf}
 \end{center}
@@
   % \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
-  \includegraphics[width=0.8\linewidth]{figures/TrainingCurves.pdf}
+  \includegraphics[width=0.8\linewidth]{figures-TrainingCurves.pdf}
   \end{center}
@@
   % \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
-  \includegraphics[width=0.8\linewidth]{figures/ExampleOutput.pdf}
+  \includegraphics[width=0.8\linewidth]{figures-ExampleOutput.pdf}
   \end{center}
@@
   % \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
-  \includegraphics[width=0.8\linewidth]{figures/EmbeddingsViz.png}
+  \includegraphics[width=0.8\linewidth]{figures-EmbeddingsViz.png}
   \end{center}
@@
 
+\subsubsection*{Acknowledgements}
+Support by ARL DCIST CRA W911NF-17-2-0181, NSF-IIS-1703319, ARL RCTA W911NF-10-2-0016, ONR N00014-17-1-2093, and the Honda Research Institute is gratefully acknowledged.
+
 {\small
@@
 
+\newpage
+\onecolumn
+
+\section*{Appendix}
+
+\subsection*{A. Relative Efficiency Against Optimization Based Methods}
+
+In figure \ref{fig:iterplot} we show a more fine grained comparison of our algorithm to optimization based methods at different numbers of iterations.
+We show the mean and standard devation of the errors of all methods, testing the optimization based methods at different iterations.
+
+%------------------------------------------------------------------------
+\begin{figure*}[ht]
+\begin{center}
+  \includegraphics[width=0.9\linewidth]{figures-IterationsPlot.pdf}
+\end{center}
+  \caption{
+    This figure plots the average accuracy of the optimization methods by iteration compared to 12 iterations of our GCN based method.
+    The bold center line shows the mean, the colored in region shows 1 standard devation of the errors.
+    As we optimize for $L_1$ error, our method's $L_1$ loss is substantially better than its $L_2$ losses.
+    The right most plot shows time, plotted on a log scale for clarity.
+  }
+\label{fig:iterplot}
+\label{fig:onecol}
+\end{figure*}
+
+\subsection*{B. Effect of Group Normalization}
+We observe that training with group normalization helps with training and generalization error, as shown in figure \ref{fig:groupnorm}.
+As the Group Normalization operation is not easily parallelized across nodes in the graph, the use of Group Normalization is the main barrier to parallelization.
+Thus we will need to find alternative more parallelizable methods to improve generalization error for future work.
+
+%------------------------------------------------------------------------
+\begin{figure*}[!hb]
+\begin{center}
+  \includegraphics[width=0.8\linewidth]{figures-GroupNormTest.pdf}
+\end{center}
+  \caption{
+    This figure plots the training curves of the network with and without Group Normalization.
+    Note that while the train/test curves are fairly similar with or without Group Normalization, distance to the ground truth is improved greatly with Group Normalization.
+  }
+\label{fig:groupnorm}
+\label{fig:onecol}
+\end{figure*}
+
 \end{document}

### 2019-03-19 data_util/tf_helpers.py
Lots of things: Got sptrain not crashing due to sparse eye matrix, got npz based testing working

@@ -1,5 +1,7 @@
+import numpy as np
 import tensorflow as tf
 
+# TODO: Add concat feed_dict (not necessary for now)
 class MyFeature(object):
   """Custom class used for decoding a serialized int64 value."""
   def __init__(self, key, description, shape=[], dtype='float32'):
@@ -9,21 +11,15 @@ class MyFeature(object):
     self.shape = shape
     self.dtype = dtype
 
-  def get_placeholder(self):
-    return tf.placeholder(self.dtype, shape=[None] + self.shape)
-
-  def _get_feature_write(self, value):
-    return value
-
-  def _get_feature_read(self):
-    return tf.FixedLenFeature([], self.dtype)
-
   def get_feature_write(self, value):
     feat_write = self._get_feature_write(value)
     if type(feat_write) == dict:
       return feat_write
     else:
       return { self._key : feat_write }
+
+  def _get_feature_write(self, value):
+    return value
 
   def get_feature_read(self):
     feat_read = self._get_feature_read()
@@ -32,12 +28,36 @@ class MyFeature(object):
     else:
       return { self._key : feat_read }
 
+  def _get_feature_read(self):
+    return tf.FixedLenFeature([], self.dtype)
+
   def tensors_to_item(self, keys_to_tensors):
     tensor = keys_to_tensors[self._key]
     return tensor
   
   def stack(self, arr):
     return tf.stack(arr)
+
+  # Placeholder related stuff
+  def get_placeholder(self, batch=True):
+    placeholder = self._get_placeholder(batch)
+    if type(placeholder) == dict:
+      return placeholder
+    else:
+      return { self._key : placeholder }
+
+  def _get_placeholder(self, batch):
+    if batch:
+      return tf.placeholder(self.dtype, shape=[None] + self.shape)
+    else:
+      return tf.placeholder(self.dtype, shape=self.shape)
+
+  def get_feed_dict(self, values, batch=True):
+    value = values[self._key]
+    if batch:
+      return np.expand_dims(value, 0) # Add batch dimension
+    else:
+      return value
 
 
 class Int64Feature(MyFeature):
@@ -76,7 +96,6 @@ class TensorFeature(MyFeature):
     sess = tf.InteractiveSession()
     return tensor
      
-
 
 class VarLenIntListFeature(MyFeature):
   """Custom class used for decoding variable length int64 lists."""
[…]

### 2019-03-19 sptest.py

@@ -57,9 +57,31 @@ def get_np_losses(opts, output_sim, matches):
   true_emb = np.eye(opts.dataset_params.points[-1])[matches]
   adjmat = np.dot(true_emb, true_emb.T).reshape(-1)
   output = output_sim.reshape(-1)
-  roc =  metrics.roc_auc_score(adjmat, output)
-  p_r =  metrics.average_precision_score(adjmat, output)
-  return { 'roc': roc, 'p_r': p_r }
+  # Standard losses
+  l1 = np.mean(np.abs(output-adjmat))
+  l2 = np.mean((output-adjmat)**2)
+  # Histogram losses
+  N = np.sum(adjmat);
+  M = np.sum(1-adjmat);
+  S = output*adjmat
+  D = output*(1-adjmat)
+  ssame = np.sum(S) / N;
+  ssame_std = np.sqrt(np.sum(S**2) / N - ssame**2);
+  sdiff = np.sum(D) / M;
+  sdiff_std = np.sqrt(np.sum(D**2) / M  - sdiff**2);
+  # Classification losses
+  roc = metrics.roc_auc_score(adjmat, output)
+  p_r = metrics.average_precision_score(adjmat, output)
+  return {
+    'l1': l1,
+    'l2': l2,
+    'ssame_m': ssame,
+    'ssame_std': ssame_std,
+    'sdiff_m': sdiff,
+    'sdiff_std': sdiff_std,
+    'roc': roc,
+    'p_r': p_r,
+  }
 
 
 def build_test_session(opts):
@@ -73,27 +95,31 @@ def test_values(opts):
   dataset = data_util.datasets.get_dataset(opts)
   network = model.get_network(opts, opts.arch)
   # Sample and network output
-  sample = dataset.load_batch('test', repeat=1)
-  print('sample')
-  print(sample)
+  # sample = dataset.load_batch('test', repeat=1)
+  # output_graph = network(sample)
+  # output_sim = get_test_output_sim(opts, output_graph)
+  # losses = get_tf_test_losses(opts, sample, output_sim)
+  # tf_evals = [ losses, output_sim, sample['true_match'] ] 
+  sample, placeholders = dataset.get_placeholders()
   output_graph = network(sample)
-  print('output_graph')
-  print(output_graph)
   output_sim = get_test_output_sim(opts, output_graph)
-  losses = get_tf_test_losses(opts, sample, output_sim)
-  tf_evals = [ losses, output_sim, sample['true_match'] ] 
[…]

### 2019-03-19 sptrain.py

@@ -159,6 +159,20 @@ class Trainer(object):
               hooks=all_hooks,
               config=config)
 
+  def build_speye(self):
+    b, v, p = self.tensor_sizes
+    x = np.arange(v*p).reshape(-1,1)
+    xb = np.arange(b).reshape(-1,1)
+    o = np.ones((v*p,1))
+    ob = np.ones((b,1))
+    concat_vals = [np.kron(xb ,o)] + [np.kron(ob, x)] * 2
+    speye_idxs = np.concatenate(concat_vals, 1).astype(np.int64)
+    speye_vals = np.ones(b*v*p).astype(np.float32)
+    speye = tf.SparseTensor(indices=tf.convert_to_tensor(speye_idxs),
+                            values=tf.convert_to_tensor(speye_vals),
+                            dense_shape=[ b, v*p, v*p ])
+    return speye
+
   ########## Training and testing functions ##########
   def get_output_sim(self, out_graph):
     out_shape = [self.batch_size, -1, self.final_embedding_dim]
@@ -194,9 +208,7 @@ class Trainer(object):
   def get_loss(self, sample, output_sim, test_mode=False, name='train'):
     # Compute loss
     sim_true = sample['true_adj_mat']
-    b, v, p = self.tensor_sizes
-    speye = tf.sparse_reshape(tf.sparse.eye(num_rows=v*p), [1, v*p, v*p])
-    sim = tf.sparse_add(sample['adj_mat'], tf.sparse_concat(0, [speye] * b))
+    sim = tf.sparse_add(sample['adj_mat'], self.build_speye())
     reconstr_loss = loss_fns[self.loss_type](output_sim, sim)
     if self.geometric_loss > 0:
       geo_loss = self.get_geometric_loss(sample, output_sim, name='geom_loss_{}'.format(name))

### 2019-03-19 latex/iccv2019/main.tex

--- 2018-11-19 cvpr2019/main.tex
@@
 
-\usepackage{cvpr}
+\usepackage{iccv}
 \usepackage{times}
@@
 \usepackage{amssymb}
+
 % Include other packages here, before hyperref.
-% \usepackage[outdir=./]{epstopdf}
 
@@
 % run, let it finish, and you should be clear).
-\usepackage[breaklinks=true,bookmarks=false]{hyperref}
+\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
 
-% \cvprfinalcopy % *** Uncomment this line for the final submission
+% \iccvfinalcopy % *** Uncomment this line for the final submission
 
-\def\cvprPaperID{3510} % *** Enter the CVPR Paper ID here
+\def\iccvPaperID{****} % *** Enter the ICCV Paper ID here
 \def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
@@
 % Pages are numbered in submission mode, and unnumbered in camera-ready
-%\ifcvprfinal\pagestyle{empty}\fi
-\setcounter{page}{1}
+\ificcvfinal\pagestyle{empty}\fi
 \begin{document}
@@
 %%%%%%%%% TITLE
-% \title{All Graphs Lead to Rome: \\
-% Cycle Consistent Multi-View Representations Using Graph CNNs}
-\title{All Graphs Lead to Rome: Learning Geometric and Cycle-Consistent Representations with Graph Convolutional Networks}
+\title{Learning Geometric and Cycle-Consistent Representations with Graph Convolutional Networks}
 
@@
 % To save space, use either the email address or home page, not both
-% \and
-% Second Author\\
-% Institution2\\
-% First line of institution2 address\\
-% {\tt\small secondauthor@i2.org}
 }
-
-% When placing figures in \LaTeX, it's almost always best to use
-% \verb+\includegraphics+, and to specify the  figure width as a multiple of
-% the line width as in the example below
-% {\small\begin{verbatim}
-%    \usepackage[dvips]{graphicx} ...
-%    \includegraphics[width=0.8\linewidth]
-%                    {myfile.eps}
-% \end{verbatim}
-% }
 
@@
 
-% Papers, excluding the references section,
-% must be no longer than eight pages in length. The references section
-
 %%%%%%%%% ABSTRACT
-% We present a learning technique for refining multi-image feature matches in an unsupervised fashion.
 \begin{abstract}
@@
 
+% \subsubsection*{Acknowledgements}
+% Support by ARL DCIST CRA W911NF-17-2-0181, NSF-IIS-1703319, ARL RCTA W911NF-10-2-0016, ONR N00014-17-1-2093, and the Honda Research Institute is gratefully acknowledged.
+% 
 {\small
 \bibliographystyle{ieee}
-\bibliography{mybib}
+\bibliography{egbib}
 }

### 2019-03-21 baselines/npz-matlab/readNPZ.m
Updated run_tests.m with new and improved features for reading npy/npz files and calculating ROC curves

@@ -1,0 +1,20 @@
+function data = readNPZ(filename)
+% Function to read NPZ files into matlab.
+% *** Only reads a subset of all possible NPY files, specifically N-D arrays of certain data types.
+% See https://github.com/kwikteam/npy-matlab/blob/master/tests/npy.ipynb for
+% more.
+%
+
+dname = '/tmp/unzip-npz-reader';
+[~,~,~] = mkdir(dname); % Ignore if has already been made
+unzip(filename, dname);
+map = containers.Map;
+% read the data
+npyfiles = dir([ dname '/*npy' ]);
+for i = 1:length(npyfiles)
+  key = npyfiles(i).name(1:end-length('.npy'));
+  value = readNPY([ dname '/' npyfiles(i).name ]);
+  map(key) = value;
+end
+delete([ dname '/*' ])
+data = map;

### 2019-03-21 baselines/roc_test.m

@@ -1,0 +1,176 @@
+function test(verbose, plot_vals)
+if nargin < 1
+  verbose = false;
+end
+if nargin < 2
+  plot_vals = false;
+end
+% This is a test script
+
+[~,~,~] = mkdir('/tmp/mymatlab');
+npzmatlab_path = 'npz-matlab';
+pathCell = regexp(path, pathsep, 'split');
+onPath = any(strcmp(npzmatlab_path, pathCell));
+if ~onPath
+  addpath(npzmatlab_path);
+end
+
+niters = 20;
+n = 10;
+nbins = 14;
+bins = linspace(0,1,nbins);
+sz = 300;
+if plot_vals
+  fig = figure('Position', [floor(1.5*sz) 4*sz 3*sz 3*sz]); 
+end
+svals = [ 0.8 ];
+% Storage array
+ml_rocs = zeros(niters, length(svals));
+py_rocs = zeros(niters, length(svals));
+my_rocs = zeros(niters, length(svals));
+ml_p_rs = zeros(niters, length(svals));
+py_p_rs = zeros(niters, length(svals));
+my_p_rs = zeros(niters, length(svals));
+
+for iter = 1:niters
+for si = 1:length(svals)
+  %%% Calculate things
+  % Build score data
+  [ y_true, y_pred ] = build_data(n,svals(si));
+  % Build classification curves
+  [mlfpr,mltpr,~,mlroc] = perfcurve(y_true, y_pred, 1);
+  [mlreca,mlprec,~,mlp_r] = perfcurve(y_true, y_pred, 1, 'XCrit', 'prec', 'YCrit', 'reca');
+  mlprec(end) = 1;
+  % Python version of classification curves
+  [pyfpr, pytpr, pyprec, pyreca, pyroc, pyp_r] = run_python(y_true, y_pred);
+  % My version of classification curves
+  [myfpr, mytpr, myprec, myreca, myroc, myp_r] = ...
+      binary_clf_curve(y_true, y_pred);
+  %% Save for iteration
+  ml_rocs(iter,si) = mlroc;
+  ml_p_rs(iter,si) = mlp_r;
+  py_rocs(iter,si) = pyroc;
+  py_p_rs(iter,si) = pyp_r;
+  my_rocs(iter,si) = myroc;
+  my_p_rs(iter,si) = myp_r;
[…]

### 2019-03-21 baselines/roc_test.py

@@ -1,0 +1,31 @@
+import os
+import sys
+import numpy as np
+import sklearn.metrics as metrics
+
+def test():
+  with open(os.path.join(sys.argv[1], 'y_true.npy'), 'rb') as f:
+    y_true = np.load(f)
+  with open(os.path.join(sys.argv[1], 'y_pred.npy'), 'rb') as f:
+    y_pred = np.load(f)
+  roc =  metrics.roc_auc_score(y_true, y_pred)
+  p_r =  metrics.average_precision_score(y_true, y_pred)
+  # import pdb; pdb.set_trace()
+  precision, recall, _ = metrics.precision_recall_curve(y_true, y_pred)
+  fpr, tpr, _ = metrics.roc_curve(y_true, y_pred)
+  print("{:.06e} {:.06e}".format(roc,p_r))
+  print(precision.shape)
+  print(recall.shape)
+  with open(os.path.join(sys.argv[1], 'precision.npy'), 'wb') as f:
+    np.save(f, precision)
+  with open(os.path.join(sys.argv[1], 'recall.npy'), 'wb') as f:
+    np.save(f, recall)
+  with open(os.path.join(sys.argv[1], 'fpr.npy'), 'wb') as f:
+    np.save(f, fpr)
+  with open(os.path.join(sys.argv[1], 'tpr.npy'), 'wb') as f:
+    np.save(f, tpr)
+
+test() 
+
+
+

### 2019-03-21 baselines/run_tests.m

@@ -1,143 +1,134 @@
-function run_tests(mat_files, views)
+function run_tests(npz_files, views, save_out)
 
 if nargin < 2
   views = 3;
+end
+if nargin < 3
+  save_out = false;
+end
+
+npzmatlab_path = 'npz-matlab';
+pathCell = regexp(path, pathsep, 'split');
+onPath = any(strcmp(npzmatlab_path, pathCell));
+if ~onPath
+  addpath(npzmatlab_path);
+end
+if save_out
+  [~,~,~] = mkdir('Adjmats');
 end
 
 v = views;
 p = 80;
 n = p*v;
 dimGroups = ones(v,1)*p;
+params015.maxiter = 15;
+params025.maxiter = 25;
+params050.maxiter = 50;
+params100.maxiter = 100;
+params200.maxiter = 200;
 
-% 'Spectral', @(W)  myspectral(W, p); ...
-
-%  'MatchALS005Iter', @(W)  mmatch_CVX_ALS(W, dimGroups, 'maxrank', p, 'maxiter', 5); ...
-%  'MatchALS010Iter', @(W)  mmatch_CVX_ALS(W, dimGroups, 'maxrank', p, 'maxiter', 10); ...
-%  'MatchALS015Iter', @(W)  mmatch_CVX_ALS(W, dimGroups, 'maxrank', p, 'maxiter', 15); ...
-%  'MatchALS020Iter', @(W)  mmatch_CVX_ALS(W, dimGroups, 'maxrank', p, 'maxiter', 20); ...
-%  'MatchALS025Iter', @(W)  mmatch_CVX_ALS(W, dimGroups, 'maxrank', p, 'maxiter', 25); ...
-%  'MatchALS035Iter', @(W)  mmatch_CVX_ALS(W, dimGroups, 'maxrank', p, 'maxiter', 35); ...
-%  'MatchALS040Iter', @(W)  mmatch_CVX_ALS(W, dimGroups, 'maxrank', p, 'maxiter', 40); ...
-%  'MatchALS045Iter', @(W)  mmatch_CVX_ALS(W, dimGroups, 'maxrank', p, 'maxiter', 45); ...
-%  'MatchALS050Iter', @(W)  mmatch_CVX_ALS(W, dimGroups, 'maxrank', p, 'maxiter', 50); ...
-%  'MatchALS075Iter', @(W)  mmatch_CVX_ALS(W, dimGroups, 'maxrank', p, 'maxiter', 75); ...
[…]

### 2019-03-21 baselines/roc_test.m
Fixed a minor bug for the roc_curve implementation check

@@ -23,7 +23,7 @@ sz = 300;
 if plot_vals
   fig = figure('Position', [floor(1.5*sz) 4*sz 3*sz 3*sz]); 
 end
-svals = [ 0.8 ];
+svals = [ 0.8 1.3 2.1 3.0 ];
 % Storage array
 ml_rocs = zeros(niters, length(svals));
 py_rocs = zeros(niters, length(svals));
@@ -96,13 +96,13 @@ end
 end
 
 for si = 1:length(svals)
-  ml_rocerr = abs(ml_rocs - my_rocs);
-  py_rocerr = abs(py_rocs - my_rocs);
-  ml_p_rerr = abs(ml_p_rs - my_p_rs);
-  py_p_rerr = abs(py_p_rs - my_p_rs);
-  mlpy_rocerr = abs(ml_rocs - py_rocs);
-  mlpy_p_rerr = abs(ml_p_rs - py_p_rs);
-  fprintf('Errs for mine vs x (s=%.04f)\n',svals(si))
+  ml_rocerr = abs(ml_rocs(:,si) - my_rocs(:,si));
+  py_rocerr = abs(py_rocs(:,si) - my_rocs(:,si));
+  ml_p_rerr = abs(ml_p_rs(:,si) - my_p_rs(:,si));
+  py_p_rerr = abs(py_p_rs(:,si) - my_p_rs(:,si));
+  mlpy_rocerr = abs(ml_rocs(:,si) - py_rocs(:,si));
+  mlpy_p_rerr = abs(ml_p_rs(:,si) - py_p_rs(:,si));
+  fprintf('\nErrs for mine vs x (s=%.04f)\n',svals(si))
   fprintf('  Mine-MATLAB: ROC: %.6e +/- %.06e, P-R: %.6e +/- %.06e\n', ...
           mean(ml_rocerr), std(ml_rocerr), mean(ml_p_rerr), std(ml_p_rerr));
   fprintf('  Mine-Python: ROC: %.6e +/- %.06e, P-R: %.6e +/- %.06e\n', ...
@@ -130,7 +130,7 @@ function [fpr, tpr, prec, reca, roc, p_r] = run_python(y_true, y_pred)
 writeNPY(y_true, '/tmp/mymatlab/y_true.npy')
 writeNPY(y_pred, '/tmp/mymatlab/y_pred.npy')
 % Get python version
-[status,cmdout] = system('python3 test.py /tmp/mymatlab');
[…]

### 2019-03-21 latex/iccv2019/main.tex
Fixed up latex folder to remove autogen files

@@
 %%%%%%%%% TITLE
-\title{Learning Geometric and Cycle-Consistent Representations with Graph Convolutional Networks}
+\title{All Graphs Lead to Rome: Learning Geometric and Cycle-Consistent Representations with Graph Networks}
 
@@
     Image feature matching is a fundamental part of many geometric computer vision applications, and using multiple images can improve performance.
-    In this work, we formulate multi-image matching as a graph embedding problem then use a Graph Convolutional Network to learn an appropriate embedding function for aligning image features.
+    In this work, we formulate multi-image matching as a graph embedding problem then use a Graph Neural Networks to learn an appropriate embedding function for aligning image features.
     We use cycle consistency to train our network in an unsupervised fashion, since ground truth correspondence is difficult or expensive to aquire.
@@
 However RANSAC-based approaches are limited to matching pairs of images, which can lead to global inconsistencies in the matching.
+% TODO: Mention trifocal tensors
 Other works, such as Wang et al.~\cite{wang2017multi}, have shown improvement in performance by optimizing cycle consistency, i.e.
@@
     An illustration of the approach of this work.
-    The Graph Convolutional Neural Network (GCN) \cite{kipf2016semi} takes as input the graph of matches and then outputs a low rank embedding of the adjacency matrix of the graph.
-    The GCN operates on an embedding over the nodes of the graph.
-    In the figure, the GCN node embeddings are represented by different colors.
+    The Graph Neural Neural Network (GNN) \cite{battaglia2018relational} takes as input the graph of matches and then outputs a low rank embedding of the adjacency matrix of the graph.
+    The GNN operates on an embedding over the vertices of the graph.
+    In the figure, the GNN vertex embeddings are represented by different colors.
     The final embedding is used to construct a pairwise similarity matrix, which we train to be a low dimensional cycle-consistent representation of the graph adjacency matrix, thus pruning the erroneous matches.
@@
 
-In this work, we propose to solve these problems using a Graph Convolutional Network (GCN) to operate on the correspondence graph.
+In this work, we propose to solve these problems using a Graph Neural Networks (GNNs) to operate on the correspondence graph.
 The proposed method works directly on the correspondence graph, which is agnostic to how the correspondences were computed, thus allowing the algorithm to work in a broad class of environments.
@@
 \begin{itemize}
-\item We use a novel architecture to address the multi-image feature matching problem using GCNs with graph embeddings.
+\item We use a novel architecture to address the multi-image feature matching problem using GNNs with graph embeddings.
 \item We introduce an unsupervised cycle consistency loss that does not require labeled correspondences to train.
@@
 \subsection{Graph Neural Networks}
-Graph neural networks have recieved more attention recently \cite{bronstein2017geometric, bruna2013spectral, defferrard2016convolutional, kipf2016semi, scarselli2009graph, gama2018mimo, gama2018convolutional, battaglia2018relational}.
+Graph neural networks have recieved more attention recently \cite{bronstein2017geometric, bruna2013spectral, defferrard2016convolutional, kipf2017semi, scarselli2009graph, gama2018mimo, gama2018convolutional, battaglia2018relational}.
 Classical so-called Spectral methods used the eigenvectors of the graph Laplacian to compute convolutions as in Bruna et al.~\cite{bruna2013spectral}, but requires an a-priori known graph structure. 
-Non-spectral methods do not require a-priori knowledge \cite{bronstein2017geometric, kipf2016semi, scarselli2009graph, gama2018convolutional}.
+Non-spectral methods do not require a-priori knowledge \cite{bronstein2017geometric, kipf2017semi, scarselli2009graph, gama2018convolutional}.
 Most of these methods use polynomials of the graph Laplacian to compute neighborhood averages.
@@
 Vectors $\mat{x}$ and matrices $\mat{A}$ are denoted with boldface, and the $i^{th}$ row of a matrix is denoted $(\mat{A})_i$.
+Graphs $\mathcal{G} = (\mathcal{V}, \mathcal{E})$ have a set of vertices $\mathcal{V}$ and of edges $\mathcal{E} \subseteq \mathcal{V} \times \mathcal{V}$.
+Implicitly in the subsequent discussions we assume the edges are directed.
+For a vertex $v \in \mathcal{V}$ we use $\mathcal{N}^{h}(v)$ to denote the $h$-hop neighbors of $v$, with the superscript left out for 1-hop neighbors.
+Similarly $\mathcal{E}(v)$ is used to denote the edges associated with $v$.
+To denote the vertices connected to an edge $e \in \mathcal{E}$ we write $e(v_1, v_2)$.
 \subsection{Correspondence Graph}
 We assume there is an initial set of feature matches represented as a graph $\mathcal{G} = (\mathcal{V}, \mathcal{E})$.
-Each vertex $v$ of the graph is a feature with its associated descriptor $f_v$. 
-The graph is represented by its Weighted Adjacency Matrix $\mat{A}(\mathcal{G}) \in \bR^{n \times n}$, where $(\mat{A}(\mathcal{G}))_{ij}$ is the strength of the match between nodes $i$ and $j$.
-We introduce the positive diagonal degree matrix $\mat{D}(\mathcal{G}) \in \bR^{n \times n}$, with $\mat{D}(\mathcal{G})_{ii} = \sum_j (\mat{A}(\mathcal{G}))_{ij}$.
-For brevity we denote these matrices $\mat{A}$ and $\mat{D}$ respectively.
-We introduce the notion of an embedding matrix $\mat{E}_0$ by concatenating the features $f_v$ from each of the vertices.
-We use $\mat{E}_0$ as the initialization for our learning algorithm.
-We add any additional knowledge we have into the embedding as well (e.g. scale, orientation, etc.).
-Putative correspondences are computed from these features and represented by weighted edges in which the weight gives the strength of the match.
+The graph is constructed from putative correspondences of image features across images, typically constructed using feature descriptor distance (e.g. SIFT feature distance).
 While there are many interesting methods for computing these putative correspondences \cite{suh2015subgraph, yi2018learning}, we do not explore them in this work.
-
-In the absence of noise or outliers, this graph would have a connected component for each visible point in the world.
-These components should be mutually disjoint. 
-In other words each feature would only have edges to other features corresponding to the same point.
-Since features in this case represent unique locations in the scene, no points in the same image would have edges between them.
-In the noisy case we expect this structure to be corrupted and thus we need to prune the erroneous edges.
-
-To compute this matching graph, we do pairwise feature matching between the images, creating putative correspondences for each of the features.
-Typically these putative correspondences are matched probabilistically, meaning a feature in one image matches to many features in another.
+Typically putative correspondences are matched probabilistically, meaning a feature in one image matches to many features in another.
 The ambiguity in the matches could come from repeated structures in the scene, insufficiently informative low-level feature descriptors, or just an error in the matching algorithm.
@@
 
-However, this graph structure does not have a regular grid structure and thus we cannot use standard convolutional nets to learn features for this task.
-Instead we use graph convolutions to learn feature representations on this space.
-We describe our approach in the next section.
+Each vertex of the graph $v \in \mathcal{V}$ is an image feature, corresponding to some ground truth 3D point $\mat{P}(v)$.
+Each edge $e = (v_1, v_2) \in \mathcal{E}$ is a potential correspondence.
+Associated with each vertex $v$ is an embedding $\mat{f}_v \in \bR^{m_0}$, which can include the visual feature descriptor, position, scale, orientation, etc.
+Similarly, each edge $e$ has an associated feature $\mat{f}_e \in \bR^{p_0}$ (in this work, initially just the weight of the feature association).
+We use these features as the initialization for our learning algorithm.
+
+In the absence of noise or outliers, this graph would have a connected component for each visible point in the world, all mutually disjoint.
+Without noise, vertices $v$ would only match with other vertices $v'$ that correspond to the same 3D point in the scene.
+Since features in this case represent unique locations in the scene, no points in the same image would have edges $e$ between them.
+Mathematically, this can be expressed as $e = (v_1, v_2) \in \mathcal{E} \implies \mat{P}(v_1) = \mat{P}(v_2)$.
+In the noisy case we expect this structure to be corrupted, i.e. there are some edges $e = (v_1, v_2) \in \mathcal{E}$ such that $\mat{P}(v_1) \neq \mat{P}(v_2)$.
+Thus we need to prune the erroneous edges.
+
+However, standard CNNs cannot operate on this general graph structure.
+Thus we cannot use standard convolutional nets to learn features for this task.
+Instead we use graph networks to learn feature representations on this space, which we describe in the next section.
 
 \subsection{Graph Neural Networks}
-As input to our method we are given the graph Laplacian $\mat{L} \in \bR^{n \times n}$ to encode the graph structure:
-\begin{equation}
-  \mat{L} =\; \mat{I} - \mat{D}^{-1/2} \mat{A} \mat{D}^{-1/2} \\
-\end{equation}
-and an initial embedding $\mat{E}_0 \in \bR^{n \times m_0}$.
-Many older methods assume $\mat{L}$ is known a-priori \cite{bruna2013spectral}, and can encode graph convolutions using the eigenvectors of $L$.
-We do not have this luxury, as the correspondence structure changes from image to image, and thus we use non-spectral Graph Neural Networks.
-The standard form of non-spectral Graph Neural Networks is:
-\begin{equation}
-\mat{E}_{i+1} =\; P\left(\sigma\left( \sum_k \mat{L}^k \mat{E}_i \mat{W}_{i,k} \right)\right)
-\end{equation}
-Here $\sigma$ is the non-linearity (typically a ReLU), $\mat{W}_{k,i}$ are the learned weights of layer $i$,  and $P$ is the `pooling' operation, known as graph coarsening \cite{bronstein2017geometric, gama2018mimo}.
-The maximum degree of $\mat{L}$ determines the number of hops away from a node one layer can access.
-In the feature matching problem, we require an embedding for each vertex.
-Therefore we cannot perform graph coarsening, and thus only perform the non-linearity step.
-This work uses Graph Convolutional Networks, proposed in Kipf and Welling \cite{kipf2016semi}:
+As input to our method we are given a graph $\mathcal{G} = (\mathcal{V}, \mathcal{E})$ with the features described last section $\mat{f}_v \forall v \in \mathcal{V}$ and $\mat{f}_e \forall e in \mathcal{E}$.
+As with any neural network, GNNs have layered outputs.
+We describe the output of layer $k$ as $\mat{f}_v^{(k)} \forall v \in \mathcal{V}$ and $\mat{f}_e^{(k)} \forall e in \mathcal{E}$, with the initial embeddings denoted $\mat{f}_v^{(0)} = \mat{f}_v^{(0)}$ and $\mat{f}_e^{(0)} = \mat{f}_e$.
+
+First we describe older methods of GNNs to give context, then we describe the method we use in this work.
+Many older methods assume we have the adjacency matrix $\mat{A}$ of the graph known a-priori \cite{bruna2013spectral}, and can encode graph convolutions using the eigenvectors of $\mat{A}$.
+However, we do not have this luxury, as the correspondence structure changes from image set to image set, and thus we use non-spectral Graph Neural Networks.
+There are many variations on non-spectral methods, often which ultimately amount to message passing between vertices of the graph with learned non-linear transformations between various steps \cite{kipf2017semi, defferrard2016convolutional, gama2018mimo, gama2018convolutional}.
+Some works such as \cite{gama2019convolutional} use pooling operations on the vertices to make the graph smaller and thus aid computation, but as we need labels on every vertex of the original graph, so we cannot use this.
+Most of GNNs used in these works can be expressed mathematically as:
+\begin{align*}
+\mat{\tilde{f}}_v^{(k+1)} =&\; b^{(k)} + \mat{W}_0^{k} \mat{f}_{v}^{(k)} + \sum_{h=0}^H \sum_{v' \in \mathcal{N}^{h}(v)} f_{e(v,v')} \mat{W}_{h}^{k} \mat{f}_{v'}^{(k)} \\
+\mat{f}_v^{(k+1)} =&\; \sigma\left(\mat{\tilde{f}}_v^{(k+1)}\right)
+\end{align*}
+The weights/biases $\mat{W}_{h}^{k}$, $b^{(k)}$ are all learned, with no learning done on the edge weights $f_{e(v,v')}$. 
+Note that this is just sums or averages over $h$-hop neighborhoods, where the weights on the edges remain static through the computation.
+Given that we are trying to prune edges, it would be sensible to add features over edges to learn which ones to prune and which to keep such as in \cite{scarselli2009graph}.
+
+Therefore, in this work we use the method and implementation described in \cite{battaglia2018relational} (more specifically repetitions of the architecture described in \cite{battaglia2016interaction}).
+This work is similar to previous works with one key difference: edges also have weights.
+Thus therefore there is intermediate processing on the edges before information is passed to the vertices.
+
+Mathematically, this is expressed as: % TODO: Maybe make this MLP oriented?
 \begin{align}
-      \widetilde{\mat{L}} =&\; (\mat{D} + \mat{I})^{-1/2} (\mat{A} + \mat{I}) (\mat{D} + \mat{I})^{-1/2} \\
-\mat{E}_{l+1} =&\; \sigma\left(\widetilde{\mat{L}} \mat{E}_i \mat{W}_i \right)  \label{eq:graph_conv}
+\mat{\tilde{f}}_{e(v_1,v_2)}^{(k+1)} =&\; \mat{U}_1^{(k)} \mat{f}_{e}^{(k)} + \mat{U}_1^{(k)} \mat{f}_{v_1}^{(k)} + \mat{U}_2^{(k)} \mat{f}_{v_2}^{(k)} \\
+\mat{f}_{e(v_1,v_2)}^{(k+1)} =&\; \sigma \left(a^{(k)} + \mat{\tilde{f}}_{e(v_1,v_2)}^{(k+1)}\right) \\
+\mat{\tilde{f}}_{v}^{(k+1)} =&\; \mat{W}_0^{(k)} \mat{f}_{v}^{(k)} + \sum_{e \in \mathcal{E}(v)} \mat{W}_1^{(k)} \mat{f}_{e}^{(k+1)} \\
+\mat{f}_v^{(k+1)} =&\; \sigma\left(b^{(k)} + \mat{\tilde{f}}_v^{(k+1)}\right)
 \end{align}
-
-The matrix $\widetilde{\mat{L}}$ is analogous to the graph Laplacian (with better numerical stability properties).
-$\widetilde{\mat{L}}$ encodes the structure of the graph and is used to perform the actual graph convolution.
-Our network has many layers, and thus the receptive field of the final embedding is quite large, even without the pooling operations.
-In principle we could use higher hop neighborhoods \cite{gama2018convolutional}, or more complicated aggregation structures \cite{battaglia2018relational}, but in this work we restrict ourselves to simpler architectures, and still obtain promising results for this task.
-For faster training, we use group normalization \cite{wu2018group} and skip connections.
-The final output $\mat{E}_n$ gives us a new descriptor for every node.
-In the next sections we will discuss the loss functions to train this network.
+Here the learned weights are denoted $\mat{W}$ and $\mat{U}$, and the biases $a^{(k)}$ and  $b^{(k)}$.
+In \cite{battaglia2018relational}, they allow for more sophisticated aggregation functions, but in this work we simply use the mean function.
+In practice, we use MLPs between message passes between the vertices and edges for better expressiveness.
 
@@
 Spectral                                                  & 0.054 $\pm$ 0.005                   & 0.018 $\pm$ 0.004                   & 0.018 $\pm$ 0.004                   \\ \hline 
-\textbf{GCN, 12 Layers (ours)}                            & \textbf{0.025} $\pm$ \textbf{0.003} & \textbf{0.016} $\pm$ \textbf{0.003} & \textbf{0.039} $\pm$ \textbf{0.009} \\
+\textbf{GNN, 12 Layers (ours)}                            & \textbf{0.025} $\pm$ \textbf{0.003} & \textbf{0.016} $\pm$ \textbf{0.003} & \textbf{0.039} $\pm$ \textbf{0.009} \\
 \hline\hline
@@
 Spectral Method                                                          & 0.055 $\pm$ 0.004                   & 0.017 $\pm$ 0.003                   & 0.028 $\pm$ 0.003                   \\ \hline
-\textbf{GCN, 12 Layers (ours)}                                           & \textbf{0.023} $\pm$ \textbf{0.003} & \textbf{0.015} $\pm$ \textbf{0.002} & \textbf{0.056} $\pm$ \textbf{0.017} \\ \hline
+\textbf{GNN, 12 Layers (ours)}                                           & \textbf{0.023} $\pm$ \textbf{0.003} & \textbf{0.015} $\pm$ \textbf{0.002} & \textbf{0.056} $\pm$ \textbf{0.017} \\ \hline
 \end{tabular}
@@
 The normalized noisy input descriptors are our baseline - they correlate with the true values but do not preserve the structure well.
-However, the GCN recovered the true structure very well, as shown in Table \ref{fig:synthtable}.
-All experiments were run with a 12 layer GCN with the ReLU nonlinearity and skip connections.
+However, the GNN recovered the true structure very well, as shown in Table \ref{fig:synthtable}.
+All experiments were run with a 12 layer GNN with the ReLU nonlinearity and skip connections.
 All were trained with the Adam optimizer \cite{kingma2014adam} and a learning rate $10^{-4}$
@@
 
-We have shown a novel method for training feature matching using GCNs, using an unsupervised cycle consistency loss and geometric consistency losses.
-We have demonstrated its effectiveness on the Rome16K dataset compared to the traditional optimization based baselines on a simple GCN.
+We have shown a novel method for training feature matching using GNNs, using an unsupervised cycle consistency loss and geometric consistency losses.
+We have demonstrated its effectiveness on the Rome16K dataset compared to the traditional optimization based baselines on a simple GNN.
 For future work, we will investigate robust losses for better outlier rejection, and using higher order geometric constraints, such as the tri-focal tensor, as additional loss terms.

### 2019-03-24 latex/iccv2019/main.tex
Final ICCV Submission (much last minute scramble)

@@
     Image feature matching is a fundamental part of many geometric computer vision applications, and using multiple images can improve performance.
-    In this work, we formulate multi-image matching as a graph embedding problem then use a Graph Neural Networks to learn an appropriate embedding function for aligning image features.
-    We use cycle consistency to train our network in an unsupervised fashion, since ground truth correspondence is difficult or expensive to aquire.
-    In addition, geometric consistency losses can be added at training time, even if the information is not available in the test set, unlike previous approaches that optimize cycle consistency directly.
+    In this work, we formulate multi-image matching as a graph embedding problem then use a Graph Neural Network to learn an appropriate embedding function for aligning image features.
+    We use cycle consistency to train our network in an unsupervised fashion, since ground truth correspondence is difficult or expensive to acquire.
+    In addition, geometric consistency losses can be added at training time, even if the information is not available in the test set, unlike previous approaches which optimize cycle consistency directly.
     To the best of our knowledge, no other works have used learning for multi-image feature matching.
@@
 However, these multi-view consistency algorithms struggle in distributed and robust settings.
-Deep learning has revolutionized how image features are computed \cite{yi2016lift}.
+Having image features suited for this task would help improve performance, and deep learning has revolutionized how image features are computed \cite{yi2016lift}.
 In this paper, we want to leverage the power of deep representations in order to compute feature descriptors that are robust across multiple views.
@@
   % \fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-  \includegraphics[width=0.8\linewidth]{figures-CycleConsistencyMainFigure-v2.pdf}
+  \includegraphics[width=0.8\linewidth]{figures-CycleConsistencyMainFigure-v4.pdf}
 \end{center}
@@
 Additionally, in the case of multi-image feature matching, geometric constraints would be helpful in rejecting outlier matches.
+Geometric constraints, such as the epipolar constraint, can help disambiguate between visually similar features during training, and help the network learn better features robust to this kind of noise.
 
-In this work, we propose to solve these problems using a Graph Neural Networks (GNNs) to operate on the correspondence graph.
+In this work, we propose to solve these problems using Graph Neural Networks (GNNs) to operate on the correspondence graph.
 The proposed method works directly on the correspondence graph, which is agnostic to how the correspondences were computed, thus allowing the algorithm to work in a broad class of environments.
@@
 We use an unsupervised loss - the cycle consistency loss - to train the network, and thus avoiding the difficulty of expensive hand labeling.
-% We incorporate geometric consistency losses to guide training, which helps training even when the geometric information is not available at test time.
 Geometric consistency losses can aid training, even if such information is not available at test time.
-Although our network is simple, it shows promising results compared to baselines which optimize for cycle-consistency without learned embeddings.
+Although our network is simple, it shows promising results compared to baselines which optimize for cycle-consistency without learned embeddings, using a matrix factorization loss \cite{zhou2015multi, leonardos2016distributed}.
 Furthermore, since inference requires only a single forward pass over the neural network, our approach is faster (to achieve comparable accuracy) than methods which must solve an optimization problem every time.
-Our contributions are:
+We perform experiments on the Rome16K \cite{li2010location} dataset to test the effectiveness of our method compared to optimization based methods.
+Our contributions in this work are:
 \begin{itemize}
@@
 \item We demonstrate the effectiveness of geometric consistency losses in improving training.
-\item We perform experiments on the Rome16K \cite{li2010location} dataset to test the effectiveness of our method compared to optimization based methods.
 \end{itemize}
@@
 Matching has a rich history of research in computer vision.
-The most well known and widely used method for image matching is RANSAC \cite{fischler1981random}.
-RANSAC, combined with hand-crafted feature descriptors such as SIFT \cite{lowe2004distinctive}, SURF \cite{bay2006surf}, BRIEF \cite{calonder2012brief}, or ORB \cite{mur2015orb}, has constituted the bulk of the matching literature for the last 40 years.
+Much work has be done using hand-crafted feature descriptors such as SIFT \cite{lowe2004distinctive}, SURF \cite{bay2006surf}, BRIEF \cite{calonder2012brief}, or ORB \cite{mur2015orb}.
+RANSAC \cite{fischler1981random} is the most widely used robust estimation technique to filter out outliers from the matches.
+The combination of RANSAC and hand-crafted feature descriptors has constituted the bulk of the matching literature for the last 40 years.
 Finally, graph matching \cite{suh2015subgraph, hu2016distributable} can be used as a final step for more robust matches.
@@
 However, they only focus on two view matching and do not exploit the advantages of the correspondence structure.
-Note that while Zhu et al.~\cite{zhu2017unpaired} use cycle consistency in their loss, their method is restricted to pairwise cycle consistency, while we use multi-image cycle consistency.
+Note that while Zhu et al.~\cite{zhu2017unpaired} use cycle consistency in their loss, their method is restricted to pairwise cycle consistency (i.e.
+enforcing consistency by going back and forth between two images).
+We use multi-image cycle consistency, which require consistency between 3 or more images.
 
@@
 Our goal is to learn optimal features that capture multiple image views by filtering out noisy feature matches.
+An outline of our approach can be seen in figure \ref{fig:pipeline}.
 The input to our algorithm is a set of features and noisy correspondences, and the output is a new set of features where the pairwise similarities of these features correspond to the true matches.
@@
 \subsection{Correspondence Graph}
-We assume there is an initial set of feature matches represented as a graph $\mathcal{G} = (\mathcal{V}, \mathcal{E})$.
+We assume there is an initial set of feature matches represented as a graph $\mathcal{G} = (\mathcal{V}, \mathcal{E})$, with an associated adjacency matrix $\mat{A}$.
 The graph is constructed from putative correspondences of image features across images, typically constructed using feature descriptor distance (e.g. SIFT feature distance).
@@
 Each edge $e = (v_1, v_2) \in \mathcal{E}$ is a potential correspondence.
-Associated with each vertex $v$ is an embedding $\mat{f}_v \in \bR^{m_0}$, which can include the visual feature descriptor, position, scale, orientation, etc.
-Similarly, each edge $e$ has an associated feature $\mat{f}_e \in \bR^{p_0}$ (in this work, initially just the weight of the feature association).
+Associated with each vertex $v$ is an embedding $\mat{f}_v \in \bR^m$, which can include the visual feature descriptor, position, scale, orientation, etc.
+Similarly, each edge $e$ has an associated feature $\mat{f}_e \in \bR^p$ (in this work, initially just the weight of the feature association).
 We use these features as the initialization for our learning algorithm.
@@
 \subsection{Graph Neural Networks}
-As input to our method we are given a graph $\mathcal{G} = (\mathcal{V}, \mathcal{E})$ with the features described last section $\mat{f}_v \forall v \in \mathcal{V}$ and $\mat{f}_e \forall e in \mathcal{E}$.
+As input to our method we are given a graph $\mathcal{G} = (\mathcal{V}, \mathcal{E})$ with the features described last section $\mat{f}_v \forall v \in \mathcal{V}$ and $\mat{f}_e \forall e \in \mathcal{E}$.
 As with any neural network, GNNs have layered outputs.
-We describe the output of layer $k$ as $\mat{f}_v^{(k)} \forall v \in \mathcal{V}$ and $\mat{f}_e^{(k)} \forall e in \mathcal{E}$, with the initial embeddings denoted $\mat{f}_v^{(0)} = \mat{f}_v^{(0)}$ and $\mat{f}_e^{(0)} = \mat{f}_e$.
+We describe the output of layer $k$ as $\mat{f}_v^{(k)} \in \bR^{m_k}\, \forall v \in \mathcal{V}$ and $\mat{f}_e^{(k)} \in \bR^{p_k}\, \forall e \in \mathcal{E}$, with the initial embeddings denoted $\mat{f}_v^{(0)} = \mat{f}_v$ and $\mat{f}_e^{(0)} = \mat{f}_e$.
+It will be useful to write these features as matrices in later sections, so we denote the vertex embedding matrix as $\mat{F}_V^{(k)}$ and the edge embedding matrix as $\mat{F}_E^{(k)}$.
+If a superscript is not specified then it refers to the final output of the network.
 
@@
 In \cite{battaglia2018relational}, they allow for more sophisticated aggregation functions, but in this work we simply use the mean function.
-In practice, we use MLPs between message passes between the vertices and edges for better expressiveness.
+In practice, we use MLPs in message passes between vertices and edges for better expressiveness
 
@@
 A more elegant way to represent cycle consistency is to first create a `universe' of features that all images match to (see figure \ref{fig:universefeatures}).
-Then, one can match the $i^{th}$ set of features to the universe using a matrix $\mat{X}_i$.
-Then the cycle consistency becomes:
+Then, one can match the $i^{th}$ set of features to the universe using a ground-truth matching matrix $\mat{X}_i$.
+Then the cycle consistency constraint becomes:
 \begin{equation}
@@
 
-This reduces our complexity from $O(n^3)$ to $O(n^2)$.
-We try to learn $\mat{E}$ to approximate $\mat{X}$ - in other words the final embedding should be an encoding of the universe of features.
-As we do not have the ground truth matches $\mat{M}$, we approximate it using the noisy adjacency matrix $\mat{A}$ of our correspondence graph.
-Thus our loss would be
+This reduces the number of our constraints from $O(n^3)$ to $O(n^2)$.
+We try to learn vertex embeddings $\mat{F}_V$ to approximate $\mat{X}$ - in other words the final embedding should be an encoding of the universe of features.
+As we do not have the ground truth matches $\mat{M}$, we approximate it using the noisy adjacency matrix $\mat{A}$ of our correspondence graph. Thus our loss would be 
 \begin{equation}
-\mathcal{L}(\mat{A}, \mat{E}_n) = \mathcal{D}(\mat{A}, \mat{E}_n\mat{E}_n^\top)
+\mathcal{L}(\mat{A}, \mat{F}_V) = \mathcal{D}(\mat{A}, \mat{F}_V \mat{F}_V^\top)
 \end{equation}
@@
 The epipolar constraint describes how the positions of features in different images corresponding to the same point should be related.
+An illustration of this is provided in figure \ref{fig:geoconsist}, showing how this loss can help reject erroneous points.
 Given a relative pose $(R_{ij}, T_{ij})$ between two cameras $i$ and $j$  (transforms $j$ to $i$) the epipolar on corresponding feature locations $X_i$ and $X_j$:
@@
 % Where the $(R_k, T_k)$ are the poses of cameras $i$ and $j$ respectively.
-The constraint assumes that the $X_k$ are calibrated i.e. the camera intrinsics are known. 
-Given the matrix of ground truth correspondences $\mat{M}_{ij}$ between camera $i$ and $j$, we can formulate this as a loss:
-\begin{equation}
-\mathcal{L}_{ij,geom}(\mat{M}_{ij}) = \sum_{k,l} (\mat{M}_{ij})_{kl} \left|X_{i,k}^\top R_{i}^\top \cross{T_{j} - T_{i}}R_{j} X_{j,l}\right|
+The constraint assumes that the $X_k$ are calibrated (i.e. the camera intrinsics are known). 
+Given our vertex embeddings matrix $\mat{F}_V$, we can formulate a loss between all cameras $i$ and $j$:
+\begin{align}
+&\mathcal{L}_{ij,geom}(\mat{F}_V) = \nonumber \\ 
+&\sum_{v \in \mathcal{V}(i),u \in \mathcal{V}(j)} \sum_{} (\mat{f}_v \cdot \mat{f}_u) \left|X_{v}^\top R_{i}^\top \cross{T_{j} - T_{i}}R_{c_j} X_{u}\right|
 \label{eq:geom_cost}
-\end{equation}
+\end{align}
+With $\mathcal{V}(i)$ being the vertices associated with camera $i$.
 For our purposes, since we use low rank embeddings $\mat{E}_{i}$, $\mat{E}_{j}$, the loss would read:
 \begin{align} 
-\mathcal{L}_{geom}(\mat{E})
-=&\; \mathrm{tr}(\mat{G}^\top \mat{E}\mat{E}^\top) = \sum_{i,j} (\mat{E})_{i} \cdot (\mat{E})_{j} (\mat{G})_{ij} \\
-(\mat{G})_{ij} =&\; \left|X_{i}^\top R_{c(i)}^\top \cross{T_{c(j)} - T_{c(i)}}R_{c(j)} X_{j}\right| \nonumber
-\label{eq:geom_cost2}
+\mathcal{L}_{geom}(\mat{F}_V)
+=&\; \mathrm{tr}(\mat{G}^\top \mat{F}_V\mat{F}_V^\top) = \sum_{k,l} (\mat{F}_V)_{k} \cdot (\mat{F}_V)_{l} (\mat{G})_{kl} \label{eq:geom_cost2} \\
+(\mat{G})_{kl} =&\; \left|X_{k}^\top R_{c(k)}^\top \cross{T_{c(l)} - T_{c(k)}}R_{c(l)} X_{l}\right| \nonumber
 \end{align}
-Where $c(i)$ is the appropriate camera for point index $i$.
+Where $c(k)$ is the appropriate camera for point index $k$.
 
@@
 \begin{center}
-\begin{tabular}{|l|c|c|c|}
+\begin{tabular}{|l|c|c|c|c|}
 \hline
-Method (3 Views)                                          & $L_1$ Loss                          & $L_2$ Loss                          & Run Time (sec)                      \\
+Method (6 Views)                                     & $L_1$             & $L_2$             & Area under ROC    & Time (sec)        \\
 \hline\hline
-MatchALS \cite{zhou2015multi} 15 Iterations               & 0.052 $\pm$ 0.003                   & 0.010 $\pm$ 0.002                   & 0.021 $\pm$ 0.003                   \\
-MatchALS \cite{zhou2015multi} 25 Iterations               & 0.045 $\pm$ 0.007                   & 0.009 $\pm$ 0.003                   & 0.034 $\pm$ 0.003                   \\
-MatchALS \cite{zhou2015multi} 50 Iterations               & 0.016 $\pm$ 0.008                   & 0.007 $\pm$ 0.003                   & 0.065 $\pm$ 0.006                   \\ \hline
-PGDDS \cite{leonardos2016distributed} 15 Iterations       & 0.016 $\pm$ 0.002                   & 0.006 $\pm$ 0.002                   & 0.287 $\pm$ 0.043                   \\
-PGDDS \cite{leonardos2016distributed} 25 Iterations       & 0.014 $\pm$ 0.002                   & 0.005 $\pm$ 0.002                   & 0.613 $\pm$ 0.089                   \\
-PGDDS \cite{leonardos2016distributed} 50 Iterations       & 0.013 $\pm$ 0.002                   & 0.005 $\pm$ 0.002                   & 1.430 $\pm$ 0.234                   \\ \hline
-Spectral                                                  & 0.054 $\pm$ 0.005                   & 0.018 $\pm$ 0.004                   & 0.018 $\pm$ 0.004                   \\ \hline 
-\textbf{GNN, 12 Layers (ours)}                            & \textbf{0.025} $\pm$ \textbf{0.003} & \textbf{0.016} $\pm$ \textbf{0.003} & \textbf{0.039} $\pm$ \textbf{0.009} \\
+MatchALS \cite{zhou2015multi} 15 Iterations          & 0.101 $\pm$ 0.008 & 0.022 $\pm$ 0.004 & 0.918 $\pm$ 0.073 & 0.074 $\pm$ 0.008 \\ \hline
+MatchALS \cite{zhou2015multi} 25 Iterations          & 0.059 $\pm$ 0.010 & 0.012 $\pm$ 0.004 & 0.921 $\pm$ 0.077 & 0.143 $\pm$ 0.064 \\ \hline
+MatchALS \cite{zhou2015multi} 35 Iterations          & 0.046 $\pm$ 0.016 & 0.010 $\pm$ 0.005 & 0.910 $\pm$ 0.072 & 0.139 $\pm$ 0.041 \\ \hline
+MatchALS \cite{zhou2015multi} 50 Iterations          & 0.029 $\pm$ 0.017 & 0.008 $\pm$ 0.005 & 0.905 $\pm$ 0.068 & 0.260 $\pm$ 0.048 \\ \hline
+PGDDS0 \cite{leonardos2016distributed} 15 Iterations & 0.017 $\pm$ 0.002 & 0.007 $\pm$ 0.001 & 0.918 $\pm$ 0.087 & 0.796 $\pm$ 0.147 \\ \hline
+PGDDS0 \cite{leonardos2016distributed} 25 Iterations & 0.016 $\pm$ 0.002 & 0.007 $\pm$ 0.002 & 0.919 $\pm$ 0.087 & 1.670 $\pm$ 0.328 \\ \hline
+PGDDS0 \cite{leonardos2016distributed} 50 Iterations & 0.015 $\pm$ 0.002 & 0.006 $\pm$ 0.002 & 0.920 $\pm$ 0.087 & 3.363 $\pm$ 0.528 \\ \hline
+Spectral \cite{pachauri2013solving}                  & 0.073 $\pm$ 0.006 & 0.027 $\pm$ 0.003 & 0.921 $\pm$ 0.083 & 0.036 $\pm$ 0.005 \\ \hline
+\textbf{GNN (ours)}                                  & 0.044 $\pm$ 0.005 & 0.031 $\pm$ 0.005 & 0.872 $\pm$ 0.081 & 0.765 $\pm$ 0.046 \\ \hline
+
 \hline\hline
-Method (4 Views)                                                         & $L_1$ Loss                          & $L_2$ Loss                          & Run Time (sec)                     \\
+Method (10 Views)                                   & $L_1$             & $L_2$             & Area under ROC    & Time (sec)        \\
 \hline\hline
-MatchALS \cite{zhou2015multi} 15 Iterations                              & 0.064 $\pm$ 0.005                   & 0.012 $\pm$ 0.002                   & 0.030 $\pm$ 0.004                   \\
-MatchALS \cite{zhou2015multi} 25 Iterations                              & 0.041 $\pm$ 0.010                   & 0.008 $\pm$ 0.004                   & 0.048 $\pm$ 0.005                   \\
-MatchALS \cite{zhou2015multi} 50 Iterations                              & 0.011 $\pm$ 0.008                   & 0.005 $\pm$ 0.003                   & 0.094 $\pm$ 0.008                   \\ \hline
-PGDDS \cite{leonardos2016distributed} 15 Iterations                      & 0.015 $\pm$ 0.002                   & 0.006 $\pm$ 0.001                   & 0.436 $\pm$ 0.090                   \\
-PGDDS \cite{leonardos2016distributed} 25 Iterations                      & 0.014 $\pm$ 0.002                   & 0.005 $\pm$ 0.001                   & 0.961 $\pm$ 0.181                   \\
-PGDDS \cite{leonardos2016distributed} 50 Iterations                      & 0.013 $\pm$ 0.002                   & 0.005 $\pm$ 0.002                   & 2.056 $\pm$ 0.424                   \\ \hline
-Spectral Method                                                          & 0.055 $\pm$ 0.004                   & 0.017 $\pm$ 0.003                   & 0.028 $\pm$ 0.003                   \\ \hline
-\textbf{GNN, 12 Layers (ours)}                                           & \textbf{0.023} $\pm$ \textbf{0.003} & \textbf{0.015} $\pm$ \textbf{0.002} & \textbf{0.056} $\pm$ \textbf{0.017} \\ \hline
+MatchALS \cite{zhou2015multi} 15 Iterations         & 0.114 $\pm$ 0.008 & 0.028 $\pm$ 0.004 & 0.915 $\pm$ 0.051 & 0.142 $\pm$ 0.009 \\ \hline
+MatchALS \cite{zhou2015multi} 25 Iterations         & 0.092 $\pm$ 0.008 & 0.019 $\pm$ 0.003 & 0.912 $\pm$ 0.055 & 0.228 $\pm$ 0.014 \\ \hline
+MatchALS \cite{zhou2015multi} 35 Iterations         & 0.065 $\pm$ 0.009 & 0.013 $\pm$ 0.003 & 0.907 $\pm$ 0.053 & 0.355 $\pm$ 0.073 \\ \hline
+MatchALS \cite{zhou2015multi} 50 Iterations         & 0.045 $\pm$ 0.012 & 0.011 $\pm$ 0.004 & 0.914 $\pm$ 0.051 & 0.455 $\pm$ 0.022 \\ \hline
+PGDDS \cite{leonardos2016distributed} 15 Iterations & 0.017 $\pm$ 0.001 & 0.008 $\pm$ 0.001 & 0.903 $\pm$ 0.061 & 1.225 $\pm$ 0.159 \\ \hline
+PGDDS \cite{leonardos2016distributed} 25 Iterations & 0.016 $\pm$ 0.001 & 0.007 $\pm$ 0.001 & 0.904 $\pm$ 0.061 & 2.637 $\pm$ 0.357 \\ \hline
+PGDDS \cite{leonardos2016distributed} 50 Iterations & 0.016 $\pm$ 0.001 & 0.007 $\pm$ 0.001 & 0.905 $\pm$ 0.061 & 6.116 $\pm$ 1.009 \\ \hline
+Spectral \cite{pachauri2013solving}                 & 0.073 $\pm$ 0.005 & 0.029 $\pm$ 0.002 & 0.912 $\pm$ 0.057 & 0.081 $\pm$ 0.021 \\ \hline
+\textbf{GNN (ours)}                                 & 0.053 $\pm$ 0.006 & 0.035 $\pm$ 0.005 & 0.872 $\pm$ 0.061 & 2.438 $\pm$ 0.070 \\ \hline
+
 \end{tabular}
 \end{center}
-% save-rome16kgeom0-normedskip2-loss-l1-geom-10-0 (028249) -> train : +3.1467e-02, test : +3.8864e-02, gt_l1 : +2.6321e-02, gt_l2 : +2.6321e-02
 
@@
 }
+\label{tab:rome16ktab}
 \end{table*}
@@
   % \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
-  \includegraphics[width=0.8\linewidth]{figures-TrainingCurves.pdf}
+  \includegraphics[width=0.8\linewidth]{figures-GeometricLoss.pdf}
   \end{center}
     \caption{
-      Training curves with and without Geometric Training loss.
+      Training curves with and without Geometric Training loss, described in \ref{eq:geom_cost2}.
       The geometric training loss improves testing performance.
-      Shown as horizontal lines are the state of the art optimization based baselines.
-      Even with a simple network we compare well with them.
+      While the training is higher due to the additional loss terms, the ground truth L1 error is substantially better with the Geometric Loss.
     }
   \label{fig:short}
+  \label{fig:geomloss}
 \end{figure*}
 
-\begin{figure*}
-\begin{center}
-  % \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
-  \includegraphics[width=0.8\linewidth]{figures-ExampleOutput.pdf}
-  \end{center}
-     \caption{Example output of our network.
+% \begin{figure*}
+% \begin{center}
+%   % \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
+%   \includegraphics[width=0.8\linewidth]{figures-ExampleOutput.pdf}
+%   \end{center}
+%      \caption{Example output of our network.
 (a) Similarity Matrix of the of the embeddings (b) Histogram of feature similarities for pairs which correspond to the same 3D point, comparing our output features with the original SIFT features (c) Histogram of feature similarities for pairs which correspond to different 3D points, comparing our output features with the original SIFT features}
-  \label{fig:short}
-\end{figure*}
+%   \label{fig:short}
+% \end{figure*}
 \subsection{Synthetic Graph Dataset}
 We first test our method on synthetically generated data as a simple proof of concept.
+As these were simpler datasets, we the simpler edge-feature free model of \cite{kipf2017semi}.
 To generate the data, we generate $p$ points, each with its own randomly generated descriptor.
@@
 All experiments were run with a 12 layer GNN with the ReLU nonlinearity and skip connections.
+The feature vector lengths were 32, 64, 128, 256, 512, 512, 512, 512, 512, 512, 1024, 1024, with skip connections between layers 1 and 6, 6 and 12, and 1 and 12.
 All were trained with the Adam optimizer \cite{kingma2014adam} and a learning rate $10^{-4}$
+The network was implemented in Tensorflow \cite{tensorflow2015}, version 1.11.
+With this simple test on synthetic data passed, we now move to more challenging datasets.
+
+\begin{figure*}[t]
+\begin{center}
+  % \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
+  \includegraphics[width=0.7\linewidth]{figures-error_lines.pdf}
+  \end{center}
+     \caption{
+         Plot of the losses of the baselines at different iteration numbers.
+         The line shows the mean of the graph while the translucent coloring shows the $25^{th}$ to $75^{th}$ percentiles.
+         The ROC AUC curves remain fairly consistent while the L1 loss goes noticibly down after more iterations.
+         Our method compares to 35-45 iterations of MatchALS, while only having 16 layers and 8 message passes.
+         PGDDS performs better than us in $L_1$ but we perform similarly in the ROC AUC metric.
+     }
+  % \label{fig:twocol}
+  \label{fig:errorlines}
+\end{figure*}
 
@@
 For the initial embedding we use the original 128 dimensional SIFT descriptors, normalized to have unit $L_2$ norm, the calibrated x-y position, the orientation, and log scale of the SIFT feature.
-% For the outlier datasets, we take 79 correspondences and 1 non-corresponding point in each image.
+To construct the graph, we take each feature as a vertex and create an edge between the 5 nearest features in each other image in SIFT descriptor space.
 
@@
 We evaluate on a test set using the ground truth adjacency matrix, which we compute from the bundle adjustment given by the Rome16K dataset.
-Traditional methods of evaluation use Precision and Recall, after making the labels 0 or 1.
-We forgo this as our method was trained to output soft labels - we in turn make the labels soft for the optimization based methods.
+However, we do not train with the ground truth adjacency matrix, only with the noisy adjacency matrix from the graph.
+We also add the geometric loss (\ref{eq:geom_cost2}) which helps improve testing performance (see figure \ref{fig:geomloss})
+We use the $L_1$ and ROC AUC metrics to measure performance.
 For this method to work, we need the dimension of the embedding to be at least the number of unique points in the scene.
@@
 Here we use the ground truth dimension of the embedding to test both our method and the baselines.
-For implementation details, our network has 12 layers, and was trained with the Adam optimizer \cite{kingma2014adam} with a learning rate of $10^{-4}$, with an exponentially decaying learning rate.
-We incorporate skip connections between the input, $6^{th}$, and $12^{th}$ layers, which greatly improved training convergence and testing performance (see supplemental material).
 
+The network was implemented using the code provided by \cite{battaglia2018relational} using Tensorflow \cite{tensorflow2015} 1.11.
+Our network has 16 layers, with 8 message passing operations placed every other layer.
+All layers were simple Multi-layer Perceptrons, with no batch norm.
+The network was trained with the Adam optimizer \cite{kingma2014adam} with a learning rate of $10^{-4}$, with an exponentially decaying learning rate.
+We incorporate skip connections between the input, $6^{th}$, and $12^{th}$ layers (all possible pairs).
+
+% Our method performs better than nearly 
 We compare our method to spectral and optimization based baselines with different maximum iteration cutoffs.
-Our method is signification better than a simple spectral based optimization.
-% Furthermore, our network, which only has 12 layers has the accuracy of the optimization based method MatchALS \cite{zhou2015multi} inbetween 25 and 50 iterations.
-Our network, though only 12 layers, has comparable accuracy to MatchALS \cite{zhou2015multi} run between 25 and 50 iterations.
-% This indicates that our method learns a more efficient update with each layer compared with an iteration in the optimization based methods.
-Although our method does not outperform the Projected Gradient Descent - Doubly Stochastic (PGDDS) \cite{leonardos2016distributed} method, we have significantly better run time.
-Additional comparisons to different iterations numbers of iterations can be found in the supplementary material.
+Figure \ref{fig:errorlines} illustrates this by plotting the means of various metrics and their $25^{th}$ and $75^{th}$ percentiles, with table \ref{tab:rome16ktab} giving the exact numbers.
+Our network, though only using 8 message passes, has comparable accuracy to MatchALS \cite{zhou2015multi} run 35 to 45 iterations, with an equivalent message passing step at each phase.
+Although our method does not outperform the Projected Gradient Descent - Doubly Stochastic (PGDDS) \cite{leonardos2016distributed} method, we perform comparably to them in the ROC AUC metric.
+% Our network, though only 12 layers, has comparable accuracy to MatchALS \cite{zhou2015multi} run between 25 and 50 iterations.
+% Additional comparisons to different iterations numbers of iterations can be found in the supplementary material.
 
@@
   % \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
-  \includegraphics[width=0.8\linewidth]{figures-EmbeddingsViz.png}
+  \includegraphics[width=0.7\linewidth]{figures-EmbeddingsViz.png}
   \end{center}
      \caption{
-         Visualization of the learned embeddings using Hinton diagrams \cite{bremner1994hinton}.
+         Visualization of the learned embeddings.
          On the left we have the raw outputs, which are difficult to interpret.
-         On the right, we rotated the features to best match the ground truth for a more interpretable visualization.
+         In the center, we rotated the features to best match the ground truth for a more interpretable visualization.
+         On the right, we have the ground truth embeddings, given as indicator vectors for which feature in the world the points correspond to.
      }
@@
 We have shown a novel method for training feature matching using GNNs, using an unsupervised cycle consistency loss and geometric consistency losses.
-We have demonstrated its effectiveness on the Rome16K dataset compared to the traditional optimization based baselines on a simple GNN.
+We have demonstrated has comparable the traditional optimization based baselines on a simple GNN, while still allowing for end-to-end training integration in deep learning pipelines.
 For future work, we will investigate robust losses for better outlier rejection, and using higher order geometric constraints, such as the tri-focal tensor, as additional loss terms.
-A long term goal is to incorporate learning image level features into this pipeline.
-Moreover we hope to adapt this method to a distributed setting, which would be a simple extention given current approach.
-% , but with group norm, we cannot distribute in its current form.
+% A long term goal is to incorporate learning image level features into this pipeline.
+% Moreover we hope to adapt this method to a distributed setting, which would be a simple extention given current approach.
+With this new architecture, we have the capability of training multi-image matching pipelines end to end, thus allowing us to train for image features explicitly for this task.
+We can also extend this to distributed settings where we can train for matching images from multiple distributed agents.
 
@@
 \end{document}
+
+% Method (6 Views)                                     & $L_1$             & $L_2$             & Area under ROC    & Area Prec.-Recall & Time (sec)        \ \hline
+% MatchALS \cite{zhou2015multi} 15 Iterations          & 0.101 $\pm$ 0.008 & 0.022 $\pm$ 0.004 & 0.918 $\pm$ 0.073 & 0.752 $\pm$ 0.160 & 0.074 $\pm$ 0.008 \\ \hline
+% MatchALS \cite{zhou2015multi} 25 Iterations          & 0.059 $\pm$ 0.010 & 0.012 $\pm$ 0.004 & 0.921 $\pm$ 0.077 & 0.767 $\pm$ 0.181 & 0.143 $\pm$ 0.064 \\ \hline
+% MatchALS \cite{zhou2015multi} 35 Iterations          & 0.046 $\pm$ 0.016 & 0.010 $\pm$ 0.005 & 0.910 $\pm$ 0.072 & 0.742 $\pm$ 0.165 & 0.139 $\pm$ 0.041 \\ \hline
+% MatchALS \cite{zhou2015multi} 50 Iterations          & 0.029 $\pm$ 0.017 & 0.008 $\pm$ 0.005 & 0.905 $\pm$ 0.068 & 0.707 $\pm$ 0.166 & 0.260 $\pm$ 0.048 \\ \hline
+% PGDDS0 \cite{leonardos2016distributed} 15 Iterations & 0.017 $\pm$ 0.002 & 0.007 $\pm$ 0.001 & 0.918 $\pm$ 0.087 & 0.727 $\pm$ 0.180 & 0.796 $\pm$ 0.147 \\ \hline
+% PGDDS0 \cite{leonardos2016distributed} 25 Iterations & 0.016 $\pm$ 0.002 & 0.007 $\pm$ 0.002 & 0.919 $\pm$ 0.087 & 0.773 $\pm$ 0.184 & 1.670 $\pm$ 0.328 \\ \hline
+% PGDDS0 \cite{leonardos2016distributed} 50 Iterations & 0.015 $\pm$ 0.002 & 0.006 $\pm$ 0.002 & 0.920 $\pm$ 0.087 & 0.798 $\pm$ 0.183 & 3.363 $\pm$ 0.528 \\ \hline
+% Spectral                                             & 0.073 $\pm$ 0.006 & 0.027 $\pm$ 0.003 & 0.921 $\pm$ 0.083 & 0.670 $\pm$ 0.163 & 0.036 $\pm$ 0.005 \\ \hline
+% GNN (ours)                                           & 0.044 $\pm$ 0.005 & 0.031 $\pm$ 0.005 & 0.872 $\pm$ 0.081 & 0.377 $\pm$ 0.062 & 0.765 $\pm$ 0.046 \\ \hline
+% Method (10 Views)                                   & $L_1$             & $L_2$             & Area under ROC    & Area Prec.-Recall & Time (sec)        \ \hline
+% \hline\hline
+% MatchALS \cite{zhou2015multi} 10 Iterations         & 0.098 $\pm$ 0.007 & 0.023 $\pm$ 0.004 & 0.909 $\pm$ 0.052 & 0.679 $\pm$ 0.151 & 0.151 $\pm$ 0.026 \\ \hline
+% MatchALS \cite{zhou2015multi} 15 Iterations         & 0.114 $\pm$ 0.008 & 0.028 $\pm$ 0.004 & 0.915 $\pm$ 0.051 & 0.756 $\pm$ 0.125 & 0.142 $\pm$ 0.009 \\ \hline
+% MatchALS \cite{zhou2015multi} 20 Iterations         & 0.111 $\pm$ 0.008 & 0.024 $\pm$ 0.004 & 0.915 $\pm$ 0.053 & 0.784 $\pm$ 0.121 & 0.300 $\pm$ 0.131 \\ \hline
+% MatchALS \cite{zhou2015multi} 25 Iterations         & 0.092 $\pm$ 0.008 & 0.019 $\pm$ 0.003 & 0.912 $\pm$ 0.055 & 0.794 $\pm$ 0.123 & 0.228 $\pm$ 0.014 \\ \hline
+% MatchALS \cite{zhou2015multi} 30 Iterations         & 0.075 $\pm$ 0.008 & 0.015 $\pm$ 0.003 & 0.911 $\pm$ 0.056 & 0.773 $\pm$ 0.130 & 0.305 $\pm$ 0.056 \\ \hline
+% MatchALS \cite{zhou2015multi} 35 Iterations         & 0.065 $\pm$ 0.009 & 0.013 $\pm$ 0.003 & 0.907 $\pm$ 0.053 & 0.741 $\pm$ 0.130 & 0.355 $\pm$ 0.073 \\ \hline
+% MatchALS \cite{zhou2015multi} 40 Iterations         & 0.058 $\pm$ 0.010 & 0.012 $\pm$ 0.004 & 0.906 $\pm$ 0.051 & 0.733 $\pm$ 0.125 & 0.386 $\pm$ 0.052 \\ \hline
+% MatchALS \cite{zhou2015multi} 45 Iterations         & 0.050 $\pm$ 0.011 & 0.011 $\pm$ 0.004 & 0.911 $\pm$ 0.051 & 0.730 $\pm$ 0.126 & 0.440 $\pm$ 0.102 \\ \hline
+% MatchALS \cite{zhou2015multi} 50 Iterations         & 0.045 $\pm$ 0.012 & 0.011 $\pm$ 0.004 & 0.914 $\pm$ 0.051 & 0.732 $\pm$ 0.130 & 0.455 $\pm$ 0.022 \\ \hline
+% PGDDS \cite{leonardos2016distributed} 10 Iterations & 0.017 $\pm$ 0.001 & 0.008 $\pm$ 0.001 & 0.903 $\pm$ 0.061 & 0.689 $\pm$ 0.125 & 1.334 $\pm$ 0.357 \\ \hline
+% PGDDS \cite{leonardos2016distributed} 15 Iterations & 0.017 $\pm$ 0.001 & 0.008 $\pm$ 0.001 & 0.903 $\pm$ 0.061 & 0.688 $\pm$ 0.125 & 1.225 $\pm$ 0.159 \\ \hline
+% PGDDS \cite{leonardos2016distributed} 20 Iterations & 0.017 $\pm$ 0.001 & 0.008 $\pm$ 0.001 & 0.903 $\pm$ 0.061 & 0.688 $\pm$ 0.125 & 1.347 $\pm$ 0.299 \\ \hline
+% PGDDS \cite{leonardos2016distributed} 25 Iterations & 0.016 $\pm$ 0.001 & 0.007 $\pm$ 0.001 & 0.904 $\pm$ 0.061 & 0.737 $\pm$ 0.127 & 2.637 $\pm$ 0.357 \\ \hline
+% PGDDS \cite{leonardos2016distributed} 50 Iterations & 0.016 $\pm$ 0.001 & 0.007 $\pm$ 0.001 & 0.905 $\pm$ 0.061 & 0.763 $\pm$ 0.127 & 6.116 $\pm$ 1.009 \\ \hline
+% Spectral \cite{pachauri2013solving}                 & 0.073 $\pm$ 0.005 & 0.029 $\pm$ 0.002 & 0.912 $\pm$ 0.057 & 0.684 $\pm$ 0.109 & 0.081 $\pm$ 0.021 \\ \hline
+% \textbf{GNN (ours)}                                 & 0.053 $\pm$ 0.006 & 0.035 $\pm$ 0.005 & 0.872 $\pm$ 0.061 & 0.330 $\pm$ 0.050 & 2.438 $\pm$ 0.070 \\ \hline

### 2019-03-24 baselines/plot_logs.py

@@ -1,11 +1,35 @@
 import os
 import sys
 import numpy as np
-import re
+import yaml
+import copy
+import tqdm
 
 import matplotlib.pyplot as plt
 
 import argparse
+
+# Debug printing
+def process(x):
+  xp = None
+  if type(x) == dict:
+    xp = {}
+    for k in x:
+      xp[k] = process(x[k])
+  elif type(x) == list:
+    xp = [ process(z) for z in x ]
+  elif type(x) == np.ndarray:
+    xp = ( x.shape, x.dtype )
+  else:
+    xp = x
+  return xp
+import pprint
+pp_xfawedfssa = pprint.PrettyPrinter(indent=2)
+def myprint(x):
+  if type(x) == str:
+    print(x)
+  else:
+    pp_xfawedfssa.pprint(process(x))
 
 parser = argparse.ArgumentParser(description='Plot the downloaded model training/testing curves')
 parser.add_argument('files', metavar='files', nargs='+',
@@ -25,6 +49,22 @@ def errorfill(x, y, yerr, color=None, label=None, alpha_fill=0.3, semilogy=None,
   else:
     ax.plot(x, y, color=color)
   ax.fill_between(x, ymax, ymin, color=color, label=label, alpha=alpha_fill)
+
+def disp_plot(y, x=None, color=None, label=None, alpha=0.25, semilogy=None, ax=None):
+  """Fancy mean/median/percentile plotter. y is presumed NxS, x length N."""
+  if x is None:
+    x = np.arange(len(y))
+  ax = ax if ax is not None else plt.gca()
+  if color is None:
+    color = ax._get_lines.color_cycle.next()
+  ymean = np.mean(y,1)
+  ymin, ymax, ymid_b, ymid_u, ymed = np.percentile(y, [ 2, 98, 25, 75, 50 ], axis=1)
+  ax.plot(x,ymean,color=color,linestyle='-', label=label)
+  # ax.plot(x,ymed,color=color,linestyle='--')
+  ax.fill_between(x,ymid_b,ymid_u,facecolor=color,alpha=alpha)
+  # ax.fill_between(x,ymin,ymax,facecolor=color,alpha=alpha**2)
+  return ax
+
 
 def myord(x):
   if x == 'M':
@@ -51,129 +91,228 @@ def myformat_old(x):
   y = "{:.03e}".format(x).split('e')
   return "{}e-{}".format(y[0], y[1][-1])
 
[…]

### 2019-03-24 baselines/print_errors.py

@@ -1,7 +1,10 @@
 import os
 import sys
+import collections
+import copy
 import numpy as np
-import re
+import yaml
+import tqdm
 
 import matplotlib.pyplot as plt
 
@@ -23,59 +26,80 @@ def myformat_old(x):
   y = "{:.03e}".format(x).split('e')
   return "{}e-{}".format(y[0], y[1][-1])
 
-efmt = '[-+]?\d+\.\d*e[-+]\d+'
-disp_match = re.compile(efmt)
-names = [
-  'l1', 'l2', 'bce', \
-  'ssame_m', 'ssame_s', 'sdiff_m', 'sdiff_s', \
-  'roc', 'pr', \
-  'time']
-def parse(line):
-  return dict(zip(names, [ float(x) for x in disp_match.findall(line) ]))
+# TODO: Error checking
+def append_to(vals, v):
+  if type(vals) == dict:
+    for key in vals:
+      append_to(vals[key], v[key])
+  elif type(vals) == list:
+    vals.append(v)
 
-agg_names = [ 'l1', 'l2', 'bce', 'ssame', 'sdiff' ]
+def gen_agg_dict(default_value=[]):
+  return {
+    **{ k: copy.deepcopy(default_value)
+        for k in ['l1', 'l2', 'roc', 'p_r', 'time'] },
+    **{ k: { 'm': copy.deepcopy(default_value),
+             'std': copy.deepcopy(default_value) }
+        for k in ['ssame', 'sdiff'] },
+  }
+#   ['l1', 'l2', 'bce', 'roc', 'p_r', 'time']
+#   'ssame_m', 'ssame_s', 'sdiff_m', 'sdiff_s', \
 def agg(vals):
-  aggs = dict(zip(agg_names, [ None for nm in agg_names ]))
-  for k in [ 'l1', 'l2', 'bce', 'roc', 'pr', 'time' ]:
+  aggs = gen_agg_dict(0)
+  for k in [ 'l1', 'l2', 'roc', 'p_r', 'time' ]:
     aggs[k] = (np.mean(vals[k]), np.std(vals[k]))
   for k in [ 'ssame', 'sdiff' ]:
-    aggs[k] = ( np.mean(vals[k + '_m']), stdagg(vals[k + '_s']) )
+    aggs[k] = ( np.mean(vals[k]['m']), stdagg(vals[k]['std']) )
   return aggs
 
-def disp_val(aggs):
[…]

### 2019-03-24 baselines/roc_test.py

@@ -10,20 +10,19 @@ def test():
     y_pred = np.load(f)
   roc =  metrics.roc_auc_score(y_true, y_pred)
   p_r =  metrics.average_precision_score(y_true, y_pred)
-  # import pdb; pdb.set_trace()
-  precision, recall, _ = metrics.precision_recall_curve(y_true, y_pred)
-  fpr, tpr, _ = metrics.roc_curve(y_true, y_pred)
   print("{:.06e} {:.06e}".format(roc,p_r))
-  print(precision.shape)
-  print(recall.shape)
-  with open(os.path.join(sys.argv[1], 'precision.npy'), 'wb') as f:
-    np.save(f, precision)
-  with open(os.path.join(sys.argv[1], 'recall.npy'), 'wb') as f:
-    np.save(f, recall)
-  with open(os.path.join(sys.argv[1], 'fpr.npy'), 'wb') as f:
-    np.save(f, fpr)
-  with open(os.path.join(sys.argv[1], 'tpr.npy'), 'wb') as f:
-    np.save(f, tpr)
+  # precision, recall, _ = metrics.precision_recall_curve(y_true, y_pred)
+  # fpr, tpr, _ = metrics.roc_curve(y_true, y_pred)
+  # print(precision.shape)
+  # print(recall.shape)
+  # with open(os.path.join(sys.argv[1], 'precision.npy'), 'wb') as f:
+  #   np.save(f, precision)
+  # with open(os.path.join(sys.argv[1], 'recall.npy'), 'wb') as f:
+  #   np.save(f, recall)
+  # with open(os.path.join(sys.argv[1], 'fpr.npy'), 'wb') as f:
+  #   np.save(f, fpr)
+  # with open(os.path.join(sys.argv[1], 'tpr.npy'), 'wb') as f:
+  #   np.save(f, tpr)
 
 test() 
 

### 2019-03-24 baselines/run_tests.m

@@ -7,6 +7,8 @@ if nargin < 3
   save_out = false;
 end
 
+% Random setup
+[~,~,~] = mkdir('/tmp/mymatlab');
 npzmatlab_path = 'npz-matlab';
 pathCell = regexp(path, pathsep, 'split');
 onPath = any(strcmp(npzmatlab_path, pathCell));
@@ -21,47 +23,58 @@ v = views;
 p = 80;
 n = p*v;
 dimGroups = ones(v,1)*p;
-params015.maxiter = 15;
+params015 = pgdds_params(15);
 params025.maxiter = 25;
 params050.maxiter = 50;
 params100.maxiter = 100;
 params200.maxiter = 200;
 
 metric_info = { ...
-      { 'l1',      'l1: %.03e, '         , @mean                 }, ...
-      { 'l2',      'l2: %.03e, '         , @mean                 }, ...
-      { 'ssame_m', 'ssame: { m: %.03e, ' , @mean                 }, ...
-      { 'ssame_s', 'std: %.03e }, '      , @(x) sqrt(mean(x.^2)) }, ...
-      { 'sdiff_m', 'sdiff: { m: %.03e, ' , @mean                 }, ...
-      { 'sdiff_s', 'std: %.03e }, '      , @(x) sqrt(mean(x.^2)) }, ...
-      { 'roc',     'roc: %.03e, '        , @mean                 }, ...
-      { 'pr',      'p_r: %.03e, '        , @mean                 }, ...
+    { 'l1',      'l1: %.03e, '         , @mean                 }, ...
+    { 'l2',      'l2: %.03e, '         , @mean                 }, ...
+    { 'ssame_m', 'ssame: { m: %.03e, ' , @mean                 }, ...
+    { 'ssame_s', 'std: %.03e }, '      , @(x) sqrt(mean(x.^2)) }, ...
+    { 'sdiff_m', 'sdiff: { m: %.03e, ' , @mean                 }, ...
+    { 'sdiff_s', 'std: %.03e }, '      , @(x) sqrt(mean(x.^2)) }, ...
+    { 'roc',     'roc: %.03e, '        , @mean                 }, ...
+    { 'pr',      'p_r: %.03e, '        , @mean                 }, ...
 };
[…]

### 2019-03-24 experiment.py

@@ -11,6 +11,8 @@ import tqdm
 import myutils
 # import options
 
+def disp_vals(x):
+  return (np.median(x), np.mean(x), np.std(x), np.min(x), np.max(x))
 def str2bool(v):
     if v.lower() in ('yes', 'true', 't', 'y', '1'):
         return True
@@ -103,6 +105,8 @@ def plot_baseline(save_dir, emb_init, emb_gt, emb_out):
 def plot_index(save_dir, emb_init, emb_gt, emb_out):
   # Embeddings
   slabels, sorted_idxs = get_sorted(emb_gt)
+  print(np.max(sorted_idxs))
+  print(emb_out.shape)
   soutput = emb_out[sorted_idxs]
   srand = myutils.dim_normalize(emb_init[sorted_idxs])
   lsim = np.abs(np.dot(slabels, slabels.T))
@@ -216,27 +220,41 @@ if __name__ == "__main__":
   # Build options
   # opts = options.get_opts()
   opts = get_experiment_opts()
-  # Run experiment
-  ld = np.load(opts.data_path)
-  emb_init = ld['input']
-  emb_gt = ld['gt']
-  emb_out = ld['output']
-  adjmat = ld['adjmat']
+  # Load data and format it
+  p = 80 # TODO: Hack
+  with open(opts.data_path, 'rb') as f:
+    ld = dict(np.load(f))
+  matches = ld['true_match']
+  emb_gt = np.eye(p)[matches]
+  b = len(ld['output'][-2]) # TODO: Hack
+  n = ld['output'][-2][0] # TODO: Hack
+  emb_out = ld['output'][0].reshape(b,n,p)
+  emb_init = ld['input_nodes'].reshape(b,n,-1)
+  A = ld['adj_mat']
+  adjmat = np.zeros(A[2])
+  adjmat[A[0][:,0],A[0][:,1],A[0][:,2]] = A[1]
   n = len(emb_gt)
+  print("emb_init.shape")
+  print(emb_init.shape)
+  print("emb_gt.shape")
+  print(emb_gt.shape)
+  print("emb_out.shape")
+  print(emb_out.shape)
+  # Run experiment
   if opts.plot_style == 'none':
-    stats = np.zeros((n,8))
+    stats = np.zeros((b,8))
     if opts.verbose:
-      for i in tqdm.tqdm(range(n)):
+      for i in tqdm.tqdm(range(b)):
[…]

### 2019-03-24 latex/latex_report.py

@@ -117,11 +117,11 @@ class Experiment(object):
 
   def generate_plot(self, size, index=0):
     if self.view_style == 'default':
-      self.generate_plot_default(size, index=index)
+      return self.generate_plot_default(size, index=index)
     elif self.view_style == 'paper':
-      self.generate_plot_paper(size, index=index)
+      return self.generate_plot_paper(size, index=index)
     elif self.view_style == 'embeddings':
-      self.generate_plot_embeddings(size, index=index)
+      return self.generate_plot_embeddings(size, index=index)
 
   def generate_plot_default(self, size, index=0):
     nrows, ncols = 1, 5
@@ -259,36 +259,55 @@ class Experiment(object):
     return fig
 
   def generate_plot_embeddings(self, size, index=0):
-    nrows, ncols = 1, 2
-    fig, ax = plt.subplots(nrows=nrows, ncols=ncols, figsize=(ncols*size,1.4*nrows*size))
+    nrows, ncols = 1, 3
+    fig, ax = plt.subplots(nrows=nrows, ncols=ncols, figsize=(0.4*ncols*size,1.3*nrows*size))
     # ax[1] = fig.add_subplot(nrows,ncols,2,projection='3d')
     fig.tight_layout()
 
     ##### Plot embeddings of a specific example
+    ### Load data and format it
+    p = 80 # TODO: Hack
+    with open(glob.glob(os.path.join(self.folder, 'test*npz'))[-1], 'rb') as f:
+      ld = dict(np.load(f))
+    matches = ld['true_match']
+    emb_gt = np.eye(p)[matches]
+    b = len(ld['output'][-2]) # TODO: Hack
+    n = ld['output'][-2][0] # TODO: Hack
+    emb_out = ld['output'][0].reshape(b,n,p)
+    emb_init = ld['input_nodes'].reshape(b,n,-1)
+    A = ld['adj_mat']
+    adjmat = np.zeros(A[2])
+    adjmat[A[0][:,0],A[0][:,1],A[0][:,2]] = A[1]
+    n = len(emb_gt)
     ### Get specific example
-    ldnames = sorted(glob.glob(os.path.join(self.folder, 'test*npz')))
-    ld = np.load(ldnames[-1])
-    emb_init = ld['input'][index]
-    emb_gt = ld['gt'][index]
-    emb_out = ld['output'][index]
[…]

### 2019-03-24 latex/imw2019/main.tex
Added Image Matching Workshop draft

--- 2019-03-21 latex/iccv2019/main.tex
@@
 
-\usepackage{iccv}
+\usepackage{cvpr}
 \usepackage{times}
@@
 \usepackage{amssymb}
-
 % Include other packages here, before hyperref.
+% \usepackage[outdir=./]{epstopdf}
 
@@
 % run, let it finish, and you should be clear).
-\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
+\usepackage[breaklinks=true,bookmarks=false]{hyperref}
 
-% \iccvfinalcopy % *** Uncomment this line for the final submission
+% \cvprfinalcopy % *** Uncomment this line for the final submission
 
-\def\iccvPaperID{****} % *** Enter the ICCV Paper ID here
+\def\cvprPaperID{3510} % *** Enter the CVPR Paper ID here
 \def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
@@
 % Pages are numbered in submission mode, and unnumbered in camera-ready
-\ificcvfinal\pagestyle{empty}\fi
+%\ifcvprfinal\pagestyle{empty}\fi
+\setcounter{page}{1}
 \begin{document}
@@
 %%%%%%%%% TITLE
-\title{All Graphs Lead to Rome: Learning Geometric and Cycle-Consistent Representations with Graph Networks}
+% \title{All Graphs Lead to Rome: \\
+% Cycle Consistent Multi-View Representations Using Graph CNNs}
+\title{All Graphs Lead to Rome: Learning Geometric and Cycle-Consistent Representations with Graph Convolutional Networks}
 
@@
 % To save space, use either the email address or home page, not both
+% \and
+% Second Author\\
+% Institution2\\
+% First line of institution2 address\\
+% {\tt\small secondauthor@i2.org}
 }
+
+% When placing figures in \LaTeX, it's almost always best to use
+% \verb+\includegraphics+, and to specify the  figure width as a multiple of
+% the line width as in the example below
+% {\small\begin{verbatim}
+%    \usepackage[dvips]{graphicx} ...
+%    \includegraphics[width=0.8\linewidth]
+%                    {myfile.eps}
+% \end{verbatim}
+% }
 
@@
 
+% Papers, excluding the references section,
+% must be no longer than eight pages in length. The references section
+
 %%%%%%%%% ABSTRACT
@@
     Image feature matching is a fundamental part of many geometric computer vision applications, and using multiple images can improve performance.
-    In this work, we formulate multi-image matching as a graph embedding problem then use a Graph Neural Networks to learn an appropriate embedding function for aligning image features.
+    In this work, we formulate multi-image matching as a graph embedding problem then use a Graph Neural Network to learn an appropriate embedding function for aligning image features.
     We use cycle consistency to train our network in an unsupervised fashion, since ground truth correspondence is difficult or expensive to aquire.
@@
 % TODO: Mention trifocal tensors
-Other works, such as Wang et al.~\cite{wang2017multi}, have shown improvement in performance by optimizing cycle consistency, i.e.
-enforcing the pairwise feature matches to be globally consistent, illustrated in figure \ref{fig:cycconsistex}.
+Other works, such as Wang et al.~\cite{wang2017multi}, have shown improvement in performance by optimizing cycle consistency, i.e. enforcing the pairwise feature matches to be globally consistent.
 
@@
 % Using features designed to deal with these confounding factors improves robustness to them, and learning may improve robustness even further.
-
-\begin{figure}[t]
-\begin{center}
-  % \fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-  \includegraphics[width=0.8\linewidth]{figures-CycleConsistencyBasic-v2.pdf}
-\end{center}
-  \caption{
-    Example of multi-image matching and cycle consistency, with images from Rome16K dataset \cite{li2010location}.
-    Pairwise matches between image can lead to global inconsistencies in the matching.
-    In this example, an error in matching leads to an inconsistent cycle (shown in red), ideally these pairwise matches would be consistent.
-    We improve the quality of pairwise matches in the multi-view matching problem by training a neural net with cycle consistency.
-  }
-\label{fig:cycconsistex}
-\label{fig:onecol}
-\end{figure}
 
@@
 
-In this work, we propose to solve these problems using a Graph Neural Networks (GNNs) to operate on the correspondence graph.
+In this work, we propose to solve these problems using Graph Neural Networks (GNNs) to operate on the correspondence graph.
 The proposed method works directly on the correspondence graph, which is agnostic to how the correspondences were computed, thus allowing the algorithm to work in a broad class of environments.
@@
 As with any neural network, GNNs have layered outputs.
-We describe the output of layer $k$ as $\mat{f}_v^{(k)} \forall v \in \mathcal{V}$ and $\mat{f}_e^{(k)} \forall e in \mathcal{E}$, with the initial embeddings denoted $\mat{f}_v^{(0)} = \mat{f}_v^{(0)}$ and $\mat{f}_e^{(0)} = \mat{f}_e$.
+We describe the output of layer $k$ as $\mat{f}_v^{(k)} \forall v \in \mathcal{V}$ and $\mat{f}_e^{(k)} \forall e \in \mathcal{E}$, with the initial embeddings denoted $\mat{f}_v^{(0)} = \mat{f}_v^{(0)}$ and $\mat{f}_e^{(0)} = \mat{f}_e$.
+It will be useful to write these features as matrices in later sections, so we denote the vertex embedding matrix as $\mat{F}_V^{(k)}$ and the edge embedding matrix as $\mat{F}_E^{(k)}$.
+If a superscript is not specified then it refers to the final output of the network.
 
@@
 
-\begin{table*}
-\begin{center}
-\begin{tabular}{|l|c|c|}
-\hline
-Method & Same Point Similarities & Different Point Similarities  \\
-\hline\hline\hline
-Ideal                              & 1.00e+0 $\pm$ 0.00e+0 & 0.00e+0 $\pm$ 0.00e+0 \\ \hline
-Initialization Baseline            & 5.11e-1 $\pm$ 1.68e-2 & 2.56e-1 $\pm$ 2.06e-1 \\ \hline
-3 Views, Noiseless                 & 9.96e-1 $\pm$ 7.70e-3 & 1.16e-1 $\pm$ 1.32e-1 \\ 
-5 Views, Noiseless                 & 1.00e+0 $\pm$ 4.15e-4 & 1.22e-1 $\pm$ 1.67e-1 \\ \hline
-3 Views, Added Noise               & 9.96e-1 $\pm$ 7.70e-3 & 1.16e-1 $\pm$ 1.32e-1 \\ 
-5 Views, Added Noise               & 9.89e-1 $\pm$ 2.47e-2 & 7.67e-2 $\pm$ 1.56e-1 \\ 
-6 Views, Added Noise               & 9.84e-1 $\pm$ 3.16e-2 & 7.46e-2 $\pm$ 1.57e-1 \\ \hline
-3 Views, 5\% Outliers              & 9.29e-1 $\pm$ 1.79e-1 & 1.41e-1 $\pm$ 1.48e-1 \\ 
-3 Views, 10\% Outliers             & 9.27e-1 $\pm$ 1.79e-1 & 1.40e-1 $\pm$ 1.51e-1 \\ \hline
-
-\hline
-\end{tabular}
-\end{center}
-\caption{
-Results on Synthetic correspondence graphs.
-The `Same Point Similarities' column is the mean and standard deviation of similarities for true corresponding points, while the `Different Point Similarities' is the same for points that do not correspond.
-For the `Same Point Similarities' column higher is better, and for `Different Point Similarities' lower is better.
-Losses tested against ground truth correspondence graph adjacency matrices.
-Our method was not trained on ground truth correspondences but using unsupervised methods.
-}
-\label{fig:synthtable}
-\end{table*}
-
-This reduces our complexity from $O(n^3)$ to $O(n^2)$.
-We try to learn $\mat{E}$ to approximate $\mat{X}$ - in other words the final embedding should be an encoding of the universe of features.
-As we do not have the ground truth matches $\mat{M}$, we approximate it using the noisy adjacency matrix $\mat{A}$ of our correspondence graph.
-Thus our loss would be
+This reduces the number of our constraints from $O(n^3)$ to $O(n^2)$.
+We try to learn vertex embeddings $\mat{F}_V$ to approximate $\mat{X}$ - in other words the final embedding should be an encoding of the universe of features.
+As we do not have the ground truth matches $\mat{M}$, we approximate it using the noisy adjacency matrix $\mat{A}$ of our correspondence graph. Thus our loss would be 
 \begin{equation}
-\mathcal{L}(\mat{A}, \mat{E}_n) = \mathcal{D}(\mat{A}, \mat{E}_n\mat{E}_n^\top)
+\mathcal{L}(\mat{A}, \mat{F}_V) = \mathcal{D}(\mat{A}, \mat{F}_V \mat{F}_V^\top)
 \end{equation}
@@
 The constraint assumes that the $X_k$ are calibrated i.e. the camera intrinsics are known. 
-Given the matrix of ground truth correspondences $\mat{M}_{ij}$ between camera $i$ and $j$, we can formulate this as a loss:
-\begin{equation}
-\mathcal{L}_{ij,geom}(\mat{M}_{ij}) = \sum_{k,l} (\mat{M}_{ij})_{kl} \left|X_{i,k}^\top R_{i}^\top \cross{T_{j} - T_{i}}R_{j} X_{j,l}\right|
+Given our vertex embeddings matrix $\mat{F}_V$, we can formulate a loss between all cameras $i$ and $j$:
+\begin{align}
+&\mathcal{L}_{ij,geom}(\mat{F}_V) = \\ \nonumber
+&\sum_{v \in \mathcal{V}(i),u \in \mathcal{V}(j)} \sum_{} (\mat{f}_v \cdot \mat{f}_u) \left|X_{v}^\top R_{i}^\top \cross{T_{j} - T_{i}}R_{c_j} X_{u}\right|
 \label{eq:geom_cost}
-\end{equation}
+\end{align}
+With $\mathcal{V}(i)$ being the vertices associated with camera $i$.
 For our purposes, since we use low rank embeddings $\mat{E}_{i}$, $\mat{E}_{j}$, the loss would read:
 \begin{align}
-\mathcal{L}_{geom}(\mat{E})
-=&\; \mathrm{tr}(\mat{G}^\top \mat{E}\mat{E}^\top) = \sum_{i,j} (\mat{E})_{i} \cdot (\mat{E})_{j} (\mat{G})_{ij} \\
-(\mat{G})_{ij} =&\; \left|X_{i}^\top R_{c(i)}^\top \cross{T_{c(j)} - T_{c(i)}}R_{c(j)} X_{j}\right| \nonumber
+\mathcal{L}_{geom}(\mat{F}_V)
+=&\; \mathrm{tr}(\mat{G}^\top \mat{F}_V\mat{F}_V^\top) = \sum_{k,l} (\mat{F}_V)_{k} \cdot (\mat{F}_V)_{l} (\mat{G})_{kl} \\
+(\mat{G})_{kl} =&\; \left|X_{k}^\top R_{c(k)}^\top \cross{T_{c(l)} - T_{c(k)}}R_{c(l)} X_{l}\right| \nonumber
 \label{eq:geom_cost2}
 \end{align}
-Where $c(i)$ is the appropriate camera for point index $i$.
-
-\begin{table*}
-\begin{center}
-\begin{tabular}{|l|c|c|c|}
-\hline
-Method (3 Views)                                          & $L_1$ Loss                          & $L_2$ Loss                          & Run Time (sec)                      \\
-\hline\hline
-MatchALS \cite{zhou2015multi} 15 Iterations               & 0.052 $\pm$ 0.003                   & 0.010 $\pm$ 0.002                   & 0.021 $\pm$ 0.003                   \\
-MatchALS \cite{zhou2015multi} 25 Iterations               & 0.045 $\pm$ 0.007                   & 0.009 $\pm$ 0.003                   & 0.034 $\pm$ 0.003                   \\
-MatchALS \cite{zhou2015multi} 50 Iterations               & 0.016 $\pm$ 0.008                   & 0.007 $\pm$ 0.003                   & 0.065 $\pm$ 0.006                   \\ \hline
-PGDDS \cite{leonardos2016distributed} 15 Iterations       & 0.016 $\pm$ 0.002                   & 0.006 $\pm$ 0.002                   & 0.287 $\pm$ 0.043                   \\
-PGDDS \cite{leonardos2016distributed} 25 Iterations       & 0.014 $\pm$ 0.002                   & 0.005 $\pm$ 0.002                   & 0.613 $\pm$ 0.089                   \\
-PGDDS \cite{leonardos2016distributed} 50 Iterations       & 0.013 $\pm$ 0.002                   & 0.005 $\pm$ 0.002                   & 1.430 $\pm$ 0.234                   \\ \hline
-Spectral                                                  & 0.054 $\pm$ 0.005                   & 0.018 $\pm$ 0.004                   & 0.018 $\pm$ 0.004                   \\ \hline 
-\textbf{GNN, 12 Layers (ours)}                            & \textbf{0.025} $\pm$ \textbf{0.003} & \textbf{0.016} $\pm$ \textbf{0.003} & \textbf{0.039} $\pm$ \textbf{0.009} \\
-\hline\hline
-Method (4 Views)                                                         & $L_1$ Loss                          & $L_2$ Loss                          & Run Time (sec)                     \\
-\hline\hline
-MatchALS \cite{zhou2015multi} 15 Iterations                              & 0.064 $\pm$ 0.005                   & 0.012 $\pm$ 0.002                   & 0.030 $\pm$ 0.004                   \\
-MatchALS \cite{zhou2015multi} 25 Iterations                              & 0.041 $\pm$ 0.010                   & 0.008 $\pm$ 0.004                   & 0.048 $\pm$ 0.005                   \\
-MatchALS \cite{zhou2015multi} 50 Iterations                              & 0.011 $\pm$ 0.008                   & 0.005 $\pm$ 0.003                   & 0.094 $\pm$ 0.008                   \\ \hline
-PGDDS \cite{leonardos2016distributed} 15 Iterations                      & 0.015 $\pm$ 0.002                   & 0.006 $\pm$ 0.001                   & 0.436 $\pm$ 0.090                   \\
-PGDDS \cite{leonardos2016distributed} 25 Iterations                      & 0.014 $\pm$ 0.002                   & 0.005 $\pm$ 0.001                   & 0.961 $\pm$ 0.181                   \\
-PGDDS \cite{leonardos2016distributed} 50 Iterations                      & 0.013 $\pm$ 0.002                   & 0.005 $\pm$ 0.002                   & 2.056 $\pm$ 0.424                   \\ \hline
-Spectral Method                                                          & 0.055 $\pm$ 0.004                   & 0.017 $\pm$ 0.003                   & 0.028 $\pm$ 0.003                   \\ \hline
-\textbf{GNN, 12 Layers (ours)}                                           & \textbf{0.023} $\pm$ \textbf{0.003} & \textbf{0.015} $\pm$ \textbf{0.002} & \textbf{0.056} $\pm$ \textbf{0.017} \\ \hline
-\end{tabular}
-\end{center}
-% save-rome16kgeom0-normedskip2-loss-l1-geom-10-0 (028249) -> train : +3.1467e-02, test : +3.8864e-02, gt_l1 : +2.6321e-02, gt_l2 : +2.6321e-02
-
-\caption{
-Results on Rome16K Correspondence graphs, showing the mean and standard deviation of the $L_1$ and $L_2$.
-Our method was not trained on ground truth correspondences but using unsupervised methods and geometric side losses.
-As our method gives soft labels, we use cannot use precision or recall as is standard in testing cycle consistency \cite{zhou2015multi}.
-Thus we test against ground truth correspondence graph adjacency matrices computed from the bundle adjustment output.
-Our method performs better than 25 iteration of the MatchALS \cite{zhou2015multi} method, but does not perform as well as 50 iterations.
-% Our network has only 12 layers, thus we have much greater efficiency per iteration.
-We do not perform as well as the Projected Gradient Descent Doubly Stochastic (PGDDS) \cite{leonardos2016distributed} but we perform significantly faster than them.
-Note that we perform much better in $L_1$ performance rather than $L_2$, as we optimized the network weights using an $L_1$ loss.
-}
-\end{table*}
+Where $c(k)$ is the appropriate camera for point index $k$.
 
@@
 \section{Experiments}
-
-\begin{figure*}
-\begin{center}
-  % \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
-  \includegraphics[width=0.8\linewidth]{figures-TrainingCurves.pdf}
-  \end{center}
-    \caption{
-      Training curves with and without Geometric Training loss.
-      The geometric training loss improves testing performance.
-      Shown as horizontal lines are the state of the art optimization based baselines.
-      Even with a simple network we compare well with them.
-    }
-  \label{fig:short}
-\end{figure*}
 
@@
 \end{figure*}
-\subsection{Synthetic Graph Dataset}
-We first test our method on synthetically generated data as a simple proof of concept.
-To generate the data, we generate $p$ points, each with its own randomly generated descriptor.
-To create the graph, we generate random permutation matrices, with a noise applied to it after it is generated.
-% The initial descriptors we use as input we created using the true descriptor plus some added Gaussian noise.
-We initialize the input descriptors using the true descriptor, plus some added Gaussian noise.
-No geometric losses were added during training for these experiments.
-However, the method was robust in testing with different noise functions and parameters.
-The normalized noisy input descriptors are our baseline - they correlate with the true values but do not preserve the structure well.
-However, the GNN recovered the true structure very well, as shown in Table \ref{fig:synthtable}.
-All experiments were run with a 12 layer GNN with the ReLU nonlinearity and skip connections.
-All were trained with the Adam optimizer \cite{kingma2014adam} and a learning rate $10^{-4}$
+
+\subsection{Implementation Details}
+The network was implemented using the code provided by \cite{battaglia2018relational} using Tensorflow \cite{tensorflow2015} 1.11.
+Our network has 16 layers, with 8 message passing operations placed ever other layer.
+All layers were simple Multi-layer Perceptrons, with no batch norm.
+The network was trained with the Adam optimizer \cite{kingma2014adam} with a learning rate of $10^{-4}$, with an exponentially decaying learning rate.
+We incorporate skip connections between the input, $6^{th}$, and $12^{th}$ layers (all possible pairs).
 
@@
 We evaluate on a test set using the ground truth adjacency matrix, which we compute from the bundle adjustment given by the Rome16K dataset.
-Traditional methods of evaluation use Precision and Recall, after making the labels 0 or 1.
-We forgo this as our method was trained to output soft labels - we in turn make the labels soft for the optimization based methods.
+We use the $L_1$ and ROC AUC metrics to measure performance.
 For this method to work, we need the dimension of the embedding to be at least the number of unique points in the scene.
@@
 Here we use the ground truth dimension of the embedding to test both our method and the baselines.
-For implementation details, our network has 12 layers, and was trained with the Adam optimizer \cite{kingma2014adam} with a learning rate of $10^{-4}$, with an exponentially decaying learning rate.
-We incorporate skip connections between the input, $6^{th}$, and $12^{th}$ layers, which greatly improved training convergence and testing performance (see supplemental material).
 
+% Our method performs better than nearly 
 We compare our method to spectral and optimization based baselines with different maximum iteration cutoffs.
-Our method is signification better than a simple spectral based optimization.
-% Furthermore, our network, which only has 12 layers has the accuracy of the optimization based method MatchALS \cite{zhou2015multi} inbetween 25 and 50 iterations.
-Our network, though only 12 layers, has comparable accuracy to MatchALS \cite{zhou2015multi} run between 25 and 50 iterations.
-% This indicates that our method learns a more efficient update with each layer compared with an iteration in the optimization based methods.
-Although our method does not outperform the Projected Gradient Descent - Doubly Stochastic (PGDDS) \cite{leonardos2016distributed} method, we have significantly better run time.
-Additional comparisons to different iterations numbers of iterations can be found in the supplementary material.
+Our network, though only using 8 message passes, has comparable accuracy to MatchALS \cite{zhou2015multi} run 35 to 45 iterations, with an equivalent message passing step at each phase.
+Although our method does not outperform the Projected Gradient Descent - Doubly Stochastic (PGDDS) \cite{leonardos2016distributed} method, we perform comparably to them in the ROC AUC metric.
+% Our network, though only 12 layers, has comparable accuracy to MatchALS \cite{zhou2015multi} run between 25 and 50 iterations.
+% Additional comparisons to different iterations numbers of iterations can be found in the supplementary material.
+
+\begin{figure*}[t]
+\begin{center}
+  % \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
+  \includegraphics[width=0.8\linewidth]{figures-error_lines.pdf}
+  \end{center}
+     \caption{
+         Plot of the losses of the baselines at different iteration numbers.
+         The line shows the mean of the graph while the translucent coloring shows the $25^{th}$ to $75^{th}$ percentiles.
+         The ROC AUC curves remain fairly consistent while the L1 loss goes noticibly down after more iterations.
+         Our method compares to 35-45 iterations of MatchALS, while only haveing 16 layers and 8 message passes.
+         PGDDS peforms better than us in $L_1$ but we peform similarly in the ROC AUC metric.
+     }
+  % \label{fig:twocol}
+  \label{fig:errorlines}
+\end{figure*}
 
@@
 We have shown a novel method for training feature matching using GNNs, using an unsupervised cycle consistency loss and geometric consistency losses.
-We have demonstrated its effectiveness on the Rome16K dataset compared to the traditional optimization based baselines on a simple GNN.
+We have demonstrated has comparable the traditional optimization based baselines on a simple GNN, while still allowing for end-to-end training integration in deep learning pipelines.
 For future work, we will investigate robust losses for better outlier rejection, and using higher order geometric constraints, such as the tri-focal tensor, as additional loss terms.

### 2019-04-22 latex/imw2019/main.tex
Massive Figure modifications for Image Matching 2019 Workshop

@@
 % must be no longer than eight pages in length. The references section
-
 %%%%%%%%% ABSTRACT
@@
     In this work, we formulate multi-image matching as a graph embedding problem then use a Graph Neural Network to learn an appropriate embedding function for aligning image features.
-    We use cycle consistency to train our network in an unsupervised fashion, since ground truth correspondence is difficult or expensive to aquire.
-    In addition, geometric consistency losses can be added at training time, even if the information is not available in the test set, unlike previous approaches that optimize cycle consistency directly.
+    We use cycle consistency to train our network in an unsupervised fashion, since ground truth correspondence is difficult or expensive to acquire.
+    In addition, geometric consistency losses can be added at training time, even if the information is not available in the test set, unlike previous approaches which optimize cycle consistency directly.
     To the best of our knowledge, no other works have used learning for multi-image feature matching.
@@
 
-%%%%%%%%% BODY TEXT
-\section{Introduction}
-
-Feature matching is an essential part of Structure from Motion and many geometric computer vision applications.
-The goal in multi-image feature matching is to take 2D image locations from three or more images and find which ones correspond to the same point in the 3D scene.
-Methods such as SIFT feature matching \cite{lowe2004distinctive} followed by RANSAC \cite{fischler1981random} have been the standard for decades.
-However RANSAC-based approaches are limited to matching pairs of images, which can lead to global inconsistencies in the matching.
-% TODO: Mention trifocal tensors
-Other works, such as Wang et al.~\cite{wang2017multi}, have shown improvement in performance by optimizing cycle consistency, i.e. enforcing the pairwise feature matches to be globally consistent.
-
-However, these multi-view consistency algorithms struggle in distributed and robust settings.
-Deep learning has revolutionized how image features are computed \cite{yi2016lift}.
-In this paper, we want to leverage the power of deep representations in order to compute feature descriptors that are robust across multiple views.
-% Typically when applied to image or feature matching, deep neural networks (DNNs) are trained with photometric losses, directly using pixel color values.
-% However direct, pixel-based losses have are not robust to the many confounding factors in the environment, such as lighting and view-point changes.
-% Using features designed to deal with these confounding factors improves robustness to them, and learning may improve robustness even further.
-
 %------------------------------------------------------------------------
-\begin{figure*}[t]
+\begin{figure}[t]
 \begin{center}
   % \fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-  \includegraphics[width=0.8\linewidth]{figures-CycleConsistencyMainFigure-v2.pdf}
+  \includegraphics[width=0.9\linewidth]{figures-CycleConsistencyMainFigure-v3.pdf}
 \end{center}
@@
     An illustration of the approach of this work.
-    The Graph Neural Neural Network (GNN) \cite{battaglia2018relational} takes as input the graph of matches and then outputs a low rank embedding of the adjacency matrix of the graph.
-    The GNN operates on an embedding over the vertices of the graph.
-    In the figure, the GNN vertex embeddings are represented by different colors.
-    The final embedding is used to construct a pairwise similarity matrix, which we train to be a low dimensional cycle-consistent representation of the graph adjacency matrix, thus pruning the erroneous matches.
-    We train the network using a reconstruction loss on the similarity matrix with the noisy adjacency matrix, and thus do not need ground truth matches.
-    In addition, we can use geometric consistency information, such as epipolar constraints, to assist training the network.
+    The Graph Neural Neural Network (GNN) \cite{battaglia2018relational} takes as input the graph of matches with vertex features and outputs an embedding over the vertices of the graph (represented by different colors in the figure).
+    The final embedding is used to construct a pairwise similarity matrix, which we train to be a low dimensional cycle-consistent representation of the graph adjacency matrix.
+    We train the network using a reconstruction loss on the similarity matrix with the noisy adjacency matrix, and geometric consistency information, such as epipolar constraints, to provide an unsupervised training method for the model.
   }
 \label{fig:pipeline}
-\label{fig:onecol}
-\end{figure*}
+% \label{fig:onecol}
+\end{figure}
 
-Unfortunately, there are obstacles to applying multi-view constraints directly to deep learning. 
-To train networks, we need a large amount of labeled data.
-In the case of multi-image feature matching, one would need hand labeled point correspondences between images, which are difficult and expensive to obtain.
-Multi-view constraints are formulated in terms of sparse features, which traditional convolutional neural nets are not designed to handle.
-Additionally, in the case of multi-image feature matching, geometric constraints would be helpful in rejecting outlier matches.
+\section{Introduction}
+Feature matching is an essential part of Structure from Motion and many geometric computer vision applications.
+The goal in multi-image feature matching is to take 2D image locations from three or more images and find which ones correspond to the same point in the 3D scene.
+Works such as Wang et al.~\cite{wang2017multi}, have shown improvement in performance by optimizing cycle consistency, i.e. enforcing the pairwise feature matches to be globally consistent.
 
-In this work, we propose to solve these problems using Graph Neural Networks (GNNs) to operate on the correspondence graph.
-The proposed method works directly on the correspondence graph, which is agnostic to how the correspondences were computed, thus allowing the algorithm to work in a broad class of environments.
+However, these multi-view consistency algorithms struggle in distributed and robust settings.
+Having image features suited for this task would help improve performance, and deep learning has revolutionized how image features are computed \cite{yi2016lift}.
+In this paper, we want to leverage the power of deep representations in order to compute feature descriptors that are robust across multiple views.
+
+In this work, we propose to training a Graph Neural Networks (GNNs) to operate directly on the sparse correspondence graph, allowing it to work in a broad class of environments.
 To the best of our knowledge this work is the first to apply deep learning to the multi-view feature matching problem.
 We use an unsupervised loss - the cycle consistency loss - to train the network, and thus avoiding the difficulty of expensive hand labeling.
-% We incorporate geometric consistency losses to guide training, which helps training even when the geometric information is not available at test time.
 Geometric consistency losses can aid training, even if such information is not available at test time.
-Although our network is simple, it shows promising results compared to baselines which optimize for cycle-consistency without learned embeddings.
+Although our network is simple, it shows promising results compared to baselines which optimize for cycle-consistency without learned embeddings, using a matrix factorization loss \cite{zhou2015multi, leonardos2016distributed}.
 Furthermore, since inference requires only a single forward pass over the neural network, our approach is faster (to achieve comparable accuracy) than methods which must solve an optimization problem every time.
-Our contributions are:
-\begin{itemize}
-\item We use a novel architecture to address the multi-image feature matching problem using GNNs with graph embeddings.
-\item We introduce an unsupervised cycle consistency loss that does not require labeled correspondences to train.
-\item We demonstrate the effectiveness of geometric consistency losses in improving training.
-\item We perform experiments on the Rome16K \cite{li2010location} dataset to test the effectiveness of our method compared to optimization based methods.
-\end{itemize}
-
-%-------------------------------------------------------------------------
-\section{Related Work}
-
-\subsection{Feature Matching}
-Matching has a rich history of research in computer vision.
-Much work has be done using hand-crafted feature descriptors such as SIFT \cite{lowe2004distinctive}, SURF \cite{bay2006surf}, BRIEF \cite{calonder2012brief}, or ORB \cite{mur2015orb}.
-RANSAC \cite{fischler1981random} is the most widely used robust estimation technique to filter out outliers from the matches.
-The combination of RANSAC and hand-crafted feature descriptors has constituted the bulk of the matching literature for the last 40 years.
-Finally, graph matching \cite{suh2015subgraph, hu2016distributable} can be used as a final step for more robust matches.
-
-\subsection{Multi-image Matching}
-Multi-image matching has traditionally been done using optimization based methods minimizing a cycle consistency based loss (see Section 3.3).
-Pachauri et al.~\cite{pachauri2013solving} and Arrigoni et al.~\cite{arrigoni2017synchronization} use the eigenvectors of the matching matrix to obtain a low dimensional embedding. 
-However, the low Gaussian noise assumption is not realistic.
-Zhou et al.~\cite{zhou2015multi} and Wang et al.~\cite{wang2017multi} use most sophisticated optimization techniques on the matching matrix and thus produce more robust solutions.
-Leonardos et al.~\cite{leonardos2016distributed} implement a distributed optimization scheme to solve for cycle consistency.
-As an alternative to optimization based techniques, Tron et al.~\cite{tron2017fast} used density based clustering techniques to compute multi-image correspondence.
-To the best of our knowledge, we are the first to use neural networks for multi-image matching.
-
-\subsection{Deep Learning for Matching}
-Previous attempts to improve image matching techniques using machine learning have focused on learning the descriptors given ground truth correspondence from curated datasets \cite{zagoruyko2015learning, yi2016lift, brachmann2017dsac}.
-This approach is limited if one do not have the ability to get the ground truth correspondences.
-There are other methods to build correspondences such as Choy et al.~\cite{choy2016universal}, but they only handle two-view constraints and require dense correspondences.
-Most similar to our work, Yi et al.~\cite{yi2018learning} attempts to improve correspondences by learning match probabilities for RANSAC for greater robustness and speed.
-However, they only focus on two view matching and do not exploit the advantages of the correspondence structure.
-Note that while Zhu et al.~\cite{zhu2017unpaired} use cycle consistency in their loss, their method is restricted to pairwise cycle consistency, while we use multi-image cycle consistency.
-
-\subsection{Graph Neural Networks}
-Graph neural networks have recieved more attention recently \cite{bronstein2017geometric, bruna2013spectral, defferrard2016convolutional, kipf2017semi, scarselli2009graph, gama2018mimo, gama2018convolutional, battaglia2018relational}.
-Classical so-called Spectral methods used the eigenvectors of the graph Laplacian to compute convolutions as in Bruna et al.~\cite{bruna2013spectral}, but requires an a-priori known graph structure. 
-Non-spectral methods do not require a-priori knowledge \cite{bronstein2017geometric, kipf2017semi, scarselli2009graph, gama2018convolutional}.
-Most of these methods use polynomials of the graph Laplacian to compute neighborhood averages.
-Gama et al.~2018 \cite{gama2018mimo, gama2018convolutional} formalize this notion and generalize it beyond the use of the graph Laplacian.
-To improve performance, more sophisticated aggregation techniques and global information passing can be used as discussed in Battaglia et al.~\cite{battaglia2018relational}.
+We perform experiments on the Rome16K \cite{li2010location} dataset to test the effectiveness of our method compared to optimization based methods.
+% Our contributions in this work are:
+% \begin{itemize}
+% \item We use a novel architecture to address the multi-image feature matching problem using GNNs with graph embeddings.
+% \item We introduce an unsupervised cycle consistency loss that does not require labeled correspondences to train.
+% \item We demonstrate the effectiveness of geometric consistency losses in improving training.
+% \end{itemize}
 
 \section{Method}
+Our goal is to learn optimal features that capture multiple image views by filtering out noisy feature matches.
+An outline of our approach can be seen in figure \ref{fig:pipeline}.
+We formulate this problem in terms of the correspondence graph of the features.
 
-\begin{figure}[t]
-\begin{center}
-  \includegraphics[width=0.9\linewidth]{figures-UniverseOfFeatures-v2.pdf}
-\end{center}
-  \caption{
-    Illustration of the universe of features.
-    Each feature in each image corresponds to a 3D point in the scene.
-    We can construct cycle consistent embeddings of the features by mapping each one to the one-hot vector of its corresponding 3D point.
-    While there can be many features, there are fewer 3D points and thus this corresponds to a low rank factorization of the correspondence matrix.
-    Best viewed in color.
-  }
-\label{fig:universefeatures}
-\label{fig:onecol}
-\end{figure}
-Our goal is to learn optimal features that capture multiple image views by filtering out noisy feature matches.
-The input to our algorithm is a set of features and noisy correspondences, and the output is a new set of features where the pairwise similarities of these features correspond to the true matches.
-We do this by training the new set of feature embeddings to be cycle consistent.
-We formulate this problem in terms of the correspondence graph of the features.
-Vectors $\mat{x}$ and matrices $\mat{A}$ are denoted with boldface, and the $i^{th}$ row of a matrix is denoted $(\mat{A})_i$.
-Graphs $\mathcal{G} = (\mathcal{V}, \mathcal{E})$ have a set of vertices $\mathcal{V}$ and of edges $\mathcal{E} \subseteq \mathcal{V} \times \mathcal{V}$.
-Implicitly in the subsequent discussions we assume the edges are directed.
-For a vertex $v \in \mathcal{V}$ we use $\mathcal{N}^{h}(v)$ to denote the $h$-hop neighbors of $v$, with the superscript left out for 1-hop neighbors.
-Similarly $\mathcal{E}(v)$ is used to denote the edges associated with $v$.
-To denote the vertices connected to an edge $e \in \mathcal{E}$ we write $e(v_1, v_2)$.
-\subsection{Correspondence Graph}
 We assume there is an initial set of feature matches represented as a graph $\mathcal{G} = (\mathcal{V}, \mathcal{E})$, with an associated adjacency matrix $\mat{A}$.
-The graph is constructed from putative correspondences of image features across images, typically constructed using feature descriptor distance (e.g. SIFT feature distance).
-While there are many interesting methods for computing these putative correspondences \cite{suh2015subgraph, yi2018learning}, we do not explore them in this work.
-Typically putative correspondences are matched probabilistically, meaning a feature in one image matches to many features in another.
-The ambiguity in the matches could come from repeated structures in the scene, insufficiently informative low-level feature descriptors, or just an error in the matching algorithm.
-Filtering out these noisy matches is our primary learning goal.
-
 Each vertex of the graph $v \in \mathcal{V}$ is an image feature, corresponding to some ground truth 3D point $\mat{P}(v)$.
 Each edge $e = (v_1, v_2) \in \mathcal{E}$ is a potential correspondence.
-Associated with each vertex $v$ is an embedding $\mat{f}_v \in \bR^{m_0}$, which can include the visual feature descriptor, position, scale, orientation, etc.
-Similarly, each edge $e$ has an associated feature $\mat{f}_e \in \bR^{p_0}$ (in this work, initially just the weight of the feature association).
+The graph is constructed from putative correspondences of image features across images, typically constructed using feature descriptor distance (e.g. SIFT feature distance).
+Associated with each vertex $v$ is an embedding $\mat{f}_v \in \bR^m$, which can include the visual feature descriptor, position, scale, orientation, etc.
+Similarly, each edge $e$ has an associated feature $\mat{f}_e \in \bR^p$ (in this work, initially just the weight of the feature association).
 We use these features as the initialization for our learning algorithm.
@@
 In the absence of noise or outliers, this graph would have a connected component for each visible point in the world, all mutually disjoint.
-Without noise, vertices $v$ would only match with other vertices $v'$ that correspond to the same 3D point in the scene.
-Since features in this case represent unique locations in the scene, no points in the same image would have edges $e$ between them.
 Mathematically, this can be expressed as $e = (v_1, v_2) \in \mathcal{E} \implies \mat{P}(v_1) = \mat{P}(v_2)$.
-In the noisy case we expect this structure to be corrupted, i.e. there are some edges $e = (v_1, v_2) \in \mathcal{E}$ such that $\mat{P}(v_1) \neq \mat{P}(v_2)$.
-Thus we need to prune the erroneous edges.
+Typically putative correspondences are matched probabilistically, meaning a feature in one image matches to many features in another.
+Thus in the noisy case we expect this structure to be corrupted, i.e. there are some edges $e = (v_1, v_2) \in \mathcal{E}$ such that $\mat{P}(v_1) \neq \mat{P}(v_2)$.
 
-However, standard CNNs cannot operate on this general graph structure.
-Thus we cannot use standard convolutional nets to learn features for this task.
-Instead we use graph networks to learn feature representations on this space, which we describe in the next section.
-
-\subsection{Graph Neural Networks}
-As input to our method we are given a graph $\mathcal{G} = (\mathcal{V}, \mathcal{E})$ with the features described last section $\mat{f}_v \forall v \in \mathcal{V}$ and $\mat{f}_e \forall e in \mathcal{E}$.
-As with any neural network, GNNs have layered outputs.
-We describe the output of layer $k$ as $\mat{f}_v^{(k)} \forall v \in \mathcal{V}$ and $\mat{f}_e^{(k)} \forall e \in \mathcal{E}$, with the initial embeddings denoted $\mat{f}_v^{(0)} = \mat{f}_v^{(0)}$ and $\mat{f}_e^{(0)} = \mat{f}_e$.
-It will be useful to write these features as matrices in later sections, so we denote the vertex embedding matrix as $\mat{F}_V^{(k)}$ and the edge embedding matrix as $\mat{F}_E^{(k)}$.
-If a superscript is not specified then it refers to the final output of the network.
-
-First we describe older methods of GNNs to give context, then we describe the method we use in this work.
-Many older methods assume we have the adjacency matrix $\mat{A}$ of the graph known a-priori \cite{bruna2013spectral}, and can encode graph convolutions using the eigenvectors of $\mat{A}$.
-However, we do not have this luxury, as the correspondence structure changes from image set to image set, and thus we use non-spectral Graph Neural Networks.
-There are many variations on non-spectral methods, often which ultimately amount to message passing between vertices of the graph with learned non-linear transformations between various steps \cite{kipf2017semi, defferrard2016convolutional, gama2018mimo, gama2018convolutional}.
-Some works such as \cite{gama2019convolutional} use pooling operations on the vertices to make the graph smaller and thus aid computation, but as we need labels on every vertex of the original graph, so we cannot use this.
+While there are many methods for operating on graphs \cite{bronstein2017geometric, bruna2013spectral, defferrard2016convolutional, kipf2017semi, scarselli2009graph, gama2018mimo, gama2018convolutional, battaglia2018relational}
 Most of GNNs used in these works can be expressed mathematically as:
@@
 In \cite{battaglia2018relational}, they allow for more sophisticated aggregation functions, but in this work we simply use the mean function.
-In practice, we use MLPs between message passes between the vertices and edges for better expressiveness.
-
-\begin{figure}[t]
-\begin{center}
-  \includegraphics[width=0.8\linewidth]{figures-GeometricConsistency-v2.pdf}
-\end{center}
-  \caption{
-    Illustrated here is an example of how the geometric loss is computed for one feature.  
-    Errors are computed via absolute distance from the epipolar line, as expressed by (\ref{eq:essential_constraint}) via the epipolar constraint.
-    The epipolar line is the line of projection of the feature on the first image, projected onto to the second.
-    The distance to this line on the second image indicates how likely that point is to correspond geometrically to the original feature.
-    There can be false positives along the projected line, as shown by the square feature in the figure, but other points will be eliminated, such as the hexagonal feature.
-    Best viewed in color.
-  }
-\label{fig:geoconsist}
-\label{fig:onecol}
-\end{figure}
+In practice, we use MLPs in message passes between vertices and edges for better expressiveness
 
@@
 Stated in this form, there are $O(n^3)$ cycle consistency constraints to check.
-A more elegant way to represent cycle consistency is to first create a `universe' of features that all images match to (see figure \ref{fig:universefeatures}).
+A more elegant way to represent cycle consistency is to first create a `universe' of features that all images match to.
 Then, one can match the $i^{th}$ set of features to the universe using a ground-truth matching matrix $\mat{X}_i$.
@@
 Here $\mathcal{D}$ could be an $L_2$ loss, $L_1$ loss, or many others. In this work, we use the $L_1$ loss.
-Note that because of this formulation, we can determine our embeddings only up to a rotation, as
-\begin{equation}
-\mat{E}R(\mat{E}R)^\top
-= \mat{E}RR^\top\mat{E}^\top
-= \mat{E}\mat{E}^\top
-\label{eq:rotinvar}
-\end{equation}
-Thus when visualizing embeddings, we rotate them to make them more interpretable (see figure \ref{fig:embeddingsviz}).
 
@@
 The epipolar constraint describes how the positions of features in different images corresponding to the same point should be related.
-An illustration of this is provided in figure \ref{fig:geoconsist}, showing how this loss can help reject erroneous points.
-Given a relative pose $(R_{ij}, T_{ij})$ between two cameras $i$ and $j$  (transforms $j$ to $i$) the epipolar on corresponding feature locations $X_i$ and $X_j$:
+The epipolar constraint between two cameras $i$ and $j$  (transforms $j$ to $i$) on corresponding feature locations $X_{i,k}$ and $X_{j,l}$ is (derived in \cite{tron2014quotient}):
 \begin{equation}
-X_{i}^\top \cross{T_{ij}}R_{ij} X_{j} = 0
-\label{eq:essential_constraint_rel}
-\end{equation}
-In this work we use the two pose epipolar constraint \cite{tron2014quotient}:
-\begin{equation}
-X_{i}^\top R_{i}^\top \cross{T_{j} - T_{i}}R_{j} X_{j} = 0
+X_{i,k}^\top R_{i}^\top \cross{T_{j} - T_{i}}R_{j} X_{j,l} = 0
 \label{eq:essential_constraint}
 \end{equation}
-% Where the $(R_k, T_k)$ are the poses of cameras $i$ and $j$ respectively.
-The constraint assumes that the $X_k$ are calibrated i.e. the camera intrinsics are known. 
+The constraint assumes that the $X_k$ are calibrated (i.e. the camera intrinsics are known). 
 Given our vertex embeddings matrix $\mat{F}_V$, we can formulate a loss between all cameras $i$ and $j$:
 \begin{align} 
-&\mathcal{L}_{ij,geom}(\mat{F}_V) = \\ \nonumber
-&\sum_{v \in \mathcal{V}(i),u \in \mathcal{V}(j)} \sum_{} (\mat{f}_v \cdot \mat{f}_u) \left|X_{v}^\top R_{i}^\top \cross{T_{j} - T_{i}}R_{c_j} X_{u}\right|
-\label{eq:geom_cost}
-\end{align}
-With $\mathcal{V}(i)$ being the vertices associated with camera $i$.
-For our purposes, since we use low rank embeddings $\mat{E}_{i}$, $\mat{E}_{j}$, the loss would read:
-\begin{align}
 \mathcal{L}_{geom}(\mat{F}_V)
-=&\; \mathrm{tr}(\mat{G}^\top \mat{F}_V\mat{F}_V^\top) = \sum_{k,l} (\mat{F}_V)_{k} \cdot (\mat{F}_V)_{l} (\mat{G})_{kl} \\
+=&\; \mathrm{tr}(\mat{G}^\top \mat{F}_V\mat{F}_V^\top) = \sum_{k,l} (\mat{F}_V)_{k} \cdot (\mat{F}_V)_{l} (\mat{G})_{kl} \label{eq:geom_cost2} \\
 (\mat{G})_{kl} =&\; \left|X_{k}^\top R_{c(k)}^\top \cross{T_{c(l)} - T_{c(k)}}R_{c(l)} X_{l}\right| \nonumber
-\label{eq:geom_cost2}
 \end{align}
 Where $c(k)$ is the appropriate camera for point index $k$.
-
-%------------------------------------------------------------------------
-\section{Experiments}
-
-\begin{figure*}
-\begin{center}
-  % \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
-  \includegraphics[width=0.8\linewidth]{figures-ExampleOutput.pdf}
-  \end{center}
-     \caption{Example output of our network.
-(a) Similarity Matrix of the of the embeddings (b) Histogram of feature similarities for pairs which correspond to the same 3D point, comparing our output features with the original SIFT features (c) Histogram of feature similarities for pairs which correspond to different 3D points, comparing our output features with the original SIFT features}
-  \label{fig:short}
-\end{figure*}
-
-\subsection{Implementation Details}
-The network was implemented using the code provided by \cite{battaglia2018relational} using Tensorflow \cite{tensorflow2015} 1.11.
-Our network has 16 layers, with 8 message passing operations placed ever other layer.
-All layers were simple Multi-layer Perceptrons, with no batch norm.
-The network was trained with the Adam optimizer \cite{kingma2014adam} with a learning rate of $10^{-4}$, with an exponentially decaying learning rate.
-We incorporate skip connections between the input, $6^{th}$, and $12^{th}$ layers (all possible pairs).
-
-\subsection{Rome 16K Graph Dataset}
-We  use the Rome16K dataset \cite{li2010location} to test our algorithm in real world settings.
-Rome16K consists of 16 thousand images of various historical sites in Rome extracted from Flickr, along with the 3D structure of the sites provided by bundle adjustment.
-While not a standard dataset to test cycle consistency, other datasets had insufficient data to train a network on.
-Rome16K is typically used to test bundle adjustment methods.
-Therefore, to use our method, we extract image triplets and quadruplets with overlap of 80 points or more to test our algorithm, with the points established as corresponding in the given bundle adjustment output.
-For the initial embedding we use the original 128 dimensional SIFT descriptors, normalized to have unit $L_2$ norm, the calibrated x-y position, the orientation, and log scale of the SIFT feature.
-To construct the graph, we take each feature as a vertex and create an edge between the 5 nearest features in each other image in SIFT descriptor space.
-
-For these experiments we train with the $L_1$ norm and geometric consistency losses.
-We evaluate on a test set using the ground truth adjacency matrix, which we compute from the bundle adjustment given by the Rome16K dataset.
-We use the $L_1$ and ROC AUC metrics to measure performance.
-For this method to work, we need the dimension of the embedding to be at least the number of unique points in the scene.
-Picking the correct number is difficult a-priori, and is a problem with all cycle consistency based methods.
-Here we use the ground truth dimension of the embedding to test both our method and the baselines.
-
-% Our method performs better than nearly 
-We compare our method to spectral and optimization based baselines with different maximum iteration cutoffs.
-Our network, though only using 8 message passes, has comparable accuracy to MatchALS \cite{zhou2015multi} run 35 to 45 iterations, with an equivalent message passing step at each phase.
-Although our method does not outperform the Projected Gradient Descent - Doubly Stochastic (PGDDS) \cite{leonardos2016distributed} method, we perform comparably to them in the ROC AUC metric.
-% Our network, though only 12 layers, has comparable accuracy to MatchALS \cite{zhou2015multi} run between 25 and 50 iterations.
-% Additional comparisons to different iterations numbers of iterations can be found in the supplementary material.
 
@@
   % \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
-  \includegraphics[width=0.8\linewidth]{figures-error_lines.pdf}
+  \includegraphics[width=0.95\linewidth]{figures-error_lines-v2.pdf}
   \end{center}
@@
          The ROC AUC curves remain fairly consistent while the L1 loss goes noticibly down after more iterations.
-         Our method compares to 35-45 iterations of MatchALS, while only haveing 16 layers and 8 message passes.
-         PGDDS peforms better than us in $L_1$ but we peform similarly in the ROC AUC metric.
+         Our method compares to 35-45 iterations of MatchALS, while only having 16 layers and 8 message passes.
+         PGDDS performs better than us in $L_1$ but we perform similarly in the ROC AUC metric.
      }
@@
 
-\begin{figure}[t]
-\begin{center}
-  % \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
-  \includegraphics[width=0.8\linewidth]{figures-EmbeddingsViz.png}
-  \end{center}
-     \caption{
-         Visualization of the learned embeddings using Hinton diagrams \cite{bremner1994hinton}.
-         On the left we have the raw outputs, which are difficult to interpret.
-         On the right, we rotated the features to best match the ground truth for a more interpretable visualization.
-     }
-  \label{fig:onecol}
-  \label{fig:embeddingsviz}
-\end{figure}
-%------------------------------------------------------------------------
-\section{Conclusion}
+\subsubsection*{Acknowledgements}
+Support by ARL DCIST CRA W911NF-17-2-0181, NSF-IIS-1703319, ARL RCTA W911NF-10-2-0016, ONR N00014-17-1-2093, and the Honda Research Institute is gratefully acknowledged.
 
-We have shown a novel method for training feature matching using GNNs, using an unsupervised cycle consistency loss and geometric consistency losses.
-We have demonstrated has comparable the traditional optimization based baselines on a simple GNN, while still allowing for end-to-end training integration in deep learning pipelines.
-For future work, we will investigate robust losses for better outlier rejection, and using higher order geometric constraints, such as the tri-focal tensor, as additional loss terms.
-A long term goal is to incorporate learning image level features into this pipeline.
-Moreover we hope to adapt this method to a distributed setting, which would be a simple extention given current approach.
-% , but with group norm, we cannot distribute in its current form.
-
-% \subsubsection*{Acknowledgements}
-% Support by ARL DCIST CRA W911NF-17-2-0181, NSF-IIS-1703319, ARL RCTA W911NF-10-2-0016, ONR N00014-17-1-2093, and the Honda Research Institute is gratefully acknowledged.
-% 
 {\small

### 2019-06-12 latex/imw2019/main.tex
Added some things (very delayed git add) to the Image Matching Workshop

@@
 
-\usepackage{cvpr}
+\usepackage{mycvpr}
 \usepackage{times}
@@
 \begin{abstract}
-    Image feature matching is a fundamental part of many geometric computer vision applications, and using multiple images can improve performance.
-    In this work, we formulate multi-image matching as a graph embedding problem then use a Graph Neural Network to learn an appropriate embedding function for aligning image features.
-    We use cycle consistency to train our network in an unsupervised fashion, since ground truth correspondence is difficult or expensive to acquire.
-    In addition, geometric consistency losses can be added at training time, even if the information is not available in the test set, unlike previous approaches which optimize cycle consistency directly.
-    To the best of our knowledge, no other works have used learning for multi-image feature matching.
-    Our experiments show that our method is competitive with other optimization based approaches.
+%     Image feature matching is a fundamental part of many geometric computer vision applications, and using multiple images can improve performance.
+    We formulate multi-image matching as a graph embedding problem and then use a Graph Neural Network to learn an appropriate embedding function for aligning image features.
+    We use cycle consistency to train our network in an unsupervised fashion since ground truth correspondence is difficult or expensive to acquire.
+%     To the best of our knowledge, no other works have used learning for multi-image feature matching.
+%     Our experiments show that our method is competitive with other optimization based approaches.
 \end{abstract}
+% In addition, geometric consistency losses can be added at training time, even if the information is not available in the test set, unlike previous approaches which optimize cycle consistency directly.
+\vspace{-1em}
+
+\section{Introduction}
+Feature matching is an essential part of Structure from Motion and many geometric computer vision applications.
+The goal in multi-image feature matching is to take 2D image locations from three or more images and find which ones correspond to the same point in the 3D scene.
+Works such as Wang et al.~\cite{wang2017multi}, have shown improvement in performance by optimizing cycle consistency, i.e. enforcing the pairwise feature matches to be globally consistent.
+In this paper, we want to leverage the power of deep representations in order to learn feature descriptors that are robust across multiple views.
+
+% However, these multi-view consistency algorithms struggle in distributed and robust settings.
+% Having image features suited for this task would help improve performance, and deep learning has revolutionized how image features are computed \cite{yi2016lift}.
+
+In this work, we propose to training a Graph Neural Networks (GNNs) to operate directly on the sparse correspondence graph, allowing it to work in a broad class of environments.
+To the best of our knowledge this work is the first to apply deep learning to the multi-view feature matching problem.
+We use an unsupervised loss - the cycle consistency loss - to train the network, and thus avoiding the difficulty of expensive hand labeling.
+Geometric consistency losses can aid training, even if such information is not available at test time.
+We compare our method with optimization based methods using a matrix factorization loss \cite{zhou2015multi, leonardos2016distributed}.
+We perform experiments on the Rome16K \cite{li2010location} dataset to test the effectiveness of our method compared to optimization based methods.
+% Our contributions in this work are:
+% \begin{itemize}
+% \item We use a novel architecture to address the multi-image feature matching problem using GNNs with graph embeddings.
+% \item We introduce an unsupervised cycle consistency loss that does not require labeled correspondences to train.
+% \item We demonstrate the effectiveness of geometric consistency losses in improving training.
+% \end{itemize}
 
@@
   \caption{
-    An illustration of the approach of this work.
-    The Graph Neural Neural Network (GNN) \cite{battaglia2018relational} takes as input the graph of matches with vertex features and outputs an embedding over the vertices of the graph (represented by different colors in the figure).
-    The final embedding is used to construct a pairwise similarity matrix, which we train to be a low dimensional cycle-consistent representation of the graph adjacency matrix.
-    We train the network using a reconstruction loss on the similarity matrix with the noisy adjacency matrix, and geometric consistency information, such as epipolar constraints, to provide an unsupervised training method for the model.
+    The GNN \cite{battaglia2018relational} takes as input the graph of matches with vertex features and outputs an cycle consistent embedding over the vertices of the graph (represented by different colors in the figure).
   }
@@
 % \label{fig:onecol}
+\vspace{-1em}
 \end{figure}
 
-\section{Introduction}
-Feature matching is an essential part of Structure from Motion and many geometric computer vision applications.
-The goal in multi-image feature matching is to take 2D image locations from three or more images and find which ones correspond to the same point in the 3D scene.
-Works such as Wang et al.~\cite{wang2017multi}, have shown improvement in performance by optimizing cycle consistency, i.e. enforcing the pairwise feature matches to be globally consistent.
-
-However, these multi-view consistency algorithms struggle in distributed and robust settings.
-Having image features suited for this task would help improve performance, and deep learning has revolutionized how image features are computed \cite{yi2016lift}.
-In this paper, we want to leverage the power of deep representations in order to compute feature descriptors that are robust across multiple views.
-
-In this work, we propose to training a Graph Neural Networks (GNNs) to operate directly on the sparse correspondence graph, allowing it to work in a broad class of environments.
-To the best of our knowledge this work is the first to apply deep learning to the multi-view feature matching problem.
-We use an unsupervised loss - the cycle consistency loss - to train the network, and thus avoiding the difficulty of expensive hand labeling.
-Geometric consistency losses can aid training, even if such information is not available at test time.
-Although our network is simple, it shows promising results compared to baselines which optimize for cycle-consistency without learned embeddings, using a matrix factorization loss \cite{zhou2015multi, leonardos2016distributed}.
-Furthermore, since inference requires only a single forward pass over the neural network, our approach is faster (to achieve comparable accuracy) than methods which must solve an optimization problem every time.
-We perform experiments on the Rome16K \cite{li2010location} dataset to test the effectiveness of our method compared to optimization based methods.
-% Our contributions in this work are:
-% \begin{itemize}
-% \item We use a novel architecture to address the multi-image feature matching problem using GNNs with graph embeddings.
-% \item We introduce an unsupervised cycle consistency loss that does not require labeled correspondences to train.
-% \item We demonstrate the effectiveness of geometric consistency losses in improving training.
-% \end{itemize}
-
-\section{Method}
-Our goal is to learn optimal features that capture multiple image views by filtering out noisy feature matches.
-An outline of our approach can be seen in figure \ref{fig:pipeline}.
-We formulate this problem in terms of the correspondence graph of the features.
-
-We assume there is an initial set of feature matches represented as a graph $\mathcal{G} = (\mathcal{V}, \mathcal{E})$, with an associated adjacency matrix $\mat{A}$.
-Each vertex of the graph $v \in \mathcal{V}$ is an image feature, corresponding to some ground truth 3D point $\mat{P}(v)$.
-Each edge $e = (v_1, v_2) \in \mathcal{E}$ is a potential correspondence.
-The graph is constructed from putative correspondences of image features across images, typically constructed using feature descriptor distance (e.g. SIFT feature distance).
-Associated with each vertex $v$ is an embedding $\mat{f}_v \in \bR^m$, which can include the visual feature descriptor, position, scale, orientation, etc.
-Similarly, each edge $e$ has an associated feature $\mat{f}_e \in \bR^p$ (in this work, initially just the weight of the feature association).
-We use these features as the initialization for our learning algorithm.
-
-In the absence of noise or outliers, this graph would have a connected component for each visible point in the world, all mutually disjoint.
-Mathematically, this can be expressed as $e = (v_1, v_2) \in \mathcal{E} \implies \mat{P}(v_1) = \mat{P}(v_2)$.
-Typically putative correspondences are matched probabilistically, meaning a feature in one image matches to many features in another.
-Thus in the noisy case we expect this structure to be corrupted, i.e. there are some edges $e = (v_1, v_2) \in \mathcal{E}$ such that $\mat{P}(v_1) \neq \mat{P}(v_2)$.
-
-While there are many methods for operating on graphs \cite{bronstein2017geometric, bruna2013spectral, defferrard2016convolutional, kipf2017semi, scarselli2009graph, gama2018mimo, gama2018convolutional, battaglia2018relational}
-Most of GNNs used in these works can be expressed mathematically as:
-\begin{align*}
-\mat{\tilde{f}}_v^{(k+1)} =&\; b^{(k)} + \mat{W}_0^{k} \mat{f}_{v}^{(k)} + \sum_{h=0}^H \sum_{v' \in \mathcal{N}^{h}(v)} f_{e(v,v')} \mat{W}_{h}^{k} \mat{f}_{v'}^{(k)} \\
-\mat{f}_v^{(k+1)} =&\; \sigma\left(\mat{\tilde{f}}_v^{(k+1)}\right)
-\end{align*}
-The weights/biases $\mat{W}_{h}^{k}$, $b^{(k)}$ are all learned, with no learning done on the edge weights $f_{e(v,v')}$. 
-Note that this is just sums or averages over $h$-hop neighborhoods, where the weights on the edges remain static through the computation.
-Given that we are trying to prune edges, it would be sensible to add features over edges to learn which ones to prune and which to keep such as in \cite{scarselli2009graph}.
-
-Therefore, in this work we use the method and implementation described in \cite{battaglia2018relational} (more specifically repetitions of the architecture described in \cite{battaglia2016interaction}).
-This work is similar to previous works with one key difference: edges also have weights.
-Thus therefore there is intermediate processing on the edges before information is passed to the vertices.
-
-Mathematically, this is expressed as: % TODO: Maybe make this MLP oriented?
-\begin{align}
-\mat{\tilde{f}}_{e(v_1,v_2)}^{(k+1)} =&\; \mat{U}_1^{(k)} \mat{f}_{e}^{(k)} + \mat{U}_1^{(k)} \mat{f}_{v_1}^{(k)} + \mat{U}_2^{(k)} \mat{f}_{v_2}^{(k)} \\
-\mat{f}_{e(v_1,v_2)}^{(k+1)} =&\; \sigma \left(a^{(k)} + \mat{\tilde{f}}_{e(v_1,v_2)}^{(k+1)}\right) \\
-\mat{\tilde{f}}_{v}^{(k+1)} =&\; \mat{W}_0^{(k)} \mat{f}_{v}^{(k)} + \sum_{e \in \mathcal{E}(v)} \mat{W}_1^{(k)} \mat{f}_{e}^{(k+1)} \\
-\mat{f}_v^{(k+1)} =&\; \sigma\left(b^{(k)} + \mat{\tilde{f}}_v^{(k+1)}\right)
-\end{align}
-Here the learned weights are denoted $\mat{W}$ and $\mat{U}$, and the biases $a^{(k)}$ and  $b^{(k)}$.
-In \cite{battaglia2018relational}, they allow for more sophisticated aggregation functions, but in this work we simply use the mean function.
-In practice, we use MLPs in message passes between vertices and edges for better expressiveness
-
-\subsection{Cycle Consistency}
-
-Let $\mat{M}$ be the noiseless set of matches between our features, with $\mat{M}_{ij}$ being the matches between image $i$ and image $j$.
-If the pairwise matches are globally consistent, then we can say that, for all $i, j, k$:
-\begin{equation}
-\mat{M}_{ij} = \mat{M}_{ik} \mat{M}_{kj}
-\label{eq:cycconsist1}
-\end{equation}
-In other words, the matches between two images stay the same no matter what path is taken to get there. 
-This constraint is known as \textit{cycle consistency}, and has been used in a number of works to optimize for global consistency \cite{zhou2015multi, wang2017multi, leonardos2016distributed}.
-Stated in this form, there are $O(n^3)$ cycle consistency constraints to check.
-A more elegant way to represent cycle consistency is to first create a `universe' of features that all images match to.
-Then, one can match the $i^{th}$ set of features to the universe using a ground-truth matching matrix $\mat{X}_i$.
-Then the cycle consistency constraint becomes:
-\begin{equation}
-\mat{M}_{ij} = \mat{X}_{i}\mat{X}_{j}^\top
-\label{eq:cycconsist2}
-\end{equation}
-
-This reduces the number of our constraints from $O(n^3)$ to $O(n^2)$.
-We try to learn vertex embeddings $\mat{F}_V$ to approximate $\mat{X}$ - in other words the final embedding should be an encoding of the universe of features.
-As we do not have the ground truth matches $\mat{M}$, we approximate it using the noisy adjacency matrix $\mat{A}$ of our correspondence graph. Thus our loss would be 
-\begin{equation}
-\mathcal{L}(\mat{A}, \mat{F}_V) = \mathcal{D}(\mat{A}, \mat{F}_V \mat{F}_V^\top)
-\end{equation}
-Here $\mathcal{D}$ could be an $L_2$ loss, $L_1$ loss, or many others. In this work, we use the $L_1$ loss.
-
-\subsection{Geometric Consistency Loss}
-
-One of the main advantages of this approach over more traditional optimization based approaches is the ability to add geometric consistency information into the loss at training time, even if it is not available at test time.
-The simplest way to add geometric consistency losses, and the approach we use here, is to use the epipolar constraint.
-The epipolar constraint describes how the positions of features in different images corresponding to the same point should be related.
-The epipolar constraint between two cameras $i$ and $j$  (transforms $j$ to $i$) on corresponding feature locations $X_{i,k}$ and $X_{j,l}$ is (derived in \cite{tron2014quotient}):
-\begin{equation}
-X_{i,k}^\top R_{i}^\top \cross{T_{j} - T_{i}}R_{j} X_{j,l} = 0
-\label{eq:essential_constraint}
-\end{equation}
-The constraint assumes that the $X_k$ are calibrated (i.e. the camera intrinsics are known). 
-Given our vertex embeddings matrix $\mat{F}_V$, we can formulate a loss between all cameras $i$ and $j$:
-\begin{align} 
-\mathcal{L}_{geom}(\mat{F}_V)
-=&\; \mathrm{tr}(\mat{G}^\top \mat{F}_V\mat{F}_V^\top) = \sum_{k,l} (\mat{F}_V)_{k} \cdot (\mat{F}_V)_{l} (\mat{G})_{kl} \label{eq:geom_cost2} \\
-(\mat{G})_{kl} =&\; \left|X_{k}^\top R_{c(k)}^\top \cross{T_{c(l)} - T_{c(k)}}R_{c(l)} X_{l}\right| \nonumber
-\end{align}
-Where $c(k)$ is the appropriate camera for point index $k$.
-
-\begin{figure*}[t]
+\begin{figure*}[h]
 \begin{center}
@@
 
+\section{Method}
+Our goal is to learn optimal features that capture multiple image views by filtering out noisy feature matches.
+An outline of our approach can be seen in figure \ref{fig:pipeline}.
+We formulate this problem in terms of the correspondence graph of the features.
+
+We assume there is an initial set of feature matches represented as a graph $\mathcal{G} = (\mathcal{V}, \mathcal{E})$, with an associated adjacency matrix $\mat{A}$.
+Each vertex of the graph $v \in \mathcal{V}$ is an image feature, corresponding to some ground truth 3D point $\mat{P}(v)$.
+Each edge $e = (v_1, v_2) \in \mathcal{E}$ is a potential correspondence.
+The graph is constructed from putative correspondences of image features across images, typically constructed using feature descriptor distance (e.g. SIFT feature distance).
+Each vertex $v$ and edge $e$ has an embedding $\mat{f}_v \in \bR^m$ and $\mat{f}_e \in \bR^p$, (e.g. SIFT Descriptor and distances).
+
+In the absence of noise or outliers, this graph would have a connected component for each visible point in the world, all mutually disjoint.
+Mathematically, this can be expressed as $e = (v_1, v_2) \in \mathcal{E} \implies \mat{P}(v_1) = \mat{P}(v_2)$.
+Typically putative correspondences are matched probabilistically, meaning a feature in one image matches to many features in another.
+Thus in the noisy case we expect this structure to be corrupted, i.e. there are some edges $e = (v_1, v_2) \in \mathcal{E}$ such that $\mat{P}(v_1) \neq \mat{P}(v_2)$.
+
+While there are many types of GNNs \cite{bronstein2017geometric, bruna2013spectral, defferrard2016convolutional, kipf2017semi, scarselli2009graph, gama2018mimo, gama2018convolutional} we use the method and code from \cite{battaglia2018relational} (more specifically repetitions of the architecture described in \cite{battaglia2016interaction}).
+The model we use can be expressed mathematically as:
+\begin{align}
+\mat{\tilde{f}}_{e(v_1,v_2)}^{(k+1)} =&\; \mat{U}_1^{(k)} \mat{f}_{e}^{(k)} + \mat{U}_1^{(k)} \mat{f}_{v_1}^{(k)} + \mat{U}_2^{(k)} \mat{f}_{v_2}^{(k)} \\
+\mat{f}_{e(v_1,v_2)}^{(k+1)} =&\; \sigma \left(a^{(k)} + \mat{\tilde{f}}_{e(v_1,v_2)}^{(k+1)}\right) \\
+\mat{\tilde{f}}_{v}^{(k+1)} =&\; \mat{W}_0^{(k)} \mat{f}_{v}^{(k)} + \sum_{e \in \mathcal{E}(v)} \mat{W}_1^{(k)} \mat{f}_{e}^{(k+1)} \\
+\mat{f}_v^{(k+1)} =&\; \sigma\left(b^{(k)} + \mat{\tilde{f}}_v^{(k+1)}\right)
+\end{align}
+Here the learned weights are denoted $\mat{W}$ (for the vertices) and $\mat{U}$ (for the edges), and the biases $a^{(k)}$ and  $b^{(k)}$.
+The learned weights on the edges allow the network to express which edges are valuable to keep and which are not.
+
+\subsection{Losses}
+
+We earlier described a necessary condition for a graph to be globally consistent, $e = (v_1, v_2) \in \mathcal{E} \implies \mat{P}(v_1) = \mat{P}(v_2)$.
+Another way to describe this is that matching a feature to another image must be path independent in the graph of matches.
+This constraint is known as \textit{cycle consistency}, and has been used in a number of works to optimize for global consistency \cite{zhou2015multi, wang2017multi, leonardos2016distributed}.
+Naively, there are $O(n^3)$ cycle consistency constraints to check, however a more elegant way to represent cycle consistency is to first create a `universe' of features that all images match to i.e.
+the 3D points, reducing the number of constraints to $O(n^2)$.
+Then, one can match the $i^{th}$ set of features to the universe using a ground-truth matching matrix $\mat{X}_i$.
+As we do not have the ground truth matches $\mat{M}$ or embeddings $\mat{X}$, we approximate the matches using the noisy adjacency matrix $\mat{A}$ of our correspondence graph and the matches with the learned representation $\mat{F}_V$.
+Then the cycle consistency loss becomes:
+\begin{equation}
+\mathcal{L}(\mat{A}, \mat{F}_V) = \mathcal{D}(\mat{A}, \mat{F}_V \mat{F}_V^\top)
+\end{equation}
+Here $\mathcal{D}$ could be an $L_2$ loss, $L_1$ loss, or many others. In this work, we use the $L_1$ loss.
+
+% The epipolar constraint describes how the positions of features in different images corresponding to the same point should be related.
+One of the main advantages of this approach over more traditional optimization based approaches is the ability to add geometric consistency information into the loss at training time, even if it is not available at test time.
+The simplest way to add geometric consistency losses, and the approach we use here, is to use the epipolar constraint between two cameras $i$ and $j$ on corresponding calibrated feature locations $X_{i,k}$ and $X_{j,l}$ is (derived in \cite{tron2014quotient}) shown in \ref{eq:epipolar}.
+Given our vertex embeddings matrix $\mat{F}_V$, we can formulate a loss between all cameras:
+\begin{align} 
+\mathcal{L}_{geom}(\mat{F}_V)
+=&\; \sum_{k,l} (\mat{F}_V)_{k} \cdot (\mat{F}_V)_{l} (\mat{G})_{kl} \label{eq:geom_cost2} \\
+(\mat{G})_{kl} =&\; \left|X_{k}^\top R_{c(k)}^\top \cross{T_{c(l)} - T_{c(k)}}R_{c(l)} X_{l}\right| \label{eq:epipolar}
+\end{align}
+Where $c(k)$ is the appropriate camera for point index $k$.
+
+\subsection{Rome 16K Graph Dataset}
+We  use the Rome16K dataset \cite{li2010location} to test our algorithm in real world settings.
+Rome16K consists of 16 thousand images of various historical sites in Rome extracted from Flickr, along with the 3D structure of the sites provided by bundle adjustment.
+While not a standard dataset to test cycle consistency, other datasets had insufficient data to train a network on.
+For these experiments we train with the $L_1$ norm and geometric consistency losses.
+We evaluate on a test set using the ground truth adjacency matrix, which we compute from the bundle adjustment given by the Rome16K dataset.
+We compare our method to spectral and optimization based baselines with different maximum iteration cutoffs.
+Figure \ref{fig:errorlines} illustrates this by plotting the means of various metrics and their $25^{th}$ and $75^{th}$ percentiles.
+
 \subsubsection*{Acknowledgements}

### 2019-06-12 data_util/rome16k/__main__.py
Fixed up tuple generation somewhat but needs to convert to non-pickle format

@@ -2,7 +2,6 @@ import numpy as np
 import os
 import sys
 import argparse
-import pickle
 import tqdm
 import time
 import itertools as it
@@ -17,7 +16,7 @@ def get_build_scene_opts():
   parser.add_argument('--build_tuples',
                       type=myutils.str2bool,
                       default=True,
-                      help='Name of pickle file to load - None if no loading')
+                      help=' None if no loading')
   parser.add_argument('--save_imsizes',
                       type=myutils.str2bool,
                       default=True,
@@ -28,11 +27,11 @@ def get_build_scene_opts():
                       help='If tuple file exists, overwrite it')
   parser.add_argument('--top_dir',
                       default='/NAS/data/stephen/Rome16K',
-                      help='Storage location for pickle files')
+                      help='Storage location for storage files')
   parser.add_argument('--save',
                       choices=parse.bundle_files + [ 'all' ],
                       default='all',
-                      help='Save out bundle file to pickle file')
+                      help='Save out bundle file to numpy file')
   parser.add_argument('--min_points',
                       default=80,
                       type=int,
@@ -66,7 +65,13 @@ def choose(n, k):
 def silent(x):
   pass
 
-def process_scene_bundle(opts, bundle_file, scene_fname, tuples_fname):
+def tuples_fname(opts, bundle_file, k):
+  return os.path.join(opts.top_dir,
+                      'tuples',
+                      '{:02d}'.format(k),
+                      parse.tuples_fname(bundle_file))
+
+def process_scene_bundle(opts, bundle_file, scene_fname):
   if opts.verbose > 0:
     myprint = lambda x: print(x)
   else:
@@ -83,8 +88,6 @@ def process_scene_bundle(opts, bundle_file, scene_fname, tuples_fname):
   ######### Build and save out k-tuples ###########
   n = len(scene.cams)
   cam_pts = lambda i: set([ f.point for f in scene.cams[i].features ])
-  tuples_full = []
-  tuples_sizes = []
   # Length 2 is a special case
   myprint("Building pairs...")
[…]

### 2019-06-12 data_util/rome16k/parse.py

@@ -97,7 +97,10 @@ def get_image_size(imname):
   url_ = URL_STR.format(photoid)
   ret = requests.get(url_)
   PARSER.feed(ret.text)
-  im_ = requests.get(PARSER.image_url)
+  try:
+    im_ = requests.get(PARSER.image_url)
+  except:
+    return (0,0)
   image = Image.open(io.BytesIO(im_.content))
   return image.size
 

### 2019-06-12 latex/iccv2019/rebuttal/egrebuttal.tex
Start of ICCV rebuttal

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{iccv_rebuttal}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

%%%%%%%%% PAPER ID  - PLEASE UPDATE
\def\iccvPaperID{****} % *** Enter the ICCV Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

\begin{document}

%%%%%%%%% TITLE - PLEASE UPDATE
\title{\LaTeX\ Guidelines for Author Response}  % **** Enter the paper title here

\maketitle
\thispagestyle{empty}

%%%%%%%%% BODY TEXT - ENTER YOUR RESPONSE BELOW
\section{Introduction}
Thank you to all the reviewers for all of your constructive comments and feedback.
We will fix all the minor typos and misunderstandings you have pointed out. 
We hope to point out the more important points here.
% Thank you to all the reviewers for all of your constructive comments and feedback. We fully understand your concerns and we elaborate on them here. We kindly ask you to trust us that the presentation will be clear in the camera-ready and to reward the novelty of the idea in your ratings.

%-------------------------------------------------------------------------
\subsection{Reviewer 1}
\textit{Things are not what they seem}: This is an ominous quote that makes things appear much more dramatic.

%------------------------------------------------------------------------
\subsection{Reviewer 2}
\textit{So it has come to this}: This is another ominous quote that while basically vacuous makes everything appear much more dramatic.

%------------------------------------------------------------------------
\subsection{Reviewer 3}
\textit{So it begins}: This also is an ominous quote that applies to most beginnings but makes things appear much more dramatic.

% \begin{figure}[t]
% \begin{center}
% \fbox{\rule{0pt}{1.8in} \rule{0.9\linewidth}{0pt}}
%    %\includegraphics[width=0.8\linewidth]{egfigure.eps}
% \end{center}
%    \caption{Example of caption.  It is set in Roman so that mathematics
%    (always set in Roman: $B \sin A = A \sin B$) may be included without an
%    ugly clash.}
% \label{fig:long}
% \label{fig:onecol}
% \end{figure}

{\small
\bibliographystyle{ieee}
\bibliography{egbib}
}

\end{document}

### 2019-06-12 latex/iccv2019/rebuttal/egrebuttal.tex
More added to rebuttal

@@
 %%%%%%%%% BODY TEXT - ENTER YOUR RESPONSE BELOW
-\section{Introduction}
 Thank you to all the reviewers for all of your constructive comments and feedback.
-We will fix all the minor typos and misunderstandings you have pointed out. 
-We hope to point out the more important points here.
+We will fix all minor typos. 
+We hope to address the more important points of criticism here.
 % Thank you to all the reviewers for all of your constructive comments and feedback.
@@
 %-------------------------------------------------------------------------
-\subsection{Reviewer 1}
-\textit{Things are not what they seem}: This is an ominous quote that makes things appear much more dramatic.
+% \textit{Things are not what they seem}: This is an ominous quote that makes things appear much more dramatic.
+\textbf{(R1)}
+\textit{The network is evaluated on generated synthetic data and on triplets and quadruplets of real data from the Rome 16K dataset}, and
+\textit{The only experiments described are on randomly generated synthetic data an on image triplets and quadruplets of real data}, and
+\textit{Moreover, the experiments are limited.}
+:
+This was an unfortunate misunderstanding.
+There was a mistake written on line 700 where we wrote `triplets and quadruplets' instead of `6-tuples and 10-tuples'.
+If you look at Figures 5 and 6 and Table 2, you can see we correctly label them as 6 and 10 views, and thus our method works are larger scales than what the typo would imply.
+
+\textbf{(R1)} \textit{The very related approach: Disambiguating visual relations using loop constraints, Zach et al. CVPR 2010, is not discussed}:
+This paper seems to be focusing on pose graph optimization and thus we overlooked it.
+We will cite it should this in the final version paper.
+
+\textbf{(R1)} \textit{There has been earlier work which used more than than two images such as, Learning Dense Correspondence via 3D-guided Cycle Consistency, Zhou et al. CVPR 2016}:
+We should have cited this, however this work \cite{zhou2016learning} to our understanding only does cycle consistency between two images, using ground truth CAD models to gain longer cycles.
+They never do cycle consistency on more than two images.
+
+\textbf{(R1)} \textit{I feel that this statement is a bit broad and might be overstating the contribution, works such as "LIFT: Learned Invariant Feature Transform" or "Learned Multi-Patch Similarity" seem to already tackle some aspects of this problem}:
+% We are sorry we did not make this clearer.
+What is meant by this is that this is the first algorithm we know of learning the matching algorithm itself on sparse features (not too clear with our language) on more than 2 images (hence multi-image).
+LIFT \cite{yi2016lift} clearly does feature matching, and thus we cite it, however it only does pairwise image matching.
+You are correct in that we did not cite Multi-patch similarity \cite{hartmann2017learned} learned mutli-patch similarity, indeed an important contribution, and we will cite it in the paper.
+We will reword it to say `To the best of our knowledge this work is the first to apply Graph Neural Networks to the sparse feature matching problem on more than 2 images'.
+% TODO: That paper only has 19 citations which is why we did not find it but it does pre-date us. Drat
+
+\textbf{(R1)} \textit{It is not very clear how this approach can be used to improve geometric computer vision problems such as SfM as mentioned in the introduction} and \textbf{(R3)} \textit{It would be nice to see how the proposed algorithm can benefit many practical computer vision tasks, such as 3D reconstruction using SfM}:
+We feel this can be used in existing SfM pipelines before bundle adjustment to improve matching.
+Also it can be used to improve works such as \cite{zhu2015single} for reconstruction using semantic features in an end to end fashion.
+We hope to address this more fully with future work, and integrate it into a SfM pipeline.
 
 %------------------------------------------------------------------------
-\subsection{Reviewer 2}
-\textit{So it has come to this}: This is another ominous quote that while basically vacuous makes everything appear much more dramatic.
+% \textit{So it has come to this}: This is another ominous quote that while basically vacuous makes everything appear much more dramatic.
+\textbf{(R2)} \textit{Line 417 says "we use the mean function" and "we use MLPs" but it is unclear how that corresponds to the equations above.
+At least in the supplemental material, they should prove a more precise and complete explanation of the neural network architecture}:
+Indeed the sentence you specify could be made clearer and we can add more detail in the paper and supplemental material to make it clearer.
+
+\textbf{(R2)} \textit{The matching matrices M in Equation 5 are not explained -- one has to read the related work in order to understand what they are} and \textit{Also, Equation 5 is only valid if all 3D points are visible in all views under consideration}:
+We can more clearly define the matching matrices.
+And Equation 5 can hold more generally if you allow rows of all zeros for places where there are no matches.
+However this is not made clear, and we will clarify it more when we clarify our language about the matching matrices.
+
+\textbf{(R2)} \textit{ Line 517 mentions $E_i$, $E_j$ but they are not used in Equation 12?}:
+No that is just a typo, thank you for catching it.
 
 %------------------------------------------------------------------------
-\subsection{Reviewer 3}
-\textit{So it begins}: This also is an ominous quote that applies to most beginnings but makes things appear much more dramatic.
+% \textit{So it begins}: This also is an ominous quote that applies to most beginnings but makes things appear much more dramatic.
+\textbf{(R3)} \textit{If we only look at a local image patch, without global/geometric constraints, there might exist multiple valid matches for a candidate patches ...
+How does the proposed GNN method handle such cases?}:
+This is where the Geometric Consistency Loss would come in, as it would disambiguate such features.
+However, if such geometric information is not available then we could learn features with more information about the intra-image feature matches.
+This could help disambiguate visually similar features within the same image, and is a direction we are working on now.
 

### 2019-06-24 latex/iccv2019/rebuttal/egrebuttal.tex
Rebuttal draft 3

@@
 %%%%%%%%% TITLE - PLEASE UPDATE
-\title{\LaTeX\ Guidelines for Author Response}  % **** Enter the paper title here
+\title{Rebuttal to ``All Graphs Lead to Rome''}  % **** Enter the paper title here
 
@@
 This paper seems to be focusing on pose graph optimization and thus we overlooked it.
-We will cite it should this in the final version paper.
+We will cite it in the final version paper.
 
 \textbf{(R1)} \textit{There has been earlier work which used more than than two images such as, Learning Dense Correspondence via 3D-guided Cycle Consistency, Zhou et al. CVPR 2016}:
-We should have cited this, however this work \cite{zhou2016learning} to our understanding only does cycle consistency between two images, using ground truth CAD models to gain longer cycles.
+We should have cited this.
+However this work \cite{zhou2016learning} to our understanding only does cycle consistency between two images, using ground truth CAD models to gain longer cycles.
 They never do cycle consistency on more than two images.
@@
 LIFT \cite{yi2016lift} clearly does feature matching, and thus we cite it, however it only does pairwise image matching.
-You are correct in that we did not cite Multi-patch similarity \cite{hartmann2017learned} learned mutli-patch similarity, indeed an important contribution, and we will cite it in the paper.
-We will reword it to say `To the best of our knowledge this work is the first to apply Graph Neural Networks to the sparse feature matching problem on more than 2 images'.
+You are correct in that we did not cite `Learned Multi-patch Similarity' \cite{hartmann2017learned}, which is an important step for our research question, so we will cite it in the paper.
+We will update the referenced sentence in the paper to say `To the best of our knowledge, this work is the first to apply Graph Neural Networks to the sparse feature matching problem on more than 2 images'.
 % TODO: That paper only has 19 citations which is why we did not find it but it does pre-date us. Drat
@@
 At least in the supplemental material, they should prove a more precise and complete explanation of the neural network architecture}:
-Indeed the sentence you specify could be made clearer and we can add more detail in the paper and supplemental material to make it clearer.
+Indeed the sentence you specify could be made clearer and we can add more detail in the paper and supplemental material to make it clearer, adding details on layer and filter sizes.
+When we say `we use the mean function', we mean that to aggregate the edge features into the node features we just take the mean of the transformed features as opposed to for example max.
+What we mean by `we use MLPs' is instead of taking a linear transformation of the node and edge embeddings between passes, we could learn a nonlinear transform using MLP.
 
@@
 This is where the Geometric Consistency Loss would come in, as it would disambiguate such features.
-However, if such geometric information is not available then we could learn features with more information about the intra-image feature matches.
+We will make this more explicit in the paper.
+In cases where such geometric information is not available, we could learn features with more information about the intra-image feature matches.
 This could help disambiguate visually similar features within the same image, and is a direction we are working on now.
@@
 
-{\footnotesize
+% {\footnotesize
+{\tiny
 \bibliographystyle{ieee}

### 2019-06-24 data_util/rome16k/__main__.py
Added updates to tuples (still need some debugging)

@@ -100,12 +100,11 @@ def process_scene_bundle(opts, bundle_file, scene_fname):
   end_time = time.time()
   myprint("Done with pairs ({} sec)".format(end_time-start_time))
   myprint("Saving pairs...")
-  tuples = [ (x, tsizes[i]) for i, x in enumerate(pairs) ]
   tfname = tuples_fname(opts, bundle_file, 2)
   if not os.path.exists(os.path.dirname(tfname)):
     os.makedirs(os.path.dirname(tfname))
   with open(tuples_fname(opts, bundle_file, 2), 'wb') as f:
-    pickle.dump(tuples, f, protocol=pickle.HIGHEST_PROTOCOL)
+    np.save(f, np.array(pairs))
   # Length 3 and above
   tlist = pairs
   for k in range(3,opts.max_tuple_size+1):
@@ -125,12 +124,11 @@ def process_scene_bundle(opts, bundle_file, scene_fname):
     end_time = time.time()
     myprint("Done with {}-tuples ({} sec)".format(k, end_time-start_time))
     myprint("Saving {}-tuples...".format(k))
-    tuples = [ (x, tsizes[i]) for i, x in enumerate(tlist) ]
     tfname = tuples_fname(opts, bundle_file, k)
     if not os.path.exists(os.path.dirname(tfname)):
       os.makedirs(os.path.dirname(tfname))
     with open(tuples_fname(opts, bundle_file, k), 'wb') as f:
-      pickle.dump(tuples, f, protocol=pickle.HIGHEST_PROTOCOL)
+      np.save(f, np.array(tlist).astype(np.uint16))
   # Final save of Tuples
   myprint("Done")
 

### 2019-06-24 data_util/rome16k/parse.py

@@ -124,12 +124,12 @@ def triplets_name(bundle_file, lite=False):
   else:
     return 'triplets.{}.pkl'.format(bundle_file)
 
-def tuples_fname(bundle_file):
+def tuples_fname(bundle_file, ext='npy'):
   if not check_valid_name(bundle_file):
     print("ERROR: Specified bundle file does not exist: {}".format(bundle_files))
     sys.exit(1)
   else:
-    return 'tuples.{}.pkl'.format(bundle_file)
+    return 'tuples.{}.{}'.format(bundle_file, ext)
 
 # Main parsing functions
 def parse_sift_gzip(fname):

### 2019-06-24 data_util/spreal_dataset.py

@@ -6,7 +6,6 @@ import glob
 import datetime
 import random
 import tqdm
-import pickle
 import networkx as nx
 
 import tensorflow as tf
@@ -51,6 +50,7 @@ class Rome16KGraphDataset(graph_dataset.GraphDataset):
   def tuples_fname(self, bundle_file):
     return os.path.join(self.rome16k_dir, 'scenes', parse.tuples_fname(bundle_file))
 
+  # TODO: NEED TO FIX ALL OF THIS
   def get_tuple_file_sizes(self):
     print("Extracting tuples...")
     tuple_file_sizes = { 'train': {}, 'test': {} }
@@ -58,7 +58,7 @@ class Rome16KGraphDataset(graph_dataset.GraphDataset):
       for bundle_file in bundle_files:
         fname = self.tuples_fname(bundle_file)
         with open(fname, 'rb') as f:
-          ld = pickle.load(f)
+          ld = np.load(f)
         tuple_file_sizes[mode][bundle_file] = \
             { i+2: len(x) for i, x in enumerate(ld) }
     print(tuple_file_sizes)
@@ -77,7 +77,7 @@ class Rome16KGraphDataset(graph_dataset.GraphDataset):
     all_tuples = []
     for bundle_file in bundle_files:
       with open(self.tuples_fname(bundle_file), 'rb') as f:
-        tuples_ = pickle.load(f)
+        tuples_ = np.load(f)
       all_tuples.extend(
         [ (bundle_file, tupl) for tupl in tuples_[tsize-2] ]
       )

### 2019-06-24 latex/iccv2019/rebuttal/egrebuttal.tex
Rebuttal draft 4

@@
 \textbf{(R1)}
-\textit{The network is evaluated on generated synthetic data and on triplets and quadruplets of real data from the Rome 16K dataset}, and
-\textit{The only experiments described are on randomly generated synthetic data an on image triplets and quadruplets of real data}, and
-\textit{Moreover, the experiments are limited.}
-:
+\textit{The network is evaluated \ldots triplets and quadruplets of real data from the Rome 16K dataset} (and related comments):
 This was an unfortunate misunderstanding.
 There was a mistake written on line 700 where we wrote `triplets and quadruplets' instead of `6-tuples and 10-tuples'.
-If you look at Figures 5 and 6 and Table 2, you can see we correctly label them as 6 and 10 views, and thus our method works are larger scales than what the typo would imply.
+In Figures 5 and 6 and Table 2, you can see we correctly label them as 6 and 10 views, and thus our method works are larger scales than what the typo would imply.
 
-\textbf{(R1)} \textit{The very related approach: Disambiguating visual relations using loop constraints, Zach et al. CVPR 2010, is not discussed}:
+\textbf{(R1)} \textit{Zach et al. CVPR 2010} \cite{zach2010disambiguating}:
 This paper seems to be focusing on pose graph optimization and thus we overlooked it.
 We will cite it in the final version paper.
+% More
 
-\textbf{(R1)} \textit{There has been earlier work which used more than than two images such as, Learning Dense Correspondence via 3D-guided Cycle Consistency, Zhou et al. CVPR 2016}:
+\textbf{(R1)} \textit{Zhou et al. CVPR 2016} (\cite{zhou2016learning}):
 We should have cited this.
 However this work \cite{zhou2016learning} to our understanding only does cycle consistency between two images, using ground truth CAD models to gain longer cycles.
-They never do cycle consistency on more than two images.
+While methodology wise this paper also uses cycle consistency, they learn cycle consistency though CAD models, while our enforces cycle consistent features through multiple views.
+% They never do cycle consistency on more than two images.
 
-\textbf{(R1)} \textit{I feel that this statement is a bit broad and might be overstating the contribution, works such as "LIFT: Learned Invariant Feature Transform" or "Learned Multi-Patch Similarity" seem to already tackle some aspects of this problem}:
+\textbf{(R1)} \textit{works such as "LIFT: Learned Invariant Feature Transform" or "Learned Multi-Patch Similarity"}:
 % We are sorry we did not make this clearer.
-What is meant by this is that this is the first algorithm we know of learning the matching algorithm itself on sparse features (not too clear with our language) on more than 2 images (hence multi-image).
 LIFT \cite{yi2016lift} clearly does feature matching, and thus we cite it, however it only does pairwise image matching.
 You are correct in that we did not cite `Learned Multi-patch Similarity' \cite{hartmann2017learned}, which is an important step for our research question, so we will cite it in the paper.
-We will update the referenced sentence in the paper to say `To the best of our knowledge, this work is the first to apply Graph Neural Networks to the sparse feature matching problem on more than 2 images'.
 % TODO: That paper only has 19 citations which is why we did not find it but it does pre-date us. Drat
 
-\textbf{(R1)} \textit{It is not very clear how this approach can be used to improve geometric computer vision problems such as SfM as mentioned in the introduction} and \textbf{(R3)} \textit{It would be nice to see how the proposed algorithm can benefit many practical computer vision tasks, such as 3D reconstruction using SfM}:
+\textbf{(R1)} \textit{It is not very clear how this approach can be used to improve \ldots SfM} and \textbf{(R3)} \textit{It would be nice to see \ldots 3D reconstruction using SfM}:
 We feel this can be used in existing SfM pipelines before bundle adjustment to improve matching.
-Also it can be used to improve works such as \cite{zhu2015single} for reconstruction using semantic features in an end to end fashion.
+However this work shows more promise in reconstructing semantic features as in \cite{wang2017multi}, but using pixels directly.
 We hope to address this more fully with future work, and integrate it into a SfM pipeline.
+
+\textbf{(R1)} \textit{Also the contribution of the submission seems a bit overstated}:
+We will be careful to not overstate the contributions in camera-ready paper.
+What is meant by this is that this is the first algorithm we know of learning the matching algorithm itself on sparse features (not too clear with our language) on more than 2 images.
+We will update the referenced sentence in the paper to say `To the best of our knowledge, this work is the first to apply Graph Neural Networks to the sparse feature matching problem on more than 2 images'.
+None of the reviewers have doubted the novelty of learning representations through correspondence and geometric constraints.
 
@@
 % \textit{So it has come to this}: This is another ominous quote that while basically vacuous makes everything appear much more dramatic.
-\textbf{(R2)} \textit{Line 417 says "we use the mean function" and "we use MLPs" but it is unclear how that corresponds to the equations above.
-At least in the supplemental material, they should prove a more precise and complete explanation of the neural network architecture}:
-Indeed the sentence you specify could be made clearer and we can add more detail in the paper and supplemental material to make it clearer, adding details on layer and filter sizes.
-When we say `we use the mean function', we mean that to aggregate the edge features into the node features we just take the mean of the transformed features as opposed to for example max.
+\textbf{(R2)} \textit{"we use the mean function" and "we use MLPs" but it is unclear \ldots}
+When we say `we use the mean function', we mean that to aggregate the edge features into the node features we just take the mean of the transformed features as opposed to the maximum.
 What we mean by `we use MLPs' is instead of taking a linear transformation of the node and edge embeddings between passes, we could learn a nonlinear transform using MLP.
 
+\textbf{(R2)} \textit{\ldots more precise and complete explanation of the neural network architecture}:
+Indeed the sentence you specify could be made clearer and we can add more detail in the paper and supplemental material to make it clearer, adding details on layer and filter sizes.
+Right now we use 6 message passes through between the node and edge features, with the number of hidden nodes starting at 32 and doubling until flattening at 256.
+Between each message pass we process the features with a 2 layer MLP.
+
 \textbf{(R2)} \textit{The matching matrices M in Equation 5 are not explained -- one has to read the related work in order to understand what they are} and \textit{Also, Equation 5 is only valid if all 3D points are visible in all views under consideration}:
-We can more clearly define the matching matrices.
-And Equation 5 can hold more generally if you allow rows of all zeros for places where there are no matches.
+We will more clearly define the matching matrices.
+Equation 5 can hold more generally if you allow rows of all zeros for places where there are no matches.
 However this is not made clear, and we will clarify it more when we clarify our language about the matching matrices.
 
-\textbf{(R2)} \textit{ Line 517 mentions $E_i$, $E_j$ but they are not used in Equation 12?}:
+\textbf{(R2)} \textit{$E_i$, $E_j$ but they are not used in Equation 12?}:
 No that is just a typo, thank you for catching it.
@@
 This could help disambiguate visually similar features within the same image, and is a direction we are working on now.
+
+\textbf{(R3)} \textit{it seems that PGDDS is both faster and more accurate in their tests, even for 15 iterations.}
+As we know from one pass inference on graph or geometry problems, it is difficult to outperform multi-iteration optimization methods.
+The advantage our method has is allowing for end-to-end training to allow learning features on pixels directly, a direction we hope to pursue in future work.
+PGDDS also uses many optimizations between passes through the graph, so in future work we could use methods like OptNet \cite{amos2017optnet} to help improve performance.
 

### 2019-07-01 latex/iccv2019/rebuttal/egrebuttal.tex
Fixed rebuttal (forgot to commit earlier)

--- 2019-06-24 latex/iccv2019/rebuttal/egrebuttal.tex
@@
 %%%%%%%%% PAPER ID  - PLEASE UPDATE
-\def\iccvPaperID{****} % *** Enter the ICCV Paper ID here
+\def\iccvPaperID{4115} % *** Enter the ICCV Paper ID here
 \def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
@@
 %%%%%%%%% BODY TEXT - ENTER YOUR RESPONSE BELOW
-Thank you to all the reviewers for all of your constructive comments and feedback.
-We will fix all minor typos. 
-We hope to address the more important points of criticism here.
-% Thank you to all the reviewers for all of your constructive comments and feedback.
-We fully understand your concerns and we elaborate on them here.
-We kindly ask you to trust us that the presentation will be clear in the camera-ready and to reward the novelty of the idea in your ratings.
+Thank you to the reviewers for all of your constructive comments and feedback.
+We hope to address some concerns expressed by the reviewers here.
+We will also address any concerns or typos not mentioned.
 
 %-------------------------------------------------------------------------
-% \textit{Things are not what they seem}: This is an ominous quote that makes things appear much more dramatic.
-\textbf{(R1)}
-\textit{The network is evaluated on generated synthetic data and on triplets and quadruplets of real data from the Rome 16K dataset}, and
-\textit{The only experiments described are on randomly generated synthetic data an on image triplets and quadruplets of real data}, and
-\textit{Moreover, the experiments are limited.}
-:
+\textbf{(R1)} \textit{Insufficient experiments}:
 This was an unfortunate misunderstanding.
-There was a mistake written on line 700 where we wrote `triplets and quadruplets' instead of `6-tuples and 10-tuples'.
-If you look at Figures 5 and 6 and Table 2, you can see we correctly label them as 6 and 10 views, and thus our method works are larger scales than what the typo would imply.
+We accidentally reported on line 700 where we wrote `triplets and quadruplets' instead of `6-tuples and 10-tuples'.
+In Figures 5 and 6 and Table 2, you can see we correctly label them as 6 and 10 views.
+Thus our method works with a larger number of images as well.
 
-\textbf{(R1)} \textit{The very related approach: Disambiguating visual relations using loop constraints, Zach et al. CVPR 2010, is not discussed}:
-This paper seems to be focusing on pose graph optimization and thus we overlooked it.
-We will cite it in the final version paper.
+\textbf{(R1)} \textit{Prohibitive size of embedding vector for large SfM}:
+This is a limitation of many works using cycle consistency, such as works [32, 28, 19, 23] cited in our paper.
+Learning cycle consistent subwindows can still be useful in filtering erroneous matches in a sliding window fashion.
 
-\textbf{(R1)} \textit{There has been earlier work which used more than than two images such as, Learning Dense Correspondence via 3D-guided Cycle Consistency, Zhou et al. CVPR 2016}:
-We should have cited this.
-However this work \cite{zhou2016learning} to our understanding only does cycle consistency between two images, using ground truth CAD models to gain longer cycles.
-They never do cycle consistency on more than two images.
+\textbf{(R1)} \textit{Citing Zach et al 2010}:
+This paper seems to be focusing on pose graph optimization and thus we did not include it in the related work.
+This work handles cycle inconsistencies by solving a convex relaxation of probabilistic inference over the validity of edges.
+It requires composable geometric relations between each of the nodes in the graph, which we do not have with our feature matches at inference time.
+Regardless, this is still very relevant and we will cite it in the final version paper.
 
-\textbf{(R1)} \textit{I feel that this statement is a bit broad and might be overstating the contribution, works such as "LIFT: Learned Invariant Feature Transform" or "Learned Multi-Patch Similarity" seem to already tackle some aspects of this problem}:
-% We are sorry we did not make this clearer.
-What is meant by this is that this is the first algorithm we know of learning the matching algorithm itself on sparse features (not too clear with our language) on more than 2 images (hence multi-image).
-LIFT \cite{yi2016lift} clearly does feature matching, and thus we cite it, however it only does pairwise image matching.
-You are correct in that we did not cite `Learned Multi-patch Similarity' \cite{hartmann2017learned}, which is an important step for our research question, so we will cite it in the paper.
-We will update the referenced sentence in the paper to say `To the best of our knowledge, this work is the first to apply Graph Neural Networks to the sparse feature matching problem on more than 2 images'.
-% TODO: That paper only has 19 citations which is why we did not find it but it does pre-date us. Drat
+\textbf{(R1)} \textit{Citing Zhou et al 2016}:
+We will cite this in the camera-ready version.
+% To our understanding this work does cycle consistency between only two images. %, using ground truth CAD models to gain longer cycles.
+While methodology wise this paper uses cycle consistency, they learn cycle consistency of two images though ground truth CAD models, while our work enforces cycle consistent features through 3 or more views.
 
-\textbf{(R1)} \textit{It is not very clear how this approach can be used to improve geometric computer vision problems such as SfM as mentioned in the introduction} and \textbf{(R3)} \textit{It would be nice to see how the proposed algorithm can benefit many practical computer vision tasks, such as 3D reconstruction using SfM}:
-We feel this can be used in existing SfM pipelines before bundle adjustment to improve matching.
-Also it can be used to improve works such as \cite{zhu2015single} for reconstruction using semantic features in an end to end fashion.
+\textbf{(R1)} \textit{Regarding ``LIFT: Learned Invariant Feature Transform'' or ``Learned Multi-Patch Similarity''}:
+LIFT ([29] in the paper) clearly does feature matching, and thus we cite it, however it only does pairwise image matching.
+You are correct in that we did not cite `Learned Multi-patch Similarity' by Hartmann et al, which is an important step for our research question, so we will cite it in the paper.
+
+\textbf{(R1)} and \textbf{(R3)} \textit{Applying this to SfM}:
+Our approach could be incorporated in existing SfM pipelines before bundle adjustment to improve matching.
+However this work shows more promise in reconstructing and matching semantic features, similar in Wang et al ([28] in the paper) but using pixels directly.
 We hope to address this more fully with future work, and integrate it into a SfM pipeline.
 
+\textbf{(R1)} \textit{Overstating the contribution}:
+We will be careful to not overstate the contributions in camera-ready version.
+Our intention was to state that this is the first algorithm we know of learning the matching algorithm itself on sparse features (not too clear with our language) on more than 2 images.
+We will update the referenced sentence in the paper to say `To the best of our knowledge, this work is the first to apply Graph Neural Networks to the sparse feature matching problem on more than 2 images'.
+Despite this, we appreciate the reviewers acknowledging the novelty of learning representations through correspondence and geometric constraints.
+
 %------------------------------------------------------------------------
-% \textit{So it has come to this}: This is another ominous quote that while basically vacuous makes everything appear much more dramatic.
-\textbf{(R2)} \textit{Line 417 says "we use the mean function" and "we use MLPs" but it is unclear how that corresponds to the equations above.
-At least in the supplemental material, they should prove a more precise and complete explanation of the neural network architecture}:
-Indeed the sentence you specify could be made clearer and we can add more detail in the paper and supplemental material to make it clearer, adding details on layer and filter sizes.
-When we say `we use the mean function', we mean that to aggregate the edge features into the node features we just take the mean of the transformed features as opposed to for example max.
+\textbf{(R2)} \textit{Meaning of "we use the mean function" and "we use MLPs"}
+When we say `we use the mean function', we mean that to aggregate the edge features into the node features we just take the mean of the transformed features as opposed to the maximum.
 What we mean by `we use MLPs' is instead of taking a linear transformation of the node and edge embeddings between passes, we could learn a nonlinear transform using MLP.
+We will clarify this in the camera ready version.
 
-\textbf{(R2)} \textit{The matching matrices M in Equation 5 are not explained -- one has to read the related work in order to understand what they are} and \textit{Also, Equation 5 is only valid if all 3D points are visible in all views under consideration}:
-We can more clearly define the matching matrices.
-And Equation 5 can hold more generally if you allow rows of all zeros for places where there are no matches.
-However this is not made clear, and we will clarify it more when we clarify our language about the matching matrices.
+\textbf{(R2)} \textit{More detail on architecture}:
+Indeed the sentence you specify could be made clearer and we will add more details in the paper and supplemental material.
+We will also publicly release our code and the implementation details in the supplemental.
+% Right now we use 6 message passes through between the node and edge features, with the number of hidden nodes starting at 32 and doubling until flattening at 256.
+Between each message pass we process the features with a 2 layer MLP.
 
-\textbf{(R2)} \textit{ Line 517 mentions $E_i$, $E_j$ but they are not used in Equation 12?}:
+\textbf{(R2)} \textit{Explaining matching matrices Equation 5}:
+We will more clearly define the matching matrices.
+Equation 5 can hold more generally if you allow rows of all zeros for places where there are no matches.
+However this is not made clear, and we will clarify it more when we clean up our language about the matching matrices.
+
+\textbf{(R2)} \textit{$E_i$, $E_j$ not used in Equation 12?}:
 No that is just a typo, thank you for catching it.
 
+\textbf{(R2)} \textit{Only on par with state of the art}:
+We agree that the contribution of this work is to allow deep learning to be applied to this problem, and to allow future works to build on top for further improvement on performance.
+% TODO: Is this comment necessary?
+
 %------------------------------------------------------------------------
-% \textit{So it begins}: This also is an ominous quote that applies to most beginnings but makes things appear much more dramatic.
-\textbf{(R3)} \textit{If we only look at a local image patch, without global/geometric constraints, there might exist multiple valid matches for a candidate patches ...
-How does the proposed GNN method handle such cases?}:
+\textbf{(R3)} \textit{Handling ambiguous matches when using purely local image patches}:
 This is where the Geometric Consistency Loss would come in, as it would disambiguate such features.
@@
 In cases where such geometric information is not available, we could learn features with more information about the intra-image feature matches.
-This could help disambiguate visually similar features within the same image, and is a direction we are working on now.
+This could help disambiguate visually similar features within the same image, and is a very interesting direction for future work.
 
-% \begin{figure}[t]
-% \begin{center}
-% \fbox{\rule{0pt}{1.8in} \rule{0.9\linewidth}{0pt}}
-%    %\includegraphics[width=0.8\linewidth]{egfigure.eps}
-% \end{center}
-%    \caption{Example of caption.  It is set in Roman so that mathematics
-%    (always set in Roman: $B \sin A = A \sin B$) may be included without an
-%    ugly clash.}
-% \label{fig:long}
-% \label{fig:onecol}
-% \end{figure}
+\textbf{(R3)} \textit{PGDDS being faster and more accurate}:
+As we know from one pass inference on graph or geometry problems, it is difficult to outperform multi-iteration optimization methods.
+The advantage our method has is allowing for end-to-end training to enable learning features from pixels directly, a direction we hope to pursue in future work.
+In addition, PGDDS uses many optimizations between passes through the graph, so in future work we could use methods like OptNet by Amos et al ICML 2017 to help improve performance.
 
 % {\footnotesize
-{\tiny
-\bibliographystyle{ieee}
-\bibliography{egbib}
-}
+% {\tiny
+% \bibliographystyle{ieee}
+% \bibliography{egbib}
+% }
 

### 2019-09-21 baselines/format_graffiti.py
Added formatting for graffiti - not finished yet

@@ -1,0 +1,729 @@
+# #!/usr/bin/env python2
+# -*- coding: utf-8 -*-
+import os
+import sys
+import collections
+import itertools
+import functools
+import time
+
+import autograd.numpy as np   # Thinly-wrapped version of Numpy
+from autograd import grad
+# import numpy as np
+import scipy.linalg as la
+import scipy.optimize as opt
+import scipy.signal as sig
+import imageio
+import cv2
+import pickle
+import networkx as nx
+
+import matplotlib.pyplot as plt
+from matplotlib.patches import ConnectionPatch
+from mpl_toolkits.mplot3d import Axes3D
+
+from tqdm import tqdm
+from operator import indexOf
+START_TIME = time.time()
+plot = 1
+# threshs = [ 1e-1, 1, 2, 5 ]
+threshs = [ 1e-1, 1, 2, 5, 10, 15 ]
+TAU = threshs[-1]
+data_files = [
+	'graff/img{}.png'.format(i+1) for i in range(6)
+]
+
+imgs = [
+  imageio.imread(fname)[:,:,:3] for fname in data_files
+]
+
+N_imgs = len(imgs)
+N_points = 800
+N_data = 80
+
+def cmp_to_key(mycmp):
+  'Convert a cmp= function into a key= function'
+  class K:
+    def __init__(self, obj, *args):
+      self.obj = obj
+    def __lt__(self, other):
+      return mycmp(self.obj, other.obj) < 0
+    def __gt__(self, other):
+      return mycmp(self.obj, other.obj) > 0
+    def __eq__(self, other):
+      return mycmp(self.obj, other.obj) == 0
+    def __le__(self, other):
+      return mycmp(self.obj, other.obj) <= 0
+    def __ge__(self, other):
+      return mycmp(self.obj, other.obj) >= 0
+    def __ne__(self, other):
+      return mycmp(self.obj, other.obj) != 0
+  return K
+
+def unpackSIFTOctave(_octave):
+    """unpackSIFTOctave(kpt)->(octave,layer,scale)
+    @created by Silencer at 2018.01.23 11:12:30 CST
+    @brief Unpack Sift Keypoint by Silencer
+    @param kpt: cv2.KeyPoint (of SIFT)
+    """
+    # _octave = kpt.octave
+    octave = _octave&0xFF
[…]

### 2019-09-21 latex/iclr2020/iclr2020_conference.tex
Added ICLR latex

\documentclass{article} % For LaTeX2e
\usepackage{iclr2020_conference,times}

% Optional math commands from https://github.com/goodfeli/dlbook_notation.
\input{math_commands.tex}

\usepackage{hyperref}
\usepackage{url}

\title{Formatting Instructions for ICLR 2020 \\ Conference Submissions}

% Authors must not appear in the submitted version. They should be hidden
% as long as the \iclrfinalcopy macro remains commented out below.
% Non-anonymous submissions will be rejected without review.

\author{Antiquus S.~Hippocampus, Natalia Cerebro \& Amelie P. Amygdale \thanks{ Use footnote for providing further information
about author (webpage, alternative address)---\emph{not} for acknowledging
funding agencies.  Funding acknowledgements go at the end of the paper.} \\
Department of Computer Science\\
Cranberry-Lemon University\\
Pittsburgh, PA 15213, USA \\
\texttt{\{hippo,brain,jen\}@cs.cranberry-lemon.edu} \\
\And
Ji Q. Ren \& Yevgeny LeNet \\
Department of Computational Neuroscience \\
University of the Witwatersrand \\
Joburg, South Africa \\
\texttt{\{robot,net\}@wits.ac.za} \\
\AND
Coauthor \\
Affiliation \\
Address \\
\texttt{email}
}

% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to \LaTeX{} to determine where to break
% the lines. Using \AND forces a linebreak at that point. So, if \LaTeX{}
% puts 3 of 4 authors names on the first line, and the last on the second
% line, try using \AND instead of \And before the third author name.

\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}

% \iclrfinalcopy % Uncomment for camera-ready version, but NOT for submission.
\begin{document}

\maketitle

\begin{abstract}
The abstract paragraph should be indented 1/2~inch (3~picas) on both left and
right-hand margins. Use 10~point type, with a vertical spacing of 11~points.
The word \textsc{Abstract} must be centered, in small caps, and in point size 12. Two
line spaces precede the abstract. The abstract must be limited to one
paragraph.
\end{abstract}

\section{Submission of conference papers to ICLR 2020}

ICLR requires electronic submissions, processed by
\url{https://openreview.net/}. See ICLR's website for more instructions.

If your paper is ultimately accepted, the statement {\tt
  {\textbackslash}iclrfinalcopy} should be inserted to adjust the
format to the camera ready requirements.

The format for the submissions is a variant of the NIPS format.
Please read carefully the instructions below, and follow them
faithfully.

\subsection{Style}

Papers to be submitted to ICLR 2020 must be prepared according to the
instructions presented here.

%% Please note that we have introduced automatic line number generation
%% into the style file for \LaTeXe. This is to help reviewers
%% refer to specific lines of the paper when they make their comments. Please do
%% NOT refer to these line numbers in your paper as they will be removed from the
%% style file for the final version of accepted papers.

Authors are required to use the ICLR \LaTeX{} style files obtainable at the
ICLR website. Please make sure you use the current files and
not previous versions. Tweaking the style files may be grounds for rejection.

\subsection{Retrieval of style files}

The style files for ICLR and other conference information are available online at:
\begin{center}
   \url{http://www.iclr.cc/}
\end{center}
The file \verb+iclr2020_conference.pdf+ contains these
instructions and illustrates the
various formatting requirements your ICLR paper must satisfy.
Submissions must be made using \LaTeX{} and the style files
\verb+iclr2020_conference.sty+ and \verb+iclr2020_conference.bst+ (to be used with \LaTeX{}2e). The file
\verb+iclr2020_conference.tex+ may be used as a ``shell'' for writing your paper. All you
have to do is replace the author, title, abstract, and text of the paper with
your own.

The formatting instructions contained in these style files are summarized in
sections \ref{gen_inst}, \ref{headings}, and \ref{others} below.

\section{General formatting instructions}
\label{gen_inst}

The text must be confined within a rectangle 5.5~inches (33~picas) wide and
9~inches (54~picas) long. The left margin is 1.5~inch (9~picas).
Use 10~point type with a vertical spacing of 11~points. Times New Roman is the
preferred typeface throughout. Paragraphs are separated by 1/2~line space,
with no indentation.

Paper title is 17~point, in small caps and left-aligned.
All pages should start at 1~inch (6~picas) from the top of the page.

Authors' names are
set in boldface, and each name is placed above its corresponding
address. The lead author's name is to be listed first, and
the co-authors' names are set to follow. Authors sharing the
same address can be on the same line.

Please pay special attention to the instructions in section \ref{others}
regarding figures, tables, acknowledgments, and references.

The recommended paper length is 8 pages, with unlimited additional pages for
citations.  There will be a strict upper limit of 10 pages for the main text.
Reviewers will be instructed to apply a higher standard to papers in excess of 8
pages.  Authors may use as many pages of appendices (after the bibliography) as
they wish, but reviewers are not required to read these.

\section{Headings: first level}
\label{headings}

First level headings are in small caps,
flush left and in point size 12. One line space before the first level
heading and 1/2~line space after the first level heading.

\subsection{Headings: second level}

Second level headings are in small caps,
flush left and in point size 10. One line space before the second level
heading and 1/2~line space after the second level heading.

\subsubsection{Headings: third level}

Third level headings are in small caps,
flush left and in point size 10. One line space before the third level
heading and 1/2~line space after the third level heading.

\section{Citations, figures, tables, references}
\label{others}

These instructions apply to everyone, regardless of the formatter being used.

\subsection{Citations within the text}

Citations within the text should be based on the \texttt{natbib} package
and include the authors' last names and year (with the ``et~al.'' construct
for more than two authors). When the authors or the publication are
included in the sentence, the citation should not be in parenthesis using \verb|\citet{}| (as
in ``See \citet{Hinton06} for more information.''). Otherwise, the citation
should be in parenthesis using \verb|\citep{}| (as in ``Deep learning shows promise to make progress 
towards AI~\citep{Bengio+chapter2007}.'').

The corresponding references are to be listed in alphabetical order of
authors, in the \textsc{References} section. As to the format of the
references themselves, any style is acceptable as long as it is used
consistently.

\subsection{Footnotes}

Indicate footnotes with a number\footnote{Sample of the first footnote} in the
text. Place the footnotes at the bottom of the page on which they appear.
Precede the footnote with a horizontal rule of 2~inches
(12~picas).\footnote{Sample of the second footnote}

\subsection{Figures}

All artwork must be neat, clean, and legible. Lines should be dark
enough for purposes of reproduction; art work should not be
hand-drawn. The figure number and caption always appear after the
figure. Place one line space before the figure caption, and one line
space after the figure. The figure caption is lower case (except for
first word and proper nouns); figures are numbered consecutively.

Make sure the figure caption does not get separated from the figure.
Leave sufficient space to avoid splitting the figure and figure caption.

You may use color figures.
However, it is best for the
figure captions and the paper body to make sense if the paper is printed
either in black/white or in color.
\begin{figure}[h]
\begin{center}
%\framebox[4.0in]{$\;$}
\fbox{\rule[-.5cm]{0cm}{4cm} \rule[-.5cm]{4cm}{0cm}}
\end{center}
\caption{Sample figure caption.}
\end{figure}

\subsection{Tables}

All tables must be centered, neat, clean and legible. Do not use hand-drawn
tables. The table number and title always appear before the table. See
Table~\ref{sample-table}.

Place one line space before the table title, one line space after the table
title, and one line space after the table. The table title must be lower case
(except for first word and proper nouns); tables are numbered consecutively.

\begin{table}[t]
\caption{Sample table title}
\label{sample-table}
\begin{center}
\begin{tabular}{ll}
\multicolumn{1}{c}{\bf PART}  &\multicolumn{1}{c}{\bf DESCRIPTION}
\\ \hline \\
Dendrite         &Input terminal \\
Axon             &Output terminal \\
Soma             &Cell body (contains cell nucleus) \\
\end{tabular}
\end{center}
\end{table}

\section{Default Notation}

In an attempt to encourage standardized notation, we have included the
notation file from the textbook, \textit{Deep Learning}
\cite{goodfellow2016deep} available at
\url{https://github.com/goodfeli/dlbook_notation/}.  Use of this style
is not required and can be disabled by commenting out
\texttt{math\_commands.tex}.

\centerline{\bf Numbers and Arrays}
\bgroup
\def\arraystretch{1.5}
\begin{tabular}{p{1in}p{3.25in}}
$\displaystyle a$ & A scalar (integer or real)\\
$\displaystyle \va$ & A vector\\
$\displaystyle \mA$ & A matrix\\
$\displaystyle \tA$ & A tensor\\
$\displaystyle \mI_n$ & Identity matrix with $n$ rows and $n$ columns\\
$\displaystyle \mI$ & Identity matrix with dimensionality implied by context\\
$\displaystyle \ve^{(i)}$ & Standard basis vector $[0,\dots,0,1,0,\dots,0]$ with a 1 at position $i$\\
$\displaystyle \text{diag}(\va)$ & A square, diagonal matrix with diagonal entries given by $\va$\\
$\displaystyle \ra$ & A scalar random variable\\
$\displaystyle \rva$ & A vector-valued random variable\\
$\displaystyle \rmA$ & A matrix-valued random variable\\
\end{tabular}
\egroup
\vspace{0.25cm}

\centerline{\bf Sets and Graphs}
\bgroup
\def\arraystretch{1.5}

\begin{tabular}{p{1.25in}p{3.25in}}
$\displaystyle \sA$ & A set\\
$\displaystyle \R$ & The set of real numbers \\
$\displaystyle \{0, 1\}$ & The set containing 0 and 1 \\
$\displaystyle \{0, 1, \dots, n \}$ & The set of all integers between $0$ and $n$\\
$\displaystyle [a, b]$ & The real interval including $a$ and $b$\\
$\displaystyle (a, b]$ & The real interval excluding $a$ but including $b$\\
$\displaystyle \sA \backslash \sB$ & Set subtraction, i.e., the set containing the elements of $\sA$ that are not in $\sB$\\
$\displaystyle \gG$ & A graph\\
$\displaystyle \parents_\gG(\ervx_i)$ & The parents of $\ervx_i$ in $\gG$
\end{tabular}
\vspace{0.25cm}

\centerline{\bf Indexing}
\bgroup
\def\arraystretch{1.5}

\begin{tabular}{p{1.25in}p{3.25in}}
$\displaystyle \eva_i$ & Element $i$ of vector $\va$, with indexing starting at 1 \\
$\displaystyle \eva_{-i}$ & All elements of vector $\va$ except for element $i$ \\
$\displaystyle \emA_{i,j}$ & Element $i, j$ of matrix $\mA$ \\
$\displaystyle \mA_{i, :}$ & Row $i$ of matrix $\mA$ \\
$\displaystyle \mA_{:, i}$ & Column $i$ of matrix $\mA$ \\
$\displaystyle \etA_{i, j, k}$ & Element $(i, j, k)$ of a 3-D tensor $\tA$\\
$\displaystyle \tA_{:, :, i}$ & 2-D slice of a 3-D tensor\\
$\displaystyle \erva_i$ & Element $i$ of the random vector $\rva$ \\
\end{tabular}
\egroup
\vspace{0.25cm}

\centerline{\bf Calculus}
\bgroup
\def\arraystretch{1.5}
\begin{tabular}{p{1.25in}p{3.25in}}
% NOTE: the [2ex] on the next line adds extra height to that row of the table.
% Without that command, the fraction on the first line is too tall and collides
% with the fraction on the second line.
$\displaystyle\frac{d y} {d x}$ & Derivative of $y$ with respect to $x$\\ [2ex]
$\displaystyle \frac{\partial y} {\partial x} $ & Partial derivative of $y$ with respect to $x$ \\
$\displaystyle \nabla_\vx y $ & Gradient of $y$ with respect to $\vx$ \\
$\displaystyle \nabla_\mX y $ & Matrix derivatives of $y$ with respect to $\mX$ \\
$\displaystyle \nabla_\tX y $ & Tensor containing derivatives of $y$ with respect to $\tX$ \\
$\displaystyle \frac{\partial f}{\partial \vx} $ & Jacobian matrix $\mJ \in \R^{m\times n}$ of $f: \R^n \rightarrow \R^m$\\
$\displaystyle \nabla_\vx^2 f(\vx)\text{ or }\mH( f)(\vx)$ & The Hessian matrix of $f$ at input point $\vx$\\
$\displaystyle \int f(\vx) d\vx $ & Definite integral over the entire domain of $\vx$ \\
$\displaystyle \int_\sS f(\vx) d\vx$ & Definite integral with respect to $\vx$ over the set $\sS$ \\
\end{tabular}
\egroup
\vspace{0.25cm}

\centerline{\bf Probability and Information Theory}
\bgroup
\def\arraystretch{1.5}
\begin{tabular}{p{1.25in}p{3.25in}}
$\displaystyle P(\ra)$ & A probability distribution over a discrete variable\\
$\displaystyle p(\ra)$ & A probability distribution over a continuous variable, or over
a variable whose type has not been specified\\
$\displaystyle \ra \sim P$ & Random variable $\ra$ has distribution $P$\\% so thing on left of \sim should always be a random variable, with name beginning with \r
$\displaystyle  \E_{\rx\sim P} [ f(x) ]\text{ or } \E f(x)$ & Expectation of $f(x)$ with respect to $P(\rx)$ \\
$\displaystyle \Var(f(x)) $ &  Variance of $f(x)$ under $P(\rx)$ \\
$\displaystyle \Cov(f(x),g(x)) $ & Covariance of $f(x)$ and $g(x)$ under $P(\rx)$\\
$\displaystyle H(\rx) $ & Shannon entropy of the random variable $\rx$\\
$\displaystyle \KL ( P \Vert Q ) $ & Kullback-Leibler divergence of P and Q \\
$\displaystyle \mathcal{N} ( \vx ; \vmu , \mSigma)$ & Gaussian distribution %
over $\vx$ with mean $\vmu$ and covariance $\mSigma$ \\
\end{tabular}
\egroup
\vspace{0.25cm}

\centerline{\bf Functions}
\bgroup
\def\arraystretch{1.5}
\begin{tabular}{p{1.25in}p{3.25in}}
$\displaystyle f: \sA \rightarrow \sB$ & The function $f$ with domain $\sA$ and range $\sB$\\
$\displaystyle f \circ g $ & Composition of the functions $f$ and $g$ \\
  $\displaystyle f(\vx ; \vtheta) $ & A function of $\vx$ parametrized by $\vtheta$.
  (Sometimes we write $f(\vx)$ and omit the argument $\vtheta$ to lighten notation) \\
$\displaystyle \log x$ & Natural logarithm of $x$ \\
$\displaystyle \sigma(x)$ & Logistic sigmoid, $\displaystyle \frac{1} {1 + \exp(-x)}$ \\
$\displaystyle \zeta(x)$ & Softplus, $\log(1 + \exp(x))$ \\
$\displaystyle || \vx ||_p $ & $\normlp$ norm of $\vx$ \\
$\displaystyle || \vx || $ & $\normltwo$ norm of $\vx$ \\
$\displaystyle x^+$ & Positive part of $x$, i.e., $\max(0,x)$\\
$\displaystyle \1_\mathrm{condition}$ & is 1 if the condition is true, 0 otherwise\\
\end{tabular}
\egroup
\vspace{0.25cm}

\section{Final instructions}
Do not change any aspects of the formatting parameters in the style files.
In particular, do not modify the width or length of the rectangle the text
should fit into, and do not change font sizes (except perhaps in the
\textsc{References} section; see below). Please note that pages should be
numbered.

\section{Preparing PostScript or PDF files}

Please prepare PostScript or PDF files with paper size ``US Letter'', and
not, for example, ``A4''. The -t
letter option on dvips will produce US Letter files.

Consider directly generating PDF files using \verb+pdflatex+
(especially if you are a MiKTeX user).
PDF figures must be substituted for EPS figures, however.

Otherwise, please generate your PostScript and PDF files with the following commands:
\begin{verbatim}
dvips mypaper.dvi -t letter -Ppdf -G0 -o mypaper.ps
ps2pdf mypaper.ps mypaper.pdf
\end{verbatim}

\subsection{Margins in LaTeX}

Most of the margin problems come from figures positioned by hand using
\verb+\special+ or other commands. We suggest using the command
\verb+\includegraphics+
from the graphicx package. Always specify the figure width as a multiple of
the line width as in the example below using .eps graphics
\begin{verbatim}
   \usepackage[dvips]{graphicx} ...
   \includegraphics[width=0.8\linewidth]{myfile.eps}
\end{verbatim}
or % Apr 2009 addition
\begin{verbatim}
   \usepackage[pdftex]{graphicx} ...
   \includegraphics[width=0.8\linewidth]{myfile.pdf}
\end{verbatim}
for .pdf graphics.
See section~4.4 in the graphics bundle documentation (\url{http://www.ctan.org/tex-archive/macros/latex/required/graphics/grfguide.ps})

A number of width problems arise when LaTeX cannot properly hyphenate a
line. Please give LaTeX hyphenation hints using the \verb+\-+ command.

\subsubsection*{Author Contributions}
If you'd like to, you may include  a section for author contributions as is done
in many journals. This is optional and at the discretion of the authors.

\subsubsection*{Acknowledgments}
Use unnumbered third level headings for the acknowledgments. All
acknowledgments, including those to funding agencies, go at the end of the paper.

\bibliography{iclr2020_conference}
\bibliographystyle{iclr2020_conference}

\appendix
\section{Appendix}
You may include other additional sections here.

\end{document}

### 2019-09-21 latex/iclr2020/main.tex
Added ICLR latex

--- 2019-03-24 latex/iccv2019/main.tex
@@
-\documentclass[10pt,twocolumn,letterpaper]{article}
+\documentclass{article} % For LaTeX2e
+\usepackage{iclr2020_conference,times}
 
-\usepackage{iccv}
-\usepackage{times}
+% Optional math commands from https://github.com/goodfeli/dlbook_notation.
+\input{math_commands.tex}
+
+\usepackage{subcaption}
 \usepackage{epsfig}
 \usepackage{graphicx}
-\usepackage{amsmath}
-\usepackage{amssymb}
+\usepackage{hyperref}
+\usepackage{url}
 
-% Include other packages here, before hyperref.
+\newcommand{\cross}[1]{[#1]_{\times}}
+\setlength{\textfloatsep}{12pt plus 2pt minus 2pt}
 
-% If you comment hyperref and then uncomment it, you should delete
-% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
-% run, let it finish, and you should be clear).
-\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
+\title{Graph Neural Networks For Multi-Image Matching}
 
-% \iccvfinalcopy % *** Uncomment this line for the final submission
+% Authors must not appear in the submitted version. They should be hidden
+% as long as the \iclrfinalcopy macro remains commented out below.
+% Non-anonymous submissions will be rejected without review.
 
-\def\iccvPaperID{****} % *** Enter the ICCV Paper ID here
-\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
+\author{Stephen Phillips, Kostas Daniilidis \\
+School of Engineering and Applied Sciences \\
+University of Pennsylvania \\
+Pennsylvania, PA 19104, USA \\
+\texttt{\{stephi, kostas\}@seas.upenn.edu} \\
+}
 
-%% Custom control sequences
-\let\oldPr\Pr
-\newcommand{\bR}{\mathbb{R}}
-\renewcommand*{\Pr}[1]{\mathbb{P}\left( #1 \right)}
-\newcommand{\mat}[1]{\mathbf{#1}}
-\DeclareMathOperator*{\argmax}{arg\,max}
-\DeclareMathOperator*{\argmin}{arg\,min}
-\newcommand{\tr}{\mathbf{tr}}
-\newcommand{\cross}[1]{[#1]_{\times}}
+% The \author macro works with any number of authors. There are two commands
+% used to separate the names and addresses of multiple authors: \And and \AND.
+%
+% Using \And between authors leaves it to \LaTeX{} to determine where to break
+% the lines. Using \AND forces a linebreak at that point. So, if \LaTeX{}
+% puts 3 of 4 authors names on the first line, and the last on the second
+% line, try using \AND instead of \And before the third author name.
 
-% Pages are numbered in submission mode, and unnumbered in camera-ready
-\ificcvfinal\pagestyle{empty}\fi
+\newcommand{\fix}{\marginpar{FIX}}
+\newcommand{\new}{\marginpar{NEW}}
+
+%\iclrfinalcopy % Uncomment for camera-ready version, but NOT for submission.
 \begin{document}
 
-%%%%%%%%% TITLE
-\title{All Graphs Lead to Rome: Learning Geometric and Cycle-Consistent Representations with Graph Networks}
+\maketitle
 
-\author{Stephen Phillips, Kostas Daniilidis \\
-GRASP Laboratory, University of Pennsylvania\\
-{\tt\small \{stephi, kostas\}@seas.upenn.edu}
-% For a paper whose authors are all at the same institution,
-% omit the following lines up until the closing ``}''.
-% Additional authors and addresses can be added with ``\and'',
-% just like the second author.
-% To save space, use either the email address or home page, not both
-}
-
-\maketitle
-%\thispagestyle{empty}
-
-%%%%%%%%% ABSTRACT
 \begin{abstract}
@@
 
-\begin{figure}[t]
-\begin{center}
-  % \fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-  \includegraphics[width=0.8\linewidth]{figures-CycleConsistencyBasic-v2.pdf}
-\end{center}
-  \caption{
-    Example of multi-image matching and cycle consistency, with images from Rome16K dataset \cite{li2010location}.
-    Pairwise matches between image can lead to global inconsistencies in the matching.
-    In this example, an error in matching leads to an inconsistent cycle (shown in red), ideally these pairwise matches would be consistent.
-    We improve the quality of pairwise matches in the multi-view matching problem by training a neural net with cycle consistency.
-  }
-\label{fig:cycconsistex}
-\label{fig:onecol}
-\end{figure}
+% \begin{figure}[t]
+% \begin{center}
+%   % \fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
+%   \includegraphics[width=0.8\linewidth]{figures-CycleConsistencyBasic-v2.pdf}
+% \end{center}
+%   \caption{
+%     Example of multi-image matching and cycle consistency, with images from Rome16K dataset \cite{li2010location}.
+%     Pairwise matches between image can lead to global inconsistencies in the matching.
+%     In this example, an error in matching leads to an inconsistent cycle (shown in red), ideally these pairwise matches would be consistent.
+%     We improve the quality of pairwise matches in the multi-view matching problem by training a neural net with cycle consistency.
+%   }
+% \label{fig:cycconsistex}
+% \end{figure}
 
@@
 \label{fig:pipeline}
-\label{fig:onecol}
 \end{figure*}
@@
 \begin{figure}[t]
-\begin{center}
-  \includegraphics[width=0.9\linewidth]{figures-UniverseOfFeatures-v2.pdf}
-\end{center}
+\begin{subfigure}[b]{.45\linewidth}
+  \centering
+  \includegraphics[width=0.95\linewidth]{figures-UniverseOfFeatures-v2.pdf}
+  \caption{Illustration of the universe of features.}
+  \label{fig:1a}
+  \label{fig:universefeatures}
+\end{subfigure}%
+\begin{subfigure}[b]{.45\linewidth}
+  \centering
+  \includegraphics[width=0.95\linewidth]{figures-GeometricConsistency-v2.pdf}
+  \caption{Illustrated here is an example of how the geometric loss is computed for one feature.}
+  \label{fig:1b}
+  \label{fig:geoconsist}
+\end{subfigure}
 \caption{
-    Illustration of the universe of features.
-    Each feature in each image corresponds to a 3D point in the scene.
+  \textbf{(a)} Each feature in each image corresponds to a 3D point in the scene.
   We can construct cycle consistent embeddings of the features by mapping each one to the one-hot vector of its corresponding 3D point.
   While there can be many features, there are fewer 3D points and thus this corresponds to a low rank factorization of the correspondence matrix.
+  \textbf{(b)} Errors are computed via absolute distance from the epipolar line, as expressed by (\ref{eq:essential_constraint}) via the epipolar constraint.
+  The epipolar line is the line of projection of the feature on the first image, projected onto to the second.
+  The distance to this line on the second image indicates how likely that point is to correspond geometrically to the original feature.
+  There can be false positives along the projected line, as shown by the square feature in the figure, but other points will be eliminated, such as the hexagonal feature.
   Best viewed in color.
 }
-\label{fig:universefeatures}
-\label{fig:onecol}
+\label{fig:1}
 \end{figure}
+
 Our goal is to learn optimal features that capture multiple image views by filtering out noisy feature matches.
@@
 We formulate this problem in terms of the correspondence graph of the features.
-Vectors $\mat{x}$ and matrices $\mat{A}$ are denoted with boldface, and the $i^{th}$ row of a matrix is denoted $(\mat{A})_i$.
-Graphs $\mathcal{G} = (\mathcal{V}, \mathcal{E})$ have a set of vertices $\mathcal{V}$ and of edges $\mathcal{E} \subseteq \mathcal{V} \times \mathcal{V}$.
-Implicitly in the subsequent discussions we assume the edges are directed.
+Graphs $\mathcal{G} = (\mathcal{V}, \mathcal{E})$ have a set of vertices $\mathcal{V}$ and of edges $\mathcal{E} \subseteq \mathcal{V} \times \mathcal{V}$ and implicitly in the subsequent discussions we assume the edges are directed.
 For a vertex $v \in \mathcal{V}$ we use $\mathcal{N}^{h}(v)$ to denote the $h$-hop neighbors of $v$, with the superscript left out for 1-hop neighbors.
@@
 \subsection{Correspondence Graph}
-We assume there is an initial set of feature matches represented as a graph $\mathcal{G} = (\mathcal{V}, \mathcal{E})$, with an associated adjacency matrix $\mat{A}$.
+We assume there is an initial set of feature matches represented as a graph $\mathcal{G} = (\mathcal{V}, \mathcal{E})$, with an associated adjacency matrix $\mA$.
 The graph is constructed from putative correspondences of image features across images, typically constructed using feature descriptor distance (e.g. SIFT feature distance).
@@
 
-Each vertex of the graph $v \in \mathcal{V}$ is an image feature, corresponding to some ground truth 3D point $\mat{P}(v)$.
+Each vertex of the graph $v \in \mathcal{V}$ is an image feature, corresponding to some ground truth 3D point $\vp(v)$.
 Each edge $e = (v_1, v_2) \in \mathcal{E}$ is a potential correspondence.
-Associated with each vertex $v$ is an embedding $\mat{f}_v \in \bR^m$, which can include the visual feature descriptor, position, scale, orientation, etc.
-Similarly, each edge $e$ has an associated feature $\mat{f}_e \in \bR^p$ (in this work, initially just the weight of the feature association).
+Associated with each vertex $v$ is an embedding $\vf_v \in \sR^m$, which can include the visual feature descriptor, position, scale, orientation, etc.
+Similarly, each edge $e$ has an associated feature $\vf_e \in \sR^p$ (in this work, initially just the weight of the feature association).
 We use these features as the initialization for our learning algorithm.
@@
 Since features in this case represent unique locations in the scene, no points in the same image would have edges $e$ between them.
-Mathematically, this can be expressed as $e = (v_1, v_2) \in \mathcal{E} \implies \mat{P}(v_1) = \mat{P}(v_2)$.
-In the noisy case we expect this structure to be corrupted, i.e. there are some edges $e = (v_1, v_2) \in \mathcal{E}$ such that $\mat{P}(v_1) \neq \mat{P}(v_2)$.
+Mathematically, this can be expressed as $e = (v_1, v_2) \in \mathcal{E} \implies \mP(v_1) = \mP(v_2)$.
+In the noisy case we expect this structure to be corrupted, i.e. there are some edges $e = (v_1, v_2) \in \mathcal{E}$ such that $\mP(v_1) \neq \mP(v_2)$.
 Thus we need to prune the erroneous edges.
@@
 \subsection{Graph Neural Networks}
-As input to our method we are given a graph $\mathcal{G} = (\mathcal{V}, \mathcal{E})$ with the features described last section $\mat{f}_v \forall v \in \mathcal{V}$ and $\mat{f}_e \forall e \in \mathcal{E}$.
+As input to our method we are given a graph $\mathcal{G} = (\mathcal{V}, \mathcal{E})$ with the features described last section $\vf_v \; \forall v \in \mathcal{V}$ and $\vf_e \; \forall e \in \mathcal{E}$.
 As with any neural network, GNNs have layered outputs.
-We describe the output of layer $k$ as $\mat{f}_v^{(k)} \in \bR^{m_k}\, \forall v \in \mathcal{V}$ and $\mat{f}_e^{(k)} \in \bR^{p_k}\, \forall e \in \mathcal{E}$, with the initial embeddings denoted $\mat{f}_v^{(0)} = \mat{f}_v$ and $\mat{f}_e^{(0)} = \mat{f}_e$.
-It will be useful to write these features as matrices in later sections, so we denote the vertex embedding matrix as $\mat{F}_V^{(k)}$ and the edge embedding matrix as $\mat{F}_E^{(k)}$.
+We describe the output of layer $k$ as $\vf_v^{(k)} \in \sR^{m_k} \, \forall v \in \mathcal{V}$ and $\vf_e^{(k)} \in \sR^{p_k}\, \forall e \in \mathcal{E}$, with the initial embeddings denoted $\vf_v^{(0)} = \vf_v$ and $\vf_e^{(0)} = \vf_e$.
+It will be useful to write these features as matrices in later sections, so we denote the vertex embedding matrix as $\mF_V^{(k)}$ and the edge embedding matrix as $\mF_E^{(k)}$.
 If a superscript is not specified then it refers to the final output of the network.
@@
 First we describe older methods of GNNs to give context, then we describe the method we use in this work.
-Many older methods assume we have the adjacency matrix $\mat{A}$ of the graph known a-priori \cite{bruna2013spectral}, and can encode graph convolutions using the eigenvectors of $\mat{A}$.
+Many older methods assume we have the adjacency matrix $\mA$ of the graph known a-priori \cite{bruna2013spectral}, and can encode graph convolutions using the eigenvectors of $\mA$.
 However, we do not have this luxury, as the correspondence structure changes from image set to image set, and thus we use non-spectral Graph Neural Networks.
@@
 \begin{align*}
-\mat{\tilde{f}}_v^{(k+1)} =&\; b^{(k)} + \mat{W}_0^{k} \mat{f}_{v}^{(k)} + \sum_{h=0}^H \sum_{v' \in \mathcal{N}^{h}(v)} f_{e(v,v')} \mat{W}_{h}^{k} \mat{f}_{v'}^{(k)} \\
-\mat{f}_v^{(k+1)} =&\; \sigma\left(\mat{\tilde{f}}_v^{(k+1)}\right)
+\tilde{\vf}_v^{(k+1)} =&\; \sigma\left( b^{(k)} + \mW_0^{k} \vf_{v}^{(k)} + \sum_{h=0}^H \sum_{v' \in \mathcal{N}^{h}(v)} f_{e(v,v')} \mW_{h}^{k} \vf_{v'}^{(k)} \right) \\
 \end{align*}
-The weights/biases $\mat{W}_{h}^{k}$, $b^{(k)}$ are all learned, with no learning done on the edge weights $f_{e(v,v')}$. 
+The weights/biases $\mW_{h}^{k}$, $b^{(k)}$ are all learned, with no learning done on the edge weights $f_{e(v,v')}$. 
 Note that this is just sums or averages over $h$-hop neighborhoods, where the weights on the edges remain static through the computation.
@@
 \begin{align}
-\mat{\tilde{f}}_{e(v_1,v_2)}^{(k+1)} =&\; \mat{U}_1^{(k)} \mat{f}_{e}^{(k)} + \mat{U}_1^{(k)} \mat{f}_{v_1}^{(k)} + \mat{U}_2^{(k)} \mat{f}_{v_2}^{(k)} \\
-\mat{f}_{e(v_1,v_2)}^{(k+1)} =&\; \sigma \left(a^{(k)} + \mat{\tilde{f}}_{e(v_1,v_2)}^{(k+1)}\right) \\
-\mat{\tilde{f}}_{v}^{(k+1)} =&\; \mat{W}_0^{(k)} \mat{f}_{v}^{(k)} + \sum_{e \in \mathcal{E}(v)} \mat{W}_1^{(k)} \mat{f}_{e}^{(k+1)} \\
-\mat{f}_v^{(k+1)} =&\; \sigma\left(b^{(k)} + \mat{\tilde{f}}_v^{(k+1)}\right)
+\tilde{\vf}_{e(v_1,v_2)}^{(k+1)} =&\; \sigma \left(a^{(k)} + \mU_1^{(k)} \vf_{e}^{(k)} + \mU_1^{(k)} \vf_{v_1}^{(k)} + \mU_2^{(k)} \vf_{v_2}^{(k)} \right) \\
+\tilde{\vf}_{v}^{(k+1)} =&\; \sigma\left(b^{(k)} + \mW_0^{(k)} \vf_{v}^{(k)} + \sum_{e \in \mathcal{E}(v)} \mW_1^{(k)} \vf_{e}^{(k+1)} \right) 
 \end{align}
-Here the learned weights are denoted $\mat{W}$ and $\mat{U}$, and the biases $a^{(k)}$ and  $b^{(k)}$.
+Here the learned weights are denoted $\mW$ and $\mU$, and the biases $a^{(k)}$ and  $b^{(k)}$.
 In \cite{battaglia2018relational}, they allow for more sophisticated aggregation functions, but in this work we simply use the mean function.
@@
 
-\begin{figure}[t]
-\begin{center}
-  \includegraphics[width=0.8\linewidth]{figures-GeometricConsistency-v2.pdf}
-\end{center}
-  \caption{
-    Illustrated here is an example of how the geometric loss is computed for one feature.  
-    Errors are computed via absolute distance from the epipolar line, as expressed by (\ref{eq:essential_constraint}) via the epipolar constraint.
-    The epipolar line is the line of projection of the feature on the first image, projected onto to the second.
-    The distance to this line on the second image indicates how likely that point is to correspond geometrically to the original feature.
-    There can be false positives along the projected line, as shown by the square feature in the figure, but other points will be eliminated, such as the hexagonal feature.
-    Best viewed in color.
-  }
-\label{fig:geoconsist}
-\label{fig:onecol}
-\end{figure}
-
 \subsection{Cycle Consistency}
 
-Let $\mat{M}$ be the noiseless set of matches between our features, with $\mat{M}_{ij}$ being the matches between image $i$ and image $j$.
-If the pairwise matches are globally consistent, then we can say that, for all $i, j, k$:
+Let $\mM$ be the noiseless set of matches between our features, with $\mM_{ij}$ being the matches between image $i$ and image $j$.
+If the pairwise matches are globally consistent, then for all $i, j, k$:
 \begin{equation}
-\mat{M}_{ij} = \mat{M}_{ik} \mat{M}_{kj}
+\mM_{ij} = \mM_{ik} \mM_{kj}
 \label{eq:cycconsist1}
@@
 A more elegant way to represent cycle consistency is to first create a `universe' of features that all images match to (see figure \ref{fig:universefeatures}).
-Then, one can match the $i^{th}$ set of features to the universe using a ground-truth matching matrix $\mat{X}_i$.
+Then, one can match the $i^{th}$ set of features to the universe using a ground-truth matching matrix $\mX_i$.
 Then the cycle consistency constraint becomes:
 \begin{equation}
-\mat{M}_{ij} = \mat{X}_{i}\mat{X}_{j}^\top
+\mM_{ij} = \mX_{i}\mX_{j}^\top
 \label{eq:cycconsist2}
@@
 
-\begin{table*}
+\begin{table*}[t]
 \begin{center}
@@
 This reduces the number of our constraints from $O(n^3)$ to $O(n^2)$.
-We try to learn vertex embeddings $\mat{F}_V$ to approximate $\mat{X}$ - in other words the final embedding should be an encoding of the universe of features.
-As we do not have the ground truth matches $\mat{M}$, we approximate it using the noisy adjacency matrix $\mat{A}$ of our correspondence graph. Thus our loss would be 
+We try to learn vertex embeddings $\mF_V$ to approximate $\mX$ - in other words the final embedding should be an encoding of the universe of features.
+As we do not have the ground truth matches $\mM$, we approximate it using the noisy adjacency matrix $\mA$ of our correspondence graph. Thus our loss would be 
 \begin{equation}
-\mathcal{L}(\mat{A}, \mat{F}_V) = \mathcal{D}(\mat{A}, \mat{F}_V \mat{F}_V^\top)
+\mathcal{L}(\mA, \mF_V) = \mathcal{D}(\mA, \mF_V \mF_V^\top)
 \end{equation}
@@
 Note that because of this formulation, we can determine our embeddings only up to a rotation, as
-\begin{equation}
-\mat{E}R(\mat{E}R)^\top
-= \mat{E}RR^\top\mat{E}^\top
-= \mat{E}\mat{E}^\top
-\label{eq:rotinvar}
-\end{equation}
-Thus when visualizing embeddings, we rotate them to make them more interpretable (see figure \ref{fig:embeddingsviz}).
+$ \mE R(\mE R)^\top
+= \mE RR^\top \mE^\top
+= \mE\mE^\top
+\label{eq:rotinvar} $
+% Thus when visualizing embeddings, we rotate them to make them more interpretable (see figure \ref{fig:embeddingsviz}).
 
@@
 An illustration of this is provided in figure \ref{fig:geoconsist}, showing how this loss can help reject erroneous points.
-Given a relative pose $(R_{ij}, T_{ij})$ between two cameras $i$ and $j$  (transforms $j$ to $i$) the epipolar on corresponding feature locations $X_i$ and $X_j$:
-\begin{equation}
-X_{i}^\top \cross{T_{ij}}R_{ij} X_{j} = 0
-\label{eq:essential_constraint_rel}
-\end{equation}
+Given a relative pose $(R_{ij}, T_{ij})$ between two cameras $i$ and $j$  (transforms $j$ to $i$) the epipolar on corresponding feature locations $X_i$ and $X_j$: $X_{i}^\top \cross{T_{ij}}R_{ij} X_{j} = 0$.
 In this work we use the two pose epipolar constraint \cite{tron2014quotient}:
@@
 The constraint assumes that the $X_k$ are calibrated (i.e. the camera intrinsics are known). 
-Given our vertex embeddings matrix $\mat{F}_V$, we can formulate a loss between all cameras $i$ and $j$:
+Given our vertex embeddings matrix $\mF_V$, we can formulate a loss between all cameras $i$ and $j$:
 \begin{align}
-&\mathcal{L}_{ij,geom}(\mat{F}_V) = \nonumber \\ 
-&\sum_{v \in \mathcal{V}(i),u \in \mathcal{V}(j)} \sum_{} (\mat{f}_v \cdot \mat{f}_u) \left|X_{v}^\top R_{i}^\top \cross{T_{j} - T_{i}}R_{c_j} X_{u}\right|
+\mathcal{L}_{ij,geom}(\mF_V) = 
+&\sum_{v \in \mV(i),u \in \mathcal{V}(j)} (\vf_v \cdot \vf_u) \left|X_{v}^\top R_{i}^\top \cross{T_{j} - T_{i}}R_{c_j} X_{u}\right|
 \label{eq:geom_cost}
@@
 With $\mathcal{V}(i)$ being the vertices associated with camera $i$.
-For our purposes, since we use low rank embeddings $\mat{E}_{i}$, $\mat{E}_{j}$, the loss would read:
+For our purposes, since we use low rank embeddings $\mE_{i}$, $\mE_{j}$, the loss would read (where $c(k)$ is the appropriate camera for point index $k$):
 \begin{align} 
-\mathcal{L}_{geom}(\mat{F}_V)
-=&\; \mathrm{tr}(\mat{G}^\top \mat{F}_V\mat{F}_V^\top) = \sum_{k,l} (\mat{F}_V)_{k} \cdot (\mat{F}_V)_{l} (\mat{G})_{kl} \label{eq:geom_cost2} \\
-(\mat{G})_{kl} =&\; \left|X_{k}^\top R_{c(k)}^\top \cross{T_{c(l)} - T_{c(k)}}R_{c(l)} X_{l}\right| \nonumber
+\mathcal{L}_{geom}(\mF_V)
+=&\; \mathrm{tr}(\mG^\top \mF_V\mF_V^\top) = \sum_{k,l} (\mF_V)_{k} \cdot (\mF_V)_{l} (\mG)_{kl} \label{eq:geom_cost2} \\
+(\mG)_{kl} =&\; \left|X_{k}^\top R_{c(k)}^\top \cross{T_{c(l)} - T_{c(k)}}R_{c(l)} X_{l}\right| \nonumber
 \end{align}
-Where $c(k)$ is the appropriate camera for point index $k$.
 
-\begin{table*}
+\begin{table*}[t]
 \begin{center}
@@
 \hline\hline
-MatchALS \cite{zhou2015multi} 15 Iterations          & 0.101 $\pm$ 0.008 & 0.022 $\pm$ 0.004 & 0.918 $\pm$ 0.073 & 0.074 $\pm$ 0.008 \\ \hline
-MatchALS \cite{zhou2015multi} 25 Iterations          & 0.059 $\pm$ 0.010 & 0.012 $\pm$ 0.004 & 0.921 $\pm$ 0.077 & 0.143 $\pm$ 0.064 \\ \hline
-MatchALS \cite{zhou2015multi} 35 Iterations          & 0.046 $\pm$ 0.016 & 0.010 $\pm$ 0.005 & 0.910 $\pm$ 0.072 & 0.139 $\pm$ 0.041 \\ \hline
-MatchALS \cite{zhou2015multi} 50 Iterations          & 0.029 $\pm$ 0.017 & 0.008 $\pm$ 0.005 & 0.905 $\pm$ 0.068 & 0.260 $\pm$ 0.048 \\ \hline
-PGDDS0 \cite{leonardos2016distributed} 15 Iterations & 0.017 $\pm$ 0.002 & 0.007 $\pm$ 0.001 & 0.918 $\pm$ 0.087 & 0.796 $\pm$ 0.147 \\ \hline
-PGDDS0 \cite{leonardos2016distributed} 25 Iterations & 0.016 $\pm$ 0.002 & 0.007 $\pm$ 0.002 & 0.919 $\pm$ 0.087 & 1.670 $\pm$ 0.328 \\ \hline
-PGDDS0 \cite{leonardos2016distributed} 50 Iterations & 0.015 $\pm$ 0.002 & 0.006 $\pm$ 0.002 & 0.920 $\pm$ 0.087 & 3.363 $\pm$ 0.528 \\ \hline
-Spectral \cite{pachauri2013solving}                  & 0.073 $\pm$ 0.006 & 0.027 $\pm$ 0.003 & 0.921 $\pm$ 0.083 & 0.036 $\pm$ 0.005 \\ \hline
+MatchALS 15 Iterations & 0.101 $\pm$ 0.008 & 0.022 $\pm$ 0.004 & 0.918 $\pm$ 0.073 & 0.074 $\pm$ 0.008 \\ \hline
+MatchALS 25 Iterations & 0.059 $\pm$ 0.010 & 0.012 $\pm$ 0.004 & 0.921 $\pm$ 0.077 & 0.143 $\pm$ 0.064 \\ \hline
+MatchALS 35 Iterations & 0.046 $\pm$ 0.016 & 0.010 $\pm$ 0.005 & 0.910 $\pm$ 0.072 & 0.139 $\pm$ 0.041 \\ \hline
+MatchALS 50 Iterations & 0.029 $\pm$ 0.017 & 0.008 $\pm$ 0.005 & 0.905 $\pm$ 0.068 & 0.260 $\pm$ 0.048 \\ \hline
+PGDDS0 15 Iterations   & 0.017 $\pm$ 0.002 & 0.007 $\pm$ 0.001 & 0.918 $\pm$ 0.087 & 0.796 $\pm$ 0.147 \\ \hline
+PGDDS0 25 Iterations   & 0.016 $\pm$ 0.002 & 0.007 $\pm$ 0.002 & 0.919 $\pm$ 0.087 & 1.670 $\pm$ 0.328 \\ \hline
+PGDDS0 50 Iterations   & 0.015 $\pm$ 0.002 & 0.006 $\pm$ 0.002 & 0.920 $\pm$ 0.087 & 3.363 $\pm$ 0.528 \\ \hline
+Spectral               & 0.073 $\pm$ 0.006 & 0.027 $\pm$ 0.003 & 0.921 $\pm$ 0.083 & 0.036 $\pm$ 0.005 \\ \hline
 \textbf{GNN (ours)}    & 0.044 $\pm$ 0.005 & 0.031 $\pm$ 0.005 & 0.872 $\pm$ 0.081 & 0.765 $\pm$ 0.046 \\ \hline
@@
 \hline\hline
-MatchALS \cite{zhou2015multi} 15 Iterations         & 0.114 $\pm$ 0.008 & 0.028 $\pm$ 0.004 & 0.915 $\pm$ 0.051 & 0.142 $\pm$ 0.009 \\ \hline
-MatchALS \cite{zhou2015multi} 25 Iterations         & 0.092 $\pm$ 0.008 & 0.019 $\pm$ 0.003 & 0.912 $\pm$ 0.055 & 0.228 $\pm$ 0.014 \\ \hline
-MatchALS \cite{zhou2015multi} 35 Iterations         & 0.065 $\pm$ 0.009 & 0.013 $\pm$ 0.003 & 0.907 $\pm$ 0.053 & 0.355 $\pm$ 0.073 \\ \hline
-MatchALS \cite{zhou2015multi} 50 Iterations         & 0.045 $\pm$ 0.012 & 0.011 $\pm$ 0.004 & 0.914 $\pm$ 0.051 & 0.455 $\pm$ 0.022 \\ \hline
-PGDDS \cite{leonardos2016distributed} 15 Iterations & 0.017 $\pm$ 0.001 & 0.008 $\pm$ 0.001 & 0.903 $\pm$ 0.061 & 1.225 $\pm$ 0.159 \\ \hline
-PGDDS \cite{leonardos2016distributed} 25 Iterations & 0.016 $\pm$ 0.001 & 0.007 $\pm$ 0.001 & 0.904 $\pm$ 0.061 & 2.637 $\pm$ 0.357 \\ \hline
-PGDDS \cite{leonardos2016distributed} 50 Iterations & 0.016 $\pm$ 0.001 & 0.007 $\pm$ 0.001 & 0.905 $\pm$ 0.061 & 6.116 $\pm$ 1.009 \\ \hline
-Spectral \cite{pachauri2013solving}                 & 0.073 $\pm$ 0.005 & 0.029 $\pm$ 0.002 & 0.912 $\pm$ 0.057 & 0.081 $\pm$ 0.021 \\ \hline
+MatchALS 15 Iterations & 0.114 $\pm$ 0.008 & 0.028 $\pm$ 0.004 & 0.915 $\pm$ 0.051 & 0.142 $\pm$ 0.009 \\ \hline
+MatchALS 25 Iterations & 0.092 $\pm$ 0.008 & 0.019 $\pm$ 0.003 & 0.912 $\pm$ 0.055 & 0.228 $\pm$ 0.014 \\ \hline
+MatchALS 35 Iterations & 0.065 $\pm$ 0.009 & 0.013 $\pm$ 0.003 & 0.907 $\pm$ 0.053 & 0.355 $\pm$ 0.073 \\ \hline
+MatchALS 50 Iterations & 0.045 $\pm$ 0.012 & 0.011 $\pm$ 0.004 & 0.914 $\pm$ 0.051 & 0.455 $\pm$ 0.022 \\ \hline
+PGDDS 15 Iterations    & 0.017 $\pm$ 0.001 & 0.008 $\pm$ 0.001 & 0.903 $\pm$ 0.061 & 1.225 $\pm$ 0.159 \\ \hline
+PGDDS 25 Iterations    & 0.016 $\pm$ 0.001 & 0.007 $\pm$ 0.001 & 0.904 $\pm$ 0.061 & 2.637 $\pm$ 0.357 \\ \hline
+PGDDS 50 Iterations    & 0.016 $\pm$ 0.001 & 0.007 $\pm$ 0.001 & 0.905 $\pm$ 0.061 & 6.116 $\pm$ 1.009 \\ \hline
+Spectral               & 0.073 $\pm$ 0.005 & 0.029 $\pm$ 0.002 & 0.912 $\pm$ 0.057 & 0.081 $\pm$ 0.021 \\ \hline
 \textbf{GNN (ours)}    & 0.053 $\pm$ 0.006 & 0.035 $\pm$ 0.005 & 0.872 $\pm$ 0.061 & 2.438 $\pm$ 0.070 \\ \hline
@@
 Our method was not trained on ground truth correspondences but using unsupervised methods and geometric side losses.
-As our method gives soft labels, we use cannot use precision or recall as is standard in testing cycle consistency \cite{zhou2015multi}.
 Thus we test against ground truth correspondence graph adjacency matrices computed from the bundle adjustment output.
@@
 We do not perform as well as the Projected Gradient Descent Doubly Stochastic (PGDDS) \cite{leonardos2016distributed} but we perform significantly faster than them.
+We perform better than a simple eigenvalue based method \cite{pachauri2013solving}.
 Note that we perform much better in $L_1$ performance rather than $L_2$, as we optimized the network weights using an $L_1$ loss.
@@
 \section{Experiments}
-
-\begin{figure*}
-\begin{center}
-  % \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
-  \includegraphics[width=0.8\linewidth]{figures-GeometricLoss.pdf}
-  \end{center}
-    \caption{
-      Training curves with and without Geometric Training loss, described in \ref{eq:geom_cost2}.
-      The geometric training loss improves testing performance.
-      While the training is higher due to the additional loss terms, the ground truth L1 error is substantially better with the Geometric Loss.
-    }
-  \label{fig:short}
-  \label{fig:geomloss}
-\end{figure*}
 
@@
 % \end{figure*}
+
 \subsection{Synthetic Graph Dataset}
@@
 
-\begin{figure*}[t]
-\begin{center}
-  % \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
-  \includegraphics[width=0.7\linewidth]{figures-error_lines.pdf}
-  \end{center}
+\begin{figure}[t]
+\centering
+\begin{subfigure}[b]{.70\textwidth}
+  \centering
+  % \includegraphics[width=0.95\linewidth]{figures-error_lines.pdf}
+  \includegraphics[height=200px]{figures-error_lines.pdf}
+  \caption{}
+  \label{fig:3a}
+  \label{fig:errorlines}
+\end{subfigure}
+\begin{subfigure}[b]{.25\textwidth}
+  \centering
+  % \includegraphics[width=0.65\linewidth]{figures-GeometricLoss.pdf}
+  \includegraphics[height=200px]{figures-GeometricLoss.pdf}
+  \caption{}
+  \label{fig:3b}
+  \label{fig:geomloss}
+\end{subfigure}
 \caption{
-         Plot of the losses of the baselines at different iteration numbers.
+  \textbf{(a)} Plot of the losses of the baselines at different iteration numbers.
   The line shows the mean of the graph while the translucent coloring shows the $25^{th}$ to $75^{th}$ percentiles.
@@
   PGDDS performs better than us in $L_1$ but we perform similarly in the ROC AUC metric.
+  \textbf{(b)} Training curves with and without Geometric Training loss, described in \ref{eq:geom_cost2}.
+  The geometric training loss improves testing performance.
+  While the training is higher due to the additional loss terms, the ground truth L1 error is substantially better with the Geometric Loss.
+  Best viewed in color.
 }
-  % \label{fig:twocol}
-  \label{fig:errorlines}
-\end{figure*}
+\label{fig:3}
+\end{figure}
 
@@
 For the initial embedding we use the original 128 dimensional SIFT descriptors, normalized to have unit $L_2$ norm, the calibrated x-y position, the orientation, and log scale of the SIFT feature.
-To construct the graph, we take each feature as a vertex and create an edge between the 5 nearest features in each other image in SIFT descriptor space.
+To construct the graph, we take each feature as a vertex and create edges to the 5 nearest SIFT descriptors for the other images.
 
@@
 
-\begin{figure}[t]
-\begin{center}
-  % \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
-  \includegraphics[width=0.7\linewidth]{figures-EmbeddingsViz.png}
-  \end{center}
-     \caption{
-         Visualization of the learned embeddings.
-         On the left we have the raw outputs, which are difficult to interpret.
-         In the center, we rotated the features to best match the ground truth for a more interpretable visualization.
-         On the right, we have the ground truth embeddings, given as indicator vectors for which feature in the world the points correspond to.
-     }
-  \label{fig:onecol}
-  \label{fig:embeddingsviz}
-\end{figure}
+% \begin{figure}[t]
+% \begin{center}
+%   % \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
+%   \includegraphics[width=0.7\linewidth]{figures-EmbeddingsViz.png}
+%   \end{center}
+%      \caption{
+%          Visualization of the learned embeddings.
+%          On the left we have the raw outputs, which are difficult to interpret.
+%          In the center, we rotated the features to best match the ground truth for a more interpretable visualization.
+%          On the right, we have the ground truth embeddings, given as indicator vectors for which feature in the world the points correspond to.
+%      }
+%   \label{fig:embeddingsviz}
+% \end{figure}
 %------------------------------------------------------------------------
@@
 %
-{\small
-\bibliographystyle{ieee}
+
+\bibliographystyle{iclr2020_conference}
 \bibliography{egbib}
-}
+
+% \appendix
+% \section{Appendix}
+% You may include other additional sections here.
 
 \end{document}
-
-% Method (6 Views)                                     & $L_1$             & $L_2$             & Area under ROC    & Area Prec.-Recall & Time (sec)        \ \hline
-% MatchALS \cite{zhou2015multi} 15 Iterations          & 0.101 $\pm$ 0.008 & 0.022 $\pm$ 0.004 & 0.918 $\pm$ 0.073 & 0.752 $\pm$ 0.160 & 0.074 $\pm$ 0.008 \\ \hline
-% MatchALS \cite{zhou2015multi} 25 Iterations          & 0.059 $\pm$ 0.010 & 0.012 $\pm$ 0.004 & 0.921 $\pm$ 0.077 & 0.767 $\pm$ 0.181 & 0.143 $\pm$ 0.064 \\ \hline
-% MatchALS \cite{zhou2015multi} 35 Iterations          & 0.046 $\pm$ 0.016 & 0.010 $\pm$ 0.005 & 0.910 $\pm$ 0.072 & 0.742 $\pm$ 0.165 & 0.139 $\pm$ 0.041 \\ \hline
-% MatchALS \cite{zhou2015multi} 50 Iterations          & 0.029 $\pm$ 0.017 & 0.008 $\pm$ 0.005 & 0.905 $\pm$ 0.068 & 0.707 $\pm$ 0.166 & 0.260 $\pm$ 0.048 \\ \hline
-% PGDDS0 \cite{leonardos2016distributed} 15 Iterations & 0.017 $\pm$ 0.002 & 0.007 $\pm$ 0.001 & 0.918 $\pm$ 0.087 & 0.727 $\pm$ 0.180 & 0.796 $\pm$ 0.147 \\ \hline
-% PGDDS0 \cite{leonardos2016distributed} 25 Iterations & 0.016 $\pm$ 0.002 & 0.007 $\pm$ 0.002 & 0.919 $\pm$ 0.087 & 0.773 $\pm$ 0.184 & 1.670 $\pm$ 0.328 \\ \hline
-% PGDDS0 \cite{leonardos2016distributed} 50 Iterations & 0.015 $\pm$ 0.002 & 0.006 $\pm$ 0.002 & 0.920 $\pm$ 0.087 & 0.798 $\pm$ 0.183 & 3.363 $\pm$ 0.528 \\ \hline
-% Spectral                                             & 0.073 $\pm$ 0.006 & 0.027 $\pm$ 0.003 & 0.921 $\pm$ 0.083 & 0.670 $\pm$ 0.163 & 0.036 $\pm$ 0.005 \\ \hline
-% GNN (ours)                                           & 0.044 $\pm$ 0.005 & 0.031 $\pm$ 0.005 & 0.872 $\pm$ 0.081 & 0.377 $\pm$ 0.062 & 0.765 $\pm$ 0.046 \\ \hline
-% Method (10 Views)                                   & $L_1$             & $L_2$             & Area under ROC    & Area Prec.-Recall & Time (sec)        \ \hline
-% \hline\hline
-% MatchALS \cite{zhou2015multi} 10 Iterations         & 0.098 $\pm$ 0.007 & 0.023 $\pm$ 0.004 & 0.909 $\pm$ 0.052 & 0.679 $\pm$ 0.151 & 0.151 $\pm$ 0.026 \\ \hline
-% MatchALS \cite{zhou2015multi} 15 Iterations         & 0.114 $\pm$ 0.008 & 0.028 $\pm$ 0.004 & 0.915 $\pm$ 0.051 & 0.756 $\pm$ 0.125 & 0.142 $\pm$ 0.009 \\ \hline
-% MatchALS \cite{zhou2015multi} 20 Iterations         & 0.111 $\pm$ 0.008 & 0.024 $\pm$ 0.004 & 0.915 $\pm$ 0.053 & 0.784 $\pm$ 0.121 & 0.300 $\pm$ 0.131 \\ \hline
-% MatchALS \cite{zhou2015multi} 25 Iterations         & 0.092 $\pm$ 0.008 & 0.019 $\pm$ 0.003 & 0.912 $\pm$ 0.055 & 0.794 $\pm$ 0.123 & 0.228 $\pm$ 0.014 \\ \hline
-% MatchALS \cite{zhou2015multi} 30 Iterations         & 0.075 $\pm$ 0.008 & 0.015 $\pm$ 0.003 & 0.911 $\pm$ 0.056 & 0.773 $\pm$ 0.130 & 0.305 $\pm$ 0.056 \\ \hline
-% MatchALS \cite{zhou2015multi} 35 Iterations         & 0.065 $\pm$ 0.009 & 0.013 $\pm$ 0.003 & 0.907 $\pm$ 0.053 & 0.741 $\pm$ 0.130 & 0.355 $\pm$ 0.073 \\ \hline
-% MatchALS \cite{zhou2015multi} 40 Iterations         & 0.058 $\pm$ 0.010 & 0.012 $\pm$ 0.004 & 0.906 $\pm$ 0.051 & 0.733 $\pm$ 0.125 & 0.386 $\pm$ 0.052 \\ \hline
-% MatchALS \cite{zhou2015multi} 45 Iterations         & 0.050 $\pm$ 0.011 & 0.011 $\pm$ 0.004 & 0.911 $\pm$ 0.051 & 0.730 $\pm$ 0.126 & 0.440 $\pm$ 0.102 \\ \hline
-% MatchALS \cite{zhou2015multi} 50 Iterations         & 0.045 $\pm$ 0.012 & 0.011 $\pm$ 0.004 & 0.914 $\pm$ 0.051 & 0.732 $\pm$ 0.130 & 0.455 $\pm$ 0.022 \\ \hline
-% PGDDS \cite{leonardos2016distributed} 10 Iterations & 0.017 $\pm$ 0.001 & 0.008 $\pm$ 0.001 & 0.903 $\pm$ 0.061 & 0.689 $\pm$ 0.125 & 1.334 $\pm$ 0.357 \\ \hline
-% PGDDS \cite{leonardos2016distributed} 15 Iterations & 0.017 $\pm$ 0.001 & 0.008 $\pm$ 0.001 & 0.903 $\pm$ 0.061 & 0.688 $\pm$ 0.125 & 1.225 $\pm$ 0.159 \\ \hline
-% PGDDS \cite{leonardos2016distributed} 20 Iterations & 0.017 $\pm$ 0.001 & 0.008 $\pm$ 0.001 & 0.903 $\pm$ 0.061 & 0.688 $\pm$ 0.125 & 1.347 $\pm$ 0.299 \\ \hline
-% PGDDS \cite{leonardos2016distributed} 25 Iterations & 0.016 $\pm$ 0.001 & 0.007 $\pm$ 0.001 & 0.904 $\pm$ 0.061 & 0.737 $\pm$ 0.127 & 2.637 $\pm$ 0.357 \\ \hline
-% PGDDS \cite{leonardos2016distributed} 50 Iterations & 0.016 $\pm$ 0.001 & 0.007 $\pm$ 0.001 & 0.905 $\pm$ 0.061 & 0.763 $\pm$ 0.127 & 6.116 $\pm$ 1.009 \\ \hline
-% Spectral \cite{pachauri2013solving}                 & 0.073 $\pm$ 0.005 & 0.029 $\pm$ 0.002 & 0.912 $\pm$ 0.057 & 0.684 $\pm$ 0.109 & 0.081 $\pm$ 0.021 \\ \hline
-% \textbf{GNN (ours)}                                 & 0.053 $\pm$ 0.006 & 0.035 $\pm$ 0.005 & 0.872 $\pm$ 0.061 & 0.330 $\pm$ 0.050 & 2.438 $\pm$ 0.070 \\ \hline

### 2019-09-21 data_util/graffiti_dataset.py
Added graffiti loading to dataset

@@ -1,0 +1,228 @@
+import os
+import sys
+import numpy as np
+import scipy.linalg as la
+import imageio
+import networkx as nx
+import functools
+
+import tensorflow as tf
+import cv2
+from graph_nets import utils_np
+
+from data_util import graph_dataset
+from data_util import tf_helpers
+
+
+def size_to_octave_desc(s, octv_size=3.6, nlayers=3):
+  octv = np.log2(s / octv_size)
+  octave = int(np.floor(octv))
+  layer  = int(np.floor(nlayers * octv) - nlayers*octave) + 1
+  if octave < -1: # This is apparently the minimum
+    octave, layer = -1, 1
+  return (octave & 255) | ((layer & 255) << 8)
+
+def get_size_angle(x0, y0, H, kpt):
+  s = kpt.size
+  theta = kpt.angle
+  dx_, dy_ = np.cos(np.deg2rad(theta)), -np.sin(np.deg2rad(theta))
+  x_0, y_0, _ = tuple(h_apply(H, (x0+s*dx_, y0+s*dy_, 1)))
+  x_1, y_1, _ = tuple(h_apply(H, (x0-s*dy_, y0+s*dx_, 1)))
+  x_2, y_2, _ = tuple(h_apply(H, (x0+s*dy_, y0-s*dx_, 1)))
+  x_3, y_3, _ = tuple(h_apply(H, (x0-s*dx_, y0-s*dy_, 1)))
+  size_new = np.mean([ np.linalg.norm((x_0 - x_3, y_0 - y_3))/2,
+                       np.linalg.norm(((x_1 - x_2, y_1 - y_2)))/2 ])
+  angle_new = np.arctan2(-y_0 + y_3, x_0 - x_3)
+  angle_new = np.rad2deg(angle_new + 2*np.pi*(angle_new < 0))
+  return size_new, angle_new
+
+def h_apply(H, x):
+  y = H @ x
+  return y / y[-1]
+
+def dist_mat(x,y):
+  x2 = np.sum(x**2, 0).reshape(-1,1)
+  y2 = np.sum(y**2, 0).reshape(1,-1)
+  Dist = np.sqrt(x2 + y2 - x.T @ y - y.T @ x)
+  return Dist
+
+def row_comp(x, thresh):
+  Xstr = ''.join([ '0' if x_ < thresh else '1' for x_ in x ])
+  return Xstr
+
+def distint_locs(xy, thresh):
[…]

### 2019-09-23 latex/iclr2020/main.tex
Fixed up more formatting issues

@@
 The goal in multi-image feature matching is to take 2D image locations from three or more images and find which ones correspond to the same point in the 3D scene.
-Methods such as SIFT feature matching \cite{lowe2004distinctive} followed by RANSAC \cite{fischler1981random} have been the standard for decades.
+Methods such as SIFT feature matching (\cite{lowe2004distinctive}) followed by RANSAC (\cite{fischler1981random}) have been the standard for decades.
 However RANSAC-based approaches are limited to matching pairs of images, which can lead to global inconsistencies in the matching.
@@
 However, these multi-view consistency algorithms struggle in distributed and robust settings.
-Having image features suited for this task would help improve performance, and deep learning has revolutionized how image features are computed \cite{yi2016lift}.
+Having image features suited for this task would help improve performance, and deep learning has revolutionized how image features are computed (\cite{yi2016lift}).
 In this paper, we want to leverage the power of deep representations in order to compute feature descriptors that are robust across multiple views.
@@
     An illustration of the approach of this work.
-    The Graph Neural Neural Network (GNN) \cite{battaglia2018relational} takes as input the graph of matches and then outputs a low rank embedding of the adjacency matrix of the graph.
+    The Graph Neural Neural Network (GNN) (\cite{battaglia2018relational}) takes as input the graph of matches and then outputs a low rank embedding of the adjacency matrix of the graph.
     The GNN operates on an embedding over the vertices of the graph.
@@
 Geometric consistency losses can aid training, even if such information is not available at test time.
-Although our network is simple, it shows promising results compared to baselines which optimize for cycle-consistency without learned embeddings, using a matrix factorization loss \cite{zhou2015multi, leonardos2016distributed}.
+Although our network is simple, it shows promising results compared to baselines which optimize for cycle-consistency without learned embeddings, using a matrix factorization loss (\cite{zhou2015multi, leonardos2016distributed}).
 Furthermore, since inference requires only a single forward pass over the neural network, our approach is faster (to achieve comparable accuracy) than methods which must solve an optimization problem every time.
-We perform experiments on the Rome16K \cite{li2010location} dataset to test the effectiveness of our method compared to optimization based methods.
+We perform experiments on the Rome16K dataset (\cite{li2010location}) to test the effectiveness of our method compared to optimization based methods.
 Our contributions in this work are:
@@
 Matching has a rich history of research in computer vision.
-Much work has be done using hand-crafted feature descriptors such as SIFT \cite{lowe2004distinctive}, SURF \cite{bay2006surf}, BRIEF \cite{calonder2012brief}, or ORB \cite{mur2015orb}.
+Much work has be done using hand-crafted feature descriptors such as SIFT (\cite{lowe2004distinctive}), SURF (\cite{bay2006surf}), BRIEF (\cite{calonder2012brief}), or ORB (\cite{mur2015orb}).
 RANSAC \cite{fischler1981random} is the most widely used robust estimation technique to filter out outliers from the matches.
 The combination of RANSAC and hand-crafted feature descriptors has constituted the bulk of the matching literature for the last 40 years.
-Finally, graph matching \cite{suh2015subgraph, hu2016distributable} can be used as a final step for more robust matches.
+Finally, graph matching (\cite{suh2015subgraph, hu2016distributable}) can be used as a final step for more robust matches.
 
@@
 Multi-image matching has traditionally been done using optimization based methods minimizing a cycle consistency based loss (see Section 3.3).
-Pachauri et al.~\cite{pachauri2013solving} and Arrigoni et al.~\cite{arrigoni2017synchronization} use the eigenvectors of the matching matrix to obtain a low dimensional embedding. 
+\cite{pachauri2013solving} and \cite{arrigoni2017synchronization} use the eigenvectors of the matching matrix to obtain a low dimensional embedding. 
 However, the low Gaussian noise assumption is not realistic.
-Zhou et al.~\cite{zhou2015multi} and Wang et al.~\cite{wang2017multi} use most sophisticated optimization techniques on the matching matrix and thus produce more robust solutions.
-Leonardos et al.~\cite{leonardos2016distributed} implement a distributed optimization scheme to solve for cycle consistency.
-As an alternative to optimization based techniques, Tron et al.~\cite{tron2017fast} used density based clustering techniques to compute multi-image correspondence.
+\cite{zhou2015multi} and \cite{wang2017multi} use most sophisticated optimization techniques on the matching matrix and thus produce more robust solutions.
+\cite{leonardos2016distributed} implement a distributed optimization scheme to solve for cycle consistency.
+As an alternative to optimization based techniques, \cite{tron2017fast} used density based clustering techniques to compute multi-image correspondence.
 To the best of our knowledge, we are the first to use neural networks for multi-image matching.
@@
 \subsection{Deep Learning for Matching}
-Previous attempts to improve image matching techniques using machine learning have focused on learning the descriptors given ground truth correspondence from curated datasets \cite{zagoruyko2015learning, yi2016lift, brachmann2017dsac}.
+Previous attempts to improve image matching techniques using machine learning have focused on learning the descriptors given ground truth correspondence from curated datasets such as \cite{zagoruyko2015learning}; \cite{yi2016lift}; and \cite{brachmann2017dsac}.
 This approach is limited if one do not have the ability to get the ground truth correspondences.
-There are other methods to build correspondences such as Choy et al.~\cite{choy2016universal}, but they only handle two-view constraints and require dense correspondences.
-Most similar to our work, Yi et al.~\cite{yi2018learning} attempts to improve correspondences by learning match probabilities for RANSAC for greater robustness and speed.
+There are other methods to build correspondences such as \cite{choy2016universal}, but they only handle two-view constraints and require dense correspondences.
+Most similar to our work, \cite{yi2018learning} attempts to improve correspondences by learning match probabilities for RANSAC for greater robustness and speed.
 However, they only focus on two view matching and do not exploit the advantages of the correspondence structure.
-Note that while Zhu et al.~\cite{zhu2017unpaired} use cycle consistency in their loss, their method is restricted to pairwise cycle consistency (i.e.
+Note that while \cite{zhu2017unpaired} use cycle consistency in their loss, their method is restricted to pairwise cycle consistency (i.e.
 enforcing consistency by going back and forth between two images).
@@
 \subsection{Graph Neural Networks}
-Graph neural networks have recieved more attention recently \cite{bronstein2017geometric, bruna2013spectral, defferrard2016convolutional, kipf2017semi, scarselli2009graph, gama2018mimo, gama2018convolutional, battaglia2018relational}.
-Classical so-called Spectral methods used the eigenvectors of the graph Laplacian to compute convolutions as in Bruna et al.~\cite{bruna2013spectral}, but requires an a-priori known graph structure. 
-Non-spectral methods do not require a-priori knowledge \cite{bronstein2017geometric, kipf2017semi, scarselli2009graph, gama2018convolutional}.
+Graph neural networks have recieved more attention recently e.g.
+\cite{bronstein2017geometric, bruna2013spectral, defferrard2016convolutional, kipf2017semi, scarselli2009graph, gama2018mimo, gama2018convolutional}; and \cite{battaglia2018relational}.
+Classical so-called Spectral methods used the eigenvectors of the graph Laplacian to compute convolutions as in \cite{bruna2013spectral}, but requires an a-priori known graph structure. 
+Non-spectral methods do not require a-priori knowledge, as seen in \cite{bronstein2017geometric, kipf2017semi, scarselli2009graph}; and \cite{gama2018convolutional}.
 Most of these methods use polynomials of the graph Laplacian to compute neighborhood averages.
-Gama et al.~2018 \cite{gama2018mimo, gama2018convolutional} formalize this notion and generalize it beyond the use of the graph Laplacian.
-To improve performance, more sophisticated aggregation techniques and global information passing can be used as discussed in Battaglia et al.~\cite{battaglia2018relational}.
+\cite{gama2018mimo, gama2018convolutional} formalize this notion and generalize it beyond the use of the graph Laplacian.
+To improve performance, more sophisticated aggregation techniques and global information passing can be used as discussed in \cite{battaglia2018relational}.
 
@@
 The graph is constructed from putative correspondences of image features across images, typically constructed using feature descriptor distance (e.g. SIFT feature distance).
-While there are many interesting methods for computing these putative correspondences \cite{suh2015subgraph, yi2018learning}, we do not explore them in this work.
+While there are many interesting methods for computing these putative correspondences (\cite{suh2015subgraph, yi2018learning}), we do not explore them in this work.
 Typically putative correspondences are matched probabilistically, meaning a feature in one image matches to many features in another.
@@
 However, we do not have this luxury, as the correspondence structure changes from image set to image set, and thus we use non-spectral Graph Neural Networks.
-There are many variations on non-spectral methods, often which ultimately amount to message passing between vertices of the graph with learned non-linear transformations between various steps \cite{kipf2017semi, defferrard2016convolutional, gama2018mimo, gama2018convolutional}.
+There are many variations on non-spectral methods, often which ultimately amount to message passing between vertices of the graph with learned non-linear transformations between various steps (\cite{kipf2017semi, defferrard2016convolutional, gama2018mimo, gama2018convolutional}).
 Some works such as \cite{gama2019convolutional} use pooling operations on the vertices to make the graph smaller and thus aid computation, but as we need labels on every vertex of the original graph, so we cannot use this.
@@
 In other words, the matches between two images stay the same no matter what path is taken to get there. 
-This constraint is known as \textit{cycle consistency}, and has been used in a number of works to optimize for global consistency \cite{zhou2015multi, wang2017multi, leonardos2016distributed}.
+This constraint is known as \textit{cycle consistency}, and has been used in a number of works to optimize for global consistency (\cite{zhou2015multi, wang2017multi, leonardos2016distributed}).
 Stated in this form, there are $O(n^3)$ cycle consistency constraints to check.
@@
 Given a relative pose $(R_{ij}, T_{ij})$ between two cameras $i$ and $j$  (transforms $j$ to $i$) the epipolar on corresponding feature locations $X_i$ and $X_j$: $X_{i}^\top \cross{T_{ij}}R_{ij} X_{j} = 0$.
-In this work we use the two pose epipolar constraint \cite{tron2014quotient}:
+In this work we use the two pose epipolar constraint (\cite{tron2014quotient}):
 \begin{equation}
@@
 MatchALS 15 Iterations & 0.101 $\pm$ 0.008 & 0.022 $\pm$ 0.004 & 0.918 $\pm$ 0.073 & 0.074 $\pm$ 0.008 \\ \hline
-MatchALS 25 Iterations & 0.059 $\pm$ 0.010 & 0.012 $\pm$ 0.004 & 0.921 $\pm$ 0.077 & 0.143 $\pm$ 0.064 \\ \hline
 MatchALS 35 Iterations & 0.046 $\pm$ 0.016 & 0.010 $\pm$ 0.005 & 0.910 $\pm$ 0.072 & 0.139 $\pm$ 0.041 \\ \hline
@@
 \hline\hline
-MatchALS 15 Iterations & 0.114 $\pm$ 0.008 & 0.028 $\pm$ 0.004 & 0.915 $\pm$ 0.051 & 0.142 $\pm$ 0.009 \\ \hline
 MatchALS 25 Iterations & 0.092 $\pm$ 0.008 & 0.019 $\pm$ 0.003 & 0.912 $\pm$ 0.055 & 0.228 $\pm$ 0.014 \\ \hline
@@
 Thus we test against ground truth correspondence graph adjacency matrices computed from the bundle adjustment output.
-Our method performs better than 25 iteration of the MatchALS \cite{zhou2015multi} method, but does not perform as well as 50 iterations.
+Our method performs better than 25 iteration of the MatchALS (\cite{zhou2015multi}) method, but does not perform as well as 50 iterations.
 % Our network has only 12 layers, thus we have much greater efficiency per iteration.
-We do not perform as well as the Projected Gradient Descent Doubly Stochastic (PGDDS) \cite{leonardos2016distributed} but we perform significantly faster than them.
-We perform better than a simple eigenvalue based method \cite{pachauri2013solving}.
+We do not perform as well as the Projected Gradient Descent Doubly Stochastic (PGDDS) (\cite{leonardos2016distributed}) but we perform significantly faster than them.
+We perform better than a simple eigenvalue based method (\cite{pachauri2013solving}).
 Note that we perform much better in $L_1$ performance rather than $L_2$, as we optimized the network weights using an $L_1$ loss.
@@
 We first test our method on synthetically generated data as a simple proof of concept.
-As these were simpler datasets, we the simpler edge-feature free model of \cite{kipf2017semi}.
+As these were simpler datasets, we the simpler edge-feature free model of (\cite{kipf2017semi}).
 To generate the data, we generate $p$ points, each with its own randomly generated descriptor.
@@
 The feature vector lengths were 32, 64, 128, 256, 512, 512, 512, 512, 512, 512, 1024, 1024, with skip connections between layers 1 and 6, 6 and 12, and 1 and 12.
-All were trained with the Adam optimizer \cite{kingma2014adam} and a learning rate $10^{-4}$
-The network was implemented in Tensorflow \cite{tensorflow2015}, version 1.11.
+All were trained with the Adam optimizer (\cite{kingma2014adam}) and a learning rate $10^{-4}$
+The network was implemented in Tensorflow (\cite{tensorflow2015}), version 1.11.
 With this simple test on synthetic data passed, we now move to more challenging datasets.
@@
 \subsection{Rome 16K Graph Dataset}
-We  use the Rome16K dataset \cite{li2010location} to test our algorithm in real world settings.
+We  use the Rome16K dataset (\cite{li2010location}) to test our algorithm in real world settings.
 Rome16K consists of 16 thousand images of various historical sites in Rome extracted from Flickr, along with the 3D structure of the sites provided by bundle adjustment.
@@
 
-The network was implemented using the code provided by \cite{battaglia2018relational} using Tensorflow \cite{tensorflow2015} 1.11.
+The network was implemented using the code provided by \cite{battaglia2018relational} using Tensorflow 1.11 (\cite{tensorflow2015}).
 Our network has 16 layers, with 8 message passing operations placed every other layer.
 All layers were simple Multi-layer Perceptrons, with no batch norm.
-The network was trained with the Adam optimizer \cite{kingma2014adam} with a learning rate of $10^{-4}$, with an exponentially decaying learning rate.
+The network was trained with the Adam optimizer (\cite{kingma2014adam}) with a learning rate of $10^{-4}$, with an exponentially decaying learning rate.
 We incorporate skip connections between the input, $6^{th}$, and $12^{th}$ layers (all possible pairs).
@@
 Figure \ref{fig:errorlines} illustrates this by plotting the means of various metrics and their $25^{th}$ and $75^{th}$ percentiles, with table \ref{tab:rome16ktab} giving the exact numbers.
-Our network, though only using 8 message passes, has comparable accuracy to MatchALS \cite{zhou2015multi} run 35 to 45 iterations, with an equivalent message passing step at each phase.
-Although our method does not outperform the Projected Gradient Descent - Doubly Stochastic (PGDDS) \cite{leonardos2016distributed} method, we perform comparably to them in the ROC AUC metric.
+Our network, though only using 8 message passes, has comparable accuracy to MatchALS (\cite{zhou2015multi}) run 35 to 45 iterations, with an equivalent message passing step at each phase.
+Although our method does not outperform the Projected Gradient Descent - Doubly Stochastic (PGDDS) (\cite{leonardos2016distributed}) method, we perform comparably to them in the ROC AUC metric.
 % Our network, though only 12 layers, has comparable accuracy to MatchALS \cite{zhou2015multi} run between 25 and 50 iterations.
@@
 \end{document}
+
+% \begin{table*}[t]
+% \begin{center}
+% \begin{tabular}{|l|c|c|c|c|}
+% \hline
+% Method (6 Views)                                     & $L_1$             & $L_2$             & Area under ROC    & Time (sec)        \\
+% \hline\hline
+% MatchALS 15 Iterations & 0.101 $\pm$ 0.008 & 0.022 $\pm$ 0.004 & 0.918 $\pm$ 0.073 & 0.074 $\pm$ 0.008 \\ \hline
+% MatchALS 25 Iterations & 0.059 $\pm$ 0.010 & 0.012 $\pm$ 0.004 & 0.921 $\pm$ 0.077 & 0.143 $\pm$ 0.064 \\ \hline
+% MatchALS 35 Iterations & 0.046 $\pm$ 0.016 & 0.010 $\pm$ 0.005 & 0.910 $\pm$ 0.072 & 0.139 $\pm$ 0.041 \\ \hline
+% MatchALS 50 Iterations & 0.029 $\pm$ 0.017 & 0.008 $\pm$ 0.005 & 0.905 $\pm$ 0.068 & 0.260 $\pm$ 0.048 \\ \hline
+% PGDDS0 15 Iterations   & 0.017 $\pm$ 0.002 & 0.007 $\pm$ 0.001 & 0.918 $\pm$ 0.087 & 0.796 $\pm$ 0.147 \\ \hline
+% PGDDS0 25 Iterations   & 0.016 $\pm$ 0.002 & 0.007 $\pm$ 0.002 & 0.919 $\pm$ 0.087 & 1.670 $\pm$ 0.328 \\ \hline
+% PGDDS0 50 Iterations   & 0.015 $\pm$ 0.002 & 0.006 $\pm$ 0.002 & 0.920 $\pm$ 0.087 & 3.363 $\pm$ 0.528 \\ \hline
+% Spectral               & 0.073 $\pm$ 0.006 & 0.027 $\pm$ 0.003 & 0.921 $\pm$ 0.083 & 0.036 $\pm$ 0.005 \\ \hline
+% \textbf{GNN (ours)}    & 0.044 $\pm$ 0.005 & 0.031 $\pm$ 0.005 & 0.872 $\pm$ 0.081 & 0.765 $\pm$ 0.046 \\ \hline
+% 
+% \hline\hline
+% Method (10 Views)                                   & $L_1$             & $L_2$             & Area under ROC    & Time (sec)        \\
+% \hline\hline
+% MatchALS 15 Iterations & 0.114 $\pm$ 0.008 & 0.028 $\pm$ 0.004 & 0.915 $\pm$ 0.051 & 0.142 $\pm$ 0.009 \\ \hline
+% MatchALS 25 Iterations & 0.092 $\pm$ 0.008 & 0.019 $\pm$ 0.003 & 0.912 $\pm$ 0.055 & 0.228 $\pm$ 0.014 \\ \hline
+% MatchALS 35 Iterations & 0.065 $\pm$ 0.009 & 0.013 $\pm$ 0.003 & 0.907 $\pm$ 0.053 & 0.355 $\pm$ 0.073 \\ \hline
+% MatchALS 50 Iterations & 0.045 $\pm$ 0.012 & 0.011 $\pm$ 0.004 & 0.914 $\pm$ 0.051 & 0.455 $\pm$ 0.022 \\ \hline
+% PGDDS 15 Iterations    & 0.017 $\pm$ 0.001 & 0.008 $\pm$ 0.001 & 0.903 $\pm$ 0.061 & 1.225 $\pm$ 0.159 \\ \hline
+% PGDDS 25 Iterations    & 0.016 $\pm$ 0.001 & 0.007 $\pm$ 0.001 & 0.904 $\pm$ 0.061 & 2.637 $\pm$ 0.357 \\ \hline
+% PGDDS 50 Iterations    & 0.016 $\pm$ 0.001 & 0.007 $\pm$ 0.001 & 0.905 $\pm$ 0.061 & 6.116 $\pm$ 1.009 \\ \hline
+% Spectral               & 0.073 $\pm$ 0.005 & 0.029 $\pm$ 0.002 & 0.912 $\pm$ 0.057 & 0.081 $\pm$ 0.021 \\ \hline
+% \textbf{GNN (ours)}    & 0.053 $\pm$ 0.006 & 0.035 $\pm$ 0.005 & 0.872 $\pm$ 0.061 & 2.438 $\pm$ 0.070 \\ \hline
+% 
+% \end{tabular}
+% \end{center}
+% 
+% \caption{
+% Results on Rome16K Correspondence graphs, showing the mean and standard deviation of the $L_1$ and $L_2$.
+% Our method was not trained on ground truth correspondences but using unsupervised methods and geometric side losses.
+% Thus we test against ground truth correspondence graph adjacency matrices computed from the bundle adjustment output.
+% Our method performs better than 25 iteration of the MatchALS (\cite{zhou2015multi}) method, but does not perform as well as 50 iterations.
+% % Our network has only 12 layers, thus we have much greater efficiency per iteration.
+% We do not perform as well as the Projected Gradient Descent Doubly Stochastic (PGDDS) (\cite{leonardos2016distributed}) but we perform significantly faster than them.
+% We perform better than a simple eigenvalue based method (\cite{pachauri2013solving}).
+% Note that we perform much better in $L_1$ performance rather than $L_2$, as we optimized the network weights using an $L_1$ loss.
+% }
+% \label{tab:rome16ktab}
+% \end{table*}

### 2019-09-23 latex/iclr2020/main.tex
figures updated

@@
 \begin{figure}[t]
+\begin{subfigure}[b]{.55\linewidth}
+  \centering
+  \includegraphics[width=0.95\linewidth]{figures-GeometricConsistency-v2.pdf}
+  \caption{Illustrated here is an example of how the geometric loss is computed for one feature.}
+  \label{fig:1b}
+  \label{fig:geoconsist}
+\end{subfigure}
+\begin{subfigure}[b]{.30\textwidth}
+  \centering
+  % \includegraphics[width=0.65\linewidth]{figures-GeometricLoss.pdf}
+  \includegraphics[height=180px]{figures-GeometricLoss.pdf}
+  \caption{}
+  \label{fig:3b}
+  \label{fig:geomloss}
+\end{subfigure}
+\caption{
+  \textbf{(a)} Errors are computed via absolute distance from the epipolar line, as expressed by (\ref{eq:essential_constraint}) via the epipolar constraint.
+  The epipolar line is the line of projection of the feature on the first image, projected onto to the second.
+  The distance to this line on the second image indicates how likely that point is to correspond geometrically to the original feature.
+  There can be false positives along the projected line, as shown by the square feature in the figure, but other points will be eliminated, such as the hexagonal feature.
+  Best viewed in color.
+  \textbf{(b)} Training curves with and without Geometric Training loss, described in \ref{eq:geom_cost2}.
+  The geometric training loss improves testing performance.
+  While the training is higher due to the additional loss terms, the ground truth L1 error is substantially better with the Geometric Loss.
+  Best viewed in color.
+}
+\label{fig:1}
+\end{figure}
+
+\begin{figure}[t]
 \begin{subfigure}[b]{.45\linewidth}
@@
 \end{subfigure}%
-\begin{subfigure}[b]{.45\linewidth}
+\begin{subfigure}[b]{.55\linewidth}
   \centering
-  \includegraphics[width=0.95\linewidth]{figures-GeometricConsistency-v2.pdf}
-  \caption{Illustrated here is an example of how the geometric loss is computed for one feature.}
+  \includegraphics[width=0.75\linewidth]{figures-EmbeddingsViz.png}
+  % \includegraphics[height=150px]{figures-EmbeddingsViz.png}
+  \caption{}
   \label{fig:1b}
-  \label{fig:geoconsist}
+  \label{fig:embeddingsviz}
 \end{subfigure}
@@
   While there can be many features, there are fewer 3D points and thus this corresponds to a low rank factorization of the correspondence matrix.
-  \textbf{(b)} Errors are computed via absolute distance from the epipolar line, as expressed by (\ref{eq:essential_constraint}) via the epipolar constraint.
-  The epipolar line is the line of projection of the feature on the first image, projected onto to the second.
-  The distance to this line on the second image indicates how likely that point is to correspond geometrically to the original feature.
-  There can be false positives along the projected line, as shown by the square feature in the figure, but other points will be eliminated, such as the hexagonal feature.
+  \textbf{(b)} Visualization of the learned embeddings.
+  On the left we have the raw outputs, which are difficult to interpret.
+  In the center, we rotated the features to best match the ground truth for a more interpretable visualization.
+  On the right, we have the ground truth embeddings, given as indicator vectors for which feature in the world the points correspond to.
   Best viewed in color.
@@
 \label{eq:rotinvar} $
-% Thus when visualizing embeddings, we rotate them to make them more interpretable (see figure \ref{fig:embeddingsviz}).
+Thus when visualizing embeddings, we rotate them to make them more interpretable (see figure \ref{fig:embeddingsviz}).
 
@@
 \centering
-\begin{subfigure}[b]{.70\textwidth}
-  \centering
-  % \includegraphics[width=0.95\linewidth]{figures-error_lines.pdf}
-  \includegraphics[height=200px]{figures-error_lines.pdf}
-  \caption{}
-  \label{fig:3a}
+\includegraphics[width=0.95\linewidth]{figures-error_lines.pdf}
+% \includegraphics[height=200px]{figures-error_lines.pdf}
+\label{fig:3}
 \label{fig:errorlines}
-\end{subfigure}
-\begin{subfigure}[b]{.25\textwidth}
-  \centering
-  % \includegraphics[width=0.65\linewidth]{figures-GeometricLoss.pdf}
-  \includegraphics[height=200px]{figures-GeometricLoss.pdf}
-  \caption{}
-  \label{fig:3b}
-  \label{fig:geomloss}
-\end{subfigure}
 \caption{
-  \textbf{(a)} Plot of the losses of the baselines at different iteration numbers.
+  Plot of the losses of the baselines at different iteration numbers.
   The line shows the mean of the graph while the translucent coloring shows the $25^{th}$ to $75^{th}$ percentiles.
@@
   PGDDS performs better than us in $L_1$ but we perform similarly in the ROC AUC metric.
-  \textbf{(b)} Training curves with and without Geometric Training loss, described in \ref{eq:geom_cost2}.
-  The geometric training loss improves testing performance.
-  While the training is higher due to the additional loss terms, the ground truth L1 error is substantially better with the Geometric Loss.
-  Best viewed in color.
 }
@@
 \end{figure}
+
+% 
+% \begin{figure}[t]
+% \centering
+% \begin{subfigure}[b]{.70\textwidth}
+%   \centering
+%   % \includegraphics[width=0.95\linewidth]{figures-error_lines.pdf}
+%   \includegraphics[height=200px]{figures-error_lines.pdf}
+%   \caption{}
+%   \label{fig:3a}
+%   \label{fig:errorlines}
+% \end{subfigure}
+% \begin{subfigure}[b]{.25\textwidth}
+%   \centering
+%   % \includegraphics[width=0.65\linewidth]{figures-GeometricLoss.pdf}
+%   \includegraphics[height=200px]{figures-GeometricLoss.pdf}
+%   \caption{}
+%   \label{fig:3b}
+%   \label{fig:geomloss}
+% \end{subfigure}
+% \caption{
+%   \textbf{(a)} Plot of the losses of the baselines at different iteration numbers.
+%   The line shows the mean of the graph while the translucent coloring shows the $25^{th}$ to $75^{th}$ percentiles.
+%   The ROC AUC curves remain fairly consistent while the L1 loss goes noticibly down after more iterations.
+%   Our method compares to 35-45 iterations of MatchALS, while only having 16 layers and 8 message passes.
+%   PGDDS performs better than us in $L_1$ but we perform similarly in the ROC AUC metric.
+%   \textbf{(b)} Training curves with and without Geometric Training loss, described in \ref{eq:geom_cost2}.
+%   The geometric training loss improves testing performance.
+%   While the training is higher due to the additional loss terms, the ground truth L1 error is substantially better with the Geometric Loss.
+%   Best viewed in color.
+% }
+% \label{fig:3}
+% \end{figure}
 
@@
 
-% \begin{figure}[t]
-% \begin{center}
-%   % \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
-%   \includegraphics[width=0.7\linewidth]{figures-EmbeddingsViz.png}
-%   \end{center}
-%      \caption{
-%          Visualization of the learned embeddings.
-%          On the left we have the raw outputs, which are difficult to interpret.
-%          In the center, we rotated the features to best match the ground truth for a more interpretable visualization.
-%          On the right, we have the ground truth embeddings, given as indicator vectors for which feature in the world the points correspond to.
-%      }
-%   \label{fig:embeddingsviz}
-% \end{figure}
 %------------------------------------------------------------------------

### 2019-09-23 baselines/plot_logs.py
Updated the plotting functions

@@ -92,18 +92,18 @@ def myformat_old(x):
   return "{}e-{}".format(y[0], y[1][-1])
 
 def get_info(fname):
-  fname = os.path.basename(fname)
-  if 'MatchALS' in fname or 'PGDDS' in fname:
-    k = str.find(fname, 'Iter')
+  fname = os.path.basename(fname).lower()
+  if 'matchals' in fname or 'pgdds' in fname:
+    k = str.find(fname, 'iter')
     niters = int(fname[k-3:k])
-    k = str.find(fname, 'View')
+    k = str.find(fname, 'view')
     views = int(fname[k-2:k])
     return { 'iters': [niters], 'views': views }
-  elif 'Spectral' in fname or 'Random' in fname:
-    k = str.find(fname, 'View')
+  elif 'spectral' in fname or 'random' in fname:
+    k = str.find(fname, 'view')
     views = int(fname[k-2:k])
     return { 'iters': [0], 'views': views }
-  elif 'rome16kgeom' in fname:
+  elif 'rome16kgeom' in fname or 'skiphop' in fname:
     k = str.find(fname, 'skiphop')
     k = str.find(fname, 'view')
     views = int(fname[k-2:k])
@@ -128,15 +128,16 @@ def get_title(k):
     return k.title()
 
 def get_label(fname):
-  if 'MatchALS' in fname:
+  fname = fname.lower()
+  if 'matchals' in fname:
     return 'MatchALS'
-  elif 'PGDDS' in fname:
+  elif 'pgdds' in fname:
     return 'PGDDS'
-  elif 'Spectral' in fname:
+  elif 'spectral' in fname:
     return 'Spectral'
-  elif 'Random' in fname:
+  elif 'random' in fname:
     return 'Random'
-  elif 'rome16kgeom' in fname:
+  elif 'rome16kgeom' in fname or 'skiphop' in fname:
     return 'Ours (6 Passes)'
   else:
     return ''
@@ -266,10 +267,16 @@ aggs_view, iters_view = parse_files(args.files)
 nviews, nplots = len(iters_view), len(plot_keys)
 sz, R, C = 4, nviews, nplots
 fig, ax_ = plt.subplots(nrows=R, ncols=C, figsize=(3+C*sz, 3+R*sz))
-ax = {
-  v: dict(zip(plot_keys, ax_[i]))
[…]

### 2019-09-23 baselines/run_tests.m

@@ -46,9 +46,9 @@ end
 
 % matchals_iters = [ 15, 25, 50, 100 ];
 % pgdds_iters = [ 15, 25, 50 ];
-% matchals_iters = [ 10, 20 ];
-matchals_iters = [ 30, 35, 40, 45 ];
-pgdds_iters = [  ];
+% matchals_iters = [ 10, 15, 20, 25, 30, 35, 40, 45 ];
+matchals_iters = [  ];
+pgdds_iters = [ 10, 15, 20, 25, 30, 35, 40, 45 ];
 test_fns = cell(2 + length(matchals_iters) + length(pgdds_iters),2);
 test_fns{1,1} = 'Spectral';
 test_fns{1,2} = @(W) myspectral(W, p);
@@ -68,7 +68,7 @@ for i = 1:length(pgdds_iters)
   offset = offset + 1;
 end
 
-saveout_str = '%sOutputs/%04d.npy';
+saveout_str = '%s%02dOutputs/%04d.npy';
 for test_fn_index = 1:size(test_fns,1)
   test_fn_tic = tic;
   test_fn = test_fns{test_fn_index,2};
@@ -92,7 +92,7 @@ for test_fn_index = 1:size(test_fns,1)
     disp_values(metric_info, fid, npz_index, values, run_time);
     test_index = test_index + 1;
     if save_out
-      output_name = sprintf(saveout_str, test_fns{test_fn_index,1}, npz_index);
+      output_name = sprintf(saveout_str, test_fns{test_fn_index,1}, views, npz_index);
       writeNPY(single(Ah), output_name);
       adjmat_name = sprintf('Adjmats/%04d.npy', npz_index);
       if ~exist(adjmat_name)

### 2019-09-23 latex/iclr2020/main.tex
Added graffiti text and a few minor typos

@@
     In addition, geometric consistency losses can be added at training time, even if the information is not available in the test set, unlike previous approaches which optimize cycle consistency directly.
-    To the best of our knowledge, no other works have used learning for multi-image feature matching.
+    To the best of our knowledge, no other works have used graph neural networks for multi-image feature matching.
     Our experiments show that our method is competitive with other optimization based approaches.
@@
 As an alternative to optimization based techniques, \cite{tron2017fast} used density based clustering techniques to compute multi-image correspondence.
-To the best of our knowledge, we are the first to use neural networks for multi-image matching.
+Moving away from feature matching, \cite{zach2010disambiguating} uses cycle consistency like constraints on pose graphs quite effectively.
+To the best of our knowledge, we are the first to use graph neural networks for multi-image matching.
 
@@
 \subsection{Graph Neural Networks}
-Graph neural networks have recieved more attention recently e.g.
+Graph neural networks have received more attention recently e.g.
 \cite{bronstein2017geometric, bruna2013spectral, defferrard2016convolutional, kipf2017semi, scarselli2009graph, gama2018mimo, gama2018convolutional}; and \cite{battaglia2018relational}.
@@
   There can be false positives along the projected line, as shown by the square feature in the figure, but other points will be eliminated, such as the hexagonal feature.
-  Best viewed in color.
   \textbf{(b)} Training curves with and without Geometric Training loss, described in \ref{eq:geom_cost2}.
@@
 
-Let $\mM$ be the noiseless set of matches between our features, with $\mM_{ij}$ being the matches between image $i$ and image $j$.
+Let $\mM$ be the noiseless set of matches between our features, with $\mM_{ij}$ being the partial permutation representing the matches between image $i$ and image $j$.
 If the pairwise matches are globally consistent, then for all $i, j, k$:
@@
 Note that because of this formulation, we can determine our embeddings only up to a rotation, as
-$ \mE R(\mE R)^\top
-= \mE RR^\top \mE^\top
-= \mE\mE^\top
+$ \mF_V R(\mF_V R)^\top
+= \mF_V RR^\top \mF_V^\top
+= \mF_V\mF_V^\top
 \label{eq:rotinvar} $
@@
 With $\mathcal{V}(i)$ being the vertices associated with camera $i$.
-For our purposes, since we use low rank embeddings $\mE_{i}$, $\mE_{j}$, the loss would read (where $c(k)$ is the appropriate camera for point index $k$):
+For our purposes, since we use low rank embeddings $\mF_{V, i}$, $\mF_{V, j}$, the loss would read (where $c(k)$ is the appropriate camera for point index $k$):
 \begin{align} 
@@
 % \includegraphics[height=200px]{figures-error_lines.pdf}
-\label{fig:3}
-\label{fig:errorlines}
 \caption{
@@
   PGDDS performs better than us in $L_1$ but we perform similarly in the ROC AUC metric.
+  These results still hold even when we change domains to the Graffiti dataset (see \ref{sec:graffiti}).
 }
 \label{fig:3}
+\label{fig:errorlines}
 \end{figure}
@@
 Rome16K is typically used to test bundle adjustment methods.
-Therefore, to use our method, we extract image triplets and quadruplets with overlap of 80 points or more to test our algorithm, with the points established as corresponding in the given bundle adjustment output.
+Therefore, to use our method, we extract 6-tuples and 10-tuples of images with overlap of 80 points or more to test our algorithm, with the points established as corresponding in the given bundle adjustment output.
 For the initial embedding we use the original 128 dimensional SIFT descriptors, normalized to have unit $L_2$ norm, the calibrated x-y position, the orientation, and log scale of the SIFT feature.
@@
 % Additional comparisons to different iterations numbers of iterations can be found in the supplementary material.
+
+\subsubsection{Graffiti Dataset} \label{sec:graffiti}
+We also run our trained model on the Graffiti Dataset (formatted to be able to be input to our model properly).
+The results are shown in \ref{fig:errorlines} in the rightmost figure.
+As the graffiti dataset is very small (only 6 views total), we were not able to train on it.
+We randomly permute the intra-image order of the features to add some variance - by design the GNN outputs the same result each time, while the optimization methods have a very small amount of variance.
+The transferred results of Graffiti are similar to the test error of Rome16K - smaller $L_1$ error and comparable ROC error.
+This shows that the GNNs trained in Rome16K generalize similarly to the optimization based methods.
 

### 2019-09-25 latex/iclr2020/main.tex
Added Sid (and a few of Daphne's) comments

@@
 \begin{abstract}
-    Image feature matching is a fundamental part of many geometric computer vision applications, and using multiple images can improve performance.
+    In geometric computer vision applications, multi-image feature matching gives more accurate and robust solutions compared to simple two-image matching.
     In this work, we formulate multi-image matching as a graph embedding problem then use a Graph Neural Network to learn an appropriate embedding function for aligning image features.
-    We use cycle consistency to train our network in an unsupervised fashion, since ground truth correspondence is difficult or expensive to acquire.
-    In addition, geometric consistency losses can be added at training time, even if the information is not available in the test set, unlike previous approaches which optimize cycle consistency directly.
+    We use cycle consistency to train our network in an unsupervised fashion, since ground truth correspondence can be difficult or expensive to acquire.
+    % TODO: Ask Sid if this is any good
+    Geometric consistency losses are added to aid training, though unlike optimization based methods no geometric information is necessary at inference time.
     To the best of our knowledge, no other works have used graph neural networks for multi-image feature matching.
@@
 \end{abstract}
+%     Image feature matching is a fundamental part of many geometric computer vision applications, and using multiple images can improve performance.
+%     In this work, we formulate multi-image matching as a graph embedding problem then use a Graph Neural Network to learn an appropriate embedding function for aligning image features.
+%     We use cycle consistency to train our network in an unsupervised fashion, since ground truth correspondence is difficult or expensive to acquire.
+%     In addition, geometric consistency losses can be added at training time, even if the information is not available in the test set, unlike previous approaches which optimize cycle consistency directly.
+%     To the best of our knowledge, no other works have used graph neural networks for multi-image feature matching.
+%     Our experiments show that our method is competitive with other optimization based approaches.
 
@@
 Feature matching is an essential part of Structure from Motion and many geometric computer vision applications.
-The goal in multi-image feature matching is to take 2D image locations from three or more images and find which ones correspond to the same point in the 3D scene.
-Methods such as SIFT feature matching (\cite{lowe2004distinctive}) followed by RANSAC (\cite{fischler1981random}) have been the standard for decades.
+The goal in multi-image feature matching is to take 2D feature positions from three or more images and find which ones correspond to the same point in the 3D scene.
+Methods such as SIFT feature matching \citep{lowe2004distinctive} followed by RANSAC \citep{fischler1981random} have been the standard for decades.
 However RANSAC-based approaches are limited to matching pairs of images, which can lead to global inconsistencies in the matching.
 % TODO: Mention trifocal tensors
-Other works, such as Wang et al.~\cite{wang2017multi}, have shown improvement in performance by optimizing cycle consistency, i.e. enforcing the pairwise feature matches to be globally consistent.
+Other works, such as \cite{wang2017multi}, have shown improvement in performance by optimizing cycle consistency, i.e. enforcing the pairwise feature matches to be globally consistent.
 
 However, these multi-view consistency algorithms struggle in distributed and robust settings.
-Having image features suited for this task would help improve performance, and deep learning has revolutionized how image features are computed (\cite{yi2016lift}).
+Having image features suited for this task would help improve performance, and deep learning has revolutionized how image features are computed \citep{yi2016lift}.
 In this paper, we want to leverage the power of deep representations in order to compute feature descriptors that are robust across multiple views.
-% Typically when applied to image or feature matching, deep neural networks (DNNs) are trained with photometric losses, directly using pixel color values.
-% However direct, pixel-based losses have are not robust to the many confounding factors in the environment, such as lighting and view-point changes.
-% Using features designed to deal with these confounding factors improves robustness to them, and learning may improve robustness even further.
-
-% \begin{figure}[t]
-% \begin{center}
-%   % \fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-%   \includegraphics[width=0.8\linewidth]{figures-CycleConsistencyBasic-v2.pdf}
-% \end{center}
-%   \caption{
-%     Example of multi-image matching and cycle consistency, with images from Rome16K dataset \cite{li2010location}.
-%     Pairwise matches between image can lead to global inconsistencies in the matching.
-%     In this example, an error in matching leads to an inconsistent cycle (shown in red), ideally these pairwise matches would be consistent.
-%     We improve the quality of pairwise matches in the multi-view matching problem by training a neural net with cycle consistency.
-%   }
-% \label{fig:cycconsistex}
-% \end{figure}
 
@@
     An illustration of the approach of this work.
-    The Graph Neural Neural Network (GNN) (\cite{battaglia2018relational}) takes as input the graph of matches and then outputs a low rank embedding of the adjacency matrix of the graph.
+    The Graph Neural Neural Network (GNN) \citep{battaglia2018relational} takes as input the graph of matches and then outputs a low rank embedding of the adjacency matrix of the graph.
     The GNN operates on an embedding over the vertices of the graph.
@@
 Unfortunately, there are obstacles to applying multi-view constraints directly to deep learning. 
-To train networks, we need a large amount of labeled data.
-In the case of multi-image feature matching, one would need hand labeled point correspondences between images, which are difficult and expensive to obtain.
 Multi-view constraints are formulated in terms of sparse features, which traditional convolutional neural nets are not designed to handle.
-Additionally, in the case of multi-image feature matching, geometric constraints would be helpful in rejecting outlier matches.
-Geometric constraints, such as the epipolar constraint, can help disambiguate between visually similar features during training, and help the network learn better features robust to this kind of noise.
+Thus we will need a new architecture to handle such constraints.
+More fundamentally, deep neural networks need large amounts of labeled data to train.
+In the case of multi-image feature matching, one would need hand-labeled point correspondences between images, which can be difficult and expensive to obtain.
+Consequently unsupervised training is a more practical approach.
+In the absence of direct supervision, the additional signal of geometric constraints can help disambiguate visually similar features and reject outliers.
+Thus incorporating such constraints is important in training a network to solve this task.
 
-In this work, we propose to solve these problems using Graph Neural Networks (GNNs) to operate on the correspondence graph.
-The proposed method works directly on the correspondence graph, which is agnostic to how the correspondences were computed, thus allowing the algorithm to work in a broad class of environments.
+In this work, we address these concerns using Graph Neural Networks (GNNs).
+The proposed method works directly on the graph of correspondences between the image features, which is agnostic to how the correspondences were computed, thus allowing the algorithm to work in a broad class of environments.
 To the best of our knowledge this work is the first to apply deep learning to the multi-view feature matching problem.
-We use an unsupervised loss - the cycle consistency loss - to train the network, and thus avoiding the difficulty of expensive hand labeling.
-Geometric consistency losses can aid training, even if such information is not available at test time.
-Although our network is simple, it shows promising results compared to baselines which optimize for cycle-consistency without learned embeddings, using a matrix factorization loss (\cite{zhou2015multi, leonardos2016distributed}).
-Furthermore, since inference requires only a single forward pass over the neural network, our approach is faster (to achieve comparable accuracy) than methods which must solve an optimization problem every time.
-We perform experiments on the Rome16K dataset (\cite{li2010location}) to test the effectiveness of our method compared to optimization based methods.
+We use an unsupervised loss, the cycle consistency loss, to train the network, thus avoiding the difficulty of expensive hand-labeling.
+We use geometric consistency losses to aid training, though no geometric information is used at inference time.
+Although our network is simple, it shows promising results compared to baselines which optimize for cycle-consistency without learned embeddings, using a matrix factorization loss \citep{zhou2015multi, leonardos2016distributed}.
+Furthermore, since inference requires only a single forward pass over the neural network, our approach is faster to achieve comparable accuracy than methods which must solve an optimization problem every time.
+We perform experiments on the Rome16K dataset \citep{li2010location} to test the effectiveness of our method compared to optimization based methods.
 Our contributions in this work are:
@@
 \subsection{Feature Matching}
-Matching has a rich history of research in computer vision.
-Much work has be done using hand-crafted feature descriptors such as SIFT (\cite{lowe2004distinctive}), SURF (\cite{bay2006surf}), BRIEF (\cite{calonder2012brief}), or ORB (\cite{mur2015orb}).
+Image feature matching has a rich history of research in computer vision.
+Much work has be done using hand-crafted feature descriptors such as SIFT \citep{lowe2004distinctive}, SURF \citep{bay2006surf}, BRIEF \citep{calonder2012brief}, or ORB \citep{mur2015orb}.
 RANSAC \cite{fischler1981random} is the most widely used robust estimation technique to filter out outliers from the matches.
 The combination of RANSAC and hand-crafted feature descriptors has constituted the bulk of the matching literature for the last 40 years.
-Finally, graph matching (\cite{suh2015subgraph, hu2016distributable}) can be used as a final step for more robust matches.
+More recently \cite{suh2015subgraph} and \cite{hu2016distributable} have shown graph matching of the features can be added for more robust matches between images.
 
@@
 \cite{pachauri2013solving} and \cite{arrigoni2017synchronization} use the eigenvectors of the matching matrix to obtain a low dimensional embedding. 
-However, the low Gaussian noise assumption is not realistic.
-\cite{zhou2015multi} and \cite{wang2017multi} use most sophisticated optimization techniques on the matching matrix and thus produce more robust solutions.
+However, the assumption of low Gaussian noise is not realistic.
+\cite{zhou2015multi} and \cite{wang2017multi} use more sophisticated optimization techniques on the matching matrix and thus produce more robust solutions.
 \cite{leonardos2016distributed} implement a distributed optimization scheme to solve for cycle consistency.
@@
 However, they only focus on two view matching and do not exploit the advantages of the correspondence structure.
-Note that while \cite{zhu2017unpaired} use cycle consistency in their loss, their method is restricted to pairwise cycle consistency (i.e.
+Like us \cite{zhu2017unpaired} use cycle consistency in their loss, however their method is restricted to pairwise cycle consistency (i.e.
 enforcing consistency by going back and forth between two images).
-We use multi-image cycle consistency, which require consistency between 3 or more images.
+Our method can be applied to 3 or more images. 
+\cite{hartmann2017learned} in fact learns multi-image matching but requires heavy supervision from 3D object reconstructions, which are not available in the context we are in.
 
 \subsection{Graph Neural Networks}
-Graph neural networks have received more attention recently e.g.
-\cite{bronstein2017geometric, bruna2013spectral, defferrard2016convolutional, kipf2017semi, scarselli2009graph, gama2018mimo, gama2018convolutional}; and \cite{battaglia2018relational}.
-Classical so-called Spectral methods used the eigenvectors of the graph Laplacian to compute convolutions as in \cite{bruna2013spectral}, but requires an a-priori known graph structure. 
-Non-spectral methods do not require a-priori knowledge, as seen in \cite{bronstein2017geometric, kipf2017semi, scarselli2009graph}; and \cite{gama2018convolutional}.
+Graph neural networks, true to their name, are deep neural networks operating in graph domains.
+Multi-image matching is novel application of them, as they are more typically used for applications such as citation networks or recommendation systems.
+They have received more attention recently \citep{bronstein2017geometric, defferrard2016convolutional, kipf2017semi, scarselli2009graph, gama2018mimo, gama2018convolutional, battaglia2018relational}.
+The first methods to learn neural networks over graphs were the so-called Spectral methods.
+They used the eigenvectors of the graph Laplacian to compute convolutions as in \cite{bruna2013spectral}, which can learn graph specific convolution kernels, but require an a-priori known graph structure.
+Newer non-spectral methods do not require a-priori knowledge, as seen in \cite{bronstein2017geometric, kipf2017semi, scarselli2009graph}; and \cite{gama2018convolutional}.
 Most of these methods use polynomials of the graph Laplacian to compute neighborhood averages.
@@
 To improve performance, more sophisticated aggregation techniques and global information passing can be used as discussed in \cite{battaglia2018relational}.
+The closest work on Graph Neural Networks to ours is \cite{kipf2016variational}, which uses GNNs to reconstruct the adjacency matrices, though not in a geometric context.
 
@@
 \begin{figure}[t]
+\begin{subfigure}[b]{.45\linewidth}
+  \centering
+  \includegraphics[width=0.95\linewidth]{figures-UniverseOfFeatures-v2.pdf}
+  \caption{}
+  \label{fig:1a}
+  \label{fig:universefeatures}
+\end{subfigure}%
 \begin{subfigure}[b]{.55\linewidth}
+  \centering
+  \includegraphics[width=0.75\linewidth]{figures-EmbeddingsViz.png}
+  % \includegraphics[height=150px]{figures-EmbeddingsViz.png}
+  \caption{}
+  \label{fig:1b}
+  \label{fig:embeddingsviz}
+\end{subfigure}
+\caption{
+  \textbf{(a)} An illustration of the idea of the universe of features.
+  Each feature in each image corresponds to a 3D point in the scene.
+  We can construct cycle consistent embeddings of the features by mapping each one to the one-hot vector of its corresponding 3D point.
+  While there can be many features, there are fewer 3D points and thus this corresponds to a low rank factorization of the correspondence matrix.
+  Best viewed in color.
+  \textbf{(b)} Visualization of the learned embeddings.
+  On the left we have the raw outputs, which are difficult to interpret.
+  In the center, we rotated the features to best match the ground truth for a more interpretable visualization (see the end of section \ref{sec:cycconsist}).
+  On the right, we have the ground truth embeddings, given as indicator vectors for which feature in the world the points correspond to.
+  For the optimally rotated embedding we can see that the true embedding structure is recovered (with some noise).
+}
+\label{fig:1}
+\end{figure}
+
+Our goal is to learn optimal features that capture multiple image views by filtering out noisy feature matches.
+The input to our algorithm is a set of features and noisy correspondences, and the output is a new set of features where the pairwise similarities of these features correspond to the true matches.
+An outline of our approach can be seen in figure \ref{fig:pipeline}.
+We do this by training the new set of feature embeddings to be cycle consistent.
+We formulate this problem in terms of the correspondence graph of the features.
+Graphs $\mathcal{G} = (\mathcal{V}, \mathcal{E})$ have a set of vertices $\mathcal{V}$ and of edges $\mathcal{E} \subseteq \mathcal{V} \times \mathcal{V}$ and implicitly in the subsequent discussions we assume the edges are directed.
+For a vertex $v \in \mathcal{V}$ we use $\mathcal{N}^{h}(v)$ to denote the $h$-hop neighbors of $v$, with the superscript left out for 1-hop neighbors.
+Similarly $\mathcal{E}(v)$ is used to denote the edges associated with $v$.
+To denote the vertices connected to an edge $e \in \mathcal{E}$ we write $e(v_1, v_2)$.
+\subsection{Correspondence Graph} \label{sec:corrgraph}
+We assume there is an initial set of feature matches represented as a graph $\mathcal{G} = (\mathcal{V}, \mathcal{E})$, with an associated adjacency matrix $\mA$.
+The graph is constructed from putative correspondences of image features across images, typically constructed using feature descriptor distance (e.g. SIFT feature distance).
+While there are many interesting methods for computing these putative correspondences \citep{suh2015subgraph, yi2018learning}, we do not explore them in this work.
+Typically putative correspondences are matched probabilistically, meaning a feature in one image matches to many features in another.
+The ambiguity in the matches could come from repeated structures in the scene, insufficiently informative low-level feature descriptors, or just an error in the matching algorithm.
+Filtering out these noisy matches is our primary learning goal.
+
+Each vertex of the graph $v \in \mathcal{V}$ is an image feature, corresponding to some ground truth 3D point $\vp(v)$.
+Each edge $e = (v_1, v_2) \in \mathcal{E}$ is a potential correspondence.
+Associated with each vertex $v$ is an embedding $\vf_v \in \sR^m$, which can include the visual feature descriptor, position, scale, orientation, etc.
+Similarly, each edge $e$ has an associated feature $\vf_e \in \sR^p$ (in this work, initially just the weight of the feature association).
+We use these features as the initialization for our learning algorithm.
+
+In the absence of noise or outliers, this graph would have a connected component for each visible point in the world, all mutually disjoint.
+Without noise, vertices $v$ would only match with other vertices $v'$ that correspond to the same 3D point in the scene.
+Since features in this case represent unique locations in the scene, no points in the same image would have edges $e$ between them.
+Mathematically, this can be expressed as $e = (v_1, v_2) \in \mathcal{E} \implies \mP(v_1) = \mP(v_2)$.
+In the noisy case we expect this structure to be corrupted, i.e. there are some edges $e = (v_1, v_2) \in \mathcal{E}$ such that $\mP(v_1) \neq \mP(v_2)$.
+Thus we need to prune the erroneous edges.
+
+However, standard CNNs cannot operate on this general graph structure.
+Thus we cannot use standard convolutional nets to learn features for this task.
+Instead we use graph networks to learn feature representations on this space, which we describe in the next section.
+
+\subsection{Graph Neural Networks} \label{sec:gnns}
+As input to our method we are given a graph $\mathcal{G} = (\mathcal{V}, \mathcal{E})$ with the features described in section \ref{sec:corrgraph} $\vf_v \; \forall v \in \mathcal{V}$ and $\vf_e \; \forall e \in \mathcal{E}$.
+As with any neural network, GNNs have layered outputs.
+We describe the output of layer $k$ as $\vf_v^{(k)} \in \sR^{m_k} \, \forall v \in \mathcal{V}$ and $\vf_e^{(k)} \in \sR^{p_k}\, \forall e \in \mathcal{E}$, with the initial embeddings denoted $\vf_v^{(0)} = \vf_v$ and $\vf_e^{(0)} = \vf_e$.
+To aid future analysis, we will represent the features as matrices, denoting the vertex embedding matrix as $\mF_V^{(k)}$ and the edge embedding matrix as $\mF_E^{(k)}$.
+If a superscript is not specified then it refers to the final output of the network.
+
+First we describe older methods of GNNs to give context, then we describe the method we use in this work.
+Many older methods assume we have the adjacency matrix $\mA$ of the graph known a-priori \cite{bruna2013spectral}, and can encode graph convolutions using the eigenvectors of $\mA$ (these are known as spectral methods).
+However, we do not have this luxury, as the correspondence structure changes from image set to image set, and thus we use non-spectral Graph Neural Networks.
+Newer models use non-spectral methods, which often ultimately amount to transforming each node with learned weights then averaging each node's representation with its neighbors, known as a message pass \citep{kipf2017semi, defferrard2016convolutional, gama2018mimo, gama2018convolutional}.
+Some works such as \cite{gama2019convolutional} use pooling operations on the vertices to make the graph smaller and thus aid computation, but as we need labels on every vertex of the original graph, so we cannot use this.
+Most GNNs used in these works can be expressed mathematically as:
+\begin{align*}
+\tilde{\vf}_v^{(k+1)} =&\; \sigma\left( b^{(k)} + \mW_0^{k} \vf_{v}^{(k)} + \sum_{h=0}^H \sum_{v' \in \mathcal{N}^{h}(v)} f_{e(v,v')} \mW_{h}^{k} \vf_{v'}^{(k)} \right) \\
+\end{align*}
+The weights/biases $\mW_{h}^{k}$, $b^{(k)}$ are all learned, with no learning done on the edge weights $f_{e(v,v')}$. 
+Note that this is just sums or averages over $h$-hop neighborhoods, where the weights on the edges remain static through the computation.
+Given that we are trying to prune edges, it would be sensible to add features over edges to learn which ones to prune and which to keep such as in \cite{scarselli2009graph}.
+
+In this work we use the method and implementation described in \cite{battaglia2018relational} (more specifically repetitions of the architecture described in \cite{battaglia2016interaction}).
+\cite{battaglia2018relational} uses message passes between node features as well as edge features, which the model can use to prune unnecessary or erroneous edges.
+Therefore there is intermediate processing on the edges before information is passed to the vertices.
+
+Mathematically, this is expressed as: % TODO: Maybe make this MLP oriented?
+\begin{align}
+\tilde{\vf}_{e(v_1,v_2)}^{(k+1)} =&\; \sigma \left(a^{(k)} + \mU_0^{(k)} \vf_{e}^{(k)} + \mU_1^{(k)} \vf_{v_1}^{(k)} + \mU_2^{(k)} \vf_{v_2}^{(k)} \right) \\
+\tilde{\vf}_{v}^{(k+1)} =&\; \sigma\left(b^{(k)} + \mW_0^{(k)} \vf_{v}^{(k)} + \sum_{e \in \mathcal{E}(v)} \mW_1^{(k)} \vf_{e}^{(k+1)} \right) 
+\end{align}
+Here the learned weights are denoted $\mW$ and $\mU$, and the biases $a^{(k)}$ and  $b^{(k)}$.
+In \cite{battaglia2018relational}, they allow for more sophisticated aggregation functions, but in this work we simply use the mean function.
+Each one of these steps we refer to here as a message pass, and it is analogously equivalent to an iteration in a distributed graph based optimization method.
+Between each of the message passes, we further process the features using MLPs.
+% In practice, we use MLPs in message passes between vertices and edges for better expressiveness
+
+\subsection{Cycle Consistency} \label{sec:cycconsist}
+
+Let $\mM$ be the noiseless set of matches between our features, with $\mM_{ij}$ being the partial permutation representing the matches between image $i$ and image $j$.
+If the pairwise matches are globally consistent, then for all $i, j, k$:
+\begin{equation}
+\mM_{ij} = \mM_{ik} \mM_{kj}
+\label{eq:cycconsist1}
+\end{equation}
+In other words, the matches between two images stay the same no matter what path is taken to get there. 
+This constraint is known as \textit{cycle consistency}, and has been used in a number of works to optimize for global consistency \cite{zhou2015multi, wang2017multi, leonardos2016distributed}.
+Stated in this form, there are $O(n^3)$ cycle consistency constraints to check.
+A more elegant way to represent cycle consistency is to first create a `universe' of features that all images match to (see figure \ref{fig:universefeatures}).
+Then, one can match the $i^{th}$ set of features to the universe using a ground-truth matching matrix $\mX_i$.
+Then the cycle consistency constraint becomes:
+\begin{equation}
+\mM_{ij} = \mX_{i}\mX_{j}^\top
+\label{eq:cycconsist2}
+\end{equation}
+
+This reduces the number of our constraints from $O(n^3)$ to $O(n^2)$.
+We try to learn vertex embeddings $\mF_V$ to approximate $\mX$ - in other words the final embedding should be an encoding of the universe of features.
+As we do not have the ground truth matches $\mM$, we approximate it using the noisy adjacency matrix $\mA$ of our correspondence graph. Thus our loss would be 
+\begin{equation}
+\mathcal{L}(\mA, \mF_V) = \mathcal{D}(\mA, \mF_V \mF_V^\top)
+\end{equation}
+Here $\mathcal{D}$ could be an $L_2$ loss, $L_1$ loss, or many others. In this work, we use the $L_1$ loss. 
+Note that because of this formulation, we can determine our embeddings only up to a rotation, as
+$ \mF_V R(\mF_V R)^\top
+= \mF_V RR^\top \mF_V^\top
+= \mF_V\mF_V^\top
+\label{eq:rotinvar} $
+Thus when visualizing embeddings, we rotate them to make them more interpretable (see figure \ref{fig:embeddingsviz}).
+
+\subsection{Geometric Consistency Loss}
+
+\begin{figure}[t]
+\centering
+\begin{subfigure}[b]{.60\linewidth}
   \centering
@@
 
-\begin{figure}[t]
-\begin{subfigure}[b]{.45\linewidth}
-  \centering
-  \includegraphics[width=0.95\linewidth]{figures-UniverseOfFeatures-v2.pdf}
-  \caption{Illustration of the universe of features.}
-  \label{fig:1a}
-  \label{fig:universefeatures}
-\end{subfigure}%
-\begin{subfigure}[b]{.55\linewidth}
-  \centering
-  \includegraphics[width=0.75\linewidth]{figures-EmbeddingsViz.png}
-  % \includegraphics[height=150px]{figures-EmbeddingsViz.png}
-  \caption{}
-  \label{fig:1b}
-  \label{fig:embeddingsviz}
-\end{subfigure}
-\caption{
-  \textbf{(a)} Each feature in each image corresponds to a 3D point in the scene.
-  We can construct cycle consistent embeddings of the features by mapping each one to the one-hot vector of its corresponding 3D point.
-  While there can be many features, there are fewer 3D points and thus this corresponds to a low rank factorization of the correspondence matrix.
-  \textbf{(b)} Visualization of the learned embeddings.
-  On the left we have the raw outputs, which are difficult to interpret.
-  In the center, we rotated the features to best match the ground truth for a more interpretable visualization.
-  On the right, we have the ground truth embeddings, given as indicator vectors for which feature in the world the points correspond to.
-  Best viewed in color.
-}
-\label{fig:1}
-\end{figure}
+% One of the main advantages of this approach over more traditional optimization based approaches is the ability to add geometric consistency information into the loss at training time, even if it is not available at test time.
+In order to use geometric information, more traditional optimization based methods require the geometric information at inference time, while with learning approaches we can use it to speed up training while not needing it at inference time.
+Thus geometric consistency losses are one distinct advantage of our method over more traditional optimization based approaches.
+We use the epipolar constraint, the simplest way to add a geometric consistency loss.
+The epipolar constraint describes how the positions of features in different images corresponding to the same point should be related.
+An illustration of this is provided in figure \ref{fig:geoconsist}, showing how this loss can help reject erroneous points.
+Given a relative pose $(R_{ij}, T_{ij})$ between two cameras $i$ and $j$  (transforms $j$ to $i$) the epipolar constraint on corresponding feature locations $X_i$ and $X_j$: $X_{i}^\top \cross{T_{ij}}R_{ij} X_{j} = 0$.
+In this work we use the two pose epipolar constraint \citep{tron2014quotient}:
+\begin{equation}
+X_{i}^\top R_{i}^\top \cross{T_{j} - T_{i}}R_{j} X_{j} = 0
+\label{eq:essential_constraint}
+\end{equation}
+The constraint assumes that the $X_k$ are calibrated (i.e. the camera intrinsics are known). 
+Given our vertex embeddings matrix $\vf_v$, we can formulate a loss between all cameras $i$ and $j$ (the vertices associated with camera $i$ denoted $\mathcal{V}(i)$):
+\begin{align}
+\mathcal{L}_{ij,geom}(\mF_V) = 
+&\sum_{v \in \mathcal{V}(i),u \in \mathcal{V}(j)} (\vf_v \cdot \vf_u) \left|X_{v}^\top R_{i}^\top \cross{T_{j} - T_{i}}R_{j} X_{u}\right|
+\label{eq:geom_cost}
+\end{align}
+For our purposes, since we use low rank embeddings $\mF_{V}$, the loss would read (where $c(k)$ is the appropriate camera for point index $k$):
+\begin{align} 
+\mathcal{L}_{geom}(\mF_V)
+=&\; \mathrm{tr}(\mG^\top \mF_V\mF_V^\top) = \sum_{k,l} (\mF_V)_{k} \cdot (\mF_V)_{l} (\mG)_{kl} \label{eq:geom_cost2} \\
+(\mG)_{kl} =&\; \left|X_{k}^\top R_{c(k)}^\top \cross{T_{c(l)} - T_{c(k)}}R_{c(l)} X_{l}\right| \nonumber
+\end{align}
 
-Our goal is to learn optimal features that capture multiple image views by filtering out noisy feature matches.
-An outline of our approach can be seen in figure \ref{fig:pipeline}.
-The input to our algorithm is a set of features and noisy correspondences, and the output is a new set of features where the pairwise similarities of these features correspond to the true matches.
-We do this by training the new set of feature embeddings to be cycle consistent.
-We formulate this problem in terms of the correspondence graph of the features.
-Graphs $\mathcal{G} = (\mathcal{V}, \mathcal{E})$ have a set of vertices $\mathcal{V}$ and of edges $\mathcal{E} \subseteq \mathcal{V} \times \mathcal{V}$ and implicitly in the subsequent discussions we assume the edges are directed.
-For a vertex $v \in \mathcal{V}$ we use $\mathcal{N}^{h}(v)$ to denote the $h$-hop neighbors of $v$, with the superscript left out for 1-hop neighbors.
-Similarly $\mathcal{E}(v)$ is used to denote the edges associated with $v$.
-To denote the vertices connected to an edge $e \in \mathcal{E}$ we write $e(v_1, v_2)$.
-\subsection{Correspondence Graph}
-We assume there is an initial set of feature matches represented as a graph $\mathcal{G} = (\mathcal{V}, \mathcal{E})$, with an associated adjacency matrix $\mA$.
-The graph is constructed from putative correspondences of image features across images, typically constructed using feature descriptor distance (e.g. SIFT feature distance).
-While there are many interesting methods for computing these putative correspondences (\cite{suh2015subgraph, yi2018learning}), we do not explore them in this work.
-Typically putative correspondences are matched probabilistically, meaning a feature in one image matches to many features in another.
-The ambiguity in the matches could come from repeated structures in the scene, insufficiently informative low-level feature descriptors, or just an error in the matching algorithm.
-Filtering out these noisy matches is our primary learning goal.
+%------------------------------------------------------------------------
+\section{Experiments}
 
-Each vertex of the graph $v \in \mathcal{V}$ is an image feature, corresponding to some ground truth 3D point $\vp(v)$.
-Each edge $e = (v_1, v_2) \in \mathcal{E}$ is a potential correspondence.
-Associated with each vertex $v$ is an embedding $\vf_v \in \sR^m$, which can include the visual feature descriptor, position, scale, orientation, etc.
-Similarly, each edge $e$ has an associated feature $\vf_e \in \sR^p$ (in this work, initially just the weight of the feature association).
-We use these features as the initialization for our learning algorithm.
-
-In the absence of noise or outliers, this graph would have a connected component for each visible point in the world, all mutually disjoint.
-Without noise, vertices $v$ would only match with other vertices $v'$ that correspond to the same 3D point in the scene.
-Since features in this case represent unique locations in the scene, no points in the same image would have edges $e$ between them.
-Mathematically, this can be expressed as $e = (v_1, v_2) \in \mathcal{E} \implies \mP(v_1) = \mP(v_2)$.
-In the noisy case we expect this structure to be corrupted, i.e. there are some edges $e = (v_1, v_2) \in \mathcal{E}$ such that $\mP(v_1) \neq \mP(v_2)$.
-Thus we need to prune the erroneous edges.
-
-However, standard CNNs cannot operate on this general graph structure.
-Thus we cannot use standard convolutional nets to learn features for this task.
-Instead we use graph networks to learn feature representations on this space, which we describe in the next section.
-
-\subsection{Graph Neural Networks}
-As input to our method we are given a graph $\mathcal{G} = (\mathcal{V}, \mathcal{E})$ with the features described last section $\vf_v \; \forall v \in \mathcal{V}$ and $\vf_e \; \forall e \in \mathcal{E}$.
-As with any neural network, GNNs have layered outputs.
-We describe the output of layer $k$ as $\vf_v^{(k)} \in \sR^{m_k} \, \forall v \in \mathcal{V}$ and $\vf_e^{(k)} \in \sR^{p_k}\, \forall e \in \mathcal{E}$, with the initial embeddings denoted $\vf_v^{(0)} = \vf_v$ and $\vf_e^{(0)} = \vf_e$.
-It will be useful to write these features as matrices in later sections, so we denote the vertex embedding matrix as $\mF_V^{(k)}$ and the edge embedding matrix as $\mF_E^{(k)}$.
-If a superscript is not specified then it refers to the final output of the network.
-
-First we describe older methods of GNNs to give context, then we describe the method we use in this work.
-Many older methods assume we have the adjacency matrix $\mA$ of the graph known a-priori \cite{bruna2013spectral}, and can encode graph convolutions using the eigenvectors of $\mA$.
-However, we do not have this luxury, as the correspondence structure changes from image set to image set, and thus we use non-spectral Graph Neural Networks.
-There are many variations on non-spectral methods, often which ultimately amount to message passing between vertices of the graph with learned non-linear transformations between various steps (\cite{kipf2017semi, defferrard2016convolutional, gama2018mimo, gama2018convolutional}).
-Some works such as \cite{gama2019convolutional} use pooling operations on the vertices to make the graph smaller and thus aid computation, but as we need labels on every vertex of the original graph, so we cannot use this.
-Most of GNNs used in these works can be expressed mathematically as:
-\begin{align*}
-\tilde{\vf}_v^{(k+1)} =&\; \sigma\left( b^{(k)} + \mW_0^{k} \vf_{v}^{(k)} + \sum_{h=0}^H \sum_{v' \in \mathcal{N}^{h}(v)} f_{e(v,v')} \mW_{h}^{k} \vf_{v'}^{(k)} \right) \\
-\end{align*}
-The weights/biases $\mW_{h}^{k}$, $b^{(k)}$ are all learned, with no learning done on the edge weights $f_{e(v,v')}$. 
-Note that this is just sums or averages over $h$-hop neighborhoods, where the weights on the edges remain static through the computation.
-Given that we are trying to prune edges, it would be sensible to add features over edges to learn which ones to prune and which to keep such as in \cite{scarselli2009graph}.
-
-Therefore, in this work we use the method and implementation described in \cite{battaglia2018relational} (more specifically repetitions of the architecture described in \cite{battaglia2016interaction}).
-This work is similar to previous works with one key difference: edges also have weights.
-Thus therefore there is intermediate processing on the edges before information is passed to the vertices.
-
-Mathematically, this is expressed as: % TODO: Maybe make this MLP oriented?
-\begin{align}
-\tilde{\vf}_{e(v_1,v_2)}^{(k+1)} =&\; \sigma \left(a^{(k)} + \mU_1^{(k)} \vf_{e}^{(k)} + \mU_1^{(k)} \vf_{v_1}^{(k)} + \mU_2^{(k)} \vf_{v_2}^{(k)} \right) \\
-\tilde{\vf}_{v}^{(k+1)} =&\; \sigma\left(b^{(k)} + \mW_0^{(k)} \vf_{v}^{(k)} + \sum_{e \in \mathcal{E}(v)} \mW_1^{(k)} \vf_{e}^{(k+1)} \right) 
-\end{align}
-Here the learned weights are denoted $\mW$ and $\mU$, and the biases $a^{(k)}$ and  $b^{(k)}$.
-In \cite{battaglia2018relational}, they allow for more sophisticated aggregation functions, but in this work we simply use the mean function.
-In practice, we use MLPs in message passes between vertices and edges for better expressiveness
-
-\subsection{Cycle Consistency}
-
-Let $\mM$ be the noiseless set of matches between our features, with $\mM_{ij}$ being the partial permutation representing the matches between image $i$ and image $j$.
-If the pairwise matches are globally consistent, then for all $i, j, k$:
-\begin{equation}
-\mM_{ij} = \mM_{ik} \mM_{kj}
-\label{eq:cycconsist1}
-\end{equation}
-In other words, the matches between two images stay the same no matter what path is taken to get there. 
-This constraint is known as \textit{cycle consistency}, and has been used in a number of works to optimize for global consistency (\cite{zhou2015multi, wang2017multi, leonardos2016distributed}).
-Stated in this form, there are $O(n^3)$ cycle consistency constraints to check.
-A more elegant way to represent cycle consistency is to first create a `universe' of features that all images match to (see figure \ref{fig:universefeatures}).
-Then, one can match the $i^{th}$ set of features to the universe using a ground-truth matching matrix $\mX_i$.
-Then the cycle consistency constraint becomes:
-\begin{equation}
-\mM_{ij} = \mX_{i}\mX_{j}^\top
-\label{eq:cycconsist2}
-\end{equation}
+\subsection{Synthetic Graph Dataset}
 
@@
 Initialization Baseline            & 5.11e-1 $\pm$ 1.68e-2 & 2.56e-1 $\pm$ 2.06e-1 \\ \hline
-3 Views, Noiseless                 & 9.96e-1 $\pm$ 7.70e-3 & 1.16e-1 $\pm$ 1.32e-1 \\ 
 5 Views, Noiseless                 & 1.00e+0 $\pm$ 4.15e-4 & 1.22e-1 $\pm$ 1.67e-1 \\ \hline
-3 Views, Added Noise               & 9.96e-1 $\pm$ 7.70e-3 & 1.16e-1 $\pm$ 1.32e-1 \\ 
-5 Views, Added Noise               & 9.89e-1 $\pm$ 2.47e-2 & 7.67e-2 $\pm$ 1.56e-1 \\ 
 6 Views, Added Noise               & 9.84e-1 $\pm$ 3.16e-2 & 7.46e-2 $\pm$ 1.57e-1 \\ \hline
@@
 \caption{
-Results on Synthetic correspondence graphs.
-The `Same Point Similarities' column is the mean and standard deviation of similarities for true corresponding points, while the `Different Point Similarities' is the same for points that do not correspond.
-For the `Same Point Similarities' column higher is better, and for `Different Point Similarities' lower is better.
-Losses tested against ground truth correspondence graph adjacency matrices.
-Our method was not trained on ground truth correspondences but using unsupervised methods.
+Results for unsupervised training on synthetic data under various noise conditions.
+The table plots out the weights (mean and standard deviation) of the edges reconstructed by our model, for true positive matches and true negative ones.
+This shows under various noise conditions that our architecture can still recover the original connectivity structure of the matching graph.
 }
@@
 
-This reduces the number of our constraints from $O(n^3)$ to $O(n^2)$.
-We try to learn vertex embeddings $\mF_V$ to approximate $\mX$ - in other words the final embedding should be an encoding of the universe of features.
-As we do not have the ground truth matches $\mM$, we approximate it using the noisy adjacency matrix $\mA$ of our correspondence graph. Thus our loss would be 
-\begin{equation}
-\mathcal{L}(\mA, \mF_V) = \mathcal{D}(\mA, \mF_V \mF_V^\top)
-\end{equation}
-Here $\mathcal{D}$ could be an $L_2$ loss, $L_1$ loss, or many others. In this work, we use the $L_1$ loss. 
-Note that because of this formulation, we can determine our embeddings only up to a rotation, as
-$ \mF_V R(\mF_V R)^\top
-= \mF_V RR^\top \mF_V^\top
-= \mF_V\mF_V^\top
-\label{eq:rotinvar} $
-Thus when visualizing embeddings, we rotate them to make them more interpretable (see figure \ref{fig:embeddingsviz}).
+We first test our method on synthetically generated data as a simple proof of concept.
+As these were simpler datasets, we the simpler edge-feature free model of \citep{kipf2017semi}.
+To generate the data, we generate $p$ points, each with its own randomly generated descriptor.
+To create the graph, we generate random permutation matrices, with a noise applied to it after it is generated.
+We initialize the input descriptors using the synthetically generated ground truth descriptor, plus some added Gaussian noise.
+No geometric losses were added during training for these experiments.
+However, the method was robust in testing with different noise functions and parameters.
+The normalized noisy input descriptors are our baseline - they correlate with the true values but do not preserve the structure well.
+However, the GNN recovered the true structure very well, as shown in Table \ref{fig:synthtable}, showing the appropriate edge similarities.
+With this simple test on synthetic data passed, we now move to more challenging datasets.
 
-\subsection{Geometric Consistency Loss}
+\subsection{Rome 16K Graph Dataset}
 
-One of the main advantages of this approach over more traditional optimization based approaches is the ability to add geometric consistency information into the loss at training time, even if it is not available at test time.
-The simplest way to add geometric consistency losses, and the approach we use here, is to use the epipolar constraint.
-The epipolar constraint describes how the positions of features in different images corresponding to the same point should be related.
-An illustration of this is provided in figure \ref{fig:geoconsist}, showing how this loss can help reject erroneous points.
-Given a relative pose $(R_{ij}, T_{ij})$ between two cameras $i$ and $j$  (transforms $j$ to $i$) the epipolar on corresponding feature locations $X_i$ and $X_j$: $X_{i}^\top \cross{T_{ij}}R_{ij} X_{j} = 0$.
-In this work we use the two pose epipolar constraint (\cite{tron2014quotient}):
-\begin{equation}
-X_{i}^\top R_{i}^\top \cross{T_{j} - T_{i}}R_{j} X_{j} = 0
-\label{eq:essential_constraint}
-\end{equation}
-% Where the $(R_k, T_k)$ are the poses of cameras $i$ and $j$ respectively.
-The constraint assumes that the $X_k$ are calibrated (i.e. the camera intrinsics are known). 
-Given our vertex embeddings matrix $\mF_V$, we can formulate a loss between all cameras $i$ and $j$:
-\begin{align}
-\mathcal{L}_{ij,geom}(\mF_V) = 
-&\sum_{v \in \mV(i),u \in \mathcal{V}(j)} (\vf_v \cdot \vf_u) \left|X_{v}^\top R_{i}^\top \cross{T_{j} - T_{i}}R_{c_j} X_{u}\right|
-\label{eq:geom_cost}
-\end{align}
-With $\mathcal{V}(i)$ being the vertices associated with camera $i$.
-For our purposes, since we use low rank embeddings $\mF_{V, i}$, $\mF_{V, j}$, the loss would read (where $c(k)$ is the appropriate camera for point index $k$):
-\begin{align} 
-\mathcal{L}_{geom}(\mF_V)
-=&\; \mathrm{tr}(\mG^\top \mF_V\mF_V^\top) = \sum_{k,l} (\mF_V)_{k} \cdot (\mF_V)_{l} (\mG)_{kl} \label{eq:geom_cost2} \\
-(\mG)_{kl} =&\; \left|X_{k}^\top R_{c(k)}^\top \cross{T_{c(l)} - T_{c(k)}}R_{c(l)} X_{l}\right| \nonumber
-\end{align}
+\begin{figure}[t]
+\centering
+\includegraphics[width=0.95\linewidth]{figures-error_lines.pdf}
+% \includegraphics[height=200px]{figures-error_lines.pdf}
+\caption{
+  Plot of the losses of the baselines at different iteration numbers.
+  The line shows the mean of the graph while the translucent coloring shows the $25^{th}$ to $75^{th}$ percentiles.
+  The ROC AUC curves remain fairly consistent while the L1 loss goes noticibly down after more iterations.
+  Our method compares to 35-45 iterations of MatchALS, while only having 8 message passes.
+  PGDDS performs better than us in $L_1$ but we perform similarly in the ROC AUC metric.
+  These results still hold even when we change domains to the Graffiti dataset (see \ref{sec:graffiti}).
+}
+\label{fig:3}
+\label{fig:errorlines}
+\end{figure}
 
@@
 \hline\hline
-MatchALS 25 Iterations & 0.092 $\pm$ 0.008 & 0.019 $\pm$ 0.003 & 0.912 $\pm$ 0.055 & 0.228 $\pm$ 0.014 \\ \hline
+MatchALS 15 Iterations & 0.114 $\pm$ 0.008 & 0.028 $\pm$ 0.004 & 0.915 $\pm$ 0.051 & 0.142 $\pm$ 0.009 \\ \hline
 MatchALS 35 Iterations & 0.065 $\pm$ 0.009 & 0.013 $\pm$ 0.003 & 0.907 $\pm$ 0.053 & 0.355 $\pm$ 0.073 \\ \hline
@@
 Thus we test against ground truth correspondence graph adjacency matrices computed from the bundle adjustment output.
-Our method performs better than 25 iteration of the MatchALS (\cite{zhou2015multi}) method, but does not perform as well as 50 iterations.
-% Our network has only 12 layers, thus we have much greater efficiency per iteration.
-We do not perform as well as the Projected Gradient Descent Doubly Stochastic (PGDDS) (\cite{leonardos2016distributed}) but we perform significantly faster than them.
-We perform better than a simple eigenvalue based method (\cite{pachauri2013solving}).
+Our method performs better than 25 iteration of the MatchALS \citep{zhou2015multi} method, but does not perform as well as 50 iterations.
+We do not perform as well as the Projected Gradient Descent Doubly Stochastic (PGDDS) \citep{leonardos2016distributed} but we perform significantly faster than them.
+We perform better than a simple eigenvalue based method \citep{pachauri2013solving}.
 Note that we perform much better in $L_1$ performance rather than $L_2$, as we optimized the network weights using an $L_1$ loss.
@@
 
-%------------------------------------------------------------------------
-\section{Experiments}
-
-% \begin{figure*}
-% \begin{center}
-%   % \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
-%   \includegraphics[width=0.8\linewidth]{figures-ExampleOutput.pdf}
-%   \end{center}
-%      \caption{Example output of our network.
-(a) Similarity Matrix of the of the embeddings (b) Histogram of feature similarities for pairs which correspond to the same 3D point, comparing our output features with the original SIFT features (c) Histogram of feature similarities for pairs which correspond to different 3D points, comparing our output features with the original SIFT features}
-%   \label{fig:short}
-% \end{figure*}
-
-\subsection{Synthetic Graph Dataset}
-We first test our method on synthetically generated data as a simple proof of concept.
-As these were simpler datasets, we the simpler edge-feature free model of (\cite{kipf2017semi}).
-To generate the data, we generate $p$ points, each with its own randomly generated descriptor.
-To create the graph, we generate random permutation matrices, with a noise applied to it after it is generated.
-% The initial descriptors we use as input we created using the true descriptor plus some added Gaussian noise.
-We initialize the input descriptors using the true descriptor, plus some added Gaussian noise.
-No geometric losses were added during training for these experiments.
-However, the method was robust in testing with different noise functions and parameters.
-The normalized noisy input descriptors are our baseline - they correlate with the true values but do not preserve the structure well.
-However, the GNN recovered the true structure very well, as shown in Table \ref{fig:synthtable}.
-All experiments were run with a 12 layer GNN with the ReLU nonlinearity and skip connections.
-The feature vector lengths were 32, 64, 128, 256, 512, 512, 512, 512, 512, 512, 1024, 1024, with skip connections between layers 1 and 6, 6 and 12, and 1 and 12.
-All were trained with the Adam optimizer (\cite{kingma2014adam}) and a learning rate $10^{-4}$
-The network was implemented in Tensorflow (\cite{tensorflow2015}), version 1.11.
-With this simple test on synthetic data passed, we now move to more challenging datasets.
-
-\begin{figure}[t]
-\centering
-\includegraphics[width=0.95\linewidth]{figures-error_lines.pdf}
-% \includegraphics[height=200px]{figures-error_lines.pdf}
-\caption{
-  Plot of the losses of the baselines at different iteration numbers.
-  The line shows the mean of the graph while the translucent coloring shows the $25^{th}$ to $75^{th}$ percentiles.
-  The ROC AUC curves remain fairly consistent while the L1 loss goes noticibly down after more iterations.
-  Our method compares to 35-45 iterations of MatchALS, while only having 16 layers and 8 message passes.
-  PGDDS performs better than us in $L_1$ but we perform similarly in the ROC AUC metric.
-  These results still hold even when we change domains to the Graffiti dataset (see \ref{sec:graffiti}).
-}
-\label{fig:3}
-\label{fig:errorlines}
-\end{figure}
-
-% 
-% \begin{figure}[t]
-% \centering
-% \begin{subfigure}[b]{.70\textwidth}
-%   \centering
-%   % \includegraphics[width=0.95\linewidth]{figures-error_lines.pdf}
-%   \includegraphics[height=200px]{figures-error_lines.pdf}
-%   \caption{}
-%   \label{fig:3a}
-%   \label{fig:errorlines}
-% \end{subfigure}
-% \begin{subfigure}[b]{.25\textwidth}
-%   \centering
-%   % \includegraphics[width=0.65\linewidth]{figures-GeometricLoss.pdf}
-%   \includegraphics[height=200px]{figures-GeometricLoss.pdf}
-%   \caption{}
-%   \label{fig:3b}
-%   \label{fig:geomloss}
-% \end{subfigure}
-% \caption{
-%   \textbf{(a)} Plot of the losses of the baselines at different iteration numbers.
-%   The line shows the mean of the graph while the translucent coloring shows the $25^{th}$ to $75^{th}$ percentiles.
-%   The ROC AUC curves remain fairly consistent while the L1 loss goes noticibly down after more iterations.
-%   Our method compares to 35-45 iterations of MatchALS, while only having 16 layers and 8 message passes.
-%   PGDDS performs better than us in $L_1$ but we perform similarly in the ROC AUC metric.
-%   \textbf{(b)} Training curves with and without Geometric Training loss, described in \ref{eq:geom_cost2}.
-%   The geometric training loss improves testing performance.
-%   While the training is higher due to the additional loss terms, the ground truth L1 error is substantially better with the Geometric Loss.
-%   Best viewed in color.
-% }
-% \label{fig:3}
-% \end{figure}
-
-\subsection{Rome 16K Graph Dataset}
-We  use the Rome16K dataset (\cite{li2010location}) to test our algorithm in real world settings.
+We  use the Rome16K dataset \citep{li2010location} to test our algorithm in real world settings.
 Rome16K consists of 16 thousand images of various historical sites in Rome extracted from Flickr, along with the 3D structure of the sites provided by bundle adjustment.
-While not a standard dataset to test cycle consistency, other datasets had insufficient data to train a network on.
+While not a standard dataset to test cycle consistency, most standard datasets have tens or hundreds images, not enough to train a GNN on.
 Rome16K is typically used to test bundle adjustment methods.
@@
 However, we do not train with the ground truth adjacency matrix, only with the noisy adjacency matrix from the graph.
-We also add the geometric loss (\ref{eq:geom_cost2}) which helps improve testing performance (see figure \ref{fig:geomloss})
+We also add the geometric loss (\ref{eq:geom_cost2}) which helps improve testing performance (see figure \ref{fig:geomloss}).
 We use the $L_1$ and ROC AUC metrics to measure performance.
@@
 
-The network was implemented using the code provided by \cite{battaglia2018relational} using Tensorflow 1.11 (\cite{tensorflow2015}).
+The network was implemented using the code provided by \cite{battaglia2018relational} using Tensorflow 1.11 \citep{tensorflow2015}.
 Our network has 16 layers, with 8 message passing operations placed every other layer.
 All layers were simple Multi-layer Perceptrons, with no batch norm.
-The network was trained with the Adam optimizer (\cite{kingma2014adam}) with a learning rate of $10^{-4}$, with an exponentially decaying learning rate.
+The network was trained with the Adam optimizer \citep{kingma2014adam} with a learning rate of $10^{-4}$, with an exponentially decaying learning rate.
 We incorporate skip connections between the input, $6^{th}$, and $12^{th}$ layers (all possible pairs).
 
-% Our method performs better than nearly 
 We compare our method to spectral and optimization based baselines with different maximum iteration cutoffs.
 Figure \ref{fig:errorlines} illustrates this by plotting the means of various metrics and their $25^{th}$ and $75^{th}$ percentiles, with table \ref{tab:rome16ktab} giving the exact numbers.
-Our network, though only using 8 message passes, has comparable accuracy to MatchALS (\cite{zhou2015multi}) run 35 to 45 iterations, with an equivalent message passing step at each phase.
-Although our method does not outperform the Projected Gradient Descent - Doubly Stochastic (PGDDS) (\cite{leonardos2016distributed}) method, we perform comparably to them in the ROC AUC metric.
-% Our network, though only 12 layers, has comparable accuracy to MatchALS \cite{zhou2015multi} run between 25 and 50 iterations.
-% Additional comparisons to different iterations numbers of iterations can be found in the supplementary material.
+Our network, though only using 8 message passes, has comparable accuracy to MatchALS \citep{zhou2015multi} run 35 to 45 iterations, with an equivalent message passing step at each phase.
+Although our method does not outperform the Projected Gradient Descent - Doubly Stochastic (PGDDS) \citep{leonardos2016distributed} method, we perform comparably to them in the ROC AUC metric.
 
 \subsubsection{Graffiti Dataset} \label{sec:graffiti}
-We also run our trained model on the Graffiti Dataset (formatted to be able to be input to our model properly).
-The results are shown in \ref{fig:errorlines} in the rightmost figure.
+We run our trained model on the more Graffiti Dataset (formatted to be able to be input to our model properly).
+The Graffiti Dataset is the most common benchmark used in feature matching algorithms (e.g. \ref{leonardos2016distributed, zhou2015multi}).
+The results are shown in figure \ref{fig:errorlines} in the rightmost figure.
 As the graffiti dataset is very small (only 6 views total), we were not able to train on it.
@@
 We have shown a novel method for training feature matching using GNNs, using an unsupervised cycle consistency loss and geometric consistency losses.
-We have demonstrated has comparable the traditional optimization based baselines on a simple GNN, while still allowing for end-to-end training integration in deep learning pipelines.
+We have demonstrated end-to-end trainable GNNs have comparable performance the traditional optimization-based baselines.
 For future work, we will investigate robust losses for better outlier rejection, and using higher order geometric constraints, such as the tri-focal tensor, as additional loss terms.
@@
 With this new architecture, we have the capability of training multi-image matching pipelines end to end, thus allowing us to train for image features explicitly for this task.
-We can also extend this to distributed settings where we can train for matching images from multiple distributed agents.
+We can extend this to distributed settings where we can train for matching images from multiple distributed agents.
 
@@
 
-% \appendix
-% \section{Appendix}
-% You may include other additional sections here.
+\appendix
+\section{More Detail on GNN Architecture}
+All experiments were run with a 12 layer GNN with the ReLU nonlinearity and skip connections.
+The feature vector lengths were 32, 64, 128, 256, 512, 512, 512, 512, 512, 512, 1024, 1024, with skip connections between layers 1 and 6, 6 and 12, and 1 and 12.
+All were trained with the Adam optimizer \citep{kingma2014adam} and a learning rate $10^{-4}$
+The network was implemented in Tensorflow \citep{tensorflow2015}, version 1.11.
 
 \end{document}
-
-% \begin{table*}[t]
-% \begin{center}
-% \begin{tabular}{|l|c|c|c|c|}
-% \hline
-% Method (6 Views)                                     & $L_1$             & $L_2$             & Area under ROC    & Time (sec)        \\
-% \hline\hline
-% MatchALS 15 Iterations & 0.101 $\pm$ 0.008 & 0.022 $\pm$ 0.004 & 0.918 $\pm$ 0.073 & 0.074 $\pm$ 0.008 \\ \hline
-% MatchALS 25 Iterations & 0.059 $\pm$ 0.010 & 0.012 $\pm$ 0.004 & 0.921 $\pm$ 0.077 & 0.143 $\pm$ 0.064 \\ \hline
-% MatchALS 35 Iterations & 0.046 $\pm$ 0.016 & 0.010 $\pm$ 0.005 & 0.910 $\pm$ 0.072 & 0.139 $\pm$ 0.041 \\ \hline
-% MatchALS 50 Iterations & 0.029 $\pm$ 0.017 & 0.008 $\pm$ 0.005 & 0.905 $\pm$ 0.068 & 0.260 $\pm$ 0.048 \\ \hline
-% PGDDS0 15 Iterations   & 0.017 $\pm$ 0.002 & 0.007 $\pm$ 0.001 & 0.918 $\pm$ 0.087 & 0.796 $\pm$ 0.147 \\ \hline
-% PGDDS0 25 Iterations   & 0.016 $\pm$ 0.002 & 0.007 $\pm$ 0.002 & 0.919 $\pm$ 0.087 & 1.670 $\pm$ 0.328 \\ \hline
-% PGDDS0 50 Iterations   & 0.015 $\pm$ 0.002 & 0.006 $\pm$ 0.002 & 0.920 $\pm$ 0.087 & 3.363 $\pm$ 0.528 \\ \hline
-% Spectral               & 0.073 $\pm$ 0.006 & 0.027 $\pm$ 0.003 & 0.921 $\pm$ 0.083 & 0.036 $\pm$ 0.005 \\ \hline
-% \textbf{GNN (ours)}    & 0.044 $\pm$ 0.005 & 0.031 $\pm$ 0.005 & 0.872 $\pm$ 0.081 & 0.765 $\pm$ 0.046 \\ \hline
-% 
-% \hline\hline
-% Method (10 Views)                                   & $L_1$             & $L_2$             & Area under ROC    & Time (sec)        \\
-% \hline\hline
-% MatchALS 15 Iterations & 0.114 $\pm$ 0.008 & 0.028 $\pm$ 0.004 & 0.915 $\pm$ 0.051 & 0.142 $\pm$ 0.009 \\ \hline
-% MatchALS 25 Iterations & 0.092 $\pm$ 0.008 & 0.019 $\pm$ 0.003 & 0.912 $\pm$ 0.055 & 0.228 $\pm$ 0.014 \\ \hline
-% MatchALS 35 Iterations & 0.065 $\pm$ 0.009 & 0.013 $\pm$ 0.003 & 0.907 $\pm$ 0.053 & 0.355 $\pm$ 0.073 \\ \hline
-% MatchALS 50 Iterations & 0.045 $\pm$ 0.012 & 0.011 $\pm$ 0.004 & 0.914 $\pm$ 0.051 & 0.455 $\pm$ 0.022 \\ \hline
-% PGDDS 15 Iterations    & 0.017 $\pm$ 0.001 & 0.008 $\pm$ 0.001 & 0.903 $\pm$ 0.061 & 1.225 $\pm$ 0.159 \\ \hline
-% PGDDS 25 Iterations    & 0.016 $\pm$ 0.001 & 0.007 $\pm$ 0.001 & 0.904 $\pm$ 0.061 & 2.637 $\pm$ 0.357 \\ \hline
-% PGDDS 50 Iterations    & 0.016 $\pm$ 0.001 & 0.007 $\pm$ 0.001 & 0.905 $\pm$ 0.061 & 6.116 $\pm$ 1.009 \\ \hline
-% Spectral               & 0.073 $\pm$ 0.005 & 0.029 $\pm$ 0.002 & 0.912 $\pm$ 0.057 & 0.081 $\pm$ 0.021 \\ \hline
-% \textbf{GNN (ours)}    & 0.053 $\pm$ 0.006 & 0.035 $\pm$ 0.005 & 0.872 $\pm$ 0.061 & 2.438 $\pm$ 0.070 \\ \hline
-% 
-% \end{tabular}
-% \end{center}
-% 
-% \caption{
-% Results on Rome16K Correspondence graphs, showing the mean and standard deviation of the $L_1$ and $L_2$.
-% Our method was not trained on ground truth correspondences but using unsupervised methods and geometric side losses.
-% Thus we test against ground truth correspondence graph adjacency matrices computed from the bundle adjustment output.
-% Our method performs better than 25 iteration of the MatchALS (\cite{zhou2015multi}) method, but does not perform as well as 50 iterations.
-% % Our network has only 12 layers, thus we have much greater efficiency per iteration.
-% We do not perform as well as the Projected Gradient Descent Doubly Stochastic (PGDDS) (\cite{leonardos2016distributed}) but we perform significantly faster than them.
-% We perform better than a simple eigenvalue based method (\cite{pachauri2013solving}).
-% Note that we perform much better in $L_1$ performance rather than $L_2$, as we optimized the network weights using an $L_1$ loss.
-% }
-% \label{tab:rome16ktab}
-% \end{table*}

### 2019-09-25 latex/iclr2020/main.tex
Added more of Daphne's suggestions

@@
     We use cycle consistency to train our network in an unsupervised fashion, since ground truth correspondence can be difficult or expensive to acquire.
-    % TODO: Ask Sid if this is any good
     Geometric consistency losses are added to aid training, though unlike optimization based methods no geometric information is necessary at inference time.
@@
 \end{abstract}
-%     Image feature matching is a fundamental part of many geometric computer vision applications, and using multiple images can improve performance.
-%     In this work, we formulate multi-image matching as a graph embedding problem then use a Graph Neural Network to learn an appropriate embedding function for aligning image features.
-%     We use cycle consistency to train our network in an unsupervised fashion, since ground truth correspondence is difficult or expensive to acquire.
-%     In addition, geometric consistency losses can be added at training time, even if the information is not available in the test set, unlike previous approaches which optimize cycle consistency directly.
-%     To the best of our knowledge, no other works have used graph neural networks for multi-image feature matching.
-%     Our experiments show that our method is competitive with other optimization based approaches.
 
@@
 \subsection{Multi-image Matching}
-Multi-image matching has traditionally been done using optimization based methods minimizing a cycle consistency based loss (see Section 3.3).
+Multi-image matching has traditionally been done using optimization based methods minimizing a cycle consistency based loss (see Section \ref{sec:cycconsist}).
 \cite{pachauri2013solving} and \cite{arrigoni2017synchronization} use the eigenvectors of the matching matrix to obtain a low dimensional embedding. 
@@
 As an alternative to optimization based techniques, \cite{tron2017fast} used density based clustering techniques to compute multi-image correspondence.
-Moving away from feature matching, \cite{zach2010disambiguating} uses cycle consistency like constraints on pose graphs quite effectively.
+Moving away from feature matching, \cite{zach2010disambiguating} uses cycle-consistency-like constraints on pose graphs quite effectively.
 To the best of our knowledge, we are the first to use graph neural networks for multi-image matching.
@@
 Previous attempts to improve image matching techniques using machine learning have focused on learning the descriptors given ground truth correspondence from curated datasets such as \cite{zagoruyko2015learning}; \cite{yi2016lift}; and \cite{brachmann2017dsac}.
-This approach is limited if one do not have the ability to get the ground truth correspondences.
+This approach is limited if one does not have the ability to get the ground truth correspondences.
 There are other methods to build correspondences such as \cite{choy2016universal}, but they only handle two-view constraints and require dense correspondences.
-Most similar to our work, \cite{yi2018learning} attempts to improve correspondences by learning match probabilities for RANSAC for greater robustness and speed.
-However, they only focus on two view matching and do not exploit the advantages of the correspondence structure.
-Like us \cite{zhu2017unpaired} use cycle consistency in their loss, however their method is restricted to pairwise cycle consistency (i.e.
-enforcing consistency by going back and forth between two images).
+Most similar to our work, \cite{yi2018learning} attempts to improve correspondences by learning match probabilities for two-view RANSAC for greater robustness and speed.
+Like us \cite{zhu2017unpaired} use cycle consistency in their loss; however their method is for image generation and is restricted to pairwise cycle consistency.
 Our method can be applied to 3 or more images. 
@@
 The first methods to learn neural networks over graphs were the so-called Spectral methods.
-They used the eigenvectors of the graph Laplacian to compute convolutions as in \cite{bruna2013spectral}, which can learn graph specific convolution kernels, but require an a-priori known graph structure.
+They used the eigenvectors of the graph Laplacian to compute convolutions, which can learn graph specific convolution kernels (as in \cite{bruna2013spectral}), but require an a-priori known graph structure.
 Newer non-spectral methods do not require a-priori knowledge, as seen in \cite{bronstein2017geometric, kipf2017semi, scarselli2009graph}; and \cite{gama2018convolutional}.
@@
   On the left we have the raw outputs, which are difficult to interpret.
-  In the center, we rotated the features to best match the ground truth for a more interpretable visualization (see the end of section \ref{sec:cycconsist}).
+  In the center, we rotated the features to best match the ground truth for a more interpretable visualization (see the end of Section \ref{sec:cycconsist}).
   On the right, we have the ground truth embeddings, given as indicator vectors for which feature in the world the points correspond to.
@@
 \subsection{Graph Neural Networks} \label{sec:gnns}
-As input to our method we are given a graph $\mathcal{G} = (\mathcal{V}, \mathcal{E})$ with the features described in section \ref{sec:corrgraph} $\vf_v \; \forall v \in \mathcal{V}$ and $\vf_e \; \forall e \in \mathcal{E}$.
+As input to our method we are given a graph $\mathcal{G} = (\mathcal{V}, \mathcal{E})$ with the features described in Section \ref{sec:corrgraph}: $\vf_v \; \forall v \in \mathcal{V}$ and $\vf_e \; \forall e \in \mathcal{E}$.
 As with any neural network, GNNs have layered outputs.
@@
 Newer models use non-spectral methods, which often ultimately amount to transforming each node with learned weights then averaging each node's representation with its neighbors, known as a message pass \citep{kipf2017semi, defferrard2016convolutional, gama2018mimo, gama2018convolutional}.
-Some works such as \cite{gama2019convolutional} use pooling operations on the vertices to make the graph smaller and thus aid computation, but as we need labels on every vertex of the original graph, so we cannot use this.
+Some works such as \cite{gama2019convolutional} use pooling operations on the vertices to make the graph smaller and thus aid computation, but as we need labels on every vertex of the original graph, we cannot use this.
 Most GNNs used in these works can be expressed mathematically as:
@@
 The weights/biases $\mW_{h}^{k}$, $b^{(k)}$ are all learned, with no learning done on the edge weights $f_{e(v,v')}$. 
-Note that this is just sums or averages over $h$-hop neighborhoods, where the weights on the edges remain static through the computation.
+Note that this is just averages over $h$-hop neighborhoods, where the weights on the edges remain static through the computation.
 Given that we are trying to prune edges, it would be sensible to add features over edges to learn which ones to prune and which to keep such as in \cite{scarselli2009graph}.
@@
 \caption{
-  \textbf{(a)} Errors are computed via absolute distance from the epipolar line, as expressed by (\ref{eq:essential_constraint}) via the epipolar constraint.
-  The epipolar line is the line of projection of the feature on the first image, projected onto to the second.
+  \textbf{(a)} Errors are computed via absolute distance from the epipolar line, as expressed by Equation \ref{eq:essential_constraint} via the epipolar constraint.
+  The epipolar line is the line of projection of the feature in the first image, projected into to the second.
   The distance to this line on the second image indicates how likely that point is to correspond geometrically to the original feature.
@@
   The geometric training loss improves testing performance.
-  While the training is higher due to the additional loss terms, the ground truth L1 error is substantially better with the Geometric Loss.
+  Note how training with geometric consistency losses decreases the convergence time of the network.
   Best viewed in color.

### 2019-10-03 latex/iclr2020/main.tex
Final Latex for ICLR - forgot to commit earlier (as usual)

@@
     In geometric computer vision applications, multi-image feature matching gives more accurate and robust solutions compared to simple two-image matching.
-    In this work, we formulate multi-image matching as a graph embedding problem then use a Graph Neural Network to learn an appropriate embedding function for aligning image features.
+    In this work, we formulate multi-image matching as a graph embedding problem, then use a Graph Neural Network to learn an appropriate embedding function for aligning image features.
     We use cycle consistency to train our network in an unsupervised fashion, since ground truth correspondence can be difficult or expensive to acquire.
@@
 The goal in multi-image feature matching is to take 2D feature positions from three or more images and find which ones correspond to the same point in the 3D scene.
-Methods such as SIFT feature matching \citep{lowe2004distinctive} followed by RANSAC \citep{fischler1981random} have been the standard for decades.
+Methods such as SIFT feature matching \citep{lowe2004distinctive} combined with RANSAC \citep{fischler1981random} have been the standard for decades.
 However RANSAC-based approaches are limited to matching pairs of images, which can lead to global inconsistencies in the matching.
@@
 
-However, these multi-view consistency algorithms struggle in distributed and robust settings.
+However, these multi-view consistency algorithms struggle in distributed and noisy settings.
 Having image features suited for this task would help improve performance, and deep learning has revolutionized how image features are computed \citep{yi2016lift}.
@@
 \item We use a novel architecture to address the multi-image feature matching problem using GNNs with graph embeddings.
-\item We introduce an unsupervised cycle consistency loss that does not require labeled correspondences to train.
+\item We introduce an unsupervised multi-view cycle consistency loss that does not require labeled correspondences to train.
 \item We demonstrate the effectiveness of geometric consistency losses in improving training.
@@
 Our method can be applied to 3 or more images. 
-\cite{hartmann2017learned} in fact learns multi-image matching but requires heavy supervision from 3D object reconstructions, which are not available in the context we are in.
+\cite{hartmann2017learned} learns multi-image matching but requires heavy supervision from 3D object reconstructions, which can be difficult or expensive to obtain.
 
@@
 To improve performance, more sophisticated aggregation techniques and global information passing can be used as discussed in \cite{battaglia2018relational}.
-The closest work on Graph Neural Networks to ours is \cite{kipf2016variational}, which uses GNNs to reconstruct the adjacency matrices, though not in a geometric context.
+The closest work on Graph Neural Networks to ours is \cite{kipf2016variational}, which uses GNNs to reconstruct adjacency matrices, though not in a geometric context.
 
@@
 We formulate this problem in terms of the correspondence graph of the features.
-Graphs $\mathcal{G} = (\mathcal{V}, \mathcal{E})$ have a set of vertices $\mathcal{V}$ and of edges $\mathcal{E} \subseteq \mathcal{V} \times \mathcal{V}$ and implicitly in the subsequent discussions we assume the edges are directed.
+Graphs $\mathcal{G} = (\mathcal{V}, \mathcal{E})$ have a set of vertices $\mathcal{V}$ and of directed edges $\mathcal{E} \subseteq \mathcal{V} \times \mathcal{V}$.
 For a vertex $v \in \mathcal{V}$ we use $\mathcal{N}^{h}(v)$ to denote the $h$-hop neighbors of $v$, with the superscript left out for 1-hop neighbors.
@@
 
-\subsection{Graph Neural Networks} \label{sec:gnns}
+\subsection{Graph Neural Networks for Feature Matching} \label{sec:gnns}
 As input to our method we are given a graph $\mathcal{G} = (\mathcal{V}, \mathcal{E})$ with the features described in Section \ref{sec:corrgraph}: $\vf_v \; \forall v \in \mathcal{V}$ and $\vf_e \; \forall e \in \mathcal{E}$.
@@
 Note that this is just averages over $h$-hop neighborhoods, where the weights on the edges remain static through the computation.
-Given that we are trying to prune edges, it would be sensible to add features over edges to learn which ones to prune and which to keep such as in \cite{scarselli2009graph}.
+Given that we are trying to prune edges, we add features over edges to learn which ones to prune and which to keep such as in \cite{scarselli2009graph}.
 
-In this work we use the method and implementation described in \cite{battaglia2018relational} (more specifically repetitions of the architecture described in \cite{battaglia2016interaction}).
+In this work we use the method and implementation described in \cite{battaglia2018relational}.
 \cite{battaglia2018relational} uses message passes between node features as well as edge features, which the model can use to prune unnecessary or erroneous edges.
@@
 Thus we test against ground truth correspondence graph adjacency matrices computed from the bundle adjustment output.
-Our method performs better than 25 iteration of the MatchALS \citep{zhou2015multi} method, but does not perform as well as 50 iterations.
-We do not perform as well as the Projected Gradient Descent Doubly Stochastic (PGDDS) \citep{leonardos2016distributed} but we perform significantly faster than them.
+Our method performs better than 35 iteration of the MatchALS \citep{zhou2015multi} method, but does not perform as well as 50 iterations.
+% We do not perform as well as the Projected Gradient Descent Doubly Stochastic (PGDDS) \citep{leonardos2016distributed} but we perform significantly faster than them.
 We perform better than a simple eigenvalue based method \citep{pachauri2013solving}.
@@
 We evaluate on a test set using the ground truth adjacency matrix, which we compute from the bundle adjustment given by the Rome16K dataset.
-However, we do not train with the ground truth adjacency matrix, only with the noisy adjacency matrix from the graph.
+However, we do not train with the ground truth adjacency matrix, only with a noisy version of the adjacency matrix.
 We also add the geometric loss (\ref{eq:geom_cost2}) which helps improve testing performance (see figure \ref{fig:geomloss}).
@@
 \subsubsection{Graffiti Dataset} \label{sec:graffiti}
-We run our trained model on the more Graffiti Dataset (formatted to be able to be input to our model properly).
-The Graffiti Dataset is the most common benchmark used in feature matching algorithms (e.g. \ref{leonardos2016distributed, zhou2015multi}).
+We run our trained model on the more Graffiti Dataset from the Affine Covariant Regions dataset (formatted to be able to be input to our model properly).
+The Graffiti Dataset is the most common benchmark used in feature matching algorithms (e.g. \cite{leonardos2016distributed, zhou2015multi}).
 The results are shown in figure \ref{fig:errorlines} in the rightmost figure.

### 2019-10-03 baselines/plot_logs.py
Adding ICLR plot code

@@ -31,7 +31,19 @@ def myprint(x):
   else:
     pp_xfawedfssa.pprint(process(x))
 
+def str2bool(v):
+  if v.lower() in ('yes', 'true', 't', 'y', '1'):
+    return True
+  elif v.lower() in ('no', 'false', 'f', 'n', '0'):
+    return False
+  else:
+    import argparse
+    raise argparse.ArgumentTypeError('Boolean value expected.')
+
+
 parser = argparse.ArgumentParser(description='Plot the downloaded model training/testing curves')
+parser.add_argument('--transpose', type=str2bool, default=True,
+                    help='Columns wise or Row wise errors')
 parser.add_argument('files', metavar='files', nargs='+',
                     help='Files to plot. If concatenating files in list put between parenthesis')
 
@@ -266,17 +278,25 @@ args = parser.parse_args()
 aggs_view, iters_view = parse_files(args.files)
 nviews, nplots = len(iters_view), len(plot_keys)
 sz, R, C = 4, nviews, nplots
+if args.transpose:
+  R, C = C, R
 fig, ax_ = plt.subplots(nrows=R, ncols=C, figsize=(3+C*sz, 3+R*sz))
-if R > 1:
-  ax = {
-    v: dict(zip(plot_keys, ax_[i]))
-    for i, v in enumerate(sorted(iters_view.keys()))
-  }
-else:
+if R == 1 or C == 1:
   ax = {
     k: dict(zip(plot_keys, ax_))
     for k in iters_view.keys()
   }
+elif args.transpose:
+  ax = {
+    v: dict(zip(plot_keys, ax_[:,i]))
+    for i, v in enumerate(sorted(iters_view.keys()))
+  }
+else:
+  ax = {
+    v: dict(zip(plot_keys, ax_[i]))
+    for i, v in enumerate(sorted(iters_view.keys()))
+  }
+
 miniters = { v: 10**9 for v in iters_view }
 maxiters = { v: 0 for v in iters_view }
 for v in iters_view:
@@ -305,14 +325,20 @@ for v in sorted(iters_view.keys()):
                 label=label,
                 ax=ax[v][k],
                 alpha=0.2)
-      title = '{} ({} views)'.format(get_title(k), v)
+      if v == 11: # TODO: such hack
+        title = '{} (Graffiti)'.format(get_title(k))
+      else:
[…]

### 2019-11-13 latex/iclr2020/main.tex
Updated tex file for rebuttal

@@
 \usepackage{url}
+\usepackage{xcolor}
 
@@
 \cite{leonardos2016distributed} implement a distributed optimization scheme to solve for cycle consistency.
+\textcolor{red}{\cite{swoboda2019convex} implement a convex relaxation of the low dimensional embedding problem.}
+\textcolor{red}{\cite{shi2016tensor} use tensor power iterations to solve the matching problem, also taking into account the intra-image matching graph.}
 As an alternative to optimization based techniques, \cite{tron2017fast} used density based clustering techniques to compute multi-image correspondence.
@@
 \cite{hartmann2017learned} learns multi-image matching but requires heavy supervision from 3D object reconstructions, which can be difficult or expensive to obtain.
+\textcolor{red}{\cite{zhou2015flowweb}, unlike our method, uses dense correspondence, but uses cycle consistency to find semantic matches accross multiple views.}
+\textcolor{red}{\cite{suwajanakorn2018discovery} find 3 dimensional latent keypoints, trained using ground truth rotation and translation.
+However, their method is restricted to a limited number of object categories, which is different from the SfM setting we are considering here.}
 
@@
 This reduces the number of our constraints from $O(n^3)$ to $O(n^2)$.
+\textcolor{red}{This was shown to be equivalent to the original definition of cycle consistency (equation \ref{eq:cycconsist1}) in \cite{huang2013consistent}.}
 We try to learn vertex embeddings $\mF_V$ to approximate $\mX$ - in other words the final embedding should be an encoding of the universe of features.
@@
 \hline\hline\hline
-Ideal                              & 1.00e+0 $\pm$ 0.00e+0 & 0.00e+0 $\pm$ 0.00e+0 \\ \hline
-Initialization Baseline            & 5.11e-1 $\pm$ 1.68e-2 & 2.56e-1 $\pm$ 2.06e-1 \\ \hline
-5 Views, Noiseless                 & 1.00e+0 $\pm$ 4.15e-4 & 1.22e-1 $\pm$ 1.67e-1 \\ \hline
-6 Views, Added Noise               & 9.84e-1 $\pm$ 3.16e-2 & 7.46e-2 $\pm$ 1.57e-1 \\ \hline
-3 Views, 5\% Outliers              & 9.29e-1 $\pm$ 1.79e-1 & 1.41e-1 $\pm$ 1.48e-1 \\ 
-3 Views, 10\% Outliers             & 9.27e-1 $\pm$ 1.79e-1 & 1.40e-1 $\pm$ 1.51e-1 \\ \hline
+Ideal                              & \textcolor{red}{1.000} $\pm$ \textcolor{red}{0.0000} & \textcolor{red}{0.0000} $\pm$ \textcolor{red}{0.0000} \\ \hline
+Initialization Baseline            & \textcolor{red}{0.511} $\pm$ \textcolor{red}{0.0168} & \textcolor{red}{0.2560} $\pm$ \textcolor{red}{0.2060} \\ \hline
+5 Views, Noiseless                 & \textcolor{red}{1.000} $\pm$ \textcolor{red}{0.0004} & \textcolor{red}{0.1220} $\pm$ \textcolor{red}{0.1670} \\ \hline
+6 Views, Added Noise               & \textcolor{red}{0.984} $\pm$ \textcolor{red}{0.0031} & \textcolor{red}{0.0746} $\pm$ \textcolor{red}{0.1570} \\ \hline
+3 Views, 5\% Outliers              & \textcolor{red}{0.929} $\pm$ \textcolor{red}{0.1790} & \textcolor{red}{0.1410} $\pm$ \textcolor{red}{0.1480} \\ 
+3 Views, 10\% Outliers             & \textcolor{red}{0.927} $\pm$ \textcolor{red}{0.1790} & \textcolor{red}{0.1400} $\pm$ \textcolor{red}{0.1510} \\ \hline
 

### 2019-11-13 latex/iclr2020/main.tex
More ICLR revisions

@@
 % TODO: Mention trifocal tensors
-Other works, such as \cite{wang2017multi}, have shown improvement in performance by optimizing cycle consistency, i.e. enforcing the pairwise feature matches to be globally consistent.
+Other works, such as \cite{wang2018multi}, have shown improvement in performance by optimizing cycle consistency, i.e. enforcing the pairwise feature matches to be globally consistent.
 
@@
 We use geometric consistency losses to aid training, though no geometric information is used at inference time.
-Although our network is simple, it shows promising results compared to baselines which optimize for cycle-consistency without learned embeddings, using a matrix factorization loss \citep{zhou2015multi, leonardos2016distributed}.
+Although our network is simple, it shows promising results compared to baselines which optimize for cycle-consistency without learned embeddings, using a matrix factorization loss \citep{zhou2015multi, leonardos2017distributed}.
 Furthermore, since inference requires only a single forward pass over the neural network, our approach is faster to achieve comparable accuracy than methods which must solve an optimization problem every time.
@@
 \cite{zhou2015multi} and \cite{wang2017multi} use more sophisticated optimization techniques on the matching matrix and thus produce more robust solutions.
-\cite{leonardos2016distributed} implement a distributed optimization scheme to solve for cycle consistency.
+\cite{leonardos2017distributed} implement a distributed optimization scheme to solve for cycle consistency.
 \textcolor{red}{\cite{swoboda2019convex} implement a convex relaxation of the low dimensional embedding problem.}
@@
 Previous attempts to improve image matching techniques using machine learning have focused on learning the descriptors given ground truth correspondence from curated datasets such as \cite{zagoruyko2015learning}; \cite{yi2016lift}; and \cite{brachmann2017dsac}.
-This approach is limited if one does not have the ability to get the ground truth correspondences.
+\textcolor{red}{\cite{rocco2018neighbourhood} use a dense matching tensor with a weakly supervised loss to learn good features for matching.
+\cite{zhou2019learn} has shown that these learned representations have limited ability for improving SfM tasks.}
+% This approach is limited if one does not have the ability to get the ground truth correspondences.
+
 There are other methods to build correspondences such as \cite{choy2016universal}, but they only handle two-view constraints and require dense correspondences.
@@
 In other words, the matches between two images stay the same no matter what path is taken to get there. 
-This constraint is known as \textit{cycle consistency}, and has been used in a number of works to optimize for global consistency \cite{zhou2015multi, wang2017multi, leonardos2016distributed}.
+This constraint is known as \textit{cycle consistency}, and has been used in a number of works to optimize for global consistency \cite{zhou2015multi, wang2017multi, leonardos2017distributed}.
 Stated in this form, there are $O(n^3)$ cycle consistency constraints to check.
@@
 Our method performs better than 35 iteration of the MatchALS \citep{zhou2015multi} method, but does not perform as well as 50 iterations.
-% We do not perform as well as the Projected Gradient Descent Doubly Stochastic (PGDDS) \citep{leonardos2016distributed} but we perform significantly faster than them.
+% We do not perform as well as the Projected Gradient Descent Doubly Stochastic (PGDDS) \citep{leonardos2017distributed} but we perform significantly faster than them.
 We perform better than a simple eigenvalue based method \citep{pachauri2013solving}.
@@
 Our network, though only using 8 message passes, has comparable accuracy to MatchALS \citep{zhou2015multi} run 35 to 45 iterations, with an equivalent message passing step at each phase.
-Although our method does not outperform the Projected Gradient Descent - Doubly Stochastic (PGDDS) \citep{leonardos2016distributed} method, we perform comparably to them in the ROC AUC metric.
+Although our method does not outperform the Projected Gradient Descent - Doubly Stochastic (PGDDS) \citep{leonardos2017distributed} method, we perform comparably to them in the ROC AUC metric.
 
@@
 We run our trained model on the more Graffiti Dataset from the Affine Covariant Regions dataset (formatted to be able to be input to our model properly).
-The Graffiti Dataset is the most common benchmark used in feature matching algorithms (e.g. \cite{leonardos2016distributed, zhou2015multi}).
+The Graffiti Dataset is the most common benchmark used in feature matching algorithms (e.g. \cite{leonardos2017distributed, zhou2015multi}).
 The results are shown in figure \ref{fig:errorlines} in the rightmost figure.

### 2019-11-15 latex/iclr2020/main.tex
Added another citation

@@
 As an alternative to optimization based techniques, \cite{tron2017fast} used density based clustering techniques to compute multi-image correspondence.
+\cite{fathian2019clear} use a similar technique but formulates it as a generalized Rayleigh quotient problem to achieve better results.
 Moving away from feature matching, \cite{zach2010disambiguating} uses cycle-consistency-like constraints on pose graphs quite effectively.
@@
 There are other methods to build correspondences such as \cite{choy2016universal}, but they only handle two-view constraints and require dense correspondences.
-Most similar to our work, \cite{yi2018learning} attempts to improve correspondences by learning match probabilities for two-view RANSAC for greater robustness and speed.
+\textcolor{red}{Most similar to our work, \cite{zhang2019iccv} use graph neural networks to do intra-image feature processing before doing two image inter-image feature similarity.
+However, their work only trains for pairs of image, while ours is explicitly trained for multi-image matching.}
+Also similarly, \cite{yi2018learning} attempts to improve correspondences by learning match probabilities for two-view RANSAC for greater robustness and speed.
 Like us \cite{zhu2017unpaired} use cycle consistency in their loss; however their method is for image generation and is restricted to pairwise cycle consistency.

### 2019-11-15 latex/iclr2020/main.tex
Added details to appendix

@@
 More fundamentally, deep neural networks need large amounts of labeled data to train.
-In the case of multi-image feature matching, one would need hand-labeled point correspondences between images, which can be difficult and expensive to obtain.
+% In the case of multi-image feature matching, one would need hand-labeled point correspondences between images, which can be difficult and expensive to obtain.
 Consequently unsupervised training is a more practical approach.
@@
 To the best of our knowledge this work is the first to apply deep learning to the multi-view feature matching problem.
-We use an unsupervised loss, the cycle consistency loss, to train the network, thus avoiding the difficulty of expensive hand-labeling.
+We use an unsupervised loss, the cycle consistency loss, to train the network. %, thus avoiding the difficulty of expensive hand-labeling.
 We use geometric consistency losses to aid training, though no geometric information is used at inference time.
@@
 For the initial embedding we use the original 128 dimensional SIFT descriptors, normalized to have unit $L_2$ norm, the calibrated x-y position, the orientation, and log scale of the SIFT feature.
+\textcolor{red}{To calibrate we use the focal lengths provided in Rome16K's data, and we assume the image center is in the center of the image (as none is provided by Rome16K).}
 To construct the graph, we take each feature as a vertex and create edges to the 5 nearest SIFT descriptors for the other images.
@@
 
+\section{\textcolor{red}{Computing Geometric Loss}}
+\textcolor{red}{
+To compute the Geometric Loss during training we use the given rotations and translations from Rome16K to compute the relative poses.
+In practice, one could just use the relative poses computed.
+We build up an intermediate Essential Matrix representations $P, Q \in \sR^{3pv \times 3}$, with $v$ being the number of views and $p$ being the number of points.
+The matrix $P$ is defined by the block matrix representation $P_i = [T_{c(i)}]_\times R_{c(i)} X_i$.
+The matrix $Q$ is defined by the block matrix representation $Q_i = R_{c(i)} X_i$.
+We build the Essential matrices using $E = Q^\top P + P^\top Q$, which has 3 by 3 blocks
+}
+\textcolor{red}{
+\begin{align*}
+E_{ij}
+=&\; (R_{c(i)} X_i)^\top [T_{c(j)}]_\times R_{c(j)} X_j + ([T_{c(i)}]_\times R_{c(i)} X_i)^\top R_{c(j)} X_j \\
+=&\;  X_i^\top R_{c(i)}^\top [T_{c(j)}]_\times R_{c(j)} X_j - X_i^\top R_{c(i)}^\top [T_{c(i)}]_\times R_{c(j)} X_j \\
+=&\;  X_i^\top R_{c(i)}^\top [T_{c(j)} - T_{c(i)}]_\times R_{c(j)} X_j
+\end{align*}
+}
+\textcolor{red}{
+Note that this is the same as equation \ref{eq:essential_constraint} and thus we have our relative pariwise constraints.
+}
+
 \end{document}
